### 2016-02-25 RSymmetry.tex
Added files via upload
Upload of first files

\section{R-Symmetry}
\subsection{R-Symmetry Transformation}
R-symmetry is a global $U(1)$ symmetry. R-symmetry should not be confused with R-parity which is a discrete $Z_2$ symmetry. A continuous global symmetry implies according to Noether's theorem a conserved charge. In the case of R-symmetry this charge is called R-charge and one therefore refers to R-symmetry as $U_R(1)$.\\
The defining property of $U_R(1)$ is that the anticommuting coordinates $\theta^\alpha$ and $\overline{\theta}^{\dot{\alpha}}$ transform like
\begin{align}
&\theta \to \mathrm{e}^{i\alpha}\theta && \overline{\theta} \to \mathrm{e}^{-i\alpha}\overline{\theta},
\end{align}
where $\alpha$ parametrizes the transformation. This in turn implies that R-symmetry does not commute with supersymmetry, meaning that superpartners do not have the same R-charge.\\
The transformation of chiral and vector superfields reads
\begin{align}
& \hat{\Phi}(x,\theta,\overline{\theta}) \to \mathrm{e}^{ir_{\hat{\Phi}}\alpha}\ \hat{\Phi}(x,\mathrm{e}^{i\alpha}\theta,\mathrm{e}^{-i\alpha}\overline{\theta})\nonumber\\
&\hat{V}(x,\theta,\overline{\theta}) \to  \hat{V}(x,\mathrm{e}^{i\alpha}\theta,\mathrm{e}^{-i\alpha}\overline{\theta}).
\end{align}
If one inserts the component decomposition \ref{eq:superfielddecomp} of the superfields one can read off the R-charges of the component fields.
\begin{table}
\begin{center}
\begin{tabular}{c|c||c|c||c|c}
\multicolumn{2}{c||}{superfield} & \multicolumn{2}{c||}{boson} & \multicolumn{2}{c}{fermion} \\
\hhline{=|=#=|=#=|=}
$\hat{\Phi}$ & $r_{\hat{\Phi}}$ & $A$ & $r_{\hat{\Phi}}$ & $\psi$ & $r_{\hat{\Phi}}-1$\\
$\hat{V}$ & 0 & $v^\mu$ & 0 & $\lambda$ & $+1$
\end{tabular}
\caption{This table shows the R-charges of a generic chiral and vector superfield.}
\end{center}
\end{table}

\subsection{The Minimal R-symmetric Supersymmetric Standard Model}
The MSSM with additional R-symmetry is called minimal R-symmetric supersymmetric standard model (MRSSM).
If one imposes R-symmetry upon the MSSM one is faced with a certain arbitrariness, i.e. the choice of the R-charges of the chiral superfields. In this thesis the R-charges are chosen in that way, that every Standard model particle has R-charge zero. Following this one obtains the R-charges of all particles which are summed up in table \ref{tab:R_charges_MRSSM}. 
\begin{table}
\begin{center}
\begin{tabular}{c||c|c||c|c||c|c}
Field & \multicolumn{2}{c||}{Superfield} & \multicolumn{2}{c||}{Boson} & \multicolumn{2}{c}{Fermion} \\
\hhline{=#=|=#=|=#=|=}
Gauge Vector & $\hat{g}$, $\hat{W}$, $\hat{B}$ & 0 & $g$, $W$, $B$ & 0 & $\tilde{g}$, $\tilde{W}$, $\tilde{B}$ &+1\\
Matter & $\hat{L}$, $\hat{E}$ & 0 & $\tilde{l}$, $\tilde{e}_R$ & +1 & $l$, $e_R$ & 0\\
 & $\hat{Q}$, $\hat{D}$, $\hat{U}$ & +1 & $\tilde{q}$, $\tilde{d}^\dagger_R$, $\tilde{u}^\dagger_R$ & +1 & $q$, $d_R$, $u_R$ & 0\\
$H$-Higgs & $\hat{H}_{d,u}$ & 0 & $H_{d,u}$ & 0 & $\tilde{H}_{d,u}$ & -1\\
\hline
$R$-Higgs & $\hat{R}_{d,u}$ & +2 & $R_{d,u}$ & +2 & $\tilde{R}_{d,u}$ & +1\\
Adjoint Chiral & $\hat{O}$, $\hat{T}$, $\hat{S}$ & 0 & $O$, $T$, $S$ & 0 & $\tilde{O}$, $\tilde{T}$, $\tilde{S}$ & -1
\end{tabular}
\caption{This table shows the R-charges of all particles in the MRSSM.}\label{tab:R_charges_MRSSM}
\end{center}
\end{table}
The gauge, matter and $H$-Higgs fields are the fields of the MSSM. Below the horizontal line one finds the fields which are not present in the MSSM, i.e. the $R$-Higgs and adjoint chiral fields. These occur for the following reason.\\
Since in the MSSM the gauginos are Majorana particles their mass terms reads 
\begin{align}
\mathcal{L}_{Majorana\ mass} = -m\lambda\lambda + h.c.
\end{align}
which is not R-invariant because the Weyl fermion $\lambda$ has R-charge +1. The only other way to account for a fermion mass is to write down a Dirac mass term.
\begin{align}
L_{Dirac\ mass} = -m \chi\lambda + h.c.
\end{align}
In order to get a R-symmetric mass term on has to choose the R-charge of the new Weyl-spinor $\chi$ to be the opposite of $\lambda$.\\
This explains the necessity of enlarging the field content if one imposes R-symmetry.\\
Of course the new Weyl-spinor $\chi$ must have also a superpartner. One chooses this superpartner to be a scalar, i.e. the additional Weyl fermion comes from a chiral superfield. In order to maintain gauge invariance this chiral superfield has to transform in the adjoint representation, hence the name adjoint chiral in table \ref{tab:R_charges_MRSSM}. To fix notation the component decomposition of the 8 chiral supermultipletts assosiated to the gluons is given by
\begin{align}
&\hat{O}^a(x, \theta, \overline{\theta}) = \sigma^a + \sqrt{2}\theta i\chi^a + \hdots && a = 1,\hdots,8.
\end{align}
The scalar components $\sigma^a$ are called scalar gluons and the Weyl spinors $\chi^a$ are called octinos.\\
The same argument as for the adjoint chiral explains the existence of additional Higgs-superfields which are referred to as $R$-Higgs fields.\\
But instead of including more fields in the model R-symmetry also forbids terms which are allowed by supersymmetry. For the above choice of R-charges the $\mu$-term in \ref{eq:W_MSSM} and the $A$-terms in the last line of \ref{eq:L_soft} are excluded. As a consequence terms which allow flavor violating processes like $\mu \to e \gamma$ are allowed in the MSSM but forbidden in the MRSSM [Kribs, Popitz, Weiner].

\subsection{The R-symmetric supersymmetric Quantumchromodynacis}
The subject of this thesis is the phenomenology of the strongly coupling sector of the MRSSM. The R-symmetric supersymmetric quantumchromodynamics (RSQCD) is therefore considered closer. Its Lagrangian reads
\begin{align}
\mathcal{L}_{RSQCD} = &\int\mathrm{d}^4\theta\ \left( \hat{\overline{Q}}_L \mathrm{e}^{2g_s\hat{V}_s} \hat{Q}_L + \hat{\overline{Q}}_R \mathrm{e}^{-2g_s\hat{V}^T_s} \hat{Q}_R + \hat{\overline{O}} \mathrm{e}^{2g_s\hat{V}^{fund}_s} \hat{O}\right)\nonumber\\
+& \left( \int \mathrm{d}^2\theta \frac{1}{16g_s^2} \hat{W}_s^{a\alpha}\hat{W}^a_{s\alpha} + h.c. \right) + \mathcal{L}_{soft}
\end{align}
where in terms of component fields the terms are given by
\begin{align}
\int\mathrm{d}^4\theta\ \hat{\overline{Q}}_L \mathrm{e}^{2g_s\hat{V}_s} \hat{Q}_L =\ & F_L^\dagger F_L + (D_\mu \tilde{q}_L)^\dagger (D^\mu \tilde{q}_L) + \overline{q}_L \overline{\sigma}^\mu i D_\mu q_L\nonumber\\
&-\sqrt{2}g_s \left( -i (\tilde{q}_L^\dagger T^a q_L ) \lambda^a + i \overline{\lambda}^a (\overline{q}_L T^a \tilde{q}_L) \right) + g_s\tilde{q}_L^\dagger T^a D^a \tilde{q}_L\label{eq:RSQCD_Feynmanrules1}\\
\int\mathrm{d}^4\theta\ \hat{\overline{Q}}_R \mathrm{e}^{-2g_s\hat{V}^T_s} \hat{Q}_R =\  & F_R^\dagger F_R + (D_\mu \tilde{q}_R)^\dagger (D^\mu \tilde{q}_R) + \overline{q}_R \overline{\sigma}^\mu i D_\mu q_R\nonumber\\
&+\sqrt{2}g_s \left( -i (\tilde{q}_R T^{\ast a} q_R ) \lambda^a + i \overline{\lambda}^a (\overline{q}_R T^{\ast a} \tilde{q}_R^\dagger) \right) - g_s \tilde{q}_R T^{\ast a} D^a \tilde{q}_R^\dagger\label{eq:RSQCD_Feynmanrules2}\\
\int\mathrm{d}^4\theta\ \hat{\overline{O}} \mathrm{e}^{2g_s\hat{V}^{fund}_s} \hat{O} =\  & F_O^\dagger F_O + (D_\mu \sigma^a)^\dagger (D^\mu \sigma^a) + \overline{\chi} \overline{\sigma}^\mu i D_\mu \chi\nonumber\\
&-\sqrt{2}g_s \left( -i (\sigma_{b\dagger} (-if_{abc}) (-i\chi^c) ) \lambda^a + i \overline{\lambda}^a (i\overline{\chi}_b (+if_{abc}) \sigma^{c\dagger}) \right)\nonumber\\
&-ig_s\sigma^{b^\dagger} f^{abc}D^a\sigma^c
\end{align}
where in the gauge covariant derivative $D_\mu = \partial_\mu +ig_sT^aG^a_\mu$ the generator $T^a$ needs to be replaced by $-T^{\ast a}$ or $-if^{abc}$ if applied to a field transforming in the antifundamental or adjoint representation respectively.\\
The soft breaking Lagrangian accounts for the squark, gaugino and scalar gluon masses. These mass terms arise from a hidden sector spurion. For the gauginos the D-type spurion is given by $\hat{W}_\alpha^\prime = \theta_\alpha D$ and mediates super symmetry breaking at the mediation scale $M$: $\int\mathrm{d}\theta^2\frac{\hat{W}_\alpha^\prime}{M}W_s^\alpha \hat{O}$. After integrating out the spurion one obtains
\begin{align}
\mathcal{L}_{soft} =\ & -\frac{m_{\tilde{q}}^2}{2}(|\tilde{q}_L|^2 + |\tilde{q}_R|^2)\nonumber\\
& -\frac{m_{\sigma_1}^2}{2}\sigma_1^2 -\frac{m_{\sigma_2}^2}{2}\sigma_2^2 - m_g(\lambda\chi -\sqrt{2}D^a \sigma^a + h.c.)
\end{align}
where the complex scalar gluons $\sigma = \frac{\sigma_1 + i\sigma_2}{\sqrt{2}}$ constitutes of two real scalar gluons with different masses.
The equations of motion for the auxiliary fields are
\begin{align}
D^a =& -g_s \tilde{q}_L^\dagger T^a \tilde{q}_L + g_s \tilde{q}_R T^a \tilde{q}_R^\dagger + ig_s\sigma^{\dagger b}f^{abc}\sigma^c -\sqrt{2}m_g(\sigma^a + \sigma^{\dagger a})\\
F_i =&\ 0 \hspace{3cm} \mathrm{for} \hspace{3cm} i = L,R,O
\end{align}
where $D^a$ is still real as the purely imaginary parts to not contribute by virtue of the antisymmetry of the structure constants. After eliminating the auxiliary fields the complete Lagrangian in 4 spinor notation\footnote{How a 4 spinor is composed of Weyl-spinors is given in the Appendix \ref{sec:2spinor_notation}} reads
\begin{align}
\mathcal{L}_{RSQCD} = & |D_\mu \sigma|^2 + |D_\mu \tilde{q}_R|^2 + |D_\mu \tilde{q}_L|^2 + \overline{q}i\slashed{D}q + \overline{\tilde{g}}^ai\slashed{D}P_L\tilde{g}^a + \overline{\tilde{g}}^ai\slashed{D}P_R\tilde{g}^a - \frac{1}{4} (F_a^{\mu\nu})^2\nonumber\\
& -\sqrt{2}g_s \left( \overline{\tilde{g}}^a P_R (q^C T^a \tilde{q}_L) + (\tilde{q}_L^\dagger T^a \overline{q}^C)P_L\tilde{g}^a \right)\nonumber\\
& +\sqrt{2}g_s \left( \overline{\tilde{g}}^a P_R (q T^{\ast a} \tilde{q}_R^\dagger) + (\tilde{q}_R T^{\ast a} \overline{q})P_L\tilde{g}^a \right) \nonumber\\
& -\sqrt{2}g_s \left( \overline{\tilde{g}}^a P_R (\tilde{g}^b (if^{abc}) \sigma^c) + (\sigma^{\dagger b} (-if^{abc}) \overline{\tilde{g}}^c)P_L\tilde{g}^a \right) \nonumber\\
& -\frac{m_{\tilde{q}}^2}{2}(|\tilde{q}_L|^2 + |\tilde{q}_R|^2) -\frac{m_{\sigma_1}^2}{2}\sigma_1^2 -\frac{m_{\sigma_2}^2}{2}\sigma_2^2 -m_g \overline{\tilde{g}}^a\tilde{g}^a\nonumber\\
& -\frac{1}{2}\left( g_s \tilde{q}_L^\dagger T^a \tilde{q}_L - g_s \tilde{q}_R T^{\ast a} \tilde{q}_R^\dagger - ig_s\sigma^{\dagger b}f^{abc}\sigma^c + \sqrt{2}m_g(\sigma^a + \sigma^{\dagger a}) \right)^2\label{eq:L_RSQCD}
\end{align}
Observe that there is no 3 sgluon vertex, because of the antisymmetry of the structure constants $f^{abc}$.
\newpage

### 2016-02-25 TreeLevel.tex
Added files via upload
Upload of first files

\section{Sparticle Production at Tree Level}

\subsection{Partonic Processes}
Using the Feynman rules in the Appendix one obtains the following sums over absolute squared Feynman amplitudes
\begin{align}
\sum|\mathcal{M}^B|^2(q_i q_j \to \tilde{q}\tilde{q}) &= \delta_{ij} 2\hat{g}_s^4\left[ \frac{4}{t_{\tilde{g}}^2} + \frac{4}{u_{\tilde{g}}^2} \right] (tu-m_{\tilde{q}}^4) + (1-\delta_{ij}) ??? \nonumber\\
\sum|\mathcal{M}^B|^2(q_i\overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij} 4 \left[ g_s^4\frac{8n_f}{s^2} + \hat{g}_s^4\frac{4}{t_{\tilde{g}}^2} - g_s^2\hat{g}_s^2\frac{8}{3 t_{\tilde{g}} s} \right] (tu-m_{\tilde{q}}^2) + (1-\delta_{ij})??? \nonumber\\
\sum|\mathcal{M}^B|^2(gg \to \tilde{q}\tilde{q}^\dagger) &= 4 n_f g_s^4 \left[ 24\left(1-2\frac{(t_{\tilde{q}}u_{\tilde{q}})}{s^2}\right)-\frac{8}{3} \right] \left[ 1-\epsilon-2\frac{s m_{\tilde{q}}^2}{t_{\tilde{q}}u_{\tilde{q}}} \left( 1-\frac{s m_{\tilde{q}}^2}{t_{\tilde{q}}u_{\tilde{q}}} \right)\right]?\nonumber\\
\sum|\mathcal{M}^B|^2(q_i\overline{q}_j \to \tilde{g}\tilde{g}) &= \delta_{ij}\left\{ 96 g_s^4 \left[ \frac{2m_{\tilde{g}}^2 s + t_{\tilde{g}}^2 + u_{\tilde{g}}^2}{s^2} -\epsilon \right]\right.\nonumber\\
&\ 96 g_s^2 \hat{g}_s^2\left[ \frac{m_{\tilde{g}}^2 s + t_{\tilde{g}}^2}{s t_{\tilde{q}}} + \frac{m_{\tilde{g}}^2 s + u_{\tilde{g}}^2}{su_{\tilde{q}}} + \epsilon\left( \frac{t_{\tilde{g}}}{t_{\tilde{q}}} + \frac{u_{\tilde{g}}}{u_{\tilde{q}}} \right) \right]\nonumber\\
&\ + \left.2\hat{g}_s^4\left[ 24\left( \frac{t_{\tilde{g}}^2}{t_{\tilde{q}}^2} + \frac{u_{\tilde{g}}^2}{u_{\tilde{q}}^2} \right) + \frac{8}{3}\left( 2\frac{m_{\tilde{g}}^2 s}{t_{\tilde{q}}u_{\tilde{q}}} - \frac{t_{\tilde{g}}^2}{t_{\tilde{q}}^2} - \frac{u_{\tilde{g}}^2}{u_{\tilde{q}}^2} \right) \right]\right\} ??? \nonumber\\
\sum|\mathcal{M}^B|^2(gg \to \tilde{g}\tilde{g}) &=  576 g_s^4 \left( 1- \frac{t_{\tilde{g}}u_{\tilde{g}}}{s^2} \right)\left[ \frac{s^2}{t_{\tilde{g}}u_{\tilde{g}}}(1-\epsilon)^2-2(1-\epsilon) + s\frac{m_{\tilde{g}}^2 s}{t_{\tilde{g}}u_{\tilde{g}}}\left(1-\frac{m_{\tilde{g}}^2 s}{t_{\tilde{g}}u_{\tilde{g}}}  \right) \right] ??? \nonumber\\
\sum|\mathcal{M}^B|^2(qg \to \tilde{q}\tilde{g}) &=  2g_s^2\hat{g}_s^2 \left[ 24\left(1-2\frac{s u_{\tilde{q}}}{t_{\tilde{g}}^2}\right) - \frac{8}{3} \right]\left[ (-1+\epsilon)\frac{t_{\tilde{g}}}{s} + \frac{2(m_{\tilde{g}}^2-m_{\tilde{q}}^2)t_{\tilde{g}}}{s u_{\tilde{q}}}\left( 1+\frac{m_{\tilde{q}}^2}{u_{\tilde{q}}} + \frac{m_{\tilde{g}}^2}{t_{\tilde{g}}} \right) \right]???
\end{align}
For NLO-corrections the results are expanded up to $\mathcal{O}(\epsilon)$. Furthermore the usual Mandelstam variables $s,t,u$ and the following modifications of them are used:
\begin{align}
& t_{\tilde{g}} = t - m_{\tilde{g}}^2 && t_{\tilde{q}} = t- m_{\tilde{q}}^2\nonumber\\
& u_{\tilde{g}} = u - m_{\tilde{g}}^2 && u_{\tilde{q}} = u- m_{\tilde{q}}^2
\end{align}

\subsection{Partonic Cross Sections}
\begin{align}
\frac{\mbox{d}^2 \sigma}{\mbox{d}t\mbox{d}u} = \frac{K_{ij}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_{\tilde{q}}^4}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_{\tilde{q}}^4) \Theta(s-4m_{\tilde{q}}^2) \delta(s+t+u-2m_{\tilde{q}}^2) \sum |\mathcal{M}^B|^2
\end{align}
with $S_\epsilon = (2\pi)2-2\epsilon$???
\begin{align}
\sigma(gg \to \tilde{q}\tilde{q}^\dagger) = \frac{n_f g_s^4}{16\pi s} \left[ \left(\frac{5}{24} + \frac{31 m_{\tilde{q}}^2}{12s}\right)\beta_{\tilde{q}} + \left( \frac{m_{\tilde{q}}^4}{3s^2} + \frac{4m_{\tilde{q}}^2}{s}\right) \ln \frac{1-\beta_{\tilde{q}}}{1+\beta_{\tilde{q}}} \right]
\end{align}
where the abbreviations 
\begin{align}
\beta_{\tilde{q}} = \sqrt{1-\frac{4 m_{\tilde{q}}^2}{s}}
\end{align}
are used.\cite{Beenakker}

\subsection{Hadronic Cross Section}
factorization (pictorial explanation in factorization paper chapter 1.4)
The hadronic cross section for the production of a final state $X$, e.g. $X = \tilde{q},\tilde{q}$, can be obtained by convolving the partonic cross section with the parton density function of the initial partons.
\begin{align}
\sigma^B(ij \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_i(x_1) f_j(x_2)\ \sigma^B (ij \to X, s = x_ 1x_2 S).
\end{align}
As the production of the final state $X$ may proceed with various initial partons one has to sum over all possible possibilities arising from the initial hadrons $H_1$ and $H_2$:
\begin{align}
\sigma^B(H_1 H_2 \to X) = \sum_{i,j} \sigma^B(i,j \to X).
\end{align}
refer to Kribs, Martin

### 2016-02-25 custom_commands_Theorie.tex
Added files via upload
Upload of first files

% Differential quotients
\newcommand{\tdfrac} [2]{\ensuremath{\frac{\mathrm{d}   #1}{\mathrm{d} {#2}}}}%
\newcommand{\tddfrac}[2]{\ensuremath{\frac{\mathrm{d}^2 #1}{\mathrm{d} {#2}^2}}}%
\newcommand{\pdfrac} [2]{\ensuremath{\frac{\partial     #1}{\partial   {#2}}}}%
\newcommand{\pddfrac}[2]{\ensuremath{\frac{\partial^2   #1}{\partial   {#2}^2}}}%
\newcommand{\varfrac} [2]{\ensuremath{\frac{\delta     #1}{\delta   {#2}}}}%

% Merke-Umgebung
\usepackage{shadethm}
\newshadetheorem{remark_}{Merke}
\newenvironment{remark}[1][]{%
  \definecolor{shadethmcolor}{rgb}{.9,.9,.9}       % Farbe Hintergrund
  \definecolor{shaderulecolor}{rgb}{1.0,0.0,0.0}   % Farbe Rahmen
  \setlength{\shadeboxrule}{1pt}%
  \begin{remark_}[#1]%
}{\end{remark_}}

% Einschub-Umgebung
\newshadetheorem{insertion_}{Einschub}
\newenvironment{insertion}{
  \definecolor{shadethmcolor}{rgb}{0.9,0.8,.9}
  \definecolor{shaderulecolor}{rgb}{0.0,0.0,1}
  \setlength{\shadeboxrule}{1pt}
  \begin{insertion_}%\hspace*{1mm}
}{\end{insertion_}}

% Nebenrechnung-Umgebung
\newshadetheorem{auxcal_}{Nebenrechnung}
\newenvironment{auxcal}{
  \definecolor{shadethmcolor}{rgb}{0.7,0.9,0.9}
  \definecolor{shaderulecolor}{rgb}{0.0,0.1,0.1}
  \setlength{\shadeboxrule}{1pt}
  \begin{auxcal_}%\hspace*{1mm}
}{\end{auxcal_}}

% tikz-Packete
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{fit}
\usetikzlibrary{shadows}

% eigene Befehle für tikz
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block1} = [rectangle, draw, fill=blue!20, 
text width=10em, text centered, rounded corners, minimum height=4em]
\tikzstyle{block2} = [rectangle, draw, fill=red!20, 
text width=10em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm, minimum height=2em]

% These are examples of Feynman Diagrams using TikZ
% Author: Flip Tanedo, 2010. pt267@cornell.edu
%\documentclass[12pt]{article}	% Why do I use such a boring document clas?
% THE USUAL PACKAGES
\usepackage{amsmath,amssymb,amsfonts}	% DON'T use cite, screws with bibtex + hyperref
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{slashed}            % for slashed characters in math mode
\usepackage{bbm}                % for \mathbbm{1} (unit matrix)
\usepackage{xspace}				% For spacing after commands
% TIKZ - for drawing Feynman diagrams
% ... use with pdflatex
\usepackage{tikz}
\usetikzlibrary{arrows,shapes}
\usetikzlibrary{trees}
\usetikzlibrary{matrix,arrows} 				% For commutative diagram
											% http://www.felixl.de/commu.pdf
\usetikzlibrary{positioning}				% For "above of=" commands
\usetikzlibrary{calc,through}				% For coordinates
\usetikzlibrary{decorations.pathreplacing}  % For curly braces
% http://www.math.ucla.edu/~getreuer/tikz.html
\usepackage{pgffor}							% For repeating patterns
\usetikzlibrary{decorations.pathmorphing}	% For Feynman Diagrams
\usetikzlibrary{decorations.markings}
\tikzset{
	% >=stealth', %%  Uncomment for more conventional arrows
    vector/.style={decorate, decoration={snake}, draw},
	provector/.style={decorate, decoration={snake,amplitude=2.5pt}, draw},
	antivector/.style={decorate, decoration={snake,amplitude=-2.5pt}, draw},
    fermion/.style={draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},   
    fermionbar/.style={draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
    fermionnoarrow/.style={draw=black},
    gluon/.style={decorate, draw=black,
        decoration={coil,amplitude=4pt, segment length=5pt}},
    scalar/.style={dashed,draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
    scalarbar/.style={dashed,draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
    scalarnoarrow/.style={dashed,draw=black},
    electron/.style={draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
	bigvector/.style={decorate, decoration={snake,amplitude=4pt}, draw},
	ghost/.style={dotted,draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
	ghostbar/.style={dotted,draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
}
% TIKZ - for block diagrams, 
% from http://www.texample.net/tikz/examples/control-system-principles/
% \usetikzlibrary{shapes,arrows}
\tikzstyle{block} = [draw, rectangle, 
    minimum height=3em, minimum width=6em]
% circled numbers
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
\usepackage{hyperref}			% Has to be at the end.

### 2016-02-25 Appendix.tex

\section{Appendix}

\subsection{System of Units and Metric}
In this thesis the natural units are used, i.e. $c= \hbar (= k_B) = 1$. Furthermore the Minkowski metric is chosen to be
\begin{align}
g^{\mu\nu} = \mathrm{diag}(1, -1, -1, -1).
\end{align}

\subsection{Colour Algebra $SU(N)$}
[Marina von Steinkirch]\\
Tha Casimir operator $C(R)\mathbbm{1}$ of a semi-simple Lie algebra in the irreducible representation $R$ is given by
\begin{align}
g^{ab} T^a(R)T^b(R) = C(R)\mathbbm{1} \label{eq:Casimir}
\end{align}
where $T^a(R)$ is the $a$-th generator of the matrix valued representation $R$, $g^{ab}$ is the metric of group, $C(R)$ is the Quadratic Casimir invariant of the representation $R$ and $\mathbbm{1}$ is the identity in the representation space.\\
Apart from $C(R)$ it is common to define the Dynkin-Index $T(R)$:
\begin{align}
\mathrm{Tr}\left[T^a(R)T^b(R)\right] = T(R)\delta^{ab}.
\end{align}
The two constants are connected by
\begin{align}
C(R) \cdot \mathrm{dim}(R) = T(R) \cdot \mathrm{dim}(G)
\end{align}
where $\mathrm{dim}(G)$ is the dimension of the group and $\mathrm{dim}(R)$ is the dimension of the irreducible representation $R$.\\
In the case of $SU(N)$ one has a diagonal metric $g^{ab} = \delta^{ab}$ and therefore \ref{eq:Casimir} turns to
\begin{align}
\sum_a (T^a(R))^2 = C(R)\mathbbm{1}_{\mathrm{dim}(R) \times \mathrm{dim}(R)}
\end{align}
and one can write down the following useful formulae for the fundamental representation $R=F$: $T^a_{ij} = \frac{\lambda^a_{ij}}{2}$ and the adjoint representation $R=A$: $(T^a_{ij})^{adj} = -if_{aij}$
\begin{align}
T^a_{ik} T^a_{kj} &= C(F)\mathbbm{1}_{ij} && \mbox{with}\ C(F) = \frac{N^2-1}{2N} = \frac{4}{3}\nonumber\\
f^{abc} f^{dbc} &= C(A)\delta^{ad} && \mbox{with}\ C(A) = N = 3\nonumber\\
\mathrm{Tr}\left[T^aT^b\right] &= T(F)\delta^{ab} && \mbox{with}\ T(F) = \frac{1}{2}
\end{align}
where $\lambda^a_{ij}$ are for $N_c = 3$ the Gell-Mann matrices and $f_{abc}$ are the structure constants of $SU(N_c)$.
%\begin{tabular}{c|c|c}
%Quadratic Casimir Invariant and $T(R)$ & $SU(N)_c$ & $SU(3)_c$\\
%\hline
%$C_2(3)$ & $\frac{N^2-1}{2N}$ & $\frac{4}{3}$\\
%$C_2(8)$ & $N$ & $3$\\
%$T(3)$ & $\frac{1}{2}$ & $\frac{1}{2}$ \\
%$T(8)$ & $N$ & $3$ 
%\end{tabular}

\subsection{Weyl basis and 2-spinor notation}\label{sec:2spinor_notation}
As representation of the $\gamma$-matrices the Weyl or chiral representation is chosen:
\begin{align}
&\gamma^\mu = \begin{pmatrix}
0 && \sigma^\mu\\
\overline{\sigma}^\mu && 0
\end{pmatrix} &&
\gamma_5 = \begin{pmatrix}
-\mathbbm{1}_2 && 0\\
0 && \mathbbm{1}_2
\end{pmatrix}
\end{align}
with
\begin{align}
&\sigma^\mu = \begin{pmatrix}
\mathbbm{1}_2 && \sigma^i
\end{pmatrix}, &&
\overline{\sigma}^\mu = \begin{pmatrix}
\mathbbm{1}_2 && -\sigma^i
\end{pmatrix},\label{eq:Pauli}
\end{align}
where $\sigma^i$ are the Pauli matrices and $\mathbbm{1}_n$ is the $n$x$n$ unit matrix. The left and right handed projectors are then given by
\begin{align}
P_L = \frac{1}{2}(\mathbbm{1}_4 - \gamma_5)\begin{pmatrix}
\mathbbm{1}_2 && 0\\
0 && 0
\end{pmatrix} && 
P_R = \frac{1}{2}(\mathbbm{1}_4 + \gamma_5)\begin{pmatrix}
0 && 0\\
0 && \mathbbm{1}_2
\end{pmatrix}\label{eq:projectors}
\end{align}
The generator of the Lorentz group on 4-spinor space is composed of the above matrices. Because of the block form of those it is not surprising that the representation on 4-spinor space is reducible to two representations on 2-spinor (Weyl spinor) spaces. It is therefore sensible to decompose a 4 spinor into a left and a right handed Weyl spinor\footnote{The projectors in the chiral basis \ref{eq:projectors} explain the names left and right handed Weyl spinors.}
\begin{align}
\Psi = \begin{pmatrix}
\psi_\alpha \\
\overline{\chi}^{\dot{\alpha}}
\end{pmatrix}
\end{align}
where $\alpha,\dot{\alpha} = 1,2$. Left handed Weyl spinors are labeled with undotted and right handed Weyl spinors with dotted indices. One distinguishes 4 different Weyl spinors:
\begin{align}
\psi^\alpha, \hspace{1cm} 
\overline{\psi}^{\dot{\alpha}} = (\psi^\alpha)^\ast, \hspace{1cm} \psi_\alpha = \epsilon_{\alpha\beta}\psi^\beta, \hspace{1cm} \mathrm{and} \hspace{1cm} \psi_{\dot{\alpha}} = \epsilon_{\dot{\alpha}\dot{\beta}}\psi^{\dot{\beta}} = (\psi_\alpha)^\ast,
\end{align}
where $^\ast$ denotes complex conjugation and indices are lowered with the antisymmetric $\epsilon_{\alpha\beta}$ ($\epsilon_{\dot{\alpha}\dot{\beta}}$), which obeys
\begin{align}
\epsilon^{\alpha\beta} = \epsilon_{\beta\alpha},\ \epsilon^{\dot{\alpha}\dot{\beta}} = \epsilon_{\dot{\beta}\dot{\alpha}} \hspace{3cm} \mathrm{and} \hspace{3cm} \epsilon_{12} = \epsilon_{\dot{1}\dot{2}}= 1.
\end{align}
By virtue of the antisymmetry of $\epsilon$ one has for the Lorentz invariant product:
\begin{align}
\psi\chi &:= \psi^\alpha\chi_\alpha = -\chi_\alpha\psi^\alpha = \chi^\alpha\psi_\alpha = \chi\psi,\nonumber\\
\overline{\psi}\overline{\chi} &:= \overline{\psi}_{\dot{\alpha}} \overline{\chi}^{\dot{\alpha}} = -\overline{\chi}^{\dot{\alpha}}\overline{\psi}_{\dot{\alpha}} = \overline{\chi}_{\dot{\alpha}}\overline{\psi}^{\dot{\alpha}} = \overline{\chi}\overline{\psi} \label{eq:Weylspinorproduct}
\end{align}
To make the index structure of the Pauli matrices explicit one writes $\sigma^\mu_{\alpha\dot{\alpha}}$ and $\sigma^{\mu\dot{\alpha}\alpha}$ for the formulae in \ref{eq:Pauli}. For the definition of the super algebra in ??? the generators of the Lorentz group on the left and right handed Weyl spinor space are introduced:
\begin{align}
\frac{1}{2}(\sigma^{\mu\nu})_\alpha^{\ \beta} := \frac{i}{4}(\sigma^\mu\overline{\sigma}^\nu - \sigma^\nu\overline{\sigma}^\mu)_\alpha^{\ \beta}\nonumber\\
\frac{1}{2}(\overline{\sigma}^{\mu\nu})^{\dot{\alpha}}_{\ \dot{\beta}} := \frac{i}{4}(\overline{\sigma}^\mu\sigma^\nu - \overline{\sigma}^\nu\sigma^\mu)^{\dot{\alpha}}_{\ \dot{\beta}}
\end{align}

With the definition of bared and charge conjugated 4-spinors\footnote{$\Psi^T$ denotes the transpose of the spinor $\Psi$ and $\Psi^\dagger$ is the Hermitian adjoint of $\Psi$.}
\begin{align}
&\overline{\Psi} := \Psi^\dagger \gamma^0, && \Psi^C := i\gamma^2\gamma^0 \overline{\Psi}^T  
\end{align}
one obtains:
\begin{align}
\Psi &= \begin{pmatrix}
\psi_\alpha \\
\overline{\chi}^{\dot{\alpha}}
\end{pmatrix}, && \ \ 
\overline{\Psi} = \begin{pmatrix}
\chi^\alpha & \overline{\psi}_{\dot{\alpha}}
\end{pmatrix},\nonumber\\
\Psi^C &= \begin{pmatrix}
\chi_\alpha \\
\overline{\psi}^{\dot{\alpha}}
\end{pmatrix}, && 
\overline{\Psi}^C = \begin{pmatrix}
\psi^\alpha & \overline{\chi}_{\dot{\alpha}}
\end{pmatrix}.
\end{align}
The 4-spinor of an arbitrary quark $q$ is given in terms of Weyl spinors $q_L$ and $\overline{q}_R$ by
\begin{align}
q = \begin{pmatrix}
q_L \\
\overline{q}_R
\end{pmatrix}
\end{align}
whereas the 4-spinor of the Dirac gauginos is given in terms of the Weyl spinors $\lambda$ and $\overline{\chi}$\footnote{$\lambda$ is the superpartner of the gluon, called the gluino and $\overline{\chi}$ is the Weyl spinor of the chiral superfield which is associated with the gluon, called the octino.}
\begin{align}
\tilde{g}^a = \begin{pmatrix}
-i \lambda^a \\
i \overline{\chi}^a
\end{pmatrix}
\end{align}

\subsection{Anticommuting numbers}
Anticommuting numbers $\theta^\alpha$ are also referred to as Grassmann numbers and are defined by $\theta^\alpha\theta^\beta = -\theta^\beta\theta^\alpha$ and commute with ordinary numbers.\\
They occur in superspace formalism in the form of 2 tuples, i.e. $\theta^\alpha$ with $\alpha=1,2$. The complex conjugate of this tuple is denoted with $\overline{\theta}^{\dot{\alpha}}$. 
Derivatives are defined by
\begin{align}
\partial^\alpha \theta_\beta := \frac{\partial}{\partial \theta_\alpha} \theta_\beta := \delta^\alpha_\beta \hspace{4cm} \partial_\alpha \theta^\beta := \frac{\partial}{\partial \theta^\alpha} \theta^\beta := \delta_\alpha^\beta\nonumber\\
\overline{\partial}^{\dot{\alpha}} \overline{\theta}_{\dot{\beta}} := \frac{\partial}{\partial \overline{\theta}_{\dot{\alpha}}} \overline{\theta}_{\dot{\beta}} := \delta^{\dot{\alpha}}_{\dot{\beta}} \hspace{4cm} \overline{\partial}_{\dot{\alpha}} \overline{\theta}^{\dot{\beta}} := \frac{\partial}{\partial \overline{\theta}^{\dot{\alpha}}} \overline{\theta}^{\dot{\beta}} := \delta_{\dot{\alpha}}^{\dot{\beta}}
\end{align}
whereby one needs to be cautious as these definitions imply
\begin{align}
\partial_\alpha = -\epsilon_{\alpha\beta}\partial^\beta \hspace{4cm} \partial_{\dot{\alpha}} = -\epsilon_{\dot{\alpha}\dot{\beta}}\partial^{\dot{\beta}}.
\end{align}
Integrals are defined by:
\begin{align}
\int\mathrm{d}\theta_\alpha\ (a+b \theta^\beta + c\theta^\beta \theta^\gamma) := b\delta_{\alpha}^{\beta} + c (\delta_\alpha^\beta \theta^\gamma - \delta_\alpha^\gamma \theta^\beta) \hspace{1cm} \mathrm{and} \hspace{1cm}
\int\mathrm{d}\theta_\alpha\ (a\overline{\theta}^{\dot{\beta}}) := (a\overline{\theta}^{\dot{\beta}}) \int\mathrm{d}\theta_\alpha\
\end{align}
where the first line mirrows the claim of translation invariance. One furthermore introduces the shortcuts
\begin{align}
\int \mathrm{d}\theta^2 = \int\frac{1}{4}\epsilon_{\alpha\beta} \mathrm{d}\theta^\alpha\mathrm{d}\theta^\beta, \hspace{1cm}
\int \mathrm{d}\overline{\theta}^2 = \int\frac{1}{4}\epsilon_{\dot{\alpha}\dot{\beta}} \mathrm{d}\theta^{\dot{\alpha}}\mathrm{d}\theta^{\dot{\beta}}, \hspace{1cm} \mathrm{and} \hspace{1cm}
\int \mathrm{d}^4\theta := \int \mathrm{d}\theta^2\mathrm{d}\overline{\theta}^2
\end{align}

\subsection{Feynman rules for the RSQCD}
The following Feynman rules are derived from \ref{eq:L_RSQCD}. When compared with the Feynman rules of the supersymmetric QCD the diagrams involving scalar gluons are new. In addition the gluon-quark-squark vertex is different in RSQCD for the gauginos are Dirac fermions.\\
refer to paper cited in Beenakker(Appendix: Feynmanrules)
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\node at (-0.5,0.7) {\circled{1}};	
	\draw[scalarnoarrow](0,0)--(1.5,0);
	\node at (180:0.4) {$(\sigma^0)^a$};
	\node at (0:1.9) {$(\sigma^0)^b$};
	\node at (3.4,0) {$\hat{=}\ \frac{i}{p^2-m_{\sigma^0}^2+i\varepsilon}\delta_{ab}$};
\begin{scope}[shift={(7,0)}]
	\node at (-0.5,0.7) {\circled{2}};
	\draw[scalarnoarrow](0,0)--(1.5,0);
	\node at (180:0.4) {$(\phi^0)^a$};
	\node at (0:1.9) {$(\phi^0)^b$};
	\node at (3.4,0) {$\hat{=}\ \frac{i}{p^2-m_{\phi^0}^2+i\varepsilon}\delta_{ab}$};
\end{scope}
\begin{scope}[shift={(0,-2)}]
	\node at (-0.5,0.7) {\circled{3}};
	\draw[scalarbar](0,0)--(1.5,0);
	\node at (180:0.3) {$\tilde{q}_{Ai}$};
	\node at (0:1.8) {$\tilde{q}_{Bj}^\dagger$};
	\node at (3,0) {$\hat{=}\ \frac{i\delta_{AB}}{p^2-m_{\tilde{q}}^2+i\varepsilon}\delta_{ij}$};
\end{scope}
\begin{scope}[shift={(7,-2)}]
	\node at (-0.5,0.7) {\circled{4}};
	\draw[fermionbar](0,0)--(1.5,0);
	\node at (180:0.2) {$q_i$};
	\node at (0:1.7) {$\overline{q}_j$};
	\node at (3,0) {$\hat{=}\ i\frac{\slashed{p}+m_q}{p^2-m_q^2+i\varepsilon}\delta_{ij}$};
\end{scope}
\begin{scope}[shift={(0,-4)}]
	\draw[gluon](1.5,0)--(0,0);
	\node at (-0.5,0.7) {\circled{5}};
	\node at (180:0.2) {$G_\mu^a$};
	\node at (0:1.7) {$G_\nu^b$};
	\node at (3,0) {$\hat{=}\ -i\frac{g^{\mu\nu}}{p^2+i\varepsilon}\delta_{ab}$};
\end{scope}
\begin{scope}[shift={(7,-4)}]
	\node at (-0.5,0.7) {\circled{6}};
	\draw[gluon](1.5,0)--(0,0);
	\draw[fermionnoarrow](0,0)--(1.5,0);
	\node at (180:0.2) {$\tilde{g}^a$};
	\node at (0:1.7) {$\overline{\tilde{g}}^b$};
	\node at (3,0) {$\hat{=}\ i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2+i\varepsilon}\delta_{ab}$};
\end{scope}
\begin{scope}[shift={(0,-6)}]
	\node at (-0.5,0.7) {\circled{7}};
	\draw[ghostbar](0,0)--(1.5,0);
	\node at (180:0.3) {$c^{a}$};
	\node at (0:1.8) {$\overline{c}^{b}$};
	\node at (3,0) {$\hat{=}\ \frac{i}{p^2+i\varepsilon}\delta_{ab}$};
\end{scope}

\begin{scope}[shift={(1,-8)}]
	\node at (-1.5,0.7) {\circled{8}};
	\draw[fermion] (0,0)--(45:1);
	\draw[fermionbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.3) {$\overline{q}i$};
	\node at (-45:1.3) {$q_j$};
	\node at (180:1.3) {$G_\mu^a$};
	\node at (2,0) {$\hat{=} -ig_s T^a_{ij}\gamma^\mu$};
\end{scope}
\begin{scope}[shift={(8,-8)}]
	\node at (-1.5,0.7) {\circled{9}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.4) {$\tilde{q}^\dagger_{Ai}(-p_1)$};
	\node at (-45:1.4) {$\tilde{q}_{Bj}(p_2)$};
	\node at (180:1.3) {$G_\mu^a$};
	\node at (3,0) {$\hat{=} -ig_s (p_2+p_1)^\mu T^a_{ij}\delta_{AB}$};
\end{scope}
\begin{scope}[shift={(1,-10.5)}]
	\node at (-1.5,0.7) {\circled{10}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(135:1);
	\draw[gluon] (0,0)--(-135:1);
	\node at (45:1.4) {$\tilde{q}^\dagger_{Ai}$};
	\node at (-45:1.4) {$\tilde{q}_{Bj}$};
	\node at (135:1.4) {$G_\mu^a$};
	\node at (-135:1.4) {$G_\nu^b$};
	\node at (3,0) {$\hat{=} \ ig_s^2 g^{\mu\nu} \left\{T^a,T^b\right\}_{ij}\delta_{AB}$};
\end{scope}
\begin{scope}[shift={(1,-13.5)}]
	\node at (-1.5,0.7) {\circled{11}};
	\draw[gluon] (0,0)--(45:1);
	\draw[gluon] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.4) {$G_\mu^a(p_a)$};
	\node at (-45:1.4) {$G_\nu^b(p_b)$};
	\node at (180:1.5) {$G_\rho^c(p_c)$};
	\node at (5.5,0) {$\hat{=}  - g_s f_{abc} \left[ g_{\mu\nu}(p_a-p_b)^\rho +\  g_{\nu\rho}(p_b-p_c)^\mu +  g_{\rho\mu}(p_c-p_a)^\nu \right]$};
\end{scope}
\end{tikzpicture}
\caption{In the Feynman diagrams of the propagators the momentum is flowing from the right to the left hand side.\newline
In the Feynman diagrams of the vertices all momenta flow towards the vertex.\newline
The indices $A,B = L,R$ label the right/left-"handedness" of the squarks. The indices $i,j=1,2,3$ are the color indices in the (anti)fundamental representation where $a,b,c,\hdots = 1,\hdots,8$ are the color indices of the adjoint representation. }
\end{center}
\end{figure}
\newpage

%The gluino-quark-squark vertex is not much different from the one in SQCD. One only must avoid replacing $\tilde{g}$ with $\tilde{g}^C$. %See for the derivation of Feynman rules for theories with fermion number violating interaction reference [a. denner, h.eck, o. hahn, j. küblbeck]
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\node at (-1.5,0.7) {\circled{12}};
	\draw[gluon] (0,0)--(45:1);
	\draw[gluon] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(135:1);
	\draw[gluon] (0,0)--(-135:1);
	\node at (45:1.4) {$G_\rho^c$};
	\node at (-45:1.4) {$G_\sigma^d$};
	\node at (135:1.4) {$G_\mu^a$};
	\node at (-135:1.4) {$G_\nu^b$};
	\node at (5.5,0) {$\hat{=} \ -ig_s^2 [f^{abe}f^{cde}(g^{\mu\rho} g^{\nu\sigma} - g^{\mu\sigma}g^{\nu\rho}) + f^{ace}f^{bde}(g^{\mu\nu} g^{\rho\sigma} - g^{\mu\sigma}g^{\nu\rho}) $};
	\node at (8,-0.5) {$+ f^{ade}f^{bce}(g^{\mu\nu} g^{\rho\sigma} - g^{\mu\rho}g^{\nu\sigma})]$};
\begin{scope}[shift={(0,-2.5)}]
	\node at (-1.5,0.7) {\circled{13}};
	\draw[gluon] (0,0)--(180:1);
	\draw[gluon] (0,0)--(45:1);
	\draw[gluon] (0,0)--(-45:1);
	\draw[fermionnoarrow] (0,0)--(-45:1);
	\draw[fermionnoarrow] (0,0)--(45:1);
	\node at (45:1.4) {$\overline{\tilde{g}}^b$};
	\node at (-45:1.4) {$\tilde{g}^c$};
	\node at (180:1.5) {$G_\mu^a$};
	\node(gbar) at (0.9,0.6) {};
	\node(g) at (0.9,-0.6) {};
	\path[line width=0.8pt,->] (g) edge [out=135, in=-135] (gbar);
	\node at (2,0) {$\hat{=}  - g_s f_{abc} \gamma^\mu$};
\end{scope}
\begin{scope}[shift={(7,-2.5)}]
	\node at (-1.5,0.7) {\circled{14}};
	\draw[gluon] (0,0)--(180:1);
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\node at (40:1.4) {$\sigma^{b\dagger}(-p_1)$};
	\node at (-40:1.4) {$\sigma^c(p_2)$};
	\node at (180:1.5) {$G_\mu^a$};
	\node at (3,0) {$\hat{=}  - g_s (p_1+p_2)^\mu f_{abc} $};
\end{scope}
\begin{scope}[shift={(0,-5)}]
	\node at (-1.5,0.7) {\circled{15}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(135:1);
	\draw[gluon] (0,0)--(-135:1);
	\node at (45:1.4) {$\sigma^{\dagger c}$};
	\node at (-45:1.4) {$\sigma^d$};
	\node at (135:1.4) {$G_\mu^a$};
	\node at (-135:1.4) {$G_\nu^b$};
	\node at (3,0) {$\hat{=} \ +ig_s^2 g^{\mu\nu}[f^{aec}f^{bed}+ f^{bec}f^{aed}]$};
\end{scope}
\begin{scope}[shift={(0,-7.5)}]
	\node at (-1.5,0.7) {\circled{16a}};
	\draw[scalar] (0,0)--(45:1);
	\draw[fermionbar] (0,0)--(-45:1);
	\draw[fermionnoarrow] (180:1)--(0,0);
	\draw[gluon] (180:1)--(0,0);
	\node at (45:1.3) {$\tilde{q}_{Li}^\dagger$};
	\node at (-45:1.3) {$\overline{q}^C_j$};
	\node at (180:1.3) {$\tilde{g}^a$};
	\node(g) at (-0.7,-0.3) {};
	\node(u) at (0.4,-0.8) {};
	\path[line width=0.8pt,->] (g) edge [out=0, in=135] (u);
	\node at (3,0) {$\hat{=} -i\sqrt{2}g_s T^a_{ij}P_L$};
\end{scope}
\begin{scope}[shift={(7,-7.5)}]
	\node at (-1.5,0.7) {\circled{16b}};
	\draw[fermion] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[fermionnoarrow] (180:1)--(0,0);
	\draw[gluon] (180:1)--(0,0);
	\node at (45:1.3) {$q^C_i$};
	\node at (-45:1.3) {$\tilde{q}_{Lj}$};
	\node at (180:1.3) {$\overline{\tilde{g}}^a$};
	\node(g) at (-0.7,0.3) {};
	\node(u) at (0.4,0.8) {};
	\path[line width=0.8pt,->] (g) edge [out=0, in=225] (u);
	\node at (3,0) {$\hat{=} -i\sqrt{2}g_s T^a_{ij}P_R$};
\end{scope}
\begin{scope}[shift={(0,-10)}]
	\node at (-1.5,0.7) {\circled{17a}};
	\draw[scalarbar] (0,0)--(45:1);
	\draw[fermion] (0,0)--(-45:1);
	\draw[fermionnoarrow] (180:1)--(0,0);
	\draw[gluon] (180:1)--(0,0);
	\node at (45:1.3) {$\tilde{q}_{Rj}$};
	\node at (-45:1.3) {$\overline{q}_i$};
	\node at (180:1.3) {$\tilde{g}^a$};
	\node(g) at (-0.7,-0.3) {};
	\node(u) at (0.4,-0.8) {};
	\path[line width=0.8pt,->] (g) edge [out=0, in=135] (u);
	\node at (3,0) {$\hat{=} +i\sqrt{2}g_s T^a_{ij}P_L$};
\end{scope}
\begin{scope}[shift={(7,-10)}]
	\node at (-1.5,0.7) {\circled{17b}};
	\draw[fermionbar] (0,0)--(45:1);
	\draw[scalar] (0,0)--(-45:1);
	\draw[fermionnoarrow] (180:1)--(0,0);
	\draw[gluon] (180:1)--(0,0);
	\node at (45:1.3) {$q_j$};
	\node at (-45:1.3) {$\tilde{q}_{Ri}^\dagger$};
	\node at (180:1.3) {$\overline{\tilde{g}}^a$};
	\node(g) at (-0.7,0.3) {};
	\node(u) at (0.4,0.8) {};
	\path[line width=0.8pt,->] (g) edge [out=0, in=225] (u);
	\node at (3,0) {$\hat{=} +i\sqrt{2}g_s T^a_{ij}P_R$};
\end{scope}
\begin{scope}[shift={(0,-12.5)}]
	\node at (-1.5,0.7) {\circled{18a}};
	\draw[scalar] (0,0)--(45:1);
	\draw[fermionnoarrow] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(-45:1);
	\draw[fermionnoarrow] (180:1)--(0,0);
	\draw[gluon] (180:1)--(0,0);
	\node at (45:1.3) {$\sigma^{b\dagger}$};
	\node at (-45:1.3) {$\overline{\tilde{g}}^c$};
	\node at (180:1.3) {$\tilde{g}^a$};
	\node(g) at (-0.7,-0.3) {};
	\node(u) at (0.4,-0.8) {};
	\path[line width=0.8pt,->] (g) edge [out=0, in=135] (u);
	\node at (3,0) {$\hat{=} -\sqrt{2}g_s f^{abc}P_L$};
\end{scope}
\begin{scope}[shift={(7,-12.5)}]
	\node at (-1.5,0.7) {\circled{18b}};
	\draw[fermionnoarrow] (0,0)--(45:1);
	\draw[gluon] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[fermionnoarrow] (180:1)--(0,0);
	\draw[gluon] (180:1)--(0,0);
	\node at (45:1.3) {$\tilde{g}^b$};
	\node at (-45:1.3) {$\sigma^c$};
	\node at (180:1.3) {$\overline{\tilde{g}}^a$};
	\node(g) at (-0.7,0.3) {};
	\node(u) at (0.4,0.8) {};
	\path[line width=0.8pt,->] (g) edge [out=0, in=225] (u);
	\node at (3,0) {$\hat{=} +\sqrt{2}g_s f^{abc} P_R$};
\end{scope}
\begin{scope}[shift={(0,-15)}]
	\node at (-1.5,0.7) {\circled{19}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[scalar] (0,0)--(135:1);
	\draw[scalarbar] (0,0)--(-135:1);
	\node at (45:1.4) {$\tilde{q}^\dagger_{Dl}$};
	\node at (-45:1.4) {$\tilde{q}_{Bj}$};
	\node at (135:1.4) {$\tilde{q}^\dagger_{Ck}$};
	\node at (-135:1.4) {$\tilde{q}_{Ai}$};
	\node at (5,0) {$\hat{=} \ -ig_s^2 [T_{ki}^a T_{lj}^a(\delta_{AL}\delta_{CL} - \delta_{AR}\delta_{CR})(\delta_{BL}\delta_{DL}-\delta_{BR}\delta_{DR})$};
	\node at (5.6,-0.5) {$T_{kj}^a T_{li}^a(\delta_{BL}\delta_{CL} - \delta_{BR}\delta_{CR})(\delta_{AL}\delta_{DL}-\delta_{AR}\delta_{DR})]$};
\end{scope}
\end{tikzpicture}
\end{center}
\caption{The curved arrows indicate the fermion flow. The Feynman rules 16b, 17b and 18b are the complex conjugates of 16a, 17a and 18a respectively. Applying a flipping rule to a vertex one has to reverse the curved arrow, i.e. the fermion flow and replace $\Psi$ with $\bar{\Psi}^C$. In addition one has to add a minus sign for Feynman rule 13.}
\end{figure}
\begin{figure}
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\node at (-1.5,0.7) {\circled{20}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[scalar] (0,0)--(135:1);
	\draw[scalarbar] (0,0)--(-135:1);
	\node at (45:1.4) {$\sigma^{b\dagger}$};
	\node at (-45:1.4) {$\sigma^c$};
	\node at (135:1.4) {$\tilde{q}^\dagger_{Aj}$};
	\node at (-135:1.4) {$\tilde{q}_{Ai}$};
	\node at (3,0) {$\hat{=} \ -g_s^2 T_{ij}^a f^{abc}(\delta_{AL}\delta_{CL} - \delta_{AR}\delta_{BR})$};
\begin{scope}[shift={(0,-2.5)}]
	\node at (-1.5,0.7) {\circled{21}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[scalar] (180:1)--(0,0);
	\node at (45:1.3) {$\tilde{q}^\dagger_{Ai}$};
	\node at (-45:1.3) {$\tilde{q}_{Bj}$};
	\node at (180:1.6) {$\sigma^a+\sigma^{a\dagger}$};
	\node at (3,0) {$\hat{=} -i\sqrt{2}g_s m_{\tilde{g}} T^a_{ij}(\delta_{AL}\delta_{BL}-\delta_{AR}\delta_{BR})$};
\end{scope}
\begin{scope}[shift={(0,-5)}]
	\node at (-1.5,0.7) {\circled{22}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[scalar] (0,0)--(135:1);
	\draw[scalarbar] (0,0)--(-135:1);
	\node at (45:1.4) {$\sigma^{\dagger d}$};
	\node at (-45:1.4) {$\sigma^e$};
	\node at (135:1.4) {$\sigma^{\dagger b}$};
	\node at (-135:1.4) {$\sigma^c$};
	\node at (3,0) {$\hat{=} \ -g_s^2 (f^{abc}f^{ade} + f^{abc}f^{adc})$};
\end{scope}
\end{tikzpicture}
\end{center}
\end{figure}

\subsection{Passarino-Veltman Integrals}

\begin{align}
A_0(m^2) &= \frac{i}{16\pi^2} \int_l \frac{1}{l^2-m^2}\nonumber\\
B_{0,\mu,\mu\nu}(p^2,m_1^2,m_2^2) &= \frac{i}{16\pi^2} \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p)^2-m_2^2]}\nonumber\\
C_{0,\mu,\mu\nu}(p_1^2,p_2^2,m_1^2,m_2^2,m_3^2) &= \frac{i}{16\pi^2} \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p_1)^2-m_2^2][(l+p_2)^2-m_3^2]}
\end{align}
with the shortcut $\int_l = \mu^{2\epsilon}\int\frac{\mathrm{d}^D l}{(2\pi)^D}$. Furthermore there are supressed $\varepsilon$'s which prescripe how the poles in the complex plane are avoided. They are hidden in the infinitesimal shift of the masses: $m_i^2 \to m_i^2 - i \varepsilon$.\\
The tensor integrals can be decomposed as
\begin{align}
B_\mu &= p_\mu B_1\nonumber\\
B_{\mu\nu} &= g_{\mu\nu}B_{00} + p_\mu p_\nu B_{11}\nonumber\\
C_\mu &= p_{1\mu}C_1 + p_{2\mu}C_2 \nonumber\\
C_{\mu\nu} &= g_{\mu\nu}C_{00} + p_{1\mu}p_{1\nu}C_{11} + p_{2\mu}p_{2\nu}C_{22} + (p_{1\mu}p_{2\nu} + p_{2\mu}p_{1\nu})C_{12} 
\end{align}
\begin{align}
A_0(m^2) = m^2\left( \Delta -\ln \frac{m^2}{\mu^2} + 1 \right) + \mathcal{O}(\epsilon)
\end{align}
$\Delta = \frac{1}{\epsilon} - \gamma_E+\ln 4\pi$
\begin{align}
B_0(0,m_1^2,m_2^2) &= \frac{A_0(m_1^2)-A_0(m_2^2)}{m_1^2-m_2^2} = \Delta + 1 -\frac{m_1^2\ln \frac{m_1^2}{\mu^2}-m_2^2\frac{m_2^2}{\mu^2}}{m_1^2-m_2^2} + \mathcal{O}(\epsilon)\\
B_0(0,m^2,m^2) &= \frac{\partial}{\partial m^2} A_0(m^2) = \Delta -\ln \frac{m^2}{\mu^2} + 1 + \mathcal{O}(\epsilon)
\end{align}

%\subsection{Cross section and Phase Space Integration}
%\begin{align}
%\mbox{d}\sigma = \frac{1}{2E_A 2E_B |v_A-v_B|}\left( \prod_f \frac{\mbox{d}^3p_f}{(2\pi)^3}\frac{1}{2E_f} \right) \sum |\mathcal{M}(p_A,p_B \to \left\{p_f\right\})|^2 (2\pi)^4 \delta^{(4)}(p_a+p_b-\sum p_f)
%\end{align}
%...\\
%\begin{align}
%\frac{\mbox{d}^2 \sigma}{\mbox{d}t\mbox{d}u} = \frac{K_{ij}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_{\tilde{q}}^4}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_{\tilde{q}}^4) \Theta(s-4m_{\tilde{q}}^2) \delta(s+t+u-2m_{\tilde{q}}^2) \sum |\mathcal{M}^B|^2
%\end{align}

### 2016-02-25 MSSM.tex

\section{The Minimal Supersymmetric Standard Model}

\subsection{Supersymmetry as Extention of Poincaré Symmetry}
The superalgebra is defined by
\begin{align}
\left\{Q_\alpha,Q_\beta\right\} = \left\{\overline{Q}_{\dot{\alpha}},\overline{Q}_{\dot{\beta}}\right\} &= 0,  \nonumber\\
\left\{Q_\alpha,\overline{Q}_{\dot{\alpha}}\right\} &= 2\sigma^\mu_{\alpha\dot{\alpha}}, \nonumber\\
[P^\mu,Q_\alpha] = [P^\mu,\overline{Q}_{\dot{\alpha}}] &= 0, \nonumber \\
[Q_\alpha, J^{\mu\nu}] &= \frac{1}{2} (\sigma^{\mu\nu})_\alpha^\beta Q_\beta
\end{align}
A representation in the form of differential operators is given by
\begin{align}
P^\mu &= i\partial^\mu\nonumber\\
J^{\mu\nu} &= i(x^\mu\partial^\nu - x^\nu\partial^\mu)\nonumber\\
Q_\alpha &= i(\partial_\alpha + i\sigma^\mu_{\alpha\dot{\alpha}}\overline{\theta}^{\dot{\alpha}}\partial_\mu\nonumber\\
\overline{Q}_{\dot{\alpha}} &= i(-\overline{\partial}_{\dot{\alpha}} - i \theta^\alpha \sigma^\mu_{\alpha\dot{\alpha}}\partial_\mu).
\end{align}
INTRODUCE AND MOTIVATE SUSY COVARIANT DERIVATIVES $\mathcal{D}_\alpha = \frac{\partial}{\partial \theta^\alpha} - i(\sigma^\mu\overline{\theta})_\alpha\partial_\mu$ is the chiral covariant derivative and $\overline{\mathcal{D}}\overline{\mathcal{D}} = \overline{\mathcal{D}}_{\dot{\alpha}}\overline{\mathcal{D}}^{\dot{\alpha}}$

\subsection{A Generic Supersymmetric Model in Superspace Formulation}
This chapter outlines the generic ingredients and terms of a supersymmetric model. To this end it is practical to work in the language of superspace and superfields.\\
Superspace is a manifold obtained by enlarging Minkowski space, whose coordinates are label with $x^\mu$, with four anticommuting numbers: $\theta^\alpha$ and $\overline{\theta}^{\dot{\alpha}}$, where $\alpha,\ \dot{\alpha} = 1,2$. Superfields are functions on superspace.\\
The for the MSSM relevant superfields\footnote{Superfield are throughout this thesis labeled with a hat.} are the chiral superfield $\hat{\Phi}$, the antichiral superfield $\hat{\overline{\Phi}}$ and the vector superfield $V$. Chiral superfields are defined by the restriction $\overline{\mathcal{D}}_{\dot{\alpha}}\hat{\Phi} = 0$, antichiral superfields by $\mathcal{D}_\alpha\hat{\overline{\Phi}} = 0$ and vector superfields by the condition of being real $V^\dagger = V$.\\
Their component decomposition reads\footnote{For tho vector superfield Wess-Zumino-gauge is applied.}
\begin{align}
\hat{\Phi}(x,\theta,\overline{\theta}) &= A(x) + \sqrt{2}\theta\psi(x) + \theta\theta F(x) - i\theta\sigma^\mu \overline{\theta}\partial_\mu A(x) - \frac{1}{4}\theta\theta\overline{\theta}\overline{\theta}\partial_\mu\partial^\mu A(x) - \frac{i}{\sqrt{2}}\theta\theta\overline{\theta}\overline{\sigma}^\mu \partial_\mu\psi(x)\nonumber\\
\hat{\overline{\Phi}}(x,\theta,\overline{\theta}) &= A^\dagger(x) + \sqrt{2}\overline{\theta}\overline{\psi}(x) + \overline{\theta}\overline{\theta} F^\dagger(x) + i\theta\sigma^\mu \overline{\theta}\partial_\mu A^\dagger(x) - \frac{1}{4}\theta\theta\overline{\theta}\overline{\theta}\partial_\mu\partial^\mu A^\dagger(x) - \frac{i}{\sqrt{2}}\overline{\theta}\overline{\theta}\theta\sigma^\mu \partial_\mu\overline{\psi}(x)\nonumber\\
\hat{V}(x,\theta,\overline{\theta}) &= \theta\sigma^\mu\overline{\theta} v_\mu + i\theta\theta\overline{\theta}\overline{\lambda}(x) -i \overline{\theta}\overline{\theta}\theta\lambda(x) + \frac{1}{2}\theta\theta\overline{\theta}\overline{\theta}D(x),\label{eq:superfielddecomp}
\end{align}
where $A(x)$ and $F(x)$ are complex scalar fields, $\psi(x)$ and $\lambda(x)$ are left handed Weyl spinors and $D(x)$ being a real scalar field.\\
The superfields transform under a generic gauge transformation as
\begin{align}
\hat{\Phi} &\to \mathrm{e}^{-2ig\Lambda}\Phi\nonumber\\
\hat{\overline{\Phi}} &\to \hat{\overline{\Phi}}\mathrm{e}^{2ig\overline{\hat{\Lambda}}}\nonumber\\
\mathrm{e}^{2g\hat{V}} &\to \mathrm{e}^{-2ig\hat{\overline{\Lambda}}}\mathrm{e}^{2g\hat{V}} \mathrm{e}^{2ig\hat{\Lambda}},
\end{align}
where $\hat{\Lambda} = \hat{\Lambda}^aT^a$ and $\hat{V} = \hat{V}^aT^a$. $\hat{\Lambda}^a$ is an arbitrary chiral superfield and the $T^a$ are the generetors of the Lie algebra, which is associated to the gauge group in question. g is the gauge coupling constant of the gauge group.\\
One can therefore construct the important gauge invariant term $\int\mathrm{d}^4\theta\ \hat{\overline{\Phi}}\mathrm{e}^{2g\hat{V}}\hat{\Phi}$. If one introduces the gauge covariant derivative $D_\mu = \partial + ig T^a v^a_\mu$ the component decomposition reads
\begin{align}
\int\mathrm{d}^4\theta\hat{\overline{\Phi}}\mathrm{e}^{2g\hat{V}}\hat{\Phi} &= F^\dagger F + \left(D_\mu A\right)^\dagger \left(D^\mu A\right) + \overline{\psi}\overline{\sigma}^\mu i D_\mu \psi\nonumber \\
&- \sqrt{2}g\left( -i(A^\dagger T^aA)\lambda^a +i\overline{\lambda}^a(AT^aA^\dagger) \right) + g(A^\dagger T^a A) D^a .\label{eq:L_matter}
\end{align}
Therefore this term gives rise to the kinetic terms of the components of the chiral and antichiral superfields $A,\ A^\dagger,\ \psi$ and $\overline{\psi}$, their minimal coupling to the gauge fields $v_\mu^a$ and their superpartners $\lambda^a$ and $\overline{\lambda}^a$ and terms involving the auxiliary fields $F,\ F^\dagger$ and $D$.\\
With the field-strength chiral superfields $\hat{W}_\alpha = -\frac{1}{4}\overline{\mathcal{D}}\overline{\mathcal{D}}(\mathrm{e}^{-2gV}\mathcal{D}_\alpha\mathrm{e}^{2gV})$ one can write down a gauge invariant term yielding the kinetic terms of the gauge fields and their superpartners:
\begin{align}
\int\mathrm{d}^2\theta \frac{1}{16g^2 }\hat{W}^{\alpha a} \hat{W}^a_\alpha + h.c.= \frac{1}{2}D^aD^a -\frac{1}{4}F^a_{\mu\nu}F^{a\mu\nu} + \frac{i}{2}\overline{\lambda}^a\overline{\sigma}^\mu(D_\mu\lambda^a) + \frac{i}{2}\lambda^a\sigma^\mu(D_\mu\overline{\lambda}^a).\label{eq:L_gauge}
\end{align}
A third generic term in a supersymmetric theory arises from the superpotential $W(\hat{\Phi})$ which is a holomorphic function in the chiral superfields:
\begin{align}
\int\mathrm{d}^2\theta\ W(\hat{\Phi}).
\end{align}
A renormalizable superpotential is given by $W(\hat{\Phi}) = c_i\hat{\Phi} + \frac{m_{ij}}{2}\hat{\Phi}_i\hat{\Phi}_j + \frac{g_{ijk}}{3!}\hat{\Phi}_i\hat{\Phi}_j\hat{\Phi}_k$. The component decomposition of the corresponding terms is
\begin{align}
\int\mathrm{d}^2\theta\ \hat{\Phi}_1 &= F_1\nonumber\\
\int\mathrm{d}^2\theta\ \hat{\Phi}_1\hat{\Phi}_2 &= A_1F_2 + F_1A_2-\psi_1\psi_2\nonumber\\
\int\mathrm{d}^2\theta\ \hat{\Phi}_1\hat{\Phi}_2\hat{\Phi}_3 &= F_1A_2A_3 + A_1F_2A_3 + A_1A_2F_3 - A_1\psi_2\psi_3 - \psi_1A_2\psi_3 - \psi_1\psi_2A_3.\label{eq:L_superpot}
\end{align}
The Lagrangian for a supersymmetric theory is therefore given by 
\begin{align}
\mathcal{L}_{SUSY} &= \mathcal{L}_{matter} + \mathcal{L}_{gauge} + \mathcal{L}_{superpot}\nonumber\\
&=\int\mathrm{d}^4\theta\hat{\overline{\Phi}}\mathrm{e}^{2g\hat{V}}\hat{\Phi} + \left(\int\mathrm{d}^2\theta \frac{1}{16g^2 }\hat{W}^{\alpha a} \hat{W}^a_\alpha + h.c. \right) +\int\mathrm{d}^2\theta\ W(\hat{\Phi})
\end{align}
Observing the component decomposition \ref{eq:L_matter},\ref{eq:L_gauge}, \ref{eq:L_superpot} of the 3 parts of this Lagrangian, one observes that the $F$ and $D$ fields have no kinetic term and are therefor auxiliary fields which can be eliminated by their equation of motion $\frac{\partial \mathcal{L}}{\partial\phi} = \partial_\mu\frac{\partial \mathcal{L}}{\partial(\partial_\mu \phi)}$ with $\phi = F, D$. Doing this one obtains
\begin{align}
\mathcal{L}_D &= \frac{1}{2} D^aD^a + g A^\dagger T^aD^a A \hspace{1cm} \Rightarrow \hspace{1cm} D^a = - A^\dagger T^a A \nonumber\\
\mathcal{L}_D &= -\frac{1}{2}\left( A^\dagger T^a A \right)^2
\end{align}
and 
\begin{align}
\mathcal{L}_F &= F_i^\dagger F_i + \left( c_iF_i + m_{ij}F_iA_j + \frac{g_{ijk}}{2}F_iA_jA_k + h.c. \right) \hspace{1cm} \Rightarrow \hspace{1cm} F^\dagger_i = - \frac{\partial W(A)}{\partial A_i}\nonumber\\
\mathcal{L}_F &= -\left| \frac{\partial W(A)}{\partial A_i} \right|^2
\end{align}

\subsection{The Minimal Supersymmetric Standard Model in superspace formulation}
The Lagrangian for the MSSM\footnote{This is the Lagrangian on the classical level, i.e. there are neither gauge fixing nor ghost terms.} reads
\begin{align}
\mathcal{L}_{MSSM} = \int \mathrm{d}^4 \theta & \left[ \hat{\overline{Q}}\mathrm{e}^{2g^\prime \hat{V}^\prime + 2g\hat{V} + 2g_s\hat{V}_s}\hat{Q} + \hat{\overline{U}}\mathrm{e}^{2g^\prime \hat{V}^\prime + 2g\hat{V} - 2g_s\hat{V}^T_s}\hat{U} + \hat{\overline{D}}\mathrm{e}^{2g^\prime \hat{V}^\prime + 2g\hat{V} - 2g_s\hat{V}^T_s}\hat{D} \right.\nonumber\\
 & + \hat{\overline{L}}\mathrm{e}^{2g^\prime \hat{V}^\prime + 2g\hat{V}}\hat{L} + \hat{\overline{E}}\mathrm{e}^{2g^\prime \hat{V}^\prime + 2g\hat{V}}\hat{E}\nonumber\\
 & + \left. \hat{\overline{H}}_d\mathrm{e}^{2g^\prime \hat{V}^\prime + 2g\hat{V}}\hat{H}_d + \hat{\overline{H}}_u\mathrm{e}^{2g^\prime \hat{V}^\prime + 2g\hat{V}}\hat{H}_u \right]\nonumber\\
 + \int \mathrm{d}^2\theta & \left[ \frac{1}{16g^{\prime 2}} \hat{W}^{\prime\alpha}\hat{W}^\prime_\alpha + \frac{1}{16g^{2}} \hat{W}^{a\alpha}\hat{W}^a_\alpha + \frac{1}{16g_s^2} \hat{W}_s^{a\alpha}\hat{W}^a_{s\alpha} \right] + h.c.\nonumber\\
 + \int \mathrm{d}^2\theta&\ W_{MSSM} + h.c.\nonumber\\
 +\  \mathcal{L}_{soft}.\ &\label{eq:L_MSSM}
\end{align}
Apart from the already discussed terms in the first 4 lines of \ref{eq:L_MSSM} there is a superpotential $W_{MSSM}$:
\begin{align}
W_{MSSM} &= y_d \hat{H}_d \hat{Q} \hat{D} + y_u \hat{H}_u \hat{Q} \hat U + y_e \hat{H}_d \hat{L} \hat{E} - \mu \hat{H}_d \hat{H}_u\label{eq:W_MSSM}
\end{align}
and terms which break supersymmetry softly, i.e. terms with coupling constants with positive mass dimension.
\begin{align}
\mathcal{L}_{soft} &= -M^2_{\tilde{Q}}|\tilde{q}_L|^2 - M^2_{\tilde{U}}|\tilde{u}_R|^2 - M^2_{\tilde{D}}|\tilde{d}_R|^2 \nonumber\\
&\ \ \ - M^2_{\tilde{L}}|\tilde{l}_L|^2 - M^2_{\tilde{E}}|\tilde{e}_R|^2 - M^2_{H_d}|H_d|^2 - M^2_{H_u}|H_u|^2\nonumber\\
&\ \ \ +\frac{1}{2}\left( M_1 \lambda\lambda + M_2 \lambda^a\lambda^a + M_3 \lambda_s^a\lambda_s^a\right) + h.c.\nonumber\\
&\ \ \ -\left( A_d y_d H_d \tilde{q}_L \tilde{d}^\dagger_R + A_u y_u H_u \tilde{q}_L \tilde{u}^\dagger_R + A_e y_e H_d \tilde{l}_L \tilde{e}^\dagger_R -B\mu H_d H_u \right) + h.c.\label{eq:L_soft}
\end{align}
The field content of the MSSM is summarized in \ref{tab:MSSMfieldcontent}
\begin{table}
\begin{center}
\begin{tabular}{c|c|c}\label{tab:MSSMfieldcontent}
Superfield & Components & $SU_\mathrm{C}(3)$ $\times$ $SU_\mathrm{L}(2)$ $\times$ $U_\mathrm{Y}(1)$\\
\hline
$\hat{\Phi}$ & $A$, $\psi$ & \\
$\hat{V}$ & $\lambda$, $v_\mu$ \\
$\hat{Q}$ & $\tilde{q}_L = \begin{pmatrix}
\tilde{u}_L \\
\tilde{d}_L
\end{pmatrix}$, $q_L = \begin{pmatrix}
u_L \\
d_L
\end{pmatrix}$ & (3, 2, $\frac{1}{6}$)\\
$\hat{U}$ & $\tilde{u}_R^\dagger$, $u_R$ & (3$^\ast$, 1, $-\frac{2}{3}$)\\
$\hat{D}$ & $\tilde{d}_R^\dagger$, $d_R$ & (3$^\ast$, 1, $+\frac{1}{3}$)\\
$\hat{L}$ & $\tilde{l}_L = \begin{pmatrix}
\tilde{\nu}_L \\
\tilde{e}_L
\end{pmatrix}$, $l_L = \begin{pmatrix}
\nu_L \\
e_L
\end{pmatrix}$ & (1, 2, $-\frac{1}{2}$)\\
$\hat{E}$ & $\tilde{e}_R^\dagger$, $e_R$ & (1, 1, 1)\\
$\hat{H}_d$ & $H_d$, $\tilde{H}_d$ & (1, 2, $-\frac{1}{2}$)\\
$\hat{H}_u$ & $H_u$, $\tilde{H}_u$ & (1, 2, $+\frac{1}{2}$)\\
$\hat{V}^\prime$ & $\lambda^\prime$, $B_\mu$ & (1, 1, 0)\\
$\hat{V}^a$ & $\lambda^a$, $W_\mu^a$ & (1, 3, 0)\\
$\hat{V}_s^a$ & $\lambda_s^a$, $G_\mu^a$ & (8, 1, 0)\\
\end{tabular}
\caption{The table shows the field content of the MSSM in terms of the superfields and their component decomposition. The first two lines show the decomposition of the generic superfields (cf. \ref{eq:superfielddecomp}).\newline
The third column shows the representation (for $SU_\mathrm{C}(3)$ and $SU_\mathrm{L}(2)$) in which the fields transform and the charges of the fields for $U_\mathrm{Y}(1)$.}\label{tab:MSSMfieldcontent}
\end{center}
\end{table}

### 2016-02-25 Masterarbeit.tex

\input{preamble}
\input{custom_commands_Theorie}
\begin{document}

\pagenumbering{gobble}   % no pagenumbering
% Titelpageseite
\begin{titlepage}
 \begin{tabularx}{\linewidth}{X}
  \includegraphics[width=6cm]{TU_Logo_SW} \\\hline\hline
  \vspace{4.5em}
  \begin{singlespace}\begin{center}\bfseries\Huge  
  Title of Master thesis  
  \end{center}\end{singlespace}
  \vspace{5.5em}
  \begin{singlespace}\begin{center}\large
   Master-Arbeit \\ zur Erlangung des Hochschulgrades \\ 
   Master of Science \\ 
   im Master-Studiengang Physik
  \end{center}\end{singlespace}\medskip
  \begin{center}vorgelegt von\end{center}
  \begin{center}
   {\large Sebastian Liebschner} \\ geboren am 08.05.1990 in Meerane
  \end{center}\medskip
  \begin{singlespace}\begin{center}\large
   Institut für Kern- und Teilchenphysik Physik \\
   Fachrichtung Physik \\
   Fakultät Mathematik und Naturwissenschaften \\
   Technische Universität Dresden \\ 2016
  \end{center}\end{singlespace}
 \end{tabularx}
\end{titlepage}

% Gutachterseite
\thispagestyle{empty}\vspace*{48em}
Eingereicht am xx.~Monat~20xx\vspace{1.5em}
\par{\large\begin{tabular}{ll}
 1. Gutachter: & Prof.~Dr.~XX \\
 2. Gutachter: & Prof.~Dr.~YY \\
\end{tabular}}
\newpage

% abstract page
\begin{center}\large\bfseries Summary\end{center}
Abstract \\ 
English: motivation: aesthetic: Coleman-Mandula --> Haag-Lopuszanski-Sohnius-Theorem\\
\vspace{20em}
Abstract \\ 
Deutsch \\
\newpage

\tableofcontents
\newpage

\pagenumbering{arabic}
\section{Introduction}
motivation: aesthetic: Coleman-Mandula --> Haag-Lopuszanski-Sohnius-Theorem\\
plots for exclusion of squarks in specific SUSY scenarios (from Michael) --> R-Symmetry could be possible explanation for that because:\\
MSSM-Lagrangian --> trafo rules for superfields under R-symm --> forbidden terms in MRSSM (write down Lagrangian for R-symmetric SUSYQCD)\\
suppression of squark production in MRSSM by less diagrams ($m_{gluino}^{-4}$ suppression at low energies in MRSSM and only $m_{gluino}^{-2}$ suppression in MSSM)\\
R-charges of all fields (show in diagram!) --> only if R-charges of final / initial particles are zero, a diagram is allowed in R-symm. model
\newpage
\input{Standardmodel}
\newpage
\input{MSSM}
\newpage
\input{RSymmetry}
\newpage
\input{TreeLevel}
\newpage
\input{Renormalization}
\newpage
\input{NLO}
\newpage
\section{Summary and Outlook}
\newpage
\input{Appendix}
\newpage
\bibliography{references}
\newpage
% Erklärung
\clearpage
\thispagestyle{empty}
\minisec{Erklärung}\vspace*{1.5em}
Hiermit erkläre ich, dass ich diese Arbeit im Rahmen der Betreuung am Institut
für ??? Physik ohne unzulässige Hilfe Dritter verfasst und alle Quellen als solche gekennzeichnet habe.
\vspace*{45em}
Vorname Nachname \par
Dresden, Monat 2012

\end{document}

### 2016-02-25 Renormalization.tex

\section{Renormalization of the MRSSM}
In order to improve the prediction of the cross section of the previous chapter one has to take quantum corrections into account. These are associated with loops in the corresponding Feynman diagrams. Computing these loop diagrams one might encounter infinities which arise from certain momentum configurations of the unspecified loop momentum. These infinities can be classified due to their origin. Infinities which are associated with loop momenta which tend to infinity are referred to as ultraviolet(UV) divergences. Infinities arising from loop momenta approaching zero can occur in loops with massless particles and are called infrared(IR) singularities. Furthermore there are collinear singularities with occur when a massless particle splits into two massless collinear particles.\\
These infinities are not physical and must therefore be removed to get sensible predictions. To this end one regularizes them to extract them from the quantity in question. UV-divergences can be removed by means of renormalization, i.e. counterterms are inserted into the Lagrangian to cancel UV-divergences. Infrared and collinear divergenves are removed by adding up all possible contributions which give rise to the considered observable.

\subsection{Regularization Schemes}\label{sec:RegSchemes}
\subsubsection*{Dimensional Regularization(DREG)}
Dimensional regularization(DREG) is a very common procedure for regularizing infinities which was devised by t'Hooft and Veltman~\cite{'tHooft:1972fi}. In this scheme loop momenta, gamma- and epsilon-tensors, phase space and fields are defined in $D$ dimensions. As in every regularization scheme a parameter with mass dimension needs to be introduced. In DREG that is the $\mu$ parameter which ensures that the loop integrals still have mass dimension 4:
\begin{align}
\int \frac{\mbox{d}^4p}{(2\pi)^4} \to \mu^{4-D} \int \frac{\mbox{d}^Dp}{(2\pi)^D}.
\end{align}
One often writes $D=4-2\epsilon$. Then the divergences of the loop integral manifest in $\frac{1}{\epsilon}$ poles.\\
However DREG suffers a flaw in supersymmetry. As the degrees of freedom for a massless gauge boson are $D-2$ but the degrees of freedom for its superpartner are 2 there is a mismatch if $D \neq 4$. As a consequence there are $2\epsilon$ degrees of freedom associated with the gluon\footnote{These degrees of freedom are identified with scalars and are therefore referred to as $\epsilon$ scalars} which do not have a supersymmetric partner. Therefore DREG violates supersymmetry.

\subsubsection*{Dimensional Reduction (DRED)}
Dimensional reduction (DRED) was introduced to rectify the imperfections of DREG, i.e. it preserves supersymmetry\footnote{It is not clear if DRED preserves supersymmetry at all orders in perturbation theory but it does preserve supersymmetry at the 1-loop level.}. DRED promotes only loop momenta to $D$ dimensions. All other quantities which are $D$ dimensional in DREG stay in 4 dimensions.\\
maybe refer to Collins: Renormalization

\subsection{Regularization Scheme Dependences}\label{sec:RegSchemeDep}
It is useful to introduce the effective action $\Gamma$ to discuss the subject of this and ensuing subchapters. A formal introduction of $\Gamma$ can be found in~\cite{Peskin}. In short $\Gamma$ can be viewed as a modification of the classical action $\Gamma_{cl} = \int \mathcal{L}_{cl}$ by quantum effects:
\begin{align}
\Gamma = \Gamma_{cl} + \mathcal{O}(\hbar)
\end{align}
This means that in addition to the vertices in the classical Lagrangian new vertices arise due to loop effects. As already suggested loop corrections might a priori not be finite and then need to be made finite by the addition of counterterms. For $\mathcal{O}(\hbar)$ corrections one writes
\begin{align}
\Gamma^{(\leq 1)} \to \Gamma^{(\leq 1)} + \Gamma^{(1),ct}
\end{align} 
These counterterms depend on the regularization (and renormalization) scheme. If one chooses to work with DREG supersymmetry will not be preserved at 1-loop order, i.e. $\Gamma^{(\leq 1)}_{DREG}$ is not supersymmetric. To maintain supersymmetry invariance of the renormalized effective action the counterterms will not only consist of supersymmetric counterterms $\Gamma^{(1),ct,sym}_{DREG}$ but also of counterterms restoring supersymmetry $\Gamma^{(1),ct,restore}_{DREG}$. 
\begin{align}
\Gamma^{(1),ct}_{DREG} = \Gamma^{(1),ct,sym}_{DREG} + \Gamma^{(1),ct,restore}_{DREG}
\end{align}
Fortunately a supersymmetry conserving regularization scheme (at 1-loop level) is given by DRED \cite{Hollik:2001cz}. One way to acquire supersymmetry restoring counterterms is therefore given by
\begin{align}
\Gamma^{(\leq 1)}_{DRED} + \Gamma^{(1),ct}_{DRED} \overset{!}{=} \Gamma^{(\leq 1)}_{DREG} + \Gamma^{(1),ct}_{DREG}.
\end{align}
Setting also the finite terms in $\Gamma^{(1),ct,sym}$ equal in DRED and DREG the choice of the supersymmetry restoring counterterms is fixed by:
\begin{align}
\Gamma^{(1),ct,restore}_{DREG} = \Gamma^{(\leq 1)}_{DRED} - \Gamma^{(\leq 1)}_{DREG}.\label{eq:GammaCtRestore}
\end{align} 
This way supersymmetry is preserved by the renormalization constants.\\ 
In the case of the MRSSM it will turn out that the only supersymmetry violation comes from correction associated with the gluon as already alluded to in \ref{sec:RegSchemes}. However supersymmetry restoring is always already included in $\delta Z^{\mathrm{DREG}}$. This is $\delta Z^{\mathrm{DREG}} = \delta Z^{\mathrm{DREG,sym}} + \delta Z^{\mathrm{trans}}$ where $\delta Z^{\mathrm{trans}} = \delta Z^{\mathrm{DREG}} - \delta Z^{\mathrm{DRED}}$ is the supersymmetry restoring renormalization constant. The only point where particularly care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms. Therefore one has to make a difference between these couplings at 1-loop level. In order to match $g_s$ to the experimentally measured coupling it is renormalized in $\overline{\mathrm{MS}}$. The Yukawa coupling $\hat{g}_s$ therefore needs to be added with the difference of the supersymmetry restoring counterterms at 1-loop in order to be renormalized the same way.

%An alternative procedure is used in \cite{Beenakker:1996ch}, where only one supersymmetry restoring counterterm, which translates between the renormalized gauge coupling $g_s$ and the renormalized Yukawa coupling $\hat{G}_s$ is needed. That is possible because the only supersymmetry violation comes from the gauge sector. For a comprehensive discussion of this issue see [Philipp Vasros Diplomarbeit and the paper with Dominik]\\
%SUSY restoring is always already in $\delta Z^{DREG}$ included. Only important thing is the coupling: $g_s$ and $\hat{g}_s$ receive different SUSY restoring counterterm. Therefore one has to make a difference between these couplings at 1-loop level. In order to match $g_s$ to the experimentaly measured coupling it is renormalized in $\overline{\mathrm{MS}}$. The Yukawa coupling $\hat{g}_s$ therefore needs to be added with the difference of the SUSY-restoring counterterms at 1-loop in order to be renormalized the same way.

\subsection{On-Shell Renormalization}\label{sec:QuarkSE}
A part of the computation of NLO processes is the calculation of renormalization constants. The field and mass renormalization constants have been calculated in DREG in the on-shell scheme. This has the advantaged that when turning to the cross section no manipulation of the Green function to the S-matrix element has to be done.

\subsubsection{The Quark Self-Energy}
The quark self-energy splits into contribution from the SM as well as a supersymmetric analogue which is already present in the MSSM.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\node at (0,0) {1L};
	\draw[fermionbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {=};
\begin{scope}[shift={(3.5,0)}]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$G$};
	\draw[fermion] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$q$};	
	\draw[fermionbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7,0)}]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\tilde{g}$};
	\draw[scalar] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\tilde{q}$};	
	\draw[fermionbar](0:0.5)--(0:1.3);
\end{scope}
\end{tikzpicture}
\caption{diagrammatic contributions to the self-energy of the quark at 1-loop level}\label{fig:QuarkSelfEnergy}
\end{center}
\end{figure}\\
The 1-PI diagrams evaluate to
\begin{align}
i\Gamma^{1L}_{q_i\overline{q}_j} = i \frac{g_s^2}{16\pi^2}\delta_{ij} C(F) \left[ 2 \left( B_0(p^2,0,0) + B_1(p^2,0,0)-\frac{1}{2}\right)\slashed{p} - 2 B_1(p^2,m_{\tilde{g}}^2,m_{\tilde{q}}^2)\slashed{p}\right].
\end{align}
With the counterterm Feynman rule\\
\\
\begin{tikzpicture}[line width=1.0 pt, scale=0.8]
	\node at (-2.5,-0.1) {$i\Gamma^{1L,ct}_{q_i\overline{q}_j}\ \hat{=}\ i$};
\begin{scope}[shift={(0.1,0)}]	
	\draw[fermionbar] (-1.3,0) --(0,0);
	\draw[fermionnoarrow] (-0.3,0.3) -- (0.3,-0.3);
	\draw[fermionnoarrow] (-0.3,-0.3) -- (0.3,0.3);
	\draw[fermionbar] (0,0) --(1.3,0);
	\node at (1.6,0) {$j$};
	\node at (3,0) {$\hat{=}\ i\delta_{ij}\delta Z_q \slashed{p} $};	
\end{scope}
\end{tikzpicture}\\
and the on-shell renormalization condition
\begin{align}
\frac{\partial}{\partial \slashed{p}} \left[ \Re (\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j}) + \Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}  \right]_{p^2 = 0} = 0
\end{align}
where $\Re (\hdots)$ denotes the real part of $\hdots$ one finds
\begin{align}
\delta Z_q = 2 C(F) \frac{g_s^2}{16\pi^2} \Re \left[ B_1(p^2,m_{\tilde{g}}^2,m_{\tilde{q}}^2) + \frac{1}{2} \right].
\end{align}
Doing the same calculation in DRED one finds that the second term in the squared brackets is absent. Therefore the transition counterterm between DREG and DRED is given by
\begin{align}
\delta Z_q^{\mathrm{trans}} = \delta Z_q^{\mathrm{DREG}} - \delta Z_q^{\mathrm{DRED}} = C(F) \frac{g_s^2}{16\pi^2}.\label{eq:QuarkSC}
\end{align}

\subsubsection{The Squark Self-Energy}
The contributions to the self-energy of the left- and right-handed squark are the same. Therefore to avoid unnecessary labeling $\Gamma_{\tilde{q}\tilde{q}^\dagger}$ stands in the following for $\Gamma_{\tilde{q}_L\tilde{q}_L^\dagger} = \Gamma_{\tilde{q}_R\tilde{q}_R^\dagger}$.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[scalarbar](180:1.3)--(180:0.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\node at (0,0) {1L};
	\draw[scalarbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {=};
\begin{scope}[shift={(3.5,0)}]
	\draw[scalarbar](-1.3,0)--(0,0);
	\draw[scalarbar](0,0)--(1.3,0);
	\draw[scalar] (0,0) arc (-90:270:.5);
	\node at (0,1.3) {$\tilde{q}$};
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7.0,0)}]
	\draw[scalarbar](-1.3,0)--(0,0);
	\draw[scalarbar](0,0)--(1.3,0);
	\draw[gluon] (0,0) arc (270:-90:.5);
	\node at (0,1.3) {$G$};
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(10.5,0)}]
	\draw[scalarbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\tilde{g}$};
	\draw[fermion] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$q$};	
	\draw[scalarbar](0:0.5)--(0:1.3);
\end{scope}
\begin{scope}[shift={(3.5,-2.5)}]
	\node at (-1.8,0) {+};
	\draw[scalarbar](180:1.3)--(180:0.5);
	\draw[scalarnoarrow] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\phi^0,\ \sigma^0$};
	\draw[scalar] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\tilde{q}$};	
	\draw[scalarbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7,-2.5)}]
	\draw[scalarbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$G$};
	\draw[scalar] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\tilde{q}$};	
	\draw[scalarbar](0:0.5)--(0:1.3);
\end{scope}
\end{tikzpicture}
\caption{diagrammatic contributions to the self-energy of the squark at 1-loop level}
\end{center}
\end{figure}\\
\begin{align}
i\Gamma^{1L}_{\tilde{q}_{i}\tilde{q}^\dagger_j} &= i \frac{g_s^2}{16\pi^2}\delta_{ij}C(F) \left[  A_0(m_{\tilde{q}}^2) + 0 - \left( 4A_0(m_{\tilde{g}}^2) + 4B_1(p^2,0,m_{\tilde{g}}^2)p^2 \right) \right.\nonumber\\
& \left.+ 4m_{\tilde{g}}^2B_0(p^2,m_{\phi^0}^2,m_{\tilde{q}}^2) - \left(2B_1(p^2,0,m_{\tilde{q}}^2)p^2 + B_0(p^2,0,m_{\tilde{q}}^2)(m_{\tilde{q}}^2+3p^2) \right) \right].
\end{align}
Suppressing $\delta_{AB}$ with $A,B = L,R$ which is present in the tree level propagator the counterterm Feynman rule is given by\\
\\
\begin{tikzpicture}[line width=1.0 pt, scale=0.8]
	\node at (-2.5,-0.1) {$i\Gamma^{1L,ct}_{q_i\overline{q}_j}\ \hat{=}\ i$};
\begin{scope}[shift={(0.1,0)}]	
	\draw[scalarbar] (-1.3,0) --(0,0);
	\draw[fermionnoarrow] (-0.3,0.3) -- (0.3,-0.3);
	\draw[fermionnoarrow] (-0.3,-0.3) -- (0.3,0.3);
	\draw[scalarbar] (0,0) --(1.3,0);
	\node at (1.6,0) {$j$};
	\node at (5,0) {$\hat{=}\ i\delta_{ij} \left[ \delta Z_{\tilde{q}}(p^2-m_{\tilde{q}}^2) - \delta m_{\tilde{q}}^2 \right] .$};	
\end{scope}
\end{tikzpicture}\\
The on-shell renormalization conditions read
\begin{align}
&\frac{\partial}{\partial p^2} \left[ \Re (\Gamma^{\mathrm{1L}}_{\tilde{q}_{i}\tilde{q}^\dagger_j}) + \Gamma^{\mathrm{1L,ct}}_{\tilde{q}_{i}\tilde{q}^\dagger_j}  \right]_{p^2 = m_{\tilde{q}}^2} = 0 && \left[ \Re (\Gamma^{\mathrm{1L}}_{\tilde{q}_{i}\tilde{q}^\dagger_j}) + \Gamma^{\mathrm{1L,ct}}_{\tilde{q}_{i}\tilde{q}^\dagger_j}  \right]_{p^2 = m_{\tilde{q}}^2} = 0.
\end{align}
This results in the following renormalization constants
\begin{align}
\delta Z_{\tilde{q}} &= \frac{g_s^2}{16\pi^2}C(F) \Re \left[ 4B_1(p^2,0,m_{\tilde{g}}^2) + 2B_1(B_1(p^2,0,m_{\tilde{q}}^2)) + 3B_0(p^2,0,m_{\tilde{q}}^2) \right.\nonumber\\
& + 4m_{\tilde{q}}^2 \frac{\partial}{\partial p^2}B_1(p^2,0,m_{\tilde{g}}^2) - 4m_{\tilde{g}}^2\frac{\partial}{\partial p^2}B_0(p^2,m_{\phi^0}^2,m_{\tilde{q}}^2) + 2m_{\tilde{q}}^2 \frac{\partial}{\partial p^2}B_1(p^2,0,m_{\tilde{q}}^2)\nonumber\\
& \left. + 4m_{\tilde{q}}^2 \frac{\partial}{\partial p^2}B_0(p^2,0,m_{\tilde{q}}^2)\right]_{p^2 = m_{\tilde{q}}^2}
\end{align}
\begin{align}
\delta m_{\tilde{q}}^2 = \frac{g_s^2}{16\pi^2}C(F)&\left[ A_0(m_{\tilde{q}}^2) - (4A_0(m_{\tilde{g}}^2) + 4B_1(m_{\tilde{q}}^2,0,m_{\tilde{g}}^2)m_{\tilde{q}}^2) + 4 m_{\tilde{g}}^2 B_0(m_{\tilde{q}}^2,m_{\phi^0}^2,m_{\tilde{q}}^2) \right.\nonumber\\
&\left. -(2B_1(m_{\tilde{q}}^2,0,m_{\tilde{q}}^2) m_{\tilde{q}}^2 + 4 B_0(m_{\tilde{q}}^2,0,m_{\tilde{q}}^2)m_{\tilde{q}}^2) \right]
\end{align}
The squark self-energy exhibits no regularization dependence. The transition counterterms are therefore 
\begin{align}
\delta Z_{\tilde{q}}^{\mathrm{trans}} = \delta m_{\tilde{q}}^{2\ \mathrm{trans}} = 0. \label{eq:SquarkSC}
\end{align}

\subsubsection{The Glunio Self-Energy}
The 4-spinor of the gluino comprises two Weyl spinors which describe very different particles.
\begin{align}
\tilde{g}^a = \begin{pmatrix}
\lambda^a \\
\overline{\chi}^a
\end{pmatrix}
\end{align}
The left-handed part $\lambda^a$ is associated with the superpartner of the gluon and therefore the "actual" gluino whereas the right-handed part $\overline{\chi}^a$ was introduced to assign a Dirac-mass to the gluino and is referred to as the octino.\\
From the Lagrangian \ref{eq:L_RSQCD} one can see that the couplings of the two particles are quite distinct. This is reflected by different field renormalization constants of the left- and right-handed part of the gluino.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[fermionnoarrow](180:1.3)--(180:0.5);
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\node at (0,0) {1L};
	\draw[fermionnoarrow](0:0.5)--(0:1.3);
	\draw[gluon](0:0.5)--(0:1.3);
	\node at (1.8,0) {=};
\begin{scope}[shift={(3.5,0)}]
	\draw[fermionnoarrow](180:1.3)--(180:0.5);
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermionbar] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$q$};
	\draw[scalarbar] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\tilde{q}$};	
	\draw[fermionnoarrow](0:0.5)--(0:1.3);
	\draw[gluon](0:0.5)--(0:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7.0,0)}]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermionnoarrow](180:1.3)--(180:0.5);
	\draw[scalarnoarrow] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\phi^0,\sigma^0$};
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);
	\draw[gluon] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\tilde{g}$};	
	\draw[gluon](0:0.5)--(0:1.3);
	\draw[fermionnoarrow](0:0.5)--(0:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(10.5,0)}]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermionnoarrow](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$G$};
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\draw[gluon] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\tilde{g}$};	
	\draw[fermionnoarrow](0:0.5)--(0:1.3);
	\draw[gluon](0:0.5)--(0:1.3);
\end{scope}
\end{tikzpicture}
\caption{diagrammatic contributions to the self-energy of the squark at 1-loop level}
\end{center}
\end{figure}
As for the quarks the fermion (and momentum) flow is from the right to the left.
\begin{align}
i\Gamma^{1L}_{\tilde{g}^a \overline{\tilde{g}}^b} &= i \frac{g_s^2}{16\pi^2}\delta_{ab} \left[-4T(F)\left( (n_f-1) B_1(p^2,0,m_{\tilde{q}}^2) + B_1(p^2,m_t^2,m_{\tilde{q}}^2) \right)P_L \slashed{p} \right.\nonumber\\
& + C(A)\left( (B_0(p^2,m_{\tilde{g}}^2,m_{\phi^0}^2) - B_0(p^2,m_{\tilde{g}}^2,m_{\sigma^0}^2))m_{\tilde{g}} - (B_1(p^2,m_{\tilde{g}}^2,m_{\phi^0}^2) + B_1(p^2,m_{\tilde{g}}^2,m_{\sigma^0}^2))\slashed{p} \right) \nonumber\\
&\left.+ C(A)\left( (2 - 4 B_0(p^2,0,m_{\tilde{g}}^2)) m_{\tilde{g}} - (1-2(B_0(p^2,0,m_{\tilde{g}}^2) + B_1(p^2,0,m_{\tilde{g}}^2)))\slashed{p} \right)\right]
\end{align}
Where $n_f = 6$ is the number of quark flavors.\\
The counterterm Feynman rule reads\\
\begin{tikzpicture}[line width=1.0 pt, scale=0.8]
	\node at (-2.5,-0.1) {$i\Gamma^{1L,ct}_{\tilde{g}^a \overline{\tilde{g}}^b}\ \hat{=}\ a$};
\begin{scope}[shift={(0.1,0)}]	
	\draw[gluon] (-1.3,0) --(1.3,0);
	\draw[fermionnoarrow] (-0.3,0.3) -- (0.3,-0.3);
	\draw[fermionnoarrow] (-0.3,-0.3) -- (0.3,0.3);
	\draw[fermionnoarrow] (-1.3,0) --(1.3,0);
	\node at (1.6,0) {$b$};
	\node at (7.8,0) {$\hat{=}\ i\delta_{ab}\left[ (\delta Z_{\tilde{g}}^L P_L + \delta Z_{\tilde{g}}^R P_R)\slashed{p} - \left(\frac{\delta Z_{\tilde{g}}^L+\delta Z_{\tilde{g}}^R}{2} m_{\tilde{g}} +\delta m_{\tilde{g}}\right) \right]. $};	
\end{scope}
\end{tikzpicture}\\
The on-shell renormalization conditions for the fields are
\begin{align}
& \frac{\partial}{\partial (P_L\slashed{p})} \left[ \Re (\Gamma^{\mathrm{1L}}_{\tilde{g}^a \overline{\tilde{g}}^b}) + \Gamma^{\mathrm{1L,ct}}_{\tilde{g}^a \overline{\tilde{g}}^b}  \right]_{\slashed{p} = m_{\tilde{g}}} = 0
&& \frac{\partial}{\partial (P_R\slashed{p})} \left[ \Re (\Gamma^{\mathrm{1L}}_{\tilde{g}^a \overline{\tilde{g}}^b}) + \Gamma^{\mathrm{1L,ct}}_{\tilde{g}^a \overline{\tilde{g}}^b}  \right]_{\slashed{p} = m_{\tilde{g}}} = 0
\end{align}
where the derivative of $\Sigma = \Sigma^{VL}P_L\slashed{p} + \Sigma^{VR}P_R\slashed{p} + \Sigma^{SL}P_L + \Sigma^{SR}P_R$ with respect to $P_A\slashed{p}$ \\
($A = L,R$) is defined by
\begin{align}
\left.\frac{\partial}{\partial (P_A\slashed{p})} \Sigma\right|_{\slashed{p} = m} = \Sigma^{VA} + \frac{\partial}{\partial p^2} \left( m^2 \Sigma^{VL} + m^2 \Sigma^{VR} + m \Sigma^{SL} + m \Sigma^{SR}\right).
\end{align}
This leads to the following renormalization constants
\begin{align}
\delta Z_{\tilde{g}}^L &= \frac{g_s^2}{16\pi^2}\Re \left[ 4T(F)\left( (n_f-1) B_1(m_{\tilde{g}}^2,0,m_{\tilde{q}}^2) + B_1(m_{\tilde{g}}^2,m_t^2,m_{\tilde{q}}^2) \right) \right.\nonumber\\
&+C(A) (B_1(m_{\tilde{g}}^2,m_{\tilde{g}}^2,m_{\phi^0}^2) + B_1(m_{\tilde{g}}^2,m_{\tilde{g}}^2,m_{\sigma^0}^2))\nonumber\\
&+C(A)(1-2(B_0(m_{\tilde{g}}^2,0,m_{\tilde{g}}^2) + B_1(m_{\tilde{g}}^2,0,m_{\tilde{g}}^2)))\nonumber\\
&+ 4T(F) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left( ((n_f-1))  B_1(p^2,0,m_{\tilde{q}}^2) +  B_1(p^2,m_t^2,m_{\tilde{q}}^2) \right)\nonumber\\
&-2 C(A) m_{\tilde{g}} \frac{\partial}{\partial p^2} \left( B_0(p^2,m_{\tilde{g}}^2,m_{\phi^0}^2)-B_0(p^2,m_{\tilde{g}}^2,m_{\sigma^0}^2) - B_1(p^2,m_{\tilde{g}}^2,m_{\phi^0}^2) - B_1(p^2,m_{\tilde{g}}^2,m_{\sigma^0}^2) \right)\nonumber\\
&-4 C(A) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left.\left( -B_0(p^2,0,m_{\tilde{g}}^2) + B_0(p^2,0,m_{\tilde{g}}^2) \right)\right]_{p^2=m_{\tilde{g}}^2}
\end{align}
and 
\begin{align}
\delta Z_{\tilde{g}}^R &= \frac{g_s^2}{16\pi^2}\Re \left[C(A) (B_1(m_{\tilde{g}}^2,m_{\tilde{g}}^2,m_{\phi^0}^2) + B_1(m_{\tilde{g}}^2,m_{\tilde{g}}^2,m_{\sigma^0}^2)) \right.\nonumber\\
&+C(A)(1-2(B_0(m_{\tilde{g}}^2,0,m_{\tilde{g}}^2) + B_1(m_{\tilde{g}}^2,0,m_{\tilde{g}}^2)))\nonumber\\
&+ 4T(F) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left( ((n_f-1))  B_1(p^2,0,m_{\tilde{q}}^2) +  B_1(p^2,m_t^2,m_{\tilde{q}}^2) \right)\nonumber\\
&-2 C(A) m_{\tilde{g}} \frac{\partial}{\partial p^2} \left( B_0(p^2,m_{\tilde{g}}^2,m_{\phi^0}^2)-B_0(p^2,m_{\tilde{g}}^2,m_{\sigma^0}^2) - B_1(p^2,m_{\tilde{g}}^2,m_{\phi^0}^2) - B_1(p^2,m_{\tilde{g}}^2,m_{\sigma^0}^2) \right)\nonumber\\
&-4 C(A) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left.\left( -B_0(p^2,0,m_{\tilde{g}}^2) + B_0(p^2,0,m_{\tilde{g}}^2) \right)\right]_{p^2=m_{\tilde{g}}^2}.
\end{align}
As for the quark there are constant terms amid the Passarino-Veltman integrals. These arise only in DREG and not in DRED. The transition counterterms are
\begin{align}
\delta Z_{\tilde{g}}^{A\ \mathrm{trans}} = \delta Z_{\tilde{g}}^{A\ \mathrm{DREG}} - \delta Z_{\tilde{g}}^{A\ \mathrm{DRED}} = C(A) \frac{g_s^2}{16\pi^2}\label{eq:GluinoSC}
\end{align}
for $A = L,R$. The gluino mass counterterm is ascertained by the condition
\begin{align}
\left[ \Re (\Gamma^{\mathrm{1L}}_{\tilde{g}^a \overline{\tilde{g}}^b}) + \Gamma^{\mathrm{1L,ct}}_{\tilde{g}^a \overline{\tilde{g}}^b}  \right]_{\slashed{p} = m_{\tilde{g}}} = 0
\end{align}
which is equivalent to 
\begin{align}
\delta m_{\tilde{g}} = \Re\left( m_{\tilde{g}}\frac{\Sigma^{VL}+\Sigma^{VR}}{2} + \frac{\Sigma^{SL}+\Sigma^{SR}}{2} \right)
\end{align}
and yields
\begin{align}
\delta m_{\tilde{g}} &= \frac{g_s^2}{16\pi^2} m_{\tilde{g}}^2\ \Re \left[ -2T(F) \left( (n_f-1)B_1(m_{\tilde{g}}^2,0,m_{\tilde{q}}^2) + B_1(m_{\tilde{g}}^2,m_t^2,m_{\tilde{q}}^2) \right) \right.\nonumber\\
& + C(A) \left( B_0(m_{\tilde{g}}^2,m_{\tilde{g}}^2,m_{\phi^0}^2) - B_0(m_{\tilde{g}}^2,m_{\tilde{g}}^2,m_{\sigma^0}^2) - B_1(m_{\tilde{g}}^2,m_{\tilde{g}}^2,m_{\phi^0}^2) -
B_1(m_{\tilde{g}}^2,m_{\tilde{g}}^2,m_{\sigma^0}^2) \right)\nonumber\\
& + C(A) \left.\left( 1 - 2 B_0(m_{\tilde{g}}^2,0,m_{\tilde{g}}^2) + 2 B_1(m_{\tilde{g}}^2,0,m_{\tilde{g}}^2) \right)\right].
\end{align}
Again there is a transition counterterm 
\begin{align}
\delta m_{\tilde{g}}^{\mathrm{trans}} = \delta m_{\tilde{g}}^{\mathrm{DREG}} - \delta m_{\tilde{g}}^{\mathrm{DRED}} = C(A) \frac{g_s^2}{16\pi^2} m_{\tilde{g}}.
\end{align}

\subsection{Renormalization of the Gauge Coupling}
The gauge coupling $g_s$ is renormalized in the $\overline{\mathrm{MS}}$-scheme with the modification that additional logarithms are substracted. This is to decouple heavy particles from the running of $\alpha_s = \frac{g_s^2}{4\pi}$. This renormalization procedure allows to adopt the experimental values of $\alpha_s$ from the PDF's. The running due to effects of heavy particles is then encoded in the logarithms of $\delta g_s$.\\
Extracting $\delta g_s$ from the quark-quark-gluon vertex requires not only the computation of $i\Gamma^{1L}_{q_i\overline{q}_jG^a}$ but also the (re)evaluation  of the auxiliary field renormalization constants $\delta Z_q^{\mathrm{aux}}$ and $\delta Z_G^{\mathrm{aux}}$. These will not be the same as the on-shell field renormalization.

\subsubsection{The Quark Self-Energy Revisited}
The quark self-energy has two contribution which are shown in figure \ref{fig:QuarkSelfEnergy}. The first one corresponds to light particles the second one to heavy particles: $i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j} = i\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j} + i\Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}$. For light particles only the UV-divergent part is kept. For heavy particles also the $\mu$-dependent terms are kept:
\begin{align}
i\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j}|_{\mathrm{UV-div}} &= i \frac{g_s^2}{16\pi^2}\delta_{ij} \slashed{p} C(F) \frac{1}{\epsilon_{\mathrm{UV}}}\\
i\Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}|_{\mathrm{UV-div,\mu-dep}} &= i \frac{g_s^2}{16\pi^2}\delta_{ij} \slashed{p} C(F)\left( \frac{1}{\epsilon_{\mathrm{UV}}} -\ln\frac{m_{\tilde{q}}^2}{\mu^2} \right)
\end{align}
The renormalization constant for the evaluation of $\delta g_s$ is determined by the condition
\begin{align}
\frac{\partial}{\partial \slashed{p}} \left[  \Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j}|_{\mathrm{UV-div}} + \Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}|_{\mathrm{UV-div,\mu-dep}} + \Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}  \right]_{p^2 = 0} = 0
\end{align}
and computes to
\begin{align}
\delta Z_q^{\mathrm{aux}} = -\frac{g_s^2}{16\pi^2} C(F)\left[\left( \frac{1}{\epsilon_{\mathrm{UV}}} \right) + \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln\frac{m_{\tilde{q}}^2}{\mu^2} \right) \right]
\end{align}
The first curved bracket corresponds to contributions from light particles in the loop whereas the second curved bracket corresponds to contributions from heavy particles in the loop.

\subsubsection{The Gluon Self-Energy}
As for the quark self-energy there are again contributions to the self-energy originating from light and heavy particles. As for the quark only specific terms are kept in calculating the auxiliary renormalization constants.  
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\node at (0,0.2) {1L};
	\node at (0,-0.18) {light};
	\draw[gluon](0:0.5)--(0:1.3);
	\node at (1.8,0) {=};
\begin{scope}[shift={(3.5,0)}]
	\draw[gluon](-1.3,0)--(0,0);
	\draw[gluon](0,0)--(1.3,0);
	\draw[gluon] (0,0) arc (-90:270:.5);
	\node at (0,1.3) {$G$};
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7.0,0)}]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermion] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {light $q$};
	\draw[fermion] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {light $q$};	
	\draw[gluon](0:0.5)--(0:1.3);
\end{scope}
\begin{scope}[shift={(10.5,0)}]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[ghost] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\eta$};
	\draw[ghost] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\eta$};	
	\draw[gluon](0:0.5)--(0:1.3);
\end{scope}
\begin{scope}[shift={(3.5,-2.5)}]
	\node at (-1.8,0) {+};
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$G$};
	\draw[gluon] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$G$};	
	\draw[gluon](0:0.5)--(0:1.3);
\end{scope}
\end{tikzpicture}
\caption{contribution to the self-energy of the gluon originating from light particles}\label{fig:lightGluonSelfEnergy}
\end{center}
\end{figure}
\begin{align}
i\Gamma^{\mathrm{1L,light}}_{G_\mu^a G_\nu^b}|_{\mathrm{UV-div}} &= i\frac{g_s^2}{16\pi^2 \epsilon_{\mathrm{UV}}}\delta_{ab} \left[ 0 - \frac{4 (n_{f}-1)}{3} T(F) (p^2g^{\mu\nu}-p^\mu p^\nu) + \frac{C(A)}{12}(p^2g^{\mu\nu} + 2 p^\mu p^\nu) \right.\nonumber\\
&+\left. \frac{C(A)}{12}(19 p^2g^{\mu\nu} - 22 p^\mu p^\nu) \right]\nonumber\\
&=i\frac{g_s^2}{16\pi^2 \epsilon_{\mathrm{UV}}}\delta_{ab} \left[ - \frac{4 (n_{f}-1)}{3} T(F) + \frac{5}{3} C(A) \right](p^2g^{\mu\nu}-p^\mu p^\nu)
\end{align}
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\node at (0,0.2) {1L};
	\node at (0,-0.18) {heavy};
	\draw[gluon](0:0.5)--(0:1.3);
	\node at (1.8,0) {=};
\begin{scope}[shift={(3.5,0)}]
	\draw[gluon](-1.3,0)--(0,0);
	\draw[gluon](0,0)--(1.3,0);
	\draw[scalar] (0,0) arc (-90:270:.5);
	\node at (0,1.3) {$\tilde{q}$};
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7.0,0)}]
	\draw[gluon](-1.3,0)--(0,0);
	\draw[gluon](0,0)--(1.3,0);
	\draw[scalarnoarrow] (0,0) arc (-90:270:.5);
	\node at (0,1.3) {$\phi^0,\sigma^0$};
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(10.5,0)}]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermion] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {heavy $q$};
	\draw[fermion] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {heavy $q$};	
	\draw[gluon](0:0.5)--(0:1.3);
\end{scope}
\begin{scope}[shift={(3.5,-2.5)}]
	\node at (-1.8,0) {+};
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\tilde{g}$};
	\draw[gluon] (0.5,0) arc (0:-180:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\tilde{g}$};	
	\draw[gluon](0:0.5)--(0:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7,-2.5)}]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[scalar] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\tilde{q}$};
	\draw[scalar] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\tilde{q}$};	
	\draw[gluon](0:0.5)--(0:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(10.5,-2.5)}]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[scalarnoarrow] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\phi^0,\sigma^0$};
	\draw[scalarnoarrow] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\phi^0,\sigma^0$};	
	\draw[gluon](0:0.5)--(0:1.3);
\end{scope}
\end{tikzpicture}
\caption{contribution to the self-energy of the gluon originating from heavy particles, in the last diagram either $\phi^0$ or $\sigma^0$ are running in the loop}
\end{center}
\end{figure}
The heavy particle contributions are given by\\
\begin{align}
i\Gamma^{\mathrm{1L,heavy}}_{G_\mu^a G_\nu^b}|_{\mathrm{UV-div, \mu-dep}} &= i\frac{g_s^2}{16\pi^2}\delta_{ab} \left[ - 4 T(F)n_f \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{q}}^2}{\mu2} \right)m_{\tilde{q}}^2 g^{\mu\nu} - C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)m_{\phi^0}^2 g^{\mu\nu} \right.\nonumber\\
&- C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\sigma^0}^2}{\mu2} \right)m_{\sigma^0}^2 g^{\mu\nu} - \frac{4}{3}T(F)\left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_t^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)\nonumber\\
& - \frac{4}{3} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{g}}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)\nonumber\\
& -\frac{2}{3}T(F) n_f \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{q}}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) + 4T(F)n_f \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{q}}^2}{\mu2} \right)m_{\tilde{q}}^2 g^{\mu\nu} \nonumber\\
&-\frac{1}{6} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) + C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)m_{\phi^0}^2 g^{\mu\nu} \nonumber\\
&\left.-\frac{1}{6} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) + C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)m_{\phi^0}^2 g^{\mu\nu}\right]\nonumber\\
&= i\frac{g_s^2}{16\pi^2}\delta_{ab} \left[- \frac{4}{3}T(F)\left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_t^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)\right.\nonumber\\
& - \frac{4}{3} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{g}}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)\nonumber\\
& -\frac{2}{3}T(F) n_f \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{q}}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) \nonumber\\
&-\frac{1}{6} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)  \nonumber\\
&\left.-\frac{1}{6} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) \right]
\end{align}
The counterterm Feynman rule for the gluon propagator is\\
\\
\begin{tikzpicture}[line width=1.0 pt, scale=0.8]
	\node at (-2.5,-0.1) {$i\Gamma^{\mathrm{1L,ct}}_{G_\mu^a G_\nu^b}\ \hat{=}\ a,\mu$};
\begin{scope}[shift={(0.4,0)}]	
	\draw[gluon] (-1.3,0) --(1.3,0);
	\draw[fermionnoarrow] (-0.3,0.3) -- (0.3,-0.3);
	\draw[fermionnoarrow] (-0.3,-0.3) -- (0.3,0.3);
	\node at (1.8,0) {$b,\nu$};
	\node at (5.6,0) {$\hat{=}\ -i \delta Z_G\left(p^2 g^{\mu\nu} - p^\mu p^\nu \right)\delta_{ab}.$};	
\end{scope}
\end{tikzpicture}\\
The renormalization condition for $\delta Z^{\mathrm{aux}}_G$ reads
\begin{align}
 \Gamma^{\mathrm{1L,light}}_{G_\mu^a G_\nu^b}|_{\mathrm{UV-div}} + \Gamma^{\mathrm{1L,heavy}}_{G_\mu^a G_\nu^b}|_{\mathrm{UV-div,\mu-dep}} - \delta Z_G^{\mathrm{aux}}\left(p^2 g^{\mu\nu} - p^\mu p^\nu \right)\delta_{ab} = 0
\end{align}
and yields
\begin{align}
\delta Z^{aux}_G &= \frac{g_s^2}{16\pi^2} \left\{\left[-\frac{4}{3}T(F)(n_f-1) + \frac{5}{3} C(A) \right] \frac{1}{\epsilon_{\mathrm{UV}}} + \left[ - \frac{4}{3}T(F) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_t^2}{\mu^2} \right)  \right.\right.\nonumber\\
&- \frac{4}{3} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{g}}^2}{\mu^2} \right) -\frac{2}{3}T(F) n_f \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{q}}^2}{\mu^2} \right)\nonumber\\
& - \frac{1}{6} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu^2} \right) - \frac{1}{6} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\sigma^0}^2}{\mu^2} \right).
\end{align}

\subsubsection{The $q\overline{q}G$ Vertex Correction}
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\node at (0,0.2) {1L};
	\node at (0,-0.18) {light};
	\draw[fermionbar](45:0.5)--(45:1.3);
	\draw[fermionbar](-45:0.5)--(-45:1.3);
	\node at (1.8,0) {=};
\begin{scope}[shift={(3.5,0)}]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermionbar](180:0.5)--(45:0.5);
	\node at (0,0.5) {$q$};
	\draw[fermionbar](180:0.5)--(-45:0.5);
	\node at (0,-0.5) {$q$};
	\draw[gluon](45:0.5)--(-45:0.5);
	\node at (0.7,0) {$G$};
	\draw[fermionbar](45:0.5)--(45:1.3);
	\draw[fermionbar](-45:0.5)--(-45:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7,0)}]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[gluon](180:0.5)--(45:0.5);
	\node at (0,0.5) {$G$};
	\draw[gluon](180:0.5)--(-45:0.5);
	\node at (0,-0.5) {$G$};
	\draw[fermion](45:0.5)--(-45:0.5);
	\node at (0.7,0) {$q$};
	\draw[fermionbar](45:0.5)--(45:1.3);
	\draw[fermionbar](-45:0.5)--(-45:1.3);
\end{scope}
\end{tikzpicture}
\caption{contribution from light particles to the $q\overline{q}G$ vertex correction}\label{fig:GaugeCouplingCorrection}
\end{center}
\end{figure}
\begin{align}
i\Gamma^{\mathrm{1L,light}}_{q_i \overline{q}_j G_\mu^a}|_{\mathrm{UV-div}} &= -i g_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2 \epsilon_{\mathrm{UV}}} \left[ \left(C(F) -\frac{C(A)}{2}\right) + \frac{3}{2} C(A) \right]
\end{align}
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\node at (0,0.2) {1L};
	\node at (0,-0.18) {heavy};
	\draw[fermionbar](45:0.5)--(45:1.3);
	\draw[fermionbar](-45:0.5)--(-45:1.3);
	\node at (1.8,0) {=};
\begin{scope}[shift={(3.5,0)}]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[scalarbar](180:0.5)--(45:0.5);
	\node at (0,0.5) {$\tilde{q}$};
	\draw[scalarbar](180:0.5)--(-45:0.5);
	\node at (0,-0.5) {$\tilde{q}$};
	\draw[gluon](45:0.5)--(-45:0.5);
	\draw[fermionnoarrow](45:0.5)--(-45:0.5);
	\node at (0.7,0) {$\tilde{g}$};
	\draw[fermionbar](45:0.5)--(45:1.3);
	\draw[fermionbar](-45:0.5)--(-45:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7,0)}]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[gluon](180:0.5)--(45:0.5);
	\draw[fermionnoarrow](180:0.5)--(45:0.5);
	\node at (0,0.5) {$\tilde{g}$};
	\draw[gluon](180:0.5)--(-45:0.5);
	\draw[fermionnoarrow](180:0.5)--(-45:0.5);
	\node at (0,-0.5) {$\tilde{g}$};
	\draw[scalar](45:0.5)--(-45:0.5);
	\node at (0.7,0) {$\tilde{q}$};
	\draw[fermionbar](45:0.5)--(45:1.3);
	\draw[fermionbar](-45:0.5)--(-45:1.3);
\end{scope}
\end{tikzpicture}
\caption{contribution from heavy particles to the $q\overline{q}G$ vertex correction}
\end{center}
\end{figure}
\begin{align}
i\Gamma^{\mathrm{1L,heavy}}_{q_i \overline{q}_j G_\mu^a}|_{\mathrm{UV-div,\mu-dep}} = -i g_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} &\left[ \left(C(F) -\frac{C(A)}{2}\right) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{g}}^2}{\mu^2} \right) \right.\nonumber\\
&+ \left.\frac{1}{2} C(A)\left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{g}}^2}{\mu^2} \right) \right]
\end{align}
The sum of the 1-loop corrections and the counterterm should be set to zero:
\begin{align}
i\Gamma^{\mathrm{1L,light}}_{q_i \overline{q}_j G_\mu^a}|_{\mathrm{UV-div}} + i\Gamma^{\mathrm{1L,heavy}}_{q_i \overline{q}_j G_\mu^a}|_{\mathrm{UV-div,\mu-dep}} + \left[ -ig_s T^a_{ij}\gamma^\mu\left( \frac{\delta g_s}{g_s} + \delta Z_q^{\mathrm{aux}} + \frac{\delta Z_G^{\mathrm{aux}}}{2} \right)\right] = 0.
\end{align}
Finally one can read off the $\frac{\delta g_s}{g_s}$
\begin{align}
\frac{\delta g_s}{g_s} &= \frac{g_s^2}{16\pi^2} \left[ \left( \frac{2}{3}T(F)(n_f-1) - \frac{11}{6}C(A) \right) \frac{1}{\epsilon_{\mathrm{UV}}} + \left( \frac{5}{6}C(A) + \frac{2}{3}T(F) + \frac{1}{3}T(F)n_f \right)\frac{1}{\epsilon_{\mathrm{UV}}}  \right.\nonumber\\
&- \frac{2}{3} C(A) \ln \frac{m_{\tilde{g}}^2}{\mu^2} - \frac{1}{3}T(F)n_f \ln \frac{m_{\tilde{q}}^2}{\mu^2} - \frac{2}{3}T(F) \ln \frac{m_t^2}{\mu^2}-\frac{1}{12} C(A) \left( \ln \frac{m_{\phi^0}^2}{\mu^2} + \ln \frac{m_{\sigma^0}^2}{\mu^2} \right)\label{eq:deltaGs}
\end{align}

\subsubsection{The Beta Function}
The beta function describes the dependence of the gauge coupling $g_s$ upon the energy scale $\mu$.\\
Writing down the action of a theory in $D$ dimensions one needs to introduce an energy scale $\mu$ in order to keep the action dimensionless. But $\mu$ is no physical parameter and can be absorped into the fields and parameters. To this end one defines
\begin{align}
g_{sB} = \mu^\epsilon g_s \left( 1 + \frac{\delta g_s}{g_s} \right)
\end{align}
which must not depend upon the unphysical scale $\mu$, ergo
\begin{align}
0 = \frac{\mathrm{d}g_{sB}}{\mathrm{d}\ln\mu} = \frac{\partial g_{sB}}{\partial \ln\mu} + \beta \frac{\partial g_{sB}}{\partial g_s}\label{eq:beta_func}
\end{align}
where the definition of the beta function $\frac{\partial g_s}{\partial\ln\mu}$ has been inserted. Equation \ref{eq:beta_func} serves to calculate $\beta(g_s,\epsilon)$.  By equating coefficients and using the shortcuts
\begin{align*}
\frac{\beta_0^L}{2} &= \frac{2}{3}T(F)(n_f-1) - \frac{11}{6}C(A)\\
\frac{\beta_0^H}{2} &= \frac{5}{6}C(A) + \frac{2}{3}T(F) + \frac{1}{3}T(F)n_f\\
L &= - \frac{2}{3} C(A) \ln \frac{m_{\tilde{g}}^2}{\mu^2} - \frac{1}{3}T(F)n_f \ln \frac{m_{\tilde{q}}^2}{\mu^2} - \frac{2}{3}T(F) \ln \frac{m_t^2}{\mu^2}-\frac{1}{12} C(A) \left( \ln \frac{m_{\phi^0}^2}{\mu^2} + \ln \frac{m_{\sigma^0}^2}{\mu^2} \right)
\end{align*}
so that 
\begin{align}
\frac{\delta g_s}{g_s} = \frac{g_s^2}{16\pi^2}\left( \frac{\beta^L_0}{2\epsilon_{\mathrm{UV}}} + \frac{\beta^H_0}{2\epsilon_{\mathrm{UV}}} + L \right)
\end{align}
one finds
\begin{align}
\beta(g_s,\epsilon) &= -\epsilon g_s \left( 1 + \frac{g_s^2}{16\pi^2} L \right) + \beta(g_s) + \mathcal{O}(\mathrm{2-loop})\\
\beta(g_s) &= \frac{g_s^3}{16\pi^2} \beta_0^L.
\end{align}
This is exactely the beta function from QCD first found by [Gross, Politzer, Wil]

\subsection{Supersymmetry Restoring Counterterm}
As already discussed in section \ref{sec:RegSchemeDep} care is required in terms of supersymmetry restoring when renormalizing  the gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$. In doing so one needs the already calculated supersymmetry restoring counterterms of the quark, squark and gluino from \ref{eq:QuarkSC}, \ref{eq:SquarkSC} and \ref{eq:GluinoSC}
as well as the supersymmetry restoring counterterm of the gluon.
\subsubsection*{The Gluon Self-Energy Revisited}
The only regularization dependence of the gluon self-energy arises from the gluon loop, i.e. the last diagram in figure \ref{fig:lightGluonSelfEnergy}. With the definition of $\Gamma^{\mathrm{(1),ct,restore}}_{\mathrm{DREG}}$ in \ref{eq:GammaCtRestore} one obtains
\begin{align}
i\Gamma^{\mathrm{(1),ct,restore}}_{\mathrm{DREG},G_\mu^a G_\nu^b} = -i\frac{1}{3} C(A) \frac{g_s^2}{16\pi^2}(p^2 g^{\mu\nu}-p^\mu p^\nu)\delta_{ab}
\end{align}
which translates to the transition counterterm
\begin{align}
\delta Z^{\mathrm{trans}}_G = \frac{C(A)}{3}\frac{g_s^2}{16\pi^2}.
\end{align}

\subsubsection*{The $q\overline{q}G$ Vertex Correction Revisited}
The supersymmetry restoring contributions to the gauge coupling correction are shown in figure \ref{fig:GaugeCouplingCorrection} and evaluate to
\begin{align}
i\Gamma^{\mathrm{(1),ct,restore}}_{\mathrm{DREG}, q_i\overline{q}_jG_\mu^a} &= -ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2}\left[ \left( C(F) - \frac{C(A)}{2} \right) + \frac{C(A)}{2} \right]\\
&= -ig_s T^a_{ij} \gamma^\mu \left[ \frac{\delta g_s^{\mathrm{trans}}}{g_s} + \delta Z^{\mathrm{trans}}_q + \frac{\delta Z^{\mathrm{trans}}_G}{2} \right]
\end{align}
where in the second line the equation with the supersymmetry restoring counterterms has been performed. This yields
\begin{align}
\frac{\delta g_s^{\mathrm{trans}}}{g_s} = -\frac{C(A)}{6} \frac{g_s^2}{16\pi^2}.
\end{align}

\subsubsection*{The $q\tilde{q}^\dagger\tilde{g}$ Vertex Correction}
The supersymmetry restoring corrections to the Yukawa coupling origin from the below diagram 
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermionnoarrow](180:1.3)--(180:0.5);
	\draw[gluon](180:0.5)--(45:0.5);
	\node at (0,0.5) {$G$};
	\draw[fermionnoarrow](180:0.5)--(-45:0.5);
	\draw[gluon](180:0.5)--(-45:0.5);
	\node at (0,-0.5) {$\tilde{g}$};
	\draw[scalar](45:0.5)--(-45:0.5);
	\node at (0.7,0) {$q$};
	\draw[fermionbar](45:0.5)--(45:1.3);
	\draw[scalarbar](-45:0.5)--(-45:1.3);
\end{tikzpicture}
\caption{diagram of the supersymmetry restoring correction of  the $q\tilde{q}\tilde{g}$ vertex}
\end{center}
\end{figure}
The supersymmetry restoring part is
\begin{align}
i\Gamma^{\mathrm{(1),ct,restore}}_{\mathrm{DREG}, q_i\tilde{q}_j\tilde{g}^a} &= -ig_s \sqrt{2} P_L T^a_{ij}  \frac{g_s^2}{16\pi^2}C(A)\\
&= -ig_s \sqrt{2} P_L T^a_{ij}  \left[ \frac{\delta \hat{g}_s^{\mathrm{trans}}}{g_s} + \frac{\delta Z^{\mathrm{trans}}_q + \delta Z^{\mathrm{trans}}_{\tilde{q}} + \delta Z^{\mathrm{trans}}_{\tilde{g}}}{2} \right].
\end{align}
The supersymmetry restoring part of the Yukawa renormalization constants is therefore
\begin{align}
\frac{\delta \hat{g}_s^{\mathrm{trans}}}{g_s} = -\frac{C(F)-C(A)}{2} \frac{g_s^2}{16\pi^2}.
\end{align}
As a consequence of the two different supersymmetry restoring parts of the coupling renormalization constants an additional renormalization constant $\delta g_s^{\mathrm{restore}}$ needs to be introduced. As described in section \label{sec:RegSchemeDep} it is given by
\begin{align}
\frac{\delta g_s^{\mathrm{restore}}}{g_s} = \frac{\delta \hat{g}_s^{\mathrm{trans}}}{g_s} -\frac{\delta g_s^{\mathrm{trans}}}{g_s} = \frac{g_s^2}{16\pi^2}\left( \frac{2C(A)}{3} - \frac{C(F)}{2} \right).
\end{align}
In short this means that the gauge coupling $g_s$ is renormalized with $\delta g_s$ given in \ref{eq:deltaGs} and the Yukawa coupling $\hat{g}_s$ is renormilzed with $\delta \hat{g}_s = \delta g_s + \delta g_s^{\mathrm{restore}}$.\\
The finite correction $g_s^{\mathrm{restore}}$ is the same as in supersymmetric QCD which should not surprise too much as all its contributions origin from loops with gluons. So there are no new contributions in RSQCD with respect to SQCD.

\subsection{$\overline{\mathrm{MS}}$ - Renormalization}
To check for UV-finiteness it might prove useful to summarize the UV-divergent part of all renormalization constants. In order to obtain these the Passarino-Veltman integrals need to be substituted by their $\frac{1}{\epsilon}$ coefficient. These  had been taken from \cite{Denner} and checked with \texttt{FeynArts} and \texttt{FormCalc} \cite{Hahn:2000}, \cite{Nejad2013}, \cite{Hahn:2000}.

### 2016-02-25 Standardmodel.tex

\section{The Standard Model}
The standard model(SM) is a relativistic quantum field theory. 
It contains different fields, whose quantized excitations are interpreted as particles.\\
%The different fields defined on Minkowski space are Dirac spinors describing matter fields (leptons and quarks), gauge vectors describing force mediators and a scalar field (the Higgs) which accounts for the masses of particles.\\
%More formally a particle state is said to give rise to an irreducible representation of the Poincaré group

\subsection{Symmetries and Transformations}
\paragraph{Space-Time Symmetries:}
The SM is defined on Minkowski space, whose coordinates are label with $x^\mu$ $\mu = 0,1,2,4$. As a relativistic theory it is invariant under Poincaré transformations, i.e. it is invariant under Lorentz-transformations (with generators $J^{\mu\nu}$) and translations (with generators $P^\mu$) in spacetime. The set of all Poincaré transformations form the Poincaré group, which is a Lie group. Its generators obey the Poincaré-algebra
\begin{align}
[P^\mu,P^\nu] &= 0\nonumber\\
[P^\mu,J^{\nu\rho}] &= i(g^{\mu\nu} P^\rho - g^{\mu\rho}P^\nu)\nonumber\\
[J^{\mu\nu},J^{\rho\sigma}] &= i(g^{\nu\rho}J^{\mu\rho} + g^{\mu\sigma}J^{\nu\rho} - g^{\mu\rho}J^{\nu\sigma} - g^{\nu\sigma}J^{\mu\rho}).
\end{align}
The fields of the SM transform in different representations of the Poincaré-group.

\paragraph{Gauge Symmetries:} In order to describe interactions of matter particles one uses gauge theories. In the SM which is such a theory matter fields are described by Dirac spinors. The Lagrangian of a free Dirac field reads
\begin{align}
\mathcal{L}_{Dirac} = \overline{\Psi} ( i\slashed{\partial} - m)\Psi.\label{eq:DiracLagrangian}
\end{align}
To include interactions one imposes a local group symmetry (gauge symmetry) upon this Lagrangian. A spinor transforms under a generic gauge transformation like 
\begin{align}
\psi(x) \to U(x)\psi(x),
\end{align}
where $U(x)$ is an element of the gauge group in question. Because the gauge group is a unitary matrix Lie group it can be written in the form $U(x)=\mathrm{exp}(-igT^a\theta^a(x))$. Here $T^a$ are the self-adjoint generators of the associated Lie algebra, $g$ is the coupling constant of the gauge group and $\theta^a(x)$ are local parameters. The structure constants $f_{abc}$ of a Lie algebra are defined by $[T^a,T^b] = if_{abc}T^c$.\\
Because the parameters of the gauge group are local the derivative in \ref{eq:DiracLagrangian} spoils the gauge invariance. In order to rectify gauge invariance of the Lagrangian one has to introduce a further field for each index $a$ of the generators - the gauge vector $G^{a\mu}$. The matrix valued gauge vector $G^\mu := G^{a\mu}T^a$ transforms as 
\begin{align}
G^{\mu}(x) \to U(x)G^\mu(x)U^{-1}(x) + \frac{i}{g}U(x)\partial^\mu U^{-1}(x)
\end{align}
One then obtains the gauge invariant Lagrangian for a non-abelian gauge theory first found by Yang and Mills [cite original paper]
\begin{align}
\mathcal{L}_{Yang-Mills} = \overline{\Psi}i\slashed{D}\Psi - \frac{1}{4}F^{a\mu\nu}F^a_{\mu\nu}
\end{align}
In comparison to the Dirac-Lagrangian \ref{eq:DiracLagrangian} the partial derivative is replaced with the gauge covariant derivative $D^\mu = \partial^\mu + igT^aG^{a\mu}$ and the gauge invariant kinetic term for the gauge fields is added. This comprises the field strenth-tensor $F^{a\mu\nu}$ which is in its matrix valued form defined by $F^{\mu\nu} = F^{a\mu\nu}T^a = \frac{1}{ig}[D^\mu,D^\nu]$.\\
The gauge group of the SM is a direct product ??? of the three gauge groups: $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$\footnote{The subscript stands for the associated charge of the groups respectively: $Y$ for hypercharge, $L$ for left handedness (weak Isospin $I_3$) and $C$ for color}. The elements $U(x)$ of those and the infinitesimal transformations of the spinors and gauge vectors are given in table \ref{tab:SM_transformations}.\\
These gauge groups give rise to 3 forces: the strong force, the weak force and the electromagnetic force.
\begin{table}[H]
\begin{center}
\begin{tabular}{|c|l|}
\hline
 & $U(x) = \mathrm{exp}\left(-ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)$\\
 $U_Y(1)$ & $\psi(x) \to \left( 1 - ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)\psi(x)$\\
 & $B^\mu(x) \to B^\mu(x) + \partial^\mu\theta_Y(x)$\\
\hline
 & $U(x) = \mathrm{exp}\left(-ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)$\\
 $SU_L(2)$ & $\psi(x) \to \left( \mathbbm{1} - ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)\psi(x)$\\
 & $W^{a\mu}(x) \to W^{a\mu}(x) +\partial^\mu\theta^a_w(x) + g_w \varepsilon^{abc} \theta^b_w(x)W^{c\mu}(x)$\\
  \hline
 & $U(x) = \mathrm{exp}\left(-ig_s T^a \cdot \theta_s^a(x)\right)$\\
$SU_C(3)$ & $\psi(x) \to \left(\mathbbm{1}-ig_s T^a \cdot \theta_s^a(x)\right)$\\
 & $G^{a\mu}(x) \to G^{a\mu}(x) + \partial^\mu\theta^a_s(x) + g_s f_{abc} \theta^b_s(x)G^{c\mu}$\\
 \hline
\end{tabular}
\caption{The table lists the explicit element $U(x)$ of the gauge groups $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$ and the infinitesimal transformations of spinor and vector fields.\newline
The hypercharge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to. $\vec{\tau}$ and $T^a$ are the geneators of $SU_L(2)$ and $SU_C(3)$ respectively. In the fundamental representation one has $\vec{\tau} = \frac{\vec{\sigma}}{2}$ where $\vec{\sigma}$ has the 3 Pauli matrices as components and $T^a = \frac{\lambda^a}{2}$ where $\lambda^a$ are the 8 Gell-Mann matrices. $\varepsilon_{abc}$ and $f_{abc}$ are the structure constants of $SU_L(2)$ and $SU_C(3)$ respectively.}\label{tab:SM_transformations}
\end{center}
\end{table}

%Furthermore the SM is a gauge theory, which has the gauge group $SU_C(3)\times SU_L(2)\times U_Y(1)$.
%\paragraph{Transformation under $U_Y(1)$:}
%Under $U_Y(1)$ spinor fields transform like
%\begin{align}
%\psi(x) = \mathrm{exp}\left(-ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)\psi(x)
%\end{align}
%where $\hat{Y}$ is the hypercharge operator. The corresponding gauge field transforms as
%\begin{align}
%B^\mu(x) \to B^\mu(x) + \partial^\mu\theta_Y(x)
%\end{align}
%\paragraph{Transformation under $SU_L(2)$:}
%Spinor fields transform under this group as
%where $\vec{\sigma}$ has the three Pauli matrices (see Appendix) as components. The gauge fields transforms as 
%\begin{align}
%W^{a\mu}(x) \to W^{a\mu}(x) +\partial^\mu\theta^a_w(x) + g_w \varepsilon^{abc} \theta^b_w(x)W^{c\mu}(x) 
%\end{align}
%\paragraph{Transformation under $SU_C(3)$:}
%Spinor fields transform under this group as
%\begin{align}
%\psi(x) = \mathrm{exp}\left(-ig_s T^a \cdot \theta_s^a(x)\right)\psi(x), 
%\end{align}
%where $T^a = \frac{\lambda^a}{2}$ and $\lambda^a$ are the 8 Gell-Mann matrices matrices (see Appendix). The Gluon fields transforms as 
%\begin{align}
%G^{a\mu}(x) \to G^{a\mu}(x) + \partial^\mu\theta^a_s(x) + g_s f_{abc} \theta^b_s(x)G^{c\mu}
%\end{align}
%Table ??? shows under which representation the fields transform
%\begin{align}
%\mathcal{L}_{gauge} = -\frac{1}{4}F^{\mu\nu}F_{\mu\nu} - \frac{1}{4}W^{a\mu\nu}W^a_{\mu\nu} - \frac{1}{4}G^{a\mu\nu}G^a_{\mu\nu}
%\end{align}

\newpage
\subsection{The particles of the SM}
In the SM different matter particles take part in different interactions, i.e. their corresponding spinor couples to different gauge vectors.\\
If a spinor couples to a certain gauge vector it transforms  non trivially (like indicated in table \ref{tab:SM_transformations}) under the gauge group which is associated with this gauge vector\footnote{In the SM all matter particles transform in the fundamental (or trivial) representation of the gauge group in question.}. This means if a particle couples to a certain force its charge which is associated with this force is nonzero.\\
The charges of particles for a force are defined as the eigenvalues of the generators which correspond to the force.
\subsubsection*{The Quarks:}
Quarks are strongly interacting fermions, which means their spinors transform non trivially under $SU_C(3)$. Because they transform in the fundamental representation of $SU_C(3)$ this means a quark spinor is built up by 3 spinors each carrying another color. This splitting of the quark spinor in colors is often suppressed for the sake of simplicity. This convention is adopted throughout this thesis.\\
Furthermore the left handed component of quarks interact weakly, which means that their spinors transform (in the fundamental representation) under $SU_L(2)$ meaning that 2 left handed quark spinors are assembled in a doublet.\\
Finally all quarks carry a hypercharge. In section ??? the mechanism of electroweak symmetry breaking is described. This mechanism explains how electromagnetism arises from the groups $SU_L(2)$ and $U_Y(1)$. All quarks interact electromagnetically.\\
After all there are 6 quarks which are listed in table\ref{tab:generations}. They are categorized in 3 generations because their quantum numbers except (for their mass) is the same in each generation. The two types of quarks which have distinct quantum numbers are the up-type-quarks and the down-type quarks. A up-type-quark and the down-type quark of the same generation built up a doublet.
\subsubsection*{The Leptons:}
Leptons do not interact strongly. They take part in the weak and the electromagnetic interaction, i.e. their spinors transform under the fundamental representation of $SU_L(2)$ and $U_Y(1)$. As for the quarks only the left handed components interact weakly.\\
As for the quarks there are 6 leptons which are classified into 3 generations (see table \ref{tab:generations}). In each generation is a lepton with a negative electrical charged and an electrically neutral lepton. The latter ones are referred to as neutrinos. Right handed neutrinos have not been observed (yet) and are therefore absent in the SM. The former are called electron, muon and tau. Each left handed leptons with an electric charge is assembled with its neutrino in a doublet.
\bigbreak
Quarks and Leptons are the matter particles of the SM. They are listed together with their charges for the different forces in table \ref{tab:SMfieldcontent}. One has the color for strong interactions, the third component of the weak isospin $I_3$ for weak interactions(the eigenvalue of the third generator of the $SU_L(2)$) and the half of the hypercharge $\frac{Y}{2}$ to obtain the electric charge $Q$ via the Gell-Mann–Nishijima formula: $Q = I_3 + \frac{Y}{2}$.\\
Because the left and right-handed parts of spinors transform differently under the $SU_L(2)$ they are listed separately.\\
All quarks occur with three different colors.\\
In the last row the Higgs-boson is listed. Its associated field is responsible for the mass of elementary particles. That is explained in section \ref{sec:EWSB}.\\
\begin{table}[H]
\begin{center}
\begin{tabular}{l?l|l|l}
Particle & 1$^{st}$ generation & 2$^{nd}$ generation & 3$^{rd}$ generation\\
\hlinewd{2pt}
$u_{i}$ \hspace{0.5cm} up-type-Quark & $u$ \hspace{0.5cm} up-Quark & $c$ \hspace{0.5cm} charm-Quark & $t$ \hspace{0.5cm} top-Quark\\
$d_{i}$ \hspace{0.5cm} down-type-Quark & $d$ \hspace{0.5cm} down-Quark & $s$ \hspace{0.5cm} strange-Quark & $b$ \hspace{0.5cm} bottom-Quark\\
\hline
$e_i$ \hspace{0.5cm} Charged Lepton & $e$ \hspace{0.5cm} Electron & $\mu$ \hspace{0.5cm} Muon &  $\tau$ \hspace{0.5cm} Tau\\
$\nu_i$ \hspace{0.5cm} Neutrino & $\nu_e$ \hspace{0.35cm} Electron Neutrino & $\nu_\mu$ \hspace{0.35cm} Muon Neutrino &  $\nu_\tau$ \hspace{0.35cm} Tau Neutrino
\end{tabular}
\caption{The matter particles of the SM. Listed are the symbol and the name of the particles.}\label{tab:generations}
\end{center}
\end{table}
\begin{table}[H]
\begin{center}
\begin{tabular}{c?c|c|c|c|c}
Particle & Symbol & color & $I_3$ & $\frac{Y}{2}$ & Q\\
\hlinewd{2pt}
Left handed Quarks & $Q_{iL} = \begin{pmatrix}
u_{iL}\\
d_{iL}
\end{pmatrix}$ & red, green, blue & $\begin{pmatrix}
+\frac{1}{2}\\
-\frac{1}{2}
\end{pmatrix}$ & $+\frac{1}{6}$ & $\begin{pmatrix}
+\frac{2}{3}\\
-\frac{1}{3}
\end{pmatrix}$\\
Right-handed Quarks & $u_{iR}$ & red, green, blue & $0$ & $+\frac{2}{3}$ & $+\frac{2}{3}$ \\
 & $d_{iR}$ & red, green, blue & $0$ & $-\frac{1}{3}$ & $-\frac{1}{3}$\\
\hline
Left-handed Leptons & $\ell_{iL} = \begin{pmatrix}
\nu_{iL}\\
e_{iL}
\end{pmatrix}$ & - & $\begin{pmatrix}
+\frac{1}{2}\\
-\frac{1}{2}
\end{pmatrix}$ & $-\frac{1}{2}$ & $\begin{pmatrix}
0\\
-1
\end{pmatrix}$\\
Right-handed Leptons & $e_{iR}$ & - & 0 & $+1$ & $+1$\\
\hline
Higgs & $H$ & - & $-\frac{1}{2}$ & $+\frac{1}{2}$ & $0$
\end{tabular}
\caption{This table lists all matter particles in the SM and the Higgs particle with their charges for all forces. This is the color, the weak isospin $I_3$, the half of their hypercharge and their electrical charge. The index $i = 1,2,3$ labels the generation of the matter particles and is written out in table \ref{tab:generations}}\label{tab:SMfieldcontent}
\end{center}
\end{table}
\subsubsection*{The Force Particles}
The force particles are described by gauge fields. The gluon field is the gauge field of $SU_C(3)$. Because the $SU_C(3)$ has 8 generators there are 8 gluons. Their coupling constant is $g_s$.\\
For the other force particles in the SM - the $W^\pm$ bosons, the $Z_0$ boson and the photon the is situation is slightly more involved. They are obtained as a mixture of the $W^b_\mu$ ($b=1,2,3$)and the $B_\mu$ field. This mixing procedure is referred to as electroweak symmetry breaking and is explained in section???.\\
For the moment being the coupling constants and gauge fields before and after EWSB are quoted in table \ref{tab:force_particles}
\begin{table}[H]
\begin{center}
\begin{tabular}{c|c|c?c|c|c}
\multicolumn{3}{c?}{before EWSB} & \multicolumn{3}{c}{after EWSB}\\
\hlinewd{2pt}
group & coupling constant & gauge field & coupling constant & gauge field & Particle\\
\hlinewd{2pt}
$SU_C(3)$ & $g_s$ & $G^a_\mu$ & $g_s$ & $G^a_\mu$ & Gluon\\
$SU_L(2)$ & $g_w$ & $W^b_\mu$ & $g_W = \sqrt{2}g_w$,  &  $W^\pm_\mu$,  & $W^\pm$,  \\
 & & & $g_Z = \sqrt{g_w^2 + g_Y^2}$ & $Z^0_\mu$ & $Z^0$ Boson\\
$U_Y(1)$ & $g_Y$ & $B_\mu$ & $e = g_Y\cdot c_w$ & $A_\mu$ & Photon
\end{tabular}
\caption{The gauge fields and their coupling constants before and after EWSB. The Gluon field is not affected by EWSB. $a = 1,\hdots 8$ and $b=1,2,3$ label the number of gauge fields. $c_w$ is the cosine of the electroweak mixing angle defined in \ref{sec:EWSB}}\label{tab:force_particles}
\end{center}
\end{table}
The Lagrangian of the SM is built up by qualitatively different terms. Firstly there are the kinetic and minimal coupling terms of the matter fields 
\begin{align}
\mathcal{L}_{matter} =  \sum_{i=1}^3 \left( \overline{\ell}_{iL} i \slashed{D} l_{iL} + \overline{e}_{iR} i \slashed{D} e_{iR} + \overline{q}_{iL} i \slashed{D} q_{iL} + \overline{u}_{iR} i \slashed{D} u_{iR} \right)
\end{align}
where $i=1,2,3$ labels the generations of matter. The gauge covariant derivative is given by
\begin{align}
D_\mu = \partial_\mu + i g_Y\frac{\hat{Y}}{2} +ig_w \vec{\tau}\cdot \vec{W}^\mu + i g_s T^a G_a^\mu
\end{align}
where for each field the corresponding representation (fundamental or trivial) of the gauge group is to be inserted (see table \ref{tab:SMfieldcontent}). The hyper charge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to. These can be taken from table \ref{tab:SMfieldcontent}.
The kinetic terms of the gauge fields are given by
\begin{align}
\mathcal{L}_{gauge} = -\frac{1}{4}F^{\mu\nu}F_{\mu\nu} - \frac{1}{4}W^{a\mu\nu}W^a_{\mu\nu} - \frac{1}{4}G^{a\mu\nu}G^a_{\mu\nu}
\end{align}

\subsection{Electroweak Symmetry Breaking}\label{sec:EWSB}
So far no mass terms like in the Dirac Lagrangian \ref{eq:DiracLagrangian} have been introduced. The reason for that is that they are not gauge invariant. The same argument forbids terms like $-\frac{m^2}{2}A^\mu A_\mu$ for a generic gauge boson. EWSB gives masses to these particles while maintaining gauge invariance. To this end one considers a complex scalar doublet
\begin{align}
\Phi = \begin{pmatrix}
\phi^+ \\ 
\phi^0
\end{pmatrix}
\end{align}
which acquires a vacuum expectation value (VEV) $\langle \Phi \rangle = \frac{1}{\sqrt{2}}\begin{pmatrix}
0 \\ v
\end{pmatrix}$ by the Higgs potential
\begin{align}
V(\Phi^\dagger\Phi) = -\mu^2 \Phi^\dagger\Phi + \lambda (\Phi^\dagger\Phi)^2
\end{align}
where $\mu^2,\lambda > 0$.
The Higgs sector of the SM reads
\begin{align}
&\mathcal{L}_{Higgs} = (D_\mu \Phi)^\dagger (D^\mu \Phi) - V(\Phi^\dagger\Phi).
\end{align}
The Higgs doublet couples to the gauge fields of $SU_L(2)$ and $U_Y(1)$ in the fundamental representation. Inserting an expansion\footnote{The complex $\phi^+(x)$ and the real $\sigma(x)$ are so called massless Goldstone bosons. These degrees of freedom can be absorbed in the longitudinal polarized degrees of freedom of the arising gauge bosons $W^\pm$ and $Z^0$. The real $H(x)$ is the Higgs field, whose excitation is the Higgs boson.} around the VEV $\Phi = \begin{pmatrix}
\phi^+(x) \\
\frac{1}{\sqrt{2}} (v + H(x) + i\sigma(x))
\end{pmatrix}$ one obtains quadratic terms, i.e. mass terms, in the gauge fields in question. In order to get mass eigenstates for the gauge bosons one performs the transformation
\begin{align}
&\begin{pmatrix}
A_\mu \\
Z^0_\mu
\end{pmatrix} = \begin{pmatrix}
\cos \theta_w & \sin \theta_w \\
-\sin \theta_w & \cos \theta_w
\end{pmatrix} \begin{pmatrix}
B_\mu \\
W^3_\mu
\end{pmatrix}
&& W^{\pm}_\mu = \frac{1}{\sqrt{2}}(W^1_\mu \mp W^2_\mu),
\end{align}
where the electroweak mixing angle is given by $\cos\theta_w = \frac{g_w}{\sqrt{g_w^2 + g_Y^2}}$
These gauge fields acquire masses:
\begin{align}
& m_W = \frac{g_w}{2} v \hspace{4cm} m_Z = \frac{\sqrt{g_w^2+g_Y^2}}{2} v \hspace{4cm} m_A = 0.
\end{align}
Apart from the massive  $W^\pm_\mu$ and $Z^0_\mu(x)$ bosons one obtains the massless photon $A_\mu$. As the photon is massless it is still associated with a gauge symmetry called $U_{em}(1)$. One therefore often writes EWSB as the braeking of the gauge group $SU_L(2) \times U_Y(1)$ to $U_Y(1)$.\\
Matter particles acquire mass via Yukawa coulings to the Higgs doublet. For up-type-quarks one uses that the charge conjugate of $\Phi$: $\Phi^C = i \sigma^2 \Phi^\ast$ transform as $\Phi$.
\begin{align}
\mathcal{L}_{Yukawa} = \sum_{i,j=1}^3 \left( y_{ij}^e \overline{\ell}_L \Phi e_R  + y_{ij}^d \overline{q}_L \Phi d_R + y_{ij}^u \overline{q}_L \Phi^C u_R\right) + h.c. 
\end{align}
where $y^e$, $y^d$, $y^u$ are 3$\times$3 matrices in generation space. The fermion mass matrices are therefore:
\begin{align}
m^e_{ij} = \frac{y^e_{ij}}{\sqrt{2}} v  \hspace{4cm} m^d_{ij} = \frac{y^d_{ij}}{\sqrt{2}} v \hspace{4cm} m^u_{ij} = \frac{y^u_{ij}}{\sqrt{2}} v.
\end{align}
The quark mass matrices are not diagonal. One therefore has to distinguish between interaction and mass eigenstates of the quark. The corresponding transformation matrix is the well known CKM-matrix [quote (original paper)].\\
The upshot of EWSB are masses for all matter particles except for the neutrinos and masses for the gauge bosons $W^\pm$ and $Z^0$.

\subsection{Quantization}
The Quantization of Spin 0 and Spin $\frac{1}{2}$ fields yield no complication in the Lagrangian formalism. To quantize Spin 1 fields it turns out that the usual gauge invariance needs to be replaced by the so called BRST invariance. This results in 2 extra terms in the Lagrangian. Firstly there is the gauge fixing term
\begin{align}
\mathcal{L}_{R_\xi} = -\frac{1}{2\xi_A} (\partial^\mu A_\mu)^2  - \frac{1}{2\xi_W} |\partial^\mu W_\mu^+ - m_W \xi_W \phi^+|^2 - \frac{1}{2\xi_Z} (\partial^\mu Z_\mu - m_Z \xi_Z \sigma)^2 CHECK!
\end{align}
Here $R_\xi$ is chosen, where the parameters $\xi_i$ specify the gauge. The last 2 terms are modified with the Goldstone bosons from section \ref{sec:EWSB} because of the massiveness of the $W^\pm$ an $Z^0$ bosons.\\
Secondly there is a ghost Lagrangian
\begin{align}
\mathcal{L}_{ghost} = 
\end{align}
see [Denner Gauge Theories S622]

\subsection{Lagrangian of the SM}
The complete Lagrangian of the SM reads
\begin{align}
\mathcal{L}_{SM} = \mathcal{L}_{matter} + \mathcal{L}_{gauge} + \mathcal{L}_{Higgs} + \mathcal{L}_{Yukawa} + \mathcal{L}_{R_\xi} + \mathcal{L}_{ghost}
\end{align}
with the corresponding parts of the previous chapters

### 2016-03-03 TreeLevel.tex
partonic cross section

@@
 \subsection{Partonic Processes}
+The top quark is excluded from the initial states as it is too heavy to be significantly present in hadrons.
+Therefore its pdf is approximately zero.
+For consistency reasons also the stop is excluded from the final states.
+One therefore deals with $n_f-1 = 5$ quark flavors.
 Using the Feynman rules in the Appendix one obtains the following sums over absolute squared Feynman amplitudes
 \begin{align}
-\sum|\mathcal{M}^B|^2(q_i q_j \to \tilde{q}\tilde{q}) &= \delta_{ij} 2\hat{g}_s^4\left[ \frac{4}{t_{\tilde{g}}^2} + \frac{4}{u_{\tilde{g}}^2} \right] (tu-m_{\tilde{q}}^4) + (1-\delta_{ij}) ???
-\nonumber\\
-\sum|\mathcal{M}^B|^2(q_i\overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij} 4 \left[ g_s^4\frac{8n_f}{s^2} + \hat{g}_s^4\frac{4}{t_{\tilde{g}}^2} - g_s^2\hat{g}_s^2\frac{8}{3 t_{\tilde{g}} s} \right] (tu-m_{\tilde{q}}^2) + (1-\delta_{ij})???
-\nonumber\\
-\sum|\mathcal{M}^B|^2(gg \to \tilde{q}\tilde{q}^\dagger) &= 4 n_f g_s^4 \left[ 24\left(1-2\frac{(t_{\tilde{q}}u_{\tilde{q}})}{s^2}\right)-\frac{8}{3} \right] \left[ 1-\epsilon-2\frac{s m_{\tilde{q}}^2}{t_{\tilde{q}}u_{\tilde{q}}} \left( 1-\frac{s m_{\tilde{q}}^2}{t_{\tilde{q}}u_{\tilde{q}}} \right)\right]?\nonumber\\
-\sum|\mathcal{M}^B|^2(q_i\overline{q}_j \to \tilde{g}\tilde{g}) &= \delta_{ij}\left\{ 96 g_s^4 \left[ \frac{2m_{\tilde{g}}^2 s + t_{\tilde{g}}^2 + u_{\tilde{g}}^2}{s^2} -\epsilon \right]\right.\nonumber\\
-&\ 96 g_s^2 \hat{g}_s^2\left[ \frac{m_{\tilde{g}}^2 s + t_{\tilde{g}}^2}{s t_{\tilde{q}}} + \frac{m_{\tilde{g}}^2 s + u_{\tilde{g}}^2}{su_{\tilde{q}}} + \epsilon\left( \frac{t_{\tilde{g}}}{t_{\tilde{q}}} + \frac{u_{\tilde{g}}}{u_{\tilde{q}}} \right) \right]\nonumber\\
-&\ + \left.2\hat{g}_s^4\left[ 24\left( \frac{t_{\tilde{g}}^2}{t_{\tilde{q}}^2} + \frac{u_{\tilde{g}}^2}{u_{\tilde{q}}^2} \right) + \frac{8}{3}\left( 2\frac{m_{\tilde{g}}^2 s}{t_{\tilde{q}}u_{\tilde{q}}} - \frac{t_{\tilde{g}}^2}{t_{\tilde{q}}^2} - \frac{u_{\tilde{g}}^2}{u_{\tilde{q}}^2} \right) \right]\right\} ???
-\nonumber\\
-\sum|\mathcal{M}^B|^2(gg \to \tilde{g}\tilde{g}) &=  576 g_s^4 \left( 1- \frac{t_{\tilde{g}}u_{\tilde{g}}}{s^2} \right)\left[ \frac{s^2}{t_{\tilde{g}}u_{\tilde{g}}}(1-\epsilon)^2-2(1-\epsilon) + s\frac{m_{\tilde{g}}^2 s}{t_{\tilde{g}}u_{\tilde{g}}}\left(1-\frac{m_{\tilde{g}}^2 s}{t_{\tilde{g}}u_{\tilde{g}}}  \right) \right] ???
-\nonumber\\
-\sum|\mathcal{M}^B|^2(qg \to \tilde{q}\tilde{g}) &=  2g_s^2\hat{g}_s^2 \left[ 24\left(1-2\frac{s u_{\tilde{q}}}{t_{\tilde{g}}^2}\right) - \frac{8}{3} \right]\left[ (-1+\epsilon)\frac{t_{\tilde{g}}}{s} + \frac{2(m_{\tilde{g}}^2-m_{\tilde{q}}^2)t_{\tilde{g}}}{s u_{\tilde{q}}}\left( 1+\frac{m_{\tilde{q}}^2}{u_{\tilde{q}}} + \frac{m_{\tilde{g}}^2}{t_{\tilde{g}}} \right) \right]???
+\sum|\mathcal{M}^B|^2(q_i\overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij}  \left[ 8 N_c C(F) g_s^4\frac{(n_f-1)}{s^2} + 4 N_c C(F) \hat{g}_s^4\frac{1}{t_{\tilde{g}}^2} - 8 C(F)g_s^2\hat{g}_s^2\frac{1}{ t_{\tilde{g}} s} \right] (tu-m_{\tilde{q}}^4)\nonumber\\
+ &+ (1-\delta_{ij}) 4 N_c C(F) \hat{g}_s^4\frac{tu-m_{\tilde{q}}^4}{t_{\tilde{g}}^2} \\
+\sum|\mathcal{M}^B|^2(GG \to \tilde{q}\tilde{q}^\dagger) &= 4 (n_f-1) g_s^4 \left[ 2N_c^2C(F) \left(1 - 2\frac{t_{\tilde{q}}u_{\tilde{q}}}{s^2} \right)- 2C(F) \right]\nonumber\\
+& \left[ 1 - \epsilon - 2\frac{s m_{\tilde{q}}^2}{t_{\tilde{q}}u_{\tilde{q}}} \left( 1-\frac{s m_{\tilde{q}}^2}{t_{\tilde{q}}u_{\tilde{q}}} \right)\right]\\
+\sum|\mathcal{M}^B|^2(q_i q_j \to \tilde{q}\tilde{q}) &= \delta_{ij} 2\hat{g}_s^4 N_c C(F)\left[ \frac{1}{t_{\tilde{g}}^2} + \frac{1}{u_{\tilde{g}}^2} \right] (tu-m_{\tilde{q}}^4)\nonumber\\ 
+& + (1-\delta_{ij}) 4 \hat{g}_s^4 N_c C(F) \frac{tu-m_{\tilde{q}}^4}{t_{\tilde{g}}^2}\\
+\sum|\mathcal{M}^B|^2(q\overline{q} \to \tilde{g}\overline{\tilde{g}}) &=  8 N_c^2 C(F) g_s^4 \left[ \frac{2m_{\tilde{g}}^2 s + t_{\tilde{g}}^2 + u_{\tilde{g}}^2}{s^2} -\epsilon \right]\nonumber\\
+& + 4 N_c^2 C(F) g_s^2 \hat{g}_s^2 \left[ \frac{m_{\tilde{g}}^2 s + t_{\tilde{g}}^2}{s t_{\tilde{q}}} + \frac{m_{\tilde{g}}^2 s + u_{\tilde{g}}^2}{su_{\tilde{q}}} + \epsilon\left( \frac{t_{\tilde{g}}}{t_{\tilde{q}}} + \frac{u_{\tilde{g}}}{u_{\tilde{q}}} \right) \right]\nonumber\\
+& + 2C(F)(N_c^2-1) \hat{g}^4_s \left( \frac{t_{\tilde{g}}^2}{t_{\tilde{q}}^2} + \frac{u_{\tilde{g}}^2}{u_{\tilde{q}}^2} \right)\\
+%& + 2 \hat{g}_s^4\left[ 2 N_c^2 C(F) \left( \frac{t_{\tilde{g}}^2}{t_{\tilde{q}}^2} + \frac{u_{\tilde{g}}^2}{u_{\tilde{q}}^2} \right) + 2 C(F) \left( 2\frac{m_{\tilde{g}}^2 s}{t_{\tilde{q}}u_{\tilde{q}}} - \frac{t_{\tilde{g}}^2}{t_{\tilde{q}}^2} - \frac{u_{\tilde{g}}^2}{u_{\tilde{q}}^2} \right) \right]\\
+\sum|\mathcal{M}^B|^2(GG \to \tilde{g}\overline{\tilde{g}}) &=  16 N_c^3 C(F) g_s^4 \left( 1- \frac{t_{\tilde{g}}u_{\tilde{g}}}{s^2} \right)\nonumber\\
+&\left[ \frac{s^2}{t_{\tilde{g}}u_{\tilde{g}}}(1-\epsilon)^2-2(1-\epsilon) + 4\frac{m_{\tilde{g}}^2 s}{t_{\tilde{g}}u_{\tilde{g}}}\left(1-\frac{m_{\tilde{g}}^2 s}{t_{\tilde{g}}u_{\tilde{g}}}  \right) \right]\\
+\sum|\mathcal{M}^B|^2(qg \to \tilde{q}\tilde{g}) &=  2g_s^2\hat{g}_s^2 \left[ 2 N_c^2 C(F) \left(1-2\frac{s u_{\tilde{q}}}{t_{\tilde{g}}^2}\right) - 2C(F) \right] \nonumber\\
+&\left[ (-1+\epsilon)\frac{t_{\tilde{g}}}{s} + \frac{2(m_{\tilde{g}}^2-m_{\tilde{q}}^2)t_{\tilde{g}}}{s u_{\tilde{q}}}\left( 1+\frac{m_{\tilde{q}}^2}{u_{\tilde{q}}} + \frac{m_{\tilde{g}}^2}{t_{\tilde{g}}} \right) \right]
 \end{align}
@@
 \begin{align}
-\frac{\mbox{d}^2 \sigma}{\mbox{d}t\mbox{d}u} = \frac{K_{ij}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_{\tilde{q}}^4}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_{\tilde{q}}^4) \Theta(s-4m_{\tilde{q}}^2) \delta(s+t+u-2m_{\tilde{q}}^2) \sum |\mathcal{M}^B|^2
+\frac{\mbox{d}^2 \sigma}{\mbox{d}t\mbox{d}u} &= \frac{K_{ij}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_{\tilde{q}}^4}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_{\tilde{q}}^4)\nonumber\\ &\ \Theta(s-4m_{\tilde{q}}^2) \delta(s+t+u-2m_{\tilde{q}}^2) \sum |\mathcal{M}^B|^2
 \end{align}
-with $S_\epsilon = (2\pi)2-2\epsilon$???
+with $S_\epsilon = (4\pi)^{-2+\epsilon}$. The leading order cross sections are
 \begin{align}
-\sigma(gg \to \tilde{q}\tilde{q}^\dagger) = \frac{n_f g_s^4}{16\pi s} \left[ \left(\frac{5}{24} + \frac{31 m_{\tilde{q}}^2}{12s}\right)\beta_{\tilde{q}} + \left( \frac{m_{\tilde{q}}^4}{3s^2} + \frac{4m_{\tilde{q}}^2}{s}\right) \ln \frac{1-\beta_{\tilde{q}}}{1+\beta_{\tilde{q}}} \right]
+\sigma(q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij}  \frac{g_s^4}{16\pi s} (n_f-1) \left[ \frac{4}{27} - \frac{16 m_{\tilde{q}}^2}{27s} \right]\nonumber\\
+&+ \delta_{ij} \frac{g_s^2\hat{g}_s^2}{16\pi s}  \left[ \left( \frac{4}{27} + \frac{8 m_-^2}{27 s} \right)\beta_{\tilde{q}}  + \left( \frac{8m_{\tilde{g}}^2}{27s} + \frac{8m_-^4}{27s^2} \right)L_1 \right]\nonumber\\
+& + \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} + \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
+\sigma(GG \to \tilde{q}\tilde{q}^\dagger) &= \frac{(n_f-1) g_s^4}{16\pi s} \left[ \left(\frac{5}{24} + \frac{31 m_{\tilde{q}}^2}{12s}\right)\beta_{\tilde{q}} + \left( \frac{4m_{\tilde{q}}^2}{3s} + \frac{m_{\tilde{q}}^4}{3s^2} \right) \ln \frac{1-\beta_{\tilde{q}}}{1+\beta_{\tilde{q}}} \right]\\
+\sigma(q_i q_j \to \tilde{q}\tilde{q}) &= \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} +  \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
+\sigma(q \overline{q} \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \frac{16}{9} + \frac{32m_{\tilde{g}}^2}{9s} \right] \beta_{\tilde{g}}\nonumber\\
+& + \frac{\hat{g}_s^2 g_s^2}{16\pi s}  \left[ \left( -\frac{4}{3}-\frac{8m_-^2}{3s} \right)\beta_{\tilde{g}} + \left( \frac{8 m_{\tilde{g}}^2}{3s} + \frac{8m_-^4}{3s^2} \right) L_2 \right]\nonumber\\
+& + \frac{\hat{g}_s^4}{16\pi s} \left[ \left( \frac{32}{27} + \frac{32 m_-^4}{m_-^4 + m_{\tilde{q}}^2s} \right)\beta_{\tilde{g}} - \frac{64m_-^2}{27s}L_2 \right]\label{eq:qqbar_to_sgsgbar}\\
+\sigma(GG \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \left( -6 - \frac{51 m_{\tilde{g}}^2}{2s} \right)\beta_{\tilde{g}} + \left( -\frac{9}{2} - \frac{18 m_{\tilde{g}}^2}{s} + \frac{18 m_{\tilde{g}}^4}{s^2} \right)\ln \frac{1-\beta_{\tilde{g}}}{1+\beta_{\tilde{g}}} \right]\\
+\sigma(q G \to \tilde{q} \tilde{g}) &= \frac{g_s^2\hat{g}_s^2}{16\pi s} \left[ \frac{\kappa}{s}\left( -\frac{7}{9} - \frac{32 m_{-}^2}{9s} \right) + \left( -\frac{8m_-^2}{9s} + \frac{2m_{\tilde{q}}^2m_-^2}{s^2} + \frac{8 m_-^4}{9s^2} \right)L_3\right.\nonumber\\
+&+\left. \left( -1-\frac{2m_-^2}{s} + \frac{2m_{\tilde{q}}m_-^2}{s^2} \right)L_4 \right]
 \end{align}
@@
 \begin{align}
-\beta_{\tilde{q}} = \sqrt{1-\frac{4 m_{\tilde{q}}^2}{s}}
+&\beta_{\tilde{q}} = \sqrt{1-\frac{4 m_{\tilde{q}}^2}{s}} && \beta_{\tilde{g}} = \sqrt{1-\frac{4 m_{\tilde{g}}^2}{s}}\nonumber\\
+&m_-^2 = m_{\tilde{g}}^2 - m_{\tilde{q}}^2 && \kappa = \sqrt{(s-m_{\tilde{g}}^2-m_{\tilde{q}}^2)^2-4m_{\tilde{g}}^2m_{\tilde{q}}^2}\nonumber\\
+& L_1 = \ln \frac{s+2m_-^2 - s\beta_{\tilde{q}}}{s+2m_-^2 + s\beta_{\tilde{q}}} && L_2= \ln \frac{s - 2m_-^2 - s\beta_{\tilde{g}}}{s - 2m_-^2 + s\beta_{\tilde{g}}}\nonumber\\
+& L_3 = \ln \frac{s - m_-^2 - \kappa}{s - m_-^2 + \kappa} && L_4= \ln \frac{s + m_-^2 - \kappa}{s + m_-^2 + \kappa}
 \end{align}
-are used.\cite{Beenakker}
+are used\cite{Beenakker:1996ch}.
+In contrast to the MSSM no statistical factor $\frac{1}{2}$ is taken into account for gluino-antigluino production, as these particles are distinguishable in the MRSSM.
+Still in comparison to the MSSM cross section for the channel $q \overline{q} \to \tilde{g}\overline{\tilde{g}}$ only the first line in \ref{eq:qqbar_to_sgsgbar} is doubled up as the part associated with an $t$ ($u$) channel squark is different.
+In the MRSSM either $\tilde{q}_L$ or $\tilde{q}_R$ is allowed whilst in the MSSM both squarks contribute to the $t$ ($u$) channel diagram.
 

### 2016-03-04 Appendix.tex
Tree level Feynman diagrams

@@
 
+\newpage
 \subsection{Passarino-Veltman Integrals}
@@
 
-%\subsection{Cross section and Phase Space Integration}
-%\begin{align}
-%\mbox{d}\sigma = \frac{1}{2E_A 2E_B |v_A-v_B|}\left( \prod_f \frac{\mbox{d}^3p_f}{(2\pi)^3}\frac{1}{2E_f} \right) \sum |\mathcal{M}(p_A,p_B \to \left\{p_f\right\})|^2 (2\pi)^4 \delta^{(4)}(p_a+p_b-\sum p_f)
-%\end{align}
-%...\\
-%\begin{align}
-%\frac{\mbox{d}^2 \sigma}{\mbox{d}t\mbox{d}u} = \frac{K_{ij}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_{\tilde{q}}^4}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_{\tilde{q}}^4) \Theta(s-4m_{\tilde{q}}^2) \delta(s+t+u-2m_{\tilde{q}}^2) \sum |\mathcal{M}^B|^2
-%\end{align}
+\subsection{Cross section and Phase Space Integration}
+Once the Feynman amplitude $\mathcal{M}$ for a $2 \to N$ body scattering\footnote{with kinematics $k_a + k_b \to p_1 + \hdots p_N$} is computed one can calculate physical observables with it.
+The differential cross section for $2 \to N$ scattering is given by
+\begin{align}
+\mbox{d}\sigma = \frac{1}{F}\mathrm{d}\Phi_N |\mathcal{M}|^2.
+\end{align}
+The flux factor is defined by $F = 4\sqrt{(k_a\cdot k_b)^2 - (m_am_b)^2}$ which equals $F = 2s$ for massless initial state particles.
+The differential for the $N$ body phase space in $D$ dimensions is given by
+\begin{align}
+\mathrm{d}\Phi_N = \left( \mu^{2\epsilon} \right)^{N-1} \left( \prod_{f=1}^N \frac{\mbox{d}^{D-1}p_f}{(2\pi)^{D-1}}\frac{1}{2E_f} \right)  (2\pi)^D \delta^{(D)}(k_a+k_b-\sum_{f=1}^N p_f).
+\end{align} 
+The factor $\mu^{2\epsilon}$ is included to maintain the mass dimension of the cross section.
+In this thesis the sum of $|\mathcal{M}|^2$ over helicities and colors $\sum |\mathcal{M}|^2$ has been calculated.
+Furthermore initial state particles are considered as massless.
+This gives
+\begin{align}
+\mathrm{d}\sigma = \frac{1}{2s} \mathrm{d}\Phi_2 K_{ab} \sum |\mathcal{M}|^2
+\end{align} 
+where $K_{ab}$ encodes the averaging over initial state helicities and colors.
+Specifying to the center-of-mass frame and assuming that $\sum|\mathcal{M}|^2$ is only a function of the modulus of one of the final state particle's 3-momentum $ |\vec{p}_i|$ and the angle $\theta$ between $\vec{k}_a$ and $\vec{p}_1$ one can write
+\begin{align}
+\int \mathrm{d}\Phi_2 &= \frac{1}{s} \mu^{2\epsilon} \int \frac{\mathrm{d}|\vec{p}_1|\mathrm{d}\Omega^{D-1}_1}{(2\pi)^{D-2}} |\vec{p}_1|^{D-2} \delta \left(k_a^0 + k_b^0 - \sqrt{m_1^2 + |\vec{p}_1|^2} - \sqrt{m_2^2 + |\vec{p}_2|^2} \right)\nonumber\\
+&= \frac{1}{s} \frac{1}{(2\pi)^{D-2}}\frac{2\pi^{\frac{D}{2}-1}}{\Gamma(\frac{D}{2}-1)} \mu^{2\epsilon} \int_0^\infty\mathrm{d}|\vec{p}_1| \int_0^\pi \mathrm{d} \cos\theta p_1^{D-2}\sin^{D-4}\theta\nonumber\\
+&\ \ \delta \left(k_a^0 + k_b^0 - \sqrt{m_1^2 + |\vec{p}_1|^2} - \sqrt{m_2^2 + |\vec{p}_2|^2} \right).\label{eq:DPhi2}
+\end{align}
+In the second line the integral over the D-dimensional hypersphere 
+\begin{align}
+\int \mathrm{d}\Omega^D = \int_0^{2\pi} \mathrm{d}\phi \prod_{i=1}^{D-2}\int_0^\pi \sin^i\theta_i \mathrm{d}\theta_i = \frac{2\pi^{\frac{D}{2}}}{\Gamma(\frac{D}{2})}
+\end{align}
+was used. Because $\sum|\mathcal{M}|^2$ is calculated in terms of Mandelstam variables 
+\begin{align}
+t &= (k_a-p_1)^2  \nonumber\\
+t &= -2\left(|\vec{k}_a| \sqrt{m_1^2 + |\vec{p}_1|^2} - |\vec{k}_a||\vec{p}_1| \cos\theta\right) + m_1^2\label{eq:t} \\
+u &= (k_b-p_1)^2\nonumber\\
+u &= -2\left(|\vec{k}_a| \sqrt{m_1^2 + |\vec{p}_1|^2} + |\vec{k}_b||\vec{p}_1| \cos\theta\right) + m_1^2\label{eq:u}
+\end{align}
+it is useful to perform a change of coordinates yielding
+\begin{align}
+\mathrm{d}|\vec{p}_1|\ \mathrm{d}\cos\theta = -\frac{\sqrt{m_1^2+|\vec{p}_1|^2}}{8|\vec{k}_a|^2|\vec{p}_1|^2}\mathrm{d}u\ \mathrm{d}t.\label{eq:PhaseTrafo}
+\end{align}
+Inserting \ref{eq:PhaseTrafo} into \ref{eq:DPhi2} and using $|\vec{k}_a| = \frac{\sqrt{s}}{2}$ gives
+\begin{align}
+\int \mathrm{d}\Phi_2 = & \frac{1}{s} \frac{\pi^{-\frac{D}{2}+1}}{2^{D-3}\Gamma(\frac{D}{2}-1)} \int \mathrm{d}u\ \mathrm{d}t\ \left( \frac{tu-m_1^2m_2^2}{\mu^{2\epsilon} s} \right)^{\frac{D-4}{2}} \nonumber\\
+&\frac{1}{4}\Theta(tu-4m_1^2m_2^2)\delta \left(s+t+u-m_1^2-m_2^2\right)
+\end{align}
+where the $\Theta$-function comes from the bounds of $|\vec{p}_1|$ and $\theta$ visible in \ref{eq:DPhi2} and the combination of \ref{eq:t} and \ref{eq:u}.
+Working in $D=4-2\epsilon$ dimensions and inserting $\Theta(s-4m^2)$ with $m = \frac{m_1 + m_2}{2}$ to account for the production threshold one finds
+\begin{align}
+\frac{\mbox{d}^2 \sigma}{\mbox{d}t\mbox{d}u} =& \frac{K_{ab}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_1^2m_2^2}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_1^2m_2^2)\nonumber\\
+&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum |\mathcal{M}|^2
+\end{align}
+where $S_\epsilon = (4\pi)^{-2+\epsilon}$ as defined in \cite{Beenakker:1996ch}.
+The averaging factors $K_{ab}$ are given by
+\begin{align}
+K_{qq} = \frac{1}{4N_c^2} \hspace{1.5cm}K_{GG} = \frac{1}{4(1-\epsilon)^2(N_c^2-1)^2} \hspace{1.5cm}K_{qG} = \frac{1}{4(1-\epsilon)N_c(N_c^2-1)}.
+\end{align}

### 2016-03-04 TreeLevel.tex
Tree level Feynman diagrams

@@
 \subsection{Partonic Processes}
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}[line width=1.0 pt, scale=1.3]
+	\draw[fermion] (-1,0.5)--(-0.42,0);
+	\draw[fermionbar] (-1,-0.5)--(-0.42,0);
+	\draw[gluon] (-0.42,0)--(0.42,0); 
+	\draw[scalar] (0.42,0)--(1,0.5);
+	\draw[scalarbar] (0.42,0)--(1,-0.5);
+\begin{scope}[shift={(3,0)}]
+	\draw[fermion] (-1,0.5)--(0,0.5);
+	\draw[fermionbar] (-1,-0.5)--(0,-0.5);
+	\draw[fermionnoarrow] (0,0.5)--(0,-0.5);
+	\draw[gluon] (0,0.5)--(0,-0.5); 
+	\draw[scalar] (0,0.5)--(1,0.5);
+	\draw[scalarbar] (0,-0.5)--(1,-0.5);
+\end{scope}
+\end{tikzpicture}
+\caption{Tree level diagrams for $q\overline{q} \to \tilde{q}\tilde{q}^\dagger$}
+\end{center}
+\end{figure}
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}[line width=1.0 pt, scale=1.3]
+	\draw[gluon] (-1,0.5)--(-0.42,0);
+	\draw[gluon] (-1,-0.5)--(-0.42,0);
+	\draw[gluon] (-0.42,0)--(0.42,0); 
+	\draw[scalar] (0.42,0)--(1,0.5);
+	\draw[scalarbar] (0.42,0)--(1,-0.5);
+\begin{scope}[shift={(3,0)}]
+	\draw[gluon] (-1,0.5)--(0,0.5);
+	\draw[gluon] (-1,-0.5)--(0,-0.5);
+	\draw[scalarbar] (0,0.5)--(0,-0.5);
+	\draw[scalar] (0,0.5)--(1,0.5);
+	\draw[scalarbar] (0,-0.5)--(1,-0.5);
+\end{scope}
+\begin{scope}[shift={(6,0)}]
+	\draw[gluon] (-1,0.5)--(0,0.5);
+	\draw[gluon] (-1,-0.5)--(0,-0.5);
+	\draw[scalar] (0,0.5)--(0,-0.5);
+	\draw[scalarnoarrow] (0,0.5)--(0.4,0.1);
+	\draw[scalarbar] (0.6,-0.1)--(1,-0.5);
+	\draw[scalarnoarrow] (0,-0.5)--(0.5,0);
+	\draw[scalar] (0.5,0)--(1,0.5);
+\end{scope}
+\begin{scope}[shift={(9,0)}]
+	\draw[gluon] (-1,0.5)--(0,0);
+	\draw[gluon] (-1,-0.5)--(0,0);
+	\draw[scalarbar] (0,0)--(1,-0.5);
+	\draw[scalar] (0,0)--(1,0.5);
+\end{scope}
+\end{tikzpicture}
+\caption{Tree level diagrams for $GG \to \tilde{q}\tilde{q}^\dagger$}
+\end{center}
+\end{figure}
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}[line width=1.0 pt, scale=1.3]
+	\draw[fermion] (-1,0.5)--(0,0.5);
+	\draw[fermion] (-1,-0.5)--(0,-0.5);
+	\draw[gluon] (0,0.5)--(0,-0.5);
+	\draw[fermionnoarrow] (0,0.5)--(0,-0.5);
+	\draw[scalar] (0,0.5)--(1,0.5);
+	\draw[scalar] (0,-0.5)--(1,-0.5);;
+\begin{scope}[shift={(3,0)}]
+	\draw[fermion] (-1,0.5)--(0,0.5);
+	\draw[fermion] (-1,-0.5)--(0,-0.5);
+	\draw[gluon] (0,0.5)--(0,-0.5);
+	\draw[fermionnoarrow] (0,0.5)--(0,-0.5);
+	\draw[scalarnoarrow] (0,0.5)--(0.4,0.1);
+	\draw[scalar] (0.6,-0.1)--(1,-0.5);
+	\draw[scalarnoarrow] (0,-0.5)--(0.5,0);
+	\draw[scalar] (0.5,0)--(1,0.5);
+\end{scope}
+\end{tikzpicture}
+\caption{Tree level diagrams for $qq \to \tilde{q}\tilde{q}$}
+\end{center}
+\end{figure}
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}[line width=1.0 pt, scale=1.3]
+	\draw[fermion] (-1,0.5)--(-0.42,0);
+	\draw[fermionbar] (-1,-0.5)--(-0.42,0);
+	\draw[gluon] (-0.42,0)--(0.42,0); 
+	\draw[gluon] (0.42,0)--(1,0.5);
+	\draw[fermionnoarrow] (0.42,0)--(1,0.5);
+	\draw[gluon] (0.42,0)--(1,-0.5);
+	\draw[fermionnoarrow] (0.42,0)--(1,-0.5);
+\begin{scope}[shift={(3,0)}]
+	\draw[fermion] (-1,0.5)--(0,0.5);
+	\draw[fermionbar] (-1,-0.5)--(0,-0.5);
+	\draw[scalar] (0,0.5)--(0,-0.5);
+	\draw[gluon] (0,0.5)--(1,0.5);
+	\draw[fermionnoarrow] (0,0.5)--(1,0.5);
+	\draw[gluon] (0,-0.5)--(1,-0.5);
+	\draw[fermionnoarrow] (0,-0.5)--(1,-0.5);
+\end{scope}
+\begin{scope}[shift={(6,0)}]
+	\draw[fermion] (-1,0.5)--(0,0.5);
+	\draw[fermionbar] (-1,-0.5)--(0,-0.5);
+	\draw[scalar] (0,0.5)--(0,-0.5);
+	\draw[gluon] (0,0.5)--(0.4,0.1);
+	\draw[fermionnoarrow] (0,0.5)--(0.4,0.1);
+	\draw[gluon] (0.6,-0.1)--(1,-0.5);
+	\draw[fermionnoarrow] (0.6,-0.1)--(1,-0.5);
+	\draw[gluon] (0,-0.5)--(1,0.5);
+	\draw[fermionnoarrow] (0,-0.5)--(1,0.5);
+\end{scope}
+\end{tikzpicture}
+\caption{Tree level diagrams for $q\overline{q} \to \tilde{g}\overline{\tilde{g}}$}
+\end{center}
+\end{figure}
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}[line width=1.0 pt, scale=1.3]
+	\draw[gluon] (-1,0.5)--(-0.42,0);
+	\draw[gluon] (-1,-0.5)--(-0.42,0);
+	\draw[gluon] (-0.42,0)--(0.42,0); 
+	\draw[gluon] (0.42,0)--(1,0.5);
+	\draw[fermionnoarrow] (0.42,0)--(1,0.5);
+	\draw[gluon] (0.42,0)--(1,-0.5);
+	\draw[fermionnoarrow] (0.42,0)--(1,-0.5);
+\begin{scope}[shift={(3,0)}]
+	\draw[gluon] (-1,0.5)--(0,0.5);
+	\draw[gluon] (-1,-0.5)--(0,-0.5);
+	\draw[gluon] (0,0.5)--(0,-0.5);	
+	\draw[fermionnoarrow] (0,0.5)--(0,-0.5);
+	\draw[gluon] (0,0.5)--(1,0.5);
+	\draw[fermionnoarrow] (0,0.5)--(1,0.5);
+	\draw[gluon] (0,-0.5)--(1,-0.5);
+	\draw[fermionnoarrow] (0,-0.5)--(1,-0.5);
+\end{scope}
+\begin{scope}[shift={(6,0)}]
+	\draw[gluon] (-1,0.5)--(0,0.5);
+	\draw[gluon] (-1,-0.5)--(0,-0.5);
+	\draw[gluon] (0,0.5)--(0,-0.5);
+	\draw[fermionnoarrow] (0,0.5)--(0,-0.5);
+	\draw[gluon] (0,0.5)--(0.4,0.1);
+	\draw[fermionnoarrow] (0,0.5)--(0.4,0.1);
+	\draw[gluon] (0.6,-0.1)--(1,-0.5);
+	\draw[fermionnoarrow] (0.6,-0.1)--(1,-0.5);
+	\draw[gluon] (0,-0.5)--(1,0.5);
+	\draw[fermionnoarrow] (0,-0.5)--(1,0.5);
+\end{scope}
+\end{tikzpicture}
+\caption{Tree level diagrams for $GG \to \tilde{g}\overline{\tilde{g}}$}
+\end{center}
+\end{figure}
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}[line width=1.0 pt, scale=1.3]
+	\draw[fermion] (-1,0.5)--(-0.42,0);
+	\draw[gluon] (-1,-0.5)--(-0.42,0);
+	\draw[fermion] (-0.42,0)--(0.42,0); 
+	\draw[scalar] (0.42,0)--(1,0.5);
+	\draw[gluon] (0.42,0)--(1,-0.5);
+	\draw[fermionnoarrow] (0.42,0)--(1,-0.5);
+\begin{scope}[shift={(3,0)}]
+	\draw[fermion] (-1,0.5)--(0,0.5);
+	\draw[gluon] (-1,-0.5)--(0,-0.5);
+	\draw[gluon] (0,0.5)--(0,-0.5);	
+	\draw[fermionnoarrow] (0,0.5)--(0,-0.5);
+	\draw[scalar] (0,0.5)--(1,0.5);
+	\draw[gluon] (0,-0.5)--(1,-0.5);
+	\draw[fermionnoarrow] (0,-0.5)--(1,-0.5);
+\end{scope}
+\begin{scope}[shift={(6,0)}]
+	\draw[fermion] (-1,0.5)--(0,0.5);
+	\draw[gluon] (-1,-0.5)--(0,-0.5);
+	\draw[gluon] (0,0.5)--(0,-0.5);
+	\draw[fermionnoarrow] (0,0.5)--(0,-0.5);
+	\draw[gluon] (0,0.5)--(0.4,0.1);
+	\draw[fermionnoarrow] (0,0.5)--(0.4,0.1);
+	\draw[gluon] (0.6,-0.1)--(1,-0.5);
+	\draw[fermionnoarrow] (0.6,-0.1)--(1,-0.5);
+	\draw[gluon] (0.6,-0.1)--(1,-0.5);
+	\draw[fermionnoarrow] (0.6,-0.1)--(1,-0.5);
+	\draw[scalarnoarrow] (0,-0.5)--(0.5,0);
+	\draw[scalar] (0.5,0)--(1,0.5);
+\end{scope}
+\end{tikzpicture}
+\caption{Tree level diagrams for $qG \to \tilde{q}\tilde{g}$}
+\end{center}
+\end{figure}
 The top quark is excluded from the initial states as it is too heavy to be significantly present in hadrons.
@@
 \subsection{Partonic Cross Sections}
-\begin{align}
-\frac{\mbox{d}^2 \sigma}{\mbox{d}t\mbox{d}u} &= \frac{K_{ij}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_{\tilde{q}}^4}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_{\tilde{q}}^4)\nonumber\\ &\ \Theta(s-4m_{\tilde{q}}^2) \delta(s+t+u-2m_{\tilde{q}}^2) \sum |\mathcal{M}^B|^2
-\end{align}
-with $S_\epsilon = (4\pi)^{-2+\epsilon}$. The leading order cross sections are
+The leading order cross sections are
 \begin{align}

### 2016-03-09 Standardmodel.tex
remark about Wilson loop (still undone)

@@
 In comparison to the Dirac-Lagrangian \ref{eq:DiracLagrangian} the partial derivative is replaced with the gauge covariant derivative $D^\mu = \partial^\mu + igT^aG^{a\mu}$ and the gauge invariant kinetic term for the gauge fields is added.
-This comprises the field strenth-tensor $F^{a\mu\nu}$ which is in its matrix valued form defined by $F^{\mu\nu} = F^{a\mu\nu}T^a = \frac{1}{ig}[D^\mu,D^\nu]$.\\
+This comprises the field strenth-tensor $F^{a\mu\nu}$ which is in its matrix valued form defined by $F^{\mu\nu} = F^{a\mu\nu}T^a = \frac{1}{ig}[D^\mu,D^\nu]$.
+In fact one has little choice for kinetic terms of the gauge fields for thy must be gauge invariant and therefore be functions of the Wilson loop \cite{Peskin}...\\
 The gauge group of the SM is a direct product ???
@@
 The hyper charge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to.
-These can be taken from table \ref{tab:SMfieldcontent}.
+These can be found in table \ref{tab:SMfieldcontent}.
 The kinetic terms of the gauge fields are given by

### 2016-04-24 Introduction.tex
Passarino-Veltman integrals and other changes

motivation: aesthetic: Coleman-Mandula --> Haag-Lopuszanski-Sohnius-Theorem\\
plots for exclusion of squarks in specific SUSY scenarios (from Michael) --> R-Symmetry could be possible explanation for that because:\\
MSSM-Lagrangian --> trafo rules for superfields under R-symm --> forbidden terms in MRSSM (write down Lagrangian for R-symmetric SUSYQCD)\\
suppression of squark production in MRSSM by less diagrams ($m_{gluino}^{-4}$ suppression at low energies in MRSSM and only $m_{gluino}^{-2}$ suppression in MSSM)\\
R-charges of all fields (show in diagram!) --> only if R-charges of final / initial particles are zero, a diagram is allowed in R-symm. model\\
references to build in
\begin{itemize}
\item "Matching Squark Pair Production at NLO with Parton Showers" from Gavin, Hangst, Krämer, Mühlleitner,.. for complete treatment of NLO calculation\\
\item "dIRAC gAUGINOS IN susy - sUPPRESSED jETS + <met sIGNALS: a sNOWMASS wHITEPAPER" FROM kRIBS, mARTIN for Squark production at LO, allude to same result\\
\item "Dirac Gaugino Masses and supersoft SUSY breaking" from Fox, Weiner, Nelson for the introduction of the MRSSM
\end{itemize}

### 2016-04-24 Appendix.tex
Passarino...

@@
 
-\subsection{Colour Algebra $SU(N)$}
+\subsection{Constants of the Colour Algebra $SU(N)$}
 [Marina von Steinkirch]\\
@@
 f^{abc} f^{dbc} &= C(A)\delta^{ad} && \mbox{with}\ C(A) = N = 3\nonumber\\
-\mathrm{Tr}\left[T^aT^b\right] &= T(F)\delta^{ab} && \mbox{with}\ T(F) = \frac{1}{2}
+\mathrm{Tr}\left[T^aT^b\right] &= T(F)\delta^{ab} && \mbox{with}\ T(F) = \frac{1}{2}\label{eq:DynkinIndex}
 \end{align}
@@
 küblbeck]
-\begin{figure}[!htbp]
+\begin{figure}[H]
 \begin{center}
@@
 \end{figure}
-\begin{figure}
+\begin{figure}[H]
 \begin{center}
@@
 
-\newpage
-\subsection{Passarino-Veltman Integrals}
-
+\subsection{Passarino-Veltman Integrals}\label{sec:Passarino}
+The definition of the Passarino-Veltman integrals in this thesis agrees with the one from \texttt{Looptools} \cite{Hahn:1998} convention.
+The original paper \cite{Passarino:1978jh} uses slightly different conventions.
+A pedagogical introduction to the evaluation of one-loop integrals can be found in \cite{Ellis:2011cr}
 \begin{align}
-A_0(m^2) &= \frac{i}{16\pi^2} \int_l \frac{1}{l^2-m^2}\nonumber\\
-B_{0,\mu,\mu\nu}(p^2,m_1^2,m_2^2) &= \frac{i}{16\pi^2} \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p)^2-m_2^2]}\nonumber\\
-C_{0,\mu,\mu\nu}(p_1^2,p_2^2,m_1^2,m_2^2,m_3^2) &= \frac{i}{16\pi^2} \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p_1)^2-m_2^2][(l+p_2)^2-m_3^2]}
+\frac{i}{16\pi^2} A_0(m^2) &= \int_l \frac{1}{l^2-m^2}\nonumber\\
+\frac{i}{16\pi^2} B_{0,\mu,\mu\nu}(p^2,m_1^2,m_2^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p)^2-m_2^2]}\\
+\frac{i}{16\pi^2} C_{0,\mu,\mu\nu}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p_1)^2-m_2^2][(l+p_1+p_2)^2-m_3^2]}\nonumber
 \end{align}
@@
 \begin{align}
-B_\mu &= p_\mu B_1\nonumber\\
-B_{\mu\nu} &= g_{\mu\nu}B_{00} + p_\mu p_\nu B_{11}\nonumber\\
-C_\mu &= p_{1\mu}C_1 + p_{2\mu}C_2 \nonumber\\
-C_{\mu\nu} &= g_{\mu\nu}C_{00} + p_{1\mu}p_{1\nu}C_{11} + p_{2\mu}p_{2\nu}C_{22} + (p_{1\mu}p_{2\nu} + p_{2\mu}p_{1\nu})C_{12} 
+B_\mu &:= p_\mu B_1\nonumber\\
+B_{\mu\nu} &:= g_{\mu\nu}B_{00} + p_\mu p_\nu B_{11}\nonumber\\
+C_\mu &= p_{1\mu}C_1 + p_{2\mu}C_2\\
+C_{\mu\nu} &:= g_{\mu\nu}C_{00} + p_{1\mu}p_{1\nu}C_{11} + p_{2\mu}p_{2\nu}C_{22} + (p_{1\mu}p_{2\nu} + p_{2\mu}p_{1\nu})C_{12}\nonumber
 \end{align}
+In the the special case of vanishing momenta the integrals take a succinct form. %The following formulae show some of these special cases.
 \begin{align}
-A_0(m^2) = m^2\left( \Delta -\ln \frac{m^2}{\mu^2} + 1 \right) + \mathcal{O}(\epsilon)
+A_0(m^2) = m^2\left( \Delta_\epsilon -\ln \frac{m^2}{\mu^2} + 1 \right) + \mathcal{O}(\epsilon)
 \end{align}
-$\Delta = \frac{1}{\epsilon} - \gamma_E+\ln 4\pi$
+where the typical UV-divergent constant $\Delta_\epsilon = \frac{1}{\epsilon} - \gamma_E+\ln 4\pi$ is defined. It comprises the Euler-Mascheroni constant $\gamma_{\mathrm{E}}$.
 \begin{align}
-B_0(0,m_1^2,m_2^2) &= \frac{A_0(m_1^2)-A_0(m_2^2)}{m_1^2-m_2^2} = \Delta + 1 -\frac{m_1^2\ln \frac{m_1^2}{\mu^2}-m_2^2\frac{m_2^2}{\mu^2}}{m_1^2-m_2^2} + \mathcal{O}(\epsilon)\\
-B_0(0,m^2,m^2) &= \frac{\partial}{\partial m^2} A_0(m^2) = \Delta -\ln \frac{m^2}{\mu^2} + 1 + \mathcal{O}(\epsilon)
+B_0(0,m_1^2,m_2^2) &= \frac{A_0(m_1^2)-A_0(m_2^2)}{m_1^2-m_2^2} = \Delta_\epsilon + 1 -\frac{m_1^2\ln \frac{m_1^2}{\mu^2}-m_2^2\ln \frac{m_2^2}{\mu^2}}{m_1^2-m_2^2} + \mathcal{O}(\epsilon)\\
+B_0(0,m^2,m^2) &= \frac{\partial}{\partial m^2} A_0(m^2) = \Delta_\epsilon -\ln \frac{m^2}{\mu^2} + \mathcal{O}(\epsilon)\\
+B_0(0,0,0) &= 0\\
+B_1(0,m_1^2,m_2^2) &= -\frac{\Delta_\epsilon}{2} + \frac{1}{2}\ln \frac{m_1^2}{\mu^2} + \frac{-3+4t-t^2-4t \ln t +2t^2 \ln t}{4(t-1)^2} + \mathcal{O}(\epsilon)\label{eq:B1}\\
+B_1(0,0,0) &= 0
 \end{align}
+The scaleless integrals are defined to be zero.
+The parameter $t$ is given by $\frac{m_2^2}{m_1^2}$.
+As can be seen from \ref{eq:B1} $B_1$ is in contrast to $B_0$ not symmetric in its masses but it can be shown [Romao] that
+\begin{align}
+B_1(p^2,m_1^2,m_2^2) = -(B_0(p^2,m_2^2,m_1^2) + B_1(p^2,m_2^2,m_1^2))
+\end{align}
+It can further be shown that
+\begin{align}
+C_{00}(0,0,0,m_1^2, m_1^2, m_2^2) = -\frac{1}{2}B_1(0, m_1^2, m_2^2)
+\end{align} and that $C_{00}(0,0,0,m_1^2, m_1^2, m_2^2)$ is a symmetric function of its masses.\\
+From the generic $\epsilon$-expansion of the $B_0$ integral \cite{Denner}
+\begin{align}
+B_0(p^2,m_1^2,m_2^2) = \Delta_\epsilon - \int_0^1\mathrm{d}x\ \ln \frac{-x(1-x)p^2 + xm_2^2 + (1-x)m_1^2}{\mu^2}
+\end{align} 
+and Passarino-Veltman decomposition \cite{Passarino:1978jh} one can determine the UV-divergent part of all $B$ and $C$ integrals.
+In chapter \ref{sec:MSRen} this was necessary in order to obtain the renormalization constants in the $\overline{\mathrm{MS}}$-scheme.
+Infrared and collinear singularities arise from the special case where one or multiple masses tend to zero.
+These poles are either regularized in terms of a small mass cutoff $\Lambda$ or also dimensionally as $\epsilon$-poles.
+In the later case the integral first needs to undergo the limit to zero masses and than being evaluated.\\
+The following list shows all necessary integrals needed to determine the renormalization constants in \ref{sec:MSRen}.
+\begin{align}
+\left.A_0(m^2)\right|_{\mathrm{UV-div}} &= m^2 \Delta_\epsilon\\
+\left.B_0(p^2,m_1^2,m_2^2)\right|_{\mathrm{UV-div}} &= \Delta_\epsilon\\
+\left.B_1(p^2,m_1^2,m_2^2)\right|_{\mathrm{UV-div}} &= -\frac{1}{2}\Delta_\epsilon\\
+\left.C_{00}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2)\right|_{\mathrm{UV-div}} &= \frac{1}{4}\Delta_\epsilon
+\end{align}
+The UV-divergent part of $C_{11}$, $C_{22}$, $C_{12}$ equals zero.
+As can be seen already from the superficial degree of divergence also $C_i|_{\mathrm{UV-div}} = 0$ for $i \in \left\{ 0, 1, 2 \right\}$ .
 
@@
 The factor $\mu^{2\epsilon}$ is included to maintain the mass dimension of the cross section.
-In this thesis the sum of $|\mathcal{M}|^2$ over helicities and colors $\sum |\mathcal{M}|^2$ has been calculated.
-Furthermore initial state particles are considered as massless.
-This gives
+As in this thesis the sum of $|\mathcal{M}|^2$ over helicities and colors $\sum |\mathcal{M}|^2$ has been calculated one can write
 \begin{align}
@@
 \begin{align}
-\int \mathrm{d}\Phi_2 &= \frac{1}{s} \mu^{2\epsilon} \int \frac{\mathrm{d}|\vec{p}_1|\mathrm{d}\Omega^{D-1}_1}{(2\pi)^{D-2}} |\vec{p}_1|^{D-2} \delta \left(k_a^0 + k_b^0 - \sqrt{m_1^2 + |\vec{p}_1|^2} - \sqrt{m_2^2 + |\vec{p}_2|^2} \right)\nonumber\\
-&= \frac{1}{s} \frac{1}{(2\pi)^{D-2}}\frac{2\pi^{\frac{D}{2}-1}}{\Gamma(\frac{D}{2}-1)} \mu^{2\epsilon} \int_0^\infty\mathrm{d}|\vec{p}_1| \int_0^\pi \mathrm{d} \cos\theta p_1^{D-2}\sin^{D-4}\theta\nonumber\\
-&\ \ \delta \left(k_a^0 + k_b^0 - \sqrt{m_1^2 + |\vec{p}_1|^2} - \sqrt{m_2^2 + |\vec{p}_2|^2} \right).\label{eq:DPhi2}
+\int \mathrm{d}\Phi_2 &= \mu^{2\epsilon} \int \frac{\mathrm{d}|\vec{p}_1|\mathrm{d}\Omega^{D-1}_1}{(2\pi)^{D-2} 4 E_1 E_2} |\vec{p}_1|^{D-2} \delta \left(k_a^0 + k_b^0 - \sqrt{m_1^2 + |\vec{p}_1|^2} - \sqrt{m_2^2 + |\vec{p}_1|^2} \right)\nonumber\\
+&= \frac{1}{(2\pi)^{D-2}}\frac{2\pi^{\frac{D}{2}-1}}{\Gamma(\frac{D}{2}-1)} \mu^{2\epsilon} \int_0^\infty\mathrm{d}|\vec{p}_1| \int_0^\pi \mathrm{d} \cos\theta \frac{1}{4 E_1 E_2} p_1^{D-2}\sin^{D-4}\theta\nonumber\\
+&\ \ \delta \left(k_a^0 + k_b^0 - \sqrt{m_1^2 + |\vec{p}_1|^2} - \sqrt{m_2^2 + |\vec{p}_1|^2} \right).\label{eq:DPhi2}
 \end{align}
@@
 \end{align}
-was used. Because $\sum|\mathcal{M}|^2$ is calculated in terms of Mandelstam variables 
+has been used. Because $\sum|\mathcal{M}|^2$ is calculated in terms of Mandelstam variables 
 \begin{align}
@@
 t &= -2\left(|\vec{k}_a| \sqrt{m_1^2 + |\vec{p}_1|^2} - |\vec{k}_a||\vec{p}_1| \cos\theta\right) + m_1^2\label{eq:t} \\
-u &= (k_b-p_1)^2\nonumber\\
-u &= -2\left(|\vec{k}_a| \sqrt{m_1^2 + |\vec{p}_1|^2} + |\vec{k}_b||\vec{p}_1| \cos\theta\right) + m_1^2\label{eq:u}
+u &= (k_a-p_2)^2\nonumber\\
+u &= -2\left(|\vec{k}_a| \sqrt{m_2^2 + |\vec{p}_1|^2} + |\vec{k}_a||\vec{p}_1| \cos\theta\right) + m_2^2\label{eq:u}
 \end{align}
@@
 \begin{align}
-\mathrm{d}|\vec{p}_1|\ \mathrm{d}\cos\theta = -\frac{\sqrt{m_1^2+|\vec{p}_1|^2}}{8|\vec{k}_a|^2|\vec{p}_1|^2}\mathrm{d}u\ \mathrm{d}t.\label{eq:PhaseTrafo}
+\mathrm{d}|\vec{p}_1|\ \mathrm{d}\cos\theta = -\frac{E_1 E_2}{4|\vec{k}_a|^2|\vec{p}_1|^2(E_1+E_2)}\mathrm{d}u\ \mathrm{d}t.\label{eq:PhaseTrafo}
 \end{align}
-Inserting \ref{eq:PhaseTrafo} into \ref{eq:DPhi2} and using $|\vec{k}_a| = \frac{\sqrt{s}}{2}$ gives
+Inserting \ref{eq:PhaseTrafo} into \ref{eq:DPhi2} and using $2|\vec{k}_a| = \sqrt{s} = E_1 + E_2$ gives
 \begin{align}

### 2016-04-24 MSSM.tex
Passarino...

@@
 \end{align}
-Observing the component decomposition \ref{eq:L_matter},\ref{eq:L_gauge}, \ref{eq:L_superpot} of the 3 parts of this Lagrangian, one observes that the $F$ and $D$ fields have no kinetic term and are therefor auxiliary fields which can be eliminated by their equation of motion $\frac{\partial \mathcal{L}}{\partial\phi} = \partial_\mu\frac{\partial \mathcal{L}}{\partial(\partial_\mu \phi)}$ with $\phi = F, D$.
+Observing the component decomposition \ref{eq:L_matter},\ref{eq:L_gauge}, \ref{eq:L_superpot} of the 3 parts of this Lagrangian, one observes that the $F$ and $D$ fields have no kinetic term and are therefore auxiliary fields which can be eliminated by their equation of motion $\frac{\partial \mathcal{L}}{\partial\phi} = \partial_\mu\frac{\partial \mathcal{L}}{\partial(\partial_\mu \phi)}$ with $\phi = F, D$.
 Doing this one obtains

### 2016-04-24 Masterarbeit.tex
Passarino...

@@
   \begin{singlespace}\begin{center}\bfseries\Huge  
-  Title of Master thesis  
+  Squark Production in the R-Symmetric Supersymmetric Standardmodel  
   \end{center}\end{singlespace}
@@
 \section{Introduction}
-motivation: aesthetic: Coleman-Mandula --> Haag-Lopuszanski-Sohnius-Theorem\\
-plots for exclusion of squarks in specific SUSY scenarios (from Michael) --> R-Symmetry could be possible explanation for that because:\\
-MSSM-Lagrangian --> trafo rules for superfields under R-symm --> forbidden terms in MRSSM (write down Lagrangian for R-symmetric SUSYQCD)\\
-suppression of squark production in MRSSM by less diagrams ($m_{gluino}^{-4}$ suppression at low energies in MRSSM and only $m_{gluino}^{-2}$ suppression in MSSM)\\
-R-charges of all fields (show in diagram!) --> only if R-charges of final / initial particles are zero, a diagram is allowed in R-symm. model
+\input{Introduction}
 \newpage
@@
 \input{Renormalization}
+\newpage
+\input{InfraredSingularities}
 \newpage

### 2016-04-24 NLO.tex
Passarino...

\section{Squark Production at One-Loop}
The cross section for squark production does not exist in the limit of an infinitely large sgluon mass, instead it was found that it diverges logarithmically.\\
\begin{align}
\lim_{m_{\sigma^0}\to\infty} \sigma(qq \to \tilde{q}\tilde{q}) \sim \ln \frac{m_{\sigma^0}^2}{\mu^2}
\end{align}
This is actually expected as an effective field theory of the MRSSM where the sgluon is integrated out is no longer supersymmetric. This is because the sgluon is together with the octino part of a supermultiplet. Integrating out only the sgluon means that the octino misses its superpartner in the effective field theory. In this case the decoupling theorem \cite{Appelquist:1974tg} does no longer hold.\\
Refer to super oblique correction and quantify difference of $g$ and $\hat{g}$ from eq 4 in \cite{Cheng:1997sq}

### 2016-04-24 Renormalization.tex
Tree level Feynman diagrams
Passarino...

@@
-\section{Renormalization of the MRSSM}
+\section{UV-Divergences and Renormalization of the MRSSM}
 In order to improve the prediction of the cross section of the previous chapter one has to take quantum corrections into account.
@@
 \end{align}
-for $A = L,R$. The gluino mass counterterm is ascertained by the condition
+for $A \in \left\{L,R\right\}$. The gluino mass counterterm is ascertained by the condition
 \begin{align}
@@
 \subsection{Renormalization of the Gauge Coupling}
-The gauge coupling $g_s$ is renormalized in the $\overline{\mathrm{MS}}$-scheme with the modification that additional logarithms are substracted.
+The gauge coupling $g_s$ is renormalized in the $\overline{\mathrm{MS}}$-scheme with the modification that additional logarithms are subtracted, i.e.
+light particles are treated in the $\overline{\mathrm{MS}}$-scheme and heavy particles in the zero-momentum subtraction scheme.
 This is to decouple heavy particles from the running of $\alpha_s = \frac{g_s^2}{4\pi}$.
@@
 The running due to effects of heavy particles is then encoded in the logarithms of $\delta g_s$.\\
-Extracting $\delta g_s$ from the quark-quark-gluon vertex requires not only the computation of $i\Gamma^{1L}_{q_i\overline{q}_jG^a}$ but also the (re)evaluation  of the auxiliary field renormalization constants $\delta Z_q^{\mathrm{aux}}$ and $\delta Z_G^{\mathrm{aux}}$.
-These will not be the same as the on-shell field renormalization.
+Extracting $\delta g_s$ from the quark-quark-gluon vertex requires not only the computation of $i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_jG^\mu_a}$ but also the (re)evaluation of auxiliary field renormalization constants $\delta Z_q^{\mathrm{aux}}$ and $\delta Z_G^{\mathrm{aux}}$ in the above mentioned scheme.
+These will not be the same as the on-shell scheme.
 
@@
 The first one corresponds to light particles the second one to heavy particles: $i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j} = i\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j} + i\Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}$.
-For light particles only the UV-divergent part is kept.
-For heavy particles also the $\mu$-dependent terms are kept:
+For light particles only the UV-divergent\footnote{In contrast to the MS-scheme in the $\overline{\mathrm{MS}}$-scheme not only the pure ultraviolet divergence but also two additional transcendent numbers are subtracted.
+It is therefore common to define $\Delta_\epsilon = \frac{1}{\epsilon} -\gamma_{\mathrm{E}} + \ln 4\pi$.} part is kept.
+The self energy corresponding to the heavy particles is taken at zero momentum $p^2=0$.
 \begin{align}
-i\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j}|_{\mathrm{UV-div}} &= i \frac{g_s^2}{16\pi^2}\delta_{ij} \slashed{p} C(F) \frac{1}{\epsilon_{\mathrm{UV}}}\\
-i\Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}|_{\mathrm{UV-div,\mu-dep}} &= i \frac{g_s^2}{16\pi^2}\delta_{ij} \slashed{p} C(F)\left( \frac{1}{\epsilon_{\mathrm{UV}}} -\ln\frac{m_{\tilde{q}}^2}{\mu^2} \right)
+\left.i\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j}\right|_{\mathrm{UV-div}} &= i C(F) \frac{g_s^2}{16\pi^2} \Delta_\epsilon \slashed{p} \delta_{ij}\\
+i\Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}(p^2=0) &= -i C(F) \frac{g_s^2}{16\pi^2} 2B_1(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\slashed{p}\delta_{ij}
 \end{align}
@@
 \begin{align}
-\frac{\partial}{\partial \slashed{p}} \left[  \Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j}|_{\mathrm{UV-div}} + \Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}|_{\mathrm{UV-div,\mu-dep}} + \Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}  \right]_{p^2 = 0} = 0
+\frac{\partial}{\partial \slashed{p}} \left[  \left.\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j}\right|_{\mathrm{UV-div}} + \Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}(p^2=0) + \Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}  \right] = 0
 \end{align}
@@
 \begin{align}
-\delta Z_q^{\mathrm{aux}} = -\frac{g_s^2}{16\pi^2} C(F)\left[\left( \frac{1}{\epsilon_{\mathrm{UV}}} \right) + \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln\frac{m_{\tilde{q}}^2}{\mu^2} \right) \right]
+\delta Z_q^{\mathrm{aux}} = -\frac{g_s^2}{16\pi^2} C(F)\left[ \Delta_\epsilon + B_1(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\right] .
 \end{align}
-The first curved bracket corresponds to contributions from light particles in the loop whereas the second curved bracket corresponds to contributions from heavy particles in the loop.
 
 \subsubsection{The Gluon Self-Energy}
-As for the quark self-energy there are again contributions to the self-energy originating from light and heavy particles.
-As for the quark only specific terms are kept in calculating the auxiliary renormalization constants.
+As for the quark self-energy there are again contributions to the self-energy originating from light and heavy particles. Again these are differently dealt with.
 \begin{figure}[!htbp]
@@
 \end{tikzpicture}
-\caption{contribution to the self-energy of the gluon originating from light particles}\label{fig:lightGluonSelfEnergy}
+\caption{Contribution to the self-energy of the gluon originating from light particles}\label{fig:lightGluonSelfEnergy}
 \end{center}
@@
 \begin{align}
-i\Gamma^{\mathrm{1L,light}}_{G_\mu^a G_\nu^b}|_{\mathrm{UV-div}} &= i\frac{g_s^2}{16\pi^2 \epsilon_{\mathrm{UV}}}\delta_{ab} \left[ 0 - \frac{4 (n_{f}-1)}{3} T(F) (p^2g^{\mu\nu}-p^\mu p^\nu) + \frac{C(A)}{12}(p^2g^{\mu\nu} + 2 p^\mu p^\nu) \right.\nonumber\\
-&+\left. \frac{C(A)}{12}(19 p^2g^{\mu\nu} - 22 p^\mu p^\nu) \right]\nonumber\\
-&=i\frac{g_s^2}{16\pi^2 \epsilon_{\mathrm{UV}}}\delta_{ab} \left[ - \frac{4 (n_{f}-1)}{3} T(F) + \frac{5}{3} C(A) \right](p^2g^{\mu\nu}-p^\mu p^\nu)
+\left.i\Gamma^{\mathrm{1L,light}}_{G_\mu^a G_\nu^b}\right|_{\mathrm{UV-div}} &= i\frac{g_s^2}{16\pi^2}\Delta_\epsilon \left[ 0 - \frac{4 (n_{f}-1)}{3} T(F) (p^2g^{\mu\nu}-p^\mu p^\nu) + \frac{C(A)}{12}(p^2g^{\mu\nu} + 2 p^\mu p^\nu) \right.\nonumber\\
+&+\left. \frac{C(A)}{12}(19 p^2g^{\mu\nu} - 22 p^\mu p^\nu) \right]\delta_{ab}\nonumber\\
+&=i\frac{g_s^2}{16\pi^2} \Delta\epsilon \left[ - \frac{4 (n_{f}-1)}{3} T(F) + \frac{5}{3} C(A) \right](p^2g^{\mu\nu}-p^\mu p^\nu)\delta_{ab}
 \end{align}
@@
 \begin{align}
- \Gamma^{\mathrm{1L,light}}_{G_\mu^a G_\nu^b}|_{\mathrm{UV-div}} + \Gamma^{\mathrm{1L,heavy}}_{G_\mu^a G_\nu^b}|_{\mathrm{UV-div,\mu-dep}} - \delta Z_G^{\mathrm{aux}}\left(p^2 g^{\mu\nu} - p^\mu p^\nu \right)\delta_{ab} = 0
+ \left.\Gamma^{\mathrm{1L,light}}_{G_\mu^a G_\nu^b}\right|_{\mathrm{UV-div}} + \Gamma^{\mathrm{1L,heavy}}_{G_\mu^a G_\nu^b}(p^2=0) - \delta Z_G^{\mathrm{aux}}\left(p^2 g^{\mu\nu} - p^\mu p^\nu \right)\delta_{ab} = 0
 \end{align}
@@
 \subsubsection{The $q\overline{q}G$ Vertex Correction}
+As for the self energies the vertex correction constitutes of loops from light particles which correspond to the Standard Model and additional heavy particle loops.
 \begin{figure}[!htbp]
@@
 \end{tikzpicture}
-\caption{contribution from light particles to the $q\overline{q}G$ vertex correction}\label{fig:GaugeCouplingCorrection}
+\caption{Contribution from light (Standard Model) particles to the $q\overline{q}G$ vertex. correction}\label{fig:GaugeCouplingCorrection}
 \end{center}
@@
 \begin{align}
-i\Gamma^{\mathrm{1L,light}}_{q_i \overline{q}_j G_\mu^a}|_{\mathrm{UV-div}} &= -i g_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2 \epsilon_{\mathrm{UV}}} \left[ \left(C(F) -\frac{C(A)}{2}\right) + \frac{3}{2} C(A) \right]
+\left.i\Gamma^{\mathrm{1L,light}}_{q_i \overline{q}_j G_\mu^a}\right|_{\mathrm{UV-div}} &= - ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} \left[\left(C(F) -\frac{C(A)}{2}\right)2(B_0(0, 0, 0) - 2C_{00}(0,0,0,0,0)) \right.\nonumber\\
+&\left.+ C(A)(B_0(0, 0, 0) + 2C_{00}(0,0,0,0,0))\right]\nonumber\\
+&= -i g_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} \Delta_\epsilon \left[ \left(C(F) -\frac{C(A)}{2}\right) + \frac{3}{2} C(A) \right]\label{eq:qqGlight}
 \end{align}
+The term in the curved brackets of eq.
+\ref{eq:qqGlight} corresponds to the first diagram in fig.
+\ref{fig:GaugeCouplingCorrection} whereas the last term in the squared brackets corresponds to the second diagram.
 \begin{figure}[!htbp]
@@
 \end{tikzpicture}
-\caption{contribution from heavy particles to the $q\overline{q}G$ vertex correction}
+\caption{Contribution from heavy particles to the $q\overline{q}G$ vertex correction.}
 \end{center}
@@
 \begin{align}
-i\Gamma^{\mathrm{1L,heavy}}_{q_i \overline{q}_j G_\mu^a}|_{\mathrm{UV-div,\mu-dep}} = -i g_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} &\left[ \left(C(F) -\frac{C(A)}{2}\right) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{g}}^2}{\mu^2} \right) \right.\nonumber\\
-&+ \left.\frac{1}{2} C(A)\left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{g}}^2}{\mu^2} \right) \right]
+i\Gamma^{\mathrm{1L,heavy}}_{q_i \overline{q}_j G_\mu^a}(p_i^2=0) = - -g_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} &\left[ \left(C(F) -\frac{C(A)}{2}\right) 4C_{00}(0, 0, m_{\tilde{g}}^2, m_{\tilde{q}}^2, m_{\tilde{q}}^2) \right.\nonumber\\
+&+ \left. C(A)\left( B_0(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2) -2C_{00}(0, 0, m_{\tilde{g}}^2, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\right) \right]
 \end{align}
+The argument $p_i^2=0$ of the vertex function denotes, that all external particles are taken on shell, i.e. at zero momentum.
 The sum of the 1-loop corrections and the counterterm should be set to zero:
 \begin{align}
-i\Gamma^{\mathrm{1L,light}}_{q_i \overline{q}_j G_\mu^a}|_{\mathrm{UV-div}} + i\Gamma^{\mathrm{1L,heavy}}_{q_i \overline{q}_j G_\mu^a}|_{\mathrm{UV-div,\mu-dep}} + \left[ -ig_s T^a_{ij}\gamma^\mu\left( \frac{\delta g_s}{g_s} + \delta Z_q^{\mathrm{aux}} + \frac{\delta Z_G^{\mathrm{aux}}}{2} \right)\right] = 0.
+\left.i\Gamma^{\mathrm{1L,light}}_{q_i \overline{q}_j G_\mu^a}\right|_{\mathrm{UV-div}} + i\Gamma^{\mathrm{1L,heavy}}_{q_i \overline{q}_j G_\mu^a}(p_i^2=0) + \left[ -ig_s T^a_{ij}\gamma^\mu\left( \frac{\delta g_s}{g_s} + \delta Z_q^{\mathrm{aux}} + \frac{\delta Z_G^{\mathrm{aux}}}{2} \right)\right] = 0.
 \end{align}
@@
 \begin{align}
-\frac{\delta g_s}{g_s} &= \frac{g_s^2}{16\pi^2} \left[ \left( \frac{2}{3}T(F)(n_f-1) - \frac{11}{6}C(A) \right) \frac{1}{\epsilon_{\mathrm{UV}}} + \left( \frac{5}{6}C(A) + \frac{2}{3}T(F) + \frac{1}{3}T(F)n_f \right)\frac{1}{\epsilon_{\mathrm{UV}}}  \right.\nonumber\\
+\frac{\delta g_s}{g_s} &= \frac{g_s^2}{16\pi^2} \left[ \left( \frac{2}{3}T(F)(n_f-1) - \frac{11}{6}C(A) \right) \Delta_\epsilon + \left( \frac{5}{6}C(A) + \frac{2}{3}T(F) + \frac{1}{3}T(F)n_f \right)\Delta_\epsilon  \right.\nonumber\\
 &- \frac{2}{3} C(A) \ln \frac{m_{\tilde{g}}^2}{\mu^2} - \frac{1}{3}T(F)n_f \ln \frac{m_{\tilde{q}}^2}{\mu^2} - \frac{2}{3}T(F) \ln \frac{m_t^2}{\mu^2}-\frac{1}{12} C(A) \left( \ln \frac{m_{\phi^0}^2}{\mu^2} + \ln \frac{m_{\sigma^0}^2}{\mu^2} \right)\label{eq:deltaGs}
@@
 \beta(g_s,\epsilon) &= -\epsilon g_s \left( 1 + \frac{g_s^2}{16\pi^2} L \right) + \beta(g_s) + \mathcal{O}(\mathrm{2-loop})\\
-\beta(g_s) &= \frac{g_s^3}{16\pi^2} \beta_0^L.
+\beta(g_s) &= \frac{g_s^3}{16\pi^2} \beta_0^L + \mathcal{O}(\mathrm{2-loop}).
 \end{align}
-This is exactely the beta function from QCD first found by [Gross, Politzer, Wil]
+This is the beta function from QCD first found by [Gross, Politzer, Wil]
 
@@
 	\node at (0,-0.5) {$\tilde{g}$};
-	\draw[scalar](45:0.5)--(-45:0.5);
+	\draw[fermion](45:0.5)--(-45:0.5);
 	\node at (0.7,0) {$q$};
@@
 
-\subsection{$\overline{\mathrm{MS}}$ - Renormalization}
-To check for UV-finiteness it might prove useful to summarize the UV-divergent part of all renormalization constants.
-In order to obtain these the Passarino-Veltman integrals need to be substituted by their $\frac{1}{\epsilon}$ coefficient.
-These  had been taken from \cite{Denner} and checked with \texttt{FeynArts} and \texttt{FormCalc} \cite{Hahn:2000}, \cite{Nejad2013}, \cite{Hahn:2000}.
+\subsection{$\overline{\mathrm{MS}}$ - Renormalization}\label{sec:MSRen}
+To quickly check for UV-finiteness of a Greenfunction or a physical observable it is useful to have the extracted UV-divergences of the renormalization constants at hand.
+How these are obtained is described in \ref{sec:Passarino}.\\
+(In order to obtain these the Passarino-Veltman integrals need to be substituted by their $\frac{1}{\epsilon}$ coefficient.
+These  had been taken from \cite{Denner} and checked with \texttt{FeynArts} and \texttt{FormCalc} \cite{Hahn:2000}, \cite{Nejad2013}, \cite{Hahn:2000}.)
+\begin{align}
+& \delta Z_{\tilde{g}}^L = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} 2\left[ T(F) n_f + C(A) \right] &&  \delta Z_{\tilde{g}}^R = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} 2 C(A)\nonumber\\
+& \delta m_{\tilde{g}} = \frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} \left[ T(F) n_f - 2C(A) \right] m_{\tilde{g}}\nonumber\\
+& \delta Z_{\tilde{q}} = 0 && \delta m_{\tilde{q}}^2 = 0\nonumber\\
+&\frac{\delta g_s}{g_s} = \frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}}\left[ T(F) n_f - C(A) \right]\nonumber\\
+& \delta Z_{\phi^0} = 0 && \delta m_{\phi^0}^2 = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}}\left[ 8T(F)n_f - 16C(A) \right]m_{\tilde{g}}^2\nonumber\\
+& \delta Z_{\sigma^0} = 0 && \delta m_{\sigma^0}^2 = 0\nonumber\\
+& \delta Z_{G} = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} 2T(F) n_f
+\end{align}

### 2016-04-24 Standardmodel.tex
Passarino...

--- 2016-02-25 Standardmodel.tex
@@
 \section{The Standard Model}
-The standard model(SM) is a relativistic quantum field theory. 
-It contains different fields, whose quantized excitations are interpreted as particles.\\
+The Standard Model of particle physics is the commonly accepted theory describing the world's fundamental particles and their interactions.
+It is a gauge quantum field theory which is characterized by its invariance under different symmetry groups.
+The Standard Model contains different fields, whose quantized excitations are interpreted as particles.\\
 %The different fields defined on Minkowski space are Dirac spinors describing matter fields (leptons and quarks), gauge vectors describing force mediators and a scalar field (the Higgs) which accounts for the masses of particles.\\
@@
 \subsection{Symmetries and Transformations}
-\paragraph{Space-Time Symmetries:}
-The SM is defined on Minkowski space, whose coordinates are label with $x^\mu$ $\mu = 0,1,2,4$.
+\subsubsection*{Spacetime Symmetries}
+The Standard Model is defined on Minkowski space, whose coordinates are label with $x^\mu$ $\mu = \left\{0,1,2,4\right\}$.
 As a relativistic theory it is invariant under Poincaré transformations, i.e.
@@
 \end{align}
-The fields of the SM transform in different representations of the Poincaré-group.
+The fields of the Standard Model transform in different representations of the Poincaré-group \cite{book:17018}.
 
-\paragraph{Gauge Symmetries:} In order to describe interactions of matter particles one uses gauge theories.
-In the SM which is such a theory matter fields are described by Dirac spinors.
-The Lagrangian of a free Dirac field reads
+\subsubsection*{Gauge Symmetries} 
+In order to describe interactions of matter particles one uses gauge theories. In the Standard Model matter fields are described by Dirac spinors. The Lagrangian of a free Dirac field reads
 \begin{align}
@@
 \begin{align}
-\psi(x) \to U(x)\psi(x),
+\Psi(x) \to U(x)\Psi(x),
 \end{align}
@@
 Because the gauge group is a unitary matrix Lie group it can be written in the form $U(x)=\mathrm{exp}(-igT^a\theta^a(x))$.
-Here $T^a$ are the self-adjoint generators of the associated Lie algebra, $g$ is the coupling constant of the gauge group and $\theta^a(x)$ are local parameters.
-The structure constants $f_{abc}$ of a Lie algebra are defined by $[T^a,T^b] = if_{abc}T^c$.\\
+Here $T^a$ are the self-adjoint generators of the associated Lie algebra which obey
+\begin{align}
+[T^a,T^b] = if_{abc}T^c
+\end{align}
+where $f_{abc}$ are the structure constants of a Lie algebra, $g$ is the coupling constant of the gauge group and $\theta^a(x)$ are local parameters.\\
 Because the parameters of the gauge group are local the derivative in \ref{eq:DiracLagrangian} spoils the gauge invariance.
-In order to rectify gauge invariance of the Lagrangian one has to introduce a further field for each index $a$ of the generators - the gauge vector $G^{a\mu}$.
-The matrix valued gauge vector $G^\mu := G^{a\mu}T^a$ transforms as
+In order to rectify gauge invariance of the Lagrangian one can introduce a further field for each index $a$ of the generators - the gauge vector $G^{a\mu}$.
+Defining the transformation of the matrix valued gauge vector $G^\mu := G^{a\mu}T^a$ as
 \begin{align}
-G^{\mu}(x) \to U(x)G^\mu(x)U^{-1}(x) + \frac{i}{g}U(x)\partial^\mu U^{-1}(x)
+G^{\mu}(x) \to U(x) \left( G^\mu(x) + \frac{i}{g}\partial^\mu \right) U^{-1}(x)
 \end{align}
-One then obtains the gauge invariant Lagrangian for a non-abelian gauge theory first found by Yang and Mills [cite original paper]
+and introducing the gauge covariant derivative
+\begin{align}
+D^\mu = \partial^\mu + igT^aG^{a\mu}
+\end{align}
+one finds that the expression $D_\mu \Psi(x)$ transforms as
+\begin{align}
+D_\mu \Psi(x) \to U(x) D_\mu \Psi(x) \label{eq:CovDerivative}
+\end{align}
+Therefore gauge invariance in \ref{eq:DiracLagrangian} is restored by replacing $\partial_\mu$ with $D_\mu$.
+But if the gauge vector is interpreted as a physical field there must apart from the so far introduced interaction term also be a kinetic term associated with it.
+Using \ref{eq:CovDerivative} one defines the field strength tensor\footnote{An alternative construction makes use of the gauge invariant Wilson loop.
+This gives some insights into the geometry of gauge transformations \cite{Peskin}.} $F^{a\mu\nu}$ whose matrix valued form
+\begin{align}
+F^{\mu\nu} = F^{a\mu\nu}T^a = \frac{1}{ig}[D^\mu,D^\nu] = \partial^\mu G^\nu - \partial^\nu G^\mu - i f_{abc}....
+\end{align}
+transforms as $F^{\mu\nu} \to U(x)F^{\mu\nu}U^{-1}(x)$.
+Using the cyclic property of the trace and the Dynkin index $T(F)$ defined in the appendix \ref{eq:DynkinIndex}  one can write down a gauge invariant kinetic term for the gauge vector:
+\begin{align}
+\mathcal{L}_{\mathrm{gauge}} = - \frac{1}{2} \mathrm{Tr} \left( F^{\mu\nu}F_{\mu\nu} \right) = -\frac{T(F)}{2} F^{a\mu\nu}F^a_{\mu\nu}
+\end{align}
+This completes the construction of a Lagrangian which is invariant under non-abelian gauge group transformations. The result is the famous Yang and Mills Lagrangian[cite original paper]
 \begin{align}
@@
 \end{align}
-In comparison to the Dirac-Lagrangian \ref{eq:DiracLagrangian} the partial derivative is replaced with the gauge covariant derivative $D^\mu = \partial^\mu + igT^aG^{a\mu}$ and the gauge invariant kinetic term for the gauge fields is added.
-This comprises the field strenth-tensor $F^{a\mu\nu}$ which is in its matrix valued form defined by $F^{\mu\nu} = F^{a\mu\nu}T^a = \frac{1}{ig}[D^\mu,D^\nu]$.\\
+This Lagragian gives rise to spin-$\frac{1}{2}$ (matter) particles which interact with spin-1 (force mediator) particles with each other.
+Furthermore if the gauge group is non-abelian, i.e.
+$f_{abc} \neq 0$, there are self interactions among the spin-1 particles.\\
 The gauge group of the SM is a direct product ???
@@
 \newpage
-\subsection{The particles of the SM}
-In the SM different matter particles take part in different interactions, i.e. their corresponding spinor couples to different gauge vectors.\\
-If a spinor couples to a certain gauge vector it transforms  non trivially (like indicated in table \ref{tab:SM_transformations}) under the gauge group which is associated with this gauge vector\footnote{In the SM all matter particles transform in the fundamental (or trivial) representation of the gauge group in question.}.
+\subsection{The Particles of the Standard Model}
+In the Standard Model different matter particles take part in different interactions, i.e. their corresponding spinor couples to different gauge vectors.\\
+If a spinor couples to a certain gauge vector it transforms  non trivially (like indicated in table \ref{tab:SM_transformations}) under the gauge group which is associated with this gauge vector\footnote{In the Standard Model all matter particles transform in the fundamental (or trivial) representation of gauge groups.}.
 This means if a particle couples to a certain force its charge which is associated with this force is nonzero.\\
@@
 \end{align}
-The quark mass matrices are not diagonal.
+The quark mass matrices are not diagonal (origin of CP - invariance).
 One therefore has to distinguish between interaction and mass eigenstates of the quark.
@@
 \begin{align}
-\mathcal{L}_{R_\xi} = -\frac{1}{2\xi_A} (\partial^\mu A_\mu)^2  - \frac{1}{2\xi_W} |\partial^\mu W_\mu^+ - m_W \xi_W \phi^+|^2 - \frac{1}{2\xi_Z} (\partial^\mu Z_\mu - m_Z \xi_Z \sigma)^2 CHECK!
+\mathcal{L}_{R_\xi} = -\frac{1}{2\xi_A} (\partial^\mu A_\mu)^2  - \frac{1}{2\xi_W} |\partial^\mu W_\mu^+ - m_W \xi_W \phi^+|^2 - \frac{1}{2\xi_Z} (\partial^\mu Z_\mu - m_Z \xi_Z \sigma)^2 
 \end{align}
 Here $R_\xi$ is chosen, where the parameters $\xi_i$ specify the gauge.
-The last 2 terms are modified with the Goldstone bosons from section \ref{sec:EWSB} because of the massiveness of the $W^\pm$ an $Z^0$ bosons.\\
+The last 2 terms are modified with the Goldstone bosons from section \ref{sec:EWSB} because of the massiveness of the $W^\pm$ an $Z^0$ bosons.\cite{book:811554}\\%page 622
 Secondly there is a ghost Lagrangian

### 2016-04-24 TreeLevel.tex
remark about Wilson loop (still undone)
Passarino...

@@
 \section{Sparticle Production at Tree Level}
+In this chapter the production of strongly interacting supersymmetric particles\footnote{The production of sgluons is excluded from the analysis as their mass will be chosen to be too large to produce them.} in the MRSSM is considered.
 
@@
 \end{tikzpicture}
-\caption{Tree level diagrams for $q\overline{q} \to \tilde{q}\tilde{q}^\dagger$}
+%\caption{Tree level diagrams for $q\overline{q} \to \tilde{q}\tilde{q}^\dagger$}
 \end{center}
-\end{figure}
-\begin{figure}[!htbp]
+%\end{figure}
+%\begin{figure}[!htbp]
 \begin{center}
 \begin{tikzpicture}[line width=1.0 pt, scale=1.3]
+    \node at (0,0) {};
+\begin{scope}[shift={(0,-1)}]
 	\draw[gluon] (-1,0.5)--(-0.42,0);
@@
 \end{scope}
+\end{scope}
 \end{tikzpicture}
-\caption{Tree level diagrams for $GG \to \tilde{q}\tilde{q}^\dagger$}
+%\caption{Tree level diagrams for $GG \to \tilde{q}\tilde{q}^\dagger$}
 \end{center}
-\end{figure}
-\begin{figure}[!htbp]
+%\end{figure}
+%\begin{figure}[!htbp]
 \begin{center}
 \begin{tikzpicture}[line width=1.0 pt, scale=1.3]
+    \node at (0,0) {};
+\begin{scope}[shift={(0,-1)}]
 	\draw[fermion] (-1,0.5)--(0,0.5);
@@
 \end{scope}
+\end{scope}
 \end{tikzpicture}
-\caption{Tree level diagrams for $qq \to \tilde{q}\tilde{q}$}
+%\caption{Tree level diagrams for $qq \to \tilde{q}\tilde{q}$}
 \end{center}
-\end{figure}
-\begin{figure}[!htbp]
+%\end{figure}
+%\begin{figure}[!htbp]
 \begin{center}
 \begin{tikzpicture}[line width=1.0 pt, scale=1.3]
+    \node at (0,0) {};
+\begin{scope}[shift={(0,-1)}]
 	\draw[fermion] (-1,0.5)--(-0.42,0);
@@
 \end{scope}
+\end{scope}
 \end{tikzpicture}
-\caption{Tree level diagrams for $q\overline{q} \to \tilde{g}\overline{\tilde{g}}$}
+%\caption{Tree level diagrams for $q\overline{q} \to \tilde{g}\overline{\tilde{g}}$}
 \end{center}
-\end{figure}
-\begin{figure}[!htbp]
+%\end{figure}
+%\begin{figure}[!htbp]
 \begin{center}
 \begin{tikzpicture}[line width=1.0 pt, scale=1.3]
+    \node at (0,0) {};
+\begin{scope}[shift={(0,-1)}]
 	\draw[gluon] (-1,0.5)--(-0.42,0);
@@
 \end{scope}
+\end{scope}
 \end{tikzpicture}
-\caption{Tree level diagrams for $GG \to \tilde{g}\overline{\tilde{g}}$}
+%\caption{Tree level diagrams for $GG \to \tilde{g}\overline{\tilde{g}}$}
 \end{center}
-\end{figure}
-\begin{figure}[!htbp]
+%\end{figure}
+%\begin{figure}[!htbp]
 \begin{center}
 \begin{tikzpicture}[line width=1.0 pt, scale=1.3]
+    \node at (0,0) {};
+\begin{scope}[shift={(0,-1)}]
 	\draw[fermion] (-1,0.5)--(-0.42,0);
@@
 \end{scope}
+\end{scope}
 \end{tikzpicture}
-\caption{Tree level diagrams for $qG \to \tilde{q}\tilde{g}$}
+\caption{Tree level diagrams for squark and gluino production at tree level in the MRSSM.
+The processes $GG \to \tilde{q}\overline{\tilde{q}}$ and $qG \to \tilde{q}\tilde{g}$ are identical to those of the MSSM.
+The processes $q\overline{q} \to \tilde{q}\tilde{\overline{q}}$ and $qq \to \tilde{q}\tilde{q}$ involve the production of less chiralities than in the MSSM.
+Also in the $q\tilde{q} \to \tilde{g}\overline{\tilde{g}}$ channel only half of the t-channel squark chiralities occur in the MRSSM.(Anti-)Gluino production via initial gluons $GG \to \tilde{g}\overline{\tilde{g}}$ proceeds via the same diagrams like in the MSSM but its cross section is twice as much in the MRSSM for gluino and antigluino are distinguishable particles.}
 \end{center}
@@
 \end{align}
-For NLO-corrections the results are expanded up to $\mathcal{O}(\epsilon)$. Furthermore the usual Mandelstam variables $s,t,u$ and the following modifications of them are used:
+For NLO-corrections the results are given in $D = 4 - 2\epsilon$ dimensions. Furthermore the usual Mandelstam variables $s,t,u$ and the following modifications of them are used:
 \begin{align}
@@
 \end{align}
+In view of the renormalization to be performed at the 1-loop level it has been distinguished between the gauge coupling $g_s$ from the gluon-quark-quark vertex and its supersymmetric analogue $\hat{g}_s$ from the gluino-squark-quark vertex.
 
 \subsection{Partonic Cross Sections}
+Having calculated the absolute squared Feynman amplitudes one obtains the partonic cross section via
+\begin{align}
+\frac{\mbox{d}^2 \sigma}{\mbox{d}t\ \mbox{d}u} =& \frac{K_{ab}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_1^2m_2^2}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_1^2m_2^2)\nonumber\\
+&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum |\mathcal{M}|^2
+\end{align}
 The leading order cross sections are
@@
 \subsection{Hadronic Cross Section}
-factorization (pictorial explanation in factorization paper chapter 1.4)
+factorization (pictorial explanation in factorization paper chapter 1.4 and Dissertori and Seymour, Marx page 24 below)
 The hadronic cross section for the production of a final state $X$, e.g.
@@
 \begin{align}
-\sigma^B(ij \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_i(x_1) f_j(x_2)\ \sigma^B (ij \to X, s = x_ 1x_2 S).
+\sigma^B_{\mathrm{Had}}(ij \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_i(x_1) f_j(x_2)\ \sigma^B_{\mathrm{Part}} (ij \to X, s = x_ 1x_2 S).
 \end{align}
@@
 \begin{align}
-\sigma^B(H_1 H_2 \to X) = \sum_{i,j} \sigma^B(i,j \to X).
+\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(i,j \to X).
 \end{align}
 refer to Kribs, Martin
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.45]{figures/mr=0,9_MSSM+MRSSM}
+\includegraphics[scale=.45]{figures/mr=2_MSSM+MRSSM}
+\end{center}
+\end{figure}
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.45]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
+\includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
+\end{center}
+\end{figure}
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.45]{figures/mr=5_MSSM+MRSSM}
+\includegraphics[scale=.45]{figures/rel_weights_mr=5_MSSM+MRSSM}
+\end{center}
+\end{figure}

### 2016-05-14 Renormalization.tex
mainly Tree Level Plots

@@
-\section{UV-Divergences and Renormalization of the MRSSM}
+\section{Renormalization of the MRSSM}\label{sec:renMRSSM}
 In order to improve the prediction of the cross section of the previous chapter one has to take quantum corrections into account.
@@
 \begin{align}
-\Gamma^{(1),ct,restore}_{DREG} = \Gamma^{(\leq 1)}_{DRED} - \Gamma^{(\leq 1)}_{DREG}.\label{eq:GammaCtRestore}
+\Gamma^{\mathrm{(1),ct,restore}}_{\mathrm{DREG}} = \Gamma^{(\leq 1)}_{\mathrm{DREG}} - \Gamma^{(\leq 1)}_{\mathrm{DREG}}.\label{eq:GammaCtRestore}
 \end{align} 
@@
 \begin{align}
-\delta Z_q = 2 C(F) \frac{g_s^2}{16\pi^2} \Re \left[ B_1(p^2,m_{\tilde{g}}^2,m_{\tilde{q}}^2) + \frac{1}{2} \right].
+\delta Z_q = 2 C(F) \frac{g_s^2}{16\pi^2} \Re \left[ B_1(0 ,m_{\tilde{g}}^2,m_{\tilde{q}}^2) + \frac{1}{2}??? \right].
 \end{align}
@@
 &+\left. \frac{C(A)}{12}(19 p^2g^{\mu\nu} - 22 p^\mu p^\nu) \right]\delta_{ab}\nonumber\\
-&=i\frac{g_s^2}{16\pi^2} \Delta\epsilon \left[ - \frac{4 (n_{f}-1)}{3} T(F) + \frac{5}{3} C(A) \right](p^2g^{\mu\nu}-p^\mu p^\nu)\delta_{ab}
+&=i\frac{g_s^2}{16\pi^2} \Delta_\epsilon \left[ - \frac{4 (n_{f}-1)}{3} T(F) + \frac{5}{3} C(A) \right](p^2g^{\mu\nu}-p^\mu p^\nu)\delta_{ab}
 \end{align}
+Both contributions the one from the gluon loop and the one from the ghost loop are not proportional to $(p^2g^{\mu\nu}-p^\mu p^\nu)$ but their sum is.
 \begin{figure}[!htbp]
@@
 \end{figure}
-The heavy particle contributions are given by\\
+The heavy particle contributions are calculated in the zero-momentum subtraction
 \begin{align}
-i\Gamma^{\mathrm{1L,heavy}}_{G_\mu^a G_\nu^b}|_{\mathrm{UV-div, \mu-dep}} &= i\frac{g_s^2}{16\pi^2}\delta_{ab} \left[ - 4 T(F)n_f \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{q}}^2}{\mu2} \right)m_{\tilde{q}}^2 g^{\mu\nu} - C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)m_{\phi^0}^2 g^{\mu\nu} \right.\nonumber\\
-&- C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\sigma^0}^2}{\mu2} \right)m_{\sigma^0}^2 g^{\mu\nu} - \frac{4}{3}T(F)\left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_t^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)\nonumber\\
-& - \frac{4}{3} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{g}}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)\nonumber\\
-& -\frac{2}{3}T(F) n_f \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{q}}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) + 4T(F)n_f \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{q}}^2}{\mu2} \right)m_{\tilde{q}}^2 g^{\mu\nu} \nonumber\\
-&-\frac{1}{6} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) + C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)m_{\phi^0}^2 g^{\mu\nu} \nonumber\\
-&\left.-\frac{1}{6} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) + C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)m_{\phi^0}^2 g^{\mu\nu}\right]\nonumber\\
-&= i\frac{g_s^2}{16\pi^2}\delta_{ab} \left[- \frac{4}{3}T(F)\left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_t^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)\right.\nonumber\\
-& - \frac{4}{3} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{g}}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)\nonumber\\
-& -\frac{2}{3}T(F) n_f \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{q}}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) \nonumber\\
-&-\frac{1}{6} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)  \nonumber\\
-&\left.-\frac{1}{6} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) \right]
+%i\Gamma^{\mathrm{1L,heavy}}_{G_\mu^a G_\nu^b}|_{\mathrm{UV-div, \mu-dep}} &= i\frac{g_s^2}{16\pi^2}\delta_{ab} \left[ - 4 T(F)n_f A_0(m_{\tilde{q}}^2) g^{\mu\nu} - C(A) A_0(m_{\phi^0}^2) g^{\mu\nu} - C(A) A_0(m_{\sigma^0}^2) g^{\mu\nu} \right.\nonumber\\
+%&- T(F)\left(\left( \frac{1}{4} A_0(m_t^2) - \frac{1}{2}B_{00}(p^2,m_t^2,m_t^2) \right)g^{\mu\nu} - \frac{1}{2} B_{11}(p^2,m_t^2,m_t^2)p^\mu p^\nu + \frac{1}{4} B_1(p^2,m_t^2,m_t^2)(p^2 g^{\mu\nu} - 2p^\mu p^\nu)  \right)\nonumber\\
+%& - \frac{4}{3} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{g}}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)\nonumber\\
+%& -\frac{2}{3}T(F) n_f \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{q}}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) + 4T(F)n_f \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{q}}^2}{\mu2} \right)m_{\tilde{q}}^2 g^{\mu\nu} \nonumber\\
+%&-\frac{1}{6} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) + C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)m_{\phi^0}^2 g^{\mu\nu} \nonumber\\
+%&\left.-\frac{1}{6} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) + C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu2} \right)m_{\phi^0}^2 g^{\mu\nu}\right]\nonumber\\
+i\Gamma^{\mathrm{1L,heavy}}_{G_\mu^a G_\nu^b}(p^2 = 0)&= i\frac{g_s^2}{16\pi^2}\delta_{ab} \left[ - 4 T(F)n_f \left( \Delta_\epsilon - \ln \frac{m_{\tilde{q}}^2}{\mu^2} \right)m_{\tilde{q}}^2 g^{\mu\nu} - C(A) \left( \Delta_\epsilon - \ln \frac{m_{\phi^0}^2}{\mu^2} \right)m_{\phi^0}^2 g^{\mu\nu} \right.\nonumber\\
+&- C(A) \left( \Delta_\epsilon - \ln \frac{m_{\sigma^0}^2}{\mu^2} \right)m_{\sigma^0}^2 g^{\mu\nu} - \frac{4}{3}T(F)\left( \Delta_\epsilon - \ln \frac{m_t^2}{\mu^2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)\nonumber\\
+& - \frac{4}{3} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\tilde{g}}^2}{\mu^2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)\nonumber\\
+& -\frac{2}{3}T(F) n_f \left( \Delta_\epsilon - \ln \frac{m_{\tilde{q}}^2}{\mu^2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) + 4T(F)n_f \left( \Delta_\epsilon - \ln \frac{m_{\tilde{q}}^2}{\mu^2} \right)m_{\tilde{q}}^2 g^{\mu\nu} \nonumber\\
+&-\frac{1}{6} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\phi^0}^2}{\mu^2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) + C(A) \left( \Delta_\epsilon - \ln \frac{m_{\phi^0}^2}{\mu^2} \right)m_{\phi^0}^2 g^{\mu\nu} \nonumber\\
+&\left.-\frac{1}{6} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\phi^0}^2}{\mu^2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) + C(A) \left( \Delta_\epsilon - \ln \frac{m_{\phi^0}^2}{\mu^2} \right)m_{\phi^0}^2 g^{\mu\nu}\right]\nonumber\\
+&= i\frac{g_s^2}{16\pi^2}\delta_{ab} \left[- \frac{4}{3}T(F)\left( \Delta_\epsilon - \ln \frac{m_t^2}{\mu^2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)\right.\nonumber\\
+& - \frac{4}{3} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\tilde{g}}^2}{\mu^2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)\nonumber\\
+& -\frac{2}{3}T(F) n_f \left( \Delta_\epsilon - \ln \frac{m_{\tilde{q}}^2}{\mu^2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) \nonumber\\
+&-\frac{1}{6} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\phi^0}^2}{\mu^2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)  \nonumber\\
+&\left.-\frac{1}{6} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\phi^0}^2}{\mu^2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) \right]
 \end{align}
@@
 \begin{align}
-\delta Z^{aux}_G &= \frac{g_s^2}{16\pi^2} \left\{\left[-\frac{4}{3}T(F)(n_f-1) + \frac{5}{3} C(A) \right] \frac{1}{\epsilon_{\mathrm{UV}}} + \left[ - \frac{4}{3}T(F) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_t^2}{\mu^2} \right)  \right.\right.\nonumber\\
-&- \frac{4}{3} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{g}}^2}{\mu^2} \right) -\frac{2}{3}T(F) n_f \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\tilde{q}}^2}{\mu^2} \right)\nonumber\\
-& - \frac{1}{6} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\phi^0}^2}{\mu^2} \right) - \frac{1}{6} C(A) \left( \frac{1}{\epsilon_{\mathrm{UV}}} - \ln \frac{m_{\sigma^0}^2}{\mu^2} \right).
+\delta Z^{aux}_G &= \frac{g_s^2}{16\pi^2} \left\{\left[-\frac{4}{3}T(F)(n_f-1) + \frac{5}{3} C(A) \right] \Delta_\epsilon + \left[ - \frac{4}{3}T(F) \left( \Delta_\epsilon - \ln \frac{m_t^2}{\mu^2} \right)  \right.\right.\nonumber\\
+&- \frac{4}{3} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\tilde{g}}^2}{\mu^2} \right) -\frac{2}{3}T(F) n_f \left( \Delta_\epsilon - \ln \frac{m_{\tilde{q}}^2}{\mu^2} \right)\nonumber\\
+& - \frac{1}{6} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\phi^0}^2}{\mu^2} \right) - \frac{1}{6} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\sigma^0}^2}{\mu^2} \right).
 \end{align}
@@
 \begin{align}
-i\Gamma^{\mathrm{1L,heavy}}_{q_i \overline{q}_j G_\mu^a}(p_i^2=0) = - -g_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} &\left[ \left(C(F) -\frac{C(A)}{2}\right) 4C_{00}(0, 0, m_{\tilde{g}}^2, m_{\tilde{q}}^2, m_{\tilde{q}}^2) \right.\nonumber\\
-&+ \left. C(A)\left( B_0(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2) -2C_{00}(0, 0, m_{\tilde{g}}^2, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\right) \right]
+i\Gamma^{\mathrm{1L,heavy}}_{q_i \overline{q}_j G_\mu^a}(p_i^2=0) &= -ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} \left[ \left(C(F) -\frac{C(A)}{2}\right) 4C_{00}(0, 0, m_{\tilde{g}}^2, m_{\tilde{q}}^2, m_{\tilde{q}}^2) \right.\nonumber\\
+&\hspace{3.3cm} + \left. C(A)\left( B_0(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2) -2C_{00}(0, 0, m_{\tilde{g}}^2, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\right) \right]\nonumber\\
+&= -ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} \left[ \left(C(F) -\frac{C(A)}{2}\right) \left( \Delta_\epsilon - \ln \frac{m_{\tilde{g}}^2}{\mu^2} \right) \right.\nonumber\\
+&\hspace{3.3cm} + \left.\frac{C(A)}{2} \left( \Delta_\epsilon - \ln \frac{m_{\tilde{g}}^2}{\mu^2} \right) \right]
 \end{align}
-The argument $p_i^2=0$ of the vertex function denotes, that all external particles are taken on shell, i.e. at zero momentum.
-The sum of the 1-loop corrections and the counterterm should be set to zero:
+The argument $p_i^2=0$ of the vertex function denotes, that all external particles are taken on shell, i.e.
+at zero momentum.
+In the second line identities from \ref{sec:Passarino} have been used.
+The renormalization condition for the counterterm of the gauge coupling $\delta g_s$ reads
 \begin{align}

### 2016-05-14 TreeLevel.tex
mainly Tree Level Plots

--- 2016-03-04 TreeLevel.tex
@@
-\section{Sparticle Production at Tree Level}
+\section{Squark and Gluino Production at Tree Level}
+In this chapter the production of strongly interacting supersymmetric particles\footnote{The production of sgluons is excluded from the analysis for their mass is chosen to be too large to significantly produce them.} in the MRSSM is considered.
+The various processes and their associated cross section is compared to their analogues in the MSSM.
 
@@
 \begin{center}
-\begin{tikzpicture}[line width=1.0 pt, scale=1.3]
+\begin{tikzpicture}[line width=1.0 pt, scale=1.3, arrow/.style={thick,->,shorten >=2pt,shorten <=2pt,>=stealth}]
 	\draw[fermion] (-1,0.5)--(-0.42,0);
@@
 	\draw[scalarbar] (0.42,0)--(1,-0.5);
+	\draw[arrow] (-1,0.7)--(-0.5,0.26);
+	\node at (-0.75,0.8) {$k_a$};
+	\draw[arrow] (-1,-0.7)--(-0.5,-0.26);
+	\node at (-0.75,-0.8) {$k_b$};
+	\draw[arrow] (0.5,0.26)--(1,0.7);
+	\node at (0.75,0.8) {$p_1$};
+	\draw[arrow] (0.5,-0.26)--(1,-0.7);
+	\node at (0.75,-0.8) {$p_2$};
 \begin{scope}[shift={(3,0)}]
@@
 	\draw[gluon] (-1,-0.5)--(0,-0.5);
-	\draw[gluon] (0,0.5)--(0,-0.5);
-	\draw[fermionnoarrow] (0,0.5)--(0,-0.5);
+	\draw[scalar] (0,0.5)--(0,-0.5);
 	\draw[gluon] (0,0.5)--(0.4,0.1);
@@
 \end{scope}
+\end{scope}
 \end{tikzpicture}
-\caption{Tree level diagrams for $qG \to \tilde{q}\tilde{g}$}
+\caption{Tree level diagrams for squark and gluino production at tree level in the MRSSM.
+The processes $GG \to \tilde{q}\overline{\tilde{q}}$ and $qG \to \tilde{q}\tilde{g}$ are identical to those in the MSSM.
+The processes $q\overline{q} \to \tilde{q}\overline{\tilde{q}}$ and $qq \to \tilde{q}\tilde{q}$ involve the production of less chiralities than in the MSSM.
+Also in the $q\tilde{q} \to \tilde{g}\overline{\tilde{g}}$ channel only half of the t-channel squark chiralities occur in the MRSSM.
+(Anti-)Gluino production via initial gluons $GG \to \tilde{g}\overline{\tilde{g}}$ proceeds via the same diagrams like in the MSSM but its cross section is twice as much in the MRSSM for gluino and antigluino are distinguishable particles.}\label{fig:TreeDiagrams}
 \end{center}
 \end{figure}
-The top quark is excluded from the initial states as it is too heavy to be significantly present in hadrons.
-Therefore its pdf is approximately zero.
+For the calculation the top quark is excluded from the initial state as it is too heavy to be significantly present in hadrons. %Therefore its pdf is approximately zero. 
 For consistency reasons also the stop is excluded from the final states.
 One therefore deals with $n_f-1 = 5$ quark flavors.
-Using the Feynman rules in the Appendix one obtains the following sums over absolute squared Feynman amplitudes
+Using the Feynman rules in the Appendix one obtains the following sums over absolute squared Feynman amplitudes.
 \begin{align}
@@
 \end{align}
-For NLO-corrections the results are expanded up to $\mathcal{O}(\epsilon)$. Furthermore the usual Mandelstam variables $s,t,u$ and the following modifications of them are used:
+In view of the renormalization to be performed at the 1-loop level the results are given in $D = 4 - 2\epsilon$ dimensions and it has been distinguished between the gauge coupling $g_s$ from the gluon-quark-quark vertex and its supersymmetric analogue $\hat{g}_s$ from the gluino-squark-quark vertex.
+The usual Mandelstam variables $s,t,u$ and the following modifications of them are used\footnote{The kinematics of the process is like denoted in fig.
+\ref{fig:TreeDiagrams}.}
 \begin{align}
+& s = (k_a + k_b)^2 = (p_1 + p_2)^2\nonumber\\
+& t = (k_a - p_1)^2 = (k_b - p_2)^2\nonumber\\
+& u = (k_a - p_2)^2 = (k_a - p_2)^2\nonumber\\
 & t_{\tilde{g}} = t - m_{\tilde{g}}^2 && t_{\tilde{q}} = t- m_{\tilde{q}}^2\nonumber\\
@@
 \subsection{Partonic Cross Sections}
+Having calculated the absolute squared Feynman amplitudes one obtains the partonic cross sections (see Appendix \ref{sec:cross_section}) via
+\begin{align}
+\frac{\mbox{d}^2 \sigma^B}{\mbox{d}t\ \mbox{d}u} =& \frac{K_{ab}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_1^2m_2^2}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_1^2m_2^2)\nonumber\\
+&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum |\mathcal{M}^B|^2
+\end{align}
 The leading order cross sections are
 \begin{align}
-\sigma(q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij}  \frac{g_s^4}{16\pi s} (n_f-1) \left[ \frac{4}{27} - \frac{16 m_{\tilde{q}}^2}{27s} \right]\nonumber\\
+\sigma^B(q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij}  \frac{g_s^4}{16\pi s} (n_f-1) \left[ \frac{4}{27} - \frac{16 m_{\tilde{q}}^2}{27s} \right]\nonumber\\
 &+ \delta_{ij} \frac{g_s^2\hat{g}_s^2}{16\pi s}  \left[ \left( \frac{4}{27} + \frac{8 m_-^2}{27 s} \right)\beta_{\tilde{q}}  + \left( \frac{8m_{\tilde{g}}^2}{27s} + \frac{8m_-^4}{27s^2} \right)L_1 \right]\nonumber\\
 & + \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} + \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
-\sigma(GG \to \tilde{q}\tilde{q}^\dagger) &= \frac{(n_f-1) g_s^4}{16\pi s} \left[ \left(\frac{5}{24} + \frac{31 m_{\tilde{q}}^2}{12s}\right)\beta_{\tilde{q}} + \left( \frac{4m_{\tilde{q}}^2}{3s} + \frac{m_{\tilde{q}}^4}{3s^2} \right) \ln \frac{1-\beta_{\tilde{q}}}{1+\beta_{\tilde{q}}} \right]\\
-\sigma(q_i q_j \to \tilde{q}\tilde{q}) &= \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} +  \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
-\sigma(q \overline{q} \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \frac{16}{9} + \frac{32m_{\tilde{g}}^2}{9s} \right] \beta_{\tilde{g}}\nonumber\\
+\sigma^B(GG \to \tilde{q}\tilde{q}^\dagger) &= \frac{(n_f-1) g_s^4}{16\pi s} \left[ \left(\frac{5}{24} + \frac{31 m_{\tilde{q}}^2}{12s}\right)\beta_{\tilde{q}} + \left( \frac{4m_{\tilde{q}}^2}{3s} + \frac{m_{\tilde{q}}^4}{3s^2} \right) \ln \frac{1-\beta_{\tilde{q}}}{1+\beta_{\tilde{q}}} \right]\\
+\sigma^B(q_i q_j \to \tilde{q}\tilde{q}) &= \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} +  \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
+\sigma^B(q \overline{q} \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \frac{16}{9} + \frac{32m_{\tilde{g}}^2}{9s} \right] \beta_{\tilde{g}}\nonumber\\
 & + \frac{\hat{g}_s^2 g_s^2}{16\pi s}  \left[ \left( -\frac{4}{3}-\frac{8m_-^2}{3s} \right)\beta_{\tilde{g}} + \left( \frac{8 m_{\tilde{g}}^2}{3s} + \frac{8m_-^4}{3s^2} \right) L_2 \right]\nonumber\\
-& + \frac{\hat{g}_s^4}{16\pi s} \left[ \left( \frac{32}{27} + \frac{32 m_-^4}{m_-^4 + m_{\tilde{q}}^2s} \right)\beta_{\tilde{g}} - \frac{64m_-^2}{27s}L_2 \right]\label{eq:qqbar_to_sgsgbar}\\
-\sigma(GG \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \left( -6 - \frac{51 m_{\tilde{g}}^2}{2s} \right)\beta_{\tilde{g}} + \left( -\frac{9}{2} - \frac{18 m_{\tilde{g}}^2}{s} + \frac{18 m_{\tilde{g}}^4}{s^2} \right)\ln \frac{1-\beta_{\tilde{g}}}{1+\beta_{\tilde{g}}} \right]\\
-\sigma(q G \to \tilde{q} \tilde{g}) &= \frac{g_s^2\hat{g}_s^2}{16\pi s} \left[ \frac{\kappa}{s}\left( -\frac{7}{9} - \frac{32 m_{-}^2}{9s} \right) + \left( -\frac{8m_-^2}{9s} + \frac{2m_{\tilde{q}}^2m_-^2}{s^2} + \frac{8 m_-^4}{9s^2} \right)L_3\right.\nonumber\\
+& + \frac{\hat{g}_s^4}{16\pi s} \left[ \left( \frac{32}{27} + \frac{32 m_-^4}{27(m_-^4 + m_{\tilde{q}}^2s)} \right)\beta_{\tilde{g}} - \frac{64m_-^2}{27s}L_2 \right]\label{eq:qqbar_to_sgsgbar}\\
+\sigma^B(GG \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \left( -6 - \frac{51 m_{\tilde{g}}^2}{2s} \right)\beta_{\tilde{g}} + \left( -\frac{9}{2} - \frac{18 m_{\tilde{g}}^2}{s} + \frac{18 m_{\tilde{g}}^4}{s^2} \right)\ln \frac{1-\beta_{\tilde{g}}}{1+\beta_{\tilde{g}}} \right]\\
+\sigma^B(q G \to \tilde{q} \tilde{g}) &= \frac{g_s^2\hat{g}_s^2}{16\pi s} \left[ \frac{\kappa}{s}\left( -\frac{7}{9} - \frac{32 m_{-}^2}{9s} \right) + \left( -\frac{8m_-^2}{9s} + \frac{2m_{\tilde{q}}^2m_-^2}{s^2} + \frac{8 m_-^4}{9s^2} \right)L_3\right.\nonumber\\
 &+\left. \left( -1-\frac{2m_-^2}{s} + \frac{2m_{\tilde{q}}m_-^2}{s^2} \right)L_4 \right]
@@
 are used\cite{Beenakker:1996ch}.
-In contrast to the MSSM no statistical factor $\frac{1}{2}$ is taken into account for gluino-antigluino production, as these particles are distinguishable in the MRSSM.
-Still in comparison to the MSSM cross section for the channel $q \overline{q} \to \tilde{g}\overline{\tilde{g}}$ only the first line in \ref{eq:qqbar_to_sgsgbar} is doubled up as the part associated with an $t$ ($u$) channel squark is different.
-In the MRSSM either $\tilde{q}_L$ or $\tilde{q}_R$ is allowed whilst in the MSSM both squarks contribute to the $t$ ($u$) channel diagram.
+
+\subsubsection*{The process $q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger$}
+The production of a squark and an antisquark through a quark and an antiquark in the initial state origins from two diagrams.
+The first one with an $s$-channel gluon is the same in MSSM and MRSSM whereas the second one exhibits a difference due to the gluino which is no Majorana particle in the MRSSM.
+As the consequence contributions from this diagram are suppressed in comparison to the MSSM.
+One can also think of the difference as a result of the conservation of R-charge.
+As left handed squarks have R-charge +1 they must be produced with a right handed squark which carries R-charge -1 in order to meet the total R-charge of 0 zero in the initial state.
+
+\subsubsection*{The process $GG \to \tilde{q}\tilde{q}^\dagger$}
+This process has the same cross section in the MRSSM and in the MSSM for also in the MSSM only like chirality squark and antisquark $\tilde{q}_A\tilde{q}_A^\dagger$ with $A \in {L,R}$ can be produced
+
+\subsubsection*{The process $q_i q_j \to \tilde{q}\tilde{q}$}
+In the MRSSM only the production of unlike chirality squarks $\tilde{q}_L + \tilde{q}_R$ is allowed whilst in the MSSM also like chirality squarks can be produced.
+This is again a consequence of the conservation of R-charge.
+The upshot of this is a suppression of squark production in the MRSSM in comparison to the MSSM.
+To be more explicit the suppression of squark production in the MRSSM grows with the gluino mass.
+This can be understood as follows: As in the MRSSM a left handed squark needs to be produced with a right handed squark one can read off from the Feynman rules given in Appendix ???
+that the gluino propagator $i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2}$ is sandwiched between the projectors $P_L$ and $P_R$ which leads to the cancellation of the gluino mass in the numerator.
+Therefore for small momenta of the gluino one gets for $\mathcal{M}$ a $\sim \frac{1}{m_{\tilde{g}}^2}$ suppression in the MRSSM while in the MSSM one finds a $\frac{1}{m_{\tilde{g}}}$ suppression.\\
+Furthermore because of the absence of chirality like squarks in the final state in the MRSSM the cross section of flavor like and unlike squarks is the same, i.e.
+on the partonic level $\sigma^B(\tilde{u}_L\tilde{u}_R) = \sigma^B(\tilde{u}_L\tilde{d}_R)$.
+That is however not true in the MSSM.
+
+\subsubsection*{The process $q \overline{q} \to \tilde{g}\overline{\tilde{g}}$}
+In contrast to the MSSM no statistical factor of $\frac{1}{2}$ is taken into account when turning from $|\mathcal{M}|^2$ to $\sigma$.
+This is because gluino and antigluino are distinguishable particles.
+Still in comparison to the MSSM cross section only the first line in \ref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines origin from an $t$ or $u$ channel squark which occurs in only one instead of two chiralities.
+Furthermore an interference term from the $t$ or $u$ channel diagram which occurs in the MSSM is absent in the MRSSM.
+% this interference term causes a huge difference, that's been checked by Philip via Madgraph
+
+\subsubsection*{The process $GG \to \tilde{g}\overline{\tilde{g}}$}
+As in the previous process the MRSSM cross section for $GG \to \tilde{g}\overline{\tilde{g}}$ receives no statistical factor of $\frac{1}{2}$.
+As there are no further differences between MSSM and MRSSM in this channel, the MRSSM cross section is simply twice as large as in the MSSM.
+
+\subsubsection*{The process $q G \to \tilde{q} \tilde{g}$}
+This process is exactly the same in the MSSM and MRSSM.
 
 \subsection{Hadronic Cross Section}
-factorization (pictorial explanation in factorization paper chapter 1.4)
+factorization (pictorial explanation in factorization paper chapter 1.4 and Dissertori and Seymour, Marx page 24 below)\\
 The hadronic cross section for the production of a final state $X$, e.g.
-$X = \tilde{q},\tilde{q}$, can be obtained by convolving the partonic cross section with the parton density function of the initial partons.
+$X = \tilde{q} \tilde{q}$, can be obtained by convolving the partonic cross section with the parton density function of the initial partons.
 \begin{align}
-\sigma^B(ij \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_i(x_1) f_j(x_2)\ \sigma^B (ij \to X, s = x_ 1x_2 S).
+\sigma^B_{\mathrm{Had}}(ij \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_i(x_1) f_j(x_2)\ \sigma^B_{\mathrm{Part}} (ij \to X, s = x_ 1x_2 S).
 \end{align}
@@
 \begin{align}
-\sigma^B(H_1 H_2 \to X) = \sum_{i,j} \sigma^B(i,j \to X).
+\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(i,j \to X).
 \end{align}
+To get an intuitive idea of the factorization consider the hadrons as extended objects consisting of partons\footnote{The proton is considered as composed of three valence quarks: Two up-quarks and one down-quark.
+In addition there are gluons and seaquarks, i.e.
+virtual quark-antiquark pairs.} which are permanently interacting which each other.
+Now consider two colliding hadrons in their center-of-mass frame.
+Due to Lorentz contraction the hadrons appear as thin discs.
+Furthermore the parton's mutual interactions are time-delayed.
+This effectively means that a hadron at the time of collision is virtually frozen.\\
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.45]{figures/MRSSM:q+q->sq+sq_mr=2_seperated}
+\caption{Hadronic cross section for squark production in the MRSSM at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
+The ratio of gluino and squark mass is fixed to 1.5.
+The parton densities used are $\mathtt{MMHT2014}$ LO with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}.
+As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}
+\end{center}
+\end{figure}
+refer to paper in Peskin on how to get pdf's
+\\
 refer to Kribs, Martin
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.4]{figures/mr=0,9_MSSM+MRSSM}
+\includegraphics[scale=.4]{figures/mr=2_MSSM+MRSSM}
+\caption{Hadronic cross section for squark and gluino production in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
+The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row).
+In the final state it has been summed over all squark flavors expect for staus.
+For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
+The parton densities used are $\mathtt{MMHT2014}$ LO with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}.
+As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}
+\end{center}
+\end{figure}
+
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.45]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
+\includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
+\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
+The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row).
+In the final state it has been summed over all squark flavors expect for staus.
+For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
+The parton densities and the renormalization and factorization scale are chosen as in fig.
+\ref{fig:TreeXsection}.}
+\end{center}
+\end{figure}
+
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.4]{figures/mr=5_MSSM+MRSSM}
+\includegraphics[scale=.45]{figures/rel_weights_mr=5_MSSM+MRSSM}
+\caption{Hadronic cross section for squark and gluino production (in the first row) and relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
+The ratio of gluino and squark mass is fixed to 5.
+In the final state it has been summed over all squark flavors expect for staus.
+For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
+The parton densities and the renormalization and factorization scale are chosen as in fig.
+\ref{fig:TreeXsection}.}
+\end{center}
+\end{figure}
+
+discussion of channels, maybe copy from above\\
+refer to Vernoica Sanz: How many SUpersymmetries?
+
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.6]{figures/contour_MRSSM_squarks}
+\caption{}
+\end{center}
+\end{figure}

### 2016-05-14 Virt_Real.tex
mainly Tree Level Plots

\section{Virtual and Real Corrections}
This section describes the necessary steps in the calculation of the squark production cross section at next-to-leading-order. The $\mathcal{O}(\alpha_s)$ correction to the tree level process includes the computation of one-loop diagrams such as shown in fig. ???. To yield $\mathcal{O}(\alpha_s)$ corrections in the cross section the interference term between the one-loop amplitude $\mathcal{M}^{\mathrm{1L}}$ and the Born amplitude $\mathcal{M}^{\mathrm{B}}$ needs to be considered. However the virtual amplitude 
\begin{align}
\mathcal{M}^{\mathrm{V}} = \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} + \mathcal{M}^{\mathrm{1L}} \mathcal{M}^{\mathrm{B}\ast} = 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right)
\end{align}
contains divergences. These come from integrals over undetermined momentum and energy of particles running in loops. Due to their origin these divergences are referred to as ultraviolet and infrared divergences.
Ultraviolet divergences occur when the loop momentum tends to infinity which corresponds to arbitrary short distance interactions. However, these divergences are cured by first regularizing them and then introducing appropriate counterterms in the Lagrangian to cancel the extracted singularities. The second step is called renormalization and can be understood as a redefinition or rescaling of parameters and fields in the Lagrangian in the first place. This procedure will be discussed in detail in section \label{sec:renMRSSM}.\\
Having removed the ultraviolet divergences one performs the 2-body phase space integration to arrive at the cross section. However, this is not finite as it comprises infrared divergences. These split into soft and collinear (or mass) singularities\footnote{The names differ in the literature. Often infrared divergences are used as a synonym for soft divergences.} which cannot be removed by means of renormalization.

Naunberg

\subsection{Virtual Correction}

### 2016-05-14 figures/Contour_Plots/MRSSM_TreeLevel.py

@@ -1,0 +1,72 @@
+# -*- coding: utf-8 -*-
+"""
+plot of cross section as contour with squark and gluino mass as axis
+"""
+
+from matplotlib import pyplot as plt
+import numpy as np
+from matplotlib.colors import LogNorm
+
+                          
+def nans(shape, dtype=float):
+    """grid of shape full nan"""
+    a = np.empty(shape, dtype)
+    a.fill(np.nan)
+    return a
+
+# grid size
+N = 50 
+
+def contourdata():
+    """
+    
+    """
+    mass = np.linspace(100, 2000, num=N)
+    mass = np.linspace(100, 2000, num=N)
+    # note reverse ordering for yi and xi because of the way   
+    # shape works in numpy                                                  
+    sigma = nans((len(mass),len(mass)))  
+    myfile = open('qq_to_sqsq_MRSSM_with_antiquarks.tex', 'r')     
+    i = 0
+    for line in myfile:
+        data = line.split()
+        for j in range(0,N):
+            sigma[j][i] = data[j]
+        i += 1   
+    myfile.close()
+    
+    fig = plt.figure(1,figsize=(9, 8)) 
+    ax1 = plt.axes()
+    font_size = 18
+    plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
+    plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
+    plt.xticks(fontsize = font_size)
+    plt.yticks(fontsize = font_size)
+    cf=ax1.contourf(mass, mass, sigma, norm = LogNorm())
+    levels1 = [0.1, 1, 10**3, 10**4, 10**5, 10**6]
+    cl1 = plt.contour(cf, levels=levels1,
+                  colors='k',
+                  linewidths=(1,),
+                  hold='on')    
+    levels2 = [10,100]
+    cl2 = plt.contour(cf, levels=levels2,
+                  colors='k',
+                  linewidths=(2,),
+                  hold='on')
+    levels3 = [20,50]
+    cl3 = plt.contour(cf, levels=levels3,
+                  colors='k',
+                  linestyles='dashed',
+                  linewidths=(1,),
+                  hold='on')
+    plt.clabel(cl2, fmt='%2.1f', colors='k', fontsize = font_size)
+    plt.clabel(cl3, fmt='%2.1f', colors='k', fontsize = font_size)
[…]

### 2016-05-14 figures/Contour_Plots/MSSM_TreeLevel.py

@@ -1,0 +1,72 @@
+# -*- coding: utf-8 -*-
+"""
+plot of cross section as contour with squark and gluino mass as axis
+"""
+
+from matplotlib import pyplot as plt
+import numpy as np
+from matplotlib.colors import LogNorm
+
+                          
+def nans(shape, dtype=float):
+    """grid of shape full nan"""
+    a = np.empty(shape, dtype)
+    a.fill(np.nan)
+    return a
+
+# grid size
+N = 50 
+
+def contourdata():
+    """
+    
+    """
+    mass = np.linspace(100, 2000, num=N)
+    mass = np.linspace(100, 2000, num=N)
+    # note reverse ordering for yi and xi because of the way   
+    # shape works in numpy                                                  
+    sigma = nans((len(mass),len(mass)))  
+    myfile = open('qq_to_sqsq_MSSM_with_antiquarks.tex', 'r')     
+    i = 0
+    for line in myfile:
+        data = line.split()
+        for j in range(0,N):
+            sigma[j][i] = data[j]
+        i += 1   
+    myfile.close()
+    
+    fig = plt.figure(1,figsize=(9, 8)) 
+    ax1 = plt.axes()
+    font_size = 18
+    plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
+    plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
+    plt.xticks(fontsize = font_size)
+    plt.yticks(fontsize = font_size)
+    cf=ax1.contourf(mass, mass, sigma, norm = LogNorm())
+    levels1 = [0.1, 1, 10**3, 10**4, 10**5, 10**6]
+    cl1 = plt.contour(cf, levels=levels1,
+                  colors='k',
+                  linewidths=(1,),
+                  hold='on')    
+    levels2 = [10,100]
+    cl2 = plt.contour(cf, levels=levels2,
+                  colors='k',
+                  linewidths=(2,),
+                  hold='on')
+    levels3 = [20,50]
+    cl3 = plt.contour(cf, levels=levels3,
+                  colors='k',
+                  linestyles='dashed',
+                  linewidths=(1,),
+                  hold='on')
+    plt.clabel(cl2, fmt='%2.1f', colors='k', fontsize = font_size)
+    plt.clabel(cl3, fmt='%2.1f', colors='k', fontsize = font_size)
[…]

### 2016-05-14 figures/WARB_TreeLevel/MRSSM:q+q->sq+sq_seperated/MRSSM_q+q->sq+sq_mr=2_seperated.py

@@ -1,0 +1,136 @@
+# -*- coding: utf-8 -*-
+"""
+C++ code on laptop in WARB-talk
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_squark = np.array([], dtype=float);
+sigma_dd = np.array([], dtype=float);
+sigma_dd_C = np.array([], dtype=float); # charged conjugated cross section
+sigma_du = np.array([], dtype=float);
+sigma_du_C = np.array([], dtype=float);
+sigma_ds = np.array([], dtype=float);
+sigma_ds_C = np.array([], dtype=float);
+sigma_dc = np.array([], dtype=float);
+sigma_dc_C = np.array([], dtype=float);
+sigma_db = np.array([], dtype=float);
+sigma_db_C = np.array([], dtype=float);
+
+sigma_uu = np.array([], dtype=float);
+sigma_uu_C = np.array([], dtype=float);
+sigma_us = np.array([], dtype=float);
+sigma_us_C = np.array([], dtype=float);
+sigma_uc = np.array([], dtype=float);
+sigma_uc_C = np.array([], dtype=float);
+sigma_ub = np.array([], dtype=float);
+sigma_ub_C = np.array([], dtype=float);
+
+sigma_ss = np.array([], dtype=float);
+sigma_ss_C = np.array([], dtype=float);
+sigma_sc = np.array([], dtype=float);
+sigma_sc_C = np.array([], dtype=float);
+sigma_sb = np.array([], dtype=float);
+sigma_sb_C = np.array([], dtype=float);
+
+sigma_cc = np.array([], dtype=float);
+sigma_cc_C = np.array([], dtype=float);
+sigma_cb = np.array([], dtype=float);
+sigma_cb_C = np.array([], dtype=float);
+
+sigma_bb = np.array([], dtype=float);
+sigma_bb_C = np.array([], dtype=float);
+
+f = open('had_cros_MRSSM_q+q->sq+sq_mr=2.txt', 'r')
+discard = f.readline()
+
+for lines in f.readlines():
+    m_squark = np.append(m_squark, float(lines.split()[0]))
[…]

### 2016-05-14 figures/WARB_TreeLevel/MSSM+MRSSM_mr=0,9.py

@@ -1,0 +1,429 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Dec  9 14:21:19 2015
+
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_squark = np.array([], dtype=float);
+# arrays for 1st parton reaction
+sigma1_MSSM_dd = np.array([], dtype=float);
+sigma1_MSSM_du = np.array([], dtype=float);
+sigma1_MSSM_ds = np.array([], dtype=float);
+sigma1_MSSM_dc = np.array([], dtype=float);
+sigma1_MSSM_db = np.array([], dtype=float);
+
+sigma1_MSSM_uu = np.array([], dtype=float);
+sigma1_MSSM_us = np.array([], dtype=float);
+sigma1_MSSM_uc = np.array([], dtype=float);
+sigma1_MSSM_ub = np.array([], dtype=float);
+
+sigma1_MSSM_ss = np.array([], dtype=float);
+sigma1_MSSM_sc = np.array([], dtype=float);
+sigma1_MSSM_sb = np.array([], dtype=float);
+
+sigma1_MSSM_cc = np.array([], dtype=float);
+sigma1_MSSM_cb = np.array([], dtype=float);
+
+sigma1_MSSM_bb = np.array([], dtype=float);
+# arrays for 2nd parton reaction
+sigma2_MSSM = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MSSM_dd = np.array([], dtype=float);
+sigma3_MSSM_du = np.array([], dtype=float);
+sigma3_MSSM_ds = np.array([], dtype=float);
+sigma3_MSSM_dc = np.array([], dtype=float);
+sigma3_MSSM_db = np.array([], dtype=float);
+
+sigma3_MSSM_uu = np.array([], dtype=float);
+sigma3_MSSM_us = np.array([], dtype=float);
+sigma3_MSSM_uc = np.array([], dtype=float);
+sigma3_MSSM_ub = np.array([], dtype=float);
+
+sigma3_MSSM_ss = np.array([], dtype=float);
[…]

### 2016-05-14 figures/WARB_TreeLevel/MSSM+MRSSM_mr=2.py

@@ -1,0 +1,429 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Dec  9 14:21:19 2015
+
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib import colors
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_squark = np.array([], dtype=float);
+# arrays for 1st parton reaction
+sigma1_MSSM_dd = np.array([], dtype=float);
+sigma1_MSSM_du = np.array([], dtype=float);
+sigma1_MSSM_ds = np.array([], dtype=float);
+sigma1_MSSM_dc = np.array([], dtype=float);
+sigma1_MSSM_db = np.array([], dtype=float);
+
+sigma1_MSSM_uu = np.array([], dtype=float);
+sigma1_MSSM_us = np.array([], dtype=float);
+sigma1_MSSM_uc = np.array([], dtype=float);
+sigma1_MSSM_ub = np.array([], dtype=float);
+
+sigma1_MSSM_ss = np.array([], dtype=float);
+sigma1_MSSM_sc = np.array([], dtype=float);
+sigma1_MSSM_sb = np.array([], dtype=float);
+
+sigma1_MSSM_cc = np.array([], dtype=float);
+sigma1_MSSM_cb = np.array([], dtype=float);
+
+sigma1_MSSM_bb = np.array([], dtype=float);
+# arrays for 2nd parton reaction
+sigma2_MSSM = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MSSM_dd = np.array([], dtype=float);
+sigma3_MSSM_du = np.array([], dtype=float);
+sigma3_MSSM_ds = np.array([], dtype=float);
+sigma3_MSSM_dc = np.array([], dtype=float);
+sigma3_MSSM_db = np.array([], dtype=float);
+
+sigma3_MSSM_uu = np.array([], dtype=float);
+sigma3_MSSM_us = np.array([], dtype=float);
+sigma3_MSSM_uc = np.array([], dtype=float);
+sigma3_MSSM_ub = np.array([], dtype=float);
+
[…]

### 2016-05-14 figures/WARB_TreeLevel/MSSM+MRSSM_mr=5.py

@@ -1,0 +1,429 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Dec  9 14:21:19 2015
+
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib import colors
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_squark = np.array([], dtype=float);
+# arrays for 1st parton reaction
+sigma1_MSSM_dd = np.array([], dtype=float);
+sigma1_MSSM_du = np.array([], dtype=float);
+sigma1_MSSM_ds = np.array([], dtype=float);
+sigma1_MSSM_dc = np.array([], dtype=float);
+sigma1_MSSM_db = np.array([], dtype=float);
+
+sigma1_MSSM_uu = np.array([], dtype=float);
+sigma1_MSSM_us = np.array([], dtype=float);
+sigma1_MSSM_uc = np.array([], dtype=float);
+sigma1_MSSM_ub = np.array([], dtype=float);
+
+sigma1_MSSM_ss = np.array([], dtype=float);
+sigma1_MSSM_sc = np.array([], dtype=float);
+sigma1_MSSM_sb = np.array([], dtype=float);
+
+sigma1_MSSM_cc = np.array([], dtype=float);
+sigma1_MSSM_cb = np.array([], dtype=float);
+
+sigma1_MSSM_bb = np.array([], dtype=float);
+# arrays for 2nd parton reaction
+sigma2_MSSM = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MSSM_dd = np.array([], dtype=float);
+sigma3_MSSM_du = np.array([], dtype=float);
+sigma3_MSSM_ds = np.array([], dtype=float);
+sigma3_MSSM_dc = np.array([], dtype=float);
+sigma3_MSSM_db = np.array([], dtype=float);
+
+sigma3_MSSM_uu = np.array([], dtype=float);
+sigma3_MSSM_us = np.array([], dtype=float);
+sigma3_MSSM_uc = np.array([], dtype=float);
+sigma3_MSSM_ub = np.array([], dtype=float);
+
[…]

### 2016-05-14 figures/WARB_TreeLevel/rel_weights_mr=0.9_MSSM+MRSSM.py

@@ -1,0 +1,443 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Dec  9 14:21:19 2015
+
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+def savitzky_golay(y, window_size, order, deriv=0, rate=1):
+    from math import factorial   
+    try:
+       window_size = np.abs(np.int(window_size))
+       order = np.abs(np.int(order))
+    except ValueError, msg:
+        raise ValueError("window_size and order have to be of type int")
+    if window_size % 2 != 1 or window_size < 1:
+        raise TypeError("window_size size must be a positive odd number")
+    if window_size < order + 2:
+        raise TypeError("window_size is too small for the polynomials order")
+    order_range = range(order+1)
+    half_window = (window_size -1) // 2
+    # precompute coefficients
+    b = np.mat([[k**i for i in order_range] for k in range(-half_window, half_window+1)])
+    m = np.linalg.pinv(b).A[deriv] * rate**deriv * factorial(deriv)
+    # pad the signal at the extremes with
+    # values taken from the signal itself
+    firstvals = y[0] - np.abs( y[1:half_window+1][::-1] - y[0] )
+    lastvals = y[-1] + np.abs(y[-half_window-1:-1][::-1] - y[-1])
+    y = np.concatenate((firstvals, y, lastvals))
+    return np.convolve( m[::-1], y, mode='valid')
+
+
+
+m_squark = np.array([], dtype=float);
+# MRSSM arrays
+# arrays for 1st parton reaction
+sigma1_MRSSM_dd = np.array([], dtype=float);
+sigma1_MRSSM_du = np.array([], dtype=float);
+sigma1_MRSSM_ds = np.array([], dtype=float);
[…]

### 2016-05-14 figures/WARB_TreeLevel/rel_weights_mr=2_MSSM+MRSSM.py

@@ -1,0 +1,415 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Dec  9 14:21:19 2015
+
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_squark = np.array([], dtype=float);
+# MRSSM arrays
+# arrays for 1st parton reaction
+sigma1_MRSSM_dd = np.array([], dtype=float);
+sigma1_MRSSM_du = np.array([], dtype=float);
+sigma1_MRSSM_ds = np.array([], dtype=float);
+sigma1_MRSSM_dc = np.array([], dtype=float);
+sigma1_MRSSM_db = np.array([], dtype=float);
+
+sigma1_MRSSM_uu = np.array([], dtype=float);
+sigma1_MRSSM_us = np.array([], dtype=float);
+sigma1_MRSSM_uc = np.array([], dtype=float);
+sigma1_MRSSM_ub = np.array([], dtype=float);
+
+sigma1_MRSSM_ss = np.array([], dtype=float);
+sigma1_MRSSM_sc = np.array([], dtype=float);
+sigma1_MRSSM_sb = np.array([], dtype=float);
+
+sigma1_MRSSM_cc = np.array([], dtype=float);
+sigma1_MRSSM_cb = np.array([], dtype=float);
+
+sigma1_MRSSM_bb = np.array([], dtype=float);
+# arrays for 2nd parton reaction
+sigma2_MRSSM = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MRSSM_dd = np.array([], dtype=float);
+sigma3_MRSSM_du = np.array([], dtype=float);
+sigma3_MRSSM_ds = np.array([], dtype=float);
+sigma3_MRSSM_dc = np.array([], dtype=float);
+sigma3_MRSSM_db = np.array([], dtype=float);
+
+sigma3_MRSSM_uu = np.array([], dtype=float);
+sigma3_MRSSM_us = np.array([], dtype=float);
+sigma3_MRSSM_uc = np.array([], dtype=float);
+sigma3_MRSSM_ub = np.array([], dtype=float);
+
[…]

### 2016-05-14 figures/WARB_TreeLevel/rel_weights_mr=5_MSSM+MRSSM.py

@@ -1,0 +1,415 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Dec  9 14:21:19 2015
+
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_squark = np.array([], dtype=float);
+# MRSSM arrays
+# arrays for 1st parton reaction
+sigma1_MRSSM_dd = np.array([], dtype=float);
+sigma1_MRSSM_du = np.array([], dtype=float);
+sigma1_MRSSM_ds = np.array([], dtype=float);
+sigma1_MRSSM_dc = np.array([], dtype=float);
+sigma1_MRSSM_db = np.array([], dtype=float);
+
+sigma1_MRSSM_uu = np.array([], dtype=float);
+sigma1_MRSSM_us = np.array([], dtype=float);
+sigma1_MRSSM_uc = np.array([], dtype=float);
+sigma1_MRSSM_ub = np.array([], dtype=float);
+
+sigma1_MRSSM_ss = np.array([], dtype=float);
+sigma1_MRSSM_sc = np.array([], dtype=float);
+sigma1_MRSSM_sb = np.array([], dtype=float);
+
+sigma1_MRSSM_cc = np.array([], dtype=float);
+sigma1_MRSSM_cb = np.array([], dtype=float);
+
+sigma1_MRSSM_bb = np.array([], dtype=float);
+# arrays for 2nd parton reaction
+sigma2_MRSSM = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MRSSM_dd = np.array([], dtype=float);
+sigma3_MRSSM_du = np.array([], dtype=float);
+sigma3_MRSSM_ds = np.array([], dtype=float);
+sigma3_MRSSM_dc = np.array([], dtype=float);
+sigma3_MRSSM_db = np.array([], dtype=float);
+
+sigma3_MRSSM_uu = np.array([], dtype=float);
+sigma3_MRSSM_us = np.array([], dtype=float);
+sigma3_MRSSM_uc = np.array([], dtype=float);
+sigma3_MRSSM_ub = np.array([], dtype=float);
+
[…]

### 2016-05-23 NLO.tex
new plots

@@
 \section{Squark Production at One-Loop}
+
+\subsection{The LSZ-Theorem}
+
+\subsection{The Cross Section in the Limit of High Sgluon Masses}
 The cross section for squark production does not exist in the limit of an infinitely large sgluon mass, instead it was found that it diverges logarithmically.\\
@@
 In this case the decoupling theorem \cite{Appelquist:1974tg} does no longer hold.\\
-Refer to super oblique correction and quantify difference of $g$ and $\hat{g}$ from eq 4 in \cite{Cheng:1997sq}
+Refer to super oblique correction and quantify difference of $g$ and $\hat{g}$ from eq 4 in \cite{Cheng:1997sq}\\
+append plot

### 2016-05-23 RSymmetry.tex
mainly Tree Level Plots
new plots

@@
 
-\subsection{The Minimal R-symmetric Supersymmetric Standard Model}
+\subsection{The Minimal R-Symmetric Supersymmetric Standard Model}
 The MSSM with additional R-symmetry is called minimal R-symmetric supersymmetric standard model (MRSSM).
@@
 \end{align}
+Maybe refer to mixed Majorana/Dirac gauginos, Mass matrix for spinors\\
 In order to get a R-symmetric mass term on has to choose the R-charge of the new Weyl-spinor $\chi$ to be the opposite of $\lambda$.\\
@@
 
-\subsection{The R-symmetric supersymmetric Quantumchromodynacis}
+\subsection{The R-Symmetric Supersymmetric Quantum Chromodynamcis}
 The subject of this thesis is the phenomenology of the strongly coupling sector of the MRSSM.
@@
 Observe that there is no 3 sgluon vertex, because of the antisymmetry of the structure constants $f^{abc}$.
+Add relation of slguon masses: $m_{\sigma^0}^2 = m_{\phi^0}^2 + 4 m_{\tilde{g}}$ and table of particle content of RSQCD
 \newpage

### 2016-05-23 Renormalization.tex
new plots

@@
 
-\subsubsection{The Quark Self-Energy}
+\subsubsection*{The Quark Self-Energy}
 The quark self-energy splits into contribution from the SM as well as a supersymmetric analogue which is already present in the MSSM.
@@
 
-\subsubsection{The Squark Self-Energy}
+\subsubsection*{The Squark Self-Energy}
 The contributions to the self-energy of the left- and right-handed squark are the same.
@@
 
-\subsubsection{The Glunio Self-Energy}
+\subsubsection*{The Glunio Self-Energy}
 The 4-spinor of the gluino comprises two Weyl spinors which describe very different particles.
@@
 
-\subsubsection{The Quark Self-Energy Revisited}
+\subsubsection*{The Quark Self-Energy Revisited}
 The quark self-energy has two contribution which are shown in figure \ref{fig:QuarkSelfEnergy}.
@@
 
-\subsubsection{The Gluon Self-Energy}
+\subsubsection*{The Gluon Self-Energy}
 As for the quark self-energy there are again contributions to the self-energy originating from light and heavy particles. Again these are differently dealt with.
@@
 
-\subsubsection{The $q\overline{q}G$ Vertex Correction}
+\subsubsection*{The $q\overline{q}G$ Vertex Correction}
 As for the self energies the vertex correction constitutes of loops from light particles which correspond to the Standard Model and additional heavy particle loops.
@@
 
-\subsubsection{The Beta Function}
+\subsection{The Beta Function}
 The beta function describes the dependence of the gauge coupling $g_s$ upon the energy scale $\mu$.\\
@@
 \begin{align}
-g_{sB} = \mu^\epsilon g_s \left( 1 + \frac{\delta g_s}{g_s} \right)
+g_{sB}(g_s, \mu) = \mu^\epsilon g_s \left( 1 + \frac{\delta g_s}{g_s} \right)
 \end{align}

### 2016-05-23 TreeLevel.tex
new plots

@@
 \end{align}
-where the abbreviations 
+where the abbreviations \cite{Beenakker:1996ch} 
 \begin{align}
@@
 \end{align}
-are used\cite{Beenakker:1996ch}.
-
-\subsubsection*{The process $q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger$}
-The production of a squark and an antisquark through a quark and an antiquark in the initial state origins from two diagrams.
-The first one with an $s$-channel gluon is the same in MSSM and MRSSM whereas the second one exhibits a difference due to the gluino which is no Majorana particle in the MRSSM.
-As the consequence contributions from this diagram are suppressed in comparison to the MSSM.
-One can also think of the difference as a result of the conservation of R-charge.
-As left handed squarks have R-charge +1 they must be produced with a right handed squark which carries R-charge -1 in order to meet the total R-charge of 0 zero in the initial state.
-
-\subsubsection*{The process $GG \to \tilde{q}\tilde{q}^\dagger$}
-This process has the same cross section in the MRSSM and in the MSSM for also in the MSSM only like chirality squark and antisquark $\tilde{q}_A\tilde{q}_A^\dagger$ with $A \in {L,R}$ can be produced
-
-\subsubsection*{The process $q_i q_j \to \tilde{q}\tilde{q}$}
-In the MRSSM only the production of unlike chirality squarks $\tilde{q}_L + \tilde{q}_R$ is allowed whilst in the MSSM also like chirality squarks can be produced.
-This is again a consequence of the conservation of R-charge.
-The upshot of this is a suppression of squark production in the MRSSM in comparison to the MSSM.
-To be more explicit the suppression of squark production in the MRSSM grows with the gluino mass.
-This can be understood as follows: As in the MRSSM a left handed squark needs to be produced with a right handed squark one can read off from the Feynman rules given in Appendix ???
-that the gluino propagator $i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2}$ is sandwiched between the projectors $P_L$ and $P_R$ which leads to the cancellation of the gluino mass in the numerator.
-Therefore for small momenta of the gluino one gets for $\mathcal{M}$ a $\sim \frac{1}{m_{\tilde{g}}^2}$ suppression in the MRSSM while in the MSSM one finds a $\frac{1}{m_{\tilde{g}}}$ suppression.\\
-Furthermore because of the absence of chirality like squarks in the final state in the MRSSM the cross section of flavor like and unlike squarks is the same, i.e.
-on the partonic level $\sigma^B(\tilde{u}_L\tilde{u}_R) = \sigma^B(\tilde{u}_L\tilde{d}_R)$.
-That is however not true in the MSSM.
-
-\subsubsection*{The process $q \overline{q} \to \tilde{g}\overline{\tilde{g}}$}
-In contrast to the MSSM no statistical factor of $\frac{1}{2}$ is taken into account when turning from $|\mathcal{M}|^2$ to $\sigma$.
-This is because gluino and antigluino are distinguishable particles.
-Still in comparison to the MSSM cross section only the first line in \ref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines origin from an $t$ or $u$ channel squark which occurs in only one instead of two chiralities.
-Furthermore an interference term from the $t$ or $u$ channel diagram which occurs in the MSSM is absent in the MRSSM.
-% this interference term causes a huge difference, that's been checked by Philip via Madgraph
-
-\subsubsection*{The process $GG \to \tilde{g}\overline{\tilde{g}}$}
-As in the previous process the MRSSM cross section for $GG \to \tilde{g}\overline{\tilde{g}}$ receives no statistical factor of $\frac{1}{2}$.
-As there are no further differences between MSSM and MRSSM in this channel, the MRSSM cross section is simply twice as large as in the MSSM.
-
-\subsubsection*{The process $q G \to \tilde{q} \tilde{g}$}
-This process is exactly the same in the MSSM and MRSSM.
+are used. The comparison of the cross sections of the MRSSM with those of the MSSM is postponed until the next subsection where the confinement of quarks and gluons within hadrons is accounted for.
 
@@
 factorization (pictorial explanation in factorization paper chapter 1.4 and Dissertori and Seymour, Marx page 24 below)\\
-The hadronic cross section for the production of a final state $X$, e.g.
-$X = \tilde{q} \tilde{q}$, can be obtained by convolving the partonic cross section with the parton density function of the initial partons.
+Quarks, anti-quarks and gluons are no free particles but are confined within hadrons.
+As hadrons consist of a variety of the just mentioned partons which share the hadron's momentum one does not have a definite initial state which is assumed in the previous subsection.
+Fortunately the hadronic cross section for the production of a final state $X$, e.g.
+$X = \tilde{q} \tilde{q}$, can be obtained by convolving the partonic cross section with the parton density functions of the initial partons.
 \begin{align}
-\sigma^B_{\mathrm{Had}}(ij \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_i(x_1) f_j(x_2)\ \sigma^B_{\mathrm{Part}} (ij \to X, s = x_ 1x_2 S).
+\sigma^B_{\mathrm{Had}}(P_1 P_2 \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_{P_1/H_1}(x_1) f_{P_2/H_2}(x_2)\ \sigma^B_{\mathrm{Part}} (P_1 P_2 \to X, s = x_ 1x_2 S).
 \end{align}
-As the production of the final state $X$ may proceed with various initial partons one has to sum over all possible possibilities arising from the initial hadrons $H_1$ and $H_2$:
+As the production of the final state $X$ may proceed via various initial partons one has to sum over all possible possibilities arising from the initial hadrons $H_1$ and $H_2$:
 \begin{align}
-\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(i,j \to X).
+\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(P_1 P_2 \to X).
 \end{align}
-To get an intuitive idea of the factorization consider the hadrons as extended objects consisting of partons\footnote{The proton is considered as composed of three valence quarks: Two up-quarks and one down-quark.
+To get an intuitive idea of this factorization consider the hadrons as extended objects consisting of partons\footnote{The proton is considered as composed of three valence quarks: Two up-quarks and one down-quark.
 In addition there are gluons and seaquarks, i.e.
@@
 Now consider two colliding hadrons in their center-of-mass frame.
-Due to Lorentz contraction the hadrons appear as thin discs.
-Furthermore the parton's mutual interactions are time-delayed.
+Due to Lorentz contraction the hadrons appear as thin discs and the parton's mutual interactions are time-delayed within this frame.
 This effectively means that a hadron at the time of collision is virtually frozen.\\
+maybe picture of colliding disks\\
+This in turn implies that the hadron consists at the time of collision of a definite number of partons which can be thought of as carrying a definite fraction of the hadron's momentum $p_{\mathrm{Part}} = x p_{\mathrm{Had}}$ with $x \in \left(0, 1 \right)$.
+The parton density function $f_{P/H}(x)$ can therefore be understood as the probability of finding a parton $P$ within the hadron $H$ carrying $x$ of its momentum.
+See ...(refer to paper in Peskin on how to get pdf's)...
+for how to ascertain parton density functions\\
+Fig.
+...
+shows a parton density function set for the proton.
+One can see that the partons most probable to carry a high fraction of momentum are the valence quarks.
+For lower values of $x$ gluons constitute the major component of the proton.\\
 \begin{figure}[!htpb]
@@
 \end{figure}
-refer to paper in Peskin on how to get pdf's
-\\
+Fig.\ref{fig:TreeXsection} shows the hadronic cross section for the production of various squarks.
+These can only be produced by their supersymmetric partner, e.g.
+two up-squarks can only be produced by two up-quarks.
+One therefore sees the influence of the parton distribution functions quite nicely: The up-squark production is the dominant contribution to squark production.
+Apart from the solid lines in fig.\ref{fig:TreeXsection} which correspond to the production of first generation squarks, also the cross section of mixed first and second generation (dashed lines) and second generation squarks is shown.
+The dashed dotted line shows the cross section of the charged conjugated particles of the dominant channel.\\
 refer to Kribs, Martin
@@
 
-discussion of channels, maybe copy from above\\
+\subsubsection*{The process $q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger$}
+The production of a squark and an antisquark through a quark and an antiquark in the initial state origins from two diagrams.
+The first one with an $s$-channel gluon is the same in MSSM and MRSSM whereas the second one exhibits a difference due to the gluino which is no Majorana particle in the MRSSM.
+As the consequence contributions from this diagram are suppressed in comparison to the MSSM.
+One can also think of the difference as a result of the conservation of R-charge.
+As left handed squarks have R-charge +1 they must be produced with a right handed squark which carries R-charge -1 in order to meet the total R-charge of 0 zero in the initial state.
+
+\subsubsection*{The process $GG \to \tilde{q}\tilde{q}^\dagger$}
+This process has the same cross section in the MRSSM and in the MSSM for also in the MSSM only like chirality squark and antisquark $\tilde{q}_A\tilde{q}_A^\dagger$ with $A \in {L,R}$ can be produced
+
+\subsubsection*{The process $q_i q_j \to \tilde{q}\tilde{q}$}
+In the MRSSM only the production of unlike chirality squarks $\tilde{q}_L + \tilde{q}_R$ is allowed whilst in the MSSM also like chirality squarks can be produced.
+This is again a consequence of the conservation of R-charge.
+The upshot of this is a suppression of squark production in the MRSSM in comparison to the MSSM.
+To be more explicit the suppression of squark production in the MRSSM grows with the gluino mass.
+This can be understood as follows: As in the MRSSM a left handed squark needs to be produced with a right handed squark one can read off from the Feynman rules given in Appendix ???
+that the gluino propagator $i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2}$ is sandwiched between the projectors $P_L$ and $P_R$ which leads to the cancellation of the gluino mass in the numerator.
+Therefore for small momenta of the gluino one gets for $\mathcal{M}$ a $\sim \frac{1}{m_{\tilde{g}}^2}$ suppression in the MRSSM while in the MSSM one finds a $\frac{1}{m_{\tilde{g}}}$ suppression.\\
+Furthermore because of the absence of chirality like squarks in the final state in the MRSSM the cross section of flavor like and unlike squarks is the same, i.e.
+on the partonic level $\sigma^B(\tilde{u}_L\tilde{u}_R) = \sigma^B(\tilde{u}_L\tilde{d}_R)$.
+That is however not true in the MSSM.
+
+\subsubsection*{The process $q \overline{q} \to \tilde{g}\overline{\tilde{g}}$}
+In contrast to the MSSM no statistical factor of $\frac{1}{2}$ is taken into account when turning from $|\mathcal{M}|^2$ to $\sigma$.
+This is because gluino and antigluino are distinguishable particles.
+Still in comparison to the MSSM cross section only the first line in \ref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines origin from an $t$ or $u$ channel squark which occurs in only one instead of two chiralities.
+Furthermore an interference term from the $t$ or $u$ channel diagram which occurs in the MSSM is absent in the MRSSM.
+% this interference term causes a huge difference, that's been checked by Philip via Madgraph
+
+\subsubsection*{The process $GG \to \tilde{g}\overline{\tilde{g}}$}
+As in the previous process the MRSSM cross section for $GG \to \tilde{g}\overline{\tilde{g}}$ receives no statistical factor of $\frac{1}{2}$.
+As there are no further differences between MSSM and MRSSM in this channel, the MRSSM cross section is simply twice as large as in the MSSM.
+
+\subsubsection*{The process $q G \to \tilde{q} \tilde{g}$}
+This process is exactly the same in the MSSM and MRSSM.
+\\
 refer to Vernoica Sanz: How many SUpersymmetries?
@@
 \includegraphics[scale=.6]{figures/contour_MRSSM_squarks}
+\includegraphics[scale=.6]{figures/contour_MSSM_squarks}
 \caption{}
@@
 \end{figure}
+
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.5]{figures/MSSM+MRSSM_msg=2000}
+\includegraphics[scale=.5]{figures/MSSM+MRSSM_msq=1000}
+\caption{add error bars}
+\end{center}
+\end{figure}

### 2016-05-23 Virt_Real.tex
new plots

@@
 \section{Virtual and Real Corrections}
-This section describes the necessary steps in the calculation of the squark production cross section at next-to-leading-order.
-The $\mathcal{O}(\alpha_s)$ correction to the tree level process includes the computation of one-loop diagrams such as shown in fig.
+The results calculated in the previous chapter are not the full theoretical predictions for the different processes but only the first term in a perturbation theory of $\alpha_s$.\\
+This section describes the necessary steps in the calculation of the squark production cross section at next-to-leading-order, i.e. its $\mathcal{O}(\alpha_s)$-correction.\\
+Reason validity of perturbation theory in this context.
+
+\subsection{Virtual Correction}
+According to quantum field theory the $\mathcal{O}(\alpha_s)$ correction to a tree level process includes the computation of one-loop diagrams such as shown in fig.
 ???.
@@
 Due to their origin these divergences are referred to as ultraviolet and infrared divergences.
-Ultraviolet divergences occur when the loop momentum tends to infinity which corresponds to arbitrary short distance interactions.
-However, these divergences are cured by first regularizing them and then introducing appropriate counterterms in the Lagrangian to cancel the extracted singularities.
-The second step is called renormalization and can be understood as a redefinition or rescaling of parameters and fields in the Lagrangian in the first place.
+Ultraviolet divergences occur when the loop momenta and energy tend to infinity which corresponds to arbitrary short distance interactions.
+However, these divergences are cured by first regularizing them and then introducing appropriate counterterms\footnote{These counterterms have to be of the same $\mathcal{O}(\hbar)$ as the loop diagrams they are constructed to cancel.
+NOCHMAL IN LAHIRI / PAL NACHSCHAUEN.} in the Lagrangian to cancel the extracted singularities.
+The second step is called renormalization and can be understood as a redefinition or rescaling of parameters and fields in the Lagrangian in the first place:
+\begin{align}
+\tilde{q}_{L/R} \to \sqrt{Z_{\tilde{q}_{L/R}}} \tilde{q}_{L/R}\\
+...
+\end{align}
 This procedure will be discussed in detail in section \label{sec:renMRSSM}.\\
-Having removed the ultraviolet divergences one performs the 2-body phase space integration to arrive at the cross section.
-However, this is not finite as it comprises infrared divergences.
+Having removed the ultraviolet divergences one performs the 2-body phase space integration to arrive at an ultraviolet-finite cross section.
+However, this cross section is not free of divergences as it comprises infrared divergences.
 These split into soft and collinear (or mass) singularities\footnote{The names differ in the literature.
@@
 
-Naunberg
-
-\subsection{Virtual Correction}
+\subsection{Real Corrections}
+Kinoshita-Lee-Naunberg-Theorem\\
+At the end: scheme of real and virtual corrections from WARB-talk

### 2016-05-23 figures/Contour_Plots/MRSSM_TreeLevel.py

@@ -62,7 +62,7 @@ def contourdata():
     plt.clabel(cl2, fmt='%2.1f', colors='k', fontsize = font_size)
     plt.clabel(cl3, fmt='%2.1f', colors='k', fontsize = font_size)
     cbar = fig.colorbar(cf, orientation='horizontal')
-    cbar.ax.set_xlabel(r'$\sigma(qq \to \tilde{q}\tilde{q})$ in fb', size = font_size)
+    cbar.ax.set_xlabel(r'$\sigma^{\mathrm{B}}_{\mathrm{MRSSM}}(qq \to \tilde{q}\tilde{q})$ in fb', size = font_size)
     cbar.ax.tick_params(labelsize=font_size)
     cbar.add_lines(cl1)
     cbar.add_lines(cl2, erase=False)

### 2016-05-23 figures/Contour_Plots/MSSM_TreeLevel.py

@@ -62,7 +62,7 @@ def contourdata():
     plt.clabel(cl2, fmt='%2.1f', colors='k', fontsize = font_size)
     plt.clabel(cl3, fmt='%2.1f', colors='k', fontsize = font_size)
     cbar = fig.colorbar(cf, orientation='horizontal')
-    cbar.ax.set_xlabel(r'$\sigma(qq \to \tilde{q}\tilde{q})$ in fb', size = font_size)
+    cbar.ax.set_xlabel(r'$\sigma^{\mathrm{B}}_{\mathrm{MSSM}}(qq \to \tilde{q}\tilde{q})$ in fb', size = font_size)
     cbar.ax.tick_params(labelsize=font_size)
     cbar.add_lines(cl1)
     cbar.add_lines(cl2, erase=False)

### 2016-05-23 figures/WARB_TreeLevel/MSSM+MRSSM_mr=0,9.py

@@ -353,17 +353,17 @@ f_MRSSM6.close()
 sigma_MRSSM = sigma1_MRSSM+sigma2_MRSSM+sigma3_MRSSM+sigma4_MRSSM+sigma5_MRSSM+sigma6_MRSSM
 
 
-sigma_min = 10**(-5)
-sigma_max = 10**(5)
+sigma_min = 10**(-2)
+sigma_max = 10**(8)
 
 fig = plt.figure(1,figsize=(17, 9))
 #fig.suptitle(r'LO cross-sections for sparticle production at the LHC at $\sqrt{s}=13$TeV', fontsize=25)
 
 
 first_window = plt.subplot(121)
-plt.title("MSSM", size = 22)
+#plt.title("MSSM", size = 22)
 plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = 22)
-plt.ylabel(r"$\sigma_{MSSM}$ in pb", size = 22)
+plt.ylabel(r"$\sigma^{\mathrm{B}}_{\mathrm{MSSM}}$ in fb", size = 22)
 plt.xticks(fontsize = 20)
 plt.yticks(fontsize = 20)
 
@@ -376,26 +376,26 @@ plt.axes(first_window)
 
 first_window.xaxis.set_major_formatter(FormatStrFormatter('%0.0f'))
 
-plt.plot(m_squark, sigma1_MSSM, lw=2, ls="--", c='orange', label = r"$q\overline{q} \to \tilde{q}\tilde{q}^\dagger$")
-plt.plot(m_squark, sigma2_MSSM, lw=2, ls="--", c='red', label = r"$GG \to \tilde{q}\tilde{q}^\dagger$")
-plt.plot(m_squark, sigma3_MSSM, lw=2, ls="-", c='green', label = r"$qq \to \tilde{q}\tilde{q}$")
-plt.plot(m_squark, sigma4_MSSM, lw=2, ls=":", c='deepskyblue', label = r"$q\overline{q} \to \tilde{g}\tilde{g}$")
-plt.plot(m_squark, sigma5_MSSM, lw=2, ls=":", c='darkblue', label = r"$GG \to \tilde{g}\tilde{g}$")
-plt.plot(m_squark, sigma6_MSSM, lw=2, ls="-.", c='black', label = r"$qG \to \tilde{q}\tilde{g}$")
[…]

### 2016-05-23 figures/WARB_TreeLevel/MSSM+MRSSM_mr=2.py

@@ -354,17 +354,17 @@ f_MRSSM6.close()
 sigma_MRSSM = sigma1_MRSSM+sigma2_MRSSM+sigma3_MRSSM+sigma4_MRSSM+sigma5_MRSSM+sigma6_MRSSM
 
 
-sigma_min = 10**(-5)
-sigma_max = 10**(5)
+sigma_min = 10**(-2)
+sigma_max = 10**(8)
 
 fig = plt.figure(1,figsize=(17, 9))
 #fig.suptitle(r'LO cross-sections for sparticle production at the LHC at $\sqrt{s}=13$TeV', fontsize=25)
 
 
 first_window = plt.subplot(121)
-plt.title("MSSM", size = 22)
+#plt.title("MSSM", size = 22)
 plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = 22)
-plt.ylabel(r"$\sigma_{MSSM}$ in pb", size = 22)
+plt.ylabel(r"$\sigma^{\mathrm{B}}_{\mathrm{MSSM}}$ in fb", size = 22)
 plt.xticks(fontsize = 20)
 plt.yticks(fontsize = 20)
 
@@ -377,26 +377,26 @@ plt.axes(first_window)
 
 first_window.xaxis.set_major_formatter(FormatStrFormatter('%0.0f'))
 
-plt.plot(m_squark, sigma1_MSSM, lw=2, ls="--", c='orange', label = r"$q\overline{q} \to \tilde{q}\tilde{q}^\dagger$")
-plt.plot(m_squark, sigma2_MSSM, lw=2, ls="--", c='red', label = r"$GG \to \tilde{q}\tilde{q}^\dagger$")
-plt.plot(m_squark, sigma3_MSSM, lw=2, ls="-", c='green', label = r"$qq \to \tilde{q}\tilde{q}$")
-plt.plot(m_squark, sigma4_MSSM, lw=2, ls=":", c='deepskyblue', label = r"$q\overline{q} \to \tilde{g}\tilde{g}$")
-plt.plot(m_squark, sigma5_MSSM, lw=2, ls=":", c='darkblue', label = r"$GG \to \tilde{g}\tilde{g}$")
-plt.plot(m_squark, sigma6_MSSM, lw=2, ls="-.", c='black', label = r"$qG \to \tilde{q}\tilde{g}$")
[…]

### 2016-05-23 figures/WARB_TreeLevel/MSSM+MRSSM_mr=5.py

@@ -354,17 +354,17 @@ f_MRSSM6.close()
 sigma_MRSSM = sigma1_MRSSM+sigma2_MRSSM+sigma3_MRSSM+sigma4_MRSSM+sigma5_MRSSM+sigma6_MRSSM
 
 
-sigma_min = 10**(-5)
-sigma_max = 10**(5)
+sigma_min = 10**(-2)
+sigma_max = 10**(8)
 
 fig = plt.figure(1,figsize=(17, 9))
 #fig.suptitle(r'LO cross-sections for sparticle production at the LHC at $\sqrt{s}=13$TeV', fontsize=25)
 
 
 first_window = plt.subplot(121)
-plt.title("MSSM", size = 22)
+#plt.title("MSSM", size = 22)
 plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = 22)
-plt.ylabel(r"$\sigma_{MSSM}$ in pb", size = 22)
+plt.ylabel(r"$\sigma^{\mathrm{B}}_{\mathrm{MSSM}}$ in fb", size = 22)
 plt.xticks(fontsize = 20)
 plt.yticks(fontsize = 20)
 
@@ -377,26 +377,26 @@ plt.axes(first_window)
 
 first_window.xaxis.set_major_formatter(FormatStrFormatter('%0.0f'))
 
-plt.plot(m_squark, sigma1_MSSM, lw=2, ls="--", c='orange', label = r"$q\overline{q} \to \tilde{q}\tilde{q}^\dagger$")
-plt.plot(m_squark, sigma2_MSSM, lw=2, ls="--", c='red', label = r"$GG \to \tilde{q}\tilde{q}^\dagger$")
-plt.plot(m_squark, sigma3_MSSM, lw=2, ls="-", c='green', label = r"$qq \to \tilde{q}\tilde{q}$")
-plt.plot(m_squark, sigma4_MSSM, lw=2, ls=":", c='deepskyblue', label = r"$q\overline{q} \to \tilde{g}\tilde{g}$")
-plt.plot(m_squark, sigma5_MSSM, lw=2, ls=":", c='darkblue', label = r"$GG \to \tilde{g}\tilde{g}$")
-plt.plot(m_squark, sigma6_MSSM, lw=2, ls="-.", c='black', label = r"$qG \to \tilde{q}\tilde{g}$")
[…]

### 2016-05-23 figures/WARB_TreeLevel/q+q->sq+sq_fixed_msg_and_msq/MSSM+MRSSM_msg=2000GeV.py

@@ -1,0 +1,180 @@
+# -*- coding: utf-8 -*-
+"""
+C++ code on laptop in WARB-talk
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_squark = np.array([], dtype=float);
+# arrays for MSSM
+sigma3_MSSM_dd = np.array([], dtype=float);
+sigma3_MSSM_du = np.array([], dtype=float);
+sigma3_MSSM_ds = np.array([], dtype=float);
+sigma3_MSSM_dc = np.array([], dtype=float);
+sigma3_MSSM_db = np.array([], dtype=float);
+
+sigma3_MSSM_uu = np.array([], dtype=float);
+sigma3_MSSM_us = np.array([], dtype=float);
+sigma3_MSSM_uc = np.array([], dtype=float);
+sigma3_MSSM_ub = np.array([], dtype=float);
+
+sigma3_MSSM_ss = np.array([], dtype=float);
+sigma3_MSSM_sc = np.array([], dtype=float);
+sigma3_MSSM_sb = np.array([], dtype=float);
+
+sigma3_MSSM_cc = np.array([], dtype=float);
+sigma3_MSSM_cb = np.array([], dtype=float);
+
+sigma3_MSSM_bb = np.array([], dtype=float);
+
+# arrays for MRSSM
+sigma3_MRSSM_dd = np.array([], dtype=float);
+sigma3_MRSSM_du = np.array([], dtype=float);
+sigma3_MRSSM_ds = np.array([], dtype=float);
+sigma3_MRSSM_dc = np.array([], dtype=float);
+sigma3_MRSSM_db = np.array([], dtype=float);
+
+sigma3_MRSSM_uu = np.array([], dtype=float);
+sigma3_MRSSM_us = np.array([], dtype=float);
+sigma3_MRSSM_uc = np.array([], dtype=float);
+sigma3_MRSSM_ub = np.array([], dtype=float);
+
+sigma3_MRSSM_ss = np.array([], dtype=float);
+sigma3_MRSSM_sc = np.array([], dtype=float);
+sigma3_MRSSM_sb = np.array([], dtype=float);
+
[…]

### 2016-05-23 figures/WARB_TreeLevel/q+q->sq+sq_fixed_msg_and_msq/MSSM+MRSSM_msq=1000GeV.py

@@ -1,0 +1,152 @@
+# -*- coding: utf-8 -*-
+"""
+code on laptop in WARB-talk
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_gluino = np.array([], dtype=float);
+# arrays for MSSM
+sigma3_MSSM_dd = np.array([], dtype=float);
+sigma3_MSSM_du = np.array([], dtype=float);
+sigma3_MSSM_ds = np.array([], dtype=float);
+sigma3_MSSM_dc = np.array([], dtype=float);
+sigma3_MSSM_db = np.array([], dtype=float);
+
+sigma3_MSSM_uu = np.array([], dtype=float);
+sigma3_MSSM_us = np.array([], dtype=float);
+sigma3_MSSM_uc = np.array([], dtype=float);
+sigma3_MSSM_ub = np.array([], dtype=float);
+
+sigma3_MSSM_ss = np.array([], dtype=float);
+sigma3_MSSM_sc = np.array([], dtype=float);
+sigma3_MSSM_sb = np.array([], dtype=float);
+
+sigma3_MSSM_cc = np.array([], dtype=float);
+sigma3_MSSM_cb = np.array([], dtype=float);
+
+sigma3_MSSM_bb = np.array([], dtype=float);
+
+# arrays for MRSSM
+sigma3_MRSSM_dd = np.array([], dtype=float);
+sigma3_MRSSM_du = np.array([], dtype=float);
+sigma3_MRSSM_ds = np.array([], dtype=float);
+sigma3_MRSSM_dc = np.array([], dtype=float);
+sigma3_MRSSM_db = np.array([], dtype=float);
+
+sigma3_MRSSM_uu = np.array([], dtype=float);
+sigma3_MRSSM_us = np.array([], dtype=float);
+sigma3_MRSSM_uc = np.array([], dtype=float);
+sigma3_MRSSM_ub = np.array([], dtype=float);
+
+sigma3_MRSSM_ss = np.array([], dtype=float);
+sigma3_MRSSM_sc = np.array([], dtype=float);
+sigma3_MRSSM_sb = np.array([], dtype=float);
+
[…]

### 2016-05-25 NLO.tex
LSZ-Theorem

@@
 
-\subsection{The LSZ-Theorem}
+\subsection{The LSZ Theorem}\label{sec:LSZ}
+The LSZ theorem\cite{Lehmann:1954rq} or LSZ reduction formula prescribes how to obtain the S-matrix element, i.e.
+a physical observable, from the time ordered correlation function of the respective field operators.
+The time ordered correlation function of fields in an interacting theory can be calculated perturbatively with the aid of the Gell-Mann and Low theorem and the Wick theorem.
+\\
+Considering a physical process with kinematics $\vec{k}_1 \hdots \vec{k}_n \to \vec{p}_1 \hdots \vec{p}_m$ and taking for the sake of simplicity only one scalar field $\phi$ the Fourier transform of the time ordered product of a correlation function is related to the corresponding S-matrix element like\footnote{In this subsection the $\sim$ indicates that the poles on either side are the same provided that all momenta are close to their mass shell, i.e.
+$p_i^0 \to E_{\vec{p}_i}$ and $k_j^0 \to E_{\vec{k}_j}$.}
+\begin{align}
+\prod_{i=1}^n \int \mathrm{d}x_i\ \mathrm{e}^{ip_i x_i} \prod_{j=1}^m \int \mathrm{d}y_j\ \mathrm{e}^{ik_j y_j} \left\langle \Omega | \mathcal{T} \left[ \phi(x_1) \hdots \phi(x_n) \phi(y_1) \hdots \phi(y_m) \right] | \Omega\right\rangle \nonumber\\
+\sim \prod_{i=1}^n \frac{i\sqrt{Z}}{p_i^2 - m^2 + i\epsilon} \prod_{j=1}^m \frac{i\sqrt{Z}}{k_j^2 - m^2 + i\epsilon} \left\langle \left.\left.\vec{p}_1 \hdots \vec{p}_n \right| S \right| \vec{k}_1 \hdots \vec{k}_m \right\rangle .\label{eq:LSZ}
+\end{align}
+Here $\mathcal{T}$ denotes the time ordering operator, $\left.| \Omega \right\rangle$ is the ground state of the interacting theory and $\sqrt{Z}$ is the residue of the single particle pole in the two-point function
+\begin{align}
+\int \mathrm{d}x\ \mathrm{e}^{ip x} \left\langle \Omega | \mathcal{T} \left[ \phi(x) \phi(0) \right] | \Omega\right\rangle &= \frac{i}{p^2-m_0^2} + \frac{i}{p^2-m_0^2} \left(\frac{i\Sigma(p^2)}{p^2-m_0^2}\right) + \frac{i}{p^2-m_0^2} \left(\frac{\Sigma(p^2)}{p^2-m_0^2}\right)^2 + \hdots\nonumber\\
+&= \frac{i}{p^2 - m_0^2 - \Sigma(p^2)}.\label{eq:propagator}
+\end{align}
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}[line width=2.0 pt, scale=1.3]
+	\draw[fermionnoarrow](180:1)--(180:0.5);	
+	\draw (0,0) circle (.5cm);
+		\begin{scope}
+	    	\clip (0,0) circle (.5cm);
+	    	\foreach \x in {-1.0,-0.9,...,1.0}
+        \draw[line width=1 pt] (\x,-.5) -- (\x+.6,.5);
+	  	\end{scope}
+	\draw[fermionnoarrow](0:0.5)--(0:1);
+	\node at (1.3,0) {=};
+	\draw[fermionnoarrow](0:1.6)--(0:2.6);
+	\node at (2.9,0) {+};
+    \draw[fermionnoarrow](0:3.2)--(0:3.7);	
+	\draw (4.2,0) circle (.5cm);
+	\node at (4.2,0) {1PI};
+	\draw[fermionnoarrow](0:4.7)--(0:5.2);
+	\node at (5.5,0) {+};	
+	\draw[fermionnoarrow](0:5.8)--(0:6.3);	
+	\draw (6.8,0) circle (.5cm);
+	\node at (6.8,0) {1PI};
+	\draw[fermionnoarrow](0:7.3)--(0:7.8);
+	\draw (8.3,0) circle (.5cm);
+	\node at (8.3,0) {1PI};
+	\draw[fermionnoarrow](0:8.8)--(0:9.3);
+	\node at (9.8,0) {+ $\hdots$};
+\end{tikzpicture}
+\caption{Diagrammatic figure of the two-point function of a scalar field: The propagator in an interaction theory can be calculated in a perturbation series in the coupling constant.}\label{fig:fullpropagator}
+\end{center}
+\end{figure}
+The parameter $m_0$ is the tree-level mass and the quantity $-i \Sigma(p^2)$ denotes the sum of all one-particle-irreducible contributions to the particle's self-energy.
+From eq.
+\ref{eq:propagator} one can read off the physical mass $m^2$ of the particle which is associated with the field $\phi$.
+It is determined as the value of $p^2$ where the propagator has a pole, i.e.
+\begin{align}
+\left[ p^2 - m_0^2 - \Sigma(p^2)\right]_{p^2 = m^2} = 0
+\end{align}
+Close to the pole the denominator of eq. \ref{eq:propagator} can by expanded like
+\begin{align}
+p^2 - m_0^2 - \Sigma(p^2) = (p^2 - m^2)\left( 1 - \frac{\partial \Sigma(p^2)}{\partial p^2} \right)_{p^2 = m^2} + \mathcal{O}((p^2 - m^2)^2).
+\end{align}
+The residue of the propagator can therefore be written as 
+\begin{align}
+Z = \left( 1 - \frac{\partial \Sigma(p^2)}{\partial p^2} \right)_{p^2 = m^2}^{-1}.
+\end{align}
+Now considers the full $(n+m)$-point function in scalar theory.
+One can decompose it into an amputated $(n+m)$-point function and "full" propagators like written in eq.
+\ref{eq:propagator} and depicted in fig.
+\ref{fig:fullpropagator}.
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}[line width=2.0 pt, scale=1.3, arrow/.style={thick,->,shorten >=2pt,shorten <=2pt,>=stealth}]
+	\draw (0,0) circle (.75);
+	\node at (0,0) {Amp.};
+	\draw (45:0.75)--(45:1.25);
+	\draw (45:1.75) circle (.5);
+		\begin{scope}[shift={(45:1.75)}]
+	    	\clip (0,0) circle (.5cm);
+	    	\foreach \x in {-1.0,-0.9,...,1.0}
+        \draw[line width=1 pt] (\x,-.5) -- (\x+.6,.5);
+	  	\end{scope}
+	\draw (45:2.25)--(45:2.75);
+	\draw[arrow] (1.768,1.597)--(2.192,2.021);
+	\node at (2.2,1.7){$p_n$};
 
-\subsection{The Cross Section in the Limit of High Sgluon Masses}
+	\draw (135:0.75)--(135:1.25);
+	\draw (135:1.75) circle (.5);
+		\begin{scope}[shift={(135:1.75)}]
+	    	\clip (0,0) circle (.5cm);
+	    	\foreach \x in {-1.0,-0.9,...,1.0}
+        \draw[line width=1 pt] (\x,-.5) -- (\x+.6,.5);
+	  	\end{scope}
+	\draw (135:2.25)--(135:2.75);
+	\draw[arrow] (-1.768,1.597)--(-2.192,2.021);
+	\node at (-2.2,1.7){$p_1$};
+
+	\draw (225:0.75)--(225:1.25);
+	\draw (225:1.75) circle (.5);
+		\begin{scope}[shift={(225:1.75)}]
+	    	\clip (0,0) circle (.5cm);
+	    	\foreach \x in {-1.0,-0.9,...,1.0}
+        \draw[line width=1 pt] (\x,-.5) -- (\x+.6,.5);
+	  	\end{scope}
+	\draw (225:2.25)--(225:2.75);
+	\draw[arrow] (-2.192,-2.021)--(-1.768,-1.597);
+	\node at (-2.2,-1.7){$k_1$};
+
+	\draw (315:0.75)--(315:1.25);
+	\draw (315:1.75) circle (.5);
+		\begin{scope}[shift={(315:1.75)}]
+	    	\clip (0,0) circle (.5cm);
+	    	\foreach \x in {-1.0,-0.9,...,1.0}
+        \draw[line width=1 pt] (\x,-.5) -- (\x+.6,.5);
+	  	\end{scope}
+	\draw (315:2.25)--(315:2.75);
+	\draw[arrow] (2.192,-2.021)--(1.768,-1.597);
+	\node at (2.2,-1.7){$k_m$};
+
+	\draw[fill=black] (80:1.5) circle (.01);
+	\draw[fill=black] (90:1.5) circle (.01);
+	\draw[fill=black] (100:1.5) circle (.01);
+	\draw[fill=black] (-80:1.5) circle (.01);
+	\draw[fill=black] (-90:1.5) circle (.01);
+	\draw[fill=black] (-100:1.5) circle (.01);
+\end{tikzpicture}
+\caption{Diagrammatic figure of a "full" $(n+m)$-point function. Apart from the "full" propagators there is the "full" amputated $(n+m)$-point function}
+\end{center}
+\end{figure}\\
+Inserting the expression
+\begin{align}
+\frac{i}{p^2 - m_0^2 - \Sigma(p^2)} \sim \frac{i Z}{p^2 - m^2}
+\end{align}
+for the full propagators one notices the same singularity as in eq. \ref{eq:LSZ}. If one now compares the coefficients of these poles in eq. \ref{eq:LSZ} one finds
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}[line width=2.0 pt, scale=1.3, arrow/.style={thick,->,shorten >=2pt,shorten <=2pt,>=stealth}]
+	\node at (-4,0) {$\left\langle \left.\left.\vec{p}_1 \hdots \vec{p}_n \right| S \right| \vec{k}_1 \hdots \vec{k}_m \right\rangle =\sqrt{Z}^{n+m} \cdot$};
+	\draw (0,0) circle (.75);
+	\node at (0,0) {Amp.};
+
+	\draw (45:0.75)--(45:1.25);
+	\draw[arrow] (0.768,0.597)--(1.192,1.021);
+	\node at (1.2,0.7){$p_n$};
+
+	\draw (135:0.75)--(135:1.25);
+	\draw[arrow] (-0.768,0.597)--(-1.192,1.021);
+	\node at (-1.2,0.7){$p_1$};
+
+	\draw (225:0.75)--(225:1.25);
+	\draw[arrow] (-1.192,-1.021)--(-0.768,-0.597);
+	\node at (-1.2,-0.7){$k_1$};
+
+	\draw (315:0.75)--(315:1.25);
+	\draw[arrow] (1.192,-1.021)--(0.768,-0.597);
+	\node at (1.2,-0.7){$k_m$};
+
+	\draw[fill=black] (80:1.1) circle (.01);
+	\draw[fill=black] (90:1.1) circle (.01);
+	\draw[fill=black] (100:1.1) circle (.01);
+	\draw[fill=black] (-80:1.1) circle (.01);
+	\draw[fill=black] (-90:1.1) circle (.01);
+	\draw[fill=black] (-100:1.1) circle (.01);
+\end{tikzpicture}
+\end{center}
+\end{figure}\\
+Now it becomes visible why the renormalization in the on-shell scheme
+\begin{align}
+\left.\frac{\partial \Sigma(p^2)}{\partial p^2}\right|_{p^2 = m^2} \stackrel{!}{=} 0
+\end{align}
+introduces no further manipulation when turning from the correlation function to the S-matrix-element because $Z = 1$ in on-shell renormalization.
+Furthermore the on-shell condition for the mass renormalization
+\begin{align}
+\Sigma(p^2)|_{p^2 = m^2} = 0
+\end{align}
+means that the physical mass equals the tree level mass.
+
+\subsection{The Cross Section in the Limit of Large Sgluon Masses}
 The cross section for squark production does not exist in the limit of an infinitely large sgluon mass, instead it was found that it diverges logarithmically.\\

### 2016-05-25 TreeLevel.tex
LSZ-Theorem

@@
 \section{Squark and Gluino Production at Tree Level}
+Comment on sgluon production: which channels, calculate cross section for at least one configuration of masses.\\
 In this chapter the production of strongly interacting supersymmetric particles\footnote{The production of sgluons is excluded from the analysis for their mass is chosen to be too large to significantly produce them.} in the MRSSM is considered.
@@
 The parton density function $f_{P/H}(x)$ can therefore be understood as the probability of finding a parton $P$ within the hadron $H$ carrying $x$ of its momentum.
-See ...(refer to paper in Peskin on how to get pdf's)...
-for how to ascertain parton density functions\\
+See \cite{Brock:1993sz} for how to ascertain parton density functions\\
 Fig.

### 2016-05-25 Virt_Real.tex
LSZ-Theorem

@@
 According to quantum field theory the $\mathcal{O}(\alpha_s)$ correction to a tree level process includes the computation of one-loop diagrams such as shown in fig.
-???.
+\ref{fig:1loopdiagrams}.
 To yield $\mathcal{O}(\alpha_s)$ corrections in the cross section the interference term between the one-loop amplitude $\mathcal{M}^{\mathrm{1L}}$ and the Born amplitude $\mathcal{M}^{\mathrm{B}}$ needs to be considered.
@@
 \end{align}
-contains divergences.
-These come from integrals over undetermined momentum and energy of particles running in loops.
+contains divergences. These come from integrals over undetermined momentum and energy of particles running in loops.
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
+	\draw[fermion](-1.5,1)--(0,1);
+	\draw[scalar](0,1)--(1.5,1);
+	\draw[gluon](0,1)--(0,0.5);
+	\draw[fermionnoarrow](0,1)--(0,0.5);
+	\draw[scalar] (0,0.5) arc (90:-90:.5);
+	\draw[fermion] (0,-0.5) arc (90:-90:-.5);
+	\draw[gluon](0,-1)--(0,-0.5);
+	\draw[fermionnoarrow](0,-1)--(0,-0.5);
+	\draw[fermion](-1.5,-1)--(0,-1);
+	\draw[scalar](0,-1)--(1.5,-1);
+\begin{scope}[shift={(5,0)}]
+	\draw[fermion](-1.5,1)--(0,1);
+	\draw[scalar](0,1)--(1.5,1);
+	\draw[gluon](0,1)--(0,0);
+	\draw[fermionnoarrow](0,1)--(0,0);
+	\draw[fermion](-1.5,-1)--(-0.5,-1);
+	\draw[scalar](-0.5,-1)--(0,0);
+	\draw[fermion](0,0)--(0.5,-1);
+	\draw[gluon](-0.5,-1)--(0.5,-1);
+	\draw[scalar](0.5,-1)--(1.5,-1);
+\end{scope}
+\begin{scope}[shift={(-0.5,-3.5)}]
+	\draw[fermion](-1,1)--(0,1);
+	\draw[gluon](0,1)--(0,-1);
+	\draw[fermionnoarrow](0,1)--(0,-1);
+	\draw[fermion](-1,-1)--(0,-1);
+	\draw[scalar](0,-1)--(1,0);
+	\draw[scalar](0,1)--(1,0);
+	\draw[black,fill=black] (1,0) circle (.03cm);
+	\draw[scalar](1,0)--(2,1);
+	\draw[scalar](1,0)--(2,-1);
+\end{scope}
+\begin{scope}[shift={(5,-3.5)}]
+	\draw[fermion](-1.5,0.5)--(-0.5,0.5);
+	\draw[scalar](-0.5,0.5)--(0.5,0.5);
+	\draw[scalar](0.5,0.5)--(1.5,0.5);
+	\draw[gluon](-0.5,0.5)--(-0.5,-0.5);
+	\draw[fermionnoarrow](-0.5,0.5)--(-0.5,-0.5);
+	\draw[scalarnoarrow](0.5,0.5)--(0.5,-0.5);
+	\draw[fermion](-1.5,-0.5)--(-0.5,-0.5);
+	\draw[scalar](-0.5,-0.5)--(0.5,-0.5);
+	\draw[scalar](0.5,-0.5)--(1.5,-0.5);
+\end{scope}
+\end{tikzpicture}
+\caption{A selection of diagrams contributing to the 1-loop matrix element for squark production.
+Each diagram is a representative of a certain diagram type.
+In the first line an example for a self-energy and a vertex-correction diagram is shown.
+The second line lists typical box-diagrams: a three-point box and a four-point box.}\label{fig:1loopdiagrams}
+\end{center}
+\end{figure}
 Due to their origin these divergences are referred to as ultraviolet and infrared divergences.
@@
 \begin{align}
-\tilde{q}_{L/R} \to \sqrt{Z_{\tilde{q}_{L/R}}} \tilde{q}_{L/R}\\
-...
+& \phi^0 / \sigma^0 \to \sqrt{Z_{\phi^0 / \sigma^0}}\phi^0 / \sigma^0 && \tilde{q}_{L/R} \to \sqrt{Z_{\tilde{q}_{L/R}}}\tilde{q}_{L/R}\nonumber\\
+& P_L \tilde{g} \to \sqrt{Z_{\tilde{g}}^L} P_L \tilde{g} && P_R \tilde{g} \to \sqrt{Z_{\tilde{g}}^R} P_R \tilde{g}\nonumber\\
+& q \to \sqrt{Z_q}q && G_\mu \to \sqrt{Z_G} G_\mu && \\
+& g_s \to g_{s\ \mathrm{bare}} && m_{\tilde{q}}^2 \to m_{\tilde{q}\ \mathrm{bare}}^2\nonumber\\
+&  m_{\sigma}^2 \to m_{\sigma\ \mathrm{bare}}^2 && m_{\tilde{g}} \to m_{\tilde{g}\ \mathrm{bare}}
 \end{align}
-This procedure will be discussed in detail in section \label{sec:renMRSSM}.\\
+This procedure will be discussed in detail in section \ref{sec:renMRSSM} and \ref{sec:LSZ}.\\
 Having removed the ultraviolet divergences one performs the 2-body phase space integration to arrive at an ultraviolet-finite cross section.
@@
 \subsection{Real Corrections}
-Kinoshita-Lee-Naunberg-Theorem\\
+Kinoshita-Lee-Naunberg-Theorem \cite{1962JMP.....3..650K},\cite{PhysRev.133.B1549}\\
 At the end: scheme of real and virtual corrections from WARB-talk

### 2016-05-25 figures/WARB_TreeLevel/q+q->sq+sq_fixed_msg_and_msq/MSSM+MRSSM_msg=2000GeV.py

@@ -52,11 +52,16 @@ sigma3_MRSSM_cb = np.array([], dtype=float);
 
 sigma3_MRSSM_bb = np.array([], dtype=float);
 
-# arrays for errors (all flavors are already summed over)
+# arrays for errors (all flavors are summed over already)
 sigma3_MRSSM_maxPdf = np.array([], dtype=float);
 sigma3_MRSSM_minPdf = np.array([], dtype=float);
 sigma3_MRSSM_maxScale = np.array([], dtype=float);
 sigma3_MRSSM_minScale = np.array([], dtype=float);
+
+sigma3_MSSM_maxPdf = np.array([], dtype=float);
+sigma3_MSSM_minPdf = np.array([], dtype=float);
+sigma3_MSSM_maxScale = np.array([], dtype=float);
+sigma3_MSSM_minScale = np.array([], dtype=float);
 
 
 f_MSSM = open('had_cros_MSSM_q+q->sq+sq_msg=2000GeV.txt', 'r')
@@ -143,6 +148,31 @@ sigma_MRSSM_min = np.sqrt((sigma_MRSSM*10**3 - sigma3_MRSSM_minPdf)**2
 sigma_MRSSM_max = np.sqrt((sigma_MRSSM*10**3 - sigma3_MRSSM_maxPdf)**2
  + (sigma_MRSSM*10**3 - sigma3_MRSSM_maxScale)**2)
 
+f_MSSM_maxPdf = open('Errors/qq_to_sqsq_MSSM_with_antiquarks_maxPdfError_msg=2000GeV.txt', 'r')
+for lines in f_MSSM_maxPdf.readlines():
+    sigma3_MSSM_maxPdf = np.append(sigma3_MSSM_maxPdf, float(lines))
+f_MSSM_maxPdf.close()
+
+f_MSSM_minPdf = open('Errors/qq_to_sqsq_MSSM_with_antiquarks_minPdfError_msg=2000GeV.txt', 'r')
+for lines in f_MSSM_minPdf.readlines():
+    sigma3_MSSM_minPdf = np.append(sigma3_MSSM_minPdf, float(lines))
+f_MSSM_minPdf.close()
+
+f_MSSM_maxScale = open('Errors/qq_to_sqsq_MSSM_with_antiquarks_maxScaleError_msg=2000GeV.txt', 'r')
+for lines in f_MSSM_maxScale.readlines():
[…]

### 2016-05-25 figures/WARB_TreeLevel/q+q->sq+sq_fixed_msg_and_msq/MSSM+MRSSM_msq=1000GeV.py

@@ -52,6 +52,16 @@ sigma3_MRSSM_cb = np.array([], dtype=float);
 
 sigma3_MRSSM_bb = np.array([], dtype=float);
 
+# arrays for errors (all flavors are summed over already)
+sigma3_MRSSM_maxPdf = np.array([], dtype=float);
+sigma3_MRSSM_minPdf = np.array([], dtype=float);
+sigma3_MRSSM_maxScale = np.array([], dtype=float);
+sigma3_MRSSM_minScale = np.array([], dtype=float);
+
+sigma3_MSSM_maxPdf = np.array([], dtype=float);
+sigma3_MSSM_minPdf = np.array([], dtype=float);
+sigma3_MSSM_maxScale = np.array([], dtype=float);
+sigma3_MSSM_minScale = np.array([], dtype=float);
 
 
 
@@ -114,6 +124,57 @@ sigma_MRSSM = sigma3_MRSSM_dd+sigma3_MRSSM_du+sigma3_MRSSM_ds+sigma3_MRSSM_dc+si
 
 f_MRSSM.close()
 
+f_MRSSM_maxPdf = open('Errors/qq_to_sqsq_MRSSM_with_antiquarks_maxPdfError_msq=1000GeV.txt', 'r')
+for lines in f_MRSSM_maxPdf.readlines():
+    sigma3_MRSSM_maxPdf = np.append(sigma3_MRSSM_maxPdf, float(lines))
+f_MRSSM_maxPdf.close()
+
+f_MRSSM_minPdf = open('Errors/qq_to_sqsq_MRSSM_with_antiquarks_minPdfError_msq=1000GeV.txt', 'r')
+for lines in f_MRSSM_minPdf.readlines():
+    sigma3_MRSSM_minPdf = np.append(sigma3_MRSSM_minPdf, float(lines))
+f_MRSSM_minPdf.close()
+
+f_MRSSM_maxScale = open('Errors/qq_to_sqsq_MRSSM_with_antiquarks_maxScaleError_msq=1000GeV.txt', 'r')
+for lines in f_MRSSM_maxScale.readlines():
+    sigma3_MRSSM_maxScale = np.append(sigma3_MRSSM_maxScale, float(lines))
+f_MRSSM_maxScale.close()
+
[…]

### 2016-05-31 Appendix.tex
mainly Tree Level Plots
Auswertung TreeLevelkanaele bis Ende qq to sqsq, noch Bezug nehmen auf hadronischen Wq

@@
 
-\subsection{Feynman rules for the RSQCD}
+\subsection{Feynman rules for the RSQCD}\label{sec:FeynmanRules}
 The following Feynman rules are derived from \ref{eq:L_RSQCD}.
@@
 
-\subsection{Cross section and Phase Space Integration}
+\subsection{Cross section and Phase Space Integration}\label{sec:cross_section}
 Once the Feynman amplitude $\mathcal{M}$ for a $2 \to N$ body scattering\footnote{with kinematics $k_a + k_b \to p_1 + \hdots p_N$} is computed one can calculate physical observables with it.

### 2016-05-31 Renormalization.tex
Auswertung TreeLevelkanaele bis Ende qq to sqsq, noch Bezug nehmen auf hadronischen Wq

@@
 A formal introduction of $\Gamma$ can be found in~\cite{Peskin}.
-In short $\Gamma$ can be viewed as a modification of the classical action $\Gamma_{cl} = \int \mathcal{L}_{cl}$ by quantum effects:
+In short $\Gamma$ can be viewed as a modification of the classical action $\Gamma_{\mathrm{cl}} = \int \mathcal{L}_{\mathrm{cl}}$ by quantum effects:
 \begin{align}
-\Gamma = \Gamma_{cl} + \mathcal{O}(\hbar)
+\Gamma = \Gamma_{\mathrm{cl}} + \mathcal{O}(\hbar)
 \end{align}
@@
 \begin{align}
-\Gamma^{(\leq 1)} \to \Gamma^{(\leq 1)} + \Gamma^{(1),ct}
+\Gamma^{(\leq 1)} \to \Gamma^{(\leq 1)} + \Gamma^{(1),\ \mathrm{ct}}
 \end{align} 
@@
 If one chooses to work with DREG supersymmetry will not be preserved at 1-loop order, i.e.
-$\Gamma^{(\leq 1)}_{DREG}$ is not supersymmetric.
-To maintain supersymmetry invariance of the renormalized effective action the counterterms will not only consist of supersymmetric counterterms $\Gamma^{(1),ct,sym}_{DREG}$ but also of counterterms restoring supersymmetry $\Gamma^{(1),ct,restore}_{DREG}$.
+$\Gamma^{(\leq 1)}_{\mathrm{DREG}}$ is not supersymmetric.
+To maintain supersymmetry invariance of the renormalized effective action the counterterms will not only consist of supersymmetric counterterms $\Gamma^{(1),\ \mathrm{ct,\ sym}}_{\mathrm{DREG}}$ but also of counterterms restoring supersymmetry $\Gamma^{(1),\ \mathrm{ct,\ restore}}_{\mathrm{DREG}}$.
 \begin{align}
-\Gamma^{(1),ct}_{DREG} = \Gamma^{(1),ct,sym}_{DREG} + \Gamma^{(1),ct,restore}_{DREG}
+\Gamma^{(1),\ \mathrm{ct}}_{\mathrm{DREG}} = \Gamma^{(1),\ \mathrm{ct,\ sym}}_{\mathrm{DREG}} + \Gamma^{(1),\ \mathrm{ct,\ restore}}_{\mathrm{DREG}}
 \end{align}
@@
 \begin{align}
-\Gamma^{(\leq 1)}_{DRED} + \Gamma^{(1),ct}_{DRED} \overset{!}{=} \Gamma^{(\leq 1)}_{DREG} + \Gamma^{(1),ct}_{DREG}.
+\Gamma^{(\leq 1)}_{\mathrm{DRED}} + \Gamma^{(1),\ \mathrm{ct}}_{\mathrm{DRED}} \overset{!}{=} \Gamma^{(\leq 1)}_{\mathrm{DREG}} + \Gamma^{(1),\ \mathrm{ct}}_{\mathrm{DREG}}.
 \end{align}
-Setting also the finite terms in $\Gamma^{(1),ct,sym}$ equal in DRED and DREG the choice of the supersymmetry restoring counterterms is fixed by:
+Setting also the finite terms in $\Gamma^{(1),\ \mathrm{ct,\ sym}}$ equal in DRED and DREG the choice of the supersymmetry restoring counterterms is fixed by:
 \begin{align}
@@
 \end{align}
-This is the beta function from QCD first found by [Gross, Politzer, Wil]
+This is the beta function of QCD first found by [Gross, Politzer, Wil]
 

### 2016-05-31 TreeLevel.tex
Auswertung TreeLevelkanaele bis Ende qq to sqsq, noch Bezug nehmen auf hadronischen Wq

@@
 \frac{\mbox{d}^2 \sigma^B}{\mbox{d}t\ \mbox{d}u} =& \frac{K_{ab}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_1^2m_2^2}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_1^2m_2^2)\nonumber\\
-&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum |\mathcal{M}^B|^2
+&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum |\mathcal{M}^B|^2\label{eq:sigma_tree}
 \end{align}
@@
 
-\begin{figure}[!htpb]
+\subsubsection*{The process $q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger$}
+The production of a squark and an antisquark through a quark and an antiquark in the initial state originates from two types of Feynman diagrams.
+The first one has an $s$-channel gluon and is the same in the MSSM and in the MRSSM.
+The second one exhibits a difference due to the $t$-channel gluino which is no Majorana particle in the MRSSM.
+\begin{figure}[!htbp]
 \begin{center}
-\includegraphics[scale=.45]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
-\includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
-\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
-The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row).
-In the final state it has been summed over all squark flavors expect for staus.
-For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
-The parton densities and the renormalization and factorization scale are chosen as in fig.
-\ref{fig:TreeXsection}.}
+\begin{tikzpicture}[line width=1.0 pt, scale=1.3]
+	\draw[fermion] (-1,0.5)--(-0.42,0);
+	\draw[fermionbar] (-1,-0.5)--(-0.42,0);
+	\draw[gluon] (-0.42,0)--(0.42,0); 
+	\draw[scalar] (0.42,0)--(1,0.5);
+	\draw[scalarbar] (0.42,0)--(1,-0.5);
+\begin{scope}[shift={(3,0)}]
+	\draw[fermion] (-1,0.5)--(0,0.5);
+	\draw[fermionbar] (-1,-0.5)--(0,-0.5);
+	\draw[fermionnoarrow] (0,0.5)--(0,-0.5);
+	\draw[gluon] (0,0.5)--(0,-0.5); 
+	\draw[scalar] (0,0.5)--(1,0.5);
+	\draw[scalarbar] (0,-0.5)--(1,-0.5);
+\end{scope}
+\end{tikzpicture}
+\caption{Tree level diagrams for $q\overline{q} \to \tilde{q}\tilde{q}^\dagger$}
 \end{center}
 \end{figure}
-
-\begin{figure}[!htpb]
-\begin{center}
-\includegraphics[scale=.4]{figures/mr=5_MSSM+MRSSM}
-\includegraphics[scale=.45]{figures/rel_weights_mr=5_MSSM+MRSSM}
-\caption{Hadronic cross section for squark and gluino production (in the first row) and relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
-The ratio of gluino and squark mass is fixed to 5.
-In the final state it has been summed over all squark flavors expect for staus.
-For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
-The parton densities and the renormalization and factorization scale are chosen as in fig.
-\ref{fig:TreeXsection}.}
-\end{center}
-\end{figure}
-
-\subsubsection*{The process $q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger$}
-The production of a squark and an antisquark through a quark and an antiquark in the initial state origins from two diagrams.
-The first one with an $s$-channel gluon is the same in MSSM and MRSSM whereas the second one exhibits a difference due to the gluino which is no Majorana particle in the MRSSM.
-As the consequence contributions from this diagram are suppressed in comparison to the MSSM.
-One can also think of the difference as a result of the conservation of R-charge.
-As left handed squarks have R-charge +1 they must be produced with a right handed squark which carries R-charge -1 in order to meet the total R-charge of 0 zero in the initial state.
+To see this one can either just apply the Feynman rules in Appendix \ref{sec:FeynmanRules} or think of the conservation of R-charge: Left handed squarks have R-charge +1 and right handed squarks have R-charge -1.
+Antiparticles have the opposite R-charge of their corresponding particles.
+The final state particles have to meet the total R-charge zero from the initial state.
+Because of this one only has $\tilde{q}_L \overline{\tilde{q}}_L$ and $\tilde{q}_R \overline{\tilde{q}}_R$ as the final states in the MRSSM whereas in the MSSM one actually has four instead of two t-channel diagrams: The corresponding final states are $\tilde{q}_L \overline{\tilde{q}}_L$, $\tilde{q}_R \overline{\tilde{q}}_R$, $\tilde{q}_L \overline{\tilde{q}}_R$ and $\overline{\tilde{q}}_R \tilde{q}_L$.
+Consequently contributions from the $t$-channel diagrams are suppressed in the MRSSM in comparison to the MSSM.
+As visible in fig.
+\ref{fig:TreeXsection} this suppression grows with the masses.
+The reason for this lies in the gluino mass dependence of the $t$-channel diagrams which is explained in the discussion of squark production.\\
+If the initial state quarks are of different flavor the $s$-channel diagram is absent.
 
@@
 \subsubsection*{The process $q_i q_j \to \tilde{q}\tilde{q}$}
-In the MRSSM only the production of unlike chirality squarks $\tilde{q}_L + \tilde{q}_R$ is allowed whilst in the MSSM also like chirality squarks can be produced.
+In the MRSSM only the production of unlike chirality squarks $\tilde{q}_L \tilde{q}_R$ is allowed whilst in the MSSM also like chirality squarks can be produced.
 This is again a consequence of the conservation of R-charge.
@@
 To be more explicit the suppression of squark production in the MRSSM grows with the gluino mass.
-This can be understood as follows: As in the MRSSM a left handed squark needs to be produced with a right handed squark one can read off from the Feynman rules given in Appendix ???
-that the gluino propagator $i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2}$ is sandwiched between the projectors $P_L$ and $P_R$ which leads to the cancellation of the gluino mass in the numerator.
-Therefore for small momenta of the gluino one gets for $\mathcal{M}$ a $\sim \frac{1}{m_{\tilde{g}}^2}$ suppression in the MRSSM while in the MSSM one finds a $\frac{1}{m_{\tilde{g}}}$ suppression.\\
-Furthermore because of the absence of chirality like squarks in the final state in the MRSSM the cross section of flavor like and unlike squarks is the same, i.e.
-on the partonic level $\sigma^B(\tilde{u}_L\tilde{u}_R) = \sigma^B(\tilde{u}_L\tilde{d}_R)$.
+This can be understood as follows: As in the MRSSM a left handed squark needs to be produced with a right handed squark one can read off from the Feynman rules given in Appendix \ref{sec:FeynmanRules} that the gluino propagator $i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2}$ is sandwiched between the projectors $P_L$ and $P_R$ which leads to the cancellation of the gluino mass in the numerator.
+Therefore for small momenta of the gluino compared to the gluino mass one gets $\mathcal{M}$ $\sim \frac{1}{m_{\tilde{g}}^2}$ in the MRSSM while in the MSSM one finds a suppression proportional to $\frac{1}{m_{\tilde{g}}}$.\\
+When considering squark production one has to sum over all $|\mathcal{M}|^2$ with different helicity.
+The diagrams for those different final state helicities are shown for flavor like squark production in tab.
+\ref{tab:squark_likeflavor} and for flavor unlike squark production in tab.
+\ref{tab:squark_unlikeflavor} for the MSSM and the MRSSM.
+To avoid double counting one needs to weight $|\mathcal{M}|^2(qq\to \tilde{q}_L\tilde{q}_L)$ and $|\mathcal{M}|^2(qq\to \tilde{q}_R\tilde{q}_R)$ with a statistical factor of $\frac{1}{2}$ as one integrates over all momenta of both particles to arrive at the cross section.\footnote{Alternatively one could discard the $u$-channel (or $t$-channel) diagram and omit the weighting with $\frac{1}{2}$.}
+\begin{table}[!htpb]
+\begin{center}
+\begin{tabular}{c|c}
+MSSM & MRSSM \\
+\hline
+\begin{tikzpicture}[line width=1.0 pt, scale=0.7]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,0)--(1,0);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[scalar] (1,1)--(2,1);
+	\draw[scalar] (1,0)--(2,0);
+	\node at (-0.2,1) {$u$};
+	\node at (-0.2,0) {$u$};
+	\node at (2.2,1) {$\tilde{u}_L^\dagger$};
+	\node at (2.2,0) {$\tilde{u}_R^\dagger$};
+\begin{scope}[shift={(4,0)}]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,0)--(1,0);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[scalar] (1,1)--(1.5,0.5);
+	\draw[scalar] (1.5,0.5)--(2,0);
+	\draw[scalar] (1,0)--(1.4,0.4);
+	\draw[scalar] (1.6,0.6)--(2,1);
+	\node at (-0.2,1) {$u$};
+	\node at (-0.2,0) {$u$};
+	\node at (2.2,1) {$\tilde{u}_L^\dagger$};
+	\node at (2.2,0) {$\tilde{u}_R^\dagger$};
+\end{scope}
+\begin{scope}[shift={(0,-2)}]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,0)--(1,0);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[scalar] (1,1)--(2,1);
+	\draw[scalar] (1,0)--(2,0);
+	\node at (-0.2,1) {$u$};
+	\node at (-0.2,0) {$u$};
+	\node at (2.2,1) {$\tilde{u}_L^\dagger$};
+	\node at (2.2,0) {$\tilde{u}_L^\dagger$};
+\end{scope}
+\begin{scope}[shift={(4,-2)}]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,0)--(1,0);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[scalar] (1,1)--(1.5,0.5);
+	\draw[scalar] (1.5,0.5)--(2,0);
+	\draw[scalar] (1,0)--(1.4,0.4);
+	\draw[scalar] (1.6,0.6)--(2,1);
+	\node at (-0.2,1) {$u$};
+	\node at (-0.2,0) {$u$};
+	\node at (2.2,1) {$\tilde{u}_L^\dagger$};
+	\node at (2.2,0) {$\tilde{u}_L^\dagger$};
+\end{scope}
+\begin{scope}[shift={(0,-4)}]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,0)--(1,0);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[scalar] (1,1)--(2,1);
+	\draw[scalar] (1,0)--(2,0);
+	\node at (-0.2,1) {$u$};
+	\node at (-0.2,0) {$u$};
+	\node at (2.2,1) {$\tilde{u}_R^\dagger$};
+	\node at (2.2,0) {$\tilde{u}_R^\dagger$};
+\end{scope}
+\begin{scope}[shift={(4,-4)}]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,0)--(1,0);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[scalar] (1,1)--(1.5,0.5);
+	\draw[scalar] (1.5,0.5)--(2,0);
+	\draw[scalar] (1,0)--(1.4,0.4);
+	\draw[scalar] (1.6,0.6)--(2,1);
+	\node at (-0.2,1) {$u$};
+	\node at (-0.2,0) {$u$};
+	\node at (2.2,1) {$\tilde{u}_R^\dagger$};
+	\node at (2.2,0) {$\tilde{u}_R^\dagger$};
+\end{scope}
+\end{tikzpicture} & \begin{tikzpicture}[line width=1.0 pt, scale=0.7]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,0)--(1,0);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[scalar] (1,1)--(2,1);
+	\draw[scalar] (1,0)--(2,0);
+	\node at (-0.2,1) {$u$};
+	\node at (-0.2,0) {$u$};
+	\node at (2.2,1) {$\tilde{u}_L^\dagger$};
+	\node at (2.2,0) {$\tilde{u}_R^\dagger$};
+\begin{scope}[shift={(4,0)}]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,0)--(1,0);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[scalar] (1,1)--(1.5,0.5);
+	\draw[scalar] (1.5,0.5)--(2,0);
+	\draw[scalar] (1,0)--(1.4,0.4);
+	\draw[scalar] (1.6,0.6)--(2,1);
+	\node at (-0.2,1) {$u$};
+	\node at (-0.2,0) {$u$};
+	\node at (2.2,1) {$\tilde{u}_L^\dagger$};
+	\node at (2.2,0) {$\tilde{u}_R^\dagger$};
+\end{scope}
+\begin{scope}[shift={(0,-4.3)}]
+\node at (0,0) {};
+\end{scope}
+\end{tikzpicture} 
+\end{tabular}
+\caption{All Feynman diagrams contributing to flavor like squark production in the MSSM and the MRSSM for the example of $u$-quarks.
+For the MSSM the absolute squared Feynman amplitudes from the diagrams with chirality like squarks need to be weighted with a factor of $\frac{1}{2}$.}\label{tab:squark_likeflavor}
+\end{center}
+\end{table}
+\begin{table}[!htpb]
+\begin{center}
+\begin{tabular}{c|c}
+MSSM & MRSSM \\
+\hline
+\begin{tikzpicture}[line width=1.0 pt, scale=0.7]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,0)--(1,0);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[scalar] (1,1)--(2,1);
+	\draw[scalar] (1,0)--(2,0);
+	\node at (-0.2,1) {$u$};
+	\node at (-0.2,0) {$d$};
+	\node at (2.2,1) {$\tilde{u}_L^\dagger$};
+	\node at (2.2,0) {$\tilde{d}_R^\dagger$};
+\begin{scope}[shift={(4,0)}]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,0)--(1,0);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[scalar] (1,1)--(2,1);
+	\draw[scalar] (1,0)--(2,0);
+	\node at (-0.2,1) {$u$};
+	\node at (-0.2,0) {$d$};
+	\node at (2.2,1) {$\tilde{u}_R^\dagger$};
+	\node at (2.2,0) {$\tilde{d}_L^\dagger$};
+\end{scope}
+\begin{scope}[shift={(0,-2)}]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,0)--(1,0);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[scalar] (1,1)--(2,1);
+	\draw[scalar] (1,0)--(2,0);
+	\node at (-0.2,1) {$u$};
+	\node at (-0.2,0) {$d$};
+	\node at (2.2,1) {$\tilde{u}_L^\dagger$};
+	\node at (2.2,0) {$\tilde{d}_L^\dagger$};
+\end{scope}
+\begin{scope}[shift={(0,-4)}]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,0)--(1,0);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[scalar] (1,1)--(2,1);
+	\draw[scalar] (1,0)--(2,0);
+	\node at (-0.2,1) {$u$};
+	\node at (-0.2,0) {$d$};
+	\node at (2.2,1) {$\tilde{u}_R^\dagger$};
+	\node at (2.2,0) {$\tilde{d}_R^\dagger$};
+\end{scope}
+\end{tikzpicture} & \begin{tikzpicture}[line width=1.0 pt, scale=0.7]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,0)--(1,0);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[scalar] (1,1)--(2,1);
+	\draw[scalar] (1,0)--(2,0);
+	\node at (-0.2,1) {$u$};
+	\node at (-0.2,0) {$d$};
+	\node at (2.2,1) {$\tilde{u}_L^\dagger$};
+	\node at (2.2,0) {$\tilde{d}_R^\dagger$};
+\begin{scope}[shift={(4,0)}]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,0)--(1,0);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[scalar] (1,1)--(2,1);
+	\draw[scalar] (1,0)--(2,0);
+	\node at (-0.2,1) {$u$};
+	\node at (-0.2,0) {$d$};
+	\node at (2.2,1) {$\tilde{u}_R^\dagger$};
+	\node at (2.2,0) {$\tilde{d}_L^\dagger$};
+\end{scope}
+\begin{scope}[shift={(0,-4.3)}]
+\node at (0,0) {};
+\end{scope}
+\end{tikzpicture} 
+\end{tabular}
+\caption{All Feynman diagrams contributing to flavor unlike squark production in the MSSM and the MRSSM for the example of $u$- and $d$-quarks.}\label{tab:squark_unlikeflavor}
+\end{center}
+\end{table}\\
+Because of the absence of chirality like squarks in the final state in the MRSSM (and a missing interference of the two diagrams in tab.
+\ref{tab:squark_likeflavor} in the MRSSM) the cross section of flavor like and unlike squarks is the same in the MRSSM, i.e.
+on the partonic level:\\ $\sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(\tilde{u}_L\tilde{u}_R) = \sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(\tilde{u}_L\tilde{d}_R)$.
 That is however not true in the MSSM.
@@
 \begin{center}
+\includegraphics[scale=.45]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
+\includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
+\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
+The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row).
+In the final state it has been summed over all squark flavors expect for staus.
+For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
+The parton densities and the renormalization and factorization scale are chosen as in fig.
+\ref{fig:TreeXsection}.}\label{fig:TreeLevelSigma_0,9_2}
+\end{center}
+\end{figure}
+
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.4]{figures/mr=5_MSSM+MRSSM}
+\includegraphics[scale=.45]{figures/rel_weights_mr=5_MSSM+MRSSM}
+\caption{Hadronic cross section for squark and gluino production (in the first row) and relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
+The ratio of gluino and squark mass is fixed to 5.
+In the final state it has been summed over all squark flavors expect for staus.
+For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
+The parton densities and the renormalization and factorization scale are chosen as in fig.
+\ref{fig:TreeXsection}.}
+\end{center}
+\end{figure}
+
+\begin{figure}[!htpb]
+\begin{center}
 \includegraphics[scale=.6]{figures/contour_MRSSM_squarks}

### 2016-05-31 Virt_Real.tex
Auswertung TreeLevelkanaele bis Ende qq to sqsq, noch Bezug nehmen auf hadronischen Wq

@@
 contains divergences. These come from integrals over undetermined momentum and energy of particles running in loops.
-\begin{figure}
+\begin{figure}[!htbp]
 \begin{center}
@@
 \end{align}
+In this thesis the computation is performed in $D = 4-2\epsilon$ dimensions in order to regularize it.
+Ultraviolet divergences show then up as single poles in $\epsilon$.
 This procedure will be discussed in detail in section \ref{sec:renMRSSM} and \ref{sec:LSZ}.\\
-Having removed the ultraviolet divergences one performs the 2-body phase space integration to arrive at an ultraviolet-finite cross section.
-However, this cross section is not free of divergences as it comprises infrared divergences.
+Having removed the ultraviolet divergences the matrix element is not free of divergences as it comprises infrared divergences.
 These split into soft and collinear (or mass) singularities\footnote{The names differ in the literature.
 Often infrared divergences are used as a synonym for soft divergences.} which cannot be removed by means of renormalization.
+These additional singularities show up as single and double poles of $\epsilon$ in the matrix element $\mathcal{M^{\mathrm{1L}}}$ and the virtual cross section which is obtained after performing the 2-body phase space  integration as in eq.
+\ref{eq:sigma_tree} but over $\left|\mathcal{M^{\mathrm{V}}}\right|^2$:
+\begin{align}
+\frac{\mbox{d}^2 \sigma^{\mathrm{V}}}{\mbox{d}t\ \mbox{d}u} =& \frac{K_{ab}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_1^2m_2^2}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_1^2m_2^2)\nonumber\\
+&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum |\mathcal{M}^{\mathrm{V}}|^2.
+\end{align}
+The single poles correspond to soft or collinear divergences whereas the double poles correspond to the coincidence of soft and collinear divergences.
 
 \subsection{Real Corrections}
-Kinoshita-Lee-Naunberg-Theorem \cite{1962JMP.....3..650K},\cite{PhysRev.133.B1549}\\
-At the end: scheme of real and virtual corrections from WARB-talk
+A crucial thing to recognize in the calculation of the $\mathcal{O}(\alpha_s)$ correction to the squark production cross section is that not only virtual corrections but also real corrections give rise to this physical observable.
+This is because one does not measure the final state partons but the jets in which they hadronize in due to confinement.
+This means that a radiation of a massless particle whose energy tends to zero or the radiation of a  particle which is collinear to one of the final state particles is in experiment measured as a two jet event even though there are three particles in the final state of the calculation.
+However real corrections also contain divergences.
+Including these contributions to the cross section causes the cancellation of singles poles coming from soft divergences and the cancellation of double poles.
+At this point the only singularities which are left in the cross section are the collinear ones.\\
+To see how these are removed consider diagram the second digram in fig. \ref{fig:RealGluon}. The propagator of the quark which radiates off a gluon is giving a contribution of the form
+\begin{align}
+\frac{1}{(p_q + p_g)^2 - m_q^2} = \frac{1}{p_q \cdot p_g} = \frac{1}{2E_qE_g(1-\beta_q \cos \theta_{qg})} \hspace{2cm} \mathrm{with}\ \beta_q = \frac{\vec{p}_q}{E_q}
+\end{align}
+to the the diagram in question.
+Where $p_q$, $p_g$ ($E_q$, $E_g$) are the quark's and gluon's four-momentum (energy) and $\theta_{qg}$ is the angle between the quark's and gluon's three-momentum.
+One observes two potentially singular limits
+\begin{align}
+\mathrm{soft\ gluon:}& \hspace{1cm} E_g \to 0\\
+%& \hspace{1cm} E_q \to 0 \hspace{1cm} \mathrm{if}\ m_q \to 0\\
+\mathrm{collinear\ particles:}& \hspace{1cm} \theta_{qg} \to 0 \hspace{1cm} \mathrm{if}\ m_q \to 0.
+\end{align}
+Within these limits the inner quark can almost be considered as on-shell which means that it may travel a long distance between the emission of a gluon and taking part in the actual interaction.
+This suggest that some divergences may come from the incoming hadron and are actually not associated with the interaction.
+In fact this turns out to be the case: The remaining collinear divergences can be absorbed in to a redefinition of the parton density functions.
+This procedure is referred to as mass factorization.
+Figure \ref{fig:DivergenceSummary} summarizes the required steps to render the next-to-leading-order cross section finite.\\
+In fact the Kinoshita-Lee-Naunberg-Theorem \cite{1962JMP.....3..650K},\cite{PhysRev.133.B1549} guarantees the finiteness of sufficiently inclusive observables.
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}
+	\node [block1a] (Mvirt) {$\mathcal{M}^{\mathrm{1L}}$ is UV- and  IR-divergent};
+	\node [block2a] at (6,0) (Mreal) {$\mathcal{M}^{\mathrm{real}}$ is IR-divergent};
+	\node [block1a] at (0,-2) (Mvirtren) {$\mathcal{M}^{\mathrm{1L}}$ is IR-divergent};
+	\path [line, line width = 1] (Mvirt) --node[right] {renormalize} (Mvirtren);
+	\node [block1b] at (0,-4) (svirtren) {$\sigma^{\mathrm{virt}}$ is IR-divergent};
+	\node [block2b] at (6,-4) (sreal) {$\sigma^{\mathrm{real}}$ is IR-divergent};
+	\path [line, line width = 1] (Mvirtren) --node[right] {integrate phase space} (svirtren);
+	\path [line, line width = 1] (Mreal) --node[right] {integrate phase space} (sreal);
+	\node [block2b] at (6, -6) (srealfac) {$\sigma^{\mathrm{real}}$ is IR-divergent};
+	\path [line, line width = 1] (sreal) --node[right] {mass factorization} (srealfac);
+	\node [block3] at (3,-8) (snlo) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{virt}} + \sigma^{\mathrm{real}}$ is finite};
+	\path [line, line width = 1] (srealfac) -- (snlo);
+	\path [line, line width = 1] (svirtren) -- (snlo);
+\end{tikzpicture}
+\caption{This scheme illustrates the necessary steps in the computation of the next-to-leading order cross section which are required to render it finite. }\label{fig:DivergenceSummary}
+\end{center}
+\end{figure}
+
+\subsubsection{Real Gluon Radiation}
+Representative Feynman-diagrams for real gluon emission are shown in fig.
+\ref{fig:RealGluon}.
+In order to extract the singularities the so called two-cut method has been adopted.
+This is the phase space has been divided into different regimes: a soft part, a hard collinear part and a hard non-collinear part.\\
+In the soft part the energy of the outgoing gluon is only integrated up to  $\delta_s \frac{\sqrt{s}}{2}$ where $\delta_s$ is a cut on which the final result must not depend on.
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
+	\draw[fermion] (0,1)--(1,1);	
+	\draw[fermion] (0,-0.5)--(1,-0.5);
+	\draw[fermionnoarrow] (1,1)--(1,-0.5);
+	\draw[gluon] (1,1)--(1,-0.5);
+	\draw[scalar] (1,1)--(2.75,1);
+	\draw[scalar] (1,-0.5)--(2,-0.5);
+	\draw[gluon] (2,-0.5)--(2.75,0.25);
+	\draw[scalar] (2,-0.5)--(2.75,-1.25);
+\begin{scope}[shift={(4,0)}]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,-1)--(1,-1);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[fermion] (1,-1)--(1,0);
+	\draw[scalar] (1,1)--(2,1);
+	\draw[gluon] (1,-1)--(2,-1);
+	\draw[scalar] (1,0)--(2,0);
+\end{scope}
+\begin{scope}[shift={(8,0)}]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[fermion] (0,-1)--(1,-1);
+	\draw[fermionnoarrow] (1,1)--(1,-1);
+	\draw[gluon] (1,1)--(1,-1);
+	\draw[scalar] (1,1)--(2,1);
+	\draw[scalar] (1,-1)--(2,-1);
+	\draw[gluon] (1,0)--(2,0);
+\end{scope}
+\end{tikzpicture}
+\caption{A selection of real gluon emission diagrams contributing to squark production.
+Again each diagram is a representative of a certain diagram type.
+The first one is final state gluon emission, the second one initial state gluon radiation and the third one is the radiation of a gluon from a virtual particle within the diagram.}\label{fig:RealGluon}
+\end{center}
+\end{figure}
+
+\subsubsection{Real Quark Radiation}
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
+\begin{scope}[shift={(0,0.25)}]
+	\draw[fermion] (-1.25,0.75)--(-0.5,0);
+	\draw[gluon] (-1.25,-0.75)--(-0.5,0);
+	\draw[fermion] (-0.5,0)--(0.5,0); 
+	\draw[scalar] (0.5,0)--(1.25,0.75);
+	\draw[gluon] (0.5,0)--(1.25,-0.75);
+	\draw[fermionnoarrow] (0.5,0)--(1.25,-0.75);
+	\draw[scalar] (1.25,-0.75)--(2,0);
+	\draw[fermion] (2,-1.5)--(1.25,-0.75);
+	\end{scope}
+\begin{scope}[shift={(3,0)}]
+	\draw[fermion] (0,1)--(1,1);	
+	\draw[gluon] (0,-0.5)--(1,-0.5);
+	\draw[fermionnoarrow] (1,1)--(1,-0.5);
+	\draw[gluon] (1,1)--(1,-0.5);
+	\draw[scalar] (1,1)--(2.75,1);
+	\draw[fermionnoarrow] (1,-0.5)--(2,-0.5);
+	\draw[gluon] (1,-0.5)--(2,-0.5);
+	\draw[scalar] (2,-0.5)--(2.75,0.25);
+	\draw[fermion] (2.75,-1.25)--(2,-0.5);
+\end{scope}
+\begin{scope}[shift={(7,0)}]
+	\draw[fermion] (0,1)--(1,1);
+	\draw[gluon] (0,-1)--(1,-1);
+	\draw[fermionnoarrow] (1,1)--(1,0);
+	\draw[gluon] (1,1)--(1,0);
+	\draw[fermion] (1,-1)--(1,0);
+	\draw[scalar] (1,1)--(2,1);
+	\draw[fermion] (2,-1)--(1,-1);
+	\draw[scalar] (1,0)--(2,0);
+\end{scope}
+\end{tikzpicture}
+\caption{A selection of real quark emission diagrams contributing to squark production.
+The first two diagrams have a gluino propagator which may go on-shell.
+In this regime of phase space these diagrams should not be included in the correction to squark-production but to a tree-level contribution to squark-gluino-production.}\
+\end{center}
+\end{figure}

### 2016-05-31 custom_commands_Theorie.tex
Auswertung TreeLevelkanaele bis Ende qq to sqsq, noch Bezug nehmen auf hadronischen Wq

@@
             \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
+%% selbst definierte Befehle für tikz
+\tikzstyle{block1a} = [rectangle, draw, fill=blue!20, 
+text width=10em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{block2a} = [rectangle, draw, fill=red!20, 
+text width=10em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{block1b} = [rectangle, draw, fill=blue!40, 
+text width=10em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{block2b} = [rectangle, draw, fill=red!40, 
+text width=10em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{block3} = [rectangle, draw, fill=green!40, 
+text width=10em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{line} = [draw, -latex']       
 \usepackage{hyperref}			% Has to be at the end.

### 2016-06-01 TreeLevel.tex
push before restructering: move Subprocesses to Partonic Cross Sections

@@
 See \cite{Brock:1993sz} for how to ascertain parton density functions\\
+\begin{figure}[!htbp]
+\begin{center}
+\includegraphics[scale=0.6]{figures/pdf's}
+\caption{pdf's}\label{fig:pdfs}
+\end{center}
+\end{figure}
 Fig.
-...
-shows a parton density function set for the proton.
+\ref{fig:pdfs} shows a parton density function set for the proton.
 One can see that the partons most probable to carry a high fraction of momentum are the valence quarks.
@@
 As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}
+\end{center}
+\end{figure}
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.45]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
+\includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
+\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
+The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row).
+In the final state it has been summed over all squark flavors expect for staus.
+For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
+The parton densities and the renormalization and factorization scale are chosen as in fig.
+\ref{fig:TreeXsection}.}\label{fig:TreeLevelSigma_0,9_2}
 \end{center}
@@
 \subsubsection*{The process $GG \to \tilde{q}\tilde{q}^\dagger$}
-This process has the same cross section in the MRSSM and in the MSSM for also in the MSSM only like chirality squark and antisquark $\tilde{q}_A\tilde{q}_A^\dagger$ with $A \in {L,R}$ can be produced
+This process has the same cross section in the MRSSM and in the MSSM for also in the MSSM only like chirality squark and antisquark $\tilde{q}_A\tilde{q}_A^\dagger$ with $A \in {L,R}$ can be produced.
 
@@
 \ref{tab:squark_unlikeflavor} for the MSSM and the MRSSM.
-To avoid double counting one needs to weight $|\mathcal{M}|^2(qq\to \tilde{q}_L\tilde{q}_L)$ and $|\mathcal{M}|^2(qq\to \tilde{q}_R\tilde{q}_R)$ with a statistical factor of $\frac{1}{2}$ as one integrates over all momenta of both particles to arrive at the cross section.\footnote{Alternatively one could discard the $u$-channel (or $t$-channel) diagram and omit the weighting with $\frac{1}{2}$.}
+To avoid double counting one needs to weight $|\mathcal{M}|^2(qq\to \tilde{q}_L\tilde{q}_L)$ and $|\mathcal{M}|^2(qq\to \tilde{q}_R\tilde{q}_R)$ with a statistical factor of $\frac{1}{2}$ as one integrates over all momenta of both particles to arrive at the cross section.
 \begin{table}[!htpb]
@@
 	\node at (-0.2,0) {$u$};
-	\node at (2.2,1) {$\tilde{u}_L^\dagger$};
-	\node at (2.2,0) {$\tilde{u}_R^\dagger$};
+	\node at (2.5,1) {$\tilde{u}_L^\dagger$};
+	\node at (2.5,0) {$\tilde{u}_R^\dagger$};
 \begin{scope}[shift={(4,0)}]
@@
 	\node at (-0.2,0) {$u$};
-	\node at (2.2,1) {$\tilde{u}_L^\dagger$};
-	\node at (2.2,0) {$\tilde{u}_R^\dagger$};
+	\node at (2.5,1) {$\tilde{u}_L^\dagger$};
+	\node at (2.5,0) {$\tilde{u}_R^\dagger$};
 \end{scope}
@@
 	\node at (-0.2,0) {$u$};
-	\node at (2.2,1) {$\tilde{u}_L^\dagger$};
-	\node at (2.2,0) {$\tilde{u}_L^\dagger$};
+	\node at (2.5,1) {$\tilde{u}_L^\dagger$};
+	\node at (2.5,0) {$\tilde{u}_L^\dagger$};
 \end{scope}
@@
 	\node at (-0.2,0) {$u$};
-	\node at (2.2,1) {$\tilde{u}_R^\dagger$};
-	\node at (2.2,0) {$\tilde{u}_R^\dagger$};
+	\node at (2.5,1) {$\tilde{u}_R^\dagger$};
+	\node at (2.5,0) {$\tilde{u}_R^\dagger$};
 \end{scope}
@@
 	\node at (-0.2,0) {$d$};
-	\node at (2.2,1) {$\tilde{u}_L^\dagger$};
-	\node at (2.2,0) {$\tilde{d}_R^\dagger$};
+	\node at (2.5,1) {$\tilde{u}_L^\dagger$};
+	\node at (2.5,0) {$\tilde{d}_R^\dagger$};
 \begin{scope}[shift={(4,0)}]
@@
 	\node at (-0.2,0) {$d$};
-	\node at (2.2,1) {$\tilde{u}_R^\dagger$};
-	\node at (2.2,0) {$\tilde{d}_L^\dagger$};
+	\node at (2.5,1) {$\tilde{u}_R^\dagger$};
+	\node at (2.5,0) {$\tilde{d}_L^\dagger$};
 \end{scope}
@@
 	\node at (-0.2,0) {$d$};
-	\node at (2.2,1) {$\tilde{u}_L^\dagger$};
-	\node at (2.2,0) {$\tilde{d}_L^\dagger$};
+	\node at (2.5,1) {$\tilde{u}_L^\dagger$};
+	\node at (2.5,0) {$\tilde{d}_L^\dagger$};
 \end{scope}
@@
 	\node at (-0.2,0) {$d$};
-	\node at (2.2,1) {$\tilde{u}_R^\dagger$};
-	\node at (2.2,0) {$\tilde{d}_R^\dagger$};
+	\node at (2.5,1) {$\tilde{u}_R^\dagger$};
+	\node at (2.5,0) {$\tilde{d}_R^\dagger$};
 \end{scope}
@@
 Because of the absence of chirality like squarks in the final state in the MRSSM (and a missing interference of the two diagrams in tab.
-\ref{tab:squark_likeflavor} in the MRSSM) the cross section of flavor like and unlike squarks is the same in the MRSSM, i.e.
-on the partonic level:\\ $\sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(\tilde{u}_L\tilde{u}_R) = \sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(\tilde{u}_L\tilde{d}_R)$.
-That is however not true in the MSSM.
+\ref{tab:squark_likeflavor} in the column of the MRSSM) the partonic cross section of flavor like and unlike squarks is the same in the MRSSM, i.e.
+on the partonic level:
+\begin{align}
+\sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(uu \to \tilde{u}_L\tilde{u}_R) = \sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(ud \to \tilde{u}_L\tilde{d}_R) + \sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(ud \to \tilde{u}_R\tilde{d}_L).
+\end{align} 
+That is however not true in the MSSM because for flavor like squarks there is a non vanishing interference of the $t$- and $u$-channel diagram of the processes $qq \to \tilde{q}_L\tilde{q}_L$ and $qq \to \tilde{q}_R\tilde{q}_R$.
+This term is given in \cite[p.7]{Beenakker:1996ch}\\
+Looking at the hadronic cross section in fig.
+\ref{fig:TreeXsection} can see the suppression of squark production in the MRSSM in comparison to the MSSM.
+One can also see that this suppression grows when going from $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ to  $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ or even to  $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 5$ in fig.
+\ref{fig:TreeXsection5}.
+This reflects the gluino mass dependence explained above.
+See also \ref{fig:TreeXsection_fixed_m} for a visualization of this behavior.\\
+Note also that for sufficiently large squark masses squark production is the dominant process, see fig.
+\ref{fig:TreeXsection} and \ref{fig:TreeLevelSigma_0,9_2}.
+This is because the production of heavy particles requires large longitudinal momenta of the colliding partons, i.e.
+large $x$.
+Looking at the parton density functions in fig.
+\ref{fig:pdfs} one sees that within the proton the partons most likely to carry large momentum are quarks.
+So looking at large $x$ the proton basically consists of quarks and because the only process involving only quarks in the initial state is squark production, this channel dominates for high masses.
 
@@
 This is because gluino and antigluino are distinguishable particles.
-Still in comparison to the MSSM cross section only the first line in \ref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines origin from an $t$ or $u$ channel squark which occurs in only one instead of two chiralities.
+Still in comparison to the MSSM cross section \cite[p.9]{Beenakker:1996ch} only the first line in \ref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines originate from an $t$ or $u$ channel squark which occurs in only one instead of two chiralities.
 Furthermore an interference term from the $t$ or $u$ channel diagram which occurs in the MSSM is absent in the MRSSM.
+For a growing gluino mass it is this interference term which makes the cross section in the MRSSM dominant over the one in the MSSM.
 % this interference term causes a huge difference, that's been checked by Philip via Madgraph
@@
 \begin{center}
-\includegraphics[scale=.45]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
-\includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
-\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
-The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row).
-In the final state it has been summed over all squark flavors expect for staus.
-For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
-The parton densities and the renormalization and factorization scale are chosen as in fig.
-\ref{fig:TreeXsection}.}\label{fig:TreeLevelSigma_0,9_2}
-\end{center}
-\end{figure}
-
-\begin{figure}[!htpb]
-\begin{center}
 \includegraphics[scale=.4]{figures/mr=5_MSSM+MRSSM}
@@
 The parton densities and the renormalization and factorization scale are chosen as in fig.
-\ref{fig:TreeXsection}.}
+\ref{fig:TreeXsection}.}\label{fig:TreeXsection5}
 \end{center}
@@
 \includegraphics[scale=.5]{figures/MSSM+MRSSM_msq=1000}
-\caption{add error bars}
+\caption{add error bars}\ref{fig:TreeXsection_fixed_m}
 \end{center}

### 2016-06-01 TreeLevel.tex
restructered TreeLevelChapter

@@
 
-\subsection{Partonic Processes} 
+\subsection{Partonic Processes and their Cross Section} 
 \begin{figure}[!htbp]
@@
 \end{figure}
-For the calculation the top quark is excluded from the initial state as it is too heavy to be significantly present in hadrons. %Therefore its pdf is approximately zero. 
+For the following calculation the top quark is excluded from the initial state as it is too heavy to be significantly present in hadrons. %Therefore its pdf is approximately zero. 
 For consistency reasons also the stop is excluded from the final states.
 One therefore deals with $n_f-1 = 5$ quark flavors.
-Using the Feynman rules in the Appendix one obtains the following sums over absolute squared Feynman amplitudes.
+In view of the renormalization to be performed at the 1-loop level the results are given in $D = 4 - 2\epsilon$ dimensions and it has been distinguished between the gauge coupling $g_s$ from the gluon-quark-quark vertex and its supersymmetric analogue $\hat{g}_s$ from the gluino-squark-quark vertex.
+The usual Mandelstam variables $s,t,u$ and the following modifications of them are used\footnote{The kinematics of the process is like denoted in fig.
+\ref{fig:TreeDiagrams}.}
+\begin{align}
+& s = (k_a + k_b)^2 = (p_1 + p_2)^2\nonumber\\
+& t = (k_a - p_1)^2 = (k_b - p_2)^2\nonumber\\
+& u = (k_a - p_2)^2 = (k_a - p_2)^2\nonumber\\
+& t_{\tilde{g}} = t - m_{\tilde{g}}^2 && t_{\tilde{q}} = t- m_{\tilde{q}}^2\nonumber\\
+& u_{\tilde{g}} = u - m_{\tilde{g}}^2 && u_{\tilde{q}} = u- m_{\tilde{q}}^2
+\end{align}
+Using the Feynman rules in the Appendix \ref{sec:FeynmanRules} one obtains the following sums over absolute squared Feynman amplitudes.
 \begin{align}
@@
 \end{align}
-In view of the renormalization to be performed at the 1-loop level the results are given in $D = 4 - 2\epsilon$ dimensions and it has been distinguished between the gauge coupling $g_s$ from the gluon-quark-quark vertex and its supersymmetric analogue $\hat{g}_s$ from the gluino-squark-quark vertex.
-The usual Mandelstam variables $s,t,u$ and the following modifications of them are used\footnote{The kinematics of the process is like denoted in fig.
-\ref{fig:TreeDiagrams}.}
-\begin{align}
-& s = (k_a + k_b)^2 = (p_1 + p_2)^2\nonumber\\
-& t = (k_a - p_1)^2 = (k_b - p_2)^2\nonumber\\
-& u = (k_a - p_2)^2 = (k_a - p_2)^2\nonumber\\
-& t_{\tilde{g}} = t - m_{\tilde{g}}^2 && t_{\tilde{q}} = t- m_{\tilde{q}}^2\nonumber\\
-& u_{\tilde{g}} = u - m_{\tilde{g}}^2 && u_{\tilde{q}} = u- m_{\tilde{q}}^2
-\end{align}
 
-\subsection{Partonic Cross Sections}
 Having calculated the absolute squared Feynman amplitudes one obtains the partonic cross sections (see Appendix \ref{sec:cross_section}) via
@@
 \end{align}
-are used. The comparison of the cross sections of the MRSSM with those of the MSSM is postponed until the next subsection where the confinement of quarks and gluons within hadrons is accounted for.
-
-\subsection{Hadronic Cross Section}
-factorization (pictorial explanation in factorization paper chapter 1.4 and Dissertori and Seymour, Marx page 24 below)\\
-Quarks, anti-quarks and gluons are no free particles but are confined within hadrons.
-As hadrons consist of a variety of the just mentioned partons which share the hadron's momentum one does not have a definite initial state which is assumed in the previous subsection.
-Fortunately the hadronic cross section for the production of a final state $X$, e.g.
-$X = \tilde{q} \tilde{q}$, can be obtained by convolving the partonic cross section with the parton density functions of the initial partons.
-\begin{align}
-\sigma^B_{\mathrm{Had}}(P_1 P_2 \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_{P_1/H_1}(x_1) f_{P_2/H_2}(x_2)\ \sigma^B_{\mathrm{Part}} (P_1 P_2 \to X, s = x_ 1x_2 S).
-\end{align}
-As the production of the final state $X$ may proceed via various initial partons one has to sum over all possible possibilities arising from the initial hadrons $H_1$ and $H_2$:
-\begin{align}
-\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(P_1 P_2 \to X).
-\end{align}
-To get an intuitive idea of this factorization consider the hadrons as extended objects consisting of partons\footnote{The proton is considered as composed of three valence quarks: Two up-quarks and one down-quark.
-In addition there are gluons and seaquarks, i.e.
-virtual quark-antiquark pairs.} which are permanently interacting which each other.
-Now consider two colliding hadrons in their center-of-mass frame.
-Due to Lorentz contraction the hadrons appear as thin discs and the parton's mutual interactions are time-delayed within this frame.
-This effectively means that a hadron at the time of collision is virtually frozen.\\
-maybe picture of colliding disks\\
-This in turn implies that the hadron consists at the time of collision of a definite number of partons which can be thought of as carrying a definite fraction of the hadron's momentum $p_{\mathrm{Part}} = x p_{\mathrm{Had}}$ with $x \in \left(0, 1 \right)$.
-The parton density function $f_{P/H}(x)$ can therefore be understood as the probability of finding a parton $P$ within the hadron $H$ carrying $x$ of its momentum.
-See \cite{Brock:1993sz} for how to ascertain parton density functions\\
-\begin{figure}[!htbp]
-\begin{center}
-\includegraphics[scale=0.6]{figures/pdf's}
-\caption{pdf's}\label{fig:pdfs}
-\end{center}
-\end{figure}
-Fig.
-\ref{fig:pdfs} shows a parton density function set for the proton.
-One can see that the partons most probable to carry a high fraction of momentum are the valence quarks.
-For lower values of $x$ gluons constitute the major component of the proton.\\
-\begin{figure}[!htpb]
-\begin{center}
-\includegraphics[scale=.45]{figures/MRSSM:q+q->sq+sq_mr=2_seperated}
-\caption{Hadronic cross section for squark production in the MRSSM at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
-The ratio of gluino and squark mass is fixed to 1.5.
-The parton densities used are $\mathtt{MMHT2014}$ LO with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}.
-As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}
-\end{center}
-\end{figure}
-Fig.\ref{fig:TreeXsection} shows the hadronic cross section for the production of various squarks.
-These can only be produced by their supersymmetric partner, e.g.
-two up-squarks can only be produced by two up-quarks.
-One therefore sees the influence of the parton distribution functions quite nicely: The up-squark production is the dominant contribution to squark production.
-Apart from the solid lines in fig.\ref{fig:TreeXsection} which correspond to the production of first generation squarks, also the cross section of mixed first and second generation (dashed lines) and second generation squarks is shown.
-The dashed dotted line shows the cross section of the charged conjugated particles of the dominant channel.\\
-refer to Kribs, Martin
-\begin{figure}[!htpb]
-\begin{center}
-\includegraphics[scale=.4]{figures/mr=0,9_MSSM+MRSSM}
-\includegraphics[scale=.4]{figures/mr=2_MSSM+MRSSM}
-\caption{Hadronic cross section for squark and gluino production in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
-The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row).
-In the final state it has been summed over all squark flavors expect for staus.
-For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
-The parton densities used are $\mathtt{MMHT2014}$ LO with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}.
-As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}
-\end{center}
-\end{figure}
-\begin{figure}[!htpb]
-\begin{center}
-\includegraphics[scale=.45]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
-\includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
-\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
-The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row).
-In the final state it has been summed over all squark flavors expect for staus.
-For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
-The parton densities and the renormalization and factorization scale are chosen as in fig.
-\ref{fig:TreeXsection}.}\label{fig:TreeLevelSigma_0,9_2}
-\end{center}
-\end{figure}
+are used. In the following the considered processes of the MRSSM are compared to those of the MSSM.
 
@@
 \subsubsection*{The process $GG \to \tilde{q}\tilde{q}^\dagger$}
-This process has the same cross section in the MRSSM and in the MSSM for also in the MSSM only like chirality squark and antisquark $\tilde{q}_A\tilde{q}_A^\dagger$ with $A \in {L,R}$ can be produced.
+This process has the same cross section as in the MSSM for also in the MSSM only like chirality squark and antisquark $\tilde{q}_A\tilde{q}_A^\dagger$ with $A \in {L,R}$ can be produced.
 
@@
 \begin{align}
-\sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(uu \to \tilde{u}_L\tilde{u}_R) = \sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(ud \to \tilde{u}_L\tilde{d}_R) + \sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(ud \to \tilde{u}_R\tilde{d}_L).
+\sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(uu \to \tilde{u}_L\tilde{u}_R) = \sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(ud \to \tilde{u}_L\tilde{d}_R) + \sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(ud \to \tilde{u}_R\tilde{d}_L).\label{eq:PartonicEquality}
 \end{align} 
@@
 This term is given in \cite[p.7]{Beenakker:1996ch}\\
-Looking at the hadronic cross section in fig.
+
+\subsubsection*{The process $q \overline{q} \to \tilde{g}\overline{\tilde{g}}$}
+In contrast to the MSSM no statistical factor of $\frac{1}{2}$ is taken into account when turning from $|\mathcal{M}|^2$ to $\sigma$.
+This is because gluino and antigluino are distinguishable particles.
+Still in comparison to the MSSM cross section \cite[p.9]{Beenakker:1996ch} only the first line in \ref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines originate from an $t$ or $u$ channel squark which occurs in only one instead of two chiralities.
+Furthermore an interference term from the $t$ and $u$ channel diagram which occurs in the MSSM is absent in the MRSSM.
+% this interference term causes a huge difference, that's been checked by Philip via Madgraph
+
+\subsubsection*{The process $GG \to \tilde{g}\overline{\tilde{g}}$}
+As in the previous process the MRSSM cross section for $GG \to \tilde{g}\overline{\tilde{g}}$ receives no statistical factor of $\frac{1}{2}$ like in the MSSM.
+As there are no further differences between MSSM and MRSSM in this channel, the MRSSM cross section is simply twice as large as in the MSSM.
+
+\subsubsection*{The process $q G \to \tilde{q} \tilde{g}$}
+This process is exactly the same in the MSSM and MRSSM.
+\\ 
+\\
+In order to account for the confinement of quarks and gluons within hadrons the hadronic cross sections for the considered processes are calculated in the next subsection.
+
+\subsection{Hadronic Cross Section}
+
+Quarks, antiquarks and gluons are no free particles but are confined within hadrons.
+As hadrons consist of a variety of the just mentioned partons which share the hadron's momentum one does not have a definite initial state in hadron collisions which is assumed in the previous subsection.
+Fortunately the hadronic cross section for the production of a final state $X$, e.g.
+$X = \tilde{q} \tilde{q}$, can be obtained by convolving the partonic cross section with parton density functions of the initial hadrons.
+\begin{align}
+\sigma^\mathrm{B}_{\mathrm{Had}}(P_1 P_2 \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_{P_1/H_1}(x_1) f_{P_2/H_2}(x_2)\ \sigma^\mathrm{B}_{\mathrm{Part}} (P_1 P_2 \to X, s = x_ 1x_2 S).
+\end{align}
+The parton density functions $f_{P_i/H_j}(x)$ and the momentum fractions $x_i$ are explained below.
+The hadrons center-of-mass energy is denoted with $\sqrt{S}$ where $\sqrt{s}$ denotes the partons center-of-mass energy.\\
+As the production of the final state $X$ may proceed via various initial partons one has to sum over all possible possibilities arising from the initial hadrons $H_1$ and $H_2$:
+\begin{align}
+\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(P_i P_j \to X).
+\end{align}
+To get an intuitive idea of this factorization consider the hadrons as extended objects consisting of partons\footnote{The proton is considered as composed of three valence quarks: Two up-quarks and one down-quark.
+In addition there are gluons and seaquarks, i.e.
+virtual quark-antiquark pairs.} which are permanently interacting which each other.
+Now consider two colliding hadrons in their center-of-mass frame.
+Due to Lorentz contraction the hadrons appear as thin discs and the parton's mutual interactions are time-delayed within this frame.
+This effectively means that a hadron at the time of collision is virtually frozen.\\
+maybe picture of colliding disks\\
+This in turn implies that the hadron consists at the time of collision of a definite number of partons which can be thought of as carrying a definite fraction of the hadron's  momentum $p_{\mathrm{Part}} = x p_{\mathrm{Had}}$ with $x \in \left(0, 1 \right)$.
+The parton density function $f_{P/H}(x)$ can therefore be understood as the probability of finding a parton $P$ within the hadron $H$ carrying $x$ of its momentum.
+\begin{figure}[!htbp]
+\begin{center}
+\includegraphics[scale=0.6]{figures/pdf's}
+\caption{Parton density function of the proton, taken from $\mathtt{MMHT2014}$ \cite{Harland-Lang:2014zoa} with 68\% confidence level.
+The pdf is multiplied by $x$ in order to counteract its peak at $x \to 0$.
+The parton density function is given at two different factorisaction scales $\mu_F = Q$}\label{fig:pdfs}
+\end{center}
+\end{figure}\\
+They actually depend on an arbitrary energy scale referred to as the factorization scale $\mu_F$.
+The $\mu_F$ evolution is given within the scope of preturbation theory by coupled integro-differential equations named after Gribov, Lipatov, Dokshitzer, Altarelli and Parisi: the DGLAP-equations.
+For further reading on parton density functions and factorization see \cite{dissertori2003quantum} and \cite{Collins:1989gx}.
+See \cite{Brock:1993sz} for how to determine parton density functions.\\
+Fig.
+\ref{fig:pdfs} shows a parton density function set for the proton.
+One can see that the partons most probable to carry a high fraction of momentum are the valence quarks.
+For lower values of $x$ gluons constitute the major component of the proton.
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.45]{figures/MRSSM:q+q->sq+sq_mr=2_seperated}
+\caption{Hadronic cross section for squark production in the MRSSM at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
+The ratio of the gluino and squark mass is fixed to 2.
+The parton densities used are $\mathtt{MMHT2014}$ LO with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}.
+As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}
+\end{center}
+\end{figure}\\
+Fig.\ref{fig:TreeXsection} shows the hadronic cross section for the production of various squarks in the MRSSM.
+These can only be produced by their non supersymmetric partner, e.g.
+two up-squarks can only be produced by two up-quarks.
+Because the partonic cross section for these processes are all the same cf.
+eq.
+\ref{eq:PartonicEquality} one can see the influence of the parton density functions quite nicely: The up-squark production is the dominant contribution to squark production.
+Apart from the solid lines in fig.\ref{fig:TreeXsection} which correspond to the production of first generation squarks, also the cross section of mixed first and second generation (dashed lines) and second generation (dotted lines) squarks is shown.
+The dashed dotted line shows the cross section of the charged conjugated particles of the dominant channel.\\
+refer to Kribs, Martin
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.4]{figures/mr=0,9_MSSM+MRSSM}
+\includegraphics[scale=.4]{figures/mr=2_MSSM+MRSSM}
+\caption{Hadronic cross section for squark and gluino production in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
+The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row).
+In the final state it has been summed over all squark flavors expect for staus.
+For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
+The parton densities used are $\mathtt{MMHT2014}$ LO with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}.
+As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}
+\end{center}
+\end{figure}
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.45]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
+\includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
+\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
+The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row).
+In the final state it has been summed over all squark flavors expect for staus.
+For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
+The parton densities and the renormalization and factorization scale are chosen as in fig.
+\ref{fig:TreeXsection}.}\label{fig:TreeLevelSigma_0,9_2}
+\end{center}
+\end{figure}
+
+refer to Vernoica Sanz: How many SUpersymmetries?
+\paragraph{qqbar to sqsqdagger}
+This channel dominates squark and gluino production for a large gluino mass but smaller squark masses.
+\paragraph{qq to sqsq} Looking at the hadronic cross section in fig.
 \ref{fig:TreeXsection} can see the suppression of squark production in the MRSSM in comparison to the MSSM.
@@
 So looking at large $x$ the proton basically consists of quarks and because the only process involving only quarks in the initial state is squark production, this channel dominates for high masses.
-
-\subsubsection*{The process $q \overline{q} \to \tilde{g}\overline{\tilde{g}}$}
-In contrast to the MSSM no statistical factor of $\frac{1}{2}$ is taken into account when turning from $|\mathcal{M}|^2$ to $\sigma$.
-This is because gluino and antigluino are distinguishable particles.
-Still in comparison to the MSSM cross section \cite[p.9]{Beenakker:1996ch} only the first line in \ref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines originate from an $t$ or $u$ channel squark which occurs in only one instead of two chiralities.
-Furthermore an interference term from the $t$ or $u$ channel diagram which occurs in the MSSM is absent in the MRSSM.
+\paragraph{qqbar to ggbar}
 For a growing gluino mass it is this interference term which makes the cross section in the MRSSM dominant over the one in the MSSM.
-% this interference term causes a huge difference, that's been checked by Philip via Madgraph
-
-\subsubsection*{The process $GG \to \tilde{g}\overline{\tilde{g}}$}
-As in the previous process the MRSSM cross section for $GG \to \tilde{g}\overline{\tilde{g}}$ receives no statistical factor of $\frac{1}{2}$.
-As there are no further differences between MSSM and MRSSM in this channel, the MRSSM cross section is simply twice as large as in the MSSM.
-
-\subsubsection*{The process $q G \to \tilde{q} \tilde{g}$}
-This process is exactly the same in the MSSM and MRSSM.
-\\
-refer to Vernoica Sanz: How many SUpersymmetries?
 

### 2016-06-07 Appendix.tex
TreeLevel CrossSection and SM-Introduction

@@
 The indices $A,B = L,R$ label the right/left-"handedness" of the squarks.
-The indices $i,j=1,2,3$ are the color indices in the (anti)fundamental representation where $a,b,c,\hdots = 1,\hdots,8$ are the color indices of the adjoint representation.
-}
+The indices $i,j=1,2,3$ are the color indices in the (anti)fundamental representation where $a,b,c,\hdots = 1,\hdots,8$ are the color indices of the adjoint representation.}\label{fig:firstFeynmanRules}
 \end{center}

### 2016-06-07 Renormalization.tex
TreeLevel CrossSection and SM-Introduction

@@
 \subsection{Regularization Scheme Dependences}\label{sec:RegSchemeDep}
-It is useful to introduce the effective action $\Gamma$ to discuss the subject of this and ensuing subchapters.
+It is useful to introduce the effective action $\Gamma$ to discuss the subject of this and ensuing subsections.
 A formal introduction of $\Gamma$ can be found in~\cite{Peskin}.
@@
 This means that in addition to the vertices in the classical Lagrangian new vertices arise due to loop effects.
-As already suggested loop corrections might a priori not be finite and then need to be made finite by the addition of counterterms.
+As already alluded to loop corrections might a priori not be finite and then need to be rendered finite by the addition of counterterms.
 For $\mathcal{O}(\hbar)$ corrections one writes
@@
 \end{align}
-Setting also the finite terms in $\Gamma^{(1),\ \mathrm{ct,\ sym}}$ equal in DRED and DREG the choice of the supersymmetry restoring counterterms is fixed by:
+Equating also the finite terms in $\Gamma^{(1),\ \mathrm{ct,\ sym}}$ in DRED and DREG the choice of the supersymmetry restoring counterterms is fixed by:
 \begin{align}
@@
 This way supersymmetry is preserved by the renormalization constants.\\ 
-In the case of the MRSSM it will turn out that the only supersymmetry violation comes from correction associated with the gluon as already alluded to in \ref{sec:RegSchemes}.
-However supersymmetry restoring is always already included in $\delta Z^{\mathrm{DREG}}$.
+In the case of the MRSSM it will turn out that the only supersymmetry violation comes from corrections associated with the gluon as already alluded to in section \ref{sec:RegSchemes}.
+However supersymmetry restoring will always already be included in $\delta Z^{\mathrm{DREG}}$.
 This is $\delta Z^{\mathrm{DREG}} = \delta Z^{\mathrm{DREG,sym}} + \delta Z^{\mathrm{trans}}$ where $\delta Z^{\mathrm{trans}} = \delta Z^{\mathrm{DREG}} - \delta Z^{\mathrm{DRED}}$ is the supersymmetry restoring renormalization constant.
-The only point where particularly care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms.
+The only point where particularly care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms due to different loop diagrams.
 Therefore one has to make a difference between these couplings at 1-loop level.
-In order to match $g_s$ to the experimentally measured coupling it is renormalized in $\overline{\mathrm{MS}}$.
-The Yukawa coupling $\hat{g}_s$ therefore needs to be added with the difference of the supersymmetry restoring counterterms at 1-loop in order to be renormalized the same way.
+In order to match $g_s$ to the experimentally measured coupling it is renormalized in the  $\overline{\mathrm{MS}}$-scheme (with an additional manipulation for heavy particles, which will be explained in section \ref{sec:RenGaugeCoupling}).
+The Yukawa coupling $\hat{g}_s$ therefore needs to be added with the difference of the supersymmetry restoring counterterms from the $q\tilde{q}^\dagger\tilde{g}$ vertex and the $q\overline{q}G$ vertex at 1-loop in order to be renormalized the same way.
 
@@
 \end{tikzpicture}
-\caption{diagrammatic contributions to the self-energy of the quark at 1-loop level}\label{fig:QuarkSelfEnergy}
+\caption{Feynman diagrams contributing to the self-energy of the quark at 1-loop level}\label{fig:QuarkSelfEnergy}
 \end{center}
@@
 \begin{align}
-i\Gamma^{1L}_{q_i\overline{q}_j} = i \frac{g_s^2}{16\pi^2}\delta_{ij} C(F) \left[ 2 \left( B_0(p^2,0,0) + B_1(p^2,0,0)-\frac{1}{2}\right)\slashed{p} - 2 B_1(p^2,m_{\tilde{g}}^2,m_{\tilde{q}}^2)\slashed{p}\right].
+i\Gamma^{1L}_{q_i\overline{q}_j} = i \frac{g_s^2}{16\pi^2}\delta_{ij} C(F) \left[ 2 \left( B_0(p^2,0,0) + B_1(p^2,0,0)-\frac{1}{2}\right)\slashed{p} - 2 B_1(p^2,m_{\tilde{g}}^2,m_{\tilde{q}}^2)\slashed{p}\right].\label{eq:QuarkSE}
 \end{align}
@@
 \begin{align}
-\delta Z_q = 2 C(F) \frac{g_s^2}{16\pi^2} \Re \left[ B_1(0 ,m_{\tilde{g}}^2,m_{\tilde{q}}^2) + \frac{1}{2}??? \right].
+\delta Z_q = 2 C(F) \frac{g_s^2}{16\pi^2} \Re \left[ B_1(0 ,m_{\tilde{g}}^2,m_{\tilde{q}}^2) \right].
 \end{align}
-Doing the same calculation in DRED one finds that the second term in the squared brackets is absent. Therefore the transition counterterm between DREG and DRED is given by
+Note that the term $\frac{1}{2}$ from eq.
+\ref{eq:QuarkSE} has vanished because the self energy is taken on-shell which means that this factor is absorbed into the on-shell $B_0$ function which is in DREG defined to be zero if it has no mass scale.\\
+Doing the same calculation in DRED one finds that this very term $\frac{1}{2}$ is absent. Therefore the transition counterterm between DREG and DRED is given by
 \begin{align}
@@
 \end{tikzpicture}
-\caption{diagrammatic contributions to the self-energy of the squark at 1-loop level}
+\caption{Diagrammatic contributions to the self-energy of the squark at 1-loop level}
 \end{center}
@@
 \end{align}
-Suppressing $\delta_{AB}$ with $A,B = L,R$ which is present in the tree level propagator the counterterm Feynman rule is given by\\
+Suppressing $\delta_{AB}$ with $A,B \in \left\{ L,R \right\}$ which is present in the tree level propagator (see fig. \ref{fig:firstFeynmanRules}) the counterterm Feynman rule is given by\\
 \\
@@
 \end{align}
-The left-handed part $\lambda^a$ is associated with the superpartner of the gluon and therefore the "actual" gluino whereas the right-handed part $\overline{\chi}^a$ was introduced to assign a Dirac-mass to the gluino and is referred to as the octino.\\
+The left-handed part $\lambda^a$ is associated with the superpartner of the gluon and therefore the "actual" gluino whereas the right-handed part $\overline{\chi}^a$ was introduced to assign a Dirac-mass to the gluino and may be referred to as the octino.\\
 From the Lagrangian \ref{eq:L_RSQCD} one can see that the couplings of the two particles are quite distinct.
@@
 \begin{align}
-& \frac{\partial}{\partial (P_L\slashed{p})} \left[ \Re (\Gamma^{\mathrm{1L}}_{\tilde{g}^a \overline{\tilde{g}}^b}) + \Gamma^{\mathrm{1L,ct}}_{\tilde{g}^a \overline{\tilde{g}}^b}  \right]_{\slashed{p} = m_{\tilde{g}}} = 0
+& \frac{\partial}{\partial (P_L\slashed{p})} \left[ \Re (\Gamma^{\mathrm{1L}}_{\tilde{g}^a \overline{\tilde{g}}^b}) + \Gamma^{\mathrm{1L,ct}}_{\tilde{g}^a \overline{\tilde{g}}^b}  \right]_{\slashed{p} = m_{\tilde{g}}} = 0,
 && \frac{\partial}{\partial (P_R\slashed{p})} \left[ \Re (\Gamma^{\mathrm{1L}}_{\tilde{g}^a \overline{\tilde{g}}^b}) + \Gamma^{\mathrm{1L,ct}}_{\tilde{g}^a \overline{\tilde{g}}^b}  \right]_{\slashed{p} = m_{\tilde{g}}} = 0
@@
 where the derivative of $\Sigma = \Sigma^{VL}P_L\slashed{p} + \Sigma^{VR}P_R\slashed{p} + \Sigma^{SL}P_L + \Sigma^{SR}P_R$ with respect to $P_A\slashed{p}$ \\
-($A = L,R$) is defined by
+($A \in \left\{ L,R \right\}$) is defined by
 \begin{align}
@@
 
-\subsection{Renormalization of the Gauge Coupling}
+\subsection{Renormalization of the Gauge Coupling}\label{sec:RenGaugeCoupling}
 The gauge coupling $g_s$ is renormalized in the $\overline{\mathrm{MS}}$-scheme with the modification that additional logarithms are subtracted, i.e.
@@
 This is to decouple heavy particles from the running of $\alpha_s = \frac{g_s^2}{4\pi}$.
-This renormalization procedure allows to adopt the experimental values of $\alpha_s$ from the PDF's.
+This renormalization procedure allows to adopt the experimental values of $\alpha_s$ from the parton density functions.
 The running due to effects of heavy particles is then encoded in the logarithms of $\delta g_s$.\\
@@
 
-\subsubsection*{The Gluon Self-Energy}
-As for the quark self-energy there are again contributions to the self-energy originating from light and heavy particles. Again these are differently dealt with.
 \begin{figure}[!htbp]
@@
 \end{figure}
+
+\subsubsection*{The Gluon Self-Energy}
+As for the quark self-energy there are again contributions to the self-energy originating from light and heavy particles. Again these are differently dealt with.
 \begin{align}
@@
 \end{align}
-Both contributions the one from the gluon loop and the one from the ghost loop are not proportional to $(p^2g^{\mu\nu}-p^\mu p^\nu)$ but their sum is.
+Both the contribution from the gluon loop and the one from the ghost loop are not proportional to $(p^2g^{\mu\nu}-p^\mu p^\nu)$ but their sum is.
 \begin{figure}[!htbp]
@@
 \end{tikzpicture}
-\caption{contribution to the self-energy of the gluon originating from heavy particles, in the last diagram either $\phi^0$ or $\sigma^0$ are running in the loop}
+\caption{Contribution to the self-energy of the gluon originating from heavy particles, in the last diagram either $\phi^0$ or $\sigma^0$ are running in the loop}
 \end{center}
@@
 \end{tikzpicture}
-\caption{Contribution from light (Standard Model) particles to the $q\overline{q}G$ vertex. correction}\label{fig:GaugeCouplingCorrection}
+\caption{Contribution from light (Standard Model) particles to the $q\overline{q}G$ vertex correction}\label{fig:GaugeCouplingCorrection}
 \end{center}
 \end{figure}
+The contributions from Standard Model particles to the $q\overline{q}G$ yield
 \begin{align}
@@
 &\left.+ C(A)(B_0(0, 0, 0) + 2C_{00}(0,0,0,0,0))\right]\nonumber\\
-&= -i g_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} \Delta_\epsilon \left[ \left(C(F) -\frac{C(A)}{2}\right) + \frac{3}{2} C(A) \right]\label{eq:qqGlight}
+&= -i g_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} \Delta_\epsilon \left[ \left(C(F) -\frac{C(A)}{2}\right) + \frac{3}{2} C(A) \right].\label{eq:qqGlight}
 \end{align}
@@
 \ref{eq:qqGlight} corresponds to the first diagram in fig.
-\ref{fig:GaugeCouplingCorrection} whereas the last term in the squared brackets corresponds to the second diagram.
+\ref{fig:GaugeCouplingCorrection} whereas the term with the prefactor $C(A)$ corresponds to the second diagram.
 \begin{figure}[!htbp]
@@
 \end{figure}
+The 3-point-function with only heavy particles running in the loop evaluates to
 \begin{align}
@@
 \end{align}
-The argument $p_i^2=0$ of the vertex function denotes, that all external particles are taken on shell, i.e.
-at zero momentum.
-In the second line identities from \ref{sec:Passarino} have been used.
-The renormalization condition for the counterterm of the gauge coupling $\delta g_s$ reads
+The argument $p_i^2=0$ of the vertex function denotes, that all external particles are taken on shell, i.e. at zero momentum.\\
+insert $B_1$ function in order to cancel contribution from quark ren.const\\
+In the second line identities from \ref{sec:Passarino} have been used. The renormalization condition for the counterterm of the gauge coupling $\delta g_s$ reads
 \begin{align}
@@
 \end{align}
-Finally one can read off the $\frac{\delta g_s}{g_s}$
+Finally one can read off $\frac{\delta g_s}{g_s}$
 \begin{align}
 \frac{\delta g_s}{g_s} &= \frac{g_s^2}{16\pi^2} \left[ \left( \frac{2}{3}T(F)(n_f-1) - \frac{11}{6}C(A) \right) \Delta_\epsilon + \left( \frac{5}{6}C(A) + \frac{2}{3}T(F) + \frac{1}{3}T(F)n_f \right)\Delta_\epsilon  \right.\nonumber\\
-&- \frac{2}{3} C(A) \ln \frac{m_{\tilde{g}}^2}{\mu^2} - \frac{1}{3}T(F)n_f \ln \frac{m_{\tilde{q}}^2}{\mu^2} - \frac{2}{3}T(F) \ln \frac{m_t^2}{\mu^2}-\frac{1}{12} C(A) \left( \ln \frac{m_{\phi^0}^2}{\mu^2} + \ln \frac{m_{\sigma^0}^2}{\mu^2} \right)\label{eq:deltaGs}
+&- \frac{2}{3} C(A) \ln \frac{m_{\tilde{g}}^2}{\mu^2} - \frac{1}{3}T(F)n_f \ln \frac{m_{\tilde{q}}^2}{\mu^2} - \frac{2}{3}T(F) \ln \frac{m_t^2}{\mu^2}-\frac{1}{12} C(A) \left( \ln \frac{m_{\phi^0}^2}{\mu^2} + \ln \frac{m_{\sigma^0}^2}{\mu^2} \right).\label{eq:deltaGs}
 \end{align}
+Note the only difference to the MSSM is the appearence of the sgluon masses as well as a factor of two in front of the logarithm of the gluino mass which is due to twice as much degrees of freedom of the gluino in the MRSSM.
 
@@
 As already discussed in section \ref{sec:RegSchemeDep} care is required in terms of supersymmetry restoring when renormalizing  the gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$.
-In doing so one needs the already calculated supersymmetry restoring counterterms of the quark, squark and gluino from \ref{eq:QuarkSC}, \ref{eq:SquarkSC} and \ref{eq:GluinoSC}
-as well as the supersymmetry restoring counterterm of the gluon.
+In doing so one needs the already calculated transition counterterms of the quark, squark and gluino from \ref{eq:QuarkSC}, \ref{eq:SquarkSC} and \ref{eq:GluinoSC}
+as well as the transition counterterm of the gluon.
 \subsubsection*{The Gluon Self-Energy Revisited}
@@
 \subsubsection*{The $q\overline{q}G$ Vertex Correction Revisited}
-The supersymmetry restoring contributions to the gauge coupling correction are shown in figure \ref{fig:GaugeCouplingCorrection} and evaluate to
+The diagrams from which the supersymmetry restoring contributions to the gauge coupling correction come from are shown in figure \ref{fig:GaugeCouplingCorrection} and evaluate to
 \begin{align}
@@
 \end{align}
-where in the second line the equation with the supersymmetry restoring counterterms has been performed. This yields
+where the second line shows the supersymmetry restoring counterterms. This yields
 \begin{align}
@@
 \subsubsection*{The $q\tilde{q}^\dagger\tilde{g}$ Vertex Correction}
-The supersymmetry restoring corrections to the Yukawa coupling origin from the below diagram 
+The supersymmetry restoring corrections to the Yukawa coupling origin from the diagram below.
 \begin{figure}[!htbp]
@@
 \end{figure}
-The supersymmetry restoring part is
+The supersymmetry restoring part is given by
 \begin{align}
@@
 As a consequence of the two different supersymmetry restoring parts of the coupling renormalization constants an additional renormalization constant $\delta g_s^{\mathrm{restore}}$ needs to be introduced.
-As described in section \label{sec:RegSchemeDep} it is given by
+As described in section \ref{sec:RegSchemeDep} it is given by
 \begin{align}
@@
 In short this means that the gauge coupling $g_s$ is renormalized with $\delta g_s$ given in \ref{eq:deltaGs} and the Yukawa coupling $\hat{g}_s$ is renormilzed with $\delta \hat{g}_s = \delta g_s + \delta g_s^{\mathrm{restore}}$.\\
-The finite correction $g_s^{\mathrm{restore}}$ is the same as in supersymmetric QCD which should not surprise too much as all its contributions origin from loops with gluons.
-So there are no new contributions in RSQCD with respect to SQCD.
+The finite correction $\delta g_s^{\mathrm{restore}}$ is the same as in supersymmetric QCD which should not surprise too much as all its contributions originate from loops with gluons.% So there are no new contributions in RSQCD with respect to SQCD.
 

### 2016-06-07 Standardmodel.tex
TreeLevel CrossSection and SM-Introduction

@@
 The Standard Model of particle physics is the commonly accepted theory describing the world's fundamental particles and their interactions.
-It is a gauge quantum field theory which is characterized by its invariance under different symmetry groups.
+It is a gauge quantum field theory which is characterized by its invariance under symmetry groups.
 The Standard Model contains different fields, whose quantized excitations are interpreted as particles.\\
+This chapter summarizes the most important aspects of the Standard Model.
 %The different fields defined on Minkowski space are Dirac spinors describing matter fields (leptons and quarks), gauge vectors describing force mediators and a scalar field (the Higgs) which accounts for the masses of particles.\\
@@
 \subsubsection*{Spacetime Symmetries}
-The Standard Model is defined on Minkowski space, whose coordinates are label with $x^\mu$ $\mu = \left\{0,1,2,4\right\}$.
+The Standard Model is defined on Minkowski space, whose coordinates are label with $x^\mu$ $\mu \in \left\{0,1,2,4\right\}$.
 As a relativistic theory it is invariant under Poincaré transformations, i.e.
@@
 \subsubsection*{Gauge Symmetries} 
-In order to describe interactions of matter particles one uses gauge theories. In the Standard Model matter fields are described by Dirac spinors. The Lagrangian of a free Dirac field reads
+In order to describe interactions of matter particles gauge theories are used. In the Standard Model matter fields are described by Dirac spinors. The Lagrangian of a free Dirac field reads
 \begin{align}
@@
 Because the parameters of the gauge group are local the derivative in \ref{eq:DiracLagrangian} spoils the gauge invariance.
-In order to rectify gauge invariance of the Lagrangian one can introduce a further field for each index $a$ of the generators - the gauge vector $G^{a\mu}$.
+In order to rectify gauge invariance of the Lagrangian one introduces a further field for each index $a$ of the generators - the gauge vector $G^{a\mu}$.
 Defining the transformation of the matrix valued gauge vector $G^\mu := G^{a\mu}T^a$ as
 \begin{align}
-G^{\mu}(x) \to U(x) \left( G^\mu(x) + \frac{i}{g}\partial^\mu \right) U^{-1}(x)
+G^{\mu}(x) \to U^{-1}(x) \left( G^\mu(x) + \frac{i}{g}\partial^\mu \right) U(x)
 \end{align}
@@
 \end{align}
-Therefore gauge invariance in \ref{eq:DiracLagrangian} is restored by replacing $\partial_\mu$ with $D_\mu$.
+Therefore gauge invariance is restored in eq.
+\ref{eq:DiracLagrangian} by replacing $\partial_\mu$ with $D_\mu$.
 But if the gauge vector is interpreted as a physical field there must apart from the so far introduced interaction term also be a kinetic term associated with it.
-Using \ref{eq:CovDerivative} one defines the field strength tensor\footnote{An alternative construction makes use of the gauge invariant Wilson loop.
+Using eq.
+\ref{eq:CovDerivative} one defines the field strength tensor\footnote{An alternative construction of the field strength tensor makes use of the gauge invariant Wilson loop.
 This gives some insights into the geometry of gauge transformations \cite{Peskin}.} $F^{a\mu\nu}$ whose matrix valued form
 \begin{align}
-F^{\mu\nu} = F^{a\mu\nu}T^a = \frac{1}{ig}[D^\mu,D^\nu] = \partial^\mu G^\nu - \partial^\nu G^\mu - i f_{abc}....
+F^{\mu\nu} = F^{a\mu\nu}T^a := \frac{1}{ig}[D^\mu,D^\nu] = \partial^\mu G^\nu - \partial^\nu G^\mu - g f_{abc} T^c G^{a\mu}G^{b\nu}
 \end{align}
 transforms as $F^{\mu\nu} \to U(x)F^{\mu\nu}U^{-1}(x)$.
-Using the cyclic property of the trace and the Dynkin index $T(F)$ defined in the appendix \ref{eq:DynkinIndex}  one can write down a gauge invariant kinetic term for the gauge vector:
+Using the cyclic property of the trace and the Dynkin index $T(F)$ defined in eq.
+\ref{eq:DynkinIndex} in the appendix one can write down a gauge invariant kinetic term for the gauge vector:
 \begin{align}
@@
 \end{align}
-This completes the construction of a Lagrangian which is invariant under non-abelian gauge group transformations. The result is the famous Yang and Mills Lagrangian[cite original paper]
+This completes the construction of a Lagrangian which is invariant under non-abelian gauge group transformations. The result is the famous Yang and Mills Lagrangian \cite{PhysRev.96.191}
 \begin{align}
@@
 \end{align}
-This Lagragian gives rise to spin-$\frac{1}{2}$ (matter) particles which interact with spin-1 (force mediator) particles with each other.
+This Lagragian gives rise to spin-$\frac{1}{2}$ (matter) particles which interact with spin-1 (force mediator) particles.
 Furthermore if the gauge group is non-abelian, i.e.
 $f_{abc} \neq 0$, there are self interactions among the spin-1 particles.\\
-The gauge group of the SM is a direct product ???
-of the three gauge groups: $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$\footnote{The subscript stands for the associated charge of the groups respectively: $Y$ for hypercharge, $L$ for left handedness (weak Isospin $I_3$) and $C$ for color}.
-The elements $U(x)$ of those and the infinitesimal transformations of the spinors and gauge vectors are given in table \ref{tab:SM_transformations}.\\
+The gauge group of the Standard Model is a direct product of the three gauge groups\footnote{The subscript stands for the associated charge of the groups respectively: $Y$ for hypercharge, $L$ for left handedness (weak Isospin $I_3$) and $C$ for color}: $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$.
+The elements $U(x)$ of those are given in table \ref{tab:SM_transformations}.\\
 These gauge groups give rise to 3 forces: the strong force, the weak force and the electromagnetic force.
@@
 \begin{center}
-\begin{tabular}{|c|l|}
+\begin{tabular}{c?c}
+Gauge Group & Group Element\\
+\hlinewd{2pt}
+$U_Y(1)$ & $U(x) = \mathrm{exp}\left(-ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)$\\
 \hline
- & $U(x) = \mathrm{exp}\left(-ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)$\\
- $U_Y(1)$ & $\psi(x) \to \left( 1 - ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)\psi(x)$\\
- & $B^\mu(x) \to B^\mu(x) + \partial^\mu\theta_Y(x)$\\
+$SU_L(2)$ & $U(x) = \mathrm{exp}\left(-ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)$\\
 \hline
- & $U(x) = \mathrm{exp}\left(-ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)$\\
- $SU_L(2)$ & $\psi(x) \to \left( \mathbbm{1} - ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)\psi(x)$\\
- & $W^{a\mu}(x) \to W^{a\mu}(x) +\partial^\mu\theta^a_w(x) + g_w \varepsilon^{abc} \theta^b_w(x)W^{c\mu}(x)$\\
-  \hline
- & $U(x) = \mathrm{exp}\left(-ig_s T^a \cdot \theta_s^a(x)\right)$\\
-$SU_C(3)$ & $\psi(x) \to \left(\mathbbm{1}-ig_s T^a \cdot \theta_s^a(x)\right)$\\
- & $G^{a\mu}(x) \to G^{a\mu}(x) + \partial^\mu\theta^a_s(x) + g_s f_{abc} \theta^b_s(x)G^{c\mu}$\\
- \hline
+$SU_C(3)$ & $U(x) = \mathrm{exp}\left(-ig_s T^a \cdot \theta_s^a(x)\right)$
 \end{tabular}
-\caption{The table lists the explicit element $U(x)$ of the gauge groups $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$ and the infinitesimal transformations of spinor and vector fields.\newline
-The hypercharge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to.
+\caption{The table lists the explicit element $U(x)$ of the gauge groups $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$.
+The hypercharge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to (see table \ref{tab:SMfieldcontent}).
+$\vec{\tau}$ and $T^a$ are the geneators of $SU_L(2)$ and $SU_C(3)$ respectively.
+In the fundamental representation $\vec{\tau} = \frac{\vec{\sigma}}{2}$ where $\vec{\sigma}$ has the 3 Pauli matrices as components and $T^a = \frac{\lambda^a}{2}$ where $\lambda^a$ are the 8 Gell-Mann matrices.
+$\varepsilon_{abc}$ and $f_{abc}$ are the structure constants of $SU_L(2)$ and $SU_C(3)$ respectively.}\label{tab:SM_transformations}
+\end{center}
+\end{table}
+
+%\begin{table}[H]
+%\begin{center}
+%\begin{tabular}{|c|l|}
+%\hline
+% & $U(x) = \mathrm{exp}\left(-ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)$\\
+% $U_Y(1)$ & $\psi(x) \to \left( 1 - ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)\psi(x)$\\
+% & $B^\mu(x) \to B^\mu(x) + \partial^\mu\theta_Y(x)$\\
+%\hline
+% & $U(x) = \mathrm{exp}\left(-ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)$\\
+% $SU_L(2)$ & $\psi(x) \to \left( \mathbbm{1} - ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)\psi(x)$\\
+% & $W^{a\mu}(x) \to W^{a\mu}(x) +\partial^\mu\theta^a_w(x) + g_w \varepsilon^{abc} \theta^b_w(x)W^{c\mu}(x)$\\
+%  \hline
+% & $U(x) = \mathrm{exp}\left(-ig_s T^a \cdot \theta_s^a(x)\right)$\\
+%$SU_C(3)$ & $\psi(x) \to \left(\mathbbm{1}-ig_s T^a \cdot \theta_s^a(x)\right)$\\
+% & $G^{a\mu}(x) \to G^{a\mu}(x) + \partial^\mu\theta^a_s(x) + g_s f_{abc} \theta^b_s(x)G^{c\mu}$\\
+% \hline
+%\end{tabular}
+%\caption{The table lists the explicit element $U(x)$ of the gauge groups $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$ and the infinitesimal transformations of spinor and vector fields.\newline
+%The hypercharge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to.
 $\vec{\tau}$ and $T^a$ are the geneators of $SU_L(2)$ and $SU_C(3)$ respectively.
@@
 $\varepsilon_{abc}$ and $f_{abc}$ are the structure constants of $SU_L(2)$ and $SU_C(3)$ respectively.}\label{tab:SM_transformations}
-\end{center}
-\end{table}
+%\end{center}
+%\end{table}
 
@@
 
-\newpage
 \subsection{The Particles of the Standard Model}
@@
 This convention is adopted throughout this thesis.\\
-Furthermore the left handed component of quarks interact weakly, which means that their spinors transform (in the fundamental representation) under $SU_L(2)$ meaning that 2 left handed quark spinors are assembled in a doublet.\\
+Furthermore the left handed component of quarks interact weakly, which means that their spinors\footnote{The left handed part of a 4-spinor $\Psi$ is projected out by the appropriate projector $P_L$.
+This is explained in Appendix \ref{sec:2spinor_notation}.} transform (in the fundamental representation) under $SU_L(2)$ transformations meaning that 2 left handed quark spinors are assembled within a doublet.\\
 Finally all quarks carry a hypercharge.
-In section ???
-the mechanism of electroweak symmetry breaking is described.
+In section \ref{sec:EWSB} the mechanism of electroweak symmetry breaking is described.
 This mechanism explains how electromagnetism arises from the groups $SU_L(2)$ and $U_Y(1)$.
 All quarks interact electromagnetically.\\
-After all there are 6 quarks which are listed in table\ref{tab:generations}.
-They are categorized in 3 generations because their quantum numbers except (for their mass) is the same in each generation.
-The two types of quarks which have distinct quantum numbers are the up-type-quarks and the down-type quarks.
-A up-type-quark and the down-type quark of the same generation built up a doublet.
+After all there are 6 quarks which are listed in table \ref{tab:generations}.
+They are categorized in 3 generations because their quantum numbers except for their masses reoccur in each generation.
+The two types of quarks within a generation which have distinct quantum numbers are referred to as up-type and down-type quarks.
+An up-type-quark and the down-type quark of the same generation built up a doublet.
 \subsubsection*{The Leptons:}
@@
 Each left handed leptons with an electric charge is assembled with its neutrino in a doublet.
-\bigbreak
-Quarks and Leptons are the matter particles of the SM.
-They are listed together with their charges for the different forces in table \ref{tab:SMfieldcontent}.
-One has the color for strong interactions, the third component of the weak isospin $I_3$ for weak interactions(the eigenvalue of the third generator of the $SU_L(2)$) and the half of the hypercharge $\frac{Y}{2}$ to obtain the electric charge $Q$ via the Gell-Mann–Nishijima formula: $Q = I_3 + \frac{Y}{2}$.\\
-Because the left and right-handed parts of spinors transform differently under the $SU_L(2)$ they are listed separately.\\
-All quarks occur with three different colors.\\
-In the last row the Higgs-boson is listed. Its associated field is responsible for the mass of elementary particles. That is explained in section \ref{sec:EWSB}.\\
 \begin{table}[H]
@@
 \end{table}
+Quarks and Leptons are the matter particles of the Standard Model.
+They are listed together with their charges for the different forces in table \ref{tab:SMfieldcontent}.
+There is the color for strong interactions, the third component of the weak isospin $I_3$ for weak interactions (the eigenvalue of the third generator of the $SU_L(2)$) and the half of the hypercharge $\frac{Y}{2}$ to obtain the electric charge $Q$ via the Gell-Mann–Nishijima formula: $Q = I_3 + \frac{Y}{2}$.\\
+Because the left and right-handed parts of spinors transform differently under the $SU_L(2)$ they are listed separately. All quarks occur with three different colors.\\
+In the last row the Higgs-boson is listed. Its associated field is responsible for the mass of elementary particles. That is explained in section \ref{sec:EWSB}.\\
 \begin{table}[H]
@@
 \end{tabular}
-\caption{This table lists all matter particles in the SM and the Higgs particle with their charges for all forces.
+\caption{This table lists all matter particles in the Standard Model and the Higgs particle with their charges for all forces.
 This is the color, the weak isospin $I_3$, the half of their hypercharge and their electrical charge.
-The index $i = 1,2,3$ labels the generation of the matter particles and is written out in table \ref{tab:generations}}\label{tab:SMfieldcontent}
+The index $i = 1,2,3$ labels the generation of the matter particles and is written out in table \ref{tab:generations}.
+If there are no colors specified or charges are zero this means that the fields in question transform trivially under the pertaining gauge transformation.}\label{tab:SMfieldcontent}
 \end{center}
 \end{table}
+
 \subsubsection*{The Force Particles}
-The force particles are described by gauge fields. The gluon field is the gauge field of $SU_C(3)$. Because the $SU_C(3)$ has 8 generators there are 8 gluons. Their coupling constant is $g_s$.\\
-For the other force particles in the SM - the $W^\pm$ bosons, the $Z_0$ boson and the photon the is situation is slightly more involved.
-They are obtained as a mixture of the $W^b_\mu$ ($b=1,2,3$)and the $B_\mu$ field.
-This mixing procedure is referred to as electroweak symmetry breaking and is explained in section???.\\
-For the moment being the coupling constants and gauge fields before and after EWSB are quoted in table \ref{tab:force_particles}
 \begin{table}[H]
@@
 \end{tabular}
-\caption{The gauge fields and their coupling constants before and after EWSB.
+\caption{The gauge fields and their coupling constants before and after electro weak symmetry breaking (EWSB).
 The Gluon field is not affected by EWSB.
@@
 \end{table}
+The force particles are described by gauge fields.
+The gauge field of $SU_C(3)$ is the gluon field.
+Because the $SU_C(3)$ has 8 generators there are 8 gluons.
+Their coupling constant is denoted with $g_s$.\\
+For the other force particles in the Standard Model - the $W^\pm$ bosons, the $Z_0$ boson and the photon the situation is slightly more involved.
+They are obtained as a mixture of the $W^b_\mu$ ($b=1,2,3$) and the $B_\mu$ field which are the gauge fields of $SU_L(2)$ and $U_Y(1)$ respectively.
+This mixing procedure is explained in section \ref{sec:EWSB}.\\
+For the moment being the coupling constants and gauge fields before and after this mixing are quoted in table \ref{tab:force_particles}.\bigbreak
 The Lagrangian of the SM is built up by qualitatively different terms. Firstly there are the kinetic and minimal coupling terms of the matter fields 
 \begin{align}
-\mathcal{L}_{matter} =  \sum_{i=1}^3 \left( \overline{\ell}_{iL} i \slashed{D} l_{iL} + \overline{e}_{iR} i \slashed{D} e_{iR} + \overline{q}_{iL} i \slashed{D} q_{iL} + \overline{u}_{iR} i \slashed{D} u_{iR} \right)
+\mathcal{L}_{\mathrm{matter}} =  \sum_{i=1}^3 \left( \overline{\ell}_{iL} i \slashed{D} l_{iL} + \overline{e}_{iR} i \slashed{D} e_{iR} + \overline{q}_{iL} i \slashed{D} q_{iL} + \overline{u}_{iR} i \slashed{D} u_{iR} \right)
 \end{align}
-where $i=1,2,3$ labels the generations of matter. The gauge covariant derivative is given by
+where $i \in \left\{1,2,3\right\}$ labels the generations of matter. The gauge covariant derivative is given by
 \begin{align}
@@
 The hyper charge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to.
-These can be found in table \ref{tab:SMfieldcontent}.
+These can also be found in table \ref{tab:SMfieldcontent}.
 The kinetic terms of the gauge fields are given by
 \begin{align}
-\mathcal{L}_{gauge} = -\frac{1}{4}F^{\mu\nu}F_{\mu\nu} - \frac{1}{4}W^{a\mu\nu}W^a_{\mu\nu} - \frac{1}{4}G^{a\mu\nu}G^a_{\mu\nu}
+\mathcal{L}_{gauge} = -\frac{1}{4}F^{\mu\nu}F_{\mu\nu} - \frac{1}{4}W^{a\mu\nu}W^a_{\mu\nu} - \frac{1}{4}G^{a\mu\nu}G^a_{\mu\nu}.
 \end{align}

### 2016-06-07 TreeLevel.tex
TreeLevel CrossSection and SM-Introduction

@@
 
-\subsection{Partonic Processes and their Cross Section} 
+\subsection{Partonic Processes and their Cross Section}\label{sec:PartProcesses}
 \begin{figure}[!htbp]
@@
 \end{align}
+where $m_1$ ($m_2$) is the mass of the first (second) final state particle and $m$ is their arithmetic mean.
 The leading order cross sections are
@@
 \begin{align}
-\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(P_i P_j \to X).
+\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(P_i P_j \to X)
 \end{align}
-To get an intuitive idea of this factorization consider the hadrons as extended objects consisting of partons\footnote{The proton is considered as composed of three valence quarks: Two up-quarks and one down-quark.
+where the sum runs over all partons $P_i$ ($P_j$) which are in the hadron $H_1$ ($H_2$).\\
+To get an intuitive idea of this factorization regard the hadrons as extended objects consisting of partons\footnote{The proton is considered as composed of three valence quarks: Two up-quarks and one down-quark.
 In addition there are gluons and seaquarks, i.e.
@@
 \caption{Parton density function of the proton, taken from $\mathtt{MMHT2014}$ \cite{Harland-Lang:2014zoa} with 68\% confidence level.
-The pdf is multiplied by $x$ in order to counteract its peak at $x \to 0$.
+The parton density function is multiplied by $x$ in order to counteract its peak at $x \to 0$.
 The parton density function is given at two different factorisaction scales $\mu_F = Q$}\label{fig:pdfs}
@@
 two up-squarks can only be produced by two up-quarks.
-Because the partonic cross section for these processes are all the same cf.
+Because the partonic cross section for these processes are  the same, cf.
 eq.
-\ref{eq:PartonicEquality} one can see the influence of the parton density functions quite nicely: The up-squark production is the dominant contribution to squark production.
+\ref{eq:PartonicEquality}, one can see the influence of the parton density functions quite nicely: The up-squark production is the dominant contribution to squark production.
 Apart from the solid lines in fig.\ref{fig:TreeXsection} which correspond to the production of first generation squarks, also the cross section of mixed first and second generation (dashed lines) and second generation (dotted lines) squarks is shown.
 The dashed dotted line shows the cross section of the charged conjugated particles of the dominant channel.\\
-refer to Kribs, Martin
+REFER TO Kribs, Martin: SNOWMASS WHITEPAPER\\
+REFER TO Vernoica Sanz: How many SUpersymmetries?\\
+\\
+The following paragraph discusses fig.
+\ref{fig:TreeXsection}, \ref{fig:TreeLevelSigma_0,9_2} and \ref{fig:TreeXsection5}, i.e.
+the hadronic cross section of all considered processes for three successive mass ratios of the gluino and squark: $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9,\ 2$ and $5$.
+Also the corresponding fraction of final states is shown.\\
 \begin{figure}[!htpb]
@@
 \includegraphics[scale=.4]{figures/mr=2_MSSM+MRSSM}
-\caption{Hadronic cross section for squark and gluino production in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
+\caption{Hadronic cross section for squark and gluino production in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC with $\sqrt{S} = \unit[13]{GeV}$.
 The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row).
-In the final state it has been summed over all squark flavors expect for staus.
+In the final state it has been summed over all squark flavors expect for $t$-squarks.
 For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
@@
 \includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
-\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
+\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC with $\sqrt{S} = \unit[13]{GeV}$.
 The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row).
-In the final state it has been summed over all squark flavors expect for staus.
+In the final state it has been summed over all squark flavors expect for $t$-quarks.
 For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
@@
 
-refer to Vernoica Sanz: How many SUpersymmetries?
-\paragraph{qqbar to sqsqdagger}
-This channel dominates squark and gluino production for a large gluino mass but smaller squark masses.
-\paragraph{qq to sqsq} Looking at the hadronic cross section in fig.
-\ref{fig:TreeXsection} can see the suppression of squark production in the MRSSM in comparison to the MSSM.
-One can also see that this suppression grows when going from $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ to  $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ or even to  $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 5$ in fig.
+For the small mass ratio $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ and small squark masses the dominant contribution comes from gluino (antigluino) production.
+This is even more dominant in the MRSSM which can be explained by the above mentioned factor of 2 difference in the $GG \to \tilde{g}\tilde{g}(\overline{\tilde{g}})$ channel which comes from the distinguishable gluino and antigluino in the MRSSM.
+Furthermore there is the above mentioned destructive interference term in the $q\overline{q} \to \tilde{g}\tilde{g}(\overline{\tilde{g}})$ channel which makes the cross section in the MRSSM dominant over the one in the MSSM.\\
+For a growing squark mass the previously subdominant gluino-squark production takes over and becomes dominant.
+A salient difference between the MSSM and the MRSSM is that squark production is strongly suppressed in the MRSSM.
+While in the MSSM it becomes dominant above about $\unit[1700]{GeV}$ it is subsubdominant for the whole displayed squark mass in the MRSSM.
+This suppression has also already been explained above.\\
+Turning from $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ to $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ suppresses quite strongly the production of gluinos in all pertaining channels.
+For the MSSM one finds above $\unit[500]{GeV}$ a growing dominance of squark production.
+The same happens in the MRSSM but for a significantly higher squark mass of about $\unit[1300]{GeV}$.
+This suppression of squark production in the MRSSM increases with a growing gluino masses which can be seen when going from $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ to  $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ or even  $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 5$ in fig.
 \ref{fig:TreeXsection5}.
-This reflects the gluino mass dependence explained above.
+This reflects the gluino mass dependence explained in detail in section \ref{sec:PartProcesses}.
 See also \ref{fig:TreeXsection_fixed_m} for a visualization of this behavior.\\
-Note also that for sufficiently large squark masses squark production is the dominant process, see fig.
+Note also that for sufficiently large squark masses squark production becomes the dominant process, see fig.
 \ref{fig:TreeXsection} and \ref{fig:TreeLevelSigma_0,9_2}.
@@
 \ref{fig:pdfs} one sees that within the proton the partons most likely to carry large momentum are quarks.
-So looking at large $x$ the proton basically consists of quarks and because the only process involving only quarks in the initial state is squark production, this channel dominates for high masses.
-\paragraph{qqbar to ggbar}
-For a growing gluino mass it is this interference term which makes the cross section in the MRSSM dominant over the one in the MSSM.
+So looking at large $x$ the proton basically consists of quarks and because the only process involving only quarks in the initial state is squark production, this channel dominates for high masses.\\
+The total cross section in the MRSSM is increasingly smaller than in the MSSM in particular from about $\unit[500]{GeV}$ onwards.
+The is because for masses below that the $GG \to \tilde{q}\tilde{q}^\dagger$ channel which is the same for both models is the dominant one.\\
+When raising the gluino squark mass ratio further to $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 5$ the above described tendency continues.
+This is all processes including a gluino get even more negligible and squark production gets further suppressed.
+While in the MSSM it becomes dominant over $GG \to \tilde{q}\tilde{q}^\dagger$ at $m_{\tilde{q}} \approx \unit[1000]{GeV}$ it is subdominant in the MRSSM in the whole displayed mass range.
+even though it does not fall that steeply as the dominant channel.\\
 
@@
 \includegraphics[scale=.45]{figures/rel_weights_mr=5_MSSM+MRSSM}
-\caption{Hadronic cross section for squark and gluino production (in the first row) and relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$.
+\caption{Hadronic cross section for squark and gluino production (in the first row) and relative contributions of the indicated final states on the total hadronic cross section (in the second row) in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC which $\sqrt{S} = \unit[13]{GeV}$.
 The ratio of gluino and squark mass is fixed to 5.
@@
 \end{figure}
-
+The following contour plots underline the already announced difference between squark production in the MRSSM and the MSSM.
+The main difference is a suppression of the cross section for higher gluino masses in the MRSSM.
 \begin{figure}[!htpb]
@@
 \end{figure}
+As a summary of the comparison between MSSM and MRSSM gluino production one can say, that the gluino production is enhanced in the MRSSM due to distinguishable gluino and antigluino.
+In order to meet missing experimental evidence for supersymmerty this suggests that gluinos might be heavier than squarks in the MRSSM.
+Focusing on $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} \geq 2$ the most significant change between the considered models is the growing suppression of squark production for a increasing gluino mass.
+This is why this channel is going to be investigated at next-to-leading order in the ensuing sections.

### 2016-06-07 figures/Contour_Plots/MSSM_TreeLevel.py

@@ -1,72 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-plot of cross section as contour with squark and gluino mass as axis
-"""
-
-from matplotlib import pyplot as plt
-import numpy as np
-from matplotlib.colors import LogNorm
-
-                          
-def nans(shape, dtype=float):
-    """grid of shape full nan"""
-    a = np.empty(shape, dtype)
-    a.fill(np.nan)
-    return a
-
-# grid size
-N = 50 
-
-def contourdata():
-    """
-    
-    """
-    mass = np.linspace(100, 2000, num=N)
-    mass = np.linspace(100, 2000, num=N)
-    # note reverse ordering for yi and xi because of the way   
-    # shape works in numpy                                                  
-    sigma = nans((len(mass),len(mass)))  
-    myfile = open('qq_to_sqsq_MSSM_with_antiquarks.tex', 'r')     
-    i = 0
-    for line in myfile:
-        data = line.split()
-        for j in range(0,N):
-            sigma[j][i] = data[j]
-        i += 1   
-    myfile.close()
-    
-    fig = plt.figure(1,figsize=(9, 8)) 
-    ax1 = plt.axes()
-    font_size = 18
-    plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
-    plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
-    plt.xticks(fontsize = font_size)
-    plt.yticks(fontsize = font_size)
-    cf=ax1.contourf(mass, mass, sigma, norm = LogNorm())
-    levels1 = [0.1, 1, 10**3, 10**4, 10**5, 10**6]
-    cl1 = plt.contour(cf, levels=levels1,
-                  colors='k',
-                  linewidths=(1,),
-                  hold='on')    
-    levels2 = [10,100]
-    cl2 = plt.contour(cf, levels=levels2,
-                  colors='k',
-                  linewidths=(2,),
-                  hold='on')
-    levels3 = [20,50]
-    cl3 = plt.contour(cf, levels=levels3,
-                  colors='k',
-                  linestyles='dashed',
-                  linewidths=(1,),
-                  hold='on')
-    plt.clabel(cl2, fmt='%2.1f', colors='k', fontsize = font_size)
[…]

### 2016-06-08 Appendix.tex
mainly SM chapter revised

@@
 \end{align}
-where $\sigma^i$ are the Pauli matrices and $\mathbbm{1}_n$ is the $n$x$n$ unit matrix. The left and right handed projectors are then given by
+where $\sigma^i$ are the Pauli matrices and $\mathbbm{1}_n$ is the $n \times n$ unit matrix. The left and right handed projectors are then given by
 \begin{align}
@@
 \end{align}
-The generator of the Lorentz group on 4-spinor space is composed of the above matrices.
+The representation of generators of the Lorentz group on 4-spinor space are composed of the above matrices.
 Because of the block form of those it is not surprising that the representation on 4-spinor space is reducible to two representations on 2-spinor (Weyl spinor) spaces.
-It is therefore sensible to decompose a 4 spinor into a left and a right handed Weyl spinor\footnote{The projectors in the chiral basis \ref{eq:projectors} explain the names left and right handed Weyl spinors.}
+It is therefore sensible to decompose a 4 spinor into a left and a right handed Weyl spinor\footnote{The projectors in the chiral basis (eq.
+\ref{eq:projectors}) explain the names left and right handed Weyl spinors.}
 \begin{align}
@@
 \end{align}
-where $\alpha,\dot{\alpha} = 1,2$. Left handed Weyl spinors are labeled with undotted and right handed Weyl spinors with dotted indices. One distinguishes 4 different Weyl spinors:
+where $\alpha,\dot{\alpha} \in \left\{ 1,2 \right\}$. Left handed Weyl spinors are labeled with undotted and right handed Weyl spinors with dotted indices. One distinguishes 4 different Weyl spinors:
 \begin{align}
@@
 \end{align}
-By virtue of the antisymmetry of $\epsilon$ one has for the Lorentz invariant product:
+By virtue of the antisymmetry of $\epsilon$ one finds the Lorentz invariant products:
 \begin{align}
@@
 To make the index structure of the Pauli matrices explicit one writes $\sigma^\mu_{\alpha\dot{\alpha}}$ and $\sigma^{\mu\dot{\alpha}\alpha}$ for the formulae in \ref{eq:Pauli}.
-For the definition of the super algebra in ???
-the generators of the Lorentz group on the left and right handed Weyl spinor space are introduced:
+For the definition of the super algebra in section \ref{sec:SUSYalgebra} the representation of the generators of the Lorentz group on the left and right handed Weyl spinor space are introduced:
 \begin{align}

### 2016-06-08 Standardmodel.tex
mainly SM chapter revised

@@
 \begin{align}
-\mathcal{L}_{\mathrm{matter}} =  \sum_{i=1}^3 \left( \overline{\ell}_{iL} i \slashed{D} l_{iL} + \overline{e}_{iR} i \slashed{D} e_{iR} + \overline{q}_{iL} i \slashed{D} q_{iL} + \overline{u}_{iR} i \slashed{D} u_{iR} \right)
+\mathcal{L}_{\mathrm{matter}} =  \sum_{i=1}^3 \left( \overline{\ell}_{iL} i \slashed{D} l_{iL} + \overline{e}_{iR} i \slashed{D} e_{iR} + \overline{q}_{iL} i \slashed{D} q_{iL} + \overline{u}_{iR} i \slashed{D} u_{iR} + \overline{d}_{iR} i \slashed{D} d_{iR} \right)
 \end{align}
@@
 \begin{align}
-\mathcal{L}_{gauge} = -\frac{1}{4}F^{\mu\nu}F_{\mu\nu} - \frac{1}{4}W^{a\mu\nu}W^a_{\mu\nu} - \frac{1}{4}G^{a\mu\nu}G^a_{\mu\nu}.
+\mathcal{L}_{\mathrm{gauge}} = -\frac{1}{4}F^{\mu\nu}F_{\mu\nu} - \frac{1}{4}W^{a\mu\nu}W^a_{\mu\nu} - \frac{1}{4}G^{a\mu\nu}G^a_{\mu\nu}.
 \end{align}
@@
 So far no mass terms like in the Dirac Lagrangian \ref{eq:DiracLagrangian} have been introduced.
-The reason for that is that they are not gauge invariant.
+The reason for this is that they are not gauge invariant for left- and right-handed spinors transform differently.
 The same argument forbids terms like $-\frac{m^2}{2}A^\mu A_\mu$ for a generic gauge boson.
-EWSB gives masses to these particles while maintaining gauge invariance.
+Electroweak symmetry breaking (EWSB) ascribes masses to those particles \cite{Higgs:1964ia}, \cite{Higgs:1964pj}, \cite{Higgs:1966ev}, \cite{Englert:1964et}, \cite{Guralnik:1964eu}, \cite{Kibble:1967sv}, \cite{Bernstein:1974rd}.
 To this end one considers a complex scalar doublet
@@
 \end{align}
-which acquires a vacuum expectation value (VEV) $\langle \Phi \rangle = \frac{1}{\sqrt{2}}\begin{pmatrix}
+which receives a vacuum expectation value (VEV) $\langle \Phi \rangle = \frac{1}{\sqrt{2}}\begin{pmatrix}
 0 \\ v
@@
 where $\mu^2,\lambda > 0$.
-The Higgs sector of the SM reads
+The Higgs sector of the Standard Model reads
 \begin{align}
@@
 The Higgs doublet couples to the gauge fields of $SU_L(2)$ and $U_Y(1)$ in the fundamental representation.
-Inserting an expansion\footnote{The complex $\phi^+(x)$ and the real $\sigma(x)$ are so called massless Goldstone bosons.
-These degrees of freedom can be absorbed in the longitudinal polarized degrees of freedom of the arising gauge bosons $W^\pm$ and $Z^0$.
+Inserting an expansion\footnote{The complex $\phi^+(x)$ and the real $\sigma(x)$ are the fields of the so called massless Goldstone bosons.
+These degrees of freedom can be absorbed in the longitudinally polarized degrees of freedom of the arising gauge bosons $W^\pm$ and $Z^0$.
+This is referred to as unitary gauge\cite{book:811554}.
 The real $H(x)$ is the Higgs field, whose excitation is the Higgs boson.} around the VEV $\Phi = \begin{pmatrix}
@@
 \frac{1}{\sqrt{2}} (v + H(x) + i\sigma(x))
-\end{pmatrix}$ one obtains quadratic terms, i.e. mass terms, in the gauge fields in question. In order to get mass eigenstates for the gauge bosons one performs the transformation
+\end{pmatrix}$ one obtains quadratic terms, i.e.
+mass terms, for the gauge fields in question.
+In order to obtain mass eigenstates out of $B_\mu$ and $W_\mu^3$ and charge eigenstates for $Q$ and $I_3$ out of $W_\mu^1$ and $W_\mu^2$ one performs the transformation
 \begin{align}
@@
 \end{pmatrix}
-&& W^{\pm}_\mu = \frac{1}{\sqrt{2}}(W^1_\mu \mp W^2_\mu),
+&& W^{\pm}_\mu = \frac{1}{\sqrt{2}}(W^1_\mu \mp i W^2_\mu),
 \end{align}
-where the electroweak mixing angle is given by $\cos\theta_w = \frac{g_w}{\sqrt{g_w^2 + g_Y^2}}$
+where the electroweak mixing angle is given by $\cos\theta_w = \frac{g_w}{\sqrt{g_w^2 + g_Y^2}}$.
 These gauge fields acquire masses:
 \begin{align}
-& m_W = \frac{g_w}{2} v \hspace{4cm} m_Z = \frac{\sqrt{g_w^2+g_Y^2}}{2} v \hspace{4cm} m_A = 0.
+& m_W = \frac{g_w}{2} v \hspace{3cm} m_Z = \frac{\sqrt{g_w^2+g_Y^2}}{2} v \hspace{3cm} m_A = 0.
 \end{align}
-Apart from the massive  $W^\pm_\mu$ and $Z^0_\mu(x)$ bosons one obtains the massless photon $A_\mu$.
+Apart from the massive bosons $W^\pm_\mu$ and $Z^0_\mu$ one obtains the massless photon $A_\mu$.
 As the photon is massless it is still associated with a gauge symmetry called $U_{em}(1)$.
-One therefore often writes EWSB as the braeking of the gauge group $SU_L(2) \times U_Y(1)$ to $U_Y(1)$.\\
-Matter particles acquire mass via Yukawa coulings to the Higgs doublet. For up-type-quarks one uses that the charge conjugate of $\Phi$: $\Phi^C = i \sigma^2 \Phi^\ast$ transform as $\Phi$.
+One therefore often writes EWSB as the breaking of the gauge group $SU_L(2) \times U_Y(1)$ to $U_{em}(1)$.\\
+Matter particles acquire mass via Yukawa coulings to the Higgs doublet. For up-type-quarks one uses that the charge conjugate of $\Phi$: $\Phi^C = i \sigma^2 \Phi^\ast$ also transform as $\Phi$.
 \begin{align}
-\mathcal{L}_{Yukawa} = \sum_{i,j=1}^3 \left( y_{ij}^e \overline{\ell}_L \Phi e_R  + y_{ij}^d \overline{q}_L \Phi d_R + y_{ij}^u \overline{q}_L \Phi^C u_R\right) + h.c. 
+\mathcal{L}_{\mathrm{Yukawa}} = \sum_{i,j=1}^3 \left( y_{ij}^e \overline{\ell}_L \Phi e_R  + y_{ij}^d \overline{q}_L \Phi d_R + y_{ij}^u \overline{q}_L \Phi^C u_R\right) + h.c. 
 \end{align}
@@
 \end{align}
-The quark mass matrices are not diagonal (origin of CP - invariance).
-One therefore has to distinguish between interaction and mass eigenstates of the quark.
-The corresponding transformation matrix is the well known CKM-matrix [quote (original paper)].\\
+The quark mass matrices are not diagonal, which is the preconditionof the violation of CP-invariance.
+\footnote{The actual CP-violating term is the coupling term from quarks to the $W$-bosons.} One therefore has to distinguish between interaction and mass eigenstates of the quarks.
+The corresponding transformation matrix is the well known CKM-matrix \cite{Cabbibo:1964zsa}, \cite{Kobayashi:1973fv}.
+Throughout this thesis, the CKM-matrix is approximated with the unit matrix as it will have a minor influence upon the results\\
 The upshot of EWSB are masses for all matter particles except for the neutrinos and masses for the gauge bosons $W^\pm$ and $Z^0$.
@@
 The Quantization of Spin 0 and Spin $\frac{1}{2}$ fields yield no complication in the Lagrangian formalism.
-To quantize Spin 1 fields it turns out that the usual gauge invariance needs to be replaced by the so called BRST invariance.
-This results in 2 extra terms in the Lagrangian.
-Firstly there is the gauge fixing term
+To quantize Spin 1 fields it turns out that the usual gauge invariance needs to be replaced by the so called BRST invariance \cite{Becchi:1974xu},\cite{Becchi:1974md}, \cite{Becchi:1975nq}.
+This results in two extra contributions in the Lagrangian.
+Firstly there are the gauge fixing terms:
 \begin{align}
-\mathcal{L}_{R_\xi} = -\frac{1}{2\xi_A} (\partial^\mu A_\mu)^2  - \frac{1}{2\xi_W} |\partial^\mu W_\mu^+ - m_W \xi_W \phi^+|^2 - \frac{1}{2\xi_Z} (\partial^\mu Z_\mu - m_Z \xi_Z \sigma)^2 
+\mathcal{L}_{R_\xi} = -\frac{1}{2\xi_A} (\partial^\mu A_\mu)^2  - \frac{1}{\xi_W} |\partial^\mu W_\mu^+ - im_W \xi_W \phi^+|^2 - \frac{1}{2\xi_Z} (\partial^\mu Z_\mu - m_Z \xi_Z \sigma)^2 - \frac{1}{2\xi_G}(\partial^\mu G_\mu^a)^2.
 \end{align}
-Here $R_\xi$ is chosen, where the parameters $\xi_i$ specify the gauge.
-The last 2 terms are modified with the Goldstone bosons from section \ref{sec:EWSB} because of the massiveness of the $W^\pm$ an $Z^0$ bosons.\cite{book:811554}\\%page 622
+Here $R_\xi$-gauge is chosen, where the parameters $\xi_i$ specify the gauge further.
+The two terms in the middle are modified with the Goldstone bosons from section \ref{sec:EWSB}.
+This is to cancel terms of the form $V_\mu \partial^\mu \phi$ up to a total derivative arising from EWSB which would lead to non-diagonal propagators, where $V$ stands for a gauge boson $W^\pm$ or $Z^0$ and $\phi$ for a Goldstone boson.\\%\cite{book:811554}page 622
 Secondly there is a ghost Lagrangian
 \begin{align}
-\mathcal{L}_{ghost} = 
+\mathcal{L}_{\mathrm{ghost}} = -\overline{c}_a \partial^\mu \left( \partial_\mu c_a + g_s f_{abc} c_b G_{c \mu} \right) + \mathcal{L}_{\mathrm{weak\ ghosts}}.\label{eq:GhostLagrangian}
 \end{align}
-see [Denner Gauge Theories S622]
+The ghost Lagrangian corresponding to the electroweak sector is not needed within this thesis and due to its lengthy form not quoted here. It can found in \cite{book:811554}. %[S622]
+In eq.
+\ref{eq:GhostLagrangian} $c_a$ and $\overline{c}_a$ are the Faddeev-Popov ghost and antighosts.
+This fields do not correspond to physical particles because they violate the spin–statistics theorem, i.e.
+they anticommute while being spin 0 fields.
+Ghost fields are an elegant way of accounting for an additional term in the Lagrangian of non-abelian gauge fields which is best seen in the path integral quantization\cite{Peskin}.
 
-\subsection{Lagrangian of the SM}
-The complete Lagrangian of the SM reads
+\subsection{Lagrangian of the Standard Model}
+The complete Lagrangian of the Standard Model reads
 \begin{align}
-\mathcal{L}_{SM} = \mathcal{L}_{matter} + \mathcal{L}_{gauge} + \mathcal{L}_{Higgs} + \mathcal{L}_{Yukawa} + \mathcal{L}_{R_\xi} + \mathcal{L}_{ghost}
+\mathcal{L}_{\mathrm{SM}} = \mathcal{L}_{\mathrm{matter}} + \mathcal{L}_{\mathrm{gauge}} + \mathcal{L}_{\mathrm{Higgs}} + \mathcal{L}_{\mathrm{Yukawa}} + \mathcal{L}_{R_\xi} + \mathcal{L}_{\mathrm{ghost}}
 \end{align}
-with the corresponding parts of the previous chapters
+with the corresponding parts of the previous chapters. For further reading and the electroweak Lagrangian given completely in terms of physical fields, see \cite{book:811554}.

### 2016-06-08 figures/Contour_Plots/MRSSM_TreeLevel.py

@@ -26,7 +26,7 @@ def contourdata():
     # note reverse ordering for yi and xi because of the way   
     # shape works in numpy                                                  
     sigma = nans((len(mass),len(mass)))  
-    myfile = open('qq_to_sqsq_MRSSM_with_antiquarks.tex', 'r')     
+    myfile = open('MSSM_1_qqbar_sqsqdagger.txt', 'r')     
     i = 0
     for line in myfile:
         data = line.split()

### 2016-06-09 MSSM.tex
mainly SM chapter revised
little changes

@@
 \section{The Minimal Supersymmetric Standard Model}
+Even though the Standard Model is a very well working machinery which has partially been tested to an impressive accuracy it is not the ultimate theory of nature.
+To name some problems or at least flaws of the Standard Model there is no dark matter incorporated in it.
+This is that astrophysical observations \cite{Adam:2015rua} indicate that only 4.9\% of the universe's mass energy consist of ordinary matter while the majority is represented by 26.8\% of dark matter and 68.3\% of dark energy.
+Another puzzle is the hierarchy problem which questions the large discrepancy between the Higgs boson mass and its quantum correction, see \cite{Martin:1997ns}.
+Finally the gauge groups of the Standard Model cannot be unified to a theoretically appealing single gauge group at some high energy scale for the three gauge couplings do not meet at any renormalization scale \cite{Martin:1997ns}.
+There are other problems like the absence of gravity in the Standard Model but they are not mentioned here\\
+Supersymmetric extensions of the Standard Model constitute a mathematically very aesthetic solution of these problems.
+This section explains briefly the mechanism of supersymmetry and the minimal supersymmetric extension of the Standard Model (MSSM).
 
-\subsection{Supersymmetry as Extention of Poincaré Symmetry}
-The superalgebra is defined by
+\subsection{Supersymmetry as Extention of Poincaré Symmetry}\label{sec:SUSYalgebra}
+As already seen in the previous chapter symmetries are of vital importance when studying particle physics.
+Coleman and Mandula \cite{Coleman:1967ad} found that for any reasonable quantum field theory space-time symmetries and internal (gauge) symmetries cannot by combined in any but the trivial way.
+Ergo the symmetry groups of the Standard Model are the most general ones.\\
+This statement was corrected by the Haag Lopuszanski-Sohnius theorem \cite{Haag:1974qh} which weakened the condition of the quantum field theory by also allowing for anticommuting symmetry generators.
+This is by introducing the generators $Q_\alpha$ and $Q_{\dot{\alpha}}$ the Poincare-algebra can by nontrivially extended to the so called superalgebra :
 \begin{align}
 \left\{Q_\alpha,Q_\beta\right\} = \left\{\overline{Q}_{\dot{\alpha}},\overline{Q}_{\dot{\beta}}\right\} &= 0,  \nonumber\\
-\left\{Q_\alpha,\overline{Q}_{\dot{\alpha}}\right\} &= 2\sigma^\mu_{\alpha\dot{\alpha}}, \nonumber\\
+\left\{Q_\alpha,\overline{Q}_{\dot{\alpha}}\right\} &= 2\sigma^\mu_{\alpha\dot{\alpha}} P_\mu, \nonumber\\
 [P^\mu,Q_\alpha] = [P^\mu,\overline{Q}_{\dot{\alpha}}] &= 0, \nonumber \\
-[Q_\alpha, J^{\mu\nu}] &= \frac{1}{2} (\sigma^{\mu\nu})_\alpha^\beta Q_\beta
+[Q_\alpha, J^{\mu\nu}] &= \frac{1}{2} (\sigma^{\mu\nu})_\alpha^{\ \beta} Q_\beta.\label{eq:SUSYalgebra}
 \end{align}
+The superalgebra eq.
+\ref{eq:SUSYalgebra} is actually the smallest extension of the Poincare-algebra as it is possible to introduce further anticommuting symmetry generators.
+Their maximal number is fixed to $N = 8$.
+The MSSM deals only with one set of anticommuting symmetry generators and is therefore referred to be a $N = 1$ supersymmetric theory.
 A representation in the form of differential operators is given by

### 2016-06-09 Masterarbeit.tex
mainly Tree Level Plots
removed chapter InfraredSing.
little changes

@@
 Abstract \\ 
-English: motivation: aesthetic: Coleman-Mandula --> Haag-Lopuszanski-Sohnius-Theorem\\
+English: flaws of the SM\\
+motivation: aesthetic: Coleman-Mandula --> Haag-Lopuszanski-Sohnius-Theorem\\
 \vspace{20em}
@@
 \newpage
+\input{Virt_Real}
+\newpage
 \input{Renormalization}
-\newpage
-\input{InfraredSingularities}
 \newpage

### 2016-06-09 TreeLevel.tex
little changes

@@
 \subsubsection*{The process $q G \to \tilde{q} \tilde{g}$}
-This process is exactly the same in the MSSM and MRSSM.
+This process is exactly the same in the MSSM and MRSSM for the are two differences between the models which exactly cancel each other: Firstly in the MRSSM there is not only the production of a squark and a gluino but also the production of a squark and an antigluino.
+But on the other hand R-charge needs to be conserved which dictates that a "left-handed" squark can only be produced with an antigluino and a "right-handed" squark can only be produced with a gluino (see table \ref{tab:R_charges_MRSSM}).
 \\ 

### 2016-06-09 figures/Contour_Plots/MRSSM_TreeLevel.py

@@ -26,12 +26,14 @@ def contourdata():
     # note reverse ordering for yi and xi because of the way   
     # shape works in numpy                                                  
     sigma = nans((len(mass),len(mass)))  
-    myfile = open('MSSM_1_qqbar_sqsqdagger.txt', 'r')     
+    #myfile = open('MSSM_1_qqbar_sqsqdagger.txt', 'r')     
+    myfile = open('MSSM_MRSSM_2_GG_sqsqdagger.txt', 'r')
     i = 0
     for line in myfile:
         data = line.split()
         for j in range(0,N):
-            sigma[j][i] = data[j]
+            #sigma[j][i] = data[j]
+            sigma[j][i] = 9/(8**2)*data[j]
         i += 1   
     myfile.close()
     

### 2016-06-13 Appendix.tex
Latex does not compile any more

@@
 
-\subsection{Anticommuting numbers}
+\subsection{Anticommuting numbers}\label{sec:AnticommNumbers}
 Anticommuting numbers $\theta^\alpha$ are also referred to as Grassmann numbers and are defined by $\theta^\alpha\theta^\beta = -\theta^\beta\theta^\alpha$ and commute with ordinary numbers.\\
@@
 \begin{align}
-\int\mathrm{d}\theta_\alpha\ (a+b \theta^\beta + c\theta^\beta \theta^\gamma) := b\delta_{\alpha}^{\beta} + c (\delta_\alpha^\beta \theta^\gamma - \delta_\alpha^\gamma \theta^\beta) \hspace{1cm} \mathrm{and} \hspace{1cm}
-\int\mathrm{d}\theta_\alpha\ (a\overline{\theta}^{\dot{\beta}}) := (a\overline{\theta}^{\dot{\beta}}) \int\mathrm{d}\theta_\alpha\
+\int\mathrm{d}\theta_\alpha\ (a+b \theta^\beta + c\theta^\beta \theta^\gamma) &:= b\delta_{\alpha}^{\beta} + c (\delta_\alpha^\beta \theta^\gamma - \delta_\alpha^\gamma \theta^\beta) \hspace{1cm} \mathrm{and} \nonumber\\
+\int\mathrm{d}\theta_\alpha\ (a\overline{\theta}^{\dot{\beta}}) &:= (a\overline{\theta}^{\dot{\beta}}) \int\mathrm{d}\theta_\alpha\
 \end{align}
@@
 \begin{align}
-\int \mathrm{d}\theta^2 = \int\frac{1}{4}\epsilon_{\alpha\beta} \mathrm{d}\theta^\alpha\mathrm{d}\theta^\beta, \hspace{1cm}
-\int \mathrm{d}\overline{\theta}^2 = \int\frac{1}{4}\epsilon_{\dot{\alpha}\dot{\beta}} \mathrm{d}\theta^{\dot{\alpha}}\mathrm{d}\theta^{\dot{\beta}}, \hspace{1cm} \mathrm{and} \hspace{1cm}
-\int \mathrm{d}^4\theta := \int \mathrm{d}\theta^2\mathrm{d}\overline{\theta}^2
+\int \mathrm{d}\theta^2 &:= \int\frac{1}{4}\epsilon_{\alpha\beta} \mathrm{d}\theta^\alpha\mathrm{d}\theta^\beta, \hspace{1cm}
+\int \mathrm{d}\overline{\theta}^2 := \int\frac{1}{4}\epsilon_{\dot{\alpha}\dot{\beta}} \mathrm{d}\theta^{\dot{\alpha}}\mathrm{d}\theta^{\dot{\beta}}, \hspace{1cm} \mathrm{and} \nonumber\\
+\int \mathrm{d}^4\theta &:= \int \mathrm{d}\theta^2\mathrm{d}\overline{\theta}^2.
+\end{align}
+For the definition of (anti-)chiral superfields and the field strength chiral superfields it proves useful to introduce supersymmetry (or chiral) covariant derivatives 
+\begin{align}
+&\mathcal{D}_\alpha := \frac{\partial}{\partial \theta^\alpha} - i(\sigma^\mu\overline{\theta})_\alpha\partial_\mu && \mathcal{D}^{\dot{\alpha}} := \frac{\partial}{\partial \overline{\theta}_{\dot{\alpha}}} - i(\overline{\sigma}^\mu\theta)^{\dot{\alpha}} \partial_\mu\nonumber\\
+&D^\alpha := \epsilon^{\alpha\beta} D_\beta = -\frac{\partial}{\partial \theta_\alpha} + i(\overline{\theta} \overline{\sigma}^\mu)^\alpha \partial_\mu && \mathcal{D}_{\dot{\alpha}} := \epsilon_{\dot{\alpha}\dot{\beta}} \mathcal{D}^{\dot{\beta}} = -\frac{\partial}{\partial \overline{\theta}^{\dot{\alpha}}} + i(\sigma^\mu\theta)^{\dot{\alpha}} \partial_\mu.
+\end{align}
+By construction they are supersymmetry invariant, i.e. they fulfill the following anticommutation relations with the supersymmetry generators from eq. \ref{eq:SUSYGen}:
+\begin{align}
+\left\{ Q_\alpha, \mathcal{D}_\beta \right\} = \left\{ \overline{Q}_{\dot{\alpha}}, \mathcal{D}_\beta \right\} = \left\{ Q_\alpha, \mathcal{\mathcal{D}}_{\dot{\beta}} \right\} = \left\{ \overline{Q}_{\dot{\alpha}}, \mathcal{\mathcal{D}}_{\dot{\beta}} \right\} = 0
 \end{align}

### 2016-06-13 MSSM.tex
Latex does not compile any more

@@
 Even though the Standard Model is a very well working machinery which has partially been tested to an impressive accuracy it is not the ultimate theory of nature.
-To name some problems or at least flaws of the Standard Model there is no dark matter incorporated in it.
+This is not only because of its incompleteness regarding gravity but also because of its missing incorporation of dark matter.
 This is that astrophysical observations \cite{Adam:2015rua} indicate that only 4.9\% of the universe's mass energy consist of ordinary matter while the majority is represented by 26.8\% of dark matter and 68.3\% of dark energy.
@@
 Finally the gauge groups of the Standard Model cannot be unified to a theoretically appealing single gauge group at some high energy scale for the three gauge couplings do not meet at any renormalization scale \cite{Martin:1997ns}.
-There are other problems like the absence of gravity in the Standard Model but they are not mentioned here\\
-Supersymmetric extensions of the Standard Model constitute a mathematically very aesthetic solution of these problems.
+There are other problems which are not mentioned here.\\
+Supersymmetry provides a possible extension of the Standard Model.
+It constitute a mathematically very aesthetic solution of these problems.
 This section explains briefly the mechanism of supersymmetry and the minimal supersymmetric extension of the Standard Model (MSSM).
 
-\subsection{Supersymmetry as Extention of Poincaré Symmetry}\label{sec:SUSYalgebra}
+\subsection{Supersymmetry as an Extention of the Poincaré Symmetry}\label{sec:SUSYalgebra}
 As already seen in the previous chapter symmetries are of vital importance when studying particle physics.
-Coleman and Mandula \cite{Coleman:1967ad} found that for any reasonable quantum field theory space-time symmetries and internal (gauge) symmetries cannot by combined in any but the trivial way.
+Coleman and Mandula \cite{Coleman:1967ad} found that for any reasonable quantum field theory spacetime symmetries and internal, i.e.
+gauge symmetries cannot by combined in any but the trivial way.
 Ergo the symmetry groups of the Standard Model are the most general ones.\\
-This statement was corrected by the Haag Lopuszanski-Sohnius theorem \cite{Haag:1974qh} which weakened the condition of the quantum field theory by also allowing for anticommuting symmetry generators.
-This is by introducing the generators $Q_\alpha$ and $Q_{\dot{\alpha}}$ the Poincare-algebra can by nontrivially extended to the so called superalgebra :
+This statement was corrected by the Haag Lopuszanski-Sohnius theorem \cite{Haag:1974qh} which weakened the condition of the quantum field theory by allowing also for anticommuting symmetry generators.
+This is by introducing the generators $Q_\alpha$ and $Q_{\dot{\alpha}}$ with $\alpha, \dot{\alpha} \in \left\{ 1,2 \right\}$ the Poincare-algebra eq.
+\ref{eq:PoincareAlgebra} can be nontrivially extended to the so called superalgebra (see Appendix \ref{sec:2spinor_notation} for the definition of the $\sigma$ matrices):
 \begin{align}
@@
 \end{align}
-The superalgebra eq.
+As $J^{\mu\nu}$ is the generalized angular momentum operator the last line in eq.
+\ref{eq:SUSYalgebra} implies that $Q_\alpha$ is a spin $\frac{1}{2}$ operator.
+Applying $Q_\alpha$ to a field will change the spin of it by $\frac{1}{2}$.
+This means supersymmetry generators convert fermions to bosons and vice versa.\\
+The superalgebra in eq.
 \ref{eq:SUSYalgebra} is actually the smallest extension of the Poincare-algebra as it is possible to introduce further anticommuting symmetry generators.
 Their maximal number is fixed to $N = 8$.
-The MSSM deals only with one set of anticommuting symmetry generators and is therefore referred to be a $N = 1$ supersymmetric theory.
-A representation in the form of differential operators is given by
+The MSSM deals only with one set of anticommuting symmetry generators and is therefore referred to be a $N = 1$ supersymmetric theory.\\
+A representation in the form of differential operators can be given by introducing superspace.
+Superspace is a manifold obtained by enlarging Minkowski space, whose coordinates are label with $x^\mu$, with four anticommuting numbers: $\theta^\alpha$ and $\overline{\theta}^{\dot{\alpha}}$, where $\alpha,\ \dot{\alpha} = 1,2$ (see Appendix \ref{sec:AnticommNumbers} for the definition of anticommuting numbers).
+A representation of the superalgebra reads
 \begin{align}
@@
 J^{\mu\nu} &= i(x^\mu\partial^\nu - x^\nu\partial^\mu)\nonumber\\
-Q_\alpha &= i(\partial_\alpha + i\sigma^\mu_{\alpha\dot{\alpha}}\overline{\theta}^{\dot{\alpha}}\partial_\mu\nonumber\\
-\overline{Q}_{\dot{\alpha}} &= i(-\overline{\partial}_{\dot{\alpha}} - i \theta^\alpha \sigma^\mu_{\alpha\dot{\alpha}}\partial_\mu).
+Q_\alpha &= i(\partial_\alpha + i\sigma^\mu_{\alpha\dot{\alpha}}
+\overline{\theta}^{\dot{\alpha}}\partial_\mu)\nonumber\\
+\overline{Q}_{\dot{\alpha}} &= i(-\overline{\partial}_{\dot{\alpha}} - i \theta^\alpha \sigma^\mu_{\alpha\dot{\alpha}}\partial_\mu).\label{eq:SUSYGen}
 \end{align}
-INTRODUCE AND MOTIVATE SUSY COVARIANT DERIVATIVES $\mathcal{D}_\alpha = \frac{\partial}{\partial \theta^\alpha} - i(\sigma^\mu\overline{\theta})_\alpha\partial_\mu$ is the chiral covariant derivative and $\overline{\mathcal{D}}\overline{\mathcal{D}} = \overline{\mathcal{D}}_{\dot{\alpha}}\overline{\mathcal{D}}^{\dot{\alpha}}$
 
 \subsection{A Generic Supersymmetric Model in Superspace Formulation}
-This chapter outlines the generic ingredients and terms of a supersymmetric model. To this end it is practical to work in the language of superspace and superfields.\\
-Superspace is a manifold obtained by enlarging Minkowski space, whose coordinates are label with $x^\mu$, with four anticommuting numbers: $\theta^\alpha$ and $\overline{\theta}^{\dot{\alpha}}$, where $\alpha,\ \dot{\alpha} = 1,2$.
-Superfields are functions on superspace.\\
+This chapter outlines the generic ingredients and terms of a supersymmetric model.
+To this end it is practical to work in the language of superspace and superfields.
+Superspace has just been introduced and superfields are functions on superspace.\\
 The for the MSSM relevant superfields\footnote{Superfield are throughout this thesis labeled with a hat.} are the chiral superfield $\hat{\Phi}$, the antichiral superfield $\hat{\overline{\Phi}}$ and the vector superfield $V$.
-Chiral superfields are defined by the restriction $\overline{\mathcal{D}}_{\dot{\alpha}}\hat{\Phi} = 0$, antichiral superfields by $\mathcal{D}_\alpha\hat{\overline{\Phi}} = 0$ and vector superfields by the condition of being real $V^\dagger = V$.\\
+Chiral superfields are defined by the restriction $\overline{\mathcal{D}}_{\dot{\alpha}}\hat{\Phi} = 0$, antichiral superfields by $\mathcal{D}_\alpha\hat{\overline{\Phi}} = 0$ (see Appendix \ref{sec:AnticommNumbers} for the definition of chiral covariant derivatives) and vector superfields by the condition of being real $V^\dagger = V$.\\
 Their component decomposition reads\footnote{For tho vector superfield Wess-Zumino-gauge is applied.}

### 2016-06-13 TreeLevel.tex
Latex does not compile any more

@@
 \end{figure}
-The following contour plots underline the already announced difference between squark production in the MRSSM and the MSSM.
+The contour plots \ref{fig:ContourTree} underline the already announced difference between squark production in the MRSSM and the MSSM.
 The main difference is a suppression of the cross section for higher gluino masses in the MRSSM.
@@
 \includegraphics[scale=.6]{figures/contour_MSSM_squarks}
-\caption{}
+\caption{Contour plot for squark production cross section including all possible flavors (also charged ) in the MRSSM (top) and MSSM (bottom) }\label{fig:ContourTree}
 \end{center}
 \end{figure}
-
+Fig.\ref{fig:TreeXsection_fixed_m} shows the Born cross section of squark production including all possible flavors for a fixed mass of the gluino $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and the squark $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).
+The figure includes errors of the calculation which come from the parton density functions and the renormalization and factorization scale.\\
+The 68\% uncertainty from the central value pdf-set is obtained by performing the calculation with all eigenvector sets of the central value and taking the minimum and maximum at each point as deviations from the calculation with the central set.\\
+The error from the renormalization scale $\mu_R$ and the factorization scale $\mu_F$ is obtained by varying both parameters with a factor of $\frac{1}{2}$ and two.
+For each parameter combination the cross section has been calculated.
+Out of these nine numbers for each point the minimum and maximum has been chosen to estimate the error originating from the scale.\\
+The total error is then obtained by Gauß's propagation of uncertainties:
+\begin{align}
+\Delta \sigma = \sqrt{(\Delta \sigma_{\mathrm{pdf}})^2 + (\Delta \sigma_{\mathrm{scale}})^2}.
+\end{align}
+The uncertainty coming from the scale variation has been found much greater than the one from the parton density functions.
+The error from the phase space integration is negligible, i.e.
+$\Delta \sigma_{\mathrm{int}} < 1\text{\textperthousand}$.
+\begin{table}
+\begin{center}
+\begin{tabular}{c|c|c|c}\label{tab:MSSMfieldcontent}
+$m_{\tilde{g}}$ \textbackslash $m_{\tilde{q}}$ & 500 & 1000 & 1500\\
+\hline
+1000 &  &  & \\
+1500 &  &  & \\
+2000 &  &  & \\
+\end{tabular}
+\caption{Table}
+\end{center}
+\end{table}
 \begin{figure}[!htpb]
@@
 \includegraphics[scale=.5]{figures/MSSM+MRSSM_msq=1000}
-\caption{add error bars}\ref{fig:TreeXsection_fixed_m}
+\caption{add error bars}\label{fig:TreeXsection_fixed_m}
 \end{center}
-\end{figure}
+\end{figure}\\
 As a summary of the comparison between MSSM and MRSSM gluino production one can say, that the gluino production is enhanced in the MRSSM due to distinguishable gluino and antigluino.
@@
 Focusing on $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} \geq 2$ the most significant change between the considered models is the growing suppression of squark production for a increasing gluino mass.
-This is why this channel is going to be investigated at next-to-leading order in the ensuing sections.
+This is why this channel is going to be investigated at next-to-leading order within this thesis.
+The ensuing sections provide the prerequisites for this calculation.

### 2016-06-13 figures/Contour_Plots/MRSSM_TreeLevel_qq_sqsq.py

@@ -1,0 +1,72 @@
+# -*- coding: utf-8 -*-
+"""
+plot of cross section as contour with squark and gluino mass as axis
+"""
+
+from matplotlib import pyplot as plt
+import numpy as np
+from matplotlib.colors import LogNorm
+
+                          
+def nans(shape, dtype=float):
+    """grid of shape full nan"""
+    a = np.empty(shape, dtype)
+    a.fill(np.nan)
+    return a
+
+# grid size
+N = 50 
+
+def contourdata():
+    """
+    
+    """
+    mass = np.linspace(100, 2000, num=N)
+    mass = np.linspace(100, 2000, num=N)
+    # note reverse ordering for yi and xi because of the way   
+    # shape works in numpy                                                  
+    sigma = nans((len(mass),len(mass)))  
+    myfile = open('MRSSM_3_qq_sqsq.txt', 'r')     
+    i = 0
+    for line in myfile:
+        data = line.split()
+        for j in range(0,N):
+            sigma[j][i] = data[j]
+        i += 1   
+    myfile.close()
+    
+    fig = plt.figure(1,figsize=(9, 8)) 
+    ax1 = plt.axes()
+    font_size = 18
+    plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
+    plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
+    plt.xticks(fontsize = font_size)
+    plt.yticks(fontsize = font_size)
+    cf=ax1.contourf(mass, mass, sigma, norm = LogNorm())
+    levels1 = [0.1, 1, 10**3, 10**4, 10**5, 10**6]
+    cl1 = plt.contour(cf, levels=levels1,
+                  colors='k',
+                  linewidths=(1,),
+                  hold='on')    
+    levels2 = [10,100]
+    cl2 = plt.contour(cf, levels=levels2,
+                  colors='k',
+                  linewidths=(2,),
+                  hold='on')
+    levels3 = [20,50]
+    cl3 = plt.contour(cf, levels=levels3,
+                  colors='k',
+                  linestyles='dashed',
+                  linewidths=(1,),
+                  hold='on')
+    plt.clabel(cl2, fmt='%2.1f', colors='k', fontsize = font_size)
+    plt.clabel(cl3, fmt='%2.1f', colors='k', fontsize = font_size)
[…]

### 2016-06-13 figures/Contour_Plots/MSSM_TreeLevel.py

@@ -1,0 +1,75 @@
+# -*- coding: utf-8 -*-
+"""
+plot of cross section as contour with squark and gluino mass as axis
+"""
+
+from matplotlib import pyplot as plt
+import numpy as np
+from matplotlib.colors import LogNorm
+
+                          
+def nans(shape, dtype=float):
+    """grid of shape full nan"""
+    a = np.empty(shape, dtype)
+    a.fill(np.nan)
+    return a
+
+# grid size
+N = 50 
+
+def contourdata():
+    """
+    
+    """
+    mass = np.linspace(100, 2000, num=N)
+    mass = np.linspace(100, 2000, num=N)
+    # note reverse ordering for yi and xi because of the way   
+    # shape works in numpy                                                  
+    sigma = nans((len(mass),len(mass)))  
+    #myfile = open('MSSM_1_qqbar_sqsqdagger.txt', 'r') 
+    myfile = open('MSSM_MRSSM_2_GG_sqsqdagger.txt', 'r')
+    #myfile = open('MSSM_3_qq_sqsq.txt', 'r')
+    i = 0
+    for line in myfile:
+        data = line.split()
+        for j in range(0,N):
+            sigma[j][i] = data[j]
+        i += 1   
+    myfile.close()
+    
+    fig = plt.figure(1,figsize=(9, 8)) 
+    ax1 = plt.axes()
+    font_size = 18
+    plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
+    plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
+    plt.xticks(fontsize = font_size)
+    plt.yticks(fontsize = font_size)
+    cf=ax1.contourf(mass, mass, sigma, norm = LogNorm())
+    #cf=ax1.contourf(mass, mass, 9/(8**2)*sigma, norm = LogNorm())   # for process 2
+    levels1 = [0.1, 1, 10**3, 10**4, 10**5, 10**6]
+    cl1 = plt.contour(cf, levels=levels1,
+                  colors='k',
+                  linewidths=(1,),
+                  hold='on')    
+    levels2 = [10,100]
+    cl2 = plt.contour(cf, levels=levels2,
+                  colors='k',
+                  linewidths=(2,),
+                  hold='on')
+    levels3 = [20,50]
+    cl3 = plt.contour(cf, levels=levels3,
[…]

### 2016-06-13 figures/Contour_Plots/MSSM_TreeLevel_qq_sqsq.py

@@ -1,0 +1,72 @@
+# -*- coding: utf-8 -*-
+"""
+plot of cross section as contour with squark and gluino mass as axis
+"""
+
+from matplotlib import pyplot as plt
+import numpy as np
+from matplotlib.colors import LogNorm
+
+                          
+def nans(shape, dtype=float):
+    """grid of shape full nan"""
+    a = np.empty(shape, dtype)
+    a.fill(np.nan)
+    return a
+
+# grid size
+N = 50 
+
+def contourdata():
+    """
+    
+    """
+    mass = np.linspace(100, 2000, num=N)
+    mass = np.linspace(100, 2000, num=N)
+    # note reverse ordering for yi and xi because of the way   
+    # shape works in numpy                                                  
+    sigma = nans((len(mass),len(mass)))  
+    myfile = open('MSSM_1_qqbar_sqsqdagger.txt', 'r') 
+    i = 0
+    for line in myfile:
+        data = line.split()
+        for j in range(0,N):
+            sigma[j][i] = data[j]
+        i += 1   
+    myfile.close()
+    
+    fig = plt.figure(1,figsize=(9, 8)) 
+    ax1 = plt.axes()
+    font_size = 18
+    plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
+    plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
+    plt.xticks(fontsize = font_size)
+    plt.yticks(fontsize = font_size)
+    cf=ax1.contourf(mass, mass, sigma, norm = LogNorm())
+    levels1 = [0.1, 1, 10**3, 10**4, 10**5, 10**6]
+    cl1 = plt.contour(cf, levels=levels1,
+                  colors='k',
+                  linewidths=(1,),
+                  hold='on')    
+    levels2 = [10,100]
+    cl2 = plt.contour(cf, levels=levels2,
+                  colors='k',
+                  linewidths=(2,),
+                  hold='on')
+    levels3 = [20,50]
+    cl3 = plt.contour(cf, levels=levels3,
+                  colors='k',
+                  linestyles='dashed',
+                  linewidths=(1,),
+                  hold='on')
+    plt.clabel(cl2, fmt='%2.1f', colors='k', fontsize = font_size)
[…]

### 2016-06-13 figures/One_Loop/MRSSM_uu_susu_Kfactors_msg=2000GeV.py

@@ -1,0 +1,94 @@
+# -*- coding: utf-8 -*-
+"""
+C++ code on laptop in WARB-talk
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_squark = np.array([], dtype=float);
+# arrays for XSection
+sigma_LO_Tree = np.array([], dtype=float);
+sigma_NLO_Tree = np.array([], dtype=float);
+sigma_NLO_Virt_withoutPrefactors = np.array([], dtype=float);
+sigma_NLO_Virt = np.array([], dtype=float);
+sigma_NLO_Real_withoutPrefactors = np.array([], dtype=float);
+sigma_NLO_Real = np.array([], dtype=float);
+sigma_NLO_1L   = np.array([], dtype=float);
+
+
+f_Tree = open('MRSSM_Tree_uu_susu_msg=2000GeV.txt', 'r')
+
+for lines in f_Tree.readlines():
+    m_squark = np.append(m_squark, float(lines.split()[0]))
+    sigma_LO_Tree = np.append(sigma_LO_Tree, float(lines.split()[1]))
+
+f_Tree.close()
+
+
+f_1L = open('MRSSM_1L_uu_susu_msg=2000GeV.txt', 'r')
+discard = f_1L.readline()
+for lines in f_1L.readlines():
+    discard = np.append(m_squark, float(lines.split()[0]))
+    sigma_NLO_Tree = np.append(sigma_NLO_Tree, float(lines.split()[1]))
+    sigma_NLO_Virt_withoutPrefactors = np.append(sigma_NLO_Virt_withoutPrefactors, float(lines.split()[2]))
+    sigma_NLO_Real_withoutPrefactors = np.append(sigma_NLO_Real_withoutPrefactors, float(lines.split()[3]))
+    sigma_NLO_1L = np.append(sigma_NLO_1L, float(lines.split()[4]))    
+f_1L.close()
+
+f_Virt = open('MRSSM_Virt_uu_susu_msg=2000GeV.txt', 'r')
+discard = f_Virt.readline()
+for lines in f_Virt.readlines():
+    discard = np.append(m_squark, float(lines.split()[0]))
[…]

### 2016-06-16 Appendix.tex
up to RSymmetry

@@
 \end{align}
-To make the index structure of the Pauli matrices explicit one writes $\sigma^\mu_{\alpha\dot{\alpha}}$ and $\sigma^{\mu\dot{\alpha}\alpha}$ for the formulae in \ref{eq:Pauli}.
-For the definition of the super algebra in section \ref{sec:SUSYalgebra} the representation of the generators of the Lorentz group on the left and right handed Weyl spinor space are introduced:
+To make the index structure of the Pauli matrices explicit one writes $\sigma^\mu_{\alpha\dot{\alpha}}$ and $\overline{\sigma}^{\mu\dot{\alpha}\alpha}$ for the formulae in \ref{eq:Pauli}.
+For the definition of the supersymmetry algebra in section \ref{sec:SUSYalgebra} the representation of the generators of the Lorentz group on the left and right handed Weyl spinor space are introduced:
 \begin{align}
@@
 &\mathcal{D}_\alpha := \frac{\partial}{\partial \theta^\alpha} - i(\sigma^\mu\overline{\theta})_\alpha\partial_\mu && \mathcal{D}^{\dot{\alpha}} := \frac{\partial}{\partial \overline{\theta}_{\dot{\alpha}}} - i(\overline{\sigma}^\mu\theta)^{\dot{\alpha}} \partial_\mu\nonumber\\
-&D^\alpha := \epsilon^{\alpha\beta} D_\beta = -\frac{\partial}{\partial \theta_\alpha} + i(\overline{\theta} \overline{\sigma}^\mu)^\alpha \partial_\mu && \mathcal{D}_{\dot{\alpha}} := \epsilon_{\dot{\alpha}\dot{\beta}} \mathcal{D}^{\dot{\beta}} = -\frac{\partial}{\partial \overline{\theta}^{\dot{\alpha}}} + i(\sigma^\mu\theta)^{\dot{\alpha}} \partial_\mu.
+&D^\alpha := \epsilon^{\alpha\beta} D_\beta = -\frac{\partial}{\partial \theta_\alpha} + i(\overline{\theta} \overline{\sigma}^\mu)^\alpha \partial_\mu && \mathcal{D}_{\dot{\alpha}} := \epsilon_{\dot{\alpha}\dot{\beta}} \mathcal{D}^{\dot{\beta}} = -\frac{\partial}{\partial \overline{\theta}^{\dot{\alpha}}} + i(\sigma^\mu\theta)_{\dot{\alpha}} \partial_\mu.
 \end{align}

### 2016-06-16 MSSM.tex
up to RSymmetry

@@
 Finally the gauge groups of the Standard Model cannot be unified to a theoretically appealing single gauge group at some high energy scale for the three gauge couplings do not meet at any renormalization scale \cite{Martin:1997ns}.
-There are other problems which are not mentioned here.\\
+There are many other problems which are not mentioned here.\\
 Supersymmetry provides a possible extension of the Standard Model.
-It constitute a mathematically very aesthetic solution of these problems.
+It constitutes a mathematically very aesthetic solution of the above mentioned problems\footnote{In its minimal extension to the Standard Model supersymmetry does not incorporate gravity but many quantum gravity models are supersymmetric}.
 This section explains briefly the mechanism of supersymmetry and the minimal supersymmetric extension of the Standard Model (MSSM).
@@
 As already seen in the previous chapter symmetries are of vital importance when studying particle physics.
-Coleman and Mandula \cite{Coleman:1967ad} found that for any reasonable quantum field theory spacetime symmetries and internal, i.e.
-gauge symmetries cannot by combined in any but the trivial way.
+Coleman and Mandula \cite{Coleman:1967ad} found that for any reasonable quantum field theory space-time and internal symmetries, i.e.
+gauge symmetries "cannot by combined in any but the trivial way"\cite{Pelc:1996vg}.
 Ergo the symmetry groups of the Standard Model are the most general ones.\\
-This statement was corrected by the Haag Lopuszanski-Sohnius theorem \cite{Haag:1974qh} which weakened the condition of the quantum field theory by allowing also for anticommuting symmetry generators.
+This statement was corrected by the Haag-Lopuszanski-Sohnius theorem \cite{Haag:1974qh} which weakened the condition of the quantum field theory by allowing also for anticommuting symmetry generators.
 This is by introducing the generators $Q_\alpha$ and $Q_{\dot{\alpha}}$ with $\alpha, \dot{\alpha} \in \left\{ 1,2 \right\}$ the Poincare-algebra eq.
-\ref{eq:PoincareAlgebra} can be nontrivially extended to the so called superalgebra (see Appendix \ref{sec:2spinor_notation} for the definition of the $\sigma$ matrices):
+\ref{eq:PoincareAlgebra} can be nontrivially extended to the so called superalgebra (see Appendix \ref{sec:2spinor_notation} for the definition of the $\sigma$-matrices):
 \begin{align}
@@
 Their maximal number is fixed to $N = 8$.
-The MSSM deals only with one set of anticommuting symmetry generators and is therefore referred to be a $N = 1$ supersymmetric theory.\\
+The MSSM deals with only one set of anticommuting symmetry generators and is therefore referred to be a $N = 1$ supersymmetric theory.\\
 A representation in the form of differential operators can be given by introducing superspace.
-Superspace is a manifold obtained by enlarging Minkowski space, whose coordinates are label with $x^\mu$, with four anticommuting numbers: $\theta^\alpha$ and $\overline{\theta}^{\dot{\alpha}}$, where $\alpha,\ \dot{\alpha} = 1,2$ (see Appendix \ref{sec:AnticommNumbers} for the definition of anticommuting numbers).
+Superspace is a manifold obtained by enlarging Minkowski space, whose coordinates are label with $x^\mu$, with four anticommuting numbers: $\theta^\alpha$ and $\overline{\theta}^{\dot{\alpha}}$, where $\alpha,\ \dot{\alpha} \in \left\{ 1,2 \right\}$ (see Appendix \ref{sec:AnticommNumbers} for the definition of anticommuting numbers).
 A representation of the superalgebra reads
@@
 Superspace has just been introduced and superfields are functions on superspace.\\
-The for the MSSM relevant superfields\footnote{Superfield are throughout this thesis labeled with a hat.} are the chiral superfield $\hat{\Phi}$, the antichiral superfield $\hat{\overline{\Phi}}$ and the vector superfield $V$.
+The superfields\footnote{Superfield are throughout this thesis labeled with a hat.} relevant for the MSSM are the chiral superfield $\hat{\Phi}$, the antichiral superfield $\hat{\overline{\Phi}}$ and the vector superfield $V$.
 Chiral superfields are defined by the restriction $\overline{\mathcal{D}}_{\dot{\alpha}}\hat{\Phi} = 0$, antichiral superfields by $\mathcal{D}_\alpha\hat{\overline{\Phi}} = 0$ (see Appendix \ref{sec:AnticommNumbers} for the definition of chiral covariant derivatives) and vector superfields by the condition of being real $V^\dagger = V$.\\
-Their component decomposition reads\footnote{For tho vector superfield Wess-Zumino-gauge is applied.}
+All superfields can be decomposed into components. The component decomposition of the above fields read\footnote{For tho vector superfield Wess-Zumino-gauge is applied.}
 \begin{align}
@@
 \begin{align}
-\hat{\Phi} &\to \mathrm{e}^{-2ig\Lambda}\Phi\nonumber\\
-\hat{\overline{\Phi}} &\to \hat{\overline{\Phi}}\mathrm{e}^{2ig\overline{\hat{\Lambda}}}\nonumber\\
+\hat{\Phi} &\to \mathrm{e}^{-2ig\hat{\Lambda}}\hat{\Phi}\nonumber\\
+\hat{\overline{\Phi}} &\to \hat{\overline{\Phi}}\mathrm{e}^{2ig\hat{\overline{\Lambda}}}\nonumber\\
 \mathrm{e}^{2g\hat{V}} &\to \mathrm{e}^{-2ig\hat{\overline{\Lambda}}}\mathrm{e}^{2g\hat{V}} \mathrm{e}^{2ig\hat{\Lambda}},
@@
 where $\hat{\Lambda} = \hat{\Lambda}^aT^a$ and $\hat{V} = \hat{V}^aT^a$.
-$\hat{\Lambda}^a$ is an arbitrary chiral superfield and the $T^a$ are the generetors of the Lie algebra, which is associated to the gauge group in question.
+$\hat{\Lambda}^a$ is an arbitrary chiral superfield and the $T^a$ are the generetors of the gauge group in question.
 g is the gauge coupling constant of the gauge group.\\
 One can therefore construct the important gauge invariant term $\int\mathrm{d}^4\theta\ \hat{\overline{\Phi}}\mathrm{e}^{2g\hat{V}}\hat{\Phi}$.
-If one introduces the gauge covariant derivative $D_\mu = \partial + ig T^a v^a_\mu$ the component decomposition reads
+If one introduces the gauge covariant derivative $D_\mu = \partial + ig T^a v^a_\mu$ its component decomposition reads
 \begin{align}
@@
 \end{align}
-Therefore this term gives rise to the kinetic terms of the components of the chiral and antichiral superfields $A,\ A^\dagger,\ \psi$ and $\overline{\psi}$, their minimal coupling to the gauge fields $v_\mu^a$ and their superpartners $\lambda^a$ and $\overline{\lambda}^a$ and terms involving the auxiliary fields $F,\ F^\dagger$ and $D$.\\
-With the field-strength chiral superfields $\hat{W}_\alpha = -\frac{1}{4}\overline{\mathcal{D}}\overline{\mathcal{D}}(\mathrm{e}^{-2gV}\mathcal{D}_\alpha\mathrm{e}^{2gV})$ one can write down a gauge invariant term yielding the kinetic terms of the gauge fields and their superpartners:
+Therefore this term gives rise to the kinetic terms of the components of the chiral and antichiral superfields $A,\ A^\dagger,\ \psi$ and $\overline{\psi}$ as well as their minimal coupling to the gauge fields $v_\mu^a$ and their superpartners $\lambda^a$ and $\overline{\lambda}^a$ and terms involving the auxiliary fields $F,\ F^\dagger$ and $D$.\\
+With the field-strength chiral superfields $\hat{W}_\alpha := -\frac{1}{4}\overline{\mathcal{D}}\overline{\mathcal{D}}(\mathrm{e}^{-2gV}\mathcal{D}_\alpha\mathrm{e}^{2gV})$ one can write down a gauge invariant term yielding the kinetic terms of the gauge fields and their superpartners:
 \begin{align}
@@
 \begin{align}
-\mathcal{L}_{SUSY} &= \mathcal{L}_{matter} + \mathcal{L}_{gauge} + \mathcal{L}_{superpot}\nonumber\\
+\mathcal{L}_{\mathrm{SUSY}} &= \mathcal{L}_{\mathrm{matter}} + \mathcal{L}_{\mathrm{gauge}} + \mathcal{L}_{\mathrm{superpot}}\nonumber\\
 &=\int\mathrm{d}^4\theta\hat{\overline{\Phi}}\mathrm{e}^{2g\hat{V}}\hat{\Phi} + \left(\int\mathrm{d}^2\theta \frac{1}{16g^2 }\hat{W}^{\alpha a} \hat{W}^a_\alpha + h.c.
@@
 \end{align}
-Observing the component decomposition \ref{eq:L_matter},\ref{eq:L_gauge}, \ref{eq:L_superpot} of the 3 parts of this Lagrangian, one observes that the $F$ and $D$ fields have no kinetic term and are therefore auxiliary fields which can be eliminated by their equation of motion $\frac{\partial \mathcal{L}}{\partial\phi} = \partial_\mu\frac{\partial \mathcal{L}}{\partial(\partial_\mu \phi)}$ with $\phi = F, D$.
+Observing the component decomposition eq.\ref{eq:L_matter}, \ref{eq:L_gauge} and \ref{eq:L_superpot} of the 3 parts of this Lagrangian one observes that the $F$ and $D$ fields have no kinetic term and are therefore auxiliary fields which can be eliminated by their equation of motion $\frac{\partial \mathcal{L}}{\partial\phi} = \partial_\mu\frac{\partial \mathcal{L}}{\partial(\partial_\mu \phi)}$ with $\phi \in \left\{ F, D \right\}$.
 Doing this one obtains
@@
 \mathcal{L}_D &= \frac{1}{2} D^aD^a + g A^\dagger T^aD^a A \hspace{1cm} \Rightarrow \hspace{1cm} D^a = - A^\dagger T^a A \nonumber\\
-\mathcal{L}_D &= -\frac{1}{2}\left( A^\dagger T^a A \right)^2
+\mathcal{L}_D &= -\frac{1}{2}\left( A^\dagger T^a A \right)^2.
 \end{align}
@@
 
-\subsection{The Minimal Supersymmetric Standard Model in superspace formulation}
-The Lagrangian for the MSSM\footnote{This is the Lagrangian on the classical level, i.e. there are neither gauge fixing nor ghost terms.} reads
-\begin{align}
-\mathcal{L}_{MSSM} = \int \mathrm{d}^4 \theta & \left[ \hat{\overline{Q}}\mathrm{e}^{2g^\prime \hat{V}^\prime + 2g\hat{V} + 2g_s\hat{V}_s}\hat{Q} + \hat{\overline{U}}\mathrm{e}^{2g^\prime \hat{V}^\prime + 2g\hat{V} - 2g_s\hat{V}^T_s}\hat{U} + \hat{\overline{D}}\mathrm{e}^{2g^\prime \hat{V}^\prime + 2g\hat{V} - 2g_s\hat{V}^T_s}\hat{D} \right.\nonumber\\
- & + \hat{\overline{L}}\mathrm{e}^{2g^\prime \hat{V}^\prime + 2g\hat{V}}\hat{L} + \hat{\overline{E}}\mathrm{e}^{2g^\prime \hat{V}^\prime + 2g\hat{V}}\hat{E}\nonumber\\
- & + \left. \hat{\overline{H}}_d\mathrm{e}^{2g^\prime \hat{V}^\prime + 2g\hat{V}}\hat{H}_d + \hat{\overline{H}}_u\mathrm{e}^{2g^\prime \hat{V}^\prime + 2g\hat{V}}\hat{H}_u \right]\nonumber\\
- + \int \mathrm{d}^2\theta & \left[ \frac{1}{16g^{\prime 2}} \hat{W}^{\prime\alpha}\hat{W}^\prime_\alpha + \frac{1}{16g^{2}} \hat{W}^{a\alpha}\hat{W}^a_\alpha + \frac{1}{16g_s^2} \hat{W}_s^{a\alpha}\hat{W}^a_{s\alpha} \right] + h.c.\nonumber\\
- + \int \mathrm{d}^2\theta&\ W_{MSSM} + h.c.\nonumber\\
- +\  \mathcal{L}_{soft}.\ &\label{eq:L_MSSM}
-\end{align}
-Apart from the already discussed terms in the first 4 lines of \ref{eq:L_MSSM} there is a superpotential $W_{MSSM}$:
-\begin{align}
-W_{MSSM} &= y_d \hat{H}_d \hat{Q} \hat{D} + y_u \hat{H}_u \hat{Q} \hat U + y_e \hat{H}_d \hat{L} \hat{E} - \mu \hat{H}_d \hat{H}_u\label{eq:W_MSSM}
-\end{align}
-and terms which break supersymmetry softly, i.e. terms with coupling constants with positive mass dimension.
-\begin{align}
-\mathcal{L}_{soft} &= -M^2_{\tilde{Q}}|\tilde{q}_L|^2 - M^2_{\tilde{U}}|\tilde{u}_R|^2 - M^2_{\tilde{D}}|\tilde{d}_R|^2 \nonumber\\
-&\ \ \ - M^2_{\tilde{L}}|\tilde{l}_L|^2 - M^2_{\tilde{E}}|\tilde{e}_R|^2 - M^2_{H_d}|H_d|^2 - M^2_{H_u}|H_u|^2\nonumber\\
-&\ \ \ +\frac{1}{2}\left( M_1 \lambda\lambda + M_2 \lambda^a\lambda^a + M_3 \lambda_s^a\lambda_s^a\right) + h.c.\nonumber\\
-&\ \ \ -\left( A_d y_d H_d \tilde{q}_L \tilde{d}^\dagger_R + A_u y_u H_u \tilde{q}_L \tilde{u}^\dagger_R + A_e y_e H_d \tilde{l}_L \tilde{e}^\dagger_R -B\mu H_d H_u \right) + h.c.\label{eq:L_soft}
-\end{align}
-The field content of the MSSM is summarized in \ref{tab:MSSMfieldcontent}
+\subsection{The Minimal Supersymmetric Standard Model}
+After having introduced a generic supersymmetric model a possible realization of supersymmetry in nature - the Minimal Supersymmetric Standardmodel (MSSM) - is discussed in this subsection. 
+The field content of the MSSM is summarized in table \ref{tab:MSSMfieldcontent}.
+In comparison to the Standard Model each particle has a superpartner which differs in its spin by $\frac{1}{2}$ .
+The superpartners of fermions have Spin 0 and are referred to as sfermions.
+The name of each sfermion is given by the name of its Standard Model partner with an additional "s" in front of it, e.g.
+selectron or up-squark.
+The superpartners of bosons have spin $\frac{1}{2}$ and get an additional "ino" at the end of their name, e.g.
+Higgsino as the superpartner of the Higgs or Zino as superpartner of the $Z$-boson.\\
+Apart from this doubling up of the field content of the Standard Model there is one modification within the Higgs sector, i.e.
+there are two instead of one Higgs superfield.
+These are necessary to avoid an anomaly in the electroweak gauge symmetry and to give masses to both up- and down-type quarks \cite[page 8]{Martin:1997ns}.\\
+Note that the "chirality" of sfermions is understood to be the chirality of their superpartners. Of course scalar particles have no handedness.
 \begin{table}
 \begin{center}
-\begin{tabular}{c|c|c}\label{tab:MSSMfieldcontent}
+\begin{tabular}{c|c|c}
 Superfield & Components & $SU_\mathrm{C}(3)$ $\times$ $SU_\mathrm{L}(2)$ $\times$ $U_\mathrm{Y}(1)$\\
@@
 $\hat{H}_u$ & $H_u$, $\tilde{H}_u$ & (1, 2, $+\frac{1}{2}$)\\
-$\hat{V}^\prime$ & $\lambda^\prime$, $B_\mu$ & (1, 1, 0)\\
-$\hat{V}^a$ & $\lambda^a$, $W_\mu^a$ & (1, 3, 0)\\
+$\hat{V}_Y$ & $\lambda_Y$, $B_\mu$ & (1, 1, 0)\\
+$\hat{V}_w^a$ & $\lambda_w^a$, $W_\mu^a$ & (1, 3, 0)\\
 $\hat{V}_s^a$ & $\lambda_s^a$, $G_\mu^a$ & (8, 1, 0)\\
@@
 The first two lines show the decomposition of the generic superfields (cf.
-\ref{eq:superfielddecomp}).\newline
+subsection \ref{eq:superfielddecomp}).\newline
 The third column shows the representation (for $SU_\mathrm{C}(3)$ and $SU_\mathrm{L}(2)$) in which the fields transform and the charges of the fields for $U_\mathrm{Y}(1)$.}\label{tab:MSSMfieldcontent}
@@
 \end{table}
+The Lagrangian\footnote{This is the Lagrangian on the classical level, i.e. there are neither gauge fixing nor ghost terms.} for the MSSM reads
+\begin{align}
+\mathcal{L}_{\mathrm{MSSM}} = \int \mathrm{d}^4 \theta & \left[ \hat{\overline{Q}}\mathrm{e}^{2g_Y \hat{V}_Y + 2g_w\hat{V}_w + 2g_s\hat{V}_s}\hat{Q} + \hat{\overline{U}}\mathrm{e}^{2g_Y \hat{V}_Y + 2g_w\hat{V}_w - 2g_s\hat{V}^T_s}\hat{U} + \hat{\overline{D}}\mathrm{e}^{2g_Y \hat{V}_Y + 2g_w\hat{V}_w - 2g_s\hat{V}^T_s}\hat{D} \right.\nonumber\\
+ & + \hat{\overline{L}}\mathrm{e}^{2g_Y \hat{V}_Y + 2g_w\hat{V}_w}\hat{L} + \hat{\overline{E}}\mathrm{e}^{2g_Y \hat{V}_Y + 2g_w\hat{V}_w}\hat{E}\nonumber\\
+ & + \left. \hat{\overline{H}}_d\mathrm{e}^{2g_Y \hat{V}_Y + 2g_w\hat{V}_w}\hat{H}_d + \hat{\overline{H}}_u\mathrm{e}^{2g_Y \hat{V}_Y + 2g_w\hat{V}_w}\hat{H}_u \right]\nonumber\\
+ + \int \mathrm{d}^2\theta & \left[ \frac{1}{16g_Y^2} \hat{W}_Y^{\alpha}\hat{W}_{Y\alpha} + \frac{1}{16g_w^{2}} \hat{W}_w^{a\alpha}\hat{W}^a_{w\alpha} + \frac{1}{16g_s^2} \hat{W}_s^{a\alpha}\hat{W}^a_{s\alpha} \right] + h.c.\nonumber\\
+ + \int \mathrm{d}^2\theta&\ W_{\mathrm{MSSM}} + h.c.\nonumber\\
+ +\  \mathcal{L}_{\mathrm{soft}}.\ &\label{eq:L_MSSM}
+\end{align}
+Apart from the kinetic and minimal coupling terms in the first four lines of \ref{eq:L_MSSM} there is a superpotential $W_{\mathrm{MSSM}}$:
+\begin{align}
+W_\mathrm{{MSSM}} &= y_d \hat{H}_d \hat{Q} \hat{D} + y_u \hat{H}_u \hat{Q} \hat U + y_e \hat{H}_d \hat{L} \hat{E} - \mu \hat{H}_d \hat{H}_u\label{eq:W_MSSM}
+\end{align}
+After eliminating auxiliary fields a Higgs potential is generated.
+In contrast to the Standard Model the quadrilinear term in the Higgs potential is given in terms of the gauge couplings and therefore no independent parameter.
+From the Higgs potential both $H_u$ and $H_d$ acquire a vacuum expectation value:
+\begin{align}
+\left\langle H_u \right\rangle = \frac{1}{\sqrt{2}}\begin{pmatrix}
+0 \\ v_u
+\end{pmatrix} \hspace{3cm} 
+\left\langle H_d \right\rangle = \frac{1}{\sqrt{2}}\begin{pmatrix}
+v_d \\ 0
+\end{pmatrix}
+\end{align}
+whose quotient is an important parameter of the electroweak MSSM.
+\begin{align}
+\tan \beta := \frac{v_u}{v_d}
+\end{align}
+As in the Standard Model this spontaneous symmetry breaking leads to Yukawa-terms (first three terms of eq.
+\ref{eq:W_MSSM}) which give masses to the fermions\footnote{Note the sum convention of $SU_{\mathrm{L}}(2)$ doublets: $\hat{H}_u \hat{Q} =  (\hat{H}_u)_{\alpha}\hat{Q}_\beta \epsilon^{\alpha\beta}$ to ensure gauge invariance.}.
+Apart from that there are also other terms like quark-squark-higgsino interactions.
+In addition there is the $\mu$-term which is responsible for Higgsino and Higgs masses.\\
+In order to explain why supersymmetric particles have not been found so far supersymmetry has to be broken.
+Like in electroweak symmetry breaking supersymmetry is preserved at some high energy scale but its vacuum state is not supersymmetric.
+However there is no consensus on how supersymmetry is broken.
+But by ignoring the exact mechanism and parameterizing it by introducing appropriate terms in the Lagrangian one accounts for it in an absolutely viable way.\\
+Terms which break supersymmetry should be soft, i.e. they should have coupling constants with positive mass dimension.
+\begin{align}
+\mathcal{L}_{\mathrm{soft}} &= -M^2_{\tilde{Q}}|\tilde{q}_L|^2 - M^2_{\tilde{U}}|\tilde{u}_R|^2 - M^2_{\tilde{D}}|\tilde{d}_R|^2 \nonumber\\
+&\ \ \ - M^2_{\tilde{L}}|\tilde{l}_L|^2 - M^2_{\tilde{E}}|\tilde{e}_R|^2 - M^2_{H_d}|H_d|^2 - M^2_{H_u}|H_u|^2\nonumber\\
+&\ \ \ +\frac{1}{2}\left( M_1 \lambda_Y\lambda_Y + M_2 \lambda_w^a\lambda_w^a + M_3 \lambda_s^a\lambda_s^a\right) + h.c.\nonumber\\
+&\ \ \ -\left( A_d y_d H_d \tilde{q}_L \tilde{d}^\dagger_R + A_u y_u H_u \tilde{q}_L \tilde{u}^\dagger_R + A_e y_e H_d \tilde{l}_L \tilde{e}^\dagger_R -B\mu H_d H_u \right) + h.c.\label{eq:L_soft}
+\end{align}
+The softly breaking terms in the MSSM comprise masses of the squarks, sleptons, Higgs-bosons and gauginos.
+The last line in eq.
+\ref{eq:L_soft} resembles the superpotential in eq.
+\ref{eq:W_MSSM}.
+In fact the only two differences are that the superfields are replaced by their scalar components and that additional parameters with mass dimension one have been added.
+$A_d$, $A_u$, $A_e$ are $3 \times 3$ matrices in family space.\\
+Many supersymmetric particles have no definite mass but mix to particles with definite mass.
+This is true for neutral higgsinos and gauginos which mix to neutralinos and charged higgsinos and gauginos which mix to charginos.
+However, for this thesis only the mass matrix for electrically charged sfermions is given because this will change significantely when introducing R-symmetry in the next section.
+The Lagrangian describing these masses reads
+\begin{align}
+\mathcal{L}_{m_{\tilde{q}},m_{\tilde{e}}} = - \begin{pmatrix}
+\tilde{u}^\dagger_L & \tilde{u}^\dagger_R 
+\end{pmatrix} M^2_{\tilde{u}} \begin{pmatrix}
+\tilde{u}_L \\
+\tilde{u}_R 
+\end{pmatrix} - \begin{pmatrix}
+\tilde{d}^\dagger_L & \tilde{d}^\dagger_R 
+\end{pmatrix} M^2_{\tilde{d}} \begin{pmatrix}
+\tilde{d}_L \\
+\tilde{d}_R 
+\end{pmatrix} - \begin{pmatrix}
+\tilde{e}^\dagger_L & \tilde{e}^\dagger_R 
+\end{pmatrix} M^2_{\tilde{e}} \begin{pmatrix}
+\tilde{e}_L \\
+\tilde{e}_R 
+\end{pmatrix}.
+\end{align}
+where the mass matrix is given by 
+\begin{align}
+M^2_{\tilde{f}} = \begin{pmatrix}
+M^2_{\tilde{f}LL} & m_f X_f^\ast \\
+m_f X_f &  M^2_{\tilde{f}RR}
+\end{pmatrix}.
+\end{align}
+The diagonal terms are given by the sum of the fermion mass squared $m_f^2$, the appropriate soft breaking term, e.g.
+$M_{\tilde{Q}}^2$ for left handed squarks and a contribution from the elimination of $D$-fields.
+In fact this last term splits the masses of fermions and sfermions already without explicit supersymmetry breaking.
+This is because the generation of fermion masses requires the breaking of gauge symmetry which is not possible without breaking supersymmetry.
+However the off-diagonal terms are given by
+\begin{align}
+X_f = A_f + \mu^\ast\left\{ \cot \beta, \tan \beta \right\} \label{eq:off_diagonal}
+\end{align}
+with $\cot \beta$ for up-type squarks and $\tan \beta$ for down-type sfermions
+
+\subsection{R-Parity}
+The MSSM does not include any terms which violate baryon (B) or lepton number (L)\footnote{The chiral superfield $\hat{Q}$ carries baryon number $\frac{1}{3}$, whereas $\mathrm{B} = -\frac{1}{3}$ for $\hat{D}$, $\hat{U}$ and $\mathrm{B} = 0$ for all other superfields.
+The only multiplets carrying a non-zero lepton number are $\hat{L}$ with $\mathrm{L} = 1$ and $\hat{E}$ with $\mathrm{L} = -1$.} like
+\begin{align}
+W_{\Delta \mathrm{B}=1} = \lambda \hat{U}\hat{D}\hat{D} \hspace{2cm}\mathrm{or}\hspace{2cm} W_{\Delta \mathrm{L}=1} = \lambda^\prime \hat{L}\hat{Q}\hat{D}\label{eq:BLviolation}
+\end{align}
+in the superpotential although this would be possible from the perspective of gauge invariance and renormalizability.
+However, this has not been oberserved experimentally.
+The most famous constraint on them is the non-observation of proton decay which restricts at least one of the parameters $\lambda$ or $\lambda^\prime$ to be extremely small\cite{Martin:1997ns}.
+Forbidding these terms by postulating a conservation of B and L might not be the best solution since both B and L are known to be violated in nature by non-perturbative effects\cite{'tHooft:1976up}.\\
+A possible way out is the postulation of the conservation of R-parity
+\begin{align}
+P_\mathrm{R} = (-1)^{3(\mathrm{B}-\mathrm{L})+2s}
+\end{align}
+where $s$ is the spin of the particle on which the R-parity operator is applied to.
+R-parity is a multiplicative quantum number which is constructed to be +1 for each Standard Model particle and -1 for each supersymmetric partner.
+Apart from the the prohibition of the terms in eq.
+\ref{eq:BLviolation} this has important consequances:
+\begin{itemize}
+\item There has to be a lightest supersymmetric particle (LSP) which is absolutely stable. This could be a candidate for dark matter.
+\item At colliders like the LHC there must always be an even number of supersymmetric particles be produced, if at all.
+\end{itemize}
+The superpotential of the MSSM (see, eq. \ref{eq:W_MSSM}) is chosen in such a way that it is the only renormalizable and gauge invariant potential which respects R-parity.

### 2016-06-16 RSymmetry.tex
up to RSymmetry

--- 2016-02-25 RSymmetry.tex
@@
 \section{R-Symmetry}
+R-symmetry is an additional continuous symmetry which extends  supersymmetry in a non-trivial way.
+This is actually covered in the Haag-Lopuszanski-Sohnius theorem \cite{Haag:1974qh} but often concealed.\\
+This section introduces R-symmetry and discusses briefly a minimal viable extension of the MSSM including R-symmetry, the MRSSM.
+Thereby some general features of the model are mentioned before the focus is laid on the strongly interacting sector which is the central topic of the thesis.
+
 \subsection{R-Symmetry Transformation}
 R-symmetry is a global $U(1)$ symmetry.
-R-symmetry should not be confused with R-parity which is a discrete $Z_2$ symmetry.
+It must not be confused with R-parity which is a discrete $\mathbb{Z}_2$ symmetry.
 A continuous global symmetry implies according to Noether's theorem a conserved charge.
-In the case of R-symmetry this charge is called R-charge and one therefore refers to R-symmetry as $U_R(1)$.\\
+In the case of R-symmetry it is called R-charge and one therefore refers to R-symmetry as $U_R(1)$.\\
 The defining property of $U_R(1)$ is that the anticommuting coordinates $\theta^\alpha$ and $\overline{\theta}^{\dot{\alpha}}$ transform like
@@
 \end{align}
-where $\alpha$ parametrizes the transformation. This in turn implies that R-symmetry does not commute with supersymmetry, meaning that superpartners do not have the same R-charge.\\
-The transformation of chiral and vector superfields reads
+where $\alpha$ parametrizes the transformation. This in turn implies that the supersymmetry generators (see eq. \ref{{eq:SUSYGen}}) transform like
+\begin{align}
+& Q \to \mathrm{e}^{-i\alpha} Q && \overline{Q} \to \mathrm{e}^{i\alpha}\overline{Q}
+\end{align}
+and R-symmetry does not commute with supersymmetry 
+\begin{align}
+\left[ R,Q \right] = -Q && \left[ R,\overline{Q} \right] = \overline{Q},
+\end{align}
+meaning that superpartners do not have the same R-charge. The transformation of chiral and vector superfields reads
 \begin{align}
 & \hat{\Phi}(x,\theta,\overline{\theta}) \to \mathrm{e}^{ir_{\hat{\Phi}}\alpha}\ \hat{\Phi}(x,\mathrm{e}^{i\alpha}\theta,\mathrm{e}^{-i\alpha}\overline{\theta})\nonumber\\
-&\hat{V}(x,\theta,\overline{\theta}) \to  \hat{V}(x,\mathrm{e}^{i\alpha}\theta,\mathrm{e}^{-i\alpha}\overline{\theta}).
+&\hat{V}(x,\theta,\overline{\theta}) \to  \hat{V}(x,\mathrm{e}^{i\alpha}\theta,\mathrm{e}^{-i\alpha}\overline{\theta}),
 \end{align}
-If one inserts the component decomposition \ref{eq:superfielddecomp} of the superfields one can read off the R-charges of the component fields.
+i.e.
+the chiral superfields transform with arbitrary R-charge where the R-charge of vector superfield is restricted to be zero by the condition that they are real.
+If one inserts the component decomposition eq.
+\ref{eq:superfielddecomp} of the superfields one can read off the R-charges of the component fields.
 \begin{table}
@@
 
-\subsection{The Minimal R-symmetric Supersymmetric Standard Model}
-The MSSM with additional R-symmetry is called minimal R-symmetric supersymmetric standard model (MRSSM).
+\subsection{The Minimal R-Symmetric Supersymmetric Standard Model}
 If one imposes R-symmetry upon the MSSM one is faced with a certain arbitrariness, i.e.
 the choice of the R-charges of the chiral superfields.
-In this thesis the R-charges are chosen in that way, that every Standard model particle has R-charge zero.
+A minimal R-symmetric extension of the MSSM is the minimal R-symmetric supersymmetric Standard Model (MRSSM)\cite{Kribs:2007ac}.
+In this model the R-charges are chosen in such a way, that every Standard Model particle has R-charge zero.
 Following this one obtains the R-charges of all particles which are summed up in table \ref{tab:R_charges_MRSSM}.
-\begin{table}
+\begin{table}[H]
 \begin{center}
@@
 \hhline{=#=|=#=|=#=|=}
-Gauge Vector & $\hat{g}$, $\hat{W}$, $\hat{B}$ & 0 & $g$, $W$, $B$ & 0 & $\tilde{g}$, $\tilde{W}$, $\tilde{B}$ &+1\\
-Matter & $\hat{L}$, $\hat{E}$ & 0 & $\tilde{l}$, $\tilde{e}_R$ & +1 & $l$, $e_R$ & 0\\
- & $\hat{Q}$, $\hat{D}$, $\hat{U}$ & +1 & $\tilde{q}$, $\tilde{d}^\dagger_R$, $\tilde{u}^\dagger_R$ & +1 & $q$, $d_R$, $u_R$ & 0\\
+Gauge Vector & $\hat{V}_s^a$, $\hat{V}_w^a$, $\hat{V}_Y$ & 0 & $G^a_\mu$, $W^a_\mu$, $B_\mu$ & 0 & $\lambda_s^a$, $\lambda_w^a$, $\lambda_Y$ &+1\\
+Matter & $\hat{L}$, $\hat{E}$ & 0 & $\tilde{l}_l$, $\tilde{e}^\dagger_R$ & +1 & $l_L$, $e_R$ & 0\\
+ & $\hat{Q}$, $\hat{D}$, $\hat{U}$ & +1 & $\tilde{q}_L$, $\tilde{d}^\dagger_R$, $\tilde{u}^\dagger_R$ & +1 & $q_L$, $d_R$, $u_R$ & 0\\
 $H$-Higgs & $\hat{H}_{d,u}$ & 0 & $H_{d,u}$ & 0 & $\tilde{H}_{d,u}$ & -1\\
@@
 $R$-Higgs & $\hat{R}_{d,u}$ & +2 & $R_{d,u}$ & +2 & $\tilde{R}_{d,u}$ & +1\\
-Adjoint Chiral & $\hat{O}$, $\hat{T}$, $\hat{S}$ & 0 & $O$, $T$, $S$ & 0 & $\tilde{O}$, $\tilde{T}$, $\tilde{S}$ & -1
+Adjoint Chiral & $\hat{O}$, $\hat{T}$, $\hat{S}$ & 0 & $\sigma^a$, $\omega^a$, $\rho$ & 0 & $\tilde{\chi}_s^a$, $\tilde{\chi}_w^a$, $\tilde{\chi}_Y$ & -1
 \end{tabular}
-\caption{This table shows the R-charges of all particles in the MRSSM.}\label{tab:R_charges_MRSSM}
+\caption{This table lists the R-charges of all superfields and their components in the MRSSM.
+The fields of the $R$-Higgs and the adjoint chiral superfields are not present in the MSSM}\label{tab:R_charges_MRSSM}
 \end{center}
@@
 These occur for the following reason.\\
-Since in the MSSM the gauginos are Majorana particles their mass terms reads 
+In the MSSM the gauginos are Majorana particles. Their mass terms  reads in 2-spinor notation
 \begin{align}
-\mathcal{L}_{Majorana\ mass} = -m\lambda\lambda + h.c.
+\mathcal{L}_{\mathrm{Majorana\ mass}} = -m\lambda\lambda + h.c.
 \end{align}
-which is not R-invariant because the Weyl fermion $\lambda$ has R-charge +1. The only other way to account for a fermion mass is to write down a Dirac mass term.
+which is not R-invariant because the Weyl fermion $\lambda$ has R-charge +1.
+Giving no mass to the gauginos is phenomenologically not possible.
+The only way to account for a fermion mass is to write down a Dirac mass term.
 \begin{align}
-L_{Dirac\ mass} = -m \chi\lambda + h.c.
+\mathcal{L}_{\mathrm{Dirac\ mass}} = -m \chi\lambda + h.c.
+\end{align}
+This means that the 4-spinor of every gaugino is a Dirac- instead of a Majorana-spinor, e.g. for the gluino:
+\begin{align}
+& \tilde{g}_\mathrm{MSSM} = \begin{pmatrix}
+-i \lambda_s \\
++i \overline{\lambda_s}
+\end{pmatrix} && \tilde{g}_\mathrm{MRSSM} = \begin{pmatrix}
+-i \lambda_s \\
++i \overline{\chi_s}
+\end{pmatrix}.
 \end{align}
@@
 \begin{align}
-&\hat{O}^a(x, \theta, \overline{\theta}) = \sigma^a + \sqrt{2}\theta i\chi^a + \hdots && a = 1,\hdots,8.
+&\hat{O}^a(x, \theta, \overline{\theta}) = \sigma^a + \sqrt{2}\theta i\chi^a_s + \hdots && a = 1,\hdots,8.
 \end{align}
-The scalar components $\sigma^a$ are called scalar gluons and the Weyl spinors $\chi^a$ are called octinos.\\
+The scalar components $\sigma^a$ are referred to as scalar gluons and the Weyl spinors $\chi^a$ are called octinos.\\
 The same argument as for the adjoint chiral explains the existence of additional Higgs-superfields which are referred to as $R$-Higgs fields.\\
-But instead of including more fields in the model R-symmetry also forbids terms which are allowed by supersymmetry.
-For the above choice of R-charges the $\mu$-term in \ref{eq:W_MSSM} and the $A$-terms in the last line of \ref{eq:L_soft} are excluded.
-As a consequence terms which allow flavor violating processes like $\mu \to e \gamma$ are allowed in the MSSM but forbidden in the MRSSM [Kribs, Popitz, Weiner].
+Apart from these extensions R-symmetry also forbids terms which are allowed by supersymmetry.
+For the above choice of R-charges the $\mu$-term in \ref{eq:W_MSSM} and the $A$-terms in the last line of \ref{eq:L_soft} are absent in the MRSSM.
+Inspecting eq.
+\ref{eq:off_diagonal} implies that there is no squark mixing in the MRSSM.
+As a consequence terms which allow flavor violating processes like $\mu \to e \gamma$ are forbidden in the MRSSM\cite{Kribs:2007ac}.
+Quite interestingly Dirac gauginos can be heavier than Majorana gauginos without being less natural in view of the hierarchy problem\cite{Nelson:2002ca, Kribs:2012gx, Hardy:2013ywa}.
+Finally the production cross section of strongly interacting particles is suppressed\cite{Kribs:2012gx, Kribs:2013oda}.
+It is this last feature which is going to be observed further in this thesis.
+To this end the colored sector of the MRSSM in now considered in more detail.
 
-\subsection{The R-symmetric supersymmetric Quantumchromodynacis}
+\subsection{The R-Symmetric Supersymmetric Quantum Chromodynamcis}
 The subject of this thesis is the phenomenology of the strongly coupling sector of the MRSSM.
-The R-symmetric supersymmetric quantumchromodynamics (RSQCD) is therefore considered closer.
-Its Lagrangian reads
+The R-symmetric supersymmetric quantum chromodynamics (RSQCD) is therefore considered closer.
+Its Lagrangian for an arbitrary massless quark reads
 \begin{align}
-\mathcal{L}_{RSQCD} = &\int\mathrm{d}^4\theta\ \left( \hat{\overline{Q}}_L \mathrm{e}^{2g_s\hat{V}_s} \hat{Q}_L + \hat{\overline{Q}}_R \mathrm{e}^{-2g_s\hat{V}^T_s} \hat{Q}_R + \hat{\overline{O}} \mathrm{e}^{2g_s\hat{V}^{fund}_s} \hat{O}\right)\nonumber\\
-+& \left( \int \mathrm{d}^2\theta \frac{1}{16g_s^2} \hat{W}_s^{a\alpha}\hat{W}^a_{s\alpha} + h.c. \right) + \mathcal{L}_{soft}
+\mathcal{L}_{\mathrm{RSQCD}} = &\int\mathrm{d}^4\theta\ \left( \hat{\overline{Q}}_L \mathrm{e}^{2g_s\hat{V}_s} \hat{Q}_L + \hat{\overline{Q}}_R \mathrm{e}^{-2g_s\hat{V}^T_s} \hat{Q}_R + \hat{\overline{O}} \mathrm{e}^{2g_s\hat{V}^{\mathrm{fund}}_s} \hat{O}\right)\nonumber\\
++& \left( \int \mathrm{d}^2\theta \frac{1}{16g_s^2} \hat{W}_s^{a\alpha}\hat{W}^a_{s\alpha} + h.c. \right) + \mathcal{L}_{\mathrm{soft}}\label{eq:L_super_RSQCD}
 \end{align}
-where in terms of component fields the terms are given by
+where $\hat{Q}_L$ and $\hat{Q}_R$ refer to the left and right handed superfield of the quark.
+Note that each field in the first line of eq.
+\ref{eq:L_super_RSQCD} transforms in a different representation of $SU_C(3)$, i.e.
+the fundamental, the antifundamental and the adjoint one.
+In terms of components fields these expressions are given by
 \begin{align}
@@
 &+\sqrt{2}g_s \left( -i (\tilde{q}_R T^{\ast a} q_R ) \lambda^a + i \overline{\lambda}^a (\overline{q}_R T^{\ast a} \tilde{q}_R^\dagger) \right) - g_s \tilde{q}_R T^{\ast a} D^a \tilde{q}_R^\dagger\label{eq:RSQCD_Feynmanrules2}\\
-\int\mathrm{d}^4\theta\ \hat{\overline{O}} \mathrm{e}^{2g_s\hat{V}^{fund}_s} \hat{O} =\  & F_O^\dagger F_O + (D_\mu \sigma^a)^\dagger (D^\mu \sigma^a) + \overline{\chi} \overline{\sigma}^\mu i D_\mu \chi\nonumber\\
-&-\sqrt{2}g_s \left( -i (\sigma_{b\dagger} (-if_{abc}) (-i\chi^c) ) \lambda^a + i \overline{\lambda}^a (i\overline{\chi}_b (+if_{abc}) \sigma^{c\dagger}) \right)\nonumber\\
+\int\mathrm{d}^4\theta\ \hat{\overline{O}} \mathrm{e}^{2g_s\hat{V}^{\mathrm{fund}}_s} \hat{O} =\  & F_O^\dagger F_O + (D_\mu \sigma^a)^\dagger (D^\mu \sigma^a) + \overline{\chi} \overline{\sigma}^\mu i D_\mu \chi\nonumber\\
+&-\sqrt{2}g_s \left( -i (\sigma_b^\dagger (-if_{abc}) (-i\chi^c) ) \lambda^a + i \overline{\lambda}^a (i\overline{\chi}_b (+if_{abc}) \sigma^{c\dagger}) \right)\nonumber\\
 &-ig_s\sigma^{b^\dagger} f^{abc}D^a\sigma^c
@@
 These mass terms arise from a hidden sector spurion.
-For the gauginos the D-type spurion is given by $\hat{W}_\alpha^\prime = \theta_\alpha D$ and mediates super symmetry breaking at the mediation scale $M$: $\int\mathrm{d}\theta^2\frac{\hat{W}_\alpha^\prime}{M}W_s^\alpha \hat{O}$.
-After integrating out the spurion one obtains
+For gauginos the D-type spurion is given by $\hat{W}_\alpha^\prime = \theta_\alpha D$ and mediates super symmetry breaking at the mediation scale $M$: $\int\mathrm{d}\theta^2\frac{\hat{W}_\alpha^\prime}{M}W_s^\alpha \hat{O}$.
+After integrating out the spurion one obtains\cite{Fox:2002bu, Diessner:2015bna}
 \begin{align}
-\mathcal{L}_{soft} =\ & -\frac{m_{\tilde{q}}^2}{2}(|\tilde{q}_L|^2 + |\tilde{q}_R|^2)\nonumber\\
-& -\frac{m_{\sigma_1}^2}{2}\sigma_1^2 -\frac{m_{\sigma_2}^2}{2}\sigma_2^2 - m_g(\lambda\chi -\sqrt{2}D^a \sigma^a + h.c.)
+\mathcal{L}_{\mathrm{soft}} =\ & -\frac{m_{\tilde{q}}^2}{2}(|\tilde{q}_L|^2 + |\tilde{q}_R|^2)\nonumber\\
+& -m_{\sigma}^2\left|\sigma^{a}\right|^2 - m_g(\lambda\chi -\sqrt{2}D^a \sigma^a + h.c.)
 \end{align}
-where the complex scalar gluons $\sigma = \frac{\sigma_1 + i\sigma_2}{\sqrt{2}}$ constitutes of two real scalar gluons with different masses.
+where the complex scalar gluons which are also referred to as sgluons $\sigma = \frac{\phi_0 + i\sigma_0}{\sqrt{2}}$ constitute of two real ones with different masses.
 The equations of motion for the auxiliary fields are
 \begin{align}
-D^a =& -g_s \tilde{q}_L^\dagger T^a \tilde{q}_L + g_s \tilde{q}_R T^a \tilde{q}_R^\dagger + ig_s\sigma^{\dagger b}f^{abc}\sigma^c -\sqrt{2}m_g(\sigma^a + \sigma^{\dagger a})\\
+D^a =& -g_s \tilde{q}_L^\dagger T^a \tilde{q}_L + g_s \tilde{q}_R T^{\ast a} \tilde{q}_R^\dagger + ig_s\sigma^{\dagger b}f^{abc}\sigma^c -\sqrt{2}m_g(\sigma^a + \sigma^{\dagger a})\\
 F_i =&\ 0 \hspace{3cm} \mathrm{for} \hspace{3cm} i = L,R,O
@@
 where $D^a$ is still real as the purely imaginary parts to not contribute by virtue of the antisymmetry of the structure constants.
-After eliminating the auxiliary fields the complete Lagrangian in 4 spinor notation\footnote{How a 4 spinor is composed of Weyl-spinors is given in the Appendix \ref{sec:2spinor_notation}} reads
+After eliminating the auxiliary fields the complete Lagrangian reads in 4 spinor notation\footnote{How a 4 spinor is composed of Weyl-spinors is given in the Appendix \ref{sec:2spinor_notation}}
 \begin{align}
@@
 & -\sqrt{2}g_s \left( \overline{\tilde{g}}^a P_R (\tilde{g}^b (if^{abc}) \sigma^c) + (\sigma^{\dagger b} (-if^{abc}) \overline{\tilde{g}}^c)P_L\tilde{g}^a \right) \nonumber\\
-& -\frac{m_{\tilde{q}}^2}{2}(|\tilde{q}_L|^2 + |\tilde{q}_R|^2) -\frac{m_{\sigma_1}^2}{2}\sigma_1^2 -\frac{m_{\sigma_2}^2}{2}\sigma_2^2 -m_g \overline{\tilde{g}}^a\tilde{g}^a\nonumber\\
+& -\frac{m_{\tilde{q}}^2}{2}(|\tilde{q}_L|^2 + |\tilde{q}_R|^2) -m_{\sigma}^2\left|\sigma^a\right|^2  - m_g \overline{\tilde{g}}^a\tilde{g}^a\nonumber\\
 & -\frac{1}{2}\left( g_s \tilde{q}_L^\dagger T^a \tilde{q}_L - g_s \tilde{q}_R T^{\ast a} \tilde{q}_R^\dagger - ig_s\sigma^{\dagger b}f^{abc}\sigma^c + \sqrt{2}m_g(\sigma^a + \sigma^{\dagger a}) \right)^2\label{eq:L_RSQCD}
@@
 Observe that there is no 3 sgluon vertex, because of the antisymmetry of the structure constants $f^{abc}$.
+As already alluded to there are two distinct sgluons with different masses.
+The mass of the pseudoscalar $\sigma_0^a$ is given by the soft breaking parameter $m_{\sigma_0} = m_\sigma$ whereas the mass of the scalar $\phi^0$ is given by
+\begin{align}
+m_{\phi_0} = \sqrt{m_{\sigma_0}^2 + 4 m_{\tilde{g}}}.
+\end{align}
+The Feynman rules infered from this Lagrangian are given in Appendix \ref{sec:FeynmanRules}.
 \newpage

### 2016-06-16 Renormalization.tex
up to RSymmetry

@@
 \begin{align}
-\delta Z_q^{\mathrm{aux}} = -\frac{g_s^2}{16\pi^2} C(F)\left[ \Delta_\epsilon + B_1(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\right] .
+\delta Z_q^{\mathrm{aux}} = \frac{g_s^2}{16\pi^2} C(F)\left[ -\Delta_\epsilon + 2B_1(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\right] .
 \end{align}
@@
 &- \frac{4}{3} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\tilde{g}}^2}{\mu^2} \right) -\frac{2}{3}T(F) n_f \left( \Delta_\epsilon - \ln \frac{m_{\tilde{q}}^2}{\mu^2} \right)\nonumber\\
-& - \frac{1}{6} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\phi^0}^2}{\mu^2} \right) - \frac{1}{6} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\sigma^0}^2}{\mu^2} \right).
+& - \frac{1}{6} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\phi^0}^2}{\mu^2} \right) - \frac{1}{6} C(A) \left.\left.\left( \Delta_\epsilon - \ln \frac{m_{\sigma^0}^2}{\mu^2} \right)\right]\right\}
 \end{align}
+where the first squared brackets come from light and the second one from heavy particles running in the loop.
 
@@
 \begin{align}
-i\Gamma^{\mathrm{1L,heavy}}_{q_i \overline{q}_j G_\mu^a}(p_i^2=0) &= -ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} \left[ \left(C(F) -\frac{C(A)}{2}\right) 4C_{00}(0, 0, m_{\tilde{g}}^2, m_{\tilde{q}}^2, m_{\tilde{q}}^2) \right.\nonumber\\
-&\hspace{3.3cm} + \left. C(A)\left( B_0(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2) -2C_{00}(0, 0, m_{\tilde{g}}^2, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\right) \right]\nonumber\\
-&= -ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} \left[ \left(C(F) -\frac{C(A)}{2}\right) \left( \Delta_\epsilon - \ln \frac{m_{\tilde{g}}^2}{\mu^2} \right) \right.\nonumber\\
-&\hspace{3.3cm} + \left.\frac{C(A)}{2} \left( \Delta_\epsilon - \ln \frac{m_{\tilde{g}}^2}{\mu^2} \right) \right]
+i\Gamma^{\mathrm{1L,heavy}}_{q_i \overline{q}_j G_\mu^a}(p_i^2=0) &= -ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} \left[ \left(C(F) -\frac{C(A)}{2}\right) 4C_{00}(0, 0, 0, m_{\tilde{g}}^2, m_{\tilde{q}}^2, m_{\tilde{q}}^2) \right.\nonumber\\
+&\hspace{3.3cm} + \left. C(A)\left( B_0(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2) -2C_{00}(0, 0, 0, m_{\tilde{g}}^2, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\right) \right]\nonumber\\
+&= -ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} 2C(F)\left[ B_0(0,m_{\tilde{g}}^2,m_{\tilde{q}}^2) + B_1(0,m_{\tilde{g}}^2,m_{\tilde{q}}^2) \right]
 \end{align}
 The argument $p_i^2=0$ of the vertex function denotes, that all external particles are taken on shell, i.e. at zero momentum.\\
-insert $B_1$ function in order to cancel contribution from quark ren.const\\
 In the second line identities from \ref{sec:Passarino} have been used. The renormalization condition for the counterterm of the gauge coupling $\delta g_s$ reads
@@
 \end{align}
-Note the only difference to the MSSM is the appearence of the sgluon masses as well as a factor of two in front of the logarithm of the gluino mass which is due to twice as much degrees of freedom of the gluino in the MRSSM.
+Note the only difference to the MSSM\cite{Beenakker:1996ch} is the appearence of the sgluon masses as well as a factor of two in front of the logarithm of the gluino mass which is due to twice as much degrees of freedom of the gluino in the MRSSM.
 

### 2016-06-16 Standardmodel.tex
Latex does not compile any more
up to RSymmetry

@@
 \subsection{Symmetries and Transformations}
-\subsubsection*{Spacetime Symmetries}
+\subsubsection*{Space-time Symmetries}
 The Standard Model is defined on Minkowski space, whose coordinates are label with $x^\mu$ $\mu \in \left\{0,1,2,4\right\}$.
@@
 [P^\mu,J^{\nu\rho}] &= i(g^{\mu\nu} P^\rho - g^{\mu\rho}P^\nu)\nonumber\\
-[J^{\mu\nu},J^{\rho\sigma}] &= i(g^{\nu\rho}J^{\mu\rho} + g^{\mu\sigma}J^{\nu\rho} - g^{\mu\rho}J^{\nu\sigma} - g^{\nu\sigma}J^{\mu\rho}).
+[J^{\mu\nu},J^{\rho\sigma}] &= i(g^{\nu\rho}J^{\mu\rho} + g^{\mu\sigma}J^{\nu\rho} - g^{\mu\rho}J^{\nu\sigma} - g^{\nu\sigma}J^{\mu\rho}).\label{eq:PoincareAlgebra}
 \end{align}
@@
 \begin{align}
-\mathcal{L}_{Yang-Mills} = \overline{\Psi}i\slashed{D}\Psi - \frac{1}{4}F^{a\mu\nu}F^a_{\mu\nu}
+\mathcal{L}_{\mathrm{Yang-Mills}} = \overline{\Psi}i\slashed{D}\Psi - \frac{1}{4}F^{a\mu\nu}F^a_{\mu\nu}
 \end{align}
@@
 The same argument forbids terms like $-\frac{m^2}{2}A^\mu A_\mu$ for a generic gauge boson.
-Electroweak symmetry breaking (EWSB) ascribes masses to those particles \cite{Higgs:1964ia}, \cite{Higgs:1964pj}, \cite{Higgs:1966ev}, \cite{Englert:1964et}, \cite{Guralnik:1964eu}, \cite{Kibble:1967sv}, \cite{Bernstein:1974rd}.
+Electroweak symmetry breaking (EWSB) ascribes masses to those particles \cite{Higgs:1964ia, Higgs:1964pj, Higgs:1966ev, Englert:1964et, Guralnik:1964eu, Kibble:1967sv, Bernstein:1974rd}.
 To this end one considers a complex scalar doublet
@@
 \begin{align}
-&\mathcal{L}_{Higgs} = (D_\mu \Phi)^\dagger (D^\mu \Phi) - V(\Phi^\dagger\Phi).
+&\mathcal{L}_{\mathrm{Higgs}} = (D_\mu \Phi)^\dagger (D^\mu \Phi) - V(\Phi^\dagger\Phi).
 \end{align}
@@
 \begin{align}
-\mathcal{L}_{\mathrm{Yukawa}} = \sum_{i,j=1}^3 \left( y_{ij}^e \overline{\ell}_L \Phi e_R  + y_{ij}^d \overline{q}_L \Phi d_R + y_{ij}^u \overline{q}_L \Phi^C u_R\right) + h.c. 
+\mathcal{L}_{\mathrm{Yukawa}} = -\sum_{i,j=1}^3 \left( y_{ij}^e \overline{\ell}_L \Phi e_R  + y_{ij}^d \overline{q}_L \Phi d_R + y_{ij}^u \overline{q}_L \Phi^C u_R\right) + h.c. \label{eq:LYukawa}
 \end{align}
@@
 \end{align}
-The quark mass matrices are not diagonal, which is the preconditionof the violation of CP-invariance.
+The quark mass matrices are not diagonal, which is the precondition of the violation of CP-invariance.
 \footnote{The actual CP-violating term is the coupling term from quarks to the $W$-bosons.} One therefore has to distinguish between interaction and mass eigenstates of the quarks.
-The corresponding transformation matrix is the well known CKM-matrix \cite{Cabbibo:1964zsa}, \cite{Kobayashi:1973fv}.
+The corresponding transformation matrix is the well known CKM-matrix \cite{Cabbibo:1964zsa, Kobayashi:1973fv}.
 Throughout this thesis, the CKM-matrix is approximated with the unit matrix as it will have a minor influence upon the results\\
@@
 The Quantization of Spin 0 and Spin $\frac{1}{2}$ fields yield no complication in the Lagrangian formalism.
-To quantize Spin 1 fields it turns out that the usual gauge invariance needs to be replaced by the so called BRST invariance \cite{Becchi:1974xu},\cite{Becchi:1974md}, \cite{Becchi:1975nq}.
+To quantize Spin 1 fields it turns out that the usual gauge invariance needs to be replaced by the so called BRST invariance \cite{Becchi:1974xu, Becchi:1974md, Becchi:1975nq}.
 This results in two extra contributions in the Lagrangian.

### 2016-06-16 figures/Contour_Plots/MRSSM_TreeLevel.py

@@ -15,7 +15,7 @@ def nans(shape, dtype=float):
     return a
 
 # grid size
-N = 50 
+N = 40 
 
 def contourdata():
     """
@@ -27,13 +27,13 @@ def contourdata():
     # shape works in numpy                                                  
     sigma = nans((len(mass),len(mass)))  
     #myfile = open('MSSM_1_qqbar_sqsqdagger.txt', 'r')     
-    myfile = open('MSSM_MRSSM_2_GG_sqsqdagger.txt', 'r')
+    myfile = open('MRSSM_4_qqbar_ggbar.txt', 'r')
     i = 0
     for line in myfile:
         data = line.split()
         for j in range(0,N):
-            #sigma[j][i] = data[j]
-            sigma[j][i] = 9/(8**2)*data[j]
+            sigma[j][i] = data[j]
+            #sigma[j][i] = 9/(8**2)*data[j]
         i += 1   
     myfile.close()
     

### 2016-06-16 figures/One_Loop/MRSSM_uu_susu_Kfactors_msq=1000GeV.py

@@ -13,12 +13,10 @@ m_squark = np.array([], dtype=float);
 # arrays for XSection
 sigma_LO_Tree = np.array([], dtype=float);
 sigma_NLO_Tree = np.array([], dtype=float);
-sigma_NLO_Virt_withoutPrefactors = np.array([], dtype=float);
-sigma_NLO_Real_withoutPrefactors = np.array([], dtype=float);
 sigma_NLO_1L   = np.array([], dtype=float);
 
 
-f_Tree = open('MRSSM_Tree_uu_susu_msg=2000GeV.txt', 'r')
+f_Tree = open('MRSSM_Tree_uu_susu_msq=1000GeV.txt', 'r')
 
 for lines in f_Tree.readlines():
     m_squark = np.append(m_squark, float(lines.split()[0]))
@@ -27,14 +25,12 @@ for lines in f_Tree.readlines():
 f_Tree.close()
 
 
-f_1L = open('MRSSM_1L_uu_susu_msg=2000GeV.txt', 'r')
+f_1L = open('MRSSM_1L_uu_susu_msq=1000GeV.txt', 'r')
 discard = f_1L.readline()
 for lines in f_1L.readlines():
     discard = np.append(m_squark, float(lines.split()[0]))
     sigma_NLO_Tree = np.append(sigma_NLO_Tree, float(lines.split()[1]))
-    sigma_NLO_Virt_withoutPrefactors = np.append(sigma_NLO_Virt_withoutPrefactors, float(lines.split()[2]))
-    sigma_NLO_Real_withoutPrefactors = np.append(sigma_NLO_Real_withoutPrefactors, float(lines.split()[3]))
-    sigma_NLO_1L = np.append(sigma_NLO_1L, float(lines.split()[4]))    
+    sigma_NLO_1L = np.append(sigma_NLO_1L, float(lines.split()[2]))    
 f_1L.close()
 
 K_min = 0
@@ -45,7 +41,7 @@ fig = plt.figure(1,figsize=(10, 9))
 
 
 first_window = plt.subplot(111)
-plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = 22)
+plt.xlabel(r"$m_{\tilde{g}}$ in GeV", size = 22)
 plt.ylabel(r"$K(uu \to \tilde{u}\tilde{u})$ ", size = 22)
 plt.xticks(fontsize = 20)
 plt.yticks(fontsize = 20)
[…]

### 2016-06-16 figures/One_Loop/MRSSM_uu_susu_Kfactors_msq=1000GeV_msg=2000GeV.py

@@ -1,0 +1,67 @@
+# -*- coding: utf-8 -*-
+"""
+C++ code on laptop in WARB-talk
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_sgluon = np.array([], dtype=float);
+# arrays for XSection
+sigma_LO_Tree = np.array([], dtype=float);
+sigma_NLO_Tree = np.array([], dtype=float);
+sigma_NLO_Virt_withoutPrefactors = np.array([], dtype=float);
+sigma_NLO_Real_withoutPrefactors = np.array([], dtype=float);
+sigma_NLO_1L   = np.array([], dtype=float);
+
+
+f_1L = open('MRSSM_1L_uu_susu_msq=1000GeV_msg=2000GeV.txt', 'r')
+discard = f_1L.readline()
+for lines in f_1L.readlines():
+    m_sgluon = np.append(m_sgluon, float(lines.split()[0]))
+    sigma_NLO_Tree = np.append(sigma_NLO_Tree, float(lines.split()[1]))
+    sigma_NLO_1L = np.append(sigma_NLO_1L, float(lines.split()[2]))    
+f_1L.close()
+
+sigma_LO_Tree = m_sgluon * 0 + 11.48
+
+K_min = 0
+K_max = max(sigma_NLO_1L/sigma_LO_Tree) + 0.1
+
+fig = plt.figure(1,figsize=(10, 9))
+#fig.suptitle(r'cross-sections for squark production at the LHC at $\sqrt{s}=13$TeV', fontsize=20)
+
+
+first_window = plt.subplot(111)
+plt.xlabel(r"$m_{\tilde{\sigma}}$ in GeV", size = 22)
+plt.ylabel(r"$K(uu \to \tilde{u}\tilde{u})$ ", size = 22)
+plt.xticks(fontsize = 20)
+plt.yticks(fontsize = 20)
+
+# set scientific notation
+plt.xscale('log')
+#plt.ticklabel_format(style='sci', axis='x', scilimits=(0,0))
+plt.axis([min(m_sgluon),max(m_sgluon),K_min,K_max])
+plt.axes(first_window)
+
+first_window.fill_between(m_sgluon, m_sgluon*0, sigma_NLO_Tree/sigma_LO_Tree, 
[…]

### 2016-06-21 Appendix.tex
Feynman Rules

@@
 \subsection{Feynman rules for the RSQCD}\label{sec:FeynmanRules}
-The following Feynman rules are derived from \ref{eq:L_RSQCD}.
+The following Feynman rules are derived from the Lagrangian of the R-symmetric supersymmetric quantum chromodynamics (RSQCD) eq.
+\ref{eq:L_RSQCD}.
 When compared with the Feynman rules of the supersymmetric QCD the diagrams involving scalar gluons are new.
-In addition the gluon-quark-squark vertex is different in RSQCD for the gauginos are Dirac fermions.\\
-refer to paper cited in Beenakker(Appendix: Feynmanrules)
+In addition the gluon-quark-squark vertex is different in RSQCD for the gauginos are Dirac fermions.
+Note that for calculations involving fermions one needs to go in the opposite direction of the fermion flow which is given by a curved arrow next to the diagrams in fig.
+\ref{fig:secondFeynmanRules} and does not always agree with the flow of fermion number given by the direction of the Dirac propagator.
+This renders the evaluation of fermion number violating processes like $qq \to \tilde{q}\tilde{q}$ unambiguous, cf.
+\cite{Beenakker:1996ch}.
+%refer to paper cited in Beenakker(Appendix: Feynmanrules)
 \begin{figure}[!htbp]
@@
 \caption{In the Feynman diagrams of the propagators the momentum is flowing from the right to the left hand side.\newline
-In the Feynman diagrams of the vertices all momenta flow towards the vertex.\newline
-The indices $A,B = L,R$ label the right/left-"handedness" of the squarks.
+In the Feynman diagrams of the vertices all momenta flow towards the vertex, i.e. in diagram 9 $-p_1$ is flowing towards the vertex.\newline
+The indices $A,B \in \left\{ L,R \right\}$ label the left/right "handedness" of the squarks.
 The indices $i,j=1,2,3$ are the color indices in the (anti)fundamental representation where $a,b,c,\hdots = 1,\hdots,8$ are the color indices of the adjoint representation.}\label{fig:firstFeynmanRules}
@@
 	\node(g) at (0.9,-0.6) {};
-	\path[line width=0.8pt,->] (g) edge [out=135, in=-135] (gbar);
+	\path[line width=0.8pt,<-] (g) edge [out=135, in=-135] (gbar);
 	\node at (2,0) {$\hat{=}  - g_s f_{abc} \gamma^\mu$};
@@
 	\node(u) at (0.4,-0.8) {};
-	\path[line width=0.8pt,->] (g) edge [out=0, in=135] (u);
+	\path[line width=0.8pt,<-] (g) edge [out=0, in=135] (u);
 	\node at (3,0) {$\hat{=} -i\sqrt{2}g_s T^a_{ij}P_L$};
@@
 	\node(u) at (0.4,-0.8) {};
-	\path[line width=0.8pt,->] (g) edge [out=0, in=135] (u);
+	\path[line width=0.8pt,<-] (g) edge [out=0, in=135] (u);
 	\node at (3,0) {$\hat{=} +i\sqrt{2}g_s T^a_{ij}P_L$};
@@
 	\node(u) at (0.4,-0.8) {};
-	\path[line width=0.8pt,->] (g) edge [out=0, in=135] (u);
+	\path[line width=0.8pt,<-] (g) edge [out=0, in=135] (u);
 	\node at (3,0) {$\hat{=} -\sqrt{2}g_s f^{abc}P_L$};
@@
 the fermion flow and replace $\Psi$ with $\bar{\Psi}^C$.
-In addition one has to add a minus sign for Feynman rule 13.}
+In addition one has to add a minus sign for Feynman rule 13.}\label{fig:secondFeynmanRules}
 \end{figure}
@@
 \end{align}
-The scaleless integrals are defined to be zero.
+The scaleless integrals are defined to be zero due to their definition  on how they scale in $D$ dimensions\cite{Collins:105730}.
 The parameter $t$ is given by $\frac{m_2^2}{m_1^2}$.

### 2016-06-21 Masterarbeit.tex
Feynman Rules

@@
 Hiermit erkläre ich, dass ich diese Arbeit im Rahmen der Betreuung am Institut
-für ??? Physik ohne unzulässige Hilfe Dritter verfasst und alle Quellen als solche gekennzeichnet habe.
+für Kern- und Teilchenphysik ohne unzulässige Hilfe Dritter verfasst und alle Quellen als solche gekennzeichnet habe.
 \vspace*{45em}
 Vorname Nachname \par
-Dresden, Monat 2012
+Dresden, Juli 2016
 

### 2016-06-21 Renormalization.tex
Feynman Rules

@@
 \section{Renormalization of the MRSSM}\label{sec:renMRSSM}
-In order to improve the prediction of the cross section of the previous chapter one has to take quantum corrections into account.
+In order to improve the prediction of cross sections one has to take quantum corrections into account.
 These are associated with loops in the corresponding Feynman diagrams.
-Computing these loop diagrams one might encounter infinities which arise from certain momentum configurations of the unspecified loop momentum.
+Computing these loop diagrams one might encounter infinities which arise from certain momentum configurations of the unspecified loop momenta.
 These infinities can be classified due to their origin.
@@
 Infinities arising from loop momenta approaching zero can occur in loops with massless particles and are called infrared(IR) singularities.
-Furthermore there are collinear singularities with occur when a massless particle splits into two massless collinear particles.\\
+\\%Furthermore there are collinear singularities with occur when a massless particle splits into two massless collinear particles.\\
 These infinities are not physical and must therefore be removed to get sensible predictions.
@@
 However DREG suffers a flaw in supersymmetry.
-As the degrees of freedom for a massless gauge boson are $D-2$ but the degrees of freedom for its superpartner are 2 there is a mismatch if $D \neq 4$.
+As the degrees of freedom of a massless gauge boson are $D-2$ but the degrees of freedom of its superpartner are 2 there is a mismatch if $D \neq 4$.
 As a consequence there are $2\epsilon$ degrees of freedom associated with the gluon\footnote{These degrees of freedom are identified with scalars and are therefore referred to as $\epsilon$ scalars} which do not have a supersymmetric partner.
@@
 \subsection{Regularization Scheme Dependences}\label{sec:RegSchemeDep}
-It is useful to introduce the effective action $\Gamma$ to discuss the subject of this and ensuing subsections.
+To discuss the subject of this and ensuing subsections it is useful to introduce the effective action $\Gamma$.
 A formal introduction of $\Gamma$ can be found in~\cite{Peskin}.
@@
 $\Gamma^{(\leq 1)}_{\mathrm{DREG}}$ is not supersymmetric.
-To maintain supersymmetry invariance of the renormalized effective action the counterterms will not only consist of supersymmetric counterterms $\Gamma^{(1),\ \mathrm{ct,\ sym}}_{\mathrm{DREG}}$ but also of counterterms restoring supersymmetry $\Gamma^{(1),\ \mathrm{ct,\ restore}}_{\mathrm{DREG}}$.
+To maintain supersymmetry invariance of the renormalized effective action the counterterms will not only consist of supersymmetric counterterms $\Gamma^{(1),\ \mathrm{ct,\ sym}}_{\mathrm{DREG}}$ but also of counterterms restoring supersymmetry $\Gamma^{(1),\ \mathrm{ct,\ trans}}_{\mathrm{DREG}}$.
 \begin{align}
-\Gamma^{(1),\ \mathrm{ct}}_{\mathrm{DREG}} = \Gamma^{(1),\ \mathrm{ct,\ sym}}_{\mathrm{DREG}} + \Gamma^{(1),\ \mathrm{ct,\ restore}}_{\mathrm{DREG}}
+\Gamma^{(1),\ \mathrm{ct}}_{\mathrm{DREG}} = \Gamma^{(1),\ \mathrm{ct,\ sym}}_{\mathrm{DREG}} + \Gamma^{(1),\ \mathrm{ct,\ trans}}_{\mathrm{DREG}}
 \end{align}
@@
 \end{align}
-Equating also the finite terms in $\Gamma^{(1),\ \mathrm{ct,\ sym}}$ in DRED and DREG the choice of the supersymmetry restoring counterterms is fixed by:
+Equating also the finite terms in $\Gamma^{(1),\ \mathrm{ct,\ sym}}$ in DRED and DREG the choice of the supersymmetry restoring counterterms is fixed by\cite{Varso}:
 \begin{align}
-\Gamma^{\mathrm{(1),ct,restore}}_{\mathrm{DREG}} = \Gamma^{(\leq 1)}_{\mathrm{DREG}} - \Gamma^{(\leq 1)}_{\mathrm{DREG}}.\label{eq:GammaCtRestore}
+\Gamma^{\mathrm{(1),ct,trans}}_{\mathrm{DREG}} = \Gamma^{(\leq 1)}_{\mathrm{DRED}} - \Gamma^{(\leq 1)}_{\mathrm{DREG}}.\label{eq:GammaCtRestore}
 \end{align} 
-This way supersymmetry is preserved by the renormalization constants.\\ 
+This equation justifies the label "trans" at the supersymmetry restoring counterterm because it actually describes the transition counterterm from DREG to DRED or vice versa.\\ %This way supersymmetry is preserved by the renormalization constants.\\
 In the case of the MRSSM it will turn out that the only supersymmetry violation comes from corrections associated with the gluon as already alluded to in section \ref{sec:RegSchemes}.
 However supersymmetry restoring will always already be included in $\delta Z^{\mathrm{DREG}}$.
-This is $\delta Z^{\mathrm{DREG}} = \delta Z^{\mathrm{DREG,sym}} + \delta Z^{\mathrm{trans}}$ where $\delta Z^{\mathrm{trans}} = \delta Z^{\mathrm{DREG}} - \delta Z^{\mathrm{DRED}}$ is the supersymmetry restoring renormalization constant.
+Referring to the field renormalization constants from eq.
+\ref{eq:fieldtrafo} this is
+\begin{align}
+\delta Z^{\mathrm{DREG}} = \delta Z^{\mathrm{DREG,sym}} + \delta Z^{\mathrm{trans}}
+\end{align}
+where 
+\begin{align}
+\delta Z^{\mathrm{trans}} = \delta Z^{\mathrm{DREG}} - \delta Z^{\mathrm{DRED}}
+\end{align}
+is the supersymmetry restoring renormalization constant.
+Note the sign within this definition in comparison to eq.
+\ref{eq:GammaCtRestore}.
 The only point where particularly care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms due to different loop diagrams.
 Therefore one has to make a difference between these couplings at 1-loop level.
-In order to match $g_s$ to the experimentally measured coupling it is renormalized in the  $\overline{\mathrm{MS}}$-scheme (with an additional manipulation for heavy particles, which will be explained in section \ref{sec:RenGaugeCoupling}).
-The Yukawa coupling $\hat{g}_s$ therefore needs to be added with the difference of the supersymmetry restoring counterterms from the $q\tilde{q}^\dagger\tilde{g}$ vertex and the $q\overline{q}G$ vertex at 1-loop in order to be renormalized the same way.
+In order to match $g_s$ to the experimentally measured coupling it is renormalized in the  $\overline{\mathrm{MS}}$-scheme (with an additional manipulation for heavy particles, which will be explained in subsection \ref{sec:RenGaugeCoupling}).
+The Yukawa coupling $\hat{g}_s$ therefore needs to be added with the difference of the supersymmetry restoring counterterms from the $q\tilde{q}^\dagger\tilde{g}$ vertex and the $q\overline{q}G$ vertex at 1-loop in order to be renormalized in the same way.
 
@@
 \subsection{On-Shell Renormalization}\label{sec:QuarkSE}
-A part of the computation of NLO processes is the calculation of renormalization constants.
+A part of the computation of the cross section at next-to-leading order is the calculation of renormalization constants. 
+Field renormalization constants $\delta Z$ and parameter renormalization constants $\delta o$ with $o \in \left\{ g, m \right\}$ are defined by
+\begin{align}
+Z = 1 + \delta Z \hspace{3cm} o_{\mathrm{bare}} = o + \delta o
+\end{align}
+where $Z$ and $o$ are defined by the multiplicative renormalization transformation, introduced in eq.
+\ref{eq:fieldtrafo} and \ref{eq:fieldtrafo}.
 The field and mass renormalization constants have been calculated in DREG in the on-shell scheme.
-This has the advantaged that when turning to the cross section no manipulation of the Green function to the S-matrix element has to be done.
+This has the advantage that when turning to the cross section no manipulation of the Green function to the S-matrix element has to be done, see section \ref{sec:LSZ}.
 
 \subsubsection*{The Quark Self-Energy}
-The quark self-energy splits into contribution from the SM as well as a supersymmetric analogue which is already present in the MSSM.
+The quark self-energy splits into contribution from the Standard Model as well as a supersymmetric analogue which is already present in the MSSM.
 \begin{figure}[!htbp]
@@
 \end{tikzpicture}
-\caption{Feynman diagrams contributing to the self-energy of the quark at 1-loop level}\label{fig:QuarkSelfEnergy}
+\caption{Feynman diagrams contributing to the self-energy of the quark at 1-loop level.}\label{fig:QuarkSelfEnergy}
 \end{center}
 \end{figure}\\
-The 1-PI diagrams evaluate to
+The one-particle-irreducible diagrams evaluate to
 \begin{align}
-i\Gamma^{1L}_{q_i\overline{q}_j} = i \frac{g_s^2}{16\pi^2}\delta_{ij} C(F) \left[ 2 \left( B_0(p^2,0,0) + B_1(p^2,0,0)-\frac{1}{2}\right)\slashed{p} - 2 B_1(p^2,m_{\tilde{g}}^2,m_{\tilde{q}}^2)\slashed{p}\right].\label{eq:QuarkSE}
+i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j} = i \frac{g_s^2}{16\pi^2}\delta_{ij} C(F) \left[ 2 \left( B_0(p^2,0,0) + B_1(p^2,0,0)-\frac{1}{2}\right)\slashed{p} - 2 B_1(p^2,m_{\tilde{g}}^2,m_{\tilde{q}}^2)\slashed{p}\right].\label{eq:QuarkSE}
 \end{align}
@@
 \begin{tikzpicture}[line width=1.0 pt, scale=0.8]
-	\node at (-2.5,-0.1) {$i\Gamma^{1L,ct}_{q_i\overline{q}_j}\ \hat{=}\ i$};
+	\node at (-2.5,-0.1) {$i\Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}\ \hat{=}\ i$};
 \begin{scope}[shift={(0.1,0)}]	
@@
 	\draw[fermionbar] (0,0) --(1.3,0);
-	\node at (1.6,0) {$j$};
+	\node at (1.6,-0.1) {$j$};
 	\node at (3,0) {$\hat{=}\ i\delta_{ij}\delta Z_q \slashed{p} $};	
@@
 \end{align}
-Note that the term $\frac{1}{2}$ from eq.
-\ref{eq:QuarkSE} has vanished because the self energy is taken on-shell which means that this factor is absorbed into the on-shell $B_0$ function which is in DREG defined to be zero if it has no mass scale.\\
-Doing the same calculation in DRED one finds that this very term $\frac{1}{2}$ is absent. Therefore the transition counterterm between DREG and DRED is given by
+Note that the Standard Model contribution to the quark renormalization constant equals zero as it is propotional to $B_0(0,0,0)$ and $B_1(0,0,0)$.
+These integrals have no mass scale and are due to their definition of their scaling in $D$ dimensions\cite{Collins:105730} defined to be zero.
+Pictorially this may be understood as a cancellation of a positive UV-divergent part and a negative IR-divergent part.
+Note further that the term $\frac{1}{2}$ from eq.
+\ref{eq:QuarkSE} has vanished because it has been absorbed in $B_0(p^2,0,0)|_{p^2 \to 0}$.\\
+Doing the same calculation in DRED one finds that this very term $\frac{1}{2}$ is absent. Therefore the transition renormalization constant between DREG and DRED is given by
 \begin{align}
@@
 \subsubsection*{The Squark Self-Energy}
-The contributions to the self-energy of the left- and right-handed squark are the same.
+The contributions to the self-energy of the left- and right-handed squark are the same for electroweak effects are neglected.
 Therefore to avoid unnecessary labeling $\Gamma_{\tilde{q}\tilde{q}^\dagger}$ stands in the following for $\Gamma_{\tilde{q}_L\tilde{q}_L^\dagger} = \Gamma_{\tilde{q}_R\tilde{q}_R^\dagger}$.
@@
 \end{tikzpicture}
-\caption{Diagrammatic contributions to the self-energy of the squark at 1-loop level}
+\caption{Diagrammatic contributions to the self-energy of the squark at 1-loop level.}
 \end{center}
@@
 \begin{align}
-i\Gamma^{1L}_{\tilde{q}_{i}\tilde{q}^\dagger_j} &= i \frac{g_s^2}{16\pi^2}\delta_{ij}C(F) \left[  A_0(m_{\tilde{q}}^2) + 0 - \left( 4A_0(m_{\tilde{g}}^2) + 4B_1(p^2,0,m_{\tilde{g}}^2)p^2 \right) \right.\nonumber\\
+i\Gamma^{\mathrm{1L}}_{\tilde{q}_{i}\tilde{q}^\dagger_j} &= i \frac{g_s^2}{16\pi^2}\delta_{ij}C(F) \left[  A_0(m_{\tilde{q}}^2) + 0 - \left( 4A_0(m_{\tilde{g}}^2) + 4B_1(p^2,0,m_{\tilde{g}}^2)p^2 \right) \right.\nonumber\\
 & \left.+ 4m_{\tilde{g}}^2B_0(p^2,m_{\phi^0}^2,m_{\tilde{q}}^2) - \left(2B_1(p^2,0,m_{\tilde{q}}^2)p^2 + B_0(p^2,0,m_{\tilde{q}}^2)(m_{\tilde{q}}^2+3p^2) \right) \right].
@@
 	\draw[scalarbar] (0,0) --(1.3,0);
-	\node at (1.6,0) {$j$};
-	\node at (5,0) {$\hat{=}\ i\delta_{ij} \left[ \delta Z_{\tilde{q}}(p^2-m_{\tilde{q}}^2) - \delta m_{\tilde{q}}^2 \right] .$};	
+	\node at (1.6,-0.1) {$j$};
+	\node at (5.1,0) {$\hat{=}\ i\delta_{ij} \left[ \delta Z_{\tilde{q}}(p^2-m_{\tilde{q}}^2) - \delta m_{\tilde{q}}^2 \right] .$};	
 \end{scope}
@@
 \end{align}
+and
 \begin{align}
 \delta m_{\tilde{q}}^2 = \frac{g_s^2}{16\pi^2}C(F)&\left[ A_0(m_{\tilde{q}}^2) - (4A_0(m_{\tilde{g}}^2) + 4B_1(m_{\tilde{q}}^2,0,m_{\tilde{g}}^2)m_{\tilde{q}}^2) + 4 m_{\tilde{g}}^2 B_0(m_{\tilde{q}}^2,m_{\phi^0}^2,m_{\tilde{q}}^2) \right.\nonumber\\
-&\left. -(2B_1(m_{\tilde{q}}^2,0,m_{\tilde{q}}^2) m_{\tilde{q}}^2 + 4 B_0(m_{\tilde{q}}^2,0,m_{\tilde{q}}^2)m_{\tilde{q}}^2) \right]
+&\left. -(2B_1(m_{\tilde{q}}^2,0,m_{\tilde{q}}^2) m_{\tilde{q}}^2 + 4 B_0(m_{\tilde{q}}^2,0,m_{\tilde{q}}^2)m_{\tilde{q}}^2) \right].
 \end{align}
@@
 \tilde{g}^a = \begin{pmatrix}
-\lambda^a \\
-\overline{\chi}^a
+-i\lambda^a \\
+i\overline{\chi}^a
 \end{pmatrix}
@@
 Where $n_f = 6$ is the number of quark flavors.\\
-The counterterm Feynman rule reads\\
+The counterterm Feynman rule derived from multiplicative renormalization reads\\
 \begin{tikzpicture}[line width=1.0 pt, scale=0.8]
@@
 where the derivative of $\Sigma = \Sigma^{VL}P_L\slashed{p} + \Sigma^{VR}P_R\slashed{p} + \Sigma^{SL}P_L + \Sigma^{SR}P_R$ with respect to $P_A\slashed{p}$ \\
-($A \in \left\{ L,R \right\}$) is defined by
+($A \in \left\{ L,R \right\}$) is defined by\cite{FormCalcManual}
 \begin{align}
@@
 \end{align}
-As for the quark there are constant terms amid the Passarino-Veltman integrals. These arise only in DREG and not in DRED. The transition counterterms are
+As for the quark there are constant terms amid the Passarino-Veltman integrals. These arise only in DREG but and not in DRED. The transition counterterms are
 \begin{align}
@@
 \end{align}
+Apart from the renormalization constant of the gauge coupling and the supersymmetry restoring counterterm these are all renormalization constants needed from squark production at next to leading order.
+In fact the field renormalization constants of the gluino are not needed as they drop out when summing up all three counterterm Feynman diagrams.
+This can be seen when writing down the matrix amplitudes for the counterterm Feynman diagrams:
+\begin{align}
+\mathcal{M}^{\mathrm{B}} &= -2g_s^2 \frac{\left\langle v2 |P_R \slashed{k}_3|u1\right\rangle}{t_{\tilde{g}}} T^a_{13} T^a_{24} + 2g_s^2 \frac{\left\langle v2 |P_L \slashed{k}_3|u1\right\rangle}{u_{\tilde{g}}} T^a_{14} T^a_{23}\\
+\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}} &= 2 \mathcal{M}^B  \left( \frac{\delta \hat{g}_s}{\hat{g}_s} \frac{\delta Z_q}{2} + \frac{\delta Z^L_{\tilde{g}}}{2} + \frac{\delta Z_{\tilde{q}}}{2} \right)\\
+\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}} &= \hdots = 
+\mathcal{M}^B \left[ \frac{-(t_{\tilde{g}})\delta Z_{\tilde{g}}^L + 2 \delta m_{\tilde{g}}m_{\tilde{g}}}{t_{\tilde{g}}}\right.\\
+&\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \left. \frac{-(u_{\tilde{g}})\delta Z_{\tilde{g}}^L + 2 \delta m_{\tilde{g}}m_{\tilde{g}}}{u_{\tilde{g}}}\right]
+\end{align}
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}[line width=1 pt, scale=1]
+	\draw[fermion] (3,0.5)--(4,0.5);
+	\draw[fermion] (3,-0.5)--(4,-0.5);
+	\draw[fermionnoarrow] (3.8,0.7)--(4.2,0.3);
+	\draw[fermionnoarrow] (3.8,0.3)--(4.2,0.7);
+	\draw[fermionnoarrow] (4,0.5)--(4,-0.5);
+	\draw[gluon] (4,0.5)--(4,-0.5);
+	\draw[scalar] (4,0.5)--(5,0.5);
+	\draw[scalar] (4,-0.5)--(5,-0.5);
+	\node at (2.8,0.5) {$u$};
+	\node at (2.8,-0.5) {$u$};
+	\node at (5.2,0.5) {$\tilde{u}_L^\dagger$};
+	\node at (5.2,-0.5) {$\tilde{u}_R^\dagger$};
+	\node at (6,0) {+};
+	\draw[fermion] (7,0.5)--(8,0.5);
+	\draw[fermion] (7,-0.5)--(8,-0.5);
+	\draw[fermionnoarrow] (7.8,-0.7)--(8.2,-0.3);
+	\draw[fermionnoarrow] (7.8,-0.3)--(8.2,-0.7);
+	\draw[fermionnoarrow] (8,0.5)--(8,-0.5);
+	\draw[gluon] (8,0.5)--(8,-0.5);
+	\draw[scalar] (8,0.5)--(9,0.5);
+	\draw[scalar] (8,-0.5)--(9,-0.5);
+	\node at (6.8,0.5) {$u$};
+	\node at (6.8,-0.5) {$u$};
+	\node at (9.2,0.5) {$\tilde{u}_L^\dagger$};
+	\node at (9.2,-0.5) {$\tilde{u}_R^\dagger$};
+\begin{scope}[shift={(8,0)}]	
+	\node at (2,0) {+};
+	\draw[fermion] (3,0.5)--(4,0.5);
+	\draw[fermion] (3,-0.5)--(4,-0.5);
+	\draw[fermionnoarrow] (3.8,0.2)--(4.2,-0.2);
+	\draw[fermionnoarrow] (3.8,-0.2)--(4.2,0.2);
+	\draw[fermionnoarrow] (4,0.5)--(4,-0.5);
+	\draw[gluon] (4,0.5)--(4,-0.5);
+	\draw[scalar] (4,0.5)--(5,0.5);
+	\draw[scalar] (4,-0.5)--(5,-0.5);
+	\node at (2.8,0.5) {$u$};
+	\node at (2.8,-0.5) {$u$};
+	\node at (5.2,0.5) {$\tilde{u}_L^\dagger$};
+	\node at (5.2,-0.5) {$\tilde{u}_R^\dagger$};
+	\node at (6.9,) {+\ \ u-channel};
+\end{scope}
+\end{tikzpicture}
+\caption{1-Loop-Level Counterterm Feynman diagrams for squark production in the MRSSM}
+\end{center}
+\end{figure}
 
@@
 \subsubsection*{The $q\overline{q}G$ Vertex Correction}
-As for the self energies the vertex correction constitutes of loops from light particles which correspond to the Standard Model and additional heavy particle loops.
+As for the self energies the vertex correction is composed of loops from light particles from the Standard Model and additional heavy particle loops.
 \begin{figure}[!htbp]
@@
 &\hspace{3.3cm} + \left. C(A)\left( B_0(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2) -2C_{00}(0, 0, 0, m_{\tilde{g}}^2, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\right) \right]\nonumber\\
-&= -ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} 2C(F)\left[ B_0(0,m_{\tilde{g}}^2,m_{\tilde{q}}^2) + B_1(0,m_{\tilde{g}}^2,m_{\tilde{q}}^2) \right]
+&= ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} 2C(F)B_1(0,m_{\tilde{g}}^2,m_{\tilde{q}}^2)
 \end{align}
@@
 As already discussed in section \ref{sec:RegSchemeDep} care is required in terms of supersymmetry restoring when renormalizing  the gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$.
-In doing so one needs the already calculated transition counterterms of the quark, squark and gluino from \ref{eq:QuarkSC}, \ref{eq:SquarkSC} and \ref{eq:GluinoSC}
+In doing so one needs the already calculated transition counterterms of the quark, squark and gluino from eq.
+\ref{eq:QuarkSC}, \ref{eq:SquarkSC} and \ref{eq:GluinoSC}
 as well as the transition counterterm of the gluon.
@@
 the last diagram in figure \ref{fig:lightGluonSelfEnergy}.
-With the definition of $\Gamma^{\mathrm{(1),ct,restore}}_{\mathrm{DREG}}$ in \ref{eq:GammaCtRestore} one obtains
+With the definition of $\Gamma^{\mathrm{(1),ct,trans}}_{\mathrm{DREG}}$ in eq.
+\ref{eq:GammaCtRestore} one obtains
 \begin{align}
-i\Gamma^{\mathrm{(1),ct,restore}}_{\mathrm{DREG},G_\mu^a G_\nu^b} = -i\frac{1}{3} C(A) \frac{g_s^2}{16\pi^2}(p^2 g^{\mu\nu}-p^\mu p^\nu)\delta_{ab}
+i\Gamma^{\mathrm{(1),ct,trans}}_{\mathrm{DREG},G_\mu^a G_\nu^b} = -i\frac{1}{3} C(A) \frac{g_s^2}{16\pi^2}(p^2 g^{\mu\nu}-p^\mu p^\nu)\delta_{ab}
 \end{align}
@@
 \begin{align}
-i\Gamma^{\mathrm{(1),ct,restore}}_{\mathrm{DREG}, q_i\overline{q}_jG_\mu^a} &= -ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2}\left[ \left( C(F) - \frac{C(A)}{2} \right) + \frac{C(A)}{2} \right]\\
+i\Gamma^{\mathrm{(1),ct,trans}}_{\mathrm{DREG}, q_i\overline{q}_jG_\mu^a} &= -ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2}\left[ \left( C(F) - \frac{C(A)}{2} \right) + \frac{C(A)}{2} \right]\\
 &= -ig_s T^a_{ij} \gamma^\mu \left[ \frac{\delta g_s^{\mathrm{trans}}}{g_s} + \delta Z^{\mathrm{trans}}_q + \frac{\delta Z^{\mathrm{trans}}_G}{2} \right]
@@
 \subsubsection*{The $q\tilde{q}^\dagger\tilde{g}$ Vertex Correction}
-The supersymmetry restoring corrections to the Yukawa coupling origin from the diagram below.
+The supersymmetry restoring corrections to the Yukawa coupling originate from the diagram below.
 \begin{figure}[!htbp]
@@
 \end{tikzpicture}
-\caption{diagram of the supersymmetry restoring correction of  the $q\tilde{q}\tilde{g}$ vertex}
+\caption{Diagram of the supersymmetry restoring correction of  the $q\tilde{q}\tilde{g}$ vertex}
 \end{center}
@@
 \begin{align}
-i\Gamma^{\mathrm{(1),ct,restore}}_{\mathrm{DREG}, q_i\tilde{q}_j\tilde{g}^a} &= -ig_s \sqrt{2} P_L T^a_{ij}  \frac{g_s^2}{16\pi^2}C(A)\\
+i\Gamma^{\mathrm{(1),ct,trans}}_{\mathrm{DREG}, q_i\tilde{q}_j\tilde{g}^a} &= -ig_s \sqrt{2} P_L T^a_{ij}  \frac{g_s^2}{16\pi^2}C(A)\\
 &= -ig_s \sqrt{2} P_L T^a_{ij}  \left[ \frac{\delta \hat{g}_s^{\mathrm{trans}}}{g_s} + \frac{\delta Z^{\mathrm{trans}}_q + \delta Z^{\mathrm{trans}}_{\tilde{q}} + \delta Z^{\mathrm{trans}}_{\tilde{g}}}{2} \right].

### 2016-06-21 figures/One_Loop/MRSSM_uu_susu_Kfactors_msg=2000GeV.py

@@ -13,8 +13,6 @@ m_squark = np.array([], dtype=float);
 # arrays for XSection
 sigma_LO_Tree = np.array([], dtype=float);
 sigma_NLO_Tree = np.array([], dtype=float);
-sigma_NLO_Virt_withoutPrefactors = np.array([], dtype=float);
-sigma_NLO_Real_withoutPrefactors = np.array([], dtype=float);
 sigma_NLO_1L   = np.array([], dtype=float);
 
 
@@ -32,9 +30,7 @@ discard = f_1L.readline()
 for lines in f_1L.readlines():
     discard = np.append(m_squark, float(lines.split()[0]))
     sigma_NLO_Tree = np.append(sigma_NLO_Tree, float(lines.split()[1]))
-    sigma_NLO_Virt_withoutPrefactors = np.append(sigma_NLO_Virt_withoutPrefactors, float(lines.split()[2]))
-    sigma_NLO_Real_withoutPrefactors = np.append(sigma_NLO_Real_withoutPrefactors, float(lines.split()[3]))
-    sigma_NLO_1L = np.append(sigma_NLO_1L, float(lines.split()[4]))    
+    sigma_NLO_1L = np.append(sigma_NLO_1L, float(lines.split()[2]))    
 f_1L.close()
 
 K_min = 0
@@ -66,9 +62,6 @@ first_window.fill_between(m_squark, sigma_NLO_Tree/sigma_LO_Tree, sigma_NLO_1L/s
 facecolor=[1,90./100,90./100], color =[1,80./100,80./100], linestyle="-", label = "Real and virtual corrections")
 
 plt.plot(m_squark, sigma_NLO_1L/sigma_LO_Tree, lw=2, ls="-", c='red')#, label = "1L")
-#plt.plot(m_squark, sigma_NLO_Tree/sigma_LO_Tree, lw=2, ls="--", c='blue')#, label = "1L")
-#plt.plot(m_squark, sigma_NLO_Virt/sigma_LO_Tree, lw=2, ls="--", c='red')#, label = "1L")
-#plt.plot(m_squark, sigma_NLO_Real/sigma_LO_Tree, lw=2, ls="--", c='green')#, label = "1L")
 
 plt.legend(loc='best',prop={'size':22})
 

### 2016-06-21 figures/One_Loop/MRSSM_uu_susu_Kfactors_msq=1000GeV_msg=2000GeV.py

@@ -58,7 +58,7 @@ plt.plot(m_sgluon, sigma_NLO_1L/sigma_LO_Tree, lw=2, ls="-", c='red')
 plt.legend(loc=4,prop={'size':22})
 
 props = dict(boxstyle='round', facecolor='w', alpha=0.5)
-first_window.text(10000, 0.8, r"$m_{\tilde{g}} = 2000$ GeV", fontsize=22,
+first_window.text(10000, 0.8, r"$m_{\tilde{g}} = 2000$ GeV, $m_{\tilde{q}} = 1000$ GeV", fontsize=22,
         verticalalignment='top', bbox=props)
 
 

### 2016-06-22 Renormalization.tex
Counterterm Diagrams, delta ZLgl drops out

@@
 \subsection{Regularization Schemes}\label{sec:RegSchemes}
-\subsubsection*{Dimensional Regularization(DREG)}
+\subsubsection*{Dimensional Regularization (DREG)}
 Dimensional regularization(DREG) is a very common procedure for regularizing infinities which was devised by t'Hooft and Veltman~\cite{'tHooft:1972fi}.
@@
 In fact the field renormalization constants of the gluino are not needed as they drop out when summing up all three counterterm Feynman diagrams.
-This can be seen when writing down the matrix amplitudes for the counterterm Feynman diagrams:
+This can be seen when writing down the matrix amplitudes for the counterterm Feynman diagrams shown in fig.
+\ref{fig:CounterTerm}:
 \begin{align}
-\mathcal{M}^{\mathrm{B}} &= -2g_s^2 \frac{\left\langle v2 |P_R \slashed{k}_3|u1\right\rangle}{t_{\tilde{g}}} T^a_{13} T^a_{24} + 2g_s^2 \frac{\left\langle v2 |P_L \slashed{k}_3|u1\right\rangle}{u_{\tilde{g}}} T^a_{14} T^a_{23}\\
-\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}} &= 2 \mathcal{M}^B  \left( \frac{\delta \hat{g}_s}{\hat{g}_s} \frac{\delta Z_q}{2} + \frac{\delta Z^L_{\tilde{g}}}{2} + \frac{\delta Z_{\tilde{q}}}{2} \right)\\
-\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}} &= \hdots = 
-\mathcal{M}^B \left[ \frac{-(t_{\tilde{g}})\delta Z_{\tilde{g}}^L + 2 \delta m_{\tilde{g}}m_{\tilde{g}}}{t_{\tilde{g}}}\right.\\
-&\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \left. \frac{-(u_{\tilde{g}})\delta Z_{\tilde{g}}^L + 2 \delta m_{\tilde{g}}m_{\tilde{g}}}{u_{\tilde{g}}}\right]
+\mathcal{M}^{\mathrm{B}} &= -2g_s^2 \frac{\left\langle v_2 |P_R \slashed{k}_3|u_1\right\rangle}{t_{\tilde{g}}} T^a_{\delta \beta} T^a_{\gamma \alpha} + 2g_s^2 \frac{\left\langle v_2 |P_L \slashed{k}_3|u_1\right\rangle}{u_{\tilde{g}}} T^a_{\gamma\beta} T^a_{\delta\alpha}\\
+\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}} &= 2 \mathcal{M}^B  \left( \frac{\delta \hat{g}_s}{\hat{g}_s} + \frac{\delta Z_q}{2} + \frac{\delta Z^L_{\tilde{g}}}{2} + \frac{\delta Z_{\tilde{q}}}{2} \right)\\
+\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}} &= 2g_s^2 \left\langle v_2 \left| P_R\ i\frac{\slashed{p}+m_{\tilde{g}}}{t_{\tilde{g}}} \left[  i(\delta Z_{\tilde{g}}^L P_L + \delta Z_{\tilde{g}}^L P_L)\slashed{p}  \right.\right.\right.\nonumber\\
+& \hspace{2cm}\left.\left.\left.\left.
+-i\left( \frac{\delta Z_{\tilde{g}}^L + \delta Z_{\tilde{g}}^R}{2}m_{\tilde{g}} + \delta m_{\tilde{g}} \right) \right]i\frac{\slashed{p}+m_{\tilde{g}}}{t_{\tilde{g}}} P_L \right|u_1\right\rangle\right|_{p = p_1-p_3} + \mathrm{u-channel}\nonumber\\
+&= -\mathcal{M}^B  \delta Z_{\tilde{g}}^L + 2  \frac{ m_{\tilde{g}}}{t_{\tilde{g}}} \left( -2g_s^2 \frac{\left\langle v_2 |P_R \slashed{k}_3|u_1\right\rangle}{t_{\tilde{g}}} T^a_{\delta \beta} T^a_{\gamma \alpha} \right)\delta m_{\tilde{g}}\nonumber\\
+& \hspace{2cm}+ 2 \frac{ m_{\tilde{g}}}{u_{\tilde{g}}} \left( 2g_s^2 \frac{\left\langle v_2 |P_L \slashed{k}_3|u_1\right\rangle}{u_{\tilde{g}}} T^a_{\gamma\beta} T^a_{\delta\alpha} \right)\delta m_{\tilde{g}}.
 \end{align}
+Where $\delta Z^R_{\tilde{g}}$ drops out already in $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ as the octino does neither couple to quarks nor to squarks the renormalization constant for the actual gluino $\delta Z^L_{\tilde{g}}$ drops out when $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ and $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}}$ are added.
+This is also true in a more general case, i.e.
+the renormalization constants of virtual particles do always drop out.
 \begin{figure}[!htbp]
@@
 	\draw[scalar] (4,-0.5)--(5,-0.5);
-	\node at (2.8,0.5) {$u$};
-	\node at (2.8,-0.5) {$u$};
-	\node at (5.2,0.5) {$\tilde{u}_L^\dagger$};
-	\node at (5.2,-0.5) {$\tilde{u}_R^\dagger$};
+	\node at (2.7,0.5) {$u_\alpha$};
+	\node at (2.7,-0.5) {$u_\beta$};
+	\node at (5.4,0.5) {$\tilde{u}_{L\gamma}^\dagger$};
+	\node at (5.4,-0.5) {$\tilde{u}_{R\delta}^\dagger$};
 	\node at (6,0) {+};
@@
 	\draw[scalar] (8,-0.5)--(9,-0.5);
-	\node at (6.8,0.5) {$u$};
-	\node at (6.8,-0.5) {$u$};
-	\node at (9.2,0.5) {$\tilde{u}_L^\dagger$};
-	\node at (9.2,-0.5) {$\tilde{u}_R^\dagger$};
+	\node at (6.7,0.5) {$u_\alpha$};
+	\node at (6.7,-0.5) {$u_\beta$};
+	\node at (9.4,0.5) {$\tilde{u}_{L\gamma}^\dagger$};
+	\node at (9.4,-0.5) {$\tilde{u}_{R\delta}^\dagger$};
 \begin{scope}[shift={(8,0)}]	
@@
 	\draw[scalar] (4,-0.5)--(5,-0.5);
-	\node at (2.8,0.5) {$u$};
-	\node at (2.8,-0.5) {$u$};
-	\node at (5.2,0.5) {$\tilde{u}_L^\dagger$};
-	\node at (5.2,-0.5) {$\tilde{u}_R^\dagger$};
-	\node at (6.9,) {+\ \ u-channel};
+	\node at (2.6,0.5) {$u_\alpha$};
+	\node at (2.6,-0.5) {$u_\beta$};
+	\node at (5.3,0.5) {$\tilde{u}_{L\gamma}^\dagger$};
+	\node at (5.3,-0.5) {$\tilde{u}_{R\delta}^\dagger$};
+	\node at (6.9,0) {+\ \ u-channel};
 \end{scope}
 \end{tikzpicture}
-\caption{1-Loop-Level Counterterm Feynman diagrams for squark production in the MRSSM}
+\caption{1-Loop-level counterterm Feynman diagrams for squark production in the MRSSM. The Greek latters label the particle's color.}\label{fig:CounterTerm}
 \end{center}

### 2016-06-23 Appendix.tex
NLO chapter

@@
 
-\subsection{Constants of the Colour Algebra $SU(N)$}
+\subsection{Constants of the Color Algebra $SU(N)$}\label{sec:coloralgebra}
 [Marina von Steinkirch]\\
@@
 \subsection{Passarino-Veltman Integrals}\label{sec:Passarino}
-The definition of the Passarino-Veltman integrals in this thesis agrees with the one from \texttt{Looptools} \cite{Hahn:1998} convention.
+The definition of the momenta within the Passarino-Veltman integrals in this thesis agrees with the one from \texttt{Looptools} \cite{Hahn:1998} convention.
 The original paper \cite{Passarino:1978jh} uses slightly different conventions.
-A pedagogical introduction to the evaluation of one-loop integrals can be found in \cite{Ellis:2011cr}
+A pedagogical introduction to the evaluation of one-loop integrals can be found in \cite{Ellis:2011cr}.
+$A$, $B$ and $C$ integrals are defined by:
 \begin{align}
@@
 \frac{i}{16\pi^2} B_{0,\mu,\mu\nu}(p^2,m_1^2,m_2^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p)^2-m_2^2]}\\
-\frac{i}{16\pi^2} C_{0,\mu,\mu\nu}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p_1)^2-m_2^2][(l+p_1+p_2)^2-m_3^2]}\nonumber
+\frac{i}{16\pi^2} C_{0,\mu,\mu\nu}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p_1)^2-m_2^2][(l+p_1+p_2)^2-m_3^2]}.\nonumber\label{eq:LoopInt}
 \end{align}
@@
 Infrared and collinear singularities arise from the special case where one or multiple masses tend to zero.
-These poles are either regularized in terms of a small mass cutoff $\Lambda$ or also dimensionally as $\epsilon$-poles.
-In the later case the integral first needs to undergo the limit to zero masses and than being evaluated.\\
+These poles can be regularized with a small mass cutoff $\Lambda$ leading singularities of the form $\ln \Lambda$ or dimensionally which leads to $\epsilon$-poles as in the treatment of UV-divergences.
+In the latter case the integral first needs to undergo the limit to zero masses and than being evaluated.\\
 The following list shows all necessary integrals needed to determine the renormalization constants in \ref{sec:MSRen}.

### 2016-06-23 MSSM.tex
NLO chapter

@@
 \section{The Minimal Supersymmetric Standard Model}
-Even though the Standard Model is a very well working machinery which has partially been tested to an impressive accuracy it is not the ultimate theory of nature.
+Even though the Standard Model is a very well working machinery which has been tested to an impressive accuracy it is not the ultimate theory of nature.
 This is not only because of its incompleteness regarding gravity but also because of its missing incorporation of dark matter.
 This is that astrophysical observations \cite{Adam:2015rua} indicate that only 4.9\% of the universe's mass energy consist of ordinary matter while the majority is represented by 26.8\% of dark matter and 68.3\% of dark energy.
-Another puzzle is the hierarchy problem which questions the large discrepancy between the Higgs boson mass and its quantum correction, see \cite{Martin:1997ns}.
-Finally the gauge groups of the Standard Model cannot be unified to a theoretically appealing single gauge group at some high energy scale for the three gauge couplings do not meet at any renormalization scale \cite{Martin:1997ns}.
-There are many other problems which are not mentioned here.\\
+Another puzzle is the hierarchy problem which questions the large difference between the Higgs boson mass and its quantum correction, see \cite{Martin:1997ns}.
+Finally, the gauge groups of the Standard Model cannot be unified to a theoretically appealing single gauge group at some high energy scale for the three gauge couplings do not meet at any renormalization scale \cite{Martin:1997ns}.
+There are many other problems which are not mentioned here\cite{Bach}.\\
 Supersymmetry provides a possible extension of the Standard Model.
@@
 Coleman and Mandula \cite{Coleman:1967ad} found that for any reasonable quantum field theory space-time and internal symmetries, i.e.
-gauge symmetries "cannot by combined in any but the trivial way"\cite{Pelc:1996vg}.
+gauge symmetries ``cannot by combined in any but the trivial way"\cite{Pelc:1996vg}.
 Ergo the symmetry groups of the Standard Model are the most general ones.\\
 This statement was corrected by the Haag-Lopuszanski-Sohnius theorem \cite{Haag:1974qh} which weakened the condition of the quantum field theory by allowing also for anticommuting symmetry generators.
-This is by introducing the generators $Q_\alpha$ and $Q_{\dot{\alpha}}$ with $\alpha, \dot{\alpha} \in \left\{ 1,2 \right\}$ the Poincare-algebra eq.
-\ref{eq:PoincareAlgebra} can be nontrivially extended to the so called superalgebra (see Appendix \ref{sec:2spinor_notation} for the definition of the $\sigma$-matrices):
+This is, by introducing the generators $Q_\alpha$ and $\overline{Q}^{\dot{\alpha}}$ with $\alpha, \dot{\alpha} \in \left\{ 1,2 \right\}$, the Poincare-algebra eq.
+\eqref{eq:PoincareAlgebra} can be nontrivially extended to the so called superalgebra (see appendix \eqref{sec:2spinor_notation} for the definition of the $\sigma$-matrices):
 \begin{align}
@@
 As $J^{\mu\nu}$ is the generalized angular momentum operator the last line in eq.
-\ref{eq:SUSYalgebra} implies that $Q_\alpha$ is a spin $\frac{1}{2}$ operator.
+\eqref{eq:SUSYalgebra} implies that $Q_\alpha$ is a spin-$\frac{1}{2}$ operator.
 Applying $Q_\alpha$ to a field will change the spin of it by $\frac{1}{2}$.
@@
 The superalgebra in eq.
-\ref{eq:SUSYalgebra} is actually the smallest extension of the Poincare-algebra as it is possible to introduce further anticommuting symmetry generators.
+\eqref{eq:SUSYalgebra} is actually the smallest extension of the Poincare-algebra as it is possible to introduce further anticommuting symmetry generators.
 Their maximal number is fixed to $N = 8$.
-The MSSM deals with only one set of anticommuting symmetry generators and is therefore referred to be a $N = 1$ supersymmetric theory.\\
+Because the MSSM is a minimal extension of the Standard Model, it deals with only one set of anticommuting symmetry generators and is therefore referred to be a $N = 1$ supersymmetric theory.\\
 A representation in the form of differential operators can be given by introducing superspace.
@@
 \begin{align}
-P^\mu &= i\partial^\mu\nonumber\\
-J^{\mu\nu} &= i(x^\mu\partial^\nu - x^\nu\partial^\mu)\nonumber\\
+P^\mu &= i\partial^\mu,\nonumber\\
+J^{\mu\nu} &= i(x^\mu\partial^\nu - x^\nu\partial^\mu),\nonumber\\
 Q_\alpha &= i(\partial_\alpha + i\sigma^\mu_{\alpha\dot{\alpha}}
-\overline{\theta}^{\dot{\alpha}}\partial_\mu)\nonumber\\
+\overline{\theta}^{\dot{\alpha}}\partial_\mu),\nonumber\\
 \overline{Q}_{\dot{\alpha}} &= i(-\overline{\partial}_{\dot{\alpha}} - i \theta^\alpha \sigma^\mu_{\alpha\dot{\alpha}}\partial_\mu).\label{eq:SUSYGen}
@@
 To this end it is practical to work in the language of superspace and superfields.
-Superspace has just been introduced and superfields are functions on superspace.\\
-The superfields\footnote{Superfield are throughout this thesis labeled with a hat.} relevant for the MSSM are the chiral superfield $\hat{\Phi}$, the antichiral superfield $\hat{\overline{\Phi}}$ and the vector superfield $V$.
-Chiral superfields are defined by the restriction $\overline{\mathcal{D}}_{\dot{\alpha}}\hat{\Phi} = 0$, antichiral superfields by $\mathcal{D}_\alpha\hat{\overline{\Phi}} = 0$ (see Appendix \ref{sec:AnticommNumbers} for the definition of chiral covariant derivatives) and vector superfields by the condition of being real $V^\dagger = V$.\\
-All superfields can be decomposed into components. The component decomposition of the above fields read\footnote{For tho vector superfield Wess-Zumino-gauge is applied.}
+Superfields are functions on superspace.\\
+The superfields\footnote{Superfield are throughout this thesis labeled with a hat.} relevant for the MSSM are the chiral superfield $\hat{\Phi}$, the antichiral superfield $\hat{\overline{\Phi}}$ and the vector superfield $\hat{V}$.
+Chiral superfields are defined by the restriction $\overline{\mathcal{D}}_{\dot{\alpha}}\hat{\Phi} = 0$, antichiral superfields by $\mathcal{D}_\alpha\hat{\overline{\Phi}} = 0$ (see appendix \ref{sec:AnticommNumbers} for the definition of chiral covariant derivatives) and vector superfields by the condition of being real $\hat{V}^\dagger = \hat{V}$.\\
+All superfields can be decomposed into component fields on Minkowski space. The component decomposition of the above fields read\footnote{For tho vector superfield Wess-Zumino-gauge is applied.}
 \begin{align}
-\hat{\Phi}(x,\theta,\overline{\theta}) &= A(x) + \sqrt{2}\theta\psi(x) + \theta\theta F(x) - i\theta\sigma^\mu \overline{\theta}\partial_\mu A(x) - \frac{1}{4}\theta\theta\overline{\theta}\overline{\theta}\partial_\mu\partial^\mu A(x) - \frac{i}{\sqrt{2}}\theta\theta\overline{\theta}\overline{\sigma}^\mu \partial_\mu\psi(x)\nonumber\\
-\hat{\overline{\Phi}}(x,\theta,\overline{\theta}) &= A^\dagger(x) + \sqrt{2}\overline{\theta}\overline{\psi}(x) + \overline{\theta}\overline{\theta} F^\dagger(x) + i\theta\sigma^\mu \overline{\theta}\partial_\mu A^\dagger(x) - \frac{1}{4}\theta\theta\overline{\theta}\overline{\theta}\partial_\mu\partial^\mu A^\dagger(x) - \frac{i}{\sqrt{2}}\overline{\theta}\overline{\theta}\theta\sigma^\mu \partial_\mu\overline{\psi}(x)\nonumber\\
+\hat{\Phi}(x,\theta,\overline{\theta}) &= A(x) + \sqrt{2}\theta\psi(x) + \theta\theta F(x) - i\theta\sigma^\mu \overline{\theta}\partial_\mu A(x) - \frac{1}{4}\theta\theta\overline{\theta}\overline{\theta}\partial_\mu\partial^\mu A(x) - \frac{i}{\sqrt{2}}\theta\theta\overline{\theta}\overline{\sigma}^\mu \partial_\mu\psi(x),\nonumber\\
+\hat{\overline{\Phi}}(x,\theta,\overline{\theta}) &= A^\dagger(x) + \sqrt{2}\overline{\theta}\overline{\psi}(x) + \overline{\theta}\overline{\theta} F^\dagger(x) + i\theta\sigma^\mu \overline{\theta}\partial_\mu A^\dagger(x) - \frac{1}{4}\theta\theta\overline{\theta}\overline{\theta}\partial_\mu\partial^\mu A^\dagger(x) - \frac{i}{\sqrt{2}}\overline{\theta}\overline{\theta}\theta\sigma^\mu \partial_\mu\overline{\psi}(x),\nonumber\\
 \hat{V}(x,\theta,\overline{\theta}) &= \theta\sigma^\mu\overline{\theta} v_\mu + i\theta\theta\overline{\theta}\overline{\lambda}(x) -i \overline{\theta}\overline{\theta}\theta\lambda(x) + \frac{1}{2}\theta\theta\overline{\theta}\overline{\theta}D(x),\label{eq:superfielddecomp}
 \end{align}
-where $A(x)$ and $F(x)$ are complex scalar fields, $\psi(x)$ and $\lambda(x)$ are left handed Weyl spinors and $D(x)$ being a real scalar field.\\
+where $A(x)$ and $F(x)$ are complex scalar fields, $\psi(x)$ and $\lambda(x)$ are left-handed Weyl spinors, $D(x)$ is a real scalar field and $v_\mu$ is a vector field.\\
 The superfields transform under a generic gauge transformation as
 \begin{align}
-\hat{\Phi} &\to \mathrm{e}^{-2ig\hat{\Lambda}}\hat{\Phi}\nonumber\\
-\hat{\overline{\Phi}} &\to \hat{\overline{\Phi}}\mathrm{e}^{2ig\hat{\overline{\Lambda}}}\nonumber\\
+\hat{\Phi} &\to \mathrm{e}^{-2ig\hat{\Lambda}}\hat{\Phi},\nonumber\\
+\hat{\overline{\Phi}} &\to \hat{\overline{\Phi}}\mathrm{e}^{2ig\hat{\overline{\Lambda}}},\nonumber\\
 \mathrm{e}^{2g\hat{V}} &\to \mathrm{e}^{-2ig\hat{\overline{\Lambda}}}\mathrm{e}^{2g\hat{V}} \mathrm{e}^{2ig\hat{\Lambda}},
@@
 where $\hat{\Lambda} = \hat{\Lambda}^aT^a$ and $\hat{V} = \hat{V}^aT^a$.
-$\hat{\Lambda}^a$ is an arbitrary chiral superfield and the $T^a$ are the generetors of the gauge group in question.
-g is the gauge coupling constant of the gauge group.\\
+$\hat{\Lambda}^a$ is an arbitrary chiral superfield, the $T^a$ are the generetors of the gauge group in question and $g$ is the gauge coupling constant of the gauge group.\\
 One can therefore construct the important gauge invariant term $\int\mathrm{d}^4\theta\ \hat{\overline{\Phi}}\mathrm{e}^{2g\hat{V}}\hat{\Phi}$.
@@
 \begin{align}
-\int\mathrm{d}^2\theta\ \hat{\Phi}_1 &= F_1\nonumber\\
-\int\mathrm{d}^2\theta\ \hat{\Phi}_1\hat{\Phi}_2 &= A_1F_2 + F_1A_2-\psi_1\psi_2\nonumber\\
+\int\mathrm{d}^2\theta\ \hat{\Phi}_1 &= F_1,\nonumber\\
+\int\mathrm{d}^2\theta\ \hat{\Phi}_1\hat{\Phi}_2 &= A_1F_2 + F_1A_2-\psi_1\psi_2,\nonumber\\
 \int\mathrm{d}^2\theta\ \hat{\Phi}_1\hat{\Phi}_2\hat{\Phi}_3 &= F_1A_2A_3 + A_1F_2A_3 + A_1A_2F_3 - A_1\psi_2\psi_3 - \psi_1A_2\psi_3 - \psi_1\psi_2A_3.\label{eq:L_superpot}
@@
 &=\int\mathrm{d}^4\theta\hat{\overline{\Phi}}\mathrm{e}^{2g\hat{V}}\hat{\Phi} + \left(\int\mathrm{d}^2\theta \frac{1}{16g^2 }\hat{W}^{\alpha a} \hat{W}^a_\alpha + h.c.
-\right) +\int\mathrm{d}^2\theta\ W(\hat{\Phi})
+\right) + \left(\int\mathrm{d}^2\theta\ W(\hat{\Phi}) + h.c.
+\right)
 \end{align}
-Observing the component decomposition eq.\ref{eq:L_matter}, \ref{eq:L_gauge} and \ref{eq:L_superpot} of the 3 parts of this Lagrangian one observes that the $F$ and $D$ fields have no kinetic term and are therefore auxiliary fields which can be eliminated by their equation of motion $\frac{\partial \mathcal{L}}{\partial\phi} = \partial_\mu\frac{\partial \mathcal{L}}{\partial(\partial_\mu \phi)}$ with $\phi \in \left\{ F, D \right\}$.
+Observing the component decomposition eq.
+\eqref{eq:L_matter}, \eqref{eq:L_gauge} and \eqref{eq:L_superpot} of the three parts of this Lagrangian one observes that the $F$ and $D$ fields have no kinetic term and are therefore auxiliary fields which can be eliminated by their equation of motion $\frac{\partial \mathcal{L}}{\partial\phi} = \partial_\mu\frac{\partial \mathcal{L}}{\partial(\partial_\mu \phi)}$ with $\phi \in \left\{ F, D \right\}$.
 Doing this one obtains
 \begin{align}
-\mathcal{L}_D &= \frac{1}{2} D^aD^a + g A^\dagger T^aD^a A \hspace{1cm} \Rightarrow \hspace{1cm} D^a = - A^\dagger T^a A \nonumber\\
+\mathcal{L}_D &= \frac{1}{2} D^aD^a + g A^\dagger T^aD^a A \hspace{1cm} \Rightarrow \hspace{1cm} D^a = - A^\dagger T^a A, \nonumber\\
 \mathcal{L}_D &= -\frac{1}{2}\left( A^\dagger T^a A \right)^2.
@@
 \subsection{The Minimal Supersymmetric Standard Model}
-After having introduced a generic supersymmetric model a possible realization of supersymmetry in nature - the Minimal Supersymmetric Standardmodel (MSSM) - is discussed in this subsection. 
+After having introduced components of a generic supersymmetric model a possible realization of supersymmetry in nature - the Minimal Supersymmetric Standardmodel (MSSM) - is discussed in this section.
 The field content of the MSSM is summarized in table \ref{tab:MSSMfieldcontent}.
@@
 The superpartners of fermions have Spin 0 and are referred to as sfermions.
-The name of each sfermion is given by the name of its Standard Model partner with an additional "s" in front of it, e.g.
+The name of each sfermion is given by the name of its Standard Model partner with an additional ``s-" in front of it, e.g.
 selectron or up-squark.
-The superpartners of bosons have spin $\frac{1}{2}$ and get an additional "ino" at the end of their name, e.g.
-Higgsino as the superpartner of the Higgs or Zino as superpartner of the $Z$-boson.\\
-Apart from this doubling up of the field content of the Standard Model there is one modification within the Higgs sector, i.e.
+The superpartners of bosons have spin $\frac{1}{2}$ and get an additional ``-ino" at the end of their name, e.g.
+higgsino as the superpartner of the Higgs or bino as superpartner of the $B$-boson.\\
+Apart from this doubling of the field content of the Standard Model, there is one modification within the Higgs sector, i.e.
 there are two instead of one Higgs superfield.
 These are necessary to avoid an anomaly in the electroweak gauge symmetry and to give masses to both up- and down-type quarks \cite[page 8]{Martin:1997ns}.\\
-Note that the "chirality" of sfermions is understood to be the chirality of their superpartners. Of course scalar particles have no handedness.
+Note that the ``chirality" of sfermions is understood to be the chirality of their superpartners. Of course scalar particles have no handedness.
 \begin{table}
 \begin{center}
-\begin{tabular}{c|c|c}
-Superfield & Components & $SU_\mathrm{C}(3)$ $\times$ $SU_\mathrm{L}(2)$ $\times$ $U_\mathrm{Y}(1)$\\
-\hline
+\begin{tabular}{c?c?c}
+Superfield & Components & $SU(3)_C$ $\times$ $SU(2)_L$ $\times$ $U(1)_Y$\\
+\hlinewd{2pt}
 $\hat{\Phi}$ & $A$, $\psi$ & \\
@@
 \end{tabular}
-\caption{The table shows the field content of the MSSM in terms of the superfields and their component decomposition.
+\caption{The table shows the field content of the MSSM in terms of the superfields and their components.
 The first two lines show the decomposition of the generic superfields (cf.
-subsection \ref{eq:superfielddecomp}).\newline
-The third column shows the representation (for $SU_\mathrm{C}(3)$ and $SU_\mathrm{L}(2)$) in which the fields transform and the charges of the fields for $U_\mathrm{Y}(1)$.}\label{tab:MSSMfieldcontent}
+subsection \eqref{eq:superfielddecomp}).\newline
+The third column shows the representation (for $SU(3)_C$ and $SU(2)_L$) in which the fields transform and in which the generator in the covariant derivative needs to be inserted as well as the charges of the fields for $U(1)_Y$.
+For $SU(3)_C$ the ``8" refers to the adjoint representation (see appendix \ref{sec:coloralgebra}), the ``3" to the fundamental and the ``3$^\ast$" to the antifundamental representation $T^a_{antifund} = -\frac{\lambda^a}{2}$.
+For $SU(2)_L$ ``3" refers to the adjoint representation and ``2" to the fundamental representation.
+For both $SU(2)_L$ and $SU(3)_C$ a ``1" indicates the the trivial representation.}\label{tab:MSSMfieldcontent}
 \end{center}
@@
 \end{align}
-Apart from the kinetic and minimal coupling terms in the first four lines of \ref{eq:L_MSSM} there is a superpotential $W_{\mathrm{MSSM}}$:
+Apart from the kinetic and minimal coupling terms in the first four lines of eq.
+\eqref{eq:L_MSSM} and the softly breaking part of the Lagrangian in the last line of eq.
+\eqref{eq:L_MSSM} which will be discussed in \ref{sec:SUSYBreaking}, there is a superpotential $W_{\mathrm{MSSM}}$:
 \begin{align}
-W_\mathrm{{MSSM}} &= y_d \hat{H}_d \hat{Q} \hat{D} + y_u \hat{H}_u \hat{Q} \hat U + y_e \hat{H}_d \hat{L} \hat{E} - \mu \hat{H}_d \hat{H}_u\label{eq:W_MSSM}
+W_\mathrm{{MSSM}} &= y_d \hat{H}_d \hat{Q} \hat{D} + y_u \hat{H}_u \hat{Q} \hat U + y_e \hat{H}_d \hat{L} \hat{E} - \mu \hat{H}_d \hat{H}_u,\label{eq:W_MSSM}
 \end{align}
-After eliminating auxiliary fields a Higgs potential is generated.
+which will in regard of its form be justified in section \ref{sec:RParity}.
+After eliminating auxiliary fields the Higgs potential is generated.
 In contrast to the Standard Model the quadrilinear term in the Higgs potential is given in terms of the gauge couplings and therefore no independent parameter.
@@
 \end{align}
-As in the Standard Model this spontaneous symmetry breaking leads to Yukawa-terms (first three terms of eq.
-\ref{eq:W_MSSM}) which give masses to the fermions\footnote{Note the sum convention of $SU_{\mathrm{L}}(2)$ doublets: $\hat{H}_u \hat{Q} =  (\hat{H}_u)_{\alpha}\hat{Q}_\beta \epsilon^{\alpha\beta}$ to ensure gauge invariance.}.
-Apart from that there are also other terms like quark-squark-higgsino interactions.
+As in the Standard Model this spontaneous symmetry breaking and the presence of Yukawa-terms (first three terms of eq.
+\eqref{eq:W_MSSM}) lead to masses of the fermions.\footnote{Note the sum convention of $SU_{\mathrm{L}}(2)$ doublets: $\hat{H}_u \hat{Q} =  (\hat{H}_u)_{\alpha}\hat{Q}_\beta \epsilon^{\alpha\beta}$ to ensure gauge invariance (see appendix \ref{sec:2spinor_notation} for the definition of $\epsilon^{\alpha\beta}$).} Apart from that there are also other terms like quark-squark-higgsino interactions.
 In addition there is the $\mu$-term which is responsible for Higgsino and Higgs masses.\\
+
+\subsubsection{Supersymmetry Breaking and Mass Eigenstates}\ref{sec:SUSYBreaking}
 In order to explain why supersymmetric particles have not been found so far supersymmetry has to be broken.
@@
 The last line in eq.
-\ref{eq:L_soft} resembles the superpotential in eq.
-\ref{eq:W_MSSM}.
+\eqref{eq:L_soft} resembles the superpotential in eq.
+\eqref{eq:W_MSSM}.
 In fact the only two differences are that the superfields are replaced by their scalar components and that additional parameters with mass dimension one have been added.
 $A_d$, $A_u$, $A_e$ are $3 \times 3$ matrices in family space.\\
-Many supersymmetric particles have no definite mass but mix to particles with definite mass.
-This is true for neutral higgsinos and gauginos which mix to neutralinos and charged higgsinos and gauginos which mix to charginos.
-However, for this thesis only the mass matrix for electrically charged sfermions is given because this will change significantely when introducing R-symmetry in the next section.
+There are fields in the MSSM which are no eigenstate of the mass operator $P^\mu P_\mu$ but have a mass matrix which is non-diagonal.
+This is true for neutral higgsinos and gauginos which mix to neutralinos and charged higgsinos and gauginos which mix to charginos to yield physical particles with definite mass.
+However, for this thesis only the mass matrix for electrically charged sfermions is given because this will change significantly when introducing $R$-symmetry in the next section.
 The Lagrangian describing these masses reads
@@
 \end{align}
-with $\cot \beta$ for up-type squarks and $\tan \beta$ for down-type sfermions
+with $\cot \beta$ for up-type squarks and $\tan \beta$ for down-type sfermions and $A_f \in \left\{ A_d, A_u, A_e \right\}$.
 
-\subsection{R-Parity}
+\subsubsection{$R$-Parity}\label{sec:RParity}
 The MSSM does not include any terms which violate baryon (B) or lepton number (L)\footnote{The chiral superfield $\hat{Q}$ carries baryon number $\frac{1}{3}$, whereas $\mathrm{B} = -\frac{1}{3}$ for $\hat{D}$, $\hat{U}$ and $\mathrm{B} = 0$ for all other superfields.
@@
 Forbidding these terms by postulating a conservation of B and L might not be the best solution since both B and L are known to be violated in nature by non-perturbative effects\cite{'tHooft:1976up}.\\
-A possible way out is the postulation of the conservation of R-parity
+A possible way out is the postulation of the conservation of $R$-parity
 \begin{align}
-P_\mathrm{R} = (-1)^{3(\mathrm{B}-\mathrm{L})+2s}
+P_R = (-1)^{3(\mathrm{B}-\mathrm{L})+2s}
 \end{align}
 where $s$ is the spin of the particle on which the R-parity operator is applied to.
-R-parity is a multiplicative quantum number which is constructed to be +1 for each Standard Model particle and -1 for each supersymmetric partner.
-Apart from the the prohibition of the terms in eq.
-\ref{eq:BLviolation} this has important consequances:
+$R$-parity is a multiplicative quantum number which is constructed to be +1 for each Standard Model particle and -1 for each supersymmetric partner.
+Apart from the prohibition of the terms in eq.
+\eqref{eq:BLviolation} this has important consequences:
 \begin{itemize}
-\item There has to be a lightest supersymmetric particle (LSP) which is absolutely stable. This could be a candidate for dark matter.
+\item There has to be a lightest supersymmetric particle (LSP) which is absolutely stable. This is a candidate for dark matter.
 \item At colliders like the LHC there must always be an even number of supersymmetric particles be produced, if at all.
 \end{itemize}
-The superpotential of the MSSM (see, eq. \ref{eq:W_MSSM}) is chosen in such a way that it is the only renormalizable and gauge invariant potential which respects R-parity.
+The superpotential of the MSSM (see, eq. \eqref{eq:W_MSSM}) is chosen in such a way that it is the only renormalizable and gauge invariant potential which respects R-parity.

### 2016-06-23 NLO.tex
Latex does not compile any more
up to RSymmetry
NLO chapter

@@
 
+\subsection{The Squark Production Cross Section at Next-to-Leading Order}
+The squark production cross section at next-to-leading order is composed out of three contributions. These are the Born or tree-level cross section, the virtual correction and the real correction. 
+\begin{align}
+\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}}\label{eq:BVR}
+\end{align}
+All three contributions have to be calculated with next-to-leading parton density functions.\\
+It has been checked that for multiple different and quite distinct choices of the parameters $m_{\tilde{q}}$ and $m_{\tilde{g}}$ the double as well as the single poles of the virtual and real correction cancel up to machine precision.
+As the real corrections have been calculated analytically it is possible to quote the double pole.
+With
+\begin{align}
+\sigma^{\mathrm{R}}_{\mathrm{double\ pole}} = -\sigma^{\mathrm{V}}_{\mathrm{double\ pole}} = C(F)\frac{\alpha_s}{\pi}\sigma^{\mathrm{B}} \frac{1}{\epsilon^2}
+\end{align}
+it has a very succinct form. \\
+The setup of the calculation is summarized in fig.
+\ref{fig:CalcSetup}.
+Both the virtual and the Born matrix amplitude have been generated with the \texttt{Mathematica} package \texttt{FeynArts}.
+To this end a modelfile generated by the \texttt{Mathematica} package \texttt{SARAH} has been adjusted by hand to include counterterm Feynman rules and the definition of those counterterms.
+The matrix amplitudes have been processed further to the absolute squared matrix amplitudes by the \texttt{Mathematica} package \texttt{FormCalc} which have then been converted to \texttt{C++} and stored in an output file.\\
+This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of the absolute squared matrix amplitudes numerically by using the package \texttt{LoopTools} \cite{Hahn:1998}.
+Finally the phase space integration is performed by the integration routine "Cuhre" which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}.\\
+Comment on how real corrections are processed.\\
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}
+	\node [block4] at (-1,0) (Mathematica) {Mathematica notebook};
+	\node [block1a] at (-1,-3) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{B}|^2}$};	
+	\node [block1a] at (-1,-1.5) (notebookV) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{1L}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{V}|^2}$};
+	\node [block5a] at (7.5,0) (C++) {\texttt{C++} code};
+	\node [block5b] at (3.7,-3.5) (Born) {\underline{Born contribution} \newline \texttt{CUBA} $\to$ num. integration over $t, x_1, x_2$ to $\sigma^{\mathrm{B}}$};
+	\node [block5b] at (7.5,-2.7) (Virt) {\underline{Virtual correction}\newline \texttt{LoopTools} $\to$ computation \newline of $ \sum |\mathcal{M}^{\mathrm{V}|^2}$ \newline \texttt{CUBA} $\to$ num.
+integration over $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$};
+	\node [block5c] at (11.5,-3.3) (Real) {\underline{Real correction}\newline \texttt{MADGRAPH} $\to$ $\mathcal{M}^{\mathrm{R}}$, phase space slicing\newline \texttt{CUBA} $\to$ num.
+integration to $\sigma^{\mathrm{R}}$};
+	\path [line, line width = 1] (1.2,-3) -- (1.9,-3);
+	\path [line, line width = 1] (1.2,-1.5) -- (5.7,-1.5);
+	\node [block6a] at (7.5,-6.5) (Sigma) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}}$};
+	\path [line, line width = 1] (Born) -- (Sigma);
+	\path [line, line width = 1] (Virt) -- (Sigma);
+	\path [line, line width = 1] (Real) -- (Sigma);
+\end{tikzpicture}
+\caption{This scheme illustrates the setup of the computation of the next-to-leading order cross section.
+The absolute squared matrix amplitudes of the Born or tree-level contribution and the virtual correction are generated by \texttt{Mathematica} packages and imported into a \texttt{C++} code.
+Loop integrals are evaluated numerically using \texttt{Looptools}.
+For all three contributions the \texttt{CUBA}-library was used for the phase space and $x_1$ and $x_2$ integration to arrive at the cross sections $\sigma^{\mathrm{B}}$, $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{V}}$.}\label{fig:CalcSetup}
+\end{center}
+\end{figure}
+
+\subsubsection{Remark on Prefactors in the Calculation}
+For the discussion of results it will not been distinguished between virtual and real corrections.
+This is because they have not been separated strictly in the calculation: As already discussed both $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{R}}$ are divergent, i.e.
+there are poles of the form $\frac{1}{\epsilon}$ and $\frac{1}{\epsilon^2}$.
+But these pole cancel completely.
+On the other hand there are also prefactors from the phase space integral and the loop integral, with can be expanded in a power series in $\epsilon$.
+In short, the virtual and real correction to the cross section can be expressed with some coefficients $A - E$, which are functions of the parameters $m_{\tilde{g}}$ and $m_{\tilde{q}}$, in the following way
+\begin{align}
+\sigma^{\mathrm{V}} &= \left( 1 + (A^{\mathrm{V}} + P_1)\epsilon + (B^{\mathrm{V}} + P_2)\epsilon^2 + \mathcal{O}(\epsilon^3) \right)\left( C^{\mathrm{V}} - \frac{D}{\epsilon} - \frac{E}{\epsilon^2} \right),\\
+\sigma^{\mathrm{R}} &= \left( 1 + (A^{\mathrm{R}} + P_1)\epsilon + (B^{\mathrm{R}} + P_2)\epsilon^2 + \mathcal{O}(\epsilon^3) \right)\left( C^{\mathrm{R}} + \frac{D}{\epsilon} + \frac{E}{\epsilon^2} \right).\label{eq:prefactoredecomp}
+\end{align}
+Here, the coefficients $A$, $B$ and $C$ are in general distinct in the virtual and real part, but $D$ and $E$ are the same as the poles of both contributions cancel exactly.\\
+Now some of the prefactors, namely $P_1$ and $P_2$, are the same in both contributions.
+Just keeping them like in eq.
+\eqref{eq:prefactoredecomp} would slow the computation of the real part down by a factor 5 because this part of the calculation is done analytically.
+Therefore a speed-up has been achieved by discarding the common prefactors at the cost of loosing track about the origin of the next-to-leading order correction.\\
+A common prefactor comes from the two-body phase space integral in eq. \eqref{eq:diffsigma}
+\begin{align}
+\frac{(4\pi)^\epsilon}{\Gamma(1-\epsilon)}\left( \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} \right)^{-\epsilon} = 1 &+ \epsilon\left( \ln 4\pi -\gamma_E - \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} \right) 
++ \epsilon^2\left( \frac{1}{2}\left( \ln 4\pi - \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} \right)^2 \right.\nonumber\\
+&+ \left.\frac{\gamma_E^2}{2} - \frac{\pi^2}{12} - \gamma_E\left( \ln 4\pi - \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} \right) \right) + \mathcal{O}(\epsilon^3).\label{eq:PhasePrefactor}
+\end{align}
+In addition the prefactor of a loop integral defined in \texttt{LoopTools} differs from the one usually, and therefore also here, used.
+The \texttt{LoopTools} definition\cite{LoopToolsManual} of a loop integral is
+\begin{align}
+T^N_{\mu_1\hdots\mu_P} = \frac{\mu^{4-D}}{i\pi^{\frac{D}{2}}r_\Gamma}\int\mathrm{d}^Dq\frac{q_{\mu_1} \hdots q_{\mu_P}}{[q^2-m_1^2] [(q+p_1)^2-m_2^2] \hdots [(q+p_1+ \hdots +p_{N-1})^2-m_N^2]}\label{eq:LoopToolsInt}
+\end{align}
+where $T^1$ is an $A$-integral, $T^2$ is an $B$-integral, etc.
+and $r_\Gamma = \frac{\Gamma(1-\epsilon)^2\Gamma(1+\epsilon)}{\Gamma(1-2\epsilon)}$, where $\Gamma(z)$ is the Gamma function.
+Comparing the prefactors of eq.
+\eqref{eq:LoopToolsInt} and eq.
+\eqref{eq:LoopInt} one finds that one has to multiply the \texttt{LoopTools} output by
+\begin{align}
+r_\Gamma (4\pi)^\epsilon = 1 + \epsilon(\ln 4\pi -\gamma_E) + \epsilon^2\left( \frac{\gamma_E^2}{2} - \frac{\pi^2}{12} + \frac{\ln^2 4\pi}{2} - \gamma_E\ln 4\pi \right) + \mathcal{O}(\epsilon^3)\label{eq:LoopPrefactor}
+\end{align}
+in order to have the same prefactors as in eq.
+\eqref{eq:LoopInt}.
+The right hand side of eq.
+\eqref{eq:PhasePrefactor} and eq.
+\eqref{eq:LoopPrefactor} are the prefactors discarded in the computation.
+Instead the prefactor ???
+has been included in the virtual correction.
+
+\subsubsection{$K$-factors for Squark Production in the MRSSM}
+A common way to describe next-to-leading order corrections is stating the $K$-factor, which is defined to be the ratio of the complete next-to-leading order cross section $\sigma^{\mathrm{NLO}}$, see eq.
+\eqref{eq:BVR} and the leading order cross section $\sigma^{\mathrm{LO}}$:
+\begin{align}
+K(X \to Y) = \frac{\sigma^{\mathrm{NLO}}(X \to Y)}{\sigma^{\mathrm{LO}}(X \to Y)}.
+\end{align}
+The process in question is described by $X \to Y$.
+Figure \ref{fig:1LXsection_fixed_m} shows the $K$-factor for the production of up-squarks in the MRSSM for varying masses of both the squark ($m_{\tilde{g}} = \unit[2000]{GeV}$) and the gluino $m_{\tilde{q}} = \unit[1000]{GeV}$.
+The mass of the pseudoscalar has been fixed to $m_{\sigma} = \unit[5000]{GeV}$ in both plots.
+It can be seen that the  $K$-factor increases with increasing squark mass and decreases with increasing gluino mass.
+Note that the sum of virtual and real corrections gets negative for very light squarks.
+But this region of parameter space is already excluded phenomenologically.
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msg=2000GeV.png}
+\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV.png}
+\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$ on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).}\label{fig:1LXsection_fixed_m}
+\end{center}
+\end{figure}
+Calculate uncertainties for multiple points(pdf, scale, integration)
+
 \subsection{The Cross Section in the Limit of Large Sgluon Masses}
@@
 \begin{align}
-\lim_{m_{\sigma^0}\to\infty} \sigma(qq \to \tilde{q}\tilde{q}) \sim \ln \frac{m_{\sigma^0}^2}{\mu^2}
+\lim_{m_{\sigma}\to\infty} \sigma(qq \to \tilde{q}\tilde{q}) \sim \ln \frac{m_{\sigma}^2}{\mu^2}
 \end{align}
@@
 In this case the decoupling theorem \cite{Appelquist:1974tg} does no longer hold.\\
-Refer to super oblique correction and quantify difference of $g$ and $\hat{g}$ from eq 4 in \cite{Cheng:1997sq}\\
-append plot
+It is even possible to predict the  logarithmic scaling of $\sigma(qq \to \tilde{q}\tilde{q})$ quantitatively.
+The coefficient of the logarithm is proportional to the difference of the one-loop $\beta$ function coefficients of $g_s$ and $\hat{g}_s$ in the effective theory with the heavy particle integrated out, see eq.
+(4) in \cite{Cheng:1997sq}.
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV_msg=2000GeV.png}
+\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$ on the mass of the pseudoscalar sgluon.
+For $m_{\sigma} \approx \unit[10^5]{GeV}$ onwards want find a logarithmic scaling as predicted by \cite{Cheng:1997sq}.}
+\end{center}
+\end{figure}

### 2016-06-23 RSymmetry.tex
Feynman Rules
NLO chapter

@@
-\section{R-Symmetry}
-R-symmetry is an additional continuous symmetry which extends  supersymmetry in a non-trivial way.
+\section{$R$-Symmetry}
+$R$-symmetry is an additional continuous symmetry which extends  supersymmetry in a non-trivial way.
 This is actually covered in the Haag-Lopuszanski-Sohnius theorem \cite{Haag:1974qh} but often concealed.\\
-This section introduces R-symmetry and discusses briefly a minimal viable extension of the MSSM including R-symmetry, the MRSSM.
+This section introduces $R$-symmetry and discusses briefly a minimal viable extension of the MSSM including $R$-symmetry, the MRSSM.
 Thereby some general features of the model are mentioned before the focus is laid on the strongly interacting sector which is the central topic of the thesis.
 
-\subsection{R-Symmetry Transformation}
-R-symmetry is a global $U(1)$ symmetry.
-It must not be confused with R-parity which is a discrete $\mathbb{Z}_2$ symmetry.
+\subsection{$R$-Symmetry Transformation}
+For a $N=1$ supersymmetric theory, $R$-symmetry is a global $U(1)$ symmetry.
+It must not be confused with $R$-parity which is a discrete $\mathbb{Z}_2$ symmetry.
 A continuous global symmetry implies according to Noether's theorem a conserved charge.
-In the case of R-symmetry it is called R-charge and one therefore refers to R-symmetry as $U_R(1)$.\\
+In the case of $R$-symmetry it is called $R$-charge and one therefore refers to $R$-symmetry as $U_R(1)$.\\
 The defining property of $U_R(1)$ is that the anticommuting coordinates $\theta^\alpha$ and $\overline{\theta}^{\dot{\alpha}}$ transform like
 \begin{align}
-&\theta \to \mathrm{e}^{i\alpha}\theta && \overline{\theta} \to \mathrm{e}^{-i\alpha}\overline{\theta},
+&\theta \to \mathrm{e}^{i\tau}\theta, && \overline{\theta} \to \mathrm{e}^{-i\tau}\overline{\theta},
 \end{align}
-where $\alpha$ parametrizes the transformation. This in turn implies that the supersymmetry generators (see eq. \ref{{eq:SUSYGen}}) transform like
+where $\tau$ parametrizes the transformation. This in turn implies that the supersymmetry generators (see eq. \ref{{eq:SUSYGen}}) transform like
 \begin{align}
-& Q \to \mathrm{e}^{-i\alpha} Q && \overline{Q} \to \mathrm{e}^{i\alpha}\overline{Q}
+& Q \to \mathrm{e}^{-i\tau} Q && \overline{Q} \to \mathrm{e}^{i\tau}\overline{Q}
 \end{align}
@@
 \begin{align}
-& \hat{\Phi}(x,\theta,\overline{\theta}) \to \mathrm{e}^{ir_{\hat{\Phi}}\alpha}\ \hat{\Phi}(x,\mathrm{e}^{i\alpha}\theta,\mathrm{e}^{-i\alpha}\overline{\theta})\nonumber\\
-&\hat{V}(x,\theta,\overline{\theta}) \to  \hat{V}(x,\mathrm{e}^{i\alpha}\theta,\mathrm{e}^{-i\alpha}\overline{\theta}),
+& \hat{\Phi}(x,\theta,\overline{\theta}) \to \mathrm{e}^{ir_{\hat{\Phi}}\tau}\ \hat{\Phi}(x,\mathrm{e}^{i\tau}\theta,\mathrm{e}^{-i\tau}\overline{\theta}),\nonumber\\
+&\hat{V}(x,\theta,\overline{\theta}) \to  \hat{V}(x,\mathrm{e}^{i\tau}\theta,\mathrm{e}^{-i\tau}\overline{\theta}),
 \end{align}
 i.e.
-the chiral superfields transform with arbitrary R-charge where the R-charge of vector superfield is restricted to be zero by the condition that they are real.
+the chiral superfields transform with arbitrary $R$-charge where the $R$-charge of vector superfield is restricted to be zero by the condition that they are real.
 If one inserts the component decomposition eq.
-\ref{eq:superfielddecomp} of the superfields one can read off the R-charges of the component fields.
+\eqref{eq:superfielddecomp} of the superfields one can read off the $R$-charges of the component fields.
 \begin{table}
 \begin{center}
-\begin{tabular}{c|c||c|c||c|c}
-\multicolumn{2}{c||}{superfield} & \multicolumn{2}{c||}{boson} & \multicolumn{2}{c}{fermion} \\
-\hhline{=|=#=|=#=|=}
+\begin{tabular}{c|c?c|c?c|c}
+\multicolumn{2}{c?}{Superfield} & \multicolumn{2}{c?}{Boson} & \multicolumn{2}{c}{Fermion} \\
+\hlinewd{2pt}
 $\hat{\Phi}$ & $r_{\hat{\Phi}}$ & $A$ & $r_{\hat{\Phi}}$ & $\psi$ & $r_{\hat{\Phi}}-1$\\
@@
 
+%\begin{table}
+%\begin{center}
+%\begin{tabular}{c|c||c|c||c|c}
+%\multicolumn{2}{c||}{superfield} & \multicolumn{2}{c||}{boson} & \multicolumn{2}{c}{fermion} \\
+%\hhline{=|=#=|=#=|=}
+%$\hat{\Phi}$ & $r_{\hat{\Phi}}$ & $A$ & $r_{\hat{\Phi}}$ & $\psi$ & $r_{\hat{\Phi}}-1$\\
+%$\hat{V}$ & 0 & $v^\mu$ & 0 & $\lambda$ & $+1$
+%\end{tabular}
+%\caption{This table shows the R-charges of a generic chiral and vector superfield.}
+%\end{center}
+%\end{table}
+
 \subsection{The Minimal R-Symmetric Supersymmetric Standard Model}
@@
 In this model the R-charges are chosen in such a way, that every Standard Model particle has R-charge zero.
-Following this one obtains the R-charges of all particles which are summed up in table \ref{tab:R_charges_MRSSM}.
+Following this one obtains the R-charges of all particles which are summed up in table \ref{tab:R_charges_MRSSM}\cite{Diessner:2015bna}.
 \begin{table}[H]
 \begin{center}
-\begin{tabular}{c||c|c||c|c||c|c}
-Field & \multicolumn{2}{c||}{Superfield} & \multicolumn{2}{c||}{Boson} & \multicolumn{2}{c}{Fermion} \\
-\hhline{=#=|=#=|=#=|=}
-Gauge Vector & $\hat{V}_s^a$, $\hat{V}_w^a$, $\hat{V}_Y$ & 0 & $G^a_\mu$, $W^a_\mu$, $B_\mu$ & 0 & $\lambda_s^a$, $\lambda_w^a$, $\lambda_Y$ &+1\\
-Matter & $\hat{L}$, $\hat{E}$ & 0 & $\tilde{l}_l$, $\tilde{e}^\dagger_R$ & +1 & $l_L$, $e_R$ & 0\\
- & $\hat{Q}$, $\hat{D}$, $\hat{U}$ & +1 & $\tilde{q}_L$, $\tilde{d}^\dagger_R$, $\tilde{u}^\dagger_R$ & +1 & $q_L$, $d_R$, $u_R$ & 0\\
-$H$-Higgs & $\hat{H}_{d,u}$ & 0 & $H_{d,u}$ & 0 & $\tilde{H}_{d,u}$ & -1\\
+\begin{tabular}{c?c|c?c|c?c|c}
+Field & \multicolumn{2}{c?}{Superfield} & \multicolumn{2}{c?}{Boson} & \multicolumn{2}{c}{Fermion} \\
+\hlinewd{2pt}
+gauge Vector & $\hat{V}_s^a$, $\hat{V}_w^a$, $\hat{V}_Y$ & 0 & $G^a_\mu$, $W^a_\mu$, $B_\mu$ & 0 & $\lambda_s^a$, $\lambda_w^a$, $\lambda_Y$ & $+1$\\
+matter & $\hat{L}$, $\hat{E}$ & $+1$ & $\tilde{l}_l$, $\tilde{e}^\dagger_R$ & $+1$ & $l_L$, $e_R$ & 0\\
+ & $\hat{Q}$, $\hat{D}$, $\hat{U}$ & $+1$ & $\tilde{q}_L$, $\tilde{d}^\dagger_R$, $\tilde{u}^\dagger_R$ & $+1$ & $q_L$, $d_R$, $u_R$ & 0\\
+$H$-Higgs & $\hat{H}_{d,u}$ & 0 & $H_{d,u}$ & 0 & $\tilde{H}_{d,u}$ & $-1$\\
 \hline
-$R$-Higgs & $\hat{R}_{d,u}$ & +2 & $R_{d,u}$ & +2 & $\tilde{R}_{d,u}$ & +1\\
-Adjoint Chiral & $\hat{O}$, $\hat{T}$, $\hat{S}$ & 0 & $\sigma^a$, $\omega^a$, $\rho$ & 0 & $\tilde{\chi}_s^a$, $\tilde{\chi}_w^a$, $\tilde{\chi}_Y$ & -1
+$R$-Higgs & $\hat{R}_{d,u}$ & $+2$ & $R_{d,u}$ & $+2$ & $\tilde{R}_{d,u}$ & $+1$\\
+adjoint chiral & $\hat{O}$, $\hat{T}$, $\hat{S}$ & 0 & $\sigma^a$, $\omega^a$, $\rho$ & 0 & $\chi_s^a$, $\chi_w^a$, $\chi_Y$ & $-1$
 \end{tabular}
-\caption{This table lists the R-charges of all superfields and their components in the MRSSM.
+\caption{This table lists the $R$-charges of all superfields and their components in the MRSSM.
 The fields of the $R$-Higgs and the adjoint chiral superfields are not present in the MSSM}\label{tab:R_charges_MRSSM}
@@
 \end{table}
+
+%\begin{table}[H]
+%\begin{center}
+%\begin{tabular}{c||c|c||c|c||c|c}
+%Field & \multicolumn{2}{c||}{Superfield} & \multicolumn{2}{c||}{Boson} & \multicolumn{2}{c}{Fermion} \\
+%\hhline{=#=|=#=|=#=|=}
+%Gauge Vector & $\hat{V}_s^a$, $\hat{V}_w^a$, $\hat{V}_Y$ & 0 & $G^a_\mu$, $W^a_\mu$, $B_\mu$ & 0 & $\lambda_s^a$, $\lambda_w^a$, $\lambda_Y$ &+1\\
+%Matter & $\hat{L}$, $\hat{E}$ & 0 & $\tilde{l}_l$, $\tilde{e}^\dagger_R$ & +1 & $l_L$, $e_R$ & 0\\
+% & $\hat{Q}$, $\hat{D}$, $\hat{U}$ & +1 & $\tilde{q}_L$, $\tilde{d}^\dagger_R$, $\tilde{u}^\dagger_R$ & +1 & $q_L$, $d_R$, $u_R$ & 0\\
+%$H$-Higgs & $\hat{H}_{d,u}$ & 0 & $H_{d,u}$ & 0 & $\tilde{H}_{d,u}$ & -1\\
+%\hline
+%$R$-Higgs & $\hat{R}_{d,u}$ & +2 & $R_{d,u}$ & +2 & $\tilde{R}_{d,u}$ & +1\\
+%Adjoint Chiral & $\hat{O}$, $\hat{T}$, $\hat{S}$ & 0 & $\sigma^a$, $\omega^a$, $\rho$ & 0 & $\tilde{\chi}_s^a$, $\tilde{\chi}_w^a$, $\tilde{\chi}_Y$ & -1
+%\end{tabular}
+%\caption{This table lists the R-charges of all superfields and their components in the MRSSM.
+The fields of the $R$-Higgs and the adjoint chiral superfields are not present in the MSSM}\label{tab:R_charges_MRSSM}
+%\end{center}
+%\end{table}
 The gauge, matter and $H$-Higgs fields are the fields of the MSSM.
@@
 \end{align}
-which is not R-invariant because the Weyl fermion $\lambda$ has R-charge +1.
+which is not R-invariant because the Weyl fermion $\lambda$ has R-charge $+1$.
 Giving no mass to the gauginos is phenomenologically not possible.
-The only way to account for a fermion mass is to write down a Dirac mass term.
+The only way to account for a fermion mass is to write down a Dirac mass term
 \begin{align}
-\mathcal{L}_{\mathrm{Dirac\ mass}} = -m \chi\lambda + h.c.
+\mathcal{L}_{\mathrm{Dirac\ mass}} = -m \chi\lambda + h.c.,
 \end{align}
-This means that the 4-spinor of every gaugino is a Dirac- instead of a Majorana-spinor, e.g. for the gluino:
+where $\chi$ is another Weyl-spinor. This means that the 4-spinor of every gaugino is a Dirac- instead of a Majorana-spinor, e.g. for the gluino:
 \begin{align}
@@
 -i \lambda_s \\
-+i \overline{\lambda_s}
++i \overline{\lambda}_s
 \end{pmatrix} && \tilde{g}_\mathrm{MRSSM} = \begin{pmatrix}
 -i \lambda_s \\
-+i \overline{\chi_s}
++i \overline{\chi}_s
 \end{pmatrix}.
@@
 In order to maintain gauge invariance this chiral superfield has to transform in the adjoint representation, hence the name adjoint chiral in table \ref{tab:R_charges_MRSSM}.
-To fix notation the component decomposition of the 8 chiral supermultipletts assosiated to the gluons is given by
+To fix notation the component decomposition of the eight chiral supermultiplets assosiated to the gluons is given by
 \begin{align}
@@
 The scalar components $\sigma^a$ are referred to as scalar gluons and the Weyl spinors $\chi^a$ are called octinos.\\
-The same argument as for the adjoint chiral explains the existence of additional Higgs-superfields which are referred to as $R$-Higgs fields.\\
-Apart from these extensions R-symmetry also forbids terms which are allowed by supersymmetry.
-For the above choice of R-charges the $\mu$-term in \ref{eq:W_MSSM} and the $A$-terms in the last line of \ref{eq:L_soft} are absent in the MRSSM.
+The same argument as for the adjoint chiral superfields explains the existence of additional Higgs-superfields which are referred to as $R$-Higgs fields.\\
+Apart from these extensions $R$-symmetry also forbids terms which are allowed by supersymmetry.
+For the above choice of $R$-charges the $\mu$-term in \eqref{eq:W_MSSM} and the $A$-terms in the last line of \eqref{eq:L_soft} are absent in the MRSSM.
 Inspecting eq.
-\ref{eq:off_diagonal} implies that there is no squark mixing in the MRSSM.
-As a consequence terms which allow flavor violating processes like $\mu \to e \gamma$ are forbidden in the MRSSM\cite{Kribs:2007ac}.
+\eqref{eq:off_diagonal} implies that there is no squark mixing in the MRSSM.
+As a consequence terms which allow flavor violating processes like $\mu \to e \gamma$ in the MSSM are suppressed in the MRSSM\cite{Kribs:2007ac}.
 Quite interestingly Dirac gauginos can be heavier than Majorana gauginos without being less natural in view of the hierarchy problem\cite{Nelson:2002ca, Kribs:2012gx, Hardy:2013ywa}.
@@
 \end{align}
-where $\hat{Q}_L$ and $\hat{Q}_R$ refer to the left and right handed superfield of the quark.
+where $\hat{Q}_L$ and $\hat{Q}_R$ refer to the left- and right-handed superfield of the quark.
 Note that each field in the first line of eq.
-\ref{eq:L_super_RSQCD} transforms in a different representation of $SU_C(3)$, i.e.
+\eqref{eq:L_super_RSQCD} transforms in a different representation of $SU_C(3)$, i.e.
 the fundamental, the antifundamental and the adjoint one.
+From now on $T^a$ stands for the fundamental representation of the generators of $SU(3)_C$.
 In terms of components fields these expressions are given by
@@
 \int\mathrm{d}^4\theta\ \hat{\overline{Q}}_L \mathrm{e}^{2g_s\hat{V}_s} \hat{Q}_L =\ & F_L^\dagger F_L + (D_\mu \tilde{q}_L)^\dagger (D^\mu \tilde{q}_L) + \overline{q}_L \overline{\sigma}^\mu i D_\mu q_L\nonumber\\
-&-\sqrt{2}g_s \left( -i (\tilde{q}_L^\dagger T^a q_L ) \lambda^a + i \overline{\lambda}^a (\overline{q}_L T^a \tilde{q}_L) \right) + g_s\tilde{q}_L^\dagger T^a D^a \tilde{q}_L\label{eq:RSQCD_Feynmanrules1}\\
+&-\sqrt{2}g_s \left( -i (\tilde{q}_L^\dagger T^a q_L ) \lambda^a + i \overline{\lambda}^a (\overline{q}_L T^a \tilde{q}_L) \right) + g_s\tilde{q}_L^\dagger T^a D^a \tilde{q}_L,\label{eq:RSQCD_Feynmanrules1}\\
 \int\mathrm{d}^4\theta\ \hat{\overline{Q}}_R \mathrm{e}^{-2g_s\hat{V}^T_s} \hat{Q}_R =\  & F_R^\dagger F_R + (D_\mu \tilde{q}_R)^\dagger (D^\mu \tilde{q}_R) + \overline{q}_R \overline{\sigma}^\mu i D_\mu q_R\nonumber\\
-&+\sqrt{2}g_s \left( -i (\tilde{q}_R T^{\ast a} q_R ) \lambda^a + i \overline{\lambda}^a (\overline{q}_R T^{\ast a} \tilde{q}_R^\dagger) \right) - g_s \tilde{q}_R T^{\ast a} D^a \tilde{q}_R^\dagger\label{eq:RSQCD_Feynmanrules2}\\
+&+\sqrt{2}g_s \left( -i (\tilde{q}_R T^{\ast a} q_R ) \lambda^a + i \overline{\lambda}^a (\overline{q}_R T^{\ast a} \tilde{q}_R^\dagger) \right) - g_s \tilde{q}_R T^{\ast a} D^a \tilde{q}_R^\dagger,\label{eq:RSQCD_Feynmanrules2}\\
 \int\mathrm{d}^4\theta\ \hat{\overline{O}} \mathrm{e}^{2g_s\hat{V}^{\mathrm{fund}}_s} \hat{O} =\  & F_O^\dagger F_O + (D_\mu \sigma^a)^\dagger (D^\mu \sigma^a) + \overline{\chi} \overline{\sigma}^\mu i D_\mu \chi\nonumber\\
 &-\sqrt{2}g_s \left( -i (\sigma_b^\dagger (-if_{abc}) (-i\chi^c) ) \lambda^a + i \overline{\lambda}^a (i\overline{\chi}_b (+if_{abc}) \sigma^{c\dagger}) \right)\nonumber\\
-&-ig_s\sigma^{b^\dagger} f^{abc}D^a\sigma^c
+&-ig_s\sigma^{b^\dagger} f^{abc}D^a\sigma^c,
 \end{align}
@@
 \begin{align}
-\mathcal{L}_{\mathrm{soft}} =\ & -\frac{m_{\tilde{q}}^2}{2}(|\tilde{q}_L|^2 + |\tilde{q}_R|^2)\nonumber\\
+\mathcal{L}_{\mathrm{soft}} =\ & -\frac{m_{\tilde{q}}^2}{2}(|\tilde{q}_L|^2 + |\tilde{q}_R|^2),\nonumber\\
 & -m_{\sigma}^2\left|\sigma^{a}\right|^2 - m_g(\lambda\chi -\sqrt{2}D^a \sigma^a + h.c.)
 \end{align}
-where the complex scalar gluons which are also referred to as sgluons $\sigma = \frac{\phi_0 + i\sigma_0}{\sqrt{2}}$ constitute of two real ones with different masses.
+where the complex scalar gluons which are also referred to as sgluons
+\begin{align}
+\sigma = \frac{\phi_0 + i\sigma_0}{\sqrt{2}},
+\end{align}
+constitute of two real ones with different masses.
 The equations of motion for the auxiliary fields are
 \begin{align}
-D^a =& -g_s \tilde{q}_L^\dagger T^a \tilde{q}_L + g_s \tilde{q}_R T^{\ast a} \tilde{q}_R^\dagger + ig_s\sigma^{\dagger b}f^{abc}\sigma^c -\sqrt{2}m_g(\sigma^a + \sigma^{\dagger a})\\
+D^a =& -g_s \tilde{q}_L^\dagger T^a \tilde{q}_L + g_s \tilde{q}_R T^{\ast a} \tilde{q}_R^\dagger + ig_s\sigma^{\dagger b}f^{abc}\sigma^c -\sqrt{2}m_g(\sigma^a + \sigma^{\dagger a}),\\
 F_i =&\ 0 \hspace{3cm} \mathrm{for} \hspace{3cm} i = L,R,O
@@
 \begin{align}
-\mathcal{L}_{RSQCD} = & |D_\mu \sigma|^2 + |D_\mu \tilde{q}_R|^2 + |D_\mu \tilde{q}_L|^2 + \overline{q}i\slashed{D}q + \overline{\tilde{g}}^ai\slashed{D}P_L\tilde{g}^a + \overline{\tilde{g}}^ai\slashed{D}P_R\tilde{g}^a - \frac{1}{4} (F_a^{\mu\nu})^2\nonumber\\
+\mathcal{L}_{\mathrm{RSQCD}} = & |D_\mu \sigma|^2 + |D_\mu \tilde{q}_R|^2 + |D_\mu \tilde{q}_L|^2 + \overline{q}i\slashed{D}q + \overline{\tilde{g}}^ai\slashed{D}P_L\tilde{g}^a + \overline{\tilde{g}}^ai\slashed{D}P_R\tilde{g}^a - \frac{1}{4} (F_a^{\mu\nu})^2\nonumber\\
 & -\sqrt{2}g_s \left( \overline{\tilde{g}}^a P_R (q^C T^a \tilde{q}_L) + (\tilde{q}_L^\dagger T^a \overline{q}^C)P_L\tilde{g}^a \right)\nonumber\\
@@
 \begin{align}
-m_{\phi_0} = \sqrt{m_{\sigma_0}^2 + 4 m_{\tilde{g}}}.
+m_{\phi_0} = \sqrt{m_{\sigma_0}^2 + 4 m_{\tilde{g}}^2}.
 \end{align}

### 2016-06-23 Renormalization.tex
NLO chapter

@@
 The field and mass renormalization constants have been calculated in DREG in the on-shell scheme.
-This has the advantage that when turning to the cross section no manipulation of the Green function to the S-matrix element has to be done, see section \ref{sec:LSZ}.
+This has the advantage that when turning to the cross section no manipulation of the Green function to the S-matrix element has to be done, see section \ref{sec:LSZ}.\\
+The calculation has partially been performed by hand but was always checked with the mathematica output generated by the packages  \texttt{FeynArts} \cite{Hahn:2000} and \texttt{FormCalc} \cite{ChokoufeNejad:2013qja, Hahn:1998yk}.
 
@@
 \mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}} &= 2 \mathcal{M}^B  \left( \frac{\delta \hat{g}_s}{\hat{g}_s} + \frac{\delta Z_q}{2} + \frac{\delta Z^L_{\tilde{g}}}{2} + \frac{\delta Z_{\tilde{q}}}{2} \right)\\
-\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}} &= 2g_s^2 \left\langle v_2 \left| P_R\ i\frac{\slashed{p}+m_{\tilde{g}}}{t_{\tilde{g}}} \left[  i(\delta Z_{\tilde{g}}^L P_L + \delta Z_{\tilde{g}}^L P_L)\slashed{p}  \right.\right.\right.\nonumber\\
+\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}} &= 2g_s^2 \left\langle v_2 \left| P_R\ i\frac{\slashed{p}+m_{\tilde{g}}}{t_{\tilde{g}}} \left[  i(\delta Z_{\tilde{g}}^L P_L + \delta Z_{\tilde{g}}^R P_R)\slashed{p}  \right.\right.\right.\nonumber\\
 & \hspace{2cm}\left.\left.\left.\left.
@@
 \end{align}
-This is the beta function of QCD first found by [Gross, Politzer, Wil]
+This is the beta function of QCD first found by Politzer \cite{Politzer:1973fx} Gross and Wilczek \cite{Gross:1973ju}
 
@@
 To quickly check for UV-finiteness of a Greenfunction or a physical observable it is useful to have the extracted UV-divergences of the renormalization constants at hand.
-How these are obtained is described in \ref{sec:Passarino}.\\
-(In order to obtain these the Passarino-Veltman integrals need to be substituted by their $\frac{1}{\epsilon}$ coefficient.
-These  had been taken from \cite{Denner} and checked with \texttt{FeynArts} and \texttt{FormCalc} \cite{Hahn:2000}, \cite{Nejad2013}, \cite{Hahn:2000}.)
+How these are obtained is described in \ref{sec:Passarino}.
 \begin{align}
@@
 & \delta Z_{\tilde{q}} = 0 && \delta m_{\tilde{q}}^2 = 0\nonumber\\
-&\frac{\delta g_s}{g_s} = \frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}}\left[ T(F) n_f - C(A) \right]\nonumber\\
+&\frac{\delta g_s}{g_s} = \frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}}\left[ T(F) n_f - C(A) \right] = 0\nonumber\\
 & \delta Z_{\phi^0} = 0 && \delta m_{\phi^0}^2 = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}}\left[ 8T(F)n_f - 16C(A) \right]m_{\tilde{g}}^2\nonumber\\
@@
 \end{align}
+Note that the renormalization constants $\delta m_{\tilde{g}}$, $\delta m^2_{\phi^0}$ and $\delta m^2_{\sigma^0}$ are not independent from each other as the masses of the gluino and the two sgluons stam from only two parameters, i.e.
+$m_{\tilde{g}}$ and $m_{\sigma}^2$ from the softly breaking part of the Lagrangian, eq.
+\ref{eq:L_RSQCD}.
+In additions it happens that the particle content of RSQCD is such that $\frac{\delta g_s}{g_s} = 0$.
+This means that the $\beta$ function of $g_s$ equals zero at 1-loop-level if one does not choose to decouple heavy particles from the running as has been done in this thesis.
+However at 2-loop-level there is a non-zero $\beta$ function of $g_s$, which has been calculated by \texttt{SARAH}\cite{Staub:2013tta, Staub:2012pb, Staub:2010jh, Staub:2009bi}.

### 2016-06-23 Standardmodel.tex
Feynman Rules
NLO chapter

@@
 The Standard Model of particle physics is the commonly accepted theory describing the world's fundamental particles and their interactions.
-It is a gauge quantum field theory which is characterized by its invariance under symmetry groups.
-The Standard Model contains different fields, whose quantized excitations are interpreted as particles.\\
+It is a gauge quantum field theory and therefore characterized by its invariance under symmetry groups.
+The Standard Model contains different fields, whose quantized excitations are interpreted as all known particles.\\
 This chapter summarizes the most important aspects of the Standard Model.
@@
 \begin{align}
-[P^\mu,P^\nu] &= 0\nonumber\\
-[P^\mu,J^{\nu\rho}] &= i(g^{\mu\nu} P^\rho - g^{\mu\rho}P^\nu)\nonumber\\
+[P^\mu,P^\nu] &= 0,\nonumber\\
+[P^\mu,J^{\nu\rho}] &= i(g^{\mu\nu} P^\rho - g^{\mu\rho}P^\nu),\nonumber\\
 [J^{\mu\nu},J^{\rho\sigma}] &= i(g^{\nu\rho}J^{\mu\rho} + g^{\mu\sigma}J^{\nu\rho} - g^{\mu\rho}J^{\nu\sigma} - g^{\nu\sigma}J^{\mu\rho}).\label{eq:PoincareAlgebra}
@@
 \subsubsection*{Gauge Symmetries} 
-In order to describe interactions of matter particles gauge theories are used. In the Standard Model matter fields are described by Dirac spinors. The Lagrangian of a free Dirac field reads
+In order to describe interactions of matter particles with spin-1 force mediators, gauge theories are used.
+In the Standard Model matter fields are described by Dirac spinors.
+The Lagrangian of a free Dirac field reads
 \begin{align}
-\mathcal{L}_{Dirac} = \overline{\Psi} ( i\slashed{\partial} - m)\Psi.\label{eq:DiracLagrangian}
+\mathcal{L}_{\mathrm{Dirac}} = \overline{\Psi} ( i\slashed{\partial} - m)\Psi,\label{eq:DiracLagrangian}
 \end{align}
-To include interactions one imposes a local group symmetry (gauge symmetry) upon this Lagrangian. A spinor transforms under a generic gauge transformation like 
+where $m$ denotes the particle's mass. To include interactions, one imposes a local group symmetry (gauge symmetry) upon this Lagrangian. A spinor transforms under a generic gauge transformation like 
 \begin{align}
@@
 where $U(x)$ is an element of the gauge group in question.
-Because the gauge group is a unitary matrix Lie group it can be written in the form $U(x)=\mathrm{exp}(-igT^a\theta^a(x))$.
-Here $T^a$ are the self-adjoint generators of the associated Lie algebra which obey
+Because the gauge group is an unitary matrix Lie group, it can be written in the form $U(x)=\mathrm{exp}(-igT^a\theta^a(x))$.
+Here, $T^a$ are the self-adjoint generators of the associated Lie algebra which obey
 \begin{align}
-[T^a,T^b] = if_{abc}T^c
+[T^a,T^b] = if_{abc}T^c,
 \end{align}
-where $f_{abc}$ are the structure constants of a Lie algebra, $g$ is the coupling constant of the gauge group and $\theta^a(x)$ are local parameters.\\
-Because the parameters of the gauge group are local the derivative in \ref{eq:DiracLagrangian} spoils the gauge invariance.
-In order to rectify gauge invariance of the Lagrangian one introduces a further field for each index $a$ of the generators - the gauge vector $G^{a\mu}$.
+with $f_{abc}$ the structure constants of a Lie algebra, $g$ is the coupling constant of the gauge group and $\theta^a(x)$ are local parameters.\\
+As the parameters of the gauge group are local, the derivative in \eqref{eq:DiracLagrangian} spoils gauge invariance.
+In order to rectify the gauge invariance of the Lagrangian, one introduces a further field for each index $a$ of the generators, the gauge vector $G^{a\mu}$.
 Defining the transformation of the matrix valued gauge vector $G^\mu := G^{a\mu}T^a$ as
@@
 \begin{align}
-D^\mu = \partial^\mu + igT^aG^{a\mu}
+D^\mu = \partial^\mu + igT^aG^{a\mu},
 \end{align}
@@
 \begin{align}
-D_\mu \Psi(x) \to U(x) D_\mu \Psi(x) \label{eq:CovDerivative}
+D_\mu \Psi(x) \to U(x) D_\mu \Psi(x). \label{eq:CovDerivative}
 \end{align}
-Therefore gauge invariance is restored in eq.
-\ref{eq:DiracLagrangian} by replacing $\partial_\mu$ with $D_\mu$.
-But if the gauge vector is interpreted as a physical field there must apart from the so far introduced interaction term also be a kinetic term associated with it.
+Therefore, gauge invariance is restored in eq.
+\eqref{eq:DiracLagrangian} by replacing $\partial_\mu$ with $D_\mu$.
+But if the gauge vector is interpreted as a physical field, there must   also be a kinetic term associated with it.
 Using eq.
-\ref{eq:CovDerivative} one defines the field strength tensor\footnote{An alternative construction of the field strength tensor makes use of the gauge invariant Wilson loop.
-This gives some insights into the geometry of gauge transformations \cite{Peskin}.} $F^{a\mu\nu}$ whose matrix valued form
+\eqref{eq:CovDerivative} one defines the field strength tensor\footnote{An alternative construction of the field strength tensor makes use of the gauge invariant Wilson loop.
+This gives some insights into the geometry of gauge transformations \cite{Peskin}.} $F^{a\mu\nu}$, whose matrix valued form
 \begin{align}
@@
 Using the cyclic property of the trace and the Dynkin index $T(F)$ defined in eq.
-\ref{eq:DynkinIndex} in the appendix one can write down a gauge invariant kinetic term for the gauge vector:
+\eqref{eq:DynkinIndex} in the appendix, one can write down a gauge invariant kinetic term for the gauge vector:
 \begin{align}
-\mathcal{L}_{\mathrm{gauge}} = - \frac{1}{2} \mathrm{Tr} \left( F^{\mu\nu}F_{\mu\nu} \right) = -\frac{T(F)}{2} F^{a\mu\nu}F^a_{\mu\nu}
+\mathcal{L}_{\mathrm{gauge}} = - \frac{1}{2} \mathrm{Tr} \left( F^{\mu\nu}F_{\mu\nu} \right) = -\frac{T(F)}{2} F^{a\mu\nu}F^a_{\mu\nu}.
 \end{align}
@@
 \begin{align}
-\mathcal{L}_{\mathrm{Yang-Mills}} = \overline{\Psi}i\slashed{D}\Psi - \frac{1}{4}F^{a\mu\nu}F^a_{\mu\nu}
+\mathcal{L}_{\mathrm{Yang-Mills}} = \overline{\Psi}(i\slashed{D} - m)\Psi - \frac{1}{4}F^{a\mu\nu}F^a_{\mu\nu}
 \end{align}
@@
 $f_{abc} \neq 0$, there are self interactions among the spin-1 particles.\\
-The gauge group of the Standard Model is a direct product of the three gauge groups\footnote{The subscript stands for the associated charge of the groups respectively: $Y$ for hypercharge, $L$ for left handedness (weak Isospin $I_3$) and $C$ for color}: $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$.
+The gauge group of the Standard Model is a direct product of the three gauge groups\footnote{The subscript stands for the associated charge of the groups respectively: $Y$ for hypercharge, $L$ for left handedness (weak Isospin $I_3$) and $C$ for color}: $U(1)_Y$, $SU(2)_L$ and $SU(3)_C$.
 The elements $U(x)$ of those are given in table \ref{tab:SM_transformations}.\\
@@
 \hlinewd{2pt}
-$U_Y(1)$ & $U(x) = \mathrm{exp}\left(-ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)$\\
+$U(1)_Y$ & $U(x) = \mathrm{exp}\left(-ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)$\\
 \hline
-$SU_L(2)$ & $U(x) = \mathrm{exp}\left(-ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)$\\
+$SU(2)_L$ & $U(x) = \mathrm{exp}\left(-ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)$\\
 \hline
-$SU_C(3)$ & $U(x) = \mathrm{exp}\left(-ig_s T^a \cdot \theta_s^a(x)\right)$
+$SU(3)_C$ & $U(x) = \mathrm{exp}\left(-ig_s T^a \cdot \theta_s^a(x)\right)$
 \end{tabular}
-\caption{The table lists the explicit element $U(x)$ of the gauge groups $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$.
+\caption{The table lists the explicit element $U(x)$ of the gauge groups $U(1)_Y$, $SU(2)_L$ and $SU(3)_C$ of the Standard Model.
 The hypercharge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to (see table \ref{tab:SMfieldcontent}).
-$\vec{\tau}$ and $T^a$ are the geneators of $SU_L(2)$ and $SU_C(3)$ respectively.
+$\vec{\tau}$ and $T^a$ are the geneators of $SU(2)_L$ and $SU(3)_C$ respectively.
 In the fundamental representation $\vec{\tau} = \frac{\vec{\sigma}}{2}$ where $\vec{\sigma}$ has the 3 Pauli matrices as components and $T^a = \frac{\lambda^a}{2}$ where $\lambda^a$ are the 8 Gell-Mann matrices.
-$\varepsilon_{abc}$ and $f_{abc}$ are the structure constants of $SU_L(2)$ and $SU_C(3)$ respectively.}\label{tab:SM_transformations}
+$\varepsilon_{abc}$ and $f_{abc}$ are the structure constants of $SU(2)_L$ and $SU(3)_C$ respectively.}\label{tab:SM_transformations}
 \end{center}
@@
 % & $U(x) = \mathrm{exp}\left(-ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)$\\
-% $SU_L(2)$ & $\psi(x) \to \left( \mathbbm{1} - ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)\psi(x)$\\
+% $SU(2)_L$ & $\psi(x) \to \left( \mathbbm{1} - ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)\psi(x)$\\
 % & $W^{a\mu}(x) \to W^{a\mu}(x) +\partial^\mu\theta^a_w(x) + g_w \varepsilon^{abc} \theta^b_w(x)W^{c\mu}(x)$\\
@@
 %\end{tabular}
-%\caption{The table lists the explicit element $U(x)$ of the gauge groups $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$ and the infinitesimal transformations of spinor and vector fields.\newline
+%\caption{The table lists the explicit element $U(x)$ of the gauge groups $U_Y(1)$, $SU(2)_L$ and $SU_C(3)$ and the infinitesimal transformations of spinor and vector fields.\newline
 %The hypercharge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to.
-$\vec{\tau}$ and $T^a$ are the geneators of $SU_L(2)$ and $SU_C(3)$ respectively.
+$\vec{\tau}$ and $T^a$ are the geneators of $SU(2)_L$ and $SU_C(3)$ respectively.
 In the fundamental representation one has $\vec{\tau} = \frac{\vec{\sigma}}{2}$ where $\vec{\sigma}$ has the 3 Pauli matrices as components and $T^a = \frac{\lambda^a}{2}$ where $\lambda^a$ are the 8 Gell-Mann matrices.
-$\varepsilon_{abc}$ and $f_{abc}$ are the structure constants of $SU_L(2)$ and $SU_C(3)$ respectively.}\label{tab:SM_transformations}
+$\varepsilon_{abc}$ and $f_{abc}$ are the structure constants of $SU(2)_L$ and $SU_C(3)$ respectively.}\label{tab:SM_transformations}
 %\end{center}
@@
 
-%Furthermore the SM is a gauge theory, which has the gauge group $SU_C(3)\times SU_L(2)\times U_Y(1)$.
+%Furthermore the SM is a gauge theory, which has the gauge group $SU_C(3)\times SU(2)_L\times U_Y(1)$.
 %\paragraph{Transformation under $U_Y(1)$:}
@@
 %\end{align}
-%\paragraph{Transformation under $SU_L(2)$:}
+%\paragraph{Transformation under $SU(2)_L$:}
 %Spinor fields transform under this group as
@@
 In the Standard Model different matter particles take part in different interactions, i.e. their corresponding spinor couples to different gauge vectors.\\
-If a spinor couples to a certain gauge vector it transforms  non trivially (like indicated in table \ref{tab:SM_transformations}) under the gauge group which is associated with this gauge vector\footnote{In the Standard Model all matter particles transform in the fundamental (or trivial) representation of gauge groups.}.
-This means if a particle couples to a certain force its charge which is associated with this force is nonzero.\\
-The charges of particles for a force are defined as the eigenvalues of the generators which correspond to the force.
+If a spinor couples to a certain gauge vector, it transforms  non-trivially (like indicated in table \ref{tab:SM_transformations}) under the gauge group which is associated with this gauge vector.\footnote{In the Standard Model all matter particles transform in the fundamental (or trivial) representation of gauge groups.} This means if a particle couples to a certain force its charge which is associated with this force is non-zero.\\
+The charges of a particle related to a force are defined as the eigenvalues of the generators which correspond to the force.
 \subsubsection*{The Quarks:}
 Quarks are strongly interacting fermions, which means their spinors transform non trivially under $SU_C(3)$.
-Because they transform in the fundamental representation of $SU_C(3)$ this means a quark spinor is built up by 3 spinors each carrying another color.
+Because they transform in the fundamental representation of $SU_C(3)$ this means a quark spinor is built up by three spinors each carrying another color.
 This splitting of the quark spinor in colors is often suppressed for the sake of simplicity.
 This convention is adopted throughout this thesis.\\
-Furthermore the left handed component of quarks interact weakly, which means that their spinors\footnote{The left handed part of a 4-spinor $\Psi$ is projected out by the appropriate projector $P_L$.
-This is explained in Appendix \ref{sec:2spinor_notation}.} transform (in the fundamental representation) under $SU_L(2)$ transformations meaning that 2 left handed quark spinors are assembled within a doublet.\\
-Finally all quarks carry a hypercharge.
+Furthermore, the left handed component of quarks interact weakly, which means that their spinors\footnote{The left handed part of a 4-spinor $\Psi$ is projected out by the appropriate projector $P_L$.
+This is explained in Appendix \ref{sec:2spinor_notation}.} transform (in the fundamental representation) under $SU(2)_L$ transformations meaning that two left handed quark spinors are assembled within a doublet.\\
+Finally, all quarks carry a hypercharge.
 In section \ref{sec:EWSB} the mechanism of electroweak symmetry breaking is described.
-This mechanism explains how electromagnetism arises from the groups $SU_L(2)$ and $U_Y(1)$.
+This mechanism explains how electromagnetism arises from the groups $SU(2)_L$ and $U(1)_Y$.
 All quarks interact electromagnetically.\\
-After all there are 6 quarks which are listed in table \ref{tab:generations}.
+All together, there are six quarks which are listed in table \ref{tab:generations}.
 They are categorized in 3 generations because their quantum numbers except for their masses reoccur in each generation.
 The two types of quarks within a generation which have distinct quantum numbers are referred to as up-type and down-type quarks.
-An up-type-quark and the down-type quark of the same generation built up a doublet.
+The up-type-quark and the down-type quark of the same generation built up a doublet.
 \subsubsection*{The Leptons:}
@@
 They take part in the weak and the electromagnetic interaction, i.e.
-their spinors transform under the fundamental representation of $SU_L(2)$ and $U_Y(1)$.
-As for the quarks only the left handed components interact weakly.\\
-As for the quarks there are 6 leptons which are classified into 3 generations (see table \ref{tab:generations}).
+their spinors transform non-trivially under the fundamental representation of $SU(2)_L$ and $U(1)_Y$.
+As for the quarks only the left handed components interact weakly and there are six leptons which are classified into three generations (see table \ref{tab:generations}).
 In each generation is a lepton with a negative electrical charged and an electrically neutral lepton.
 The latter ones are referred to as neutrinos.
-Right handed neutrinos have not been observed (yet) and are therefore absent in the SM.
+Right handed neutrinos have not been observed (yet) and are therefore absent in the Standard Model.
 The former are called electron, muon and tau.
@@
 \begin{tabular}{l?l|l|l}
-Particle & 1$^{st}$ generation & 2$^{nd}$ generation & 3$^{rd}$ generation\\
+Particle & 1$^{st}$ Generation & 2$^{nd}$ Generation & 3$^{rd}$ Generation\\
 \hlinewd{2pt}
-$u_{i}$ \hspace{0.5cm} up-type-Quark & $u$ \hspace{0.5cm} up-Quark & $c$ \hspace{0.5cm} charm-Quark & $t$ \hspace{0.5cm} top-Quark\\
-$d_{i}$ \hspace{0.5cm} down-type-Quark & $d$ \hspace{0.5cm} down-Quark & $s$ \hspace{0.5cm} strange-Quark & $b$ \hspace{0.5cm} bottom-Quark\\
+$u_{i}$ \hspace{0.5cm} up-type-quark & $u$ \hspace{0.5cm} up-quark & $c$ \hspace{0.5cm} charm-quark & $t$ \hspace{0.5cm} top-quark\\
+$d_{i}$ \hspace{0.5cm} down-type-quark & $d$ \hspace{0.5cm} down-quark & $s$ \hspace{0.5cm} strange-quark & $b$ \hspace{0.5cm} bottom-quark\\
 \hline
-$e_i$ \hspace{0.5cm} Charged Lepton & $e$ \hspace{0.5cm} Electron & $\mu$ \hspace{0.5cm} Muon &  $\tau$ \hspace{0.5cm} Tau\\
-$\nu_i$ \hspace{0.5cm} Neutrino & $\nu_e$ \hspace{0.35cm} Electron Neutrino & $\nu_\mu$ \hspace{0.35cm} Muon Neutrino &  $\nu_\tau$ \hspace{0.35cm} Tau Neutrino
+$e_i$ \hspace{0.5cm} charged lepton & $e$ \hspace{0.5cm} electron & $\mu$ \hspace{0.5cm} muon &  $\tau$ \hspace{0.5cm} tau\\
+$\nu_i$ \hspace{0.5cm} neutrino & $\nu_e$ \hspace{0.35cm} electron neutrino & $\nu_\mu$ \hspace{0.35cm} muon neutrino &  $\nu_\tau$ \hspace{0.35cm} tau neutrino
 \end{tabular}
-\caption{The matter particles of the SM. Listed are the symbol and the name of the particles.}\label{tab:generations}
+\caption{The matter particles of the Standard Model.
+Listed are the symbol and the name of the particles.
+The labeling of particles has been taken from \cite{Bach}.
+The shortcut charged lepton refers to electrically charged leptons.}\label{tab:generations}
 \end{center}
 \end{table}
-Quarks and Leptons are the matter particles of the Standard Model.
+Quarks and leptons are the matter particles of the Standard Model.
 They are listed together with their charges for the different forces in table \ref{tab:SMfieldcontent}.
-There is the color for strong interactions, the third component of the weak isospin $I_3$ for weak interactions (the eigenvalue of the third generator of the $SU_L(2)$) and the half of the hypercharge $\frac{Y}{2}$ to obtain the electric charge $Q$ via the Gell-Mann–Nishijima formula: $Q = I_3 + \frac{Y}{2}$.\\
-Because the left and right-handed parts of spinors transform differently under the $SU_L(2)$ they are listed separately. All quarks occur with three different colors.\\
-In the last row the Higgs-boson is listed. Its associated field is responsible for the mass of elementary particles. That is explained in section \ref{sec:EWSB}.\\
+There is the color for strong interactions, the third component of the weak isospin $I_3$ for weak interactions (the eigenvalue of the third generator of the $SU(2)_L$) and the half of the hypercharge $\frac{Y}{2}$ to obtain the electric charge $Q$ via the Gell-Mann–Nishijima formula: $Q = I_3 + \frac{Y}{2}$.\\
+Because the left- and right-handed parts of spinors transform differently under the $SU_L(2)$ they are listed separately. All quarks occur with three different colors.\\
+In the last row, the Higgs-boson is listed. Its associated field is responsible for the mass of elementary particles. That is explained in section \ref{sec:EWSB}.\\
 \begin{table}[H]
@@
 \begin{tabular}{c?c|c|c|c|c}
-Particle & Symbol & color & $I_3$ & $\frac{Y}{2}$ & Q\\
+Particle & Symbol & Color & $I_3$ & $\frac{Y}{2}$ & Q\\
 \hlinewd{2pt}
-Left handed Quarks & $Q_{iL} = \begin{pmatrix}
+left-handed quarks & $q_{iL} = \begin{pmatrix}
 u_{iL}\\
@@
 \end{pmatrix}$\\
-Right-handed Quarks & $u_{iR}$ & red, green, blue & $0$ & $+\frac{2}{3}$ & $+\frac{2}{3}$ \\
+right-handed quarks & $u_{iR}$ & red, green, blue & $0$ & $+\frac{2}{3}$ & $+\frac{2}{3}$ \\
  & $d_{iR}$ & red, green, blue & $0$ & $-\frac{1}{3}$ & $-\frac{1}{3}$\\
 \hline
-Left-handed Leptons & $\ell_{iL} = \begin{pmatrix}
+left-handed leptons & $\ell_{iL} = \begin{pmatrix}
 \nu_{iL}\\
@@
 \end{pmatrix}$\\
-Right-handed Leptons & $e_{iR}$ & - & 0 & $+1$ & $+1$\\
+right-handed leptons & $e_{iR}$ & - & 0 & $+1$ & $+1$\\
 \hline
@@
 The index $i = 1,2,3$ labels the generation of the matter particles and is written out in table \ref{tab:generations}.
-If there are no colors specified or charges are zero this means that the fields in question transform trivially under the pertaining gauge transformation.}\label{tab:SMfieldcontent}
+If there are no colors specified or charges are zero this means that the fields in question transform trivially under the pertaining gauge transformation.
+In fact, the Higgs particle originates from a $SU(2)_L$-doublet.
+This is not given here because within a certain gauge only the Higgs particle is a real particle.
+}\label{tab:SMfieldcontent}
 \end{center}
@@
 \begin{tabular}{c|c|c?c|c|c}
-\multicolumn{3}{c?}{before EWSB} & \multicolumn{3}{c}{after EWSB}\\
+\multicolumn{3}{c?}{Before EWSB} & \multicolumn{3}{c}{After EWSB}\\
 \hlinewd{2pt}
@@
 \hlinewd{2pt}
-$SU_C(3)$ & $g_s$ & $G^a_\mu$ & $g_s$ & $G^a_\mu$ & Gluon\\
-$SU_L(2)$ & $g_w$ & $W^b_\mu$ & $g_W = \sqrt{2}g_w$,  &  $W^\pm_\mu$,  & $W^\pm$,  \\
+$SU(3)_C$ & $g_s$ & $G^a_\mu$ & $g_s$ & $G^a_\mu$ & Gluon\\
+$SU(2)_L$ & $g_w$ & $W^b_\mu$ & $g_W = \sqrt{2}g_w$,  &  $W^\pm_\mu$,  & $W^\pm$,  \\
  & & & $g_Z = \sqrt{g_w^2 + g_Y^2}$ & $Z^0_\mu$ & $Z^0$ Boson\\
-$U_Y(1)$ & $g_Y$ & $B_\mu$ & $e = g_Y\cdot c_w$ & $A_\mu$ & Photon
+$U(1)_Y$ & $g_Y$ & $B_\mu$ & $e = g_Y\cdot c_w$ & $A_\mu$ & Photon
 \end{tabular}
@@
 $a = 1,\hdots 8$ and $b=1,2,3$ label the number of gauge fields.
-$c_w$ is the cosine of the electroweak mixing angle defined in \ref{sec:EWSB}}\label{tab:force_particles}
+$c_w$ is the cosine of the electroweak mixing angle defined in \ref{sec:EWSB}.}\label{tab:force_particles}
 \end{center}
@@
 The force particles are described by gauge fields.
-The gauge field of $SU_C(3)$ is the gluon field.
-Because the $SU_C(3)$ has 8 generators there are 8 gluons.
+The gauge field of $SU(3)_C$ is the gluon field.
+Because the $SU_C(3)$ has eight generators there are eight gluons.
 Their coupling constant is denoted with $g_s$.\\
 For the other force particles in the Standard Model - the $W^\pm$ bosons, the $Z_0$ boson and the photon the situation is slightly more involved.
-They are obtained as a mixture of the $W^b_\mu$ ($b=1,2,3$) and the $B_\mu$ field which are the gauge fields of $SU_L(2)$ and $U_Y(1)$ respectively.
+They are obtained as a mixture of the $W^b_\mu$ ($b=1,2,3$) and the $B_\mu$ field which are the gauge fields of $SU_L(2)_L$ and $U_Y(1)_Y$ respectively.
 This mixing procedure is explained in section \ref{sec:EWSB}.\\
@@
 \begin{align}
-\mathcal{L}_{\mathrm{matter}} =  \sum_{i=1}^3 \left( \overline{\ell}_{iL} i \slashed{D} l_{iL} + \overline{e}_{iR} i \slashed{D} e_{iR} + \overline{q}_{iL} i \slashed{D} q_{iL} + \overline{u}_{iR} i \slashed{D} u_{iR} + \overline{d}_{iR} i \slashed{D} d_{iR} \right)
+\mathcal{L}_{\mathrm{matter}} =  \sum_{i=1}^3 \left( \overline{\ell}_{iL} i \slashed{D} l_{iL} + \overline{e}_{iR} i \slashed{D} e_{iR} + \overline{q}_{iL} i \slashed{D} q_{iL} + \overline{u}_{iR} i \slashed{D} u_{iR} + \overline{d}_{iR} i \slashed{D} d_{iR} \right),
 \end{align}
@@
 \begin{align}
-D_\mu = \partial_\mu + i g_Y\frac{\hat{Y}}{2} +ig_w \vec{\tau}\cdot \vec{W}^\mu + i g_s T^a G_a^\mu
+D_\mu = \partial_\mu + i g_Y\frac{\hat{Y}}{2} +ig_w \vec{\tau}\cdot \vec{W}^\mu + i g_s T^a G_a^\mu,
 \end{align}
 where for each field the corresponding representation (fundamental or trivial) of the gauge group is to be inserted (see table \ref{tab:SMfieldcontent}).
-The hyper charge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to.
+The hypercharge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to.
 These can also be found in table \ref{tab:SMfieldcontent}.
@@
 \subsection{Electroweak Symmetry Breaking}\label{sec:EWSB}
-So far no mass terms like in the Dirac Lagrangian \ref{eq:DiracLagrangian} have been introduced.
-The reason for this is that they are not gauge invariant for left- and right-handed spinors transform differently.
+So far, no mass terms like in the Dirac Lagrangian \ref{eq:DiracLagrangian} have been introduced.
+The reason for this is that they are not gauge invariant, for left- and right-handed spinors transform differently.
 The same argument forbids terms like $-\frac{m^2}{2}A^\mu A_\mu$ for a generic gauge boson.
@@
 \phi^0
-\end{pmatrix}
+\end{pmatrix},
 \end{align}
@@
 \end{align}
-where $\mu^2,\lambda > 0$.
+where $\mu^2,\lambda > 0$ and $v$ is given by $v = \sqrt{\frac{\mu^2}{\lambda}}$.
 The Higgs sector of the Standard Model reads
@@
 \end{align}
-The Higgs doublet couples to the gauge fields of $SU_L(2)$ and $U_Y(1)$ in the fundamental representation.
-Inserting an expansion\footnote{The complex $\phi^+(x)$ and the real $\sigma(x)$ are the fields of the so called massless Goldstone bosons.
+The Higgs doublet couples to the gauge fields of $SU(2)_L$ and $U_Y(1)$ in the fundamental representation.
+Inserting an expansion\footnote{The complex $\phi^+(x)$ and the real $\sigma(x)$ are the fields of the so-called massless Goldstone bosons.
 These degrees of freedom can be absorbed in the longitudinally polarized degrees of freedom of the arising gauge bosons $W^\pm$ and $Z^0$.
 This is referred to as unitary gauge\cite{book:811554}.
-The real $H(x)$ is the Higgs field, whose excitation is the Higgs boson.} around the VEV $\Phi = \begin{pmatrix}
+The real $H(x)$ is the Higgs field, whose excitation is the Higgs boson.} around the VEV
+\begin{align}
+\Phi = \begin{pmatrix}
 \phi^+(x) \\
 \frac{1}{\sqrt{2}} (v + H(x) + i\sigma(x))
-\end{pmatrix}$ one obtains quadratic terms, i.e.
+\end{pmatrix}
+\end{align}
+one obtains quadratic terms, i.e.
 mass terms, for the gauge fields in question.
@@
 W^3_\mu
-\end{pmatrix}
+\end{pmatrix},
 && W^{\pm}_\mu = \frac{1}{\sqrt{2}}(W^1_\mu \mp i W^2_\mu),
@@
 \begin{align}
-& m_W = \frac{g_w}{2} v \hspace{3cm} m_Z = \frac{\sqrt{g_w^2+g_Y^2}}{2} v \hspace{3cm} m_A = 0.
+& m_W = \frac{g_w}{2} v, \hspace{3cm} m_Z = \frac{\sqrt{g_w^2+g_Y^2}}{2} v, \hspace{3cm} m_A = 0.
 \end{align}
@@
 As the photon is massless it is still associated with a gauge symmetry called $U_{em}(1)$.
-One therefore often writes EWSB as the breaking of the gauge group $SU_L(2) \times U_Y(1)$ to $U_{em}(1)$.\\
-Matter particles acquire mass via Yukawa coulings to the Higgs doublet. For up-type-quarks one uses that the charge conjugate of $\Phi$: $\Phi^C = i \sigma^2 \Phi^\ast$ also transform as $\Phi$.
+One therefore often writes EWSB as the breaking of the gauge group $SU(2)_L \times U_Y(1)$ to $U_{em}(1)$.\\
+Matter particles acquire mass via Yukawa coulings to the Higgs doublet.
+For up-type-quarks one uses that the charge conjugate of $\Phi$: $\Phi^C = i \sigma^2 \Phi^\ast$ also transforms as $\Phi$.
+The Yukawa Lagrangian is given by
 \begin{align}
-\mathcal{L}_{\mathrm{Yukawa}} = -\sum_{i,j=1}^3 \left( y_{ij}^e \overline{\ell}_L \Phi e_R  + y_{ij}^d \overline{q}_L \Phi d_R + y_{ij}^u \overline{q}_L \Phi^C u_R\right) + h.c. \label{eq:LYukawa}
+\mathcal{L}_{\mathrm{Yukawa}} = -\sum_{i,j=1}^3 \left( y_{ij}^e \overline{\ell}_L \Phi e_R  + y_{ij}^d \overline{q}_L \Phi d_R + y_{ij}^u \overline{q}_L \Phi^C u_R\right) + h.c., \label{eq:LYukawa}
 \end{align}
@@
 \begin{align}
-m^e_{ij} = \frac{y^e_{ij}}{\sqrt{2}} v  \hspace{4cm} m^d_{ij} = \frac{y^d_{ij}}{\sqrt{2}} v \hspace{4cm} m^u_{ij} = \frac{y^u_{ij}}{\sqrt{2}} v.
+m^e_{ij} = \frac{y^e_{ij}}{\sqrt{2}} v,  \hspace{4cm} m^d_{ij} = \frac{y^d_{ij}}{\sqrt{2}} v, \hspace{4cm} m^u_{ij} = \frac{y^u_{ij}}{\sqrt{2}} v.
 \end{align}
-The quark mass matrices are not diagonal, which is the precondition of the violation of CP-invariance.
-\footnote{The actual CP-violating term is the coupling term from quarks to the $W$-bosons.} One therefore has to distinguish between interaction and mass eigenstates of the quarks.
+The quark mass matrices are not diagonal, which is the precondition of the violation of CP-invariance.\footnote{The actual CP-violating term is in the coupling term of quarks to the $W$-bosons.} One therefore has to distinguish between interaction and mass eigenstates of the quarks.
 The corresponding transformation matrix is the well known CKM-matrix \cite{Cabbibo:1964zsa, Kobayashi:1973fv}.
-Throughout this thesis, the CKM-matrix is approximated with the unit matrix as it will have a minor influence upon the results\\
+Throughout this thesis, the CKM-matrix is approximated with the unit matrix as it will have no influence upon the results.\\
 The upshot of EWSB are masses for all matter particles except for the neutrinos and masses for the gauge bosons $W^\pm$ and $Z^0$.
@@
 \subsection{Quantization}
-The Quantization of Spin 0 and Spin $\frac{1}{2}$ fields yield no complication in the Lagrangian formalism.
-To quantize Spin 1 fields it turns out that the usual gauge invariance needs to be replaced by the so called BRST invariance \cite{Becchi:1974xu, Becchi:1974md, Becchi:1975nq}.
+The Quantization of spin-0 and spin-$\frac{1}{2}$ fields yield no complication in the Lagrangian formalism.
+To quantize spin 1 fields it turns out that the usual gauge invariance needs to be replaced by the so called BRST invariance \cite{Becchi:1974xu, Becchi:1974md, Becchi:1975nq}.
 This results in two extra contributions in the Lagrangian.
@@
 \end{align}
-Here $R_\xi$-gauge is chosen, where the parameters $\xi_i$ specify the gauge further.
-The two terms in the middle are modified with the Goldstone bosons from section \ref{sec:EWSB}.
+Here, $R_\xi$-gauge is chosen, where the parameters $\xi_i$ specify the gauge further.
+The second and third term are modified with the Goldstone bosons from section \ref{sec:EWSB}.
 This is to cancel terms of the form $V_\mu \partial^\mu \phi$ up to a total derivative arising from EWSB which would lead to non-diagonal propagators, where $V$ stands for a gauge boson $W^\pm$ or $Z^0$ and $\phi$ for a Goldstone boson.\\%\cite{book:811554}page 622
-Secondly there is a ghost Lagrangian
+Secondly, there is a ghost Lagrangian
 \begin{align}

### 2016-06-23 Virt_Real.tex
Feynman Rules
NLO chapter

@@
 	\draw[gluon](-0.5,-1)--(0.5,-1);
+	\draw[fermionnoarrow](-0.5,-1)--(0.5,-1);
 	\draw[scalar](0.5,-1)--(1.5,-1);
@@
 \end{figure}
-Due to their origin these divergences are referred to as ultraviolet and infrared divergences.
-Ultraviolet divergences occur when the loop momenta and energy tend to infinity which corresponds to arbitrary short distance interactions.
-However, these divergences are cured by first regularizing them and then introducing appropriate counterterms\footnote{These counterterms have to be of the same $\mathcal{O}(\hbar)$ as the loop diagrams they are constructed to cancel.
-NOCHMAL IN LAHIRI / PAL NACHSCHAUEN.} in the Lagrangian to cancel the extracted singularities.
+Due to their origin these divergences are referred to as ultraviolet (UV) and infrared divergences (IR).
+Ultraviolet divergences occur when loop momenta and energy tend to infinity which corresponds to arbitrary short distance interactions.
+However, these divergences are cured by first regularizing them and then introducing appropriate counterterms\footnote{These counterterms have to be of the same $\mathcal{O}(\hbar)$ as the loop diagrams they are constructed to cancel \cite{lahiri2005first}.} in the Lagrangian to cancel the extracted singularities.
 The second step is called renormalization and can be understood as a redefinition or rescaling of parameters and fields in the Lagrangian in the first place:
@@
 & P_L \tilde{g} \to \sqrt{Z_{\tilde{g}}^L} P_L \tilde{g} && P_R \tilde{g} \to \sqrt{Z_{\tilde{g}}^R} P_R \tilde{g}\nonumber\\
-& q \to \sqrt{Z_q}q && G_\mu \to \sqrt{Z_G} G_\mu && \\
+& q \to \sqrt{Z_q}q && G_\mu \to \sqrt{Z_G} G_\mu && \label{eq:fieldtrafo}\\
 & g_s \to g_{s\ \mathrm{bare}} && m_{\tilde{q}}^2 \to m_{\tilde{q}\ \mathrm{bare}}^2\nonumber\\
-&  m_{\sigma}^2 \to m_{\sigma\ \mathrm{bare}}^2 && m_{\tilde{g}} \to m_{\tilde{g}\ \mathrm{bare}}
+&  m_{\sigma}^2 \to m_{\sigma\ \mathrm{bare}}^2 && m_{\tilde{g}} \to m_{\tilde{g}\ \mathrm{bare}}\label{eq:parametertrafo}
 \end{align}
-In this thesis the computation is performed in $D = 4-2\epsilon$ dimensions in order to regularize it.
+In this thesis the computation of amplitudes is performed in $D = 4-2\epsilon$ dimensions in order to regularize infinities.
 Ultraviolet divergences show then up as single poles in $\epsilon$.
-This procedure will be discussed in detail in section \ref{sec:renMRSSM} and \ref{sec:LSZ}.\\
+The renormalization will be discussed in detail in section \ref{sec:renMRSSM} and \ref{sec:LSZ}.\\
 Having removed the ultraviolet divergences the matrix element is not free of divergences as it comprises infrared divergences.
@@
 \frac{\mbox{d}^2 \sigma^{\mathrm{V}}}{\mbox{d}t\ \mbox{d}u} =& \frac{K_{ab}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_1^2m_2^2}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_1^2m_2^2)\nonumber\\
-&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum |\mathcal{M}^{\mathrm{V}}|^2.
+&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum |\mathcal{M}^{\mathrm{V}}|^2.\label{eq:diffsigma}
 \end{align}
@@
 However real corrections also contain divergences.
-Including these contributions to the cross section causes the cancellation of singles poles coming from soft divergences and the cancellation of double poles.
+Including these contributions to the cross section causes the cancellation of single poles coming from soft divergences and the cancellation of double poles.
 At this point the only singularities which are left in the cross section are the collinear ones.\\
-To see how these are removed consider diagram the second digram in fig. \ref{fig:RealGluon}. The propagator of the quark which radiates off a gluon is giving a contribution of the form
+To see how these are removed consider the second diagram in fig. \ref{fig:RealGluon}. The propagator of the quark which radiates off a gluon gives a contribution of the form
 \begin{align}
@@
 to the the diagram in question.
-Where $p_q$, $p_g$ ($E_q$, $E_g$) are the quark's and gluon's four-momentum (energy) and $\theta_{qg}$ is the angle between the quark's and gluon's three-momentum.
+Here $p_q$, $p_g$ ($E_q$, $E_g$) are the quark's and gluon's four-momentum (energy) and $\theta_{qg}$ is the angle between the quark's and gluon's three-momentum.
 One observes two potentially singular limits
@@
 This suggest that some divergences may come from the incoming hadron and are actually not associated with the interaction.
-In fact this turns out to be the case: The remaining collinear divergences can be absorbed in to a redefinition of the parton density functions.
-This procedure is referred to as mass factorization.
-Figure \ref{fig:DivergenceSummary} summarizes the required steps to render the next-to-leading-order cross section finite.\\
-In fact the Kinoshita-Lee-Naunberg-Theorem \cite{1962JMP.....3..650K},\cite{PhysRev.133.B1549} guarantees the finiteness of sufficiently inclusive observables.
+In fact this turns out to be the case: The remaining collinear divergences have a generic form (evtl.
+angeben) and can, by redefinition, be absorbed into the parton density functions.
+This procedure is referred to as mass factorization \cite{dissertori2003quantum}.
+In fact the Kinoshita-Lee-Naunberg-Theorem \cite{1962JMP.....3..650K},\cite{PhysRev.133.B1549} guarantees the finiteness of sufficiently inclusive observables.\\
+Figure \ref{fig:DivergenceSummary} summarizes the required steps to render the next-to-leading-order cross section finite.
 \begin{figure}[!htbp]
@@
 \subsubsection{Real Gluon Radiation}
-Representative Feynman-diagrams for real gluon emission are shown in fig.
+A representative set of Feynman-diagrams for real gluon emission are shown in fig.
 \ref{fig:RealGluon}.

### 2016-06-23 custom_commands_Theorie.tex
NLO chapter

--- 2016-02-25 custom_commands_Theorie.tex
@@
             \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
+%% selbst definierte Befehle für tikz
+\tikzstyle{block1a} = [rectangle, draw, fill=blue!20, 
+text width=10em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{block2a} = [rectangle, draw, fill=red!20, 
+text width=10em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{block1b} = [rectangle, draw, fill=blue!40, 
+text width=10em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{block2b} = [rectangle, draw, fill=red!40, 
+text width=10em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{block3} = [rectangle, draw, fill=green!40, 
+text width=10em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{block4} = [rectangle, draw, fill=blue!40, 
+text width=11em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{block5a} = [rectangle, draw, fill=red!40, 
+text width=28.5em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{block5b} = [rectangle, draw, fill=red!20, 
+text width=8em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{block5c} = [rectangle, draw, fill=red!20, 
+text width=9em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{block6a} = [rectangle, draw, fill=green!40, 
+text width=15em, text centered, rounded corners, minimum height=1cm]
+\tikzstyle{line} = [draw, -latex']       
 \usepackage{hyperref}			% Has to be at the end.

### 2016-06-24 MSSM.tex
added matrix element plot M_virt/M_tree like Dominik wanted

@@
 Coleman and Mandula \cite{Coleman:1967ad} found that for any reasonable quantum field theory space-time and internal symmetries, i.e.
-gauge symmetries ``cannot by combined in any but the trivial way"\cite{Pelc:1996vg}.
+gauge symmetries ``cannot by combined in any but the trivial way''\cite{Pelc:1996vg}.
 Ergo the symmetry groups of the Standard Model are the most general ones.\\
@@
 The superpartners of fermions have Spin 0 and are referred to as sfermions.
-The name of each sfermion is given by the name of its Standard Model partner with an additional ``s-" in front of it, e.g.
+The name of each sfermion is given by the name of its Standard Model partner with an additional ``s-'' in front of it, e.g.
 selectron or up-squark.
-The superpartners of bosons have spin $\frac{1}{2}$ and get an additional ``-ino" at the end of their name, e.g.
+The superpartners of bosons have spin $\frac{1}{2}$ and get an additional ``-ino'' at the end of their name, e.g.
 higgsino as the superpartner of the Higgs or bino as superpartner of the $B$-boson.\\
@@
 These are necessary to avoid an anomaly in the electroweak gauge symmetry and to give masses to both up- and down-type quarks \cite[page 8]{Martin:1997ns}.\\
-Note that the ``chirality" of sfermions is understood to be the chirality of their superpartners. Of course scalar particles have no handedness.
+Note that the ``chirality'' of sfermions is understood to be the chirality of their superpartners. Of course scalar particles have no handedness.
 \begin{table}
@@
 The third column shows the representation (for $SU(3)_C$ and $SU(2)_L$) in which the fields transform and in which the generator in the covariant derivative needs to be inserted as well as the charges of the fields for $U(1)_Y$.
-For $SU(3)_C$ the ``8" refers to the adjoint representation (see appendix \ref{sec:coloralgebra}), the ``3" to the fundamental and the ``3$^\ast$" to the antifundamental representation $T^a_{antifund} = -\frac{\lambda^a}{2}$.
-For $SU(2)_L$ ``3" refers to the adjoint representation and ``2" to the fundamental representation.
-For both $SU(2)_L$ and $SU(3)_C$ a ``1" indicates the the trivial representation.}\label{tab:MSSMfieldcontent}
+For $SU(3)_C$ the ``8'' refers to the adjoint representation (see appendix \ref{sec:coloralgebra}), the ``3'' to the fundamental and the ``3$^\ast$'' to the antifundamental representation $T^a_{antifund} = -\frac{\lambda^a}{2}$.
+For $SU(2)_L$ ``3'' refers to the adjoint representation and ``2'' to the fundamental representation.
+For both $SU(2)_L$ and $SU(3)_C$ a ``1'' indicates the the trivial representation.}\label{tab:MSSMfieldcontent}
 \end{center}

### 2016-06-24 RSymmetry.tex
added matrix element plot M_virt/M_tree like Dominik wanted

@@
 \end{align}
-and R-symmetry does not commute with supersymmetry 
+and $R$-symmetry does not commute with supersymmetry 
 \begin{align}
@@
 \end{align}
-meaning that superpartners do not have the same R-charge. The transformation of chiral and vector superfields reads
+meaning that superpartners do not have the same $R$-charge. The transformation of chiral and vector superfields reads
 \begin{align}
@@
 %\end{tabular}
-%\caption{This table shows the R-charges of a generic chiral and vector superfield.}
+%\caption{This table shows the$R$-charges of a generic chiral and vector superfield.}
 %\end{center}
@@
 
-\subsection{The Minimal R-Symmetric Supersymmetric Standard Model}
-If one imposes R-symmetry upon the MSSM one is faced with a certain arbitrariness, i.e.
-the choice of the R-charges of the chiral superfields.
-A minimal R-symmetric extension of the MSSM is the minimal R-symmetric supersymmetric Standard Model (MRSSM)\cite{Kribs:2007ac}.
-In this model the R-charges are chosen in such a way, that every Standard Model particle has R-charge zero.
-Following this one obtains the R-charges of all particles which are summed up in table \ref{tab:R_charges_MRSSM}\cite{Diessner:2015bna}.
+\subsection{The Minimal$R$-Symmetric Supersymmetric Standard Model}
+If one imposes$R$-symmetry upon the MSSM one is faced with a certain arbitrariness, i.e.
+the choice of the$R$-charges of the chiral superfields.
+A minimal$R$-symmetric extension of the MSSM is the minimal$R$-symmetric supersymmetric Standard Model (MRSSM)\cite{Kribs:2007ac}.
+In this model the$R$-charges are chosen in such a way, that every Standard Model particle has$R$-charge zero.
+Following this one obtains the$R$-charges of all particles which are summed up in table \ref{tab:R_charges_MRSSM}\cite{Diessner:2015bna}.
 \begin{table}[H]
@@
 %\end{tabular}
-%\caption{This table lists the R-charges of all superfields and their components in the MRSSM.
+%\caption{This table lists the$R$-charges of all superfields and their components in the MRSSM.
 The fields of the $R$-Higgs and the adjoint chiral superfields are not present in the MSSM}\label{tab:R_charges_MRSSM}
@@
 \end{align}
-which is not R-invariant because the Weyl fermion $\lambda$ has R-charge $+1$.
+which is not$R$-invariant because the Weyl fermion $\lambda$ has$R$-charge $+1$.
 Giving no mass to the gauginos is phenomenologically not possible.
@@
 \end{align}
-In order to get a R-symmetric mass term on has to choose the R-charge of the new Weyl-spinor $\chi$ to be the opposite of $\lambda$.\\
-This explains the necessity of enlarging the field content if one imposes R-symmetry.\\
+In order to get a$R$-symmetric mass term on has to choose the$R$-charge of the new Weyl-spinor $\chi$ to be the opposite of $\lambda$.\\
+This explains the necessity of enlarging the field content if one imposes$R$-symmetry.\\
 Of course the new Weyl-spinor $\chi$ must have also a superpartner.
@@
 
-\subsection{The R-Symmetric Supersymmetric Quantum Chromodynamcis}
+\subsection{The $R$-Symmetric Supersymmetric Quantum Chromodynamics}
 The subject of this thesis is the phenomenology of the strongly coupling sector of the MRSSM.
-The R-symmetric supersymmetric quantum chromodynamics (RSQCD) is therefore considered closer.
+The $R$-symmetric supersymmetric quantum chromodynamics (RSQCD) is therefore considered closer.
 Its Lagrangian for an arbitrary massless quark reads

### 2016-06-24 figures/MatrixElement/MatrixEl.py

@@ -1,0 +1,47 @@
+# -*- coding: utf-8 -*-
+"""
+C++ code on laptop in WARB-talk
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+t = np.array([], dtype=float);
+m_tree = np.array([], dtype=float);
+m_virt = np.array([], dtype=float);
+
+f_matrix = open('MatrixEl_Virt_uu_susu.txt', 'r')
+discard = f_matrix.readline()
+
+for lines in f_matrix.readlines():
+    t = np.append(t, float(lines.split()[0]))
+    m_tree = np.append(m_tree, float(lines.split()[1]))
+    m_virt = np.append(m_virt, float(lines.split()[2]))
+f_matrix.close()
+
+fig = plt.figure(1,figsize=(10, 9))
+first_window = plt.subplot(111)
+#plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = 22)
+#plt.ylabel(r"$\sigma^{\mathrm{B}}(qq \to \tilde{q}\tilde{q})$ in fb", size = 22)
+plt.xticks(fontsize = 20)
+plt.yticks(fontsize = 20)
+#plt.yscale('log')
+#plt.ticklabel_format(style='sci', axis='x', scilimits=(0,0))
+plt.axis([min(t),max(t),min(m_virt/m_tree),max(m_virt/m_tree)])
+plt.axes(first_window)
+
+#first_window.xaxis.set_major_formatter(FormatStrFormatter('%0.0f'))
+plt.plot(t, m_virt/m_tree, lw=2, ls="-", c='blue')#, label = "MSSM")
+
+#plt.legend(loc='best',prop={'size':22})
+
+#props = dict(boxstyle='round', facecolor='w', alpha=0.5)
+#first_window.text(300, 4, r"$m_{\tilde{g}} = 2000$ GeV", fontsize=22,
+#        verticalalignment='top', bbox=props)
+
+
+plt.show()
+plt.draw()

### 2016-06-25 figures/MatrixEl/MatrixEl.py
plots for virtual Matrixelement over Mandelstam t

@@ -1,0 +1,57 @@
+# -*- coding: utf-8 -*-
+"""
+C++ code on laptop in WARB-talk
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+#from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+t = np.array([], dtype=float);
+matrix_LO_Tree = np.array([], dtype=float);
+matrix_NLO_Tree = np.array([], dtype=float);
+matrix_NLO_Virt = np.array([], dtype=float);
+matrix_NLO_Single = np.array([], dtype=float);
+matrix_NLO_Double   = np.array([], dtype=float);
+
+
+f_matrix = open('MatrixEl_Virt_uu_susu.txt', 'r')
+discard = f_matrix.readline()
+for lines in f_matrix.readlines():
+    t = np.append(t, float(lines.split()[0]))
+    matrix_LO_Tree = np.append(matrix_LO_Tree, float(lines.split()[1]))
+    matrix_NLO_Tree = np.append(matrix_NLO_Tree, float(lines.split()[2]))
+    matrix_NLO_Virt = np.append(matrix_NLO_Virt, float(lines.split()[3]))
+    matrix_NLO_Single = np.append(matrix_NLO_Single, float(lines.split()[4]))
+    matrix_NLO_Double = np.append(matrix_NLO_Double, float(lines.split()[5]))    
+f_matrix.close()
+
+
+fig = plt.figure(1,figsize=(12, 9))
+
+first_window = plt.subplot(111)
+plt.rcParams.update({'font.size': 22})
+plt.xlabel(r"$t$ in $10^6$ GeV$^2$")#, size = 22)
+
+# plot without poles
+plt.ylabel(r"$|\mathcal{M}_{\mathrm{MRSSM}}(uu \to \tilde{u}_L\tilde{u}_R)|^2$")
+plt.axis([min(t/10**6) - 1.1,max(t/10**6) + 1.1,0,0.8])
+plt.plot(t/10**6, matrix_LO_Tree, lw=2, ls="-", c='black', label = r"$|\mathcal{M}^{\mathrm{B}}_{\mathrm{MRSSM}}|^2$ mit LO $\alpha_s$")
[…]

### 2016-06-26 RSymmetry.tex
Renormalization chapter: new introduction

@@
 
-\subsection{The Minimal$R$-Symmetric Supersymmetric Standard Model}
-If one imposes$R$-symmetry upon the MSSM one is faced with a certain arbitrariness, i.e.
-the choice of the$R$-charges of the chiral superfields.
-A minimal$R$-symmetric extension of the MSSM is the minimal$R$-symmetric supersymmetric Standard Model (MRSSM)\cite{Kribs:2007ac}.
-In this model the$R$-charges are chosen in such a way, that every Standard Model particle has$R$-charge zero.
-Following this one obtains the$R$-charges of all particles which are summed up in table \ref{tab:R_charges_MRSSM}\cite{Diessner:2015bna}.
+\subsection{The Minimal $R$-Symmetric Supersymmetric Standard Model}
+If one imposes $R$-symmetry upon the MSSM one is faced with a certain arbitrariness, i.e.
+the choice of the $R$-charges of the chiral superfields.
+A minimal $R$-symmetric extension of the MSSM is the minimal $R$-symmetric supersymmetric Standard Model (MRSSM)\cite{Kribs:2007ac}.
+In this model the $R$-charges are chosen in such a way, that every Standard Model particle has $R$-charge zero.
+Following this one obtains the $R$-charges of all particles which are summed up in table \ref{tab:R_charges_MRSSM}\cite{Diessner:2015bna}.
 \begin{table}[H]
@@
 \end{align}
-which is not$R$-invariant because the Weyl fermion $\lambda$ has$R$-charge $+1$.
+which is not $R$-invariant because the Weyl fermion $\lambda$ has $R$-charge $+1$.
 Giving no mass to the gauginos is phenomenologically not possible.
@@
 \end{align}
-In order to get a$R$-symmetric mass term on has to choose the$R$-charge of the new Weyl-spinor $\chi$ to be the opposite of $\lambda$.\\
-This explains the necessity of enlarging the field content if one imposes$R$-symmetry.\\
+In order to get a $R$-symmetric mass term on has to choose the $R$-charge of the new Weyl-spinor $\chi$ to be the opposite of $\lambda$.\\
+This explains the necessity of enlarging the field content if one imposes $R$-symmetry.\\
 Of course the new Weyl-spinor $\chi$ must have also a superpartner.

### 2016-06-26 Renormalization.tex
Renormalization chapter: new introduction

@@
 \section{Renormalization of the MRSSM}\label{sec:renMRSSM}
-In order to improve the prediction of cross sections one has to take quantum corrections into account.
+This section discusses the removal of ultraviolet divergences in the amplitude of squark production at 1-loop level in the RSQCD.
+After an introduction and discussion of the regularization schemes, field and mass renormalization constants are calculated in dimensional regularization in the on-shell scheme.
+After that the renormalization constant of the strong gauge coupling $g_s$ is computed in a mixture of $\overline{\mathrm{MS}}$- and zero-momentum subtraction scheme.
+This was done because the gauge coupling of the parton density functions is given in the $\overline{\mathrm{MS}}$-scheme but does not include heavy particles, such as the top-quark or supersymmetric particles in its $\beta$-function.
+However renormalizing these heavy particles in the zero-momentum subtraction implies that the $\beta$-function of $g_s$ is exactly the one from QCD.
+This is shown in section \ref{sec:beta_function}.
+After that a fact already discussed in section \ref{sec:RegSchemeDep} is revisited: the used regularization breaks supersymmetry.
+Section \ref{sec:SUSYrestore} describes the calculation of an extra counterterm which restores supersymmetry.
+Finally the UV-divergent parts of all renormalization constants in the RSQCD are given.
+These might prove useful when someone is to check for UV-finiteness of a Green-function or a physical observable.
+The chapter closes with a discussion of the renormalizes matrix amplitude.
+%In order to improve the prediction of cross sections one has to take quantum corrections into account.
 These are associated with loops in the corresponding Feynman diagrams.
@@
 \\%Furthermore there are collinear singularities with occur when a massless particle splits into two massless collinear particles.\\
-These infinities are not physical and must therefore be removed to get sensible predictions.
+%These infinities are not physical and must therefore be removed to get sensible predictions.
 To this end one regularizes them to extract them from the quantity in question.
@@
 
-\subsection{The Beta Function}
+\subsection{The Beta Function}\label{sec:beta_function}
 The beta function describes the dependence of the gauge coupling $g_s$ upon the energy scale $\mu$.\\
@@
 
-\subsection{Supersymmetry Restoring Counterterm}
+\subsection{Supersymmetry Restoring Counterterm}\label{sec:SUSYrestore}
 As already discussed in section \ref{sec:RegSchemeDep} care is required in terms of supersymmetry restoring when renormalizing  the gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$.
@@
 However at 2-loop-level there is a non-zero $\beta$ function of $g_s$, which has been calculated by \texttt{SARAH}\cite{Staub:2013tta, Staub:2012pb, Staub:2010jh, Staub:2009bi}.
+
+\subsection{The Renormalized Matrix Element}
+After having renormalized the matrix element for squark production all UV-divergences are removed.
+This has been achieved by extending the model file, generated by \texttt{SARAH} with counterterm Feynman rules and the above calculated renormalization constants.
+The derivation of the counterterm Feynman rules has been performed by the author whereas the implementation into the modelfile was mainly done by Philip Dießner, another member of the group.
+The renormalization constants for masses and fields are calculated by \texttt{FormCalc} functions like \textsc{MassRC} and \textsc{FieldRC}\cite{FormCalcManual}.
+Their result has been checked with the above calculated renormalization constants.\\
+Auszug von modelfile\\
+To keep track of all divergences, the calculation has been performed with the option: \textsc{Dimensions} $\to 0$.
+This is the only opportunity in \texttt{FormCalc} to really work in $D$ dimensions, i.e.
+the result contains a quantity $Dminus4$ which equals $-2\epsilon$ in DREG.
+The absolute matrix element coming from \texttt{FormCalc} is given in terms of scalar integrals, like defined in appendix \ref{sec:Passarino}.\\
+To extract infrared divergences \texttt{LoopTools} has been used.
+This  tool provides the function \textsc{SetLambda} which can be set to 0, $-1$ or $-2$ to extract the finite part, single pole or double pole of  scalar integrals.
+This allows for numerically extracting the coefficients of $\epsilon^i$ with $i \in \left\{ 0,-1,-2 \right\}$ of the absolute squared matrix amplitude.
+The respective poles of $|\mathcal{M}^{\mathrm{V}}_{\mathrm{MRSSM}}(uu \to \tilde{u}_L\tilde{u}_R)|^2$ are shown in figure \ref{fig:MatrixElement}.
+In addition the tree-level absolute squared matrix amplitude with leading order $\alpha_s$ is compared with its analogue with next-to-leading order $\alpha_s$ and virtual absolute squared matrix amplitude.
+The latter is  not given analytically.
+All $|\mathcal{M}|^2$ are color and spin averaged in the final state and summed over in the initial state.
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.5]{figures/MatrixElement_Poles.png}
+\includegraphics[scale=.5]{figures/MatrixElement.png}
+\caption{The figure at the top shows the coefficients of $\mathcal{O}(\epsilon^0)$, $\mathcal{O}(\epsilon^{-1})$ and $\mathcal{O}(\epsilon^{-2})$ terms of the absolute squared matrix element of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM as a function of the Mandelstam variable $t$.
+External helicities and colors are averaged.
+The parameters are fixed to $m_{\tilde{q}} = \mu = \unit[1000]{GeV}$, $m_{\tilde{g}} = \unit[2000]{GeV}$, $m_{\sigma} = \unit[5000]{GeV}$ and $\sqrt{s} = \unit[6000]{GeV}$ which is the partnoic center of mass energy.\newline
+The figure at the bottom shows the absolute squared matrix element of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM at tree-level with $\alpha_s = $ from the leading order parton density function $\mathtt{MMHT2014}$\cite{Harland-Lang:2014zoa}, and $\alpha_s = $ from the netxt-to-leading order parton density function as well as the contribution from the virtual absolute squared matrix element.}\label{fig:MatrixElement}
+\end{center}
+\end{figure}

### 2016-06-26 figures/MatrixElement/MatrixEl.py

@@ -1,47 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-C++ code on laptop in WARB-talk
-@author: sebastian
-"""
-
-import numpy as np
-from matplotlib import pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-
-t = np.array([], dtype=float);
-m_tree = np.array([], dtype=float);
-m_virt = np.array([], dtype=float);
-
-f_matrix = open('MatrixEl_Virt_uu_susu.txt', 'r')
-discard = f_matrix.readline()
-
-for lines in f_matrix.readlines():
-    t = np.append(t, float(lines.split()[0]))
-    m_tree = np.append(m_tree, float(lines.split()[1]))
-    m_virt = np.append(m_virt, float(lines.split()[2]))
-f_matrix.close()
-
-fig = plt.figure(1,figsize=(10, 9))
-first_window = plt.subplot(111)
-#plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = 22)
-#plt.ylabel(r"$\sigma^{\mathrm{B}}(qq \to \tilde{q}\tilde{q})$ in fb", size = 22)
-plt.xticks(fontsize = 20)
-plt.yticks(fontsize = 20)
-#plt.yscale('log')
-#plt.ticklabel_format(style='sci', axis='x', scilimits=(0,0))
-plt.axis([min(t),max(t),min(m_virt/m_tree),max(m_virt/m_tree)])
-plt.axes(first_window)
-
-#first_window.xaxis.set_major_formatter(FormatStrFormatter('%0.0f'))
-plt.plot(t, m_virt/m_tree, lw=2, ls="-", c='blue')#, label = "MSSM")
-
-#plt.legend(loc='best',prop={'size':22})
-
-#props = dict(boxstyle='round', facecolor='w', alpha=0.5)
-#first_window.text(300, 4, r"$m_{\tilde{g}} = 2000$ GeV", fontsize=22,
-#        verticalalignment='top', bbox=props)
-
-
-plt.show()
-plt.draw()

### 2016-07-01 Introduction.tex
Introduction, NEXT STEP: REDO PLOTS WITH SQUARK PRODUCTION AT TREE LEVEL WHICH DOES INCLUDE ALSO ud to susd, IN ADITION TO ds to sdsu

@@
-motivation: aesthetic: Coleman-Mandula --> Haag-Lopuszanski-Sohnius-Theorem\\
-plots for exclusion of squarks in specific SUSY scenarios (from Michael) --> R-Symmetry could be possible explanation for that because:\\
-MSSM-Lagrangian --> trafo rules for superfields under R-symm --> forbidden terms in MRSSM (write down Lagrangian for R-symmetric SUSYQCD)\\
-suppression of squark production in MRSSM by less diagrams ($m_{gluino}^{-4}$ suppression at low energies in MRSSM and only $m_{gluino}^{-2}$ suppression in MSSM)\\
-R-charges of all fields (show in diagram!) --> only if R-charges of final / initial particles are zero, a diagram is allowed in R-symm. model\\
-references to build in
-\begin{itemize}
-\item "Matching Squark Pair Production at NLO with Parton Showers" from Gavin, Hangst, Krämer, Mühlleitner,.. for complete treatment of NLO calculation\\
-\item "dIRAC gAUGINOS IN susy - sUPPRESSED jETS + <met sIGNALS: a sNOWMASS wHITEPAPER" FROM kRIBS, mARTIN for Squark production at LO, allude to same result\\
-\item "Dirac Gaugino Masses and supersoft SUSY breaking" from Fox, Weiner, Nelson for the introduction of the MRSSM
-\end{itemize}
+\section{Introduction}
+The Standard Model of particle physics is a quantum field theory which relies on the principle of gauge invariance.
+It describes the world's fundamental particles and the interactions among them.
+It predicts the most accurately measured observables in physics and is therefore considered to be a very successful theory.\\
+Besides these triumphs, it is known to be incomplete for it does, for example, not include dark matter.
+Because of these and other flaws, one studies extensions of the Standard Model.
+One mathematically very appealing extension is the concept of supersymmetry.
+However, besides the provision of a dark matter candidate and elegant solutions of, e.g.
+the hierarchy problem, supersymmetry does not come without problems.
+First of all, supersymmetric particles have not been discovered so far.
+Secondly, there are flaws like the ``SUSY flavor problem''.
+A non-trivial extension of supersymmetry - $R$-symmetry - may explain or solve these issues.
+Imposing supersymmetry and $R$-symmetry on the Standard Model, gives - according to the Haag-Lopuszanski-Sohnius theorem - the maximal symmetry group a reasonable quantum field theory can have.\\
+In this thesis a minimal extension of the Standard Model including supersymmetry and $R$-symmetry - the MRSSM - will be considered.
+More specifically, the production cross section of strongly interacting supersymmetric particles is studied.
+It will turn out that there are significant changes in the production of squarks and gluinos when turning from the Minimal Supersymmetric Standard Model (MSSM) to the Minimal $R$-symmetric Supersymmetric Standard Model (MRSSM).\\
+This thesis starts with summarizing the main aspects of the Standard Model before introducing the concept of supersymmetry and $R$-symmetry.
+Hereby, the relevant models including the minimal extension of the respective symmetry, the MSSM and the MRSSM are introduced.
+Section \ref{sec:SquarkGluinoTree} compares the production cross section of squark and gluinos in both models at tree-level.
+It will turn out that the most striking difference manifests in the channel of squark production.
+Therefore, the rest of the thesis focuses on the next-to-leading order calculation of this process: Section \ref{sec:VirtRealCorr} discusses the golden thread of the calculation of a next-to-leading order cross section including massless external particles before section \ref{sec:renMRSSM} gives detailed information about the renormalization of the MRSSM.
+This includes the explicit form of the required renormalization constants, reaching form the on-shell scheme over a mixture of $\overline{\mathrm{MS}}$- and zero-momentum subtraction scheme to supersymmetry restoring counterterms.
+This section also discusses what the most copious contributions to the renormalized matrix element are.
+The thesis closes with the representation of the next-to-leading order cross section for squark production in the form of $K$-factors.
+
+%motivation: aesthetic: Coleman-Mandula --> Haag-Lopuszanski-Sohnius-Theorem\\
+%plots for exclusion of squarks in specific SUSY scenarios (from Michael) --> R-Symmetry could be possible explanation for that because:\\
+%MSSM-Lagrangian --> trafo rules for superfields under R-symm --> forbidden terms in MRSSM (write down Lagrangian for R-symmetric SUSYQCD)\\
+%suppression of squark production in MRSSM by less diagrams ($m_{gluino}^{-4}$ suppression at low energies in MRSSM and only $m_{gluino}^{-2}$ suppression in MSSM)\\
+%R-charges of all fields (show in diagram!) --> only if R-charges of final / initial particles are zero, a diagram is allowed in R-symm. model\\
+%references to build in
+%\begin{itemize}
+%\item "Matching Squark Pair Production at NLO with Parton Showers" from Gavin, Hangst, Krämer, Mühlleitner,.. for complete treatment of NLO calculation\\
+%\item "dIRAC gAUGINOS IN susy - sUPPRESSED jETS + <met sIGNALS: a sNOWMASS wHITEPAPER" FROM kRIBS, mARTIN for Squark production at LO, allude to same result\\
+%\item "Dirac Gaugino Masses and supersoft SUSY breaking" from Fox, Weiner, Nelson for the introduction of the MRSSM
+%\end{itemize}

### 2016-07-01 NLO.tex
Introduction, NEXT STEP: REDO PLOTS WITH SQUARK PRODUCTION AT TREE LEVEL WHICH DOES INCLUDE ALSO ud to susd, IN ADITION TO ds to sdsu

@@
 Loop integrals are evaluated numerically using \texttt{Looptools}.
-For all three contributions the \texttt{CUBA}-library was used for the phase space and $x_1$ and $x_2$ integration to arrive at the cross sections $\sigma^{\mathrm{B}}$, $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{V}}$.}\label{fig:CalcSetup}
+For all three contributions the \texttt{CUBA}-library was used for the phase space and $x_1$ and $x_2$ integration to arrive at the cross sections $\sigma^{\mathrm{B}}$, $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{V}}$.
+The real corrections have been calculated by Wojciech Kotlarski, another member of the group.}\label{fig:CalcSetup}
 \end{center}

### 2016-07-01 Renormalization.tex
Introduction, NEXT STEP: REDO PLOTS WITH SQUARK PRODUCTION AT TREE LEVEL WHICH DOES INCLUDE ALSO ud to susd, IN ADITION TO ds to sdsu

@@
 This is shown in section \ref{sec:beta_function}.
-After that a fact already discussed in section \ref{sec:RegSchemeDep} is revisited: the used regularization breaks supersymmetry.
-Section \ref{sec:SUSYrestore} describes the calculation of an extra counterterm which restores supersymmetry.
-Finally the UV-divergent parts of all renormalization constants in the RSQCD are given.
-These might prove useful when someone is to check for UV-finiteness of a Green-function or a physical observable.
-The chapter closes with a discussion of the renormalizes matrix amplitude.
+After that, a fact already discussed in section \ref{sec:RegSchemeDep} is revisited: dimensinal regularization breaks supersymmetry.
+Section \ref{sec:SUSYrestore} describes the calculation of an extra counterterm which restores supersymmetry within the renomalization.
+Finally, the UV-divergent parts of all renormalization constants in the RSQCD are given.
+These might prove useful, when someone is to check for UV-finiteness of a Green-function or a physical observable.
+The chapter closes with a discussion of the renormalized matrix amplitude.
 %In order to improve the prediction of cross sections one has to take quantum corrections into account.
@@
 \subsection{Regularization Scheme Dependences}\label{sec:RegSchemeDep}
-To discuss the subject of this and ensuing subsections it is useful to introduce the effective action $\Gamma$.
+To discuss the subject of this and ensuing subsections, it is useful to introduce the effective action $\Gamma$.
 A formal introduction of $\Gamma$ can be found in~\cite{Peskin}.
-In short $\Gamma$ can be viewed as a modification of the classical action $\Gamma_{\mathrm{cl}} = \int \mathcal{L}_{\mathrm{cl}}$ by quantum effects:
+In short $\Gamma$ can be viewed as a generalization of the classical action $\Gamma_{\mathrm{cl}} = \int \mathcal{L}_{\mathrm{cl}}$ by quantum effects:
 \begin{align}
@@
 \end{align}
-This means that in addition to the vertices in the classical Lagrangian new vertices arise due to loop effects.
-As already alluded to loop corrections might a priori not be finite and then need to be rendered finite by the addition of counterterms.
+This means that in addition to the vertices in the classical Lagrangian, new vertices arise due to loop effects.
+As already alluded to, loop corrections might a priori not be finite and then need to be rendered finite by the addition of counterterms.
 For $\mathcal{O}(\hbar)$ corrections one writes
@@
 These counterterms depend on the regularization (and renormalization) scheme.
-If one chooses to work with DREG supersymmetry will not be preserved at 1-loop order, i.e.
+If one chooses to work with DREG, supersymmetry will not be preserved at 1-loop order, i.e.
 $\Gamma^{(\leq 1)}_{\mathrm{DREG}}$ is not supersymmetric.
-To maintain supersymmetry invariance of the renormalized effective action the counterterms will not only consist of supersymmetric counterterms $\Gamma^{(1),\ \mathrm{ct,\ sym}}_{\mathrm{DREG}}$ but also of counterterms restoring supersymmetry $\Gamma^{(1),\ \mathrm{ct,\ trans}}_{\mathrm{DREG}}$.
+To maintain supersymmetry invariance of the renormalized effective action, the counterterms will not only consist of supersymmetric counterterms $\Gamma^{(1),\ \mathrm{ct,\ sym}}_{\mathrm{DREG}}$ but also of counterterms restoring supersymmetry $\Gamma^{(1),\ \mathrm{ct,\ trans}}_{\mathrm{DREG}}$.
 \begin{align}
@@
 \end{align} 
-This equation justifies the label "trans" at the supersymmetry restoring counterterm because it actually describes the transition counterterm from DREG to DRED or vice versa.\\ %This way supersymmetry is preserved by the renormalization constants.\\
-In the case of the MRSSM it will turn out that the only supersymmetry violation comes from corrections associated with the gluon as already alluded to in section \ref{sec:RegSchemes}.
-However supersymmetry restoring will always already be included in $\delta Z^{\mathrm{DREG}}$.
+This equation justifies the label ``trans'' at the supersymmetry restoring counterterm because it actually describes the transition counterterm from DREG to DRED or vice versa.\\ %This way supersymmetry is preserved by the renormalization constants.\\
+In the case of the MRSSM it will turn out that the only supersymmetry violation comes from corrections associated with the gluon, as already alluded to in section \ref{sec:RegSchemes}.
+However, supersymmetry restoring will always already be included in $\delta Z^{\mathrm{DREG}}$.
 Referring to the field renormalization constants from eq.
-\ref{eq:fieldtrafo} this is
+\ref{eq:fieldtrafo}, this is
 \begin{align}
@@
 \ref{eq:GammaCtRestore}.
-The only point where particularly care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms due to different loop diagrams.
+The only point where particularly care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms, due to different loop diagrams.
 Therefore one has to make a difference between these couplings at 1-loop level.
-In order to match $g_s$ to the experimentally measured coupling it is renormalized in the  $\overline{\mathrm{MS}}$-scheme (with an additional manipulation for heavy particles, which will be explained in subsection \ref{sec:RenGaugeCoupling}).
+In order to match $g_s$ to the experimentally measured coupling, it is renormalized in the  $\overline{\mathrm{MS}}$-scheme (with an additional manipulation for heavy particles, which will be explained in subsection \ref{sec:RenGaugeCoupling}).
 The Yukawa coupling $\hat{g}_s$ therefore needs to be added with the difference of the supersymmetry restoring counterterms from the $q\tilde{q}^\dagger\tilde{g}$ vertex and the $q\overline{q}G$ vertex at 1-loop in order to be renormalized in the same way.
@@
 The beta function describes the dependence of the gauge coupling $g_s$ upon the energy scale $\mu$.\\
-Writing down the action of a theory in $D$ dimensions one needs to introduce an energy scale $\mu$ in order to keep the action dimensionless.
-But $\mu$ is no physical parameter and can be absorped into the fields and parameters.
+Writing down the action of a theory in $D$ dimensions, one needs to introduce an energy scale $\mu$ in order to keep the action dimensionless.
+But $\mu$ is no physical parameter but can be absorped into the fields and parameters.
 To this end one defines
@@
 \end{align}
-This is the beta function of QCD first found by Politzer \cite{Politzer:1973fx} Gross and Wilczek \cite{Gross:1973ju}
+This is the beta function of QCD first found by Politzer \cite{Politzer:1973fx} Gross and Wilczek \cite{Gross:1973ju}.
+This means that renormalizing $g_s$ in the way it is, decouples heavy particles from the $\beta$ function and allows to adopt $\alpha_s = \frac{g_s^2}{4\pi}$ from the parton density functions.
 

### 2016-07-01 TreeLevel.tex
up to RSymmetry
Feynman Rules
Introduction, NEXT STEP: REDO PLOTS WITH SQUARK PRODUCTION AT TREE LEVEL WHICH DOES INCLUDE ALSO ud to susd, IN ADITION TO ds to sdsu

@@
-\section{Squark and Gluino Production at Tree Level}
+\section{Squark and Gluino Production at Tree Level}\label{sec:SquarkGluinoTree}
 Comment on sgluon production: which channels, calculate cross section for at least one configuration of masses.\\
@@
 \begin{center}
-\includegraphics[scale=.45]{figures/MRSSM:q+q->sq+sq_mr=2_seperated}
+\includegraphics[scale=.45]{figures/MRSSM_q+q_sq+sq_mr=2_seperated}
 \caption{Hadronic cross section for squark production in the MRSSM at the LHC at $\sqrt{S} = \unit[13]{GeV}$.

### 2016-07-01 Virt_Real.tex
Introduction, NEXT STEP: REDO PLOTS WITH SQUARK PRODUCTION AT TREE LEVEL WHICH DOES INCLUDE ALSO ud to susd, IN ADITION TO ds to sdsu

@@
-\section{Virtual and Real Corrections}
+\section{Virtual and Real Corrections}\label{sec:VirtRealCorr}
 The results calculated in the previous chapter are not the full theoretical predictions for the different processes but only the first term in a perturbation theory of $\alpha_s$.\\

### 2016-07-01 figures/MatrixEl/MatrixEl.py
matrix amplitude plots with self-energy, vertices and boxes contributions

@@ -15,6 +15,9 @@ matrix_NLO_Tree = np.array([], dtype=float);
 matrix_NLO_Virt = np.array([], dtype=float);
 matrix_NLO_Single = np.array([], dtype=float);
 matrix_NLO_Double   = np.array([], dtype=float);
+matrix_NLO_SE = np.array([], dtype=float);
+matrix_NLO_Vertex = np.array([], dtype=float);
+matrix_NLO_Boxes = np.array([], dtype=float);
 
 
 f_matrix = open('MatrixEl_Virt_uu_susu.txt', 'r')
@@ -28,30 +31,73 @@ for lines in f_matrix.readlines():
     matrix_NLO_Double = np.append(matrix_NLO_Double, float(lines.split()[5]))    
 f_matrix.close()
 
+f_SE = open('MatrixEl_SE_uu_susu.txt', 'r')
+discard = f_SE.readline()
+for lines in f_SE.readlines():
+    discard = np.append(discard, float(lines.split()[0]))
+    discard = np.append(discard, float(lines.split()[1]))
+    discard = np.append(discard, float(lines.split()[2]))
+    matrix_NLO_SE = np.append(matrix_NLO_SE, float(lines.split()[3]))
+    discard = np.append(discard, float(lines.split()[4]))
+    discard = np.append(discard, float(lines.split()[5]))    
+f_SE.close()
 
-fig = plt.figure(1,figsize=(12, 9))
+f_Vertex = open('MatrixEl_Vertex_uu_susu.txt', 'r')
+discard = f_Vertex.readline()
+for lines in f_Vertex.readlines():
+    discard = np.append(discard, float(lines.split()[0]))
+    discard = np.append(discard, float(lines.split()[1]))
+    discard = np.append(discard, float(lines.split()[2]))
+    matrix_NLO_Vertex = np.append(matrix_NLO_Vertex, float(lines.split()[3]))
+    discard = np.append(discard, float(lines.split()[4]))
[…]

### 2016-07-02 TreeLevel.tex
TreeLevel SquarkProduction with errors including ALL channels redone

@@
 \section{Squark and Gluino Production at Tree Level}\label{sec:SquarkGluinoTree}
-Comment on sgluon production: which channels, calculate cross section for at least one configuration of masses.\\
-In this chapter the production of strongly interacting supersymmetric particles\footnote{The production of sgluons is excluded from the analysis for their mass is chosen to be too large to significantly produce them.} in the MRSSM is considered.
-The various processes and their associated cross section is compared to their analogues in the MSSM.
+In this chapter, the production of strongly interacting supersymmetric particles\footnote{The production of sgluons is excluded from the analysis for their mass is chosen to be too large to significantly produce them.
+See \cite{GoncalvesNetto:2012nt} for a calculation of sgluon cross section.} in the MRSSM is considered.
+The various processes and their associated cross section are compared to their analogues in the MSSM.\\
+Section \ref{sec:PartProcesses} will give analytic results for the parton reaction before the next section describes how the hadronic cross section is obtained.
+Section ???
+presents the hadronic cross section of all considered processes.
+In particular, squark production is considered more closely.
+This includes the statement of uncertainties of the calculation.
 
@@
 The dashed dotted line shows the cross section of the charged conjugated particles of the dominant channel.\\
+
+\subsection{Results for Squark and Gluino Production at Tree-Level}
 REFER TO Kribs, Martin: SNOWMASS WHITEPAPER\\
@@
 \\
+calculation done by SARAH,...
 The following paragraph discusses fig.
 \ref{fig:TreeXsection}, \ref{fig:TreeLevelSigma_0,9_2} and \ref{fig:TreeXsection5}, i.e.
-the hadronic cross section of all considered processes for three successive mass ratios of the gluino and squark: $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9,\ 2$ and $5$.
-Also the corresponding fraction of final states is shown.\\
+the hadronic cross section of all considered processes for three successive mass ratios of gluino and squark: $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9,\ 2$ and $5$.
+Also, the corresponding fraction of final states is shown.\\
+Note that for the following plots all possible production channels are taken into account.
+This is, for squark and squark-gluino production also the charged conjugated processes, i.e.
+$\tilde{q}^\dagger\tilde{q}^\dagger$ and $\tilde{q}^\dagger\overline{\tilde{g}}$, are included.
+In addition, squark production counts processes involving flavor unlike quarks twice, e.g.
+$ud \to \tilde{u}\tilde{d}$ as the $d$-quark may come from either proton.
+This logic applies also to squark antisquark production through a quark antiquark pair.
 \begin{figure}[!htpb]

### 2016-07-02 figures/WARB_TreeLevel/q+q->sq+sq_fixed_msg_and_msq/MSSM+MRSSM_msg=2000GeV.py

@@ -10,47 +10,8 @@ from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
 
 
 m_squark = np.array([], dtype=float);
-# arrays for MSSM
-sigma3_MSSM_dd = np.array([], dtype=float);
-sigma3_MSSM_du = np.array([], dtype=float);
-sigma3_MSSM_ds = np.array([], dtype=float);
-sigma3_MSSM_dc = np.array([], dtype=float);
-sigma3_MSSM_db = np.array([], dtype=float);
-
-sigma3_MSSM_uu = np.array([], dtype=float);
-sigma3_MSSM_us = np.array([], dtype=float);
-sigma3_MSSM_uc = np.array([], dtype=float);
-sigma3_MSSM_ub = np.array([], dtype=float);
-
-sigma3_MSSM_ss = np.array([], dtype=float);
-sigma3_MSSM_sc = np.array([], dtype=float);
-sigma3_MSSM_sb = np.array([], dtype=float);
-
-sigma3_MSSM_cc = np.array([], dtype=float);
-sigma3_MSSM_cb = np.array([], dtype=float);
-
-sigma3_MSSM_bb = np.array([], dtype=float);
-
-# arrays for MRSSM
-sigma3_MRSSM_dd = np.array([], dtype=float);
-sigma3_MRSSM_du = np.array([], dtype=float);
-sigma3_MRSSM_ds = np.array([], dtype=float);
-sigma3_MRSSM_dc = np.array([], dtype=float);
-sigma3_MRSSM_db = np.array([], dtype=float);
-
-sigma3_MRSSM_uu = np.array([], dtype=float);
-sigma3_MRSSM_us = np.array([], dtype=float);
-sigma3_MRSSM_uc = np.array([], dtype=float);
-sigma3_MRSSM_ub = np.array([], dtype=float);
-
-sigma3_MRSSM_ss = np.array([], dtype=float);
-sigma3_MRSSM_sc = np.array([], dtype=float);
-sigma3_MRSSM_sb = np.array([], dtype=float);
-
-sigma3_MRSSM_cc = np.array([], dtype=float);
-sigma3_MRSSM_cb = np.array([], dtype=float);
-
[…]

### 2016-07-02 figures/WARB_TreeLevel/q+q->sq+sq_fixed_msg_and_msq/MSSM+MRSSM_msq=1000GeV.py

@@ -10,47 +10,8 @@ from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
 
 
 m_gluino = np.array([], dtype=float);
-# arrays for MSSM
-sigma3_MSSM_dd = np.array([], dtype=float);
-sigma3_MSSM_du = np.array([], dtype=float);
-sigma3_MSSM_ds = np.array([], dtype=float);
-sigma3_MSSM_dc = np.array([], dtype=float);
-sigma3_MSSM_db = np.array([], dtype=float);
-
-sigma3_MSSM_uu = np.array([], dtype=float);
-sigma3_MSSM_us = np.array([], dtype=float);
-sigma3_MSSM_uc = np.array([], dtype=float);
-sigma3_MSSM_ub = np.array([], dtype=float);
-
-sigma3_MSSM_ss = np.array([], dtype=float);
-sigma3_MSSM_sc = np.array([], dtype=float);
-sigma3_MSSM_sb = np.array([], dtype=float);
-
-sigma3_MSSM_cc = np.array([], dtype=float);
-sigma3_MSSM_cb = np.array([], dtype=float);
-
-sigma3_MSSM_bb = np.array([], dtype=float);
-
-# arrays for MRSSM
-sigma3_MRSSM_dd = np.array([], dtype=float);
-sigma3_MRSSM_du = np.array([], dtype=float);
-sigma3_MRSSM_ds = np.array([], dtype=float);
-sigma3_MRSSM_dc = np.array([], dtype=float);
-sigma3_MRSSM_db = np.array([], dtype=float);
-
-sigma3_MRSSM_uu = np.array([], dtype=float);
-sigma3_MRSSM_us = np.array([], dtype=float);
-sigma3_MRSSM_uc = np.array([], dtype=float);
-sigma3_MRSSM_ub = np.array([], dtype=float);
-
-sigma3_MRSSM_ss = np.array([], dtype=float);
-sigma3_MRSSM_sc = np.array([], dtype=float);
-sigma3_MRSSM_sb = np.array([], dtype=float);
-
-sigma3_MRSSM_cc = np.array([], dtype=float);
-sigma3_MRSSM_cb = np.array([], dtype=float);
-
[…]

### 2016-07-02 figures/WARB_TreeLevel/MSSM+MRSSM_mr=0,9.py
in plots with gluino/squark mass ratio: factor 2 added to processes like ud to susd

@@ -153,7 +153,7 @@ for lines in f_MSSM1.readlines():
     
     sigma1_MSSM_bb = np.append(sigma1_MSSM_bb, float(lines.split()[15]))
 
-sigma1_MSSM = sigma1_MSSM_dd+sigma1_MSSM_du+sigma1_MSSM_ds+sigma1_MSSM_dc+sigma1_MSSM_db+sigma1_MSSM_uu+sigma1_MSSM_us+sigma1_MSSM_uc+sigma1_MSSM_ub+sigma1_MSSM_ss+sigma1_MSSM_sc+sigma1_MSSM_sb+sigma1_MSSM_cc+sigma1_MSSM_cb+sigma1_MSSM_bb 
+sigma1_MSSM = sigma1_MSSM_dd+2*sigma1_MSSM_du+2*sigma1_MSSM_ds+2*sigma1_MSSM_dc+2*sigma1_MSSM_db+sigma1_MSSM_uu+2*sigma1_MSSM_us+2*sigma1_MSSM_uc+2*sigma1_MSSM_ub+sigma1_MSSM_ss+2*sigma1_MSSM_sc+2*sigma1_MSSM_sb+sigma1_MSSM_cc+2*sigma1_MSSM_cb+sigma1_MSSM_bb 
 
 f_MSSM1.close()
 
@@ -193,7 +193,7 @@ for lines in f_MSSM3.readlines():
     
     sigma3_MSSM_bb = np.append(sigma3_MSSM_bb, float(lines.split()[15]))
 
-sigma3_MSSM = sigma3_MSSM_dd+sigma3_MSSM_du+sigma3_MSSM_ds+sigma3_MSSM_dc+sigma3_MSSM_db+sigma3_MSSM_uu+sigma3_MSSM_us+sigma3_MSSM_uc+sigma3_MSSM_ub+sigma3_MSSM_ss+sigma3_MSSM_sc+sigma3_MSSM_sb+sigma3_MSSM_cc+sigma3_MSSM_cb+sigma3_MSSM_bb 
[…]

### 2016-07-02 figures/WARB_TreeLevel/MSSM+MRSSM_mr=2.py

@@ -154,7 +154,7 @@ for lines in f_MSSM1.readlines():
     
     sigma1_MSSM_bb = np.append(sigma1_MSSM_bb, float(lines.split()[15]))
 
-sigma1_MSSM = sigma1_MSSM_dd+sigma1_MSSM_du+sigma1_MSSM_ds+sigma1_MSSM_dc+sigma1_MSSM_db+sigma1_MSSM_uu+sigma1_MSSM_us+sigma1_MSSM_uc+sigma1_MSSM_ub+sigma1_MSSM_ss+sigma1_MSSM_sc+sigma1_MSSM_sb+sigma1_MSSM_cc+sigma1_MSSM_cb+sigma1_MSSM_bb 
+sigma1_MSSM = sigma1_MSSM_dd+2*sigma1_MSSM_du+2*sigma1_MSSM_ds+2*sigma1_MSSM_dc+2*sigma1_MSSM_db+sigma1_MSSM_uu+2*sigma1_MSSM_us+2*sigma1_MSSM_uc+2*sigma1_MSSM_ub+sigma1_MSSM_ss+2*sigma1_MSSM_sc+2*sigma1_MSSM_sb+sigma1_MSSM_cc+2*sigma1_MSSM_cb+sigma1_MSSM_bb 
 
 f_MSSM1.close()
 
@@ -194,7 +194,7 @@ for lines in f_MSSM3.readlines():
     
     sigma3_MSSM_bb = np.append(sigma3_MSSM_bb, float(lines.split()[15]))
 
-sigma3_MSSM = sigma3_MSSM_dd+sigma3_MSSM_du+sigma3_MSSM_ds+sigma3_MSSM_dc+sigma3_MSSM_db+sigma3_MSSM_uu+sigma3_MSSM_us+sigma3_MSSM_uc+sigma3_MSSM_ub+sigma3_MSSM_ss+sigma3_MSSM_sc+sigma3_MSSM_sb+sigma3_MSSM_cc+sigma3_MSSM_cb+sigma3_MSSM_bb 
[…]

### 2016-07-02 figures/WARB_TreeLevel/rel_weights_mr=0.9_MSSM+MRSSM.py

@@ -178,7 +178,7 @@ for lines in f_MRSSM1.readlines():
     
     sigma1_MRSSM_bb = np.append(sigma1_MRSSM_bb, float(lines.split()[15]))
 
-sigma1_MRSSM = sigma1_MRSSM_dd+sigma1_MRSSM_du+sigma1_MRSSM_ds+sigma1_MRSSM_dc+sigma1_MRSSM_db+sigma1_MRSSM_uu+sigma1_MRSSM_us+sigma1_MRSSM_uc+sigma1_MRSSM_ub+sigma1_MRSSM_ss+sigma1_MRSSM_sc+sigma1_MRSSM_sb+sigma1_MRSSM_cc+sigma1_MRSSM_cb+sigma1_MRSSM_bb 
+sigma1_MRSSM = sigma1_MRSSM_dd+2*sigma1_MRSSM_du+2*sigma1_MRSSM_ds+2*sigma1_MRSSM_dc+2*sigma1_MRSSM_db+sigma1_MRSSM_uu+2*sigma1_MRSSM_us+2*sigma1_MRSSM_uc+2*sigma1_MRSSM_ub+sigma1_MRSSM_ss+2*sigma1_MRSSM_sc+2*sigma1_MRSSM_sb+sigma1_MRSSM_cc+2*sigma1_MRSSM_cb+sigma1_MRSSM_bb 
 
 f_MRSSM1.close()
 
@@ -218,7 +218,7 @@ for lines in f_MRSSM3.readlines():
     
     sigma3_MRSSM_bb = np.append(sigma3_MRSSM_bb, float(lines.split()[15]))
 
-sigma3_MRSSM = sigma3_MRSSM_dd+sigma3_MRSSM_du+sigma3_MRSSM_ds+sigma3_MRSSM_dc+sigma3_MRSSM_db+sigma3_MRSSM_uu+sigma3_MRSSM_us+sigma3_MRSSM_uc+sigma3_MRSSM_ub+sigma3_MRSSM_ss+sigma3_MRSSM_sc+sigma3_MRSSM_sb+sigma3_MRSSM_cc+sigma3_MRSSM_cb+sigma3_MRSSM_bb 
[…]

### 2016-07-02 figures/WARB_TreeLevel/rel_weights_mr=5_MSSM+MRSSM.py

@@ -154,7 +154,7 @@ for lines in f_MRSSM1.readlines():
     
     sigma1_MRSSM_bb = np.append(sigma1_MRSSM_bb, float(lines.split()[15]))
 
-sigma1_MRSSM = sigma1_MRSSM_dd+sigma1_MRSSM_du+sigma1_MRSSM_ds+sigma1_MRSSM_dc+sigma1_MRSSM_db+sigma1_MRSSM_uu+sigma1_MRSSM_us+sigma1_MRSSM_uc+sigma1_MRSSM_ub+sigma1_MRSSM_ss+sigma1_MRSSM_sc+sigma1_MRSSM_sb+sigma1_MRSSM_cc+sigma1_MRSSM_cb+sigma1_MRSSM_bb 
+sigma1_MRSSM = sigma1_MRSSM_dd+2*sigma1_MRSSM_du+2*sigma1_MRSSM_ds+2*sigma1_MRSSM_dc+2*sigma1_MRSSM_db+sigma1_MRSSM_uu+2*sigma1_MRSSM_us+2*sigma1_MRSSM_uc+2*sigma1_MRSSM_ub+sigma1_MRSSM_ss+2*sigma1_MRSSM_sc+2*sigma1_MRSSM_sb+sigma1_MRSSM_cc+2*sigma1_MRSSM_cb+sigma1_MRSSM_bb 
 
 f_MRSSM1.close()
 
@@ -194,7 +194,7 @@ for lines in f_MRSSM3.readlines():
     
     sigma3_MRSSM_bb = np.append(sigma3_MRSSM_bb, float(lines.split()[15]))
 
-sigma3_MRSSM = sigma3_MRSSM_dd+sigma3_MRSSM_du+sigma3_MRSSM_ds+sigma3_MRSSM_dc+sigma3_MRSSM_db+sigma3_MRSSM_uu+sigma3_MRSSM_us+sigma3_MRSSM_uc+sigma3_MRSSM_ub+sigma3_MRSSM_ss+sigma3_MRSSM_sc+sigma3_MRSSM_sb+sigma3_MRSSM_cc+sigma3_MRSSM_cb+sigma3_MRSSM_bb 
[…]

### 2016-07-02 figures/Contour_Plots/MRSSM_TreeLevel_qq_sqsq.py
improved squark contour plot in MRSSM

@@ -21,12 +21,12 @@ def contourdata():
     """
     
     """
-    mass = np.linspace(100, 2000, num=N)
-    mass = np.linspace(100, 2000, num=N)
+    mass_sq = np.linspace(100, 2000, num=N)
+    mass_glu = np.linspace(100, 3000, num=N)
     # note reverse ordering for yi and xi because of the way   
     # shape works in numpy                                                  
-    sigma = nans((len(mass),len(mass)))  
-    myfile = open('MRSSM_3_qq_sqsq.txt', 'r')     
+    sigma = nans((len(mass_sq),len(mass_glu)))  
+    myfile = open('MRSSM_3_qq_sqLsqR.txt', 'r')     
     i = 0
     for line in myfile:
         data = line.split()
@@ -35,6 +35,7 @@ def contourdata():
         i += 1   
     myfile.close()
     
+    v = 10**np.linspace(-1, 7, 9, endpoint=True)
     fig = plt.figure(1,figsize=(9, 8)) 
     ax1 = plt.axes()
     font_size = 18
@@ -42,8 +43,8 @@ def contourdata():
     plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
     plt.xticks(fontsize = font_size)
     plt.yticks(fontsize = font_size)
-    cf=ax1.contourf(mass, mass, sigma, norm = LogNorm())
-    levels1 = [0.1, 1, 10**3, 10**4, 10**5, 10**6]
+    cf=ax1.contourf(mass_sq, mass_glu, sigma, v, norm = LogNorm(), vmin=1, vmax =10**6)
+    levels1 = [1, 10**3, 10**4, 10**5, 10**6]
     cl1 = plt.contour(cf, levels=levels1,
                   colors='k',
                   linewidths=(1,),
@@ -59,9 +60,12 @@ def contourdata():
                   linestyles='dashed',
                   linewidths=(1,),
                   hold='on')
-    plt.clabel(cl2, fmt='%2.1f', colors='k', fontsize = font_size)
-    plt.clabel(cl3, fmt='%2.1f', colors='k', fontsize = font_size)
-    cbar = fig.colorbar(cf, orientation='horizontal')
+    manual_locations2 = [(1000.0, 2500.0), (1000.0, 1000.0)]              
+    manual_locations3 = [(1000.0, 2000.0), (1000.0, 1400.0)]
[…]

### 2016-07-02 figures/Contour_Plots/MSSM_TreeLevel_qq_sqsq.py
countour plot squark masses MSSM

@@ -21,12 +21,12 @@ def contourdata():
     """
     
     """
-    mass = np.linspace(100, 2000, num=N)
-    mass = np.linspace(100, 2000, num=N)
+    mass_sq = np.linspace(100, 2000, num=N)
+    mass_glu = np.linspace(100, 3000, num=N)
     # note reverse ordering for yi and xi because of the way   
     # shape works in numpy                                                  
-    sigma = nans((len(mass),len(mass)))  
-    myfile = open('MSSM_1_qqbar_sqsqdagger.txt', 'r') 
+    sigma = nans((len(mass_sq),len(mass_glu)))  
+    myfile = open('MSSM_3_qq_sqsq.txt', 'r') 
     i = 0
     for line in myfile:
         data = line.split()
@@ -35,6 +35,7 @@ def contourdata():
         i += 1   
     myfile.close()
     
+    v = 10**np.linspace(-1, 7, 9, endpoint=True)
     fig = plt.figure(1,figsize=(9, 8)) 
     ax1 = plt.axes()
     font_size = 18
@@ -42,8 +43,8 @@ def contourdata():
     plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
     plt.xticks(fontsize = font_size)
     plt.yticks(fontsize = font_size)
-    cf=ax1.contourf(mass, mass, sigma, norm = LogNorm())
-    levels1 = [0.1, 1, 10**3, 10**4, 10**5, 10**6]
+    cf=ax1.contourf(mass_sq, mass_glu, sigma, v, norm = LogNorm(), vmin=1, vmax =10**6)
+    levels1 = [1, 10**3, 10**4, 10**5, 10**6]
     cl1 = plt.contour(cf, levels=levels1,
                   colors='k',
                   linewidths=(1,),
@@ -59,9 +60,11 @@ def contourdata():
                   linestyles='dashed',
                   linewidths=(1,),
                   hold='on')
-    plt.clabel(cl2, fmt='%2.1f', colors='k', fontsize = font_size)
-    plt.clabel(cl3, fmt='%2.1f', colors='k', fontsize = font_size)
-    cbar = fig.colorbar(cf, orientation='horizontal')
+    manual_locations2 = [(1700.0, 1500.0), (1250.0, 1500.0)]              
+    manual_locations3 = [(1300.0, 1500.0), (1500.0, 1500.0)]              
[…]

### 2016-07-04 Appendix.tex
uncertainties for squark production in table

@@
 \end{tikzpicture}
-\caption{In the Feynman diagrams of the propagators the momentum is flowing from the right to the left hand side.\newline
+\caption{In the Feynman diagrams of the propagators the momentum is flowing from the right to the left hand side. The gluon propagator is given in Feynman gauge.\newline
 In the Feynman diagrams of the vertices all momenta flow towards the vertex, i.e. in diagram 9 $-p_1$ is flowing towards the vertex.\newline
-The indices $A,B \in \left\{ L,R \right\}$ label the left/right "handedness" of the squarks.
+The indices $A,B \in \left\{ L,R \right\}$ label the left/right ``handedness'' of the squarks.
 The indices $i,j=1,2,3$ are the color indices in the (anti)fundamental representation where $a,b,c,\hdots = 1,\hdots,8$ are the color indices of the adjoint representation.}\label{fig:firstFeynmanRules}

### 2016-07-04 MSSM.tex
uncertainties for squark production in table

@@
 gauge symmetries ``cannot by combined in any but the trivial way''\cite{Pelc:1996vg}.
-Ergo the symmetry groups of the Standard Model are the most general ones.\\
+Ergo, the symmetry groups of the Standard Model are the most general ones.\\
 This statement was corrected by the Haag-Lopuszanski-Sohnius theorem \cite{Haag:1974qh} which weakened the condition of the quantum field theory by allowing also for anticommuting symmetry generators.
 This is, by introducing the generators $Q_\alpha$ and $\overline{Q}^{\dot{\alpha}}$ with $\alpha, \dot{\alpha} \in \left\{ 1,2 \right\}$, the Poincare-algebra eq.
-\eqref{eq:PoincareAlgebra} can be nontrivially extended to the so called superalgebra (see appendix \eqref{sec:2spinor_notation} for the definition of the $\sigma$-matrices):
+\eqref{eq:PoincareAlgebra} can be nontrivially extended to the so called superalgebra (see Appendix \eqref{sec:2spinor_notation} for the definition of the $\sigma$-matrices):
 \begin{align}
@@
 The superfields\footnote{Superfield are throughout this thesis labeled with a hat.} relevant for the MSSM are the chiral superfield $\hat{\Phi}$, the antichiral superfield $\hat{\overline{\Phi}}$ and the vector superfield $\hat{V}$.
-Chiral superfields are defined by the restriction $\overline{\mathcal{D}}_{\dot{\alpha}}\hat{\Phi} = 0$, antichiral superfields by $\mathcal{D}_\alpha\hat{\overline{\Phi}} = 0$ (see appendix \ref{sec:AnticommNumbers} for the definition of chiral covariant derivatives) and vector superfields by the condition of being real $\hat{V}^\dagger = \hat{V}$.\\
+Chiral superfields are defined by the restriction $\overline{\mathcal{D}}_{\dot{\alpha}}\hat{\Phi} = 0$, antichiral superfields by $\mathcal{D}_\alpha\hat{\overline{\Phi}} = 0$ (see Appendix \ref{sec:AnticommNumbers} for the definition of chiral covariant derivatives) and vector superfields by the condition of being real $\hat{V}^\dagger = \hat{V}$.\\
 All superfields can be decomposed into component fields on Minkowski space. The component decomposition of the above fields read\footnote{For tho vector superfield Wess-Zumino-gauge is applied.}
@@
 The third column shows the representation (for $SU(3)_C$ and $SU(2)_L$) in which the fields transform and in which the generator in the covariant derivative needs to be inserted as well as the charges of the fields for $U(1)_Y$.
-For $SU(3)_C$ the ``8'' refers to the adjoint representation (see appendix \ref{sec:coloralgebra}), the ``3'' to the fundamental and the ``3$^\ast$'' to the antifundamental representation $T^a_{antifund} = -\frac{\lambda^a}{2}$.
+For $SU(3)_C$ the ``8'' refers to the adjoint representation (see Appendix \ref{sec:coloralgebra}), the ``3'' to the fundamental and the ``3$^\ast$'' to the antifundamental representation $T^a_{antifund} = -\frac{\lambda^a}{2}$.
 For $SU(2)_L$ ``3'' refers to the adjoint representation and ``2'' to the fundamental representation.
@@
 \eqref{eq:L_MSSM} and the softly breaking part of the Lagrangian in the last line of eq.
-\eqref{eq:L_MSSM} which will be discussed in \ref{sec:SUSYBreaking}, there is a superpotential $W_{\mathrm{MSSM}}$:
+\eqref{eq:L_MSSM} which will be discussed in section \ref{sec:SUSYBreaking}, there is a superpotential $W_{\mathrm{MSSM}}$:
 \begin{align}
@@
 As in the Standard Model this spontaneous symmetry breaking and the presence of Yukawa-terms (first three terms of eq.
-\eqref{eq:W_MSSM}) lead to masses of the fermions.\footnote{Note the sum convention of $SU_{\mathrm{L}}(2)$ doublets: $\hat{H}_u \hat{Q} =  (\hat{H}_u)_{\alpha}\hat{Q}_\beta \epsilon^{\alpha\beta}$ to ensure gauge invariance (see appendix \ref{sec:2spinor_notation} for the definition of $\epsilon^{\alpha\beta}$).} Apart from that there are also other terms like quark-squark-higgsino interactions.
+\eqref{eq:W_MSSM}) lead to masses of the fermions.\footnote{Note the sum convention of $SU_{\mathrm{L}}(2)$ doublets: $\hat{H}_u \hat{Q} =  (\hat{H}_u)_{\alpha}\hat{Q}_\beta \epsilon^{\alpha\beta}$ to ensure gauge invariance (see Appendix \ref{sec:2spinor_notation} for the definition of $\epsilon^{\alpha\beta}$).} Apart from that there are also other terms like quark-squark-higgsino interactions.
 In addition there is the $\mu$-term which is responsible for Higgsino and Higgs masses.\\
 
-\subsubsection{Supersymmetry Breaking and Mass Eigenstates}\ref{sec:SUSYBreaking}
-In order to explain why supersymmetric particles have not been found so far supersymmetry has to be broken.
+\subsubsection{Supersymmetry Breaking and Mass Eigenstates}\label{sec:SUSYBreaking}
+In order to explain why supersymmetric particles have not been found so far, supersymmetry has to be broken.
 Like in electroweak symmetry breaking supersymmetry is preserved at some high energy scale but its vacuum state is not supersymmetric.

### 2016-07-04 NLO.tex
uncertainties for squark production in table

@@
 From eq.
-\ref{eq:propagator} one can read off the physical mass $m^2$ of the particle which is associated with the field $\phi$.
+\eqref{eq:propagator} one can read off the physical mass $m^2$ of the particle which is associated with the field $\phi$.
 It is determined as the value of $p^2$ where the propagator has a pole, i.e.
@@
 \end{align}
-Close to the pole the denominator of eq. \ref{eq:propagator} can by expanded like
+Close to the pole the denominator of eq. \eqref{eq:propagator} can by expanded like
 \begin{align}
@@
 One can decompose it into an amputated $(n+m)$-point function and "full" propagators like written in eq.
-\ref{eq:propagator} and depicted in fig.
+\eqref{eq:propagator} and depicted in fig.
 \ref{fig:fullpropagator}.
@@
 \end{align}
-for the full propagators one notices the same singularity as in eq. \ref{eq:LSZ}. If one now compares the coefficients of these poles in eq. \ref{eq:LSZ} one finds
+for the full propagators one notices the same singularity as in eq. \eqref{eq:LSZ}. If one now compares the coefficients of these poles in eq. \eqref{eq:LSZ} one finds
 \begin{figure}[!htbp]

### 2016-07-04 Renormalization.tex
uncertainties for squark production in table

@@
 Referring to the field renormalization constants from eq.
-\ref{eq:fieldtrafo}, this is
+\eqref{eq:fieldtrafo}, this is
 \begin{align}
@@
 Note the sign within this definition in comparison to eq.
-\ref{eq:GammaCtRestore}.
+\eqref{eq:GammaCtRestore}.
 The only point where particularly care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms, due to different loop diagrams.
@@
 where $Z$ and $o$ are defined by the multiplicative renormalization transformation, introduced in eq.
-\ref{eq:fieldtrafo} and \ref{eq:fieldtrafo}.
+\eqref{eq:fieldtrafo} and \eqref{eq:fieldtrafo}.
 The field and mass renormalization constants have been calculated in DREG in the on-shell scheme.
 This has the advantage that when turning to the cross section no manipulation of the Green function to the S-matrix element has to be done, see section \ref{sec:LSZ}.\\
-The calculation has partially been performed by hand but was always checked with the mathematica output generated by the packages  \texttt{FeynArts} \cite{Hahn:2000} and \texttt{FormCalc} \cite{ChokoufeNejad:2013qja, Hahn:1998yk}.
+The calculation has partially been performed by hand but was always checked with the mathematica output generated by the packages  \texttt{FeynArts} \cite{Hahn:2000} and \texttt{FormCalc} \cite{ChokoufeNejad:2013qja, Hahn:1998yk} which used a model file generated by \texttt{SARAH}\cite{Staub:2013tta, Staub:2012pb, Staub:2010jh, Staub:2009bi}.\\
+The renormalization constants are given in terms of Passarino-Veltman integrals whose definition may be found in Appendix \ref{sec:Passarino}.
 
@@
 Note further that the term $\frac{1}{2}$ from eq.
-\ref{eq:QuarkSE} has vanished because it has been absorbed in $B_0(p^2,0,0)|_{p^2 \to 0}$.\\
+\eqref{eq:QuarkSE} has vanished because it has been absorbed in $B_0(p^2,0,0)|_{p^2 \to 0}$.\\
 Doing the same calculation in DRED one finds that this very term $\frac{1}{2}$ is absent. Therefore the transition renormalization constant between DREG and DRED is given by
@@
 \end{align}
-The left-handed part $\lambda^a$ is associated with the superpartner of the gluon and therefore the "actual" gluino whereas the right-handed part $\overline{\chi}^a$ was introduced to assign a Dirac-mass to the gluino and may be referred to as the octino.\\
-From the Lagrangian \ref{eq:L_RSQCD} one can see that the couplings of the two particles are quite distinct.
+The left-handed part $\lambda^a$ is associated with the superpartner of the gluon and therefore the ``actual'' gluino whereas the right-handed part $\overline{\chi}^a$ was introduced to assign a Dirac-mass to the gluino and may be referred to as the octino.\\
+From the Lagrangian \eqref{eq:L_RSQCD} one can see that the couplings of the two particles are quite distinct.
 This is reflected by different field renormalization constants of the left- and right-handed part of the gluino.
@@
 \end{align}
-Where $\delta Z^R_{\tilde{g}}$ drops out already in $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ as the octino does neither couple to quarks nor to squarks the renormalization constant for the actual gluino $\delta Z^L_{\tilde{g}}$ drops out when $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ and $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}}$ are added.
+Where $\delta Z^R_{\tilde{g}}$ drops out already in $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ as the octino does neither couple to quarks nor to squarks, the renormalization constant of the actual gluino $\delta Z^L_{\tilde{g}}$ drops out when $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ and $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}}$ are added.
 This is also true in a more general case, i.e.
@@
 The term in the curved brackets of eq.
-\ref{eq:qqGlight} corresponds to the first diagram in fig.
+\eqref{eq:qqGlight} corresponds to the first diagram in fig.
 \ref{fig:GaugeCouplingCorrection} whereas the term with the prefactor $C(A)$ corresponds to the second diagram.
@@
 where the definition of the beta function $\frac{\partial g_s}{\partial\ln\mu}$ has been inserted.
-Equation \ref{eq:beta_func} serves to calculate $\beta(g_s,\epsilon)$.
+Equation \eqref{eq:beta_func} serves to calculate $\beta(g_s,\epsilon)$.
 By equating coefficients and using the shortcuts
@@
 In doing so one needs the already calculated transition counterterms of the quark, squark and gluino from eq.
-\ref{eq:QuarkSC}, \ref{eq:SquarkSC} and \ref{eq:GluinoSC}
+\eqref{eq:QuarkSC}, \eqref{eq:SquarkSC} and \eqref{eq:GluinoSC}
 as well as the transition counterterm of the gluon.
@@
 With the definition of $\Gamma^{\mathrm{(1),ct,trans}}_{\mathrm{DREG}}$ in eq.
-\ref{eq:GammaCtRestore} one obtains
+\eqref{eq:GammaCtRestore} one obtains
 \begin{align}
@@
 \end{align}
-In short this means that the gauge coupling $g_s$ is renormalized with $\delta g_s$ given in \ref{eq:deltaGs} and the Yukawa coupling $\hat{g}_s$ is renormilzed with $\delta \hat{g}_s = \delta g_s + \delta g_s^{\mathrm{restore}}$.\\
+In short this means that the gauge coupling $g_s$ is renormalized with $\delta g_s$ given in \eqref{eq:deltaGs} and the Yukawa coupling $\hat{g}_s$ is renormilzed with $\delta \hat{g}_s = \delta g_s + \delta g_s^{\mathrm{restore}}$.\\
 The finite correction $\delta g_s^{\mathrm{restore}}$ is the same as in supersymmetric QCD which should not surprise too much as all its contributions originate from loops with gluons.% So there are no new contributions in RSQCD with respect to SQCD.
@@
 $m_{\tilde{g}}$ and $m_{\sigma}^2$ from the softly breaking part of the Lagrangian, eq.
-\ref{eq:L_RSQCD}.
+\eqref{eq:L_RSQCD}.
 In additions it happens that the particle content of RSQCD is such that $\frac{\delta g_s}{g_s} = 0$.
 This means that the $\beta$ function of $g_s$ equals zero at 1-loop-level if one does not choose to decouple heavy particles from the running as has been done in this thesis.
-However at 2-loop-level there is a non-zero $\beta$ function of $g_s$, which has been calculated by \texttt{SARAH}\cite{Staub:2013tta, Staub:2012pb, Staub:2010jh, Staub:2009bi}.
+However at 2-loop-level there is a non-zero $\beta$ function of $g_s$, which has been calculated by \texttt{SARAH}.
 
@@
 the result contains a quantity $Dminus4$ which equals $-2\epsilon$ in DREG.
-The absolute matrix element coming from \texttt{FormCalc} is given in terms of scalar integrals, like defined in appendix \ref{sec:Passarino}.\\
+The absolute matrix element coming from \texttt{FormCalc} is given in terms of scalar integrals, like defined in Appendix \ref{sec:Passarino}.\\
 To extract infrared divergences \texttt{LoopTools} has been used.
@@
 All $|\mathcal{M}|^2$ are color and spin averaged in the final state and summed over in the initial state.
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.5]{figures/MatrixElement_SE_Vertices_Boxes}
+\caption{•}
+\end{center}
+\end{figure}
+
 \begin{figure}[!htpb]

### 2016-07-04 TreeLevel.tex
uncertainties for squark production in table

@@
 In this chapter, the production of strongly interacting supersymmetric particles\footnote{The production of sgluons is excluded from the analysis for their mass is chosen to be too large to significantly produce them.
-See \cite{GoncalvesNetto:2012nt} for a calculation of sgluon cross section.} in the MRSSM is considered.
+See \cite{Choi:2008ub, GoncalvesNetto:2012nt} for a calculation of sgluon cross section.} in the MRSSM is considered.
 The various processes and their associated cross section are compared to their analogues in the MSSM.\\
@@
 \end{figure}
-For the following calculation the top quark is excluded from the initial state as it is too heavy to be significantly present in hadrons. %Therefore its pdf is approximately zero. 
+For the following calculation the top quark is excluded from the initial state as it is too heavy to be significantly present in protons. %Therefore its pdf is approximately zero. 
 For consistency reasons also the stop is excluded from the final states.
@@
 \begin{align}
-& s = (k_a + k_b)^2 = (p_1 + p_2)^2\nonumber\\
-& t = (k_a - p_1)^2 = (k_b - p_2)^2\nonumber\\
-& u = (k_a - p_2)^2 = (k_a - p_2)^2\nonumber\\
-& t_{\tilde{g}} = t - m_{\tilde{g}}^2 && t_{\tilde{q}} = t- m_{\tilde{q}}^2\nonumber\\
-& u_{\tilde{g}} = u - m_{\tilde{g}}^2 && u_{\tilde{q}} = u- m_{\tilde{q}}^2
+& s = (k_a + k_b)^2 = (p_1 + p_2)^2,\nonumber\\
+& t = (k_a - p_1)^2 = (k_b - p_2)^2,\nonumber\\
+& u = (k_a - p_2)^2 = (k_a - p_2)^2,\nonumber\\
+& t_{\tilde{g}} = t - m_{\tilde{g}}^2, && t_{\tilde{q}} = t- m_{\tilde{q}}^2,\nonumber\\
+& u_{\tilde{g}} = u - m_{\tilde{g}}^2, && u_{\tilde{q}} = u- m_{\tilde{q}}^2.
 \end{align}
-Using the Feynman rules in the Appendix \ref{sec:FeynmanRules} one obtains the following sums over absolute squared Feynman amplitudes.
+Applying the Feynman rules in the Appendix \ref{sec:FeynmanRules}, one obtains the following sums\footnote{The sum $\sum$ denotes the summation over all external spins and colors.} over absolute squared Feynman amplitudes:
 \begin{align}
 \sum|\mathcal{M}^B|^2(q_i\overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij}  \left[ 8 N_c C(F) g_s^4\frac{(n_f-1)}{s^2} + 4 N_c C(F) \hat{g}_s^4\frac{1}{t_{\tilde{g}}^2} - 8 C(F)g_s^2\hat{g}_s^2\frac{1}{ t_{\tilde{g}} s} \right] (tu-m_{\tilde{q}}^4)\nonumber\\
- &+ (1-\delta_{ij}) 4 N_c C(F) \hat{g}_s^4\frac{tu-m_{\tilde{q}}^4}{t_{\tilde{g}}^2} \\
+ &+ (1-\delta_{ij}) 4 N_c C(F) \hat{g}_s^4\frac{tu-m_{\tilde{q}}^4}{t_{\tilde{g}}^2}, \\
 \sum|\mathcal{M}^B|^2(GG \to \tilde{q}\tilde{q}^\dagger) &= 4 (n_f-1) g_s^4 \left[ 2N_c^2C(F) \left(1 - 2\frac{t_{\tilde{q}}u_{\tilde{q}}}{s^2} \right)- 2C(F) \right]\nonumber\\
-& \left[ 1 - \epsilon - 2\frac{s m_{\tilde{q}}^2}{t_{\tilde{q}}u_{\tilde{q}}} \left( 1-\frac{s m_{\tilde{q}}^2}{t_{\tilde{q}}u_{\tilde{q}}} \right)\right]\\
+& \left[ 1 - \epsilon - 2\frac{s m_{\tilde{q}}^2}{t_{\tilde{q}}u_{\tilde{q}}} \left( 1-\frac{s m_{\tilde{q}}^2}{t_{\tilde{q}}u_{\tilde{q}}} \right)\right],\\
 \sum|\mathcal{M}^B|^2(q_i q_j \to \tilde{q}\tilde{q}) &= \delta_{ij} 2\hat{g}_s^4 N_c C(F)\left[ \frac{1}{t_{\tilde{g}}^2} + \frac{1}{u_{\tilde{g}}^2} \right] (tu-m_{\tilde{q}}^4)\nonumber\\ 
-& + (1-\delta_{ij}) 4 \hat{g}_s^4 N_c C(F) \frac{tu-m_{\tilde{q}}^4}{t_{\tilde{g}}^2}\\
+& + (1-\delta_{ij}) 4 \hat{g}_s^4 N_c C(F) \frac{tu-m_{\tilde{q}}^4}{t_{\tilde{g}}^2},\\
 \sum|\mathcal{M}^B|^2(q\overline{q} \to \tilde{g}\overline{\tilde{g}}) &=  8 N_c^2 C(F) g_s^4 \left[ \frac{2m_{\tilde{g}}^2 s + t_{\tilde{g}}^2 + u_{\tilde{g}}^2}{s^2} -\epsilon \right]\nonumber\\
@@
 & + 2C(F)(N_c^2-1) \hat{g}^4_s \left( \frac{t_{\tilde{g}}^2}{t_{\tilde{q}}^2} + \frac{u_{\tilde{g}}^2}{u_{\tilde{q}}^2} \right)\\
-%& + 2 \hat{g}_s^4\left[ 2 N_c^2 C(F) \left( \frac{t_{\tilde{g}}^2}{t_{\tilde{q}}^2} + \frac{u_{\tilde{g}}^2}{u_{\tilde{q}}^2} \right) + 2 C(F) \left( 2\frac{m_{\tilde{g}}^2 s}{t_{\tilde{q}}u_{\tilde{q}}} - \frac{t_{\tilde{g}}^2}{t_{\tilde{q}}^2} - \frac{u_{\tilde{g}}^2}{u_{\tilde{q}}^2} \right) \right]\\
+%& + 2 \hat{g}_s^4\left[ 2 N_c^2 C(F) \left( \frac{t_{\tilde{g}}^2}{t_{\tilde{q}}^2} + \frac{u_{\tilde{g}}^2}{u_{\tilde{q}}^2} \right) + 2 C(F) \left( 2\frac{m_{\tilde{g}}^2 s}{t_{\tilde{q}}u_{\tilde{q}}} - \frac{t_{\tilde{g}}^2}{t_{\tilde{q}}^2} - \frac{u_{\tilde{g}}^2}{u_{\tilde{q}}^2} \right) \right],\\
 \sum|\mathcal{M}^B|^2(GG \to \tilde{g}\overline{\tilde{g}}) &=  16 N_c^3 C(F) g_s^4 \left( 1- \frac{t_{\tilde{g}}u_{\tilde{g}}}{s^2} \right)\nonumber\\
-&\left[ \frac{s^2}{t_{\tilde{g}}u_{\tilde{g}}}(1-\epsilon)^2-2(1-\epsilon) + 4\frac{m_{\tilde{g}}^2 s}{t_{\tilde{g}}u_{\tilde{g}}}\left(1-\frac{m_{\tilde{g}}^2 s}{t_{\tilde{g}}u_{\tilde{g}}}  \right) \right]\\
-\sum|\mathcal{M}^B|^2(qg \to \tilde{q}\tilde{g}) &=  2g_s^2\hat{g}_s^2 \left[ 2 N_c^2 C(F) \left(1-2\frac{s u_{\tilde{q}}}{t_{\tilde{g}}^2}\right) - 2C(F) \right] \nonumber\\
-&\left[ (-1+\epsilon)\frac{t_{\tilde{g}}}{s} + \frac{2(m_{\tilde{g}}^2-m_{\tilde{q}}^2)t_{\tilde{g}}}{s u_{\tilde{q}}}\left( 1+\frac{m_{\tilde{q}}^2}{u_{\tilde{q}}} + \frac{m_{\tilde{g}}^2}{t_{\tilde{g}}} \right) \right]
+&\left[ \frac{s^2}{t_{\tilde{g}}u_{\tilde{g}}}(1-\epsilon)^2-2(1-\epsilon) + 4\frac{m_{\tilde{g}}^2 s}{t_{\tilde{g}}u_{\tilde{g}}}\left(1-\frac{m_{\tilde{g}}^2 s}{t_{\tilde{g}}u_{\tilde{g}}}  \right) \right],\\
+\sum|\mathcal{M}^B|^2(qG \to \tilde{q}\tilde{g}) &=  2g_s^2\hat{g}_s^2 \left[ 2 N_c^2 C(F) \left(1-2\frac{s u_{\tilde{q}}}{t_{\tilde{g}}^2}\right) - 2C(F) \right] \nonumber\\
+&\left[ (-1+\epsilon)\frac{t_{\tilde{g}}}{s} + \frac{2(m_{\tilde{g}}^2-m_{\tilde{q}}^2)t_{\tilde{g}}}{s u_{\tilde{q}}}\left( 1+\frac{m_{\tilde{q}}^2}{u_{\tilde{q}}} + \frac{m_{\tilde{g}}^2}{t_{\tilde{g}}} \right) \right].
 \end{align}
-
+The absolute squared amplitudes have been checked with the mathematica output generated by the packages  \texttt{FeynArts} \cite{Hahn:2000} and \texttt{FormCalc} \cite{ChokoufeNejad:2013qja, Hahn:1998yk} which used a model file for the MRSSM generated by \texttt{SARAH}\cite{Staub:2013tta, Staub:2012pb, Staub:2010jh, Staub:2009bi}.\\
 Having calculated the absolute squared Feynman amplitudes one obtains the partonic cross sections (see Appendix \ref{sec:cross_section}) via
@@
 \frac{\mbox{d}^2 \sigma^B}{\mbox{d}t\ \mbox{d}u} =& \frac{K_{ab}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_1^2m_2^2}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_1^2m_2^2)\nonumber\\
-&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum |\mathcal{M}^B|^2\label{eq:sigma_tree}
+&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum |\mathcal{M}^B|^2,\label{eq:sigma_tree}
 \end{align}
-where $m_1$ ($m_2$) is the mass of the first (second) final state particle and $m$ is their arithmetic mean.
-The leading order cross sections are
+where $m_1$ ($m_2$) is the mass of the first (second) final state particle and $m$ is their arithmetic mean. The leading order cross sections then evaluate to
 \begin{align}
@@
 &+ \delta_{ij} \frac{g_s^2\hat{g}_s^2}{16\pi s}  \left[ \left( \frac{4}{27} + \frac{8 m_-^2}{27 s} \right)\beta_{\tilde{q}}  + \left( \frac{8m_{\tilde{g}}^2}{27s} + \frac{8m_-^4}{27s^2} \right)L_1 \right]\nonumber\\
-& + \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} + \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
-\sigma^B(GG \to \tilde{q}\tilde{q}^\dagger) &= \frac{(n_f-1) g_s^4}{16\pi s} \left[ \left(\frac{5}{24} + \frac{31 m_{\tilde{q}}^2}{12s}\right)\beta_{\tilde{q}} + \left( \frac{4m_{\tilde{q}}^2}{3s} + \frac{m_{\tilde{q}}^4}{3s^2} \right) \ln \frac{1-\beta_{\tilde{q}}}{1+\beta_{\tilde{q}}} \right]\\
-\sigma^B(q_i q_j \to \tilde{q}\tilde{q}) &= \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} +  \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
+& + \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} + \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right],\\
+\sigma^B(GG \to \tilde{q}\tilde{q}^\dagger) &= \frac{(n_f-1) g_s^4}{16\pi s} \left[ \left(\frac{5}{24} + \frac{31 m_{\tilde{q}}^2}{12s}\right)\beta_{\tilde{q}} + \left( \frac{4m_{\tilde{q}}^2}{3s} + \frac{m_{\tilde{q}}^4}{3s^2} \right) \ln \frac{1-\beta_{\tilde{q}}}{1+\beta_{\tilde{q}}} \right],\\
+\sigma^B(q_i q_j \to \tilde{q}\tilde{q}) &= \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} +  \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right],\\
 \sigma^B(q \overline{q} \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \frac{16}{9} + \frac{32m_{\tilde{g}}^2}{9s} \right] \beta_{\tilde{g}}\nonumber\\
 & + \frac{\hat{g}_s^2 g_s^2}{16\pi s}  \left[ \left( -\frac{4}{3}-\frac{8m_-^2}{3s} \right)\beta_{\tilde{g}} + \left( \frac{8 m_{\tilde{g}}^2}{3s} + \frac{8m_-^4}{3s^2} \right) L_2 \right]\nonumber\\
-& + \frac{\hat{g}_s^4}{16\pi s} \left[ \left( \frac{32}{27} + \frac{32 m_-^4}{27(m_-^4 + m_{\tilde{q}}^2s)} \right)\beta_{\tilde{g}} - \frac{64m_-^2}{27s}L_2 \right]\label{eq:qqbar_to_sgsgbar}\\
-\sigma^B(GG \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \left( -6 - \frac{51 m_{\tilde{g}}^2}{2s} \right)\beta_{\tilde{g}} + \left( -\frac{9}{2} - \frac{18 m_{\tilde{g}}^2}{s} + \frac{18 m_{\tilde{g}}^4}{s^2} \right)\ln \frac{1-\beta_{\tilde{g}}}{1+\beta_{\tilde{g}}} \right]\\
+& + \frac{\hat{g}_s^4}{16\pi s} \left[ \left( \frac{32}{27} + \frac{32 m_-^4}{27(m_-^4 + m_{\tilde{q}}^2s)} \right)\beta_{\tilde{g}} - \frac{64m_-^2}{27s}L_2 \right],\label{eq:qqbar_to_sgsgbar}\\
+\sigma^B(GG \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \left( -6 - \frac{51 m_{\tilde{g}}^2}{2s} \right)\beta_{\tilde{g}} + \left( -\frac{9}{2} - \frac{18 m_{\tilde{g}}^2}{s} + \frac{18 m_{\tilde{g}}^4}{s^2} \right)\ln \frac{1-\beta_{\tilde{g}}}{1+\beta_{\tilde{g}}} \right],\\
 \sigma^B(q G \to \tilde{q} \tilde{g}) &= \frac{g_s^2\hat{g}_s^2}{16\pi s} \left[ \frac{\kappa}{s}\left( -\frac{7}{9} - \frac{32 m_{-}^2}{9s} \right) + \left( -\frac{8m_-^2}{9s} + \frac{2m_{\tilde{q}}^2m_-^2}{s^2} + \frac{8 m_-^4}{9s^2} \right)L_3\right.\nonumber\\
-&+\left. \left( -1-\frac{2m_-^2}{s} + \frac{2m_{\tilde{q}}m_-^2}{s^2} \right)L_4 \right]
+&+\left. \left( -1-\frac{2m_-^2}{s} + \frac{2m_{\tilde{q}}m_-^2}{s^2} \right)L_4 \right],
 \end{align}
@@
 \end{align}
-are used. In the following the considered processes of the MRSSM are compared to those of the MSSM.
+have been used. In the following, the considered processes of the MRSSM are compared to those of the MSSM.
 
@@
 \subsubsection*{The process $GG \to \tilde{q}\tilde{q}^\dagger$}
-This process has the same cross section as in the MSSM for also in the MSSM only like chirality squark and antisquark $\tilde{q}_A\tilde{q}_A^\dagger$ with $A \in {L,R}$ can be produced.
+This process has the same cross section as in the MSSM for also in the MSSM only like chirality squark and antisquark $\tilde{q}_A\tilde{q}_A^\dagger$ with $A \in \left\{L,R\right\}$ can be produced.
 
@@
 This is because gluino and antigluino are distinguishable particles.
-Still in comparison to the MSSM cross section \cite[p.9]{Beenakker:1996ch} only the first line in \ref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines originate from an $t$ or $u$ channel squark which occurs in only one instead of two chiralities.
+Still in comparison to the MSSM cross section \cite[p.9]{Beenakker:1996ch} only the first line in \eqref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines originate from an $t$ or $u$ channel squark which occurs in only one instead of two chiralities.
 Furthermore an interference term from the $t$ and $u$ channel diagram which occurs in the MSSM is absent in the MRSSM.
@@
 This process is exactly the same in the MSSM and MRSSM for the are two differences between the models which exactly cancel each other: Firstly in the MRSSM there is not only the production of a squark and a gluino but also the production of a squark and an antigluino.
-But on the other hand R-charge needs to be conserved which dictates that a "left-handed" squark can only be produced with an antigluino and a "right-handed" squark can only be produced with a gluino (see table \ref{tab:R_charges_MRSSM}).
+But on the other hand R-charge needs to be conserved which dictates that a ``left-hande'' squark can only be produced with an antigluino and a ``right-handed'' squark can only be produced with a gluino (see table \ref{tab:R_charges_MRSSM}).
 \\ 
@@
 eq.
-\ref{eq:PartonicEquality}, one can see the influence of the parton density functions quite nicely: The up-squark production is the dominant contribution to squark production.
+\eqref{eq:PartonicEquality}, one can see the influence of the parton density functions quite nicely: The up-squark production is the dominant contribution to squark production.
 Apart from the solid lines in fig.\ref{fig:TreeXsection} which correspond to the production of first generation squarks, also the cross section of mixed first and second generation (dashed lines) and second generation (dotted lines) squarks is shown.
@@
 \\
-calculation done by SARAH,...
+This section presents hadronic tree-level or (Born) cross sections of squark and gluino production for two colliding protons in both, the MSSM and the MRSSM.\\
+Note that in the following all possible production channels are taken into account.
+This is, for squark and squark-gluino production, also the charged conjugated processes, i.e.
+$\tilde{q}^\dagger\tilde{q}^\dagger$ and $\tilde{q}^\dagger\overline{\tilde{g}}$, are included.
+In addition, squark production counts thoses processes twice which involve flavor unlike quarks, e.g.
+$ud \to \tilde{u}\tilde{d}$ is counted twice as the $d$-quark may come from either proton.
+This logic applies also to squark-antisquark production through a quark-antiquark pair.\\
+The calculations have been performed by a $\texttt{C++}$ code which uses a library containing the absolute squared amplitudes for the processes in question.
+Note that the author has opted for the absolute squared amplitudes and not the partonic cross sections because this allows also for the calculation of partial differential cross section like the one shown in fig.
+???
+at the end of the section.\\
 The following paragraph discusses fig.
@@
 the hadronic cross section of all considered processes for three successive mass ratios of gluino and squark: $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9,\ 2$ and $5$.
-Also, the corresponding fraction of final states is shown.\\
-Note that for the following plots all possible production channels are taken into account.
-This is, for squark and squark-gluino production also the charged conjugated processes, i.e.
-$\tilde{q}^\dagger\tilde{q}^\dagger$ and $\tilde{q}^\dagger\overline{\tilde{g}}$, are included.
-In addition, squark production counts processes involving flavor unlike quarks twice, e.g.
-$ud \to \tilde{u}\tilde{d}$ as the $d$-quark may come from either proton.
-This logic applies also to squark antisquark production through a quark antiquark pair.
+Also, the corresponding fraction of final states is shown.
 \begin{figure}[!htpb]
@@
 For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
-The parton densities and the renormalization and factorization scale are chosen as in fig.
+The parton density functions and the renormalization and factorization scale are chosen as in fig.
 \ref{fig:TreeXsection}.}\label{fig:TreeXsection5}
@@
 The contour plots \ref{fig:ContourTree} underline the already announced difference between squark production in the MRSSM and the MSSM.
-The main difference is a suppression of the cross section for higher gluino masses in the MRSSM.
+While the cross sections for small gluino masses resemble each other closely, the cross section in the MRSSM gets increasingly suppressed with increasing gluino mass.
 \begin{figure}[!htpb]
 \begin{center}
-\includegraphics[scale=.6]{figures/contour_MRSSM_squarks}
-\includegraphics[scale=.6]{figures/contour_MSSM_squarks}
-\caption{Contour plot for squark production cross section including all possible flavors (also charged ) in the MRSSM (top) and MSSM (bottom) }\label{fig:ContourTree}
+\includegraphics[scale=.55]{figures/contour_MRSSM_squarks}
+\includegraphics[scale=.55]{figures/contour_MSSM_squarks}
+\caption{The squark production cross section including five flavors (also including $\tilde{q}^\dagger\tilde{q}^{\prime\dagger}$) in the MRSSM (top) and MSSM (bottom) at the LHC which $\sqrt{S} = \unit[13]{GeV}$.
+The parton density functions and the renormalization and factorization scale are chosen as in fig.
+\ref{fig:TreeXsection}.}\label{fig:ContourTree}
 \end{center}
@@
 The 68\% uncertainty from the central value pdf-set is obtained by performing the calculation with all eigenvector sets of the central value and taking the minimum and maximum at each point as deviations from the calculation with the central set.\\
-The error from the renormalization scale $\mu_R$ and the factorization scale $\mu_F$ is obtained by varying both parameters with a factor of $\frac{1}{2}$ and two.
+The uncertainty from the renormalization scale $\mu_R$ and the factorization scale $\mu_F$ is obtained by varying both parameters with a factor of $\frac{1}{2}$ and two.
 For each parameter combination the cross section has been calculated.
-Out of these nine numbers for each point the minimum and maximum has been chosen to estimate the error originating from the scale.\\
-The total error is then obtained by Gauß's propagation of uncertainties:
+The uncertainty originating from the scale has then been determined by taking the minimum and maximum of these nine numbers for each point.\\
+The total uncertainty is then obtained by Gauß's propagation of uncertainties:
 \begin{align}
@@
 The uncertainty coming from the scale variation has been found much greater than the one from the parton density functions.
-The error from the phase space integration is negligible, i.e.
+The uncertainty from the phase space integration is negligible, i.e.
 $\Delta \sigma_{\mathrm{int}} < 1\text{\textperthousand}$.
+
 \begin{table}
 \begin{center}
-\begin{tabular}{c|c|c|c}\label{tab:MSSMfieldcontent}
-$m_{\tilde{g}}$ \textbackslash $m_{\tilde{q}}$ & 500 & 1000 & 1500\\
+\begin{tabular}{c|c|c|c}
+$m_{\tilde{g}}$ \textbackslash $m_{\tilde{q}}$ & $\unit[500]{GeV}$ & $\unit[1000]{GeV}$ & $\unit[1500]{GeV}$\\
 \hline
-1000 &  &  & \\
-1500 &  &  & \\
-2000 &  &  & \\
+$\unit[1000]{GeV}$ & $934.9_{\pm 27.2\%\ignore{735}\pm 2.1\% \ignore{915}}^{\pm 30.0\% \ignore{1213}\pm 1.2\% \ignore{946}}$ & $102.1_{\pm 29.2\% \ignore{79.0}\pm 2.1\%\ignore{100}}^{\pm 31.2\% \ignore{134}\pm 1.9\% \ignore{104}}$ & $13.12_{\pm 31.6\% \ignore{9.97}\pm 1.7\% \ignore{12.9}}^{\pm 34.1\% \ignore{17.6}\pm 2.1\% \ignore{13.4}}$\\
+$\unit[1500]{GeV}$ & $360.9_{\pm 30.0\% \ignore{282}\pm 2.2\% \ignore{353}}^{\pm 30.5\% \ignore{471}\pm 1.1\% \ignore{365}}$ & $50.52_{\pm 29.5\% \ignore{39.0}\pm 1.9\% \ignore{49.6}}^{\pm 32.4\% \ignore{66.9}\pm 1.7\% \ignore{51.4}}$ & $7.712_{\pm 31.8\% \ignore{5.85}\pm 2.8\% \ignore{7.5}}^{\pm 34.9\% \ignore{10.4}\pm 2.4\% \ignore{7.9}}$\\
+$\unit[2000]{GeV}$ & $165.5_{\pm 28.2\% \ignore{129}\pm 2.1\% \ignore{162}}^{\pm 30.5\% \ignore{216}\pm 0.9\% \ignore{167}}$ & $26.97_{\pm 29.8\%\ignore{20.8}\pm 2.1\% \ignore{26.4}}^{\pm 32.6\%\ignore{35.8} \pm 1.5\% \ignore{27.4}}$ & $4.625_{\pm 31.8\% \ignore{3.51}\pm 1.6\% \ignore{4.55}}^{\pm 34.5\% \ignore{6.22}\pm 1.8\% \ignore{4.71}}$\\
 \end{tabular}
-\caption{Table}
+\caption{MRSSM The uncertainty of the numerical integration is lower than one permille.}
 \end{center}
 \end{table}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c|c|c|c}
+$m_{\tilde{g}}$ \textbackslash $m_{\tilde{q}}$ & $\unit[500]{GeV}$ & $\unit[1000]{GeV}$ & $\unit[1500]{GeV}$\\
+\hline
+$\unit[1000]{GeV}$ & $5257_{\pm 24.6\% \ignore{4196}\pm 1.2\% \ignore{5163}}^{\pm 28.4\% \ignore{6714}\pm 1.8\% \ignore{5319}}$ 
+& $340.4_{\pm 28.4\% \ignore{265}\pm 1.9\% \ignore{334}}^{\pm 31.0\% \ignore{446} \pm 1.6\% \ignore{346}}$ 
+& $33.97_{\pm 30.6\% \ignore{26.0}\pm 1.2\%\ignore{33.5}}^{\pm 33.6\% \ignore{45.4}\pm 2.3\%\ignore{34.7}}$\\
+$\unit[1500]{GeV}$ & $3263_{\pm 25.4\% \ignore{2602}\pm1.8\%\ignore{3205}}^{\pm 27.9\%\ignore{4172}\pm 1.2\%\ignore{3301}}$ 
+& $260.7_{\pm 28.4\%\ignore{203}\pm 2.2\%\ignore{255}}^{\pm 30.8\% \ignore{341}\pm 1.3\% \ignore{264}}$ 
+& $30.46_{\pm 30.7\%\ignore{23.3} \pm 1.9\%\ignore{29.9}}^{\pm  33.2\% \ignore{40.6} \pm 1.8\% \ignore{31.0}}$\\
+$\unit[2000]{GeV}$ & $2179_{\pm 25.6\% \ignore{1735}\pm 1.9\%\ignore{2139}}^{\pm 27.9\% \ignore{2788}\pm 1.1\%\ignore{2204}}$ 
+& $198.1^{\pm 30.7\%\ignore{259} \pm 1.5\%\ignore{201}}_{\pm 28.6\% \ignore{154}\pm 2.1\%\ignore{194}}$ 
+& $25.75^{\pm 33.2\%\ignore{34.3}\pm 1.5\%\ignore{26.2}}_{\pm 30.7\% \ignore{19.7}\pm 2.0\%\ignore{25.3}}$\\
+\end{tabular}
+\caption{MSSM The uncertainty of the numerical integration is lower than one permille.}
+\end{center}
+\end{table}
+
 \begin{figure}[!htpb]
@@
 \includegraphics[scale=.5]{figures/MSSM+MRSSM_msq=1000}
-\caption{add error bars}\label{fig:TreeXsection_fixed_m}
+\caption{Comparison of squark production cross section including five flavors (also including $\tilde{q}^\dagger\tilde{q}^{\prime\dagger}$) in the MSSM and MRSSM at the LHC which $\sqrt{S} = \unit[13]{GeV}$ for fixed gluino mass (top) and fixed squark mass (bottom).
+The parton density functions and the renormalization and factorization scale are chosen as in fig.
+\ref{fig:TreeXsection}.}\label{fig:TreeXsection_fixed_m}
 \end{center}
-\end{figure}\\
+\end{figure}
 As a summary of the comparison between MSSM and MRSSM gluino production one can say, that the gluino production is enhanced in the MRSSM due to distinguishable gluino and antigluino.

### 2016-07-06 Introduction.tex
a lot of changes

@@
 The Standard Model of particle physics is a quantum field theory which relies on the principle of gauge invariance.
-It describes the world's fundamental particles and the interactions among them.
-It predicts the most accurately measured observables in physics and is therefore considered to be a very successful theory.\\
-Besides these triumphs, it is known to be incomplete for it does, for example, not include dark matter.
+It describes the world's fundamental particles and the interactions among them and predicts the most accurately measured observables in physics.\\
+Besides these triumphs, it is known to be incomplete for it does, for example, not include dark matter or a description of gravity.
 Because of these and other flaws, one studies extensions of the Standard Model.
@@
 the hierarchy problem, supersymmetry does not come without problems.
-First of all, supersymmetric particles have not been discovered so far.
+Firstly, supersymmetric particles have not been discovered so far.
 Secondly, there are flaws like the ``SUSY flavor problem''.
-A non-trivial extension of supersymmetry - $R$-symmetry - may explain or solve these issues.
-Imposing supersymmetry and $R$-symmetry on the Standard Model, gives - according to the Haag-Lopuszanski-Sohnius theorem - the maximal symmetry group a reasonable quantum field theory can have.\\
-In this thesis a minimal extension of the Standard Model including supersymmetry and $R$-symmetry - the MRSSM - will be considered.
+$R$-symmetry, a non-trivial extension of supersymmetry, may explain or solve these issues.
+Another motivation to study $R$-symmetry is that, according to the Haag-Lopuszanski-Sohnius theorem, the combination of Poincaré symmetry, supersymmetry and $R$-symmetry is the maximal symmetry group a reasonable quantum field theory can have.\\
+\ignore{Imposing supersymmetry and $R$-symmetry on the Standard Model, gives - according to the Haag-Lopuszanski-Sohnius theorem - the maximal symmetry group a reasonable quantum field theory can have.\\}
+In this thesis a minimal extension of the Standard Model including supersymmetry and \mbox{$R$-symmetry} - the MRSSM - will be considered.
 More specifically, the production cross section of strongly interacting supersymmetric particles is studied.
@@
 This thesis starts with summarizing the main aspects of the Standard Model before introducing the concept of supersymmetry and $R$-symmetry.
-Hereby, the relevant models including the minimal extension of the respective symmetry, the MSSM and the MRSSM are introduced.
-Section \ref{sec:SquarkGluinoTree} compares the production cross section of squark and gluinos in both models at tree-level.
-It will turn out that the most striking difference manifests in the channel of squark production.
+Hereby, the relevant models including the minimal extension associated to the respective symmetry, the MSSM and the MRSSM, are introduced.
+Section \ref{sec:SquarkGluinoTree} compares the production cross section of squark and gluinos in both models at \mbox{tree-level}.
+It will turn out that the most interesting difference manifests in the channel of squark production.
 Therefore, the rest of the thesis focuses on the next-to-leading order calculation of this process: Section \ref{sec:VirtRealCorr} discusses the golden thread of the calculation of a next-to-leading order cross section including massless external particles before section \ref{sec:renMRSSM} gives detailed information about the renormalization of the MRSSM.

### 2016-07-06 NLO.tex
a lot of changes

@@
 All three contributions have to be calculated with next-to-leading parton density functions.\\
-It has been checked that for multiple different and quite distinct choices of the parameters $m_{\tilde{q}}$ and $m_{\tilde{g}}$ the double as well as the single poles of the virtual and real correction cancel up to machine precision.
+It has been checked that for multiple different and quite distinct choices of the parameters $m_{\tilde{q}}$ and $m_{\tilde{g}}$, the double as well as the single poles of the virtual and real correction cancel up to machine precision.
 As the real corrections have been calculated analytically it is possible to quote the double pole.
@@
 Finally the phase space integration is performed by the integration routine "Cuhre" which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}.\\
-Comment on how real corrections are processed.\\
+The computation of the real correction have been done by Wojciech Kotlarski, another member of the group. Comment on how real corrections are processed.\\
 \begin{figure}[!htbp]

### 2016-07-06 RSymmetry.tex
TreeLevel SquarkProduction with errors including ALL channels redone
a lot of changes

@@
 
-\subsection{$R$-Symmetry Transformation}
+\subsection{$R$-Symmetry Transformations}
 For a $N=1$ supersymmetric theory, $R$-symmetry is a global $U(1)$ symmetry.
@@
 \end{align}
-where $\tau$ parametrizes the transformation. This in turn implies that the supersymmetry generators (see eq. \ref{{eq:SUSYGen}}) transform like
+where $\tau$ parametrizes the transformation. This in turn implies that the supersymmetry generators (see eq. \eqref{eq:SUSYGen}) transform like
 \begin{align}
@@
 In this model the $R$-charges are chosen in such a way, that every Standard Model particle has $R$-charge zero.
-Following this one obtains the $R$-charges of all particles which are summed up in table \ref{tab:R_charges_MRSSM}\cite{Diessner:2015bna}.
+Following this one obtains the $R$-charges of all particles which are summed up in table \ref{tab:R_charges_MRSSM}\cite{Diessner:2014ksa}.
 \begin{table}[H]
@@
 & -\sqrt{2}g_s \left( \overline{\tilde{g}}^a P_R (\tilde{g}^b (if^{abc}) \sigma^c) + (\sigma^{\dagger b} (-if^{abc}) \overline{\tilde{g}}^c)P_L\tilde{g}^a \right) \nonumber\\
-& -\frac{m_{\tilde{q}}^2}{2}(|\tilde{q}_L|^2 + |\tilde{q}_R|^2) -m_{\sigma}^2\left|\sigma^a\right|^2  - m_g \overline{\tilde{g}}^a\tilde{g}^a\nonumber\\
-& -\frac{1}{2}\left( g_s \tilde{q}_L^\dagger T^a \tilde{q}_L - g_s \tilde{q}_R T^{\ast a} \tilde{q}_R^\dagger - ig_s\sigma^{\dagger b}f^{abc}\sigma^c + \sqrt{2}m_g(\sigma^a + \sigma^{\dagger a}) \right)^2\label{eq:L_RSQCD}
+& -\frac{m_{\tilde{q}}^2}{2}(|\tilde{q}_L|^2 + |\tilde{q}_R|^2) -m_{\sigma}^2\left|\sigma^a\right|^2  - m_{\tilde{g}} \overline{\tilde{g}}^a\tilde{g}^a\nonumber\\
+& -\frac{1}{2}\left( g_s \tilde{q}_L^\dagger T^a \tilde{q}_L - g_s \tilde{q}_R T^{\ast a} \tilde{q}_R^\dagger - ig_s\sigma^{\dagger b}f^{abc}\sigma^c + \sqrt{2}m_{\tilde{g}}(\sigma^a + \sigma^{\dagger a}) \right)^2\label{eq:L_RSQCD}
 \end{align}
@@
 As already alluded to there are two distinct sgluons with different masses.
-The mass of the pseudoscalar $\sigma_0^a$ is given by the soft breaking parameter $m_{\sigma_0} = m_\sigma$ whereas the mass of the scalar $\phi^0$ is given by
+The mass of the pseudoscalar $\sigma_0^a$ is given by the soft breaking parameter $m_{\sigma_0} = m_\sigma$ whereas the mass of the scalar $\phi_0$ is given by
 \begin{align}
@@
 \end{align}
-The Feynman rules infered from this Lagrangian are given in Appendix \ref{sec:FeynmanRules}.
+The Feynman rules inferred from this Lagrangian are given in Appendix \ref{sec:FeynmanRules}.
 \newpage

### 2016-07-06 Renormalization.tex
a lot of changes

@@
 After that, a fact already discussed in section \ref{sec:RegSchemeDep} is revisited: dimensinal regularization breaks supersymmetry.
-Section \ref{sec:SUSYrestore} describes the calculation of an extra counterterm which restores supersymmetry within the renomalization.
+Section \ref{sec:SUSYrestore} describes the calculation of an additional counterterm which restores supersymmetry within the renomalization.
 Finally, the UV-divergent parts of all renormalization constants in the RSQCD are given.
@@
 \subsubsection*{Dimensional Regularization (DREG)}
-Dimensional regularization(DREG) is a very common procedure for regularizing infinities which was devised by t'Hooft and Veltman~\cite{'tHooft:1972fi}.
-In this scheme loop momenta, gamma- and epsilon-tensors, phase space and fields are defined in $D$ dimensions.
+Dimensional regularization (DREG) is a very common procedure for regularizing infinities which was devised by t'Hooft and Veltman~\cite{'tHooft:1972fi}.
+In this scheme loop momenta, gamma- and epsilon-tensors, phase space and fields are defined in $D$ dimensions\cite{Collins:105730}.
 As in every regularization scheme a parameter with mass dimension needs to be introduced.
-In DREG that is the $\mu$ parameter which ensures that the loop integrals still have mass dimension 4:
+In DREG, that is the $\mu$ parameter which ensures that the loop integrals still have mass dimension four:
 \begin{align}
@@
 \end{align}
-One often writes $D=4-2\epsilon$. Then the divergences of the loop integral manifest in $\frac{1}{\epsilon}$ poles.\\
+If one writes $D=4-2\epsilon$, the divergences of the loop integral manifest in $\frac{1}{\epsilon}$ poles.\\
 However DREG suffers a flaw in supersymmetry.
@@
 Dimensional reduction (DRED) was introduced to rectify the imperfections of DREG, i.e.
-it preserves supersymmetry\footnote{It is not clear if DRED preserves supersymmetry at all orders in perturbation theory but it does preserve supersymmetry at the 1-loop level.}.
-DRED promotes only loop momenta to $D$ dimensions.
-All other quantities which are $D$ dimensional in DREG stay in 4 dimensions.\\
-maybe refer to Collins: Renormalization
+it preserves supersymmetry.\footnote{It is not clear whether DRED preserves supersymmetry at all orders in perturbation theory\cite{Jack:1997sr} but it does preserve supersymmetry at 1-loop level\cite{Hollik:2001cz}.} DRED promotes only loop momenta to $D$ dimensions.
+All other quantities which are $D$ dimensional in DREG stay in 4 dimensions.
+The most important difference is the contraction of the metric tensor with itself equals four
+\begin{align}
+g_{\mu\nu}g^{\mu\nu} = 4,
+\end{align}
+instead of $D$ in dimensional regularization. It has been shown in \cite{Stockinger:2005gx} that DRED can be defined in a mathematically consistent way.
 
@@
 \end{align}
-Equating also the finite terms in $\Gamma^{(1),\ \mathrm{ct,\ sym}}$ in DRED and DREG the choice of the supersymmetry restoring counterterms is fixed by\cite{Varso}:
+Equating also the finite terms in $\Gamma^{(1),\ \mathrm{ct,\ sym}}$ in DRED and DREG the choice of the supersymmetry restoring counterterms is fixed by\cite{Varso, Stockinger:2011gp, Martin:1993yx}:
 \begin{align}
@@
 Therefore one has to make a difference between these couplings at 1-loop level.
-In order to match $g_s$ to the experimentally measured coupling, it is renormalized in the  $\overline{\mathrm{MS}}$-scheme (with an additional manipulation for heavy particles, which will be explained in subsection \ref{sec:RenGaugeCoupling}).
+In order to match $g_s$ to the experimentally measured coupling, it is renormalized in the  $\overline{\mathrm{MS}}$-scheme (with an additional manipulation for heavy particles, which will be explained in section \ref{sec:RenGaugeCoupling}).
 The Yukawa coupling $\hat{g}_s$ therefore needs to be added with the difference of the supersymmetry restoring counterterms from the $q\tilde{q}^\dagger\tilde{g}$ vertex and the $q\overline{q}G$ vertex at 1-loop in order to be renormalized in the same way.
@@
 
-\subsubsection*{The Glunio Self-Energy}
+\subsubsection*{The Gluino Self-Energy}
 The 4-spinor of the gluino comprises two Weyl spinors which describe very different particles.
@@
 \end{align}
-Where $\delta Z^R_{\tilde{g}}$ drops out already in $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ as the octino does neither couple to quarks nor to squarks, the renormalization constant of the actual gluino $\delta Z^L_{\tilde{g}}$ drops out when $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ and $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}}$ are added.
+Where $\delta Z^R_{\tilde{g}}$ drops out already in $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ as the octino does neither couple to quarks nor to squarks.
+The renormalization constant of the actual gluino $\delta Z^L_{\tilde{g}}$ drops out when $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ and $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}}$ are added.
 This is also true in a more general case, i.e.
 the renormalization constants of virtual particles do always drop out.
+This may be understood in the path integral approach of quantum field theory\cite{Peskin}: When considering a certain process, the Green function corresponding to this process, can be expressed as a path integral over fields within the theory.
+The field of virtual particles does not occur next to the path integral measure, in contrast to the fields of external particles.
+This means, that rescaling a field of an inner particle has no influence on the Green function.
+Ergo the field renormalization constants of any virtual particle must always drop out when considering a certain process.
 \begin{figure}[!htbp]
@@
 \end{align}
-Note that the renormalization constants $\delta m_{\tilde{g}}$, $\delta m^2_{\phi^0}$ and $\delta m^2_{\sigma^0}$ are not independent from each other as the masses of the gluino and the two sgluons stam from only two parameters, i.e.
+Note that the renormalization constants $\delta m_{\tilde{g}}$, $\delta m^2_{\phi^0}$ and $\delta m^2_{\sigma^0}$ are not independent from each other as the masses of the gluino and the two sgluons arise  from only two parameters, i.e.
 $m_{\tilde{g}}$ and $m_{\sigma}^2$ from the softly breaking part of the Lagrangian, eq.
@@
 \includegraphics[scale=.5]{figures/MatrixElement_SE_Vertices_Boxes}
-\caption{•}
+\caption{bla}
 \end{center}

### 2016-07-06 Standardmodel.tex
uncertainties for squark production in table
a lot of changes

@@
 Using the cyclic property of the trace and the Dynkin index $T(F)$ defined in eq.
-\eqref{eq:DynkinIndex} in the appendix, one can write down a gauge invariant kinetic term for the gauge vector:
+\eqref{eq:DynkinIndex} in the Appendix, one can write down a gauge invariant kinetic term for the gauge vector:
 \begin{align}
@@
 Listed are the symbol and the name of the particles.
-The labeling of particles has been taken from \cite{Bach}.
+The labeling of particles has been taken from \cite{Diessner, Bach}.
 The shortcut charged lepton refers to electrically charged leptons.}\label{tab:generations}
@@
 In fact, the Higgs particle originates from a $SU(2)_L$-doublet.
-This is not given here because within a certain gauge only the Higgs particle is a real particle.
-}\label{tab:SMfieldcontent}
+This is not given here because only the Higgs particle, is a real particle.
+The other degrees of freedom of the doublet can be absorbed into the longitudinally polarized degrees of freedom of the three massive gauge bosons, see section \ref{sec:EWSB}.}\label{tab:SMfieldcontent}
 \end{center}
@@
 \hlinewd{2pt}
-group & coupling constant & gauge field & coupling constant & gauge field & Particle\\
+Group & Coupling Constant & Gauge Field & Coupling Constant & Gauge Field & Particle\\
 \hlinewd{2pt}
-$SU(3)_C$ & $g_s$ & $G^a_\mu$ & $g_s$ & $G^a_\mu$ & Gluon\\
+$SU(3)_C$ & $g_s$ & $G^a_\mu$ & $g_s$ & $G^a_\mu$ & gluon\\
 $SU(2)_L$ & $g_w$ & $W^b_\mu$ & $g_W = \sqrt{2}g_w$,  &  $W^\pm_\mu$,  & $W^\pm$,  \\
- & & & $g_Z = \sqrt{g_w^2 + g_Y^2}$ & $Z^0_\mu$ & $Z^0$ Boson\\
-$U(1)_Y$ & $g_Y$ & $B_\mu$ & $e = g_Y\cdot c_w$ & $A_\mu$ & Photon
+ & & & $g_Z = \sqrt{g_w^2 + g_Y^2}$ & $Z^0_\mu$ & $Z^0$ boson\\
+$U(1)_Y$ & $g_Y$ & $B_\mu$ & $e = g_Y\cdot c_w$ & $A_\mu$ & photon
 \end{tabular}
@@
 \subsection{Electroweak Symmetry Breaking}\label{sec:EWSB}
-So far, no mass terms like in the Dirac Lagrangian \ref{eq:DiracLagrangian} have been introduced.
+So far, no mass terms like in the Dirac Lagrangian \eqref{eq:DiracLagrangian} have been introduced.
 The reason for this is that they are not gauge invariant, for left- and right-handed spinors transform differently.
@@
 \end{align}
-one obtains quadratic terms, i.e.
-mass terms, for the gauge fields in question.
+one obtains quadratic terms, i.e. mass terms, for the gauge fields in question and the Higgs field $H$. The mass of the Higgs boson is then given by
+\begin{align}
+m_H = \mu.
+\end{align}
 In order to obtain mass eigenstates out of $B_\mu$ and $W_\mu^3$ and charge eigenstates for $Q$ and $I_3$ out of $W_\mu^1$ and $W_\mu^2$ one performs the transformation
@@
 In eq.
-\ref{eq:GhostLagrangian} $c_a$ and $\overline{c}_a$ are the Faddeev-Popov ghost and antighosts.
+\eqref{eq:GhostLagrangian} $c_a$ and $\overline{c}_a$ are the Faddeev-Popov ghosts and antighosts.
 This fields do not correspond to physical particles because they violate the spin–statistics theorem, i.e.

### 2016-07-06 TreeLevel.tex
a lot of changes

@@
 \section{Squark and Gluino Production at Tree Level}\label{sec:SquarkGluinoTree}
-In this chapter, the production of strongly interacting supersymmetric particles\footnote{The production of sgluons is excluded from the analysis for their mass is chosen to be too large to significantly produce them.
-See \cite{Choi:2008ub, GoncalvesNetto:2012nt} for a calculation of sgluon cross section.} in the MRSSM is considered.
-The various processes and their associated cross section are compared to their analogues in the MSSM.\\
-Section \ref{sec:PartProcesses} will give analytic results for the parton reaction before the next section describes how the hadronic cross section is obtained.
-Section ???
-presents the hadronic cross section of all considered processes.
+This chapter considers the production of strongly interacting supersymmetric particles in the MRSSM\footnote{In fact only the RSQCD is considered as contribution coming from the electroweak sector scale with $\alpha_w = \frac{g_w^2}{4\pi}$ or $\alpha_{\mathrm{em}} = \frac{e^2}{4\pi}$ and are therefore significantly smaller than contribution from the strongly interacting sector which scale with $\alpha_s = \frac{g_s^2}{4\pi}$.} The various processes and their associated cross section are compared to their analogues in the MSSM.\\
+The production of sgluons is not included in the following analysis.
+However, there are two possible channels for sgluon production at tree-level: a quark-antiquark and a gluon-gluon initiated process:
+\begin{align}
+q\overline{q} \to \phi_0\phi_0\ (\sigma_0\sigma_0), \hspace{2cm} GG \to \phi_0\phi_0\ (\sigma_0\sigma_0).
+\end{align}
+To give a reasonable and consistent prediction of hadronic cross sections, a scenario with large sgluon mass, i.e.
+soft breaking parameter $m_\sigma = \unit[5]{TeV}$, is considered.
+This validates the negligence of sgluon production as in this case they are too heavy to significantly produce them at the LHC with $\sqrt{S} = \unit[13]{TeV}$.
+See \cite{Choi:2008ub, GoncalvesNetto:2012nt} for a calculation of the sgluon production cross section.
+\ignore{Feynman diagrams there are only ones, one can only produce sigma,sigma or phi,phi but not sigma,phi}
+Section \ref{sec:PartProcesses} gives analytic results for the parton reaction before the next section describes how the hadronic cross section is obtained.
+Section \ref{sec:tree-level_cross_sections} presents the hadronic cross section of all considered processes for various choices of squark and gluino mass.
 In particular, squark production is considered more closely.
@@
 One therefore deals with $n_f-1 = 5$ quark flavors.
-In view of the renormalization to be performed at the 1-loop level the results are given in $D = 4 - 2\epsilon$ dimensions and it has been distinguished between the gauge coupling $g_s$ from the gluon-quark-quark vertex and its supersymmetric analogue $\hat{g}_s$ from the gluino-squark-quark vertex.
-The usual Mandelstam variables $s,t,u$ and the following modifications of them are used\footnote{The kinematics of the process is like denoted in fig.
-\ref{fig:TreeDiagrams}.}
+In view of the renormalization and mass factorization to be performed at the 1-loop level, the results are calculated in (conventional) dimensional regularization (see section \ref{sec:RegSchemes}) and are therefore given in $D = 4 - 2\epsilon$ dimensions.
+Furthermore it has been distinguished between the gauge coupling $g_s$ from the gluon-quark-quark vertex and its supersymmetric analogue $\hat{g}_s$ from the gluino-squark-quark vertex.
+So far, it has not been distinguished between them because supersymmetry dictates them to be identical.
+However, the loop corrections to their corresponding vertex differ in dimensional regularization by a finite amount, as will be shown in section \ref{sec:renMRSSM}.
+To rectify this, an additional finite (supersymmetry restoring) counterterm needs to be added to one of renormalization constants of $g_s$ or $\hat{g}_s$.
+This will be done in \ref{sec:SUSYrestore}.\\
+To parametrize results, the usual Mandelstam variables $s,t,u$ and the following modifications of them are used\footnote{The kinematics of the process is denoted in fig. \ref{fig:TreeDiagrams}.}
 \begin{align}
@@
 \end{figure}
-To see this one can either just apply the Feynman rules in Appendix \ref{sec:FeynmanRules} or think of the conservation of R-charge: Left handed squarks have R-charge +1 and right handed squarks have R-charge -1.
-Antiparticles have the opposite R-charge of their corresponding particles.
-The final state particles have to meet the total R-charge zero from the initial state.
-Because of this one only has $\tilde{q}_L \overline{\tilde{q}}_L$ and $\tilde{q}_R \overline{\tilde{q}}_R$ as the final states in the MRSSM whereas in the MSSM one actually has four instead of two t-channel diagrams: The corresponding final states are $\tilde{q}_L \overline{\tilde{q}}_L$, $\tilde{q}_R \overline{\tilde{q}}_R$, $\tilde{q}_L \overline{\tilde{q}}_R$ and $\overline{\tilde{q}}_R \tilde{q}_L$.
+To see this one can either just apply the Feynman rules in Appendix \ref{sec:FeynmanRules} or think of the conservation of $R$-charge: Left handed squarks have R-charge $+1$ and right handed squarks have $R$-charge $-$1.
+Antiparticles have the opposite $R$-charge of their corresponding particles.
+The final state particles have to meet the total $R$-charge zero from the initial state.
+Because of this, one only has $\tilde{q}_L \overline{\tilde{q}}_L$ and $\tilde{q}_R \overline{\tilde{q}}_R$ as the final states in the MRSSM whereas in the MSSM one actually has four instead of two t-channel diagrams: The corresponding final states are $\tilde{q}_L \overline{\tilde{q}}_L$, $\tilde{q}_R \overline{\tilde{q}}_R$, $\tilde{q}_L \overline{\tilde{q}}_R$ and $\overline{\tilde{q}}_R \tilde{q}_L$.
 Consequently contributions from the $t$-channel diagrams are suppressed in the MRSSM in comparison to the MSSM.
@@
 The reason for this lies in the gluino mass dependence of the $t$-channel diagrams which is explained in the discussion of squark production.\\
-If the initial state quarks are of different flavor the $s$-channel diagram is absent.
+If the initial state quarks are of different flavor, the $s$-channel diagram is absent.
 
@@
 To be more explicit the suppression of squark production in the MRSSM grows with the gluino mass.
-This can be understood as follows: As in the MRSSM a left handed squark needs to be produced with a right handed squark one can read off from the Feynman rules given in Appendix \ref{sec:FeynmanRules} that the gluino propagator $i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2}$ is sandwiched between the projectors $P_L$ and $P_R$ which leads to the cancellation of the gluino mass in the numerator.
-Therefore for small momenta of the gluino compared to the gluino mass one gets $\mathcal{M}$ $\sim \frac{1}{m_{\tilde{g}}^2}$ in the MRSSM while in the MSSM one finds a suppression proportional to $\frac{1}{m_{\tilde{g}}}$.\\
-When considering squark production one has to sum over all $|\mathcal{M}|^2$ with different helicity.
+This can be understood as follows: As in the MRSSM a left handed squark needs to be produced with a right handed squark one can read off, from the Feynman rules given in Appendix \ref{sec:FeynmanRules}, that the gluino propagator $i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2}$ is sandwiched between the projectors $P_L$ and $P_R$ which leads to the cancellation of the gluino mass in the numerator.
+Therefore for small momenta of the gluino compared to the gluino mass one gets $\mathcal{M}$ $\sim m_{\tilde{g}}^{-2}$ in the MRSSM while in the MSSM one finds a suppression proportional to $m_{\tilde{g}}^{-1}$.\\
+When considering squark production, one has to sum over all $|\mathcal{M}|^2$ with different helicity.
 The diagrams for those different final state helicities are shown for flavor like squark production in tab.
@@
 \ref{tab:squark_unlikeflavor} for the MSSM and the MRSSM.
-To avoid double counting one needs to weight $|\mathcal{M}|^2(qq\to \tilde{q}_L\tilde{q}_L)$ and $|\mathcal{M}|^2(qq\to \tilde{q}_R\tilde{q}_R)$ with a statistical factor of $\frac{1}{2}$ as one integrates over all momenta of both particles to arrive at the cross section.
+To avoid double counting one needs to weight $|\mathcal{M}|^2(qq\to \tilde{q}_L\tilde{q}_L)$ and $|\mathcal{M}|^2(qq\to \tilde{q}_R\tilde{q}_R)$ with a statistical factor of $\frac{1}{2}$ as one integrates over the momenta of both particles in $t$- and $u$-channel diagram to arrive at the cross section.
 \begin{table}[!htpb]
@@
 Because of the absence of chirality like squarks in the final state in the MRSSM (and a missing interference of the two diagrams in tab.
-\ref{tab:squark_likeflavor} in the column of the MRSSM) the partonic cross section of flavor like and unlike squarks is the same in the MRSSM, i.e.
+\ref{tab:squark_likeflavor} in the column of the MRSSM), the partonic cross section of flavor like and unlike squarks is the same in the MRSSM, i.e.
 on the partonic level:
@@
 \end{align} 
-That is however not true in the MSSM because for flavor like squarks there is a non vanishing interference of the $t$- and $u$-channel diagram of the processes $qq \to \tilde{q}_L\tilde{q}_L$ and $qq \to \tilde{q}_R\tilde{q}_R$.
-This term is given in \cite[p.7]{Beenakker:1996ch}\\
+That is however not true in the MSSM because for flavor like squarks, there is a non vanishing interference of the $t$- and $u$-channel diagram of the processes $qq \to \tilde{q}_L\tilde{q}_L$ and $qq \to \tilde{q}_R\tilde{q}_R$.
+This term is given in \cite[p.7]{Beenakker:1996ch}.\\
 
@@
 This is because gluino and antigluino are distinguishable particles.
-Still in comparison to the MSSM cross section \cite[p.9]{Beenakker:1996ch} only the first line in \eqref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines originate from an $t$ or $u$ channel squark which occurs in only one instead of two chiralities.
+Still in comparison to the MSSM cross section \cite[p.9]{Beenakker:1996ch} only the first line in eq.
+\eqref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines originate from an $t$ or $u$ channel squark which occurs in only one instead of two chiralities.
 Furthermore an interference term from the $t$ and $u$ channel diagram which occurs in the MSSM is absent in the MRSSM.
@@
 \subsubsection*{The process $GG \to \tilde{g}\overline{\tilde{g}}$}
-As in the previous process the MRSSM cross section for $GG \to \tilde{g}\overline{\tilde{g}}$ receives no statistical factor of $\frac{1}{2}$ like in the MSSM.
+As in the previous process, the MRSSM cross section for $GG \to \tilde{g}\overline{\tilde{g}}$ receives no statistical factor of $\frac{1}{2}$ like in the MSSM.
 As there are no further differences between MSSM and MRSSM in this channel, the MRSSM cross section is simply twice as large as in the MSSM.
@@
 \subsubsection*{The process $q G \to \tilde{q} \tilde{g}$}
-This process is exactly the same in the MSSM and MRSSM for the are two differences between the models which exactly cancel each other: Firstly in the MRSSM there is not only the production of a squark and a gluino but also the production of a squark and an antigluino.
-But on the other hand R-charge needs to be conserved which dictates that a ``left-hande'' squark can only be produced with an antigluino and a ``right-handed'' squark can only be produced with a gluino (see table \ref{tab:R_charges_MRSSM}).
+This process is exactly the same in the MSSM and MRSSM for there are two differences between the models which exactly cancel each other: Firstly in the MRSSM there is not only the production of a squark and a gluino but also the production of a squark and an antigluino.
+But on the other hand R-charge needs to be conserved which dictates that a ``left-handed'' squark can only be produced with an antigluino and a ``right-handed'' squark can only be produced with a gluino (see table \ref{tab:R_charges_MRSSM}).
 \\ 
 \\
-In order to account for the confinement of quarks and gluons within hadrons the hadronic cross sections for the considered processes are calculated in the next subsection.
+In order to account for the confinement of quarks and gluons within hadrons, the next section describes how to obtain the hadronic cross sections for the considered processes.
 
@@
 Quarks, antiquarks and gluons are no free particles but are confined within hadrons.
-As hadrons consist of a variety of the just mentioned partons which share the hadron's momentum one does not have a definite initial state in hadron collisions which is assumed in the previous subsection.
+As hadrons consist of a variety of the just mentioned partons which share the hadron's momentum, one does not have a definite initial state in hadron collisions which is assumed in the previous section.
 Fortunately the hadronic cross section for the production of a final state $X$, e.g.
@@
 The parton density functions $f_{P_i/H_j}(x)$ and the momentum fractions $x_i$ are explained below.
-The hadrons center-of-mass energy is denoted with $\sqrt{S}$ where $\sqrt{s}$ denotes the partons center-of-mass energy.\\
-As the production of the final state $X$ may proceed via various initial partons one has to sum over all possible possibilities arising from the initial hadrons $H_1$ and $H_2$:
+The hadrons center-of-mass energy is denoted with $\sqrt{S}$ where $\sqrt{s} = \sqrt{S x_1 x_2}$ denotes the partons center-of-mass energy.\\
+As the production of the final state $X$ may proceed via various initial partons, one has to sum over all possible possibilities arising from the initial hadrons $H_1$ and $H_2$:
 \begin{align}
-\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(P_i P_j \to X)
+\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(P_i P_j \to X)m
 \end{align}
 where the sum runs over all partons $P_i$ ($P_j$) which are in the hadron $H_1$ ($H_2$).\\
-To get an intuitive idea of this factorization regard the hadrons as extended objects consisting of partons\footnote{The proton is considered as composed of three valence quarks: Two up-quarks and one down-quark.
+To get an intuitive idea of this factorization, regard the hadrons as extended objects consisting of partons\footnote{The proton is considered as composed of three valence quarks: Two up-quarks and one down-quark.
 In addition there are gluons and seaquarks, i.e.
@@
 Due to Lorentz contraction the hadrons appear as thin discs and the parton's mutual interactions are time-delayed within this frame.
-This effectively means that a hadron at the time of collision is virtually frozen.\\
-maybe picture of colliding disks\\
-This in turn implies that the hadron consists at the time of collision of a definite number of partons which can be thought of as carrying a definite fraction of the hadron's  momentum $p_{\mathrm{Part}} = x p_{\mathrm{Had}}$ with $x \in \left(0, 1 \right)$.
+This effectively means that a hadron at the time of collision is virtually frozen.\\ % maybe picture of colliding discs\\
+This in turn implies that the hadron consists, at the time of collision, of a definite number of partons which can be thought of as carrying a definite fraction of the hadron's  momentum $p_{\mathrm{Part}} = x p_{\mathrm{Had}}$ with $x \in \left\{0, 1 \right\}$.
 The parton density function $f_{P/H}(x)$ can therefore be understood as the probability of finding a parton $P$ within the hadron $H$ carrying $x$ of its momentum.
@@
 \end{center}
-\end{figure}\\
-They actually depend on an arbitrary energy scale referred to as the factorization scale $\mu_F$.
-The $\mu_F$ evolution is given within the scope of preturbation theory by coupled integro-differential equations named after Gribov, Lipatov, Dokshitzer, Altarelli and Parisi: the DGLAP-equations.
-For further reading on parton density functions and factorization see \cite{dissertori2003quantum} and \cite{Collins:1989gx}.
-See \cite{Brock:1993sz} for how to determine parton density functions.\\
-Fig.
-\ref{fig:pdfs} shows a parton density function set for the proton.
-One can see that the partons most probable to carry a high fraction of momentum are the valence quarks.
-For lower values of $x$ gluons constitute the major component of the proton.
+\end{figure}
 \begin{figure}[!htpb]
@@
 \end{figure}\\
+They actually depend on an arbitrary energy scale referred to as the factorization scale $\mu_F$.
+The $\mu_F$ evolution is given within the scope of perturbation theory by coupled integro-differential equations named after Gribov, Lipatov, Dokshitzer, Altarelli and Parisi: the DGLAP-equations.
+For further reading on parton density functions and factorization see \cite{dissertori2003quantum} and \cite{Collins:1989gx}.
+See \cite{Brock:1993sz} for how to determine parton density functions.\\
+Fig.
+\ref{fig:pdfs} shows a parton density function set for the proton.
+One can see that the partons most probable to carry a high fraction of momentum are the valence quarks.
+For lower values of $x$, gluons constitute the major component of the proton.\\
 Fig.\ref{fig:TreeXsection} shows the hadronic cross section for the production of various squarks in the MRSSM.
@@
 \eqref{eq:PartonicEquality}, one can see the influence of the parton density functions quite nicely: The up-squark production is the dominant contribution to squark production.
-Apart from the solid lines in fig.\ref{fig:TreeXsection} which correspond to the production of first generation squarks, also the cross section of mixed first and second generation (dashed lines) and second generation (dotted lines) squarks is shown.
+Apart from the solid lines in fig.
+\ref{fig:TreeXsection} which correspond to the production of first generation squarks, also the cross section of mixed first and second generation (dashed lines) and second generation (dotted lines) squarks is shown.
 The dashed dotted line shows the cross section of the charged conjugated particles of the dominant channel.\\
 
-\subsection{Results for Squark and Gluino Production at Tree-Level}
-REFER TO Kribs, Martin: SNOWMASS WHITEPAPER\\
-REFER TO Vernoica Sanz: How many SUpersymmetries?\\
-\\
+\subsection{Results for Squark and Gluino Production at Tree-Level}\label{sec:tree-level_cross_sections}
+%REFER TO Kribs, Martin: SNOWMASS WHITEPAPER\\
+%REFER TO Vernoica Sanz: How many SUpersymmetries?\\
+%\\
 This section presents hadronic tree-level or (Born) cross sections of squark and gluino production for two colliding protons in both, the MSSM and the MRSSM.\\
@@
 This is, for squark and squark-gluino production, also the charged conjugated processes, i.e.
-$\tilde{q}^\dagger\tilde{q}^\dagger$ and $\tilde{q}^\dagger\overline{\tilde{g}}$, are included.
+$\tilde{q}^\dagger\tilde{q}^\dagger$ and $\tilde{q}^\dagger\tilde{g}\left( \overline{\tilde{g}} \right)$, are included.
 In addition, squark production counts thoses processes twice which involve flavor unlike quarks, e.g.
@@
 The calculations have been performed by a $\texttt{C++}$ code which uses a library containing the absolute squared amplitudes for the processes in question.
-Note that the author has opted for the absolute squared amplitudes and not the partonic cross sections because this allows also for the calculation of partial differential cross section like the one shown in fig.
-???
-at the end of the section.\\
+Note that the author has opted for the absolute squared amplitudes and not the partonic cross sections because this allows also for the calculation of partial differential cross sections.\\
 The following paragraph discusses fig.
@@
 The same happens in the MRSSM but for a significantly higher squark mass of about $\unit[1300]{GeV}$.
-This suppression of squark production in the MRSSM increases with a growing gluino masses which can be seen when going from $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ to  $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ or even  $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 5$ in fig.
+This suppression of squark production in the MRSSM increases with a growing gluino masses which can be seen when going from $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ to  $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ or even $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 5$ depicted in fig.
 \ref{fig:TreeXsection5}.
-This reflects the gluino mass dependence explained in detail in section \ref{sec:PartProcesses}.
+This reflects the gluino mass dependence explained in detail in section \ref{sec:PartProcesses}.\\
 See also \ref{fig:TreeXsection_fixed_m} for a visualization of this behavior.\\
@@
 \end{figure}
+\newpage
 The contour plots \ref{fig:ContourTree} underline the already announced difference between squark production in the MRSSM and the MSSM.
@@
 \hline
-$\unit[1000]{GeV}$ & $934.9_{\pm 27.2\%\ignore{735}\pm 2.1\% \ignore{915}}^{\pm 30.0\% \ignore{1213}\pm 1.2\% \ignore{946}}$ & $102.1_{\pm 29.2\% \ignore{79.0}\pm 2.1\%\ignore{100}}^{\pm 31.2\% \ignore{134}\pm 1.9\% \ignore{104}}$ & $13.12_{\pm 31.6\% \ignore{9.97}\pm 1.7\% \ignore{12.9}}^{\pm 34.1\% \ignore{17.6}\pm 2.1\% \ignore{13.4}}$\\
-$\unit[1500]{GeV}$ & $360.9_{\pm 30.0\% \ignore{282}\pm 2.2\% \ignore{353}}^{\pm 30.5\% \ignore{471}\pm 1.1\% \ignore{365}}$ & $50.52_{\pm 29.5\% \ignore{39.0}\pm 1.9\% \ignore{49.6}}^{\pm 32.4\% \ignore{66.9}\pm 1.7\% \ignore{51.4}}$ & $7.712_{\pm 31.8\% \ignore{5.85}\pm 2.8\% \ignore{7.5}}^{\pm 34.9\% \ignore{10.4}\pm 2.4\% \ignore{7.9}}$\\
-$\unit[2000]{GeV}$ & $165.5_{\pm 28.2\% \ignore{129}\pm 2.1\% \ignore{162}}^{\pm 30.5\% \ignore{216}\pm 0.9\% \ignore{167}}$ & $26.97_{\pm 29.8\%\ignore{20.8}\pm 2.1\% \ignore{26.4}}^{\pm 32.6\%\ignore{35.8} \pm 1.5\% \ignore{27.4}}$ & $4.625_{\pm 31.8\% \ignore{3.51}\pm 1.6\% \ignore{4.55}}^{\pm 34.5\% \ignore{6.22}\pm 1.8\% \ignore{4.71}}$\\
+& & & \\
+$\unit[1000]{GeV}$ & $\unit[934.9]{fb}\ _{- 27.2\%\ignore{735}- 2.1\% \ignore{915}}^{+ 30.0\% \ignore{1213}+ 1.2\% \ignore{946}}$ & $\unit[102.1]{fb}\ _{- 29.2\% \ignore{79.0}- 2.1\%\ignore{100}}^{+ 31.2\% \ignore{134}+ 1.9\% \ignore{104}}$ & $\unit[13.12]{fb}\ _{- 31.6\% \ignore{9.97}- 1.7\% \ignore{12.9}}^{+ 34.1\% \ignore{17.6}+ 2.1\% \ignore{13.4}}$\\
+& & & \\
+$\unit[1500]{GeV}$ & $\unit[360.9]{fb}\ _{- 30.0\% \ignore{282}- 2.2\% \ignore{353}}^{+ 30.5\% \ignore{471}+ 1.1\% \ignore{365}}$ & $\unit[50.52]{fb}\ _{- 29.5\% \ignore{39.0}- 1.9\% \ignore{49.6}}^{+ 32.4\% \ignore{66.9}+ 1.7\% \ignore{51.4}}$ & $\unit[7.712]{fb}\ _{- 31.8\% \ignore{5.85}- 2.8\% \ignore{7.5}}^{+ 34.9\% \ignore{10.4}+ 2.4\% \ignore{7.9}}$\\
+& & & \\
+$\unit[2000]{GeV}$ & $\unit[165.5]{fb}\ _{- 28.2\% \ignore{129}- 2.1\% \ignore{162}}^{+ 30.5\% \ignore{216}+ 0.9\% \ignore{167}}$ & $\unit[26.97]{fb}\ _{- 29.8\%\ignore{20.8}- 2.1\% \ignore{26.4}}^{+ 32.6\%\ignore{35.8} + 1.5\% \ignore{27.4}}$ & $\unit[4.625]{fb}\ _{- 31.8\% \ignore{3.51}- 1.6\% \ignore{4.55}}^{+ 34.5\% \ignore{6.22}+ 1.8\% \ignore{4.71}}$\\
 \end{tabular}
-\caption{MRSSM The uncertainty of the numerical integration is lower than one permille.}
+\caption{Squark production cross section at tree-level (including five flavors and also the production of antisquarks) in the MRSSM for various squark and gluino masses.
+The uncertainty of the numerical integration is lower than one permille.
+The first relative uncertainty comes from the variation of $\mu_R$ and $\mu_F$ as described in the text.
+The second uncertainty corresponds to the parton density function uncertainty.}\label{tab:squarkMRSSM}
 \end{center}
 \end{table}
-
+%\vspace{1cm}
 \begin{table}
@@
 \hline
-$\unit[1000]{GeV}$ & $5257_{\pm 24.6\% \ignore{4196}\pm 1.2\% \ignore{5163}}^{\pm 28.4\% \ignore{6714}\pm 1.8\% \ignore{5319}}$ 
-& $340.4_{\pm 28.4\% \ignore{265}\pm 1.9\% \ignore{334}}^{\pm 31.0\% \ignore{446} \pm 1.6\% \ignore{346}}$ 
-& $33.97_{\pm 30.6\% \ignore{26.0}\pm 1.2\%\ignore{33.5}}^{\pm 33.6\% \ignore{45.4}\pm 2.3\%\ignore{34.7}}$\\
-$\unit[1500]{GeV}$ & $3263_{\pm 25.4\% \ignore{2602}\pm1.8\%\ignore{3205}}^{\pm 27.9\%\ignore{4172}\pm 1.2\%\ignore{3301}}$ 
-& $260.7_{\pm 28.4\%\ignore{203}\pm 2.2\%\ignore{255}}^{\pm 30.8\% \ignore{341}\pm 1.3\% \ignore{264}}$ 
-& $30.46_{\pm 30.7\%\ignore{23.3} \pm 1.9\%\ignore{29.9}}^{\pm  33.2\% \ignore{40.6} \pm 1.8\% \ignore{31.0}}$\\
-$\unit[2000]{GeV}$ & $2179_{\pm 25.6\% \ignore{1735}\pm 1.9\%\ignore{2139}}^{\pm 27.9\% \ignore{2788}\pm 1.1\%\ignore{2204}}$ 
-& $198.1^{\pm 30.7\%\ignore{259} \pm 1.5\%\ignore{201}}_{\pm 28.6\% \ignore{154}\pm 2.1\%\ignore{194}}$ 
-& $25.75^{\pm 33.2\%\ignore{34.3}\pm 1.5\%\ignore{26.2}}_{\pm 30.7\% \ignore{19.7}\pm 2.0\%\ignore{25.3}}$\\
+& & & \\
+$\unit[1000]{GeV}$ & $\unit[5257]{fb}\ _{- 24.6\% \ignore{4196}- 1.2\% \ignore{5163}}^{+ 28.4\% \ignore{6714}+ 1.8\% \ignore{5319}}$ 
+& $\unit[340.4]{fb}\ _{- 28.4\% \ignore{265}- 1.9\% \ignore{334}}^{+ 31.0\% \ignore{446} + 1.6\% \ignore{346}}$ 
+& $\unit[33.97]{fb}\ _{\- 30.6\% \ignore{26.0}- 1.2\%\ignore{33.5}}^{+ 33.6\% \ignore{45.4}+ 2.3\%\ignore{34.7}}$\\
+& & & \\
+$\unit[1500]{GeV}$ & $\unit[3263]{fb}\ _{- 25.4\% \ignore{2602}- 1.8\%\ignore{3205}}^{+ 27.9\%\ignore{4172}+ 1.2\%\ignore{3301}}$ 
+& $\unit[260.7]{fb}\ _{- 28.4\%\ignore{203}- 2.2\%\ignore{255}}^{+ 30.8\% \ignore{341}+ 1.3\% \ignore{264}}$ 
+& $\unit[30.46]{fb}\ _{- 30.7\%\ignore{23.3} - 1.9\%\ignore{29.9}}^{+  33.2\% \ignore{40.6} + 1.8\% \ignore{31.0}}$\\
+& & & \\
+$\unit[2000]{GeV}$ & $\unit[2179]{fb}\ _{- 25.6\% \ignore{1735}- 1.9\%\ignore{2139}}^{+ 27.9\% \ignore{2788}+ 1.1\%\ignore{2204}}$ 
+& $\unit[198.1]{fb}\ ^{+ 30.7\%\ignore{259} + 1.5\%\ignore{201}}_{- 28.6\% \ignore{154}- 2.1\%\ignore{194}}$ 
+& $\unit[25.75]{fb}\ ^{+ 33.2\%\ignore{34.3}+ 1.5\%\ignore{26.2}}_{- 30.7\% \ignore{19.7}- 2.0\%\ignore{25.3}}$\\
 \end{tabular}
-\caption{MSSM The uncertainty of the numerical integration is lower than one permille.}
+\caption{Same content as in \ref{tab:squarkMRSSM} but for the MSSM.}
 \end{center}

### 2016-07-06 Virt_Real.tex
matrix amplitude plots with self-energy, vertices and boxes contributions
uncertainties for squark production in table
a lot of changes

--- 2016-06-23 Virt_Real.tex
@@
-\section{Virtual and Real Corrections}
-The results calculated in the previous chapter are not the full theoretical predictions for the different processes but only the first term in a perturbation theory of $\alpha_s$.\\
+\section{Virtual and Real Corrections}\label{sec:VirtRealCorr}
+The results calculated in the previous chapter are not the full theoretical predictions for the different processes but only the first term in a perturbation series of $\alpha_s$.\\
 This section describes the necessary steps in the calculation of the squark production cross section at next-to-leading-order, i.e. its $\mathcal{O}(\alpha_s)$-correction.\\
-Reason validity of perturbation theory in this context.
+\ignore{Reason validity of perturbation theory in this context.}
 
@@
 \begin{align}
-\mathcal{M}^{\mathrm{V}} = \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} + \mathcal{M}^{\mathrm{1L}} \mathcal{M}^{\mathrm{B}\ast} = 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right)
+\left( \mathcal{M}^{\mathrm{V}} \right)^2 = \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} + \mathcal{M}^{\mathrm{1L}} \mathcal{M}^{\mathrm{B}\ast} = 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right)
 \end{align}
@@
 These additional singularities show up as single and double poles of $\epsilon$ in the matrix element $\mathcal{M^{\mathrm{1L}}}$ and the virtual cross section which is obtained after performing the 2-body phase space  integration as in eq.
-\ref{eq:sigma_tree} but over $\left|\mathcal{M^{\mathrm{V}}}\right|^2$:
+\eqref{eq:sigma_tree} but over $\left(\mathcal{M^{\mathrm{V}}}\right)^2$:
 \begin{align}
 \frac{\mbox{d}^2 \sigma^{\mathrm{V}}}{\mbox{d}t\ \mbox{d}u} =& \frac{K_{ab}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_1^2m_2^2}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_1^2m_2^2)\nonumber\\
-&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum |\mathcal{M}^{\mathrm{V}}|^2.\label{eq:diffsigma}
+&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum \left(\mathcal{M}^{\mathrm{V}}\right)^2.\label{eq:diffsigma}
 \end{align}
@@
 A crucial thing to recognize in the calculation of the $\mathcal{O}(\alpha_s)$ correction to the squark production cross section is that not only virtual corrections but also real corrections give rise to this physical observable.
-This is because one does not measure the final state partons but the jets in which they hadronize in due to confinement.
-This means that a radiation of a massless particle whose energy tends to zero or the radiation of a  particle which is collinear to one of the final state particles is in experiment measured as a two jet event even though there are three particles in the final state of the calculation.
-However real corrections also contain divergences.
+This is because one does not measure the final state partons but the jets in which they hadronize in, due to confinement.
+This means that a radiation of a massless particle whose energy tends to zero or the radiation of a  particle which is collinear to one of the final state particles is in experiment measured as a two jet event even though there are three particles in the final state of the calculation.\\
+However, real corrections also contain divergences.
 Including these contributions to the cross section causes the cancellation of single poles coming from soft divergences and the cancellation of double poles.
 At this point the only singularities which are left in the cross section are the collinear ones.\\
-To see how these are removed consider the second diagram in fig. \ref{fig:RealGluon}. The propagator of the quark which radiates off a gluon gives a contribution of the form
-\begin{align}
-\frac{1}{(p_q + p_g)^2 - m_q^2} = \frac{1}{p_q \cdot p_g} = \frac{1}{2E_qE_g(1-\beta_q \cos \theta_{qg})} \hspace{2cm} \mathrm{with}\ \beta_q = \frac{\vec{p}_q}{E_q}
-\end{align}
-to the the diagram in question.
-Here $p_q$, $p_g$ ($E_q$, $E_g$) are the quark's and gluon's four-momentum (energy) and $\theta_{qg}$ is the angle between the quark's and gluon's three-momentum.
-One observes two potentially singular limits
-\begin{align}
-\mathrm{soft\ gluon:}& \hspace{1cm} E_g \to 0\\
-%& \hspace{1cm} E_q \to 0 \hspace{1cm} \mathrm{if}\ m_q \to 0\\
-\mathrm{collinear\ particles:}& \hspace{1cm} \theta_{qg} \to 0 \hspace{1cm} \mathrm{if}\ m_q \to 0.
-\end{align}
-Within these limits the inner quark can almost be considered as on-shell which means that it may travel a long distance between the emission of a gluon and taking part in the actual interaction.
-This suggest that some divergences may come from the incoming hadron and are actually not associated with the interaction.
-In fact this turns out to be the case: The remaining collinear divergences have a generic form (evtl.
-angeben) and can, by redefinition, be absorbed into the parton density functions.
-This procedure is referred to as mass factorization \cite{dissertori2003quantum}.
-In fact the Kinoshita-Lee-Naunberg-Theorem \cite{1962JMP.....3..650K},\cite{PhysRev.133.B1549} guarantees the finiteness of sufficiently inclusive observables.\\
-Figure \ref{fig:DivergenceSummary} summarizes the required steps to render the next-to-leading-order cross section finite.
-\begin{figure}[!htbp]
-\begin{center}
-\begin{tikzpicture}
-	\node [block1a] (Mvirt) {$\mathcal{M}^{\mathrm{1L}}$ is UV- and  IR-divergent};
-	\node [block2a] at (6,0) (Mreal) {$\mathcal{M}^{\mathrm{real}}$ is IR-divergent};
-	\node [block1a] at (0,-2) (Mvirtren) {$\mathcal{M}^{\mathrm{1L}}$ is IR-divergent};
-	\path [line, line width = 1] (Mvirt) --node[right] {renormalize} (Mvirtren);
-	\node [block1b] at (0,-4) (svirtren) {$\sigma^{\mathrm{virt}}$ is IR-divergent};
-	\node [block2b] at (6,-4) (sreal) {$\sigma^{\mathrm{real}}$ is IR-divergent};
-	\path [line, line width = 1] (Mvirtren) --node[right] {integrate phase space} (svirtren);
-	\path [line, line width = 1] (Mreal) --node[right] {integrate phase space} (sreal);
-	\node [block2b] at (6, -6) (srealfac) {$\sigma^{\mathrm{real}}$ is IR-divergent};
-	\path [line, line width = 1] (sreal) --node[right] {mass factorization} (srealfac);
-	\node [block3] at (3,-8) (snlo) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{virt}} + \sigma^{\mathrm{real}}$ is finite};
-	\path [line, line width = 1] (srealfac) -- (snlo);
-	\path [line, line width = 1] (svirtren) -- (snlo);
-\end{tikzpicture}
-\caption{This scheme illustrates the necessary steps in the computation of the next-to-leading order cross section which are required to render it finite. }\label{fig:DivergenceSummary}
-\end{center}
-\end{figure}
-
-\subsubsection{Real Gluon Radiation}
-A representative set of Feynman-diagrams for real gluon emission are shown in fig.
-\ref{fig:RealGluon}.
-In order to extract the singularities the so called two-cut method has been adopted.
-This is the phase space has been divided into different regimes: a soft part, a hard collinear part and a hard non-collinear part.\\
-In the soft part the energy of the outgoing gluon is only integrated up to  $\delta_s \frac{\sqrt{s}}{2}$ where $\delta_s$ is a cut on which the final result must not depend on.
 \begin{figure}[!htbp]
@@
 \end{figure}
+To see how these are removed, consider the second diagram in fig. \ref{fig:RealGluon}. The propagator of the quark which radiates off a gluon gives a contribution of the form
+\begin{align}
+\frac{1}{(p_q + p_g)^2 - m_q^2} = \frac{1}{p_q \cdot p_g} = \frac{1}{2E_qE_g(1-\beta_q \cos \theta_{qg})} \hspace{2cm} \mathrm{with}\ \beta_q = \frac{\vec{p}_q}{E_q}
+\end{align}
+to the diagram in question.
+Here, $p_q$, $p_g$ ($E_q$, $E_g$) are the quark's and gluon's four-momentum (energy) and $\theta_{qg}$ is the angle between the quark's and gluon's three-momentum.
+One observes two potentially singular limits
+\begin{align}
+\mathrm{soft\ gluon:}& \hspace{1cm} E_g \to 0\\
+%& \hspace{1cm} E_q \to 0 \hspace{1cm} \mathrm{if}\ m_q \to 0\\
+\mathrm{collinear\ particles:}& \hspace{1cm} \theta_{qg} \to 0 \hspace{1cm} \mathrm{if}\ m_q \to 0.
+\end{align}
+Within these limits the inner quark can almost be considered as on-shell which means that it may travel a long distance between the emission of a gluon and taking part in the actual interaction.
+This suggest that some divergences may come from the incoming hadron and are actually not associated with the interaction.
+In fact this turns out to be the case: The remaining collinear divergences have a generic form (given in [...]) and can, by redefinition, be absorbed into the parton density functions.
+This procedure is referred to as mass factorization \cite{dissertori2003quantum}.
+In fact the Kinoshita-Lee-Naunberg-Theorem \cite{1962JMP.....3..650K},\cite{PhysRev.133.B1549} guarantees the finiteness of sufficiently inclusive observables.\\
+Figure \ref{fig:DivergenceSummary} summarizes the required steps to render the next-to-leading-order cross section finite.
+\begin{figure}[H]
+\begin{center}
+\begin{tikzpicture}
+	\node [block1a] (Mvirt) {$\mathcal{M}^{\mathrm{1L}}$ is UV- and  IR-divergent};
+	\node [block2a] at (6,0) (Mreal) {$\mathcal{M}^{\mathrm{real}}$ is IR-divergent};
+	\node [block1a] at (0,-2) (Mvirtren) {$\mathcal{M}^{\mathrm{1L}}$ is IR-divergent};
+	\path [line, line width = 1] (Mvirt) --node[right] {renormalize} (Mvirtren);
+	\node [block1b] at (0,-4) (svirtren) {$\sigma^{\mathrm{virt}}$ is IR-divergent};
+	\node [block2b] at (6,-4) (sreal) {$\sigma^{\mathrm{real}}$ is IR-divergent};
+	\path [line, line width = 1] (Mvirtren) --node[right] {integrate phase space} (svirtren);
+	\path [line, line width = 1] (Mreal) --node[right] {integrate phase space} (sreal);
+	\node [block2b] at (6, -6) (srealfac) {$\sigma^{\mathrm{real}}$ is IR-divergent};
+	\path [line, line width = 1] (sreal) --node[right] {mass factorization} (srealfac);
+	\node [block3] at (3,-8) (snlo) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{virt}} + \sigma^{\mathrm{real}}$ is finite};
+	\path [line, line width = 1] (srealfac) -- (snlo);
+	\path [line, line width = 1] (svirtren) -- (snlo);
+\end{tikzpicture}
+\caption{This scheme illustrates the necessary steps in the computation of the next-to-leading order cross section which are required to render it finite.
+Within the virtual corrections, UV-divergences of the loop diagrams are removed on the level of the matrix element.
+The matrix element of the real correction becomes singular within certain regions of phase space.
+Collinear divergences can be removed by mass factorization.
+After this the poles of virtual and real corrections add up to zero.}\label{fig:DivergenceSummary}
+\end{center}
+\end{figure}
 
-\subsubsection{Real Quark Radiation}
+\subsubsection*{Real Gluon Radiation}
+A representative set of Feynman-diagrams for real gluon emission are shown in fig.
+\ref{fig:RealGluon}.
+In order to extract the singularities the so called ``two-cut phase space slicing method''[cite??] has been adopted.
+Within this approach the phase space has been divided into different regimes: a soft part ($S$), a hard collinear part ($HC$) and a hard non-collinear part ($H\overline{C}$):
+\begin{align}
+\sigma^{\mathrm{R}} = \int_S \mathrm{d}\sigma^{\mathrm{R}} + \int_H \mathrm{d}\sigma^{\mathrm{R}} = \int_S \mathrm{d}\sigma^{\mathrm{R}} + \int_{HC} \mathrm{d}\sigma^{\mathrm{R}} + \int_{H\overline{C}}\mathrm{d} \sigma^{\mathrm{R}}.
+\end{align}
+In the soft part the energy of the outgoing gluon is only integrated up to  $\delta_s \frac{\sqrt{s}}{2}$ where $\delta_s$ is a cut on which the final result must not depend on.
+A second cut $\delta_c$ is introduced to separate the collinear from the non-collinear region.
+After deviding the phase space in the three mentioned part, each integration is performed analytically in $D = 4 - 2\epsilon$ dimensions.
+After performing mass factorization and adding up all three contributions, the real corrections do not depend on the two cut parameters $\delta_s$ and $\delta_c$.
+Furthermore the $\frac{1}{\epsilon^2}$ and $\frac{1}{\epsilon}$ poles have exactly the opposite sign of the ones extracted from the virtual corrections.
+
+\subsubsection*{Real Quark Radiation}
+As already mentioned before, adding up virtual and real gluon emission contributions results in the cancellation of divergences.
+However, there is a further contribution to squark production at next-to-leading order.
+This involves the radiation of an additional antiquark in the final state.
+To meet color conservation, the initial state has to be composed of a quark and a gluon, see fig.
+\ref{fig:quarkradiation}.
 \begin{figure}[!htbp]
@@
 The first two diagrams have a gluino propagator which may go on-shell.
-In this regime of phase space these diagrams should not be included in the correction to squark-production but to a tree-level contribution to squark-gluino-production.}\
+In this regime of phase space these diagrams should not be included in the correction to squark-production but to a tree-level contribution to squark-gluino-production.}\label{fig:quarkradiation}
 \end{center}
 \end{figure}
+These contributions do not comprise soft divergences.
+A split-up of space space in a soft and a hard part is therefore not needed.
+However, there are collinear singularities, originating from initial state radiation like shown in the last diagram of \ref{fig:quarkradiation}, which again have to be removed by means of mass factorization.\\
+But there is another complication: The first and second diagram in fig.
+\ref{fig:quarkradiation} include a gluino which subsequently decays into a squark-antiquark pair.
+If the squared gluino's four-momentum approaches its mass-shell $p^2 = m^2_{\tilde{g}}$ the amplitude of this diagram hits a singularity.
+Of course, this can only happen if $m_{\tilde{g}} > m_{\tilde{q}}$.\\
+These singularities are treated by introducing a non-zero width $\Gamma_{\tilde{q}}$ for the gluino as a regulator, i.e. modifying the propagator to the Breit-Wigner form
+\begin{align}
+\frac{1}{p^2 - m_{\tilde{q}}^2} \to \frac{1}{p^2 - m_{\tilde{q}}^2 + i m_{\tilde{q}} \Gamma_{\tilde{q}}}.
+\end{align}
+Integrating over the regime of phase space, where the gluino approaches its mass-shell, actually gives the tree-level contribution of the process $qG \to \tilde{q}\tilde{g}$ weighted by the branching ratio $\frac{\Gamma_{\tilde{q}\to q \tilde{g}}}{\Gamma_{\tilde{q}}}$.
+To avoid double counting, one has to cut this very regime of phase space out and subtract it from the total contribution originating from those diagrams.
+For a detailed prescription on how to deal with this issue, see \cite{Beenakker:1996ch, Gavin:2013kga}.
+
+\newpage

### 2016-07-06 figures/WARB_TreeLevel/MRSSM:q+q->sq+sq_seperated/MRSSM_q+q->sq+sq_mr=2_seperated.py

@@ -1,136 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-C++ code on laptop in WARB-talk
-@author: sebastian
-"""
-
-import numpy as np
-from matplotlib import pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-
-m_squark = np.array([], dtype=float);
-sigma_dd = np.array([], dtype=float);
-sigma_dd_C = np.array([], dtype=float); # charged conjugated cross section
-sigma_du = np.array([], dtype=float);
-sigma_du_C = np.array([], dtype=float);
-sigma_ds = np.array([], dtype=float);
-sigma_ds_C = np.array([], dtype=float);
-sigma_dc = np.array([], dtype=float);
-sigma_dc_C = np.array([], dtype=float);
-sigma_db = np.array([], dtype=float);
-sigma_db_C = np.array([], dtype=float);
-
-sigma_uu = np.array([], dtype=float);
-sigma_uu_C = np.array([], dtype=float);
-sigma_us = np.array([], dtype=float);
-sigma_us_C = np.array([], dtype=float);
-sigma_uc = np.array([], dtype=float);
-sigma_uc_C = np.array([], dtype=float);
-sigma_ub = np.array([], dtype=float);
-sigma_ub_C = np.array([], dtype=float);
-
-sigma_ss = np.array([], dtype=float);
-sigma_ss_C = np.array([], dtype=float);
-sigma_sc = np.array([], dtype=float);
-sigma_sc_C = np.array([], dtype=float);
-sigma_sb = np.array([], dtype=float);
-sigma_sb_C = np.array([], dtype=float);
-
-sigma_cc = np.array([], dtype=float);
-sigma_cc_C = np.array([], dtype=float);
-sigma_cb = np.array([], dtype=float);
-sigma_cb_C = np.array([], dtype=float);
-
-sigma_bb = np.array([], dtype=float);
-sigma_bb_C = np.array([], dtype=float);
-
-f = open('had_cros_MRSSM_q+q->sq+sq_mr=2.txt', 'r')
-discard = f.readline()
-
-for lines in f.readlines():
-    m_squark = np.append(m_squark, float(lines.split()[0]))
[…]

### 2016-07-06 figures/WARB_TreeLevel/q+q->sq+sq_fixed_msg_and_msq/MSSM+MRSSM_msg=2000GeV.py

@@ -1,133 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-C++ code on laptop in WARB-talk
-@author: sebastian
-"""
-
-import numpy as np
-from matplotlib import pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-
-m_squark = np.array([], dtype=float);
-sigma_MSSM = np.array([], dtype=float);
-sigma_MRSSM = np.array([], dtype=float);
-
-# arrays for errors (all flavors are summed over already)
-sigma3_MRSSM_maxPdf = np.array([], dtype=float);
-sigma3_MRSSM_minPdf = np.array([], dtype=float);
-sigma3_MRSSM_maxScale = np.array([], dtype=float);
-sigma3_MRSSM_minScale = np.array([], dtype=float);
-
-sigma3_MSSM_maxPdf = np.array([], dtype=float);
-sigma3_MSSM_minPdf = np.array([], dtype=float);
-sigma3_MSSM_maxScale = np.array([], dtype=float);
-sigma3_MSSM_minScale = np.array([], dtype=float);
-
-
-f_MSSM = open('MSSM_3_qq_sqsq_msg=2000GeV.txt', 'r')
-#discard = f_MSSM.readline()
-
-for lines in f_MSSM.readlines():
-    m_squark = np.append(m_squark, float(lines.split()[0]))
-    sigma_MSSM = np.append(sigma_MSSM, float(lines.split()[1]))
-
-f_MSSM.close()
-
-
-f_MRSSM = open('MRSSM_3_qq_sqLsqR_msg=2000GeV.txt', 'r')
-#discard = f_MRSSM.readline()
-
-for lines in f_MRSSM.readlines():
-    discard = np.append(m_squark, float(lines.split()[0]))
-    sigma_MRSSM = np.append(sigma_MRSSM, float(lines.split()[1]))
-
-f_MRSSM.close()
-
-f_MRSSM_maxPdf = open('Errors/qq_to_sqsq_MRSSM_maxPdfError_msg=2000GeV.txt', 'r')
-for lines in f_MRSSM_maxPdf.readlines():
-    sigma3_MRSSM_maxPdf = np.append(sigma3_MRSSM_maxPdf, float(lines))
-f_MRSSM_maxPdf.close()
-
[…]

### 2016-07-06 figures/WARB_TreeLevel/q+q->sq+sq_fixed_msg_and_msq/MSSM+MRSSM_msq=1000GeV.py

@@ -1,135 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-code on laptop in WARB-talk
-@author: sebastian
-"""
-
-import numpy as np
-from matplotlib import pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-
-m_gluino = np.array([], dtype=float);
-sigma_MSSM = np.array([], dtype=float);
-sigma_MRSSM = np.array([], dtype=float);
-
-# arrays for errors (all flavors are summed over already)
-sigma3_MRSSM_maxPdf = np.array([], dtype=float);
-sigma3_MRSSM_minPdf = np.array([], dtype=float);
-sigma3_MRSSM_maxScale = np.array([], dtype=float);
-sigma3_MRSSM_minScale = np.array([], dtype=float);
-
-sigma3_MSSM_maxPdf = np.array([], dtype=float);
-sigma3_MSSM_minPdf = np.array([], dtype=float);
-sigma3_MSSM_maxScale = np.array([], dtype=float);
-sigma3_MSSM_minScale = np.array([], dtype=float);
-
-
-
-f_MSSM = open('MSSM_3_qq_sqsq_msq=1000GeV.txt', 'r')
-#discard = f_MSSM.readline()
-
-for lines in f_MSSM.readlines():
-    discard = np.append(m_gluino, float(lines.split()[0]))
-    sigma_MSSM = np.append(sigma_MSSM, float(lines.split()[1]))
-    
-f_MSSM.close()
-
-
-f_MRSSM = open('MRSSM_3_qq_sqLsqR_msq=1000GeV.txt', 'r')
-#discard = f_MRSSM.readline()
-
-for lines in f_MRSSM.readlines():
-    m_gluino = np.append(m_gluino, float(lines.split()[0]))
-    sigma_MRSSM = np.append(sigma_MRSSM, float(lines.split()[1]))
-f_MRSSM.close()
-
-f_MRSSM_maxPdf = open('Errors/qq_to_sqsq_MRSSM_maxPdfError_msq=1000GeV.txt', 'r')
-for lines in f_MRSSM_maxPdf.readlines():
-    sigma3_MRSSM_maxPdf = np.append(sigma3_MRSSM_maxPdf, float(lines))
-f_MRSSM_maxPdf.close()
-
[…]

### 2016-07-07 NLO.tex
MSSM K-factors

@@
 This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of the absolute squared matrix amplitudes numerically by using the package \texttt{LoopTools} \cite{Hahn:1998}.
-Finally the phase space integration is performed by the integration routine "Cuhre" which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}.\\
+Finally the phase space integration and the integration over $x_1$ and $x_2$ is performed by the integration routine "Cuhre" which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}.
+The parton density functions are included using \texttt{LHAPDF6}\cite{Buckley:2014ana}\\
 The computation of the real correction have been done by Wojciech Kotlarski, another member of the group. Comment on how real corrections are processed.\\
@@
 \includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV.png}
-\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$ on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).}\label{fig:1LXsection_fixed_m}
+\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).}\label{fig:1LXsection_fixed_m}
 \end{center}
@@
 Calculate uncertainties for multiple points(pdf, scale, integration)
+
+\subsubsection{$K$-factors for Squark Production in the MSSM}
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.5]{figures/MSSM_uu_susu_Kfactors_msg=2000GeV.png}
+\includegraphics[scale=.5]{figures/MSSM_uu_susu_Kfactors_msq=1000GeV.png}
+\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).}\label{fig:1LXsection_fixed_m}
+\end{center}
+\end{figure}
+Calculate uncertainties for multiple points(pdf, scale, integration)
+\texttt{MadGraph5_aMC@NLO}\cite{Alwall:2014hca}
+When generating the code for the process in question, e.g. two protons to $\tilde{u}_L + \tilde{u}_R$, with
+\begin{lstlisting}
+generate p p > ul ur [QCD] $$go
+\end{lstlisting}
+the $s$-channel gluinos were omitted as MadGraph does not deal with divergences coming from the gluino in the on-shell limit.
 

### 2016-07-07 Renormalization.tex
MSSM K-factors

@@
 Their result has been checked with the above calculated renormalization constants.\\
-Auszug von modelfile\\
+\begin{lstlisting}
+Auszug von modelfile
+\end{lstlisting}
 To keep track of all divergences, the calculation has been performed with the option: \textsc{Dimensions} $\to 0$.

### 2016-07-07 figures/One_Loop/MSSM/MSSM_uu_susu_Kfactors_msg=2000GeV.py
MSSM K-factors and plots added

@@ -1,0 +1,141 @@
+# -*- coding: utf-8 -*-
+"""
+C++ code on laptop in WARB-talk
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_gluino = np.array([], dtype=float);
+# arrays for XSection
+sigma_LO_Tree_lr = np.array([], dtype=float);
+sigma_NLO_Tree_lr = np.array([], dtype=float);
+sigma_NLO_1L_lr   = np.array([], dtype=float);
+sigma_LO_Tree_ll = np.array([], dtype=float);
+sigma_NLO_Tree_ll = np.array([], dtype=float);
+sigma_NLO_1L_ll   = np.array([], dtype=float);
+
+
+f_Tree = open('data/MSSM_ulur_LO_tree_msg=2000GeV.txt', 'r')
+for lines in f_Tree.readlines():
+    m_gluino = np.append(m_gluino, float(lines.split()[0]))
+    sigma_LO_Tree_lr = np.append(sigma_LO_Tree_lr, float(lines.split()[1]))
+f_Tree.close()
+
+f_Tree = open('data/MSSM_ulul_LO_tree_msg=2000GeV.txt', 'r')
+for lines in f_Tree.readlines():
+    discard = np.append(m_gluino, float(lines.split()[0]))
+    sigma_LO_Tree_ll = np.append(sigma_LO_Tree_ll, float(lines.split()[1]))
+f_Tree.close()
+
+f_Tree = open('data/MSSM_ulur_NLO_tree_msg=2000GeV.txt', 'r')
+for lines in f_Tree.readlines():
+    discard = np.append(m_gluino, float(lines.split()[0]))
+    sigma_NLO_Tree_lr = np.append(sigma_NLO_Tree_lr, float(lines.split()[1]))
+f_Tree.close()
+
+f_Tree = open('data/MSSM_ulul_NLO_tree_msg=2000GeV.txt', 'r')
+for lines in f_Tree.readlines():
+    discard = np.append(m_gluino, float(lines.split()[0]))
+    sigma_NLO_Tree_ll = np.append(sigma_NLO_Tree_ll, float(lines.split()[1]))
+f_Tree.close()
+
+
+f_1L = open('data/MSSM_1L_ulur_msg=2000GeV.txt', 'r')
+for lines in f_1L.readlines():
[…]

### 2016-07-07 figures/One_Loop/MSSM/MSSM_uu_susu_Kfactors_msq=1000GeV.py

@@ -1,0 +1,141 @@
+# -*- coding: utf-8 -*-
+"""
+C++ code on laptop in WARB-talk
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_gluino = np.array([], dtype=float);
+# arrays for XSection
+sigma_LO_Tree_lr = np.array([], dtype=float);
+sigma_NLO_Tree_lr = np.array([], dtype=float);
+sigma_NLO_1L_lr   = np.array([], dtype=float);
+sigma_LO_Tree_ll = np.array([], dtype=float);
+sigma_NLO_Tree_ll = np.array([], dtype=float);
+sigma_NLO_1L_ll   = np.array([], dtype=float);
+
+
+f_Tree = open('data/MSSM_ulur_LO_tree_msq=1000GeV.txt', 'r')
+for lines in f_Tree.readlines():
+    m_gluino = np.append(m_gluino, float(lines.split()[0]))
+    sigma_LO_Tree_lr = np.append(sigma_LO_Tree_lr, float(lines.split()[1]))
+f_Tree.close()
+
+f_Tree = open('data/MSSM_ulul_LO_tree_msq=1000GeV.txt', 'r')
+for lines in f_Tree.readlines():
+    discard = np.append(m_gluino, float(lines.split()[0]))
+    sigma_LO_Tree_ll = np.append(sigma_LO_Tree_ll, float(lines.split()[1]))
+f_Tree.close()
+
+f_Tree = open('data/MSSM_ulur_NLO_tree_msq=1000GeV.txt', 'r')
+for lines in f_Tree.readlines():
+    discard = np.append(m_gluino, float(lines.split()[0]))
+    sigma_NLO_Tree_lr = np.append(sigma_NLO_Tree_lr, float(lines.split()[1]))
+f_Tree.close()
+
+f_Tree = open('data/MSSM_ulul_NLO_tree_msq=1000GeV.txt', 'r')
+for lines in f_Tree.readlines():
+    discard = np.append(m_gluino, float(lines.split()[0]))
+    sigma_NLO_Tree_ll = np.append(sigma_NLO_Tree_ll, float(lines.split()[1]))
+f_Tree.close()
+
+
+f_1L = open('data/MSSM_1L_ulur_msq=1000GeV.txt', 'r')
+for lines in f_1L.readlines():
[…]

### 2016-07-09 MSSM.tex
changes, presumably mainly in Virt_Real chapter

@@
 As in the Standard Model this spontaneous symmetry breaking and the presence of Yukawa-terms (first three terms of eq.
-\eqref{eq:W_MSSM}) lead to masses of the fermions.\footnote{Note the sum convention of $SU_{\mathrm{L}}(2)$ doublets: $\hat{H}_u \hat{Q} =  (\hat{H}_u)_{\alpha}\hat{Q}_\beta \epsilon^{\alpha\beta}$ to ensure gauge invariance (see Appendix \ref{sec:2spinor_notation} for the definition of $\epsilon^{\alpha\beta}$).} Apart from that there are also other terms like quark-squark-higgsino interactions.
+\eqref{eq:W_MSSM}) lead to masses of the fermions.\footnote{Note the sum convention of $SU_{\mathrm{L}}(2)$ doublets: $\hat{H}_u \hat{Q} =  (\hat{H}_u)_{\alpha}\hat{Q}_\beta \epsilon^{\alpha\beta}$ to ensure gauge invariance (see Appendix \ref{sec:2spinor_notation} for the definition of $\epsilon^{\alpha\beta}$).
+This convention was not used in the Standard Model.} Apart from that there are also other terms like quark-squark-higgsino interactions.
 In addition there is the $\mu$-term which is responsible for Higgsino and Higgs masses.\\

### 2016-07-09 NLO.tex
changes, presumably mainly in Virt_Real chapter

@@
 Now considers the full $(n+m)$-point function in scalar theory.
-One can decompose it into an amputated $(n+m)$-point function and "full" propagators like written in eq.
+One can decompose it into an amputated $(n+m)$-point function and ``full'' propagators like written in eq.
 \eqref{eq:propagator} and depicted in fig.
@@
 \end{tikzpicture}
-\caption{Diagrammatic figure of a "full" $(n+m)$-point function. Apart from the "full" propagators there is the "full" amputated $(n+m)$-point function}
+\caption{Diagrammatic figure of a ``full' $(n+m)$-point function. Apart from the ``full'' propagators there is the ``full'' amputated $(n+m)$-point function}
 \end{center}
@@
 This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of the absolute squared matrix amplitudes numerically by using the package \texttt{LoopTools} \cite{Hahn:1998}.
-Finally the phase space integration and the integration over $x_1$ and $x_2$ is performed by the integration routine "Cuhre" which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}.
+Finally the phase space integration and the integration over $x_1$ and $x_2$ is performed by the integration routine ``Cuhre'' which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}.
 The parton density functions are included using \texttt{LHAPDF6}\cite{Buckley:2014ana}\\
-The computation of the real correction have been done by Wojciech Kotlarski, another member of the group. Comment on how real corrections are processed.\\
+The computation of the real correction has been done by Wojciech Kotlarski, another member of the group. Comment on how real corrections are processed.\\
 \begin{figure}[!htbp]
@@
 	\node [block1a] at (-1,-3) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{B}|^2}$};	
-	\node [block1a] at (-1,-1.5) (notebookV) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{1L}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{V}|^2}$};
+	\node [block1a] at (-1,-1.5) (notebookV) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{1L}}$ \newline \texttt{FormCalc} $\to 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$};
 	\node [block5a] at (7.5,0) (C++) {\texttt{C++} code};
 	\node [block5b] at (3.7,-3.5) (Born) {\underline{Born contribution} \newline \texttt{CUBA} $\to$ num. integration over $t, x_1, x_2$ to $\sigma^{\mathrm{B}}$};
-	\node [block5b] at (7.5,-2.7) (Virt) {\underline{Virtual correction}\newline \texttt{LoopTools} $\to$ computation \newline of $ \sum |\mathcal{M}^{\mathrm{V}|^2}$ \newline \texttt{CUBA} $\to$ num.
+	\node [block5b] at (7.5,-2.7) (Virt) {\underline{Virtual correction}\newline \texttt{LoopTools} $\to$ computation \newline of $ 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$ \newline \texttt{CUBA} $\to$ num.
 integration over $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$};
@@
 Calculate uncertainties for multiple points(pdf, scale, integration)
-\texttt{MadGraph5_aMC@NLO}\cite{Alwall:2014hca}
+\texttt{MadGraph5\_aMC@NLO}\cite{Alwall:2014hca}
 When generating the code for the process in question, e.g. two protons to $\tilde{u}_L + \tilde{u}_R$, with
-\begin{lstlisting}
+\begin{lstlisting}[style=Mybash]
 generate p p > ul ur [QCD] $$go

### 2016-07-09 Renormalization.tex
changes, presumably mainly in Virt_Real chapter

--- 2016-07-06 Renormalization.tex
@@
 This section discusses the removal of ultraviolet divergences in the amplitude of squark production at 1-loop level in the RSQCD.
-After an introduction and discussion of the regularization schemes, field and mass renormalization constants are calculated in dimensional regularization in the on-shell scheme.
-After that the renormalization constant of the strong gauge coupling $g_s$ is computed in a mixture of $\overline{\mathrm{MS}}$- and zero-momentum subtraction scheme.
+After a very brief introduction and discussion of the regularization schemes, field and mass renormalization constants are calculated, using dimensional regularization, in the on-shell scheme.
+After that, the renormalization constant of the strong gauge coupling $g_s$ is computed in a mixture of $\overline{\mathrm{MS}}$- and zero-momentum subtraction scheme.
 This was done because the gauge coupling of the parton density functions is given in the $\overline{\mathrm{MS}}$-scheme but does not include heavy particles, such as the top-quark or supersymmetric particles in its $\beta$-function.
-However renormalizing these heavy particles in the zero-momentum subtraction implies that the $\beta$-function of $g_s$ is exactly the one from QCD.
+However renormalizing these heavy particles in the zero-momentum subtraction, implies that the $\beta$-function of $g_s$ is exactly the one from QCD.
 This is shown in section \ref{sec:beta_function}.
@@
 Dimensional regularization (DREG) is a very common procedure for regularizing infinities which was devised by t'Hooft and Veltman~\cite{'tHooft:1972fi}.
-In this scheme loop momenta, gamma- and epsilon-tensors, phase space and fields are defined in $D$ dimensions\cite{Collins:105730}.
-As in every regularization scheme a parameter with mass dimension needs to be introduced.
+In this scheme, loop momenta, gamma- and epsilon-tensors, phase space and fields are defined in $D$ dimensions\cite{Collins:105730}.
+As in every regularization scheme, a parameter with mass dimension needs to be introduced.
 In DREG, that is the $\mu$ parameter which ensures that the loop integrals still have mass dimension four:
@@
 \end{align}
-If one writes $D=4-2\epsilon$, the divergences of the loop integral manifest in $\frac{1}{\epsilon}$ poles.\\
+If one writes $D=4-2\epsilon$, the divergences of the loop integrals manifest in $\frac{1}{\epsilon}$ poles.\\
 However DREG suffers a flaw in supersymmetry.
-As the degrees of freedom of a massless gauge boson are $D-2$ but the degrees of freedom of its superpartner are 2 there is a mismatch if $D \neq 4$.
-As a consequence there are $2\epsilon$ degrees of freedom associated with the gluon\footnote{These degrees of freedom are identified with scalars and are therefore referred to as $\epsilon$ scalars} which do not have a supersymmetric partner.
+As the degrees of freedom of a massless gauge boson are $D-2$ but the degrees of freedom of its superpartner are two, there is a mismatch if $D \neq 4$.
+As a consequence, there are $2\epsilon$ degrees of freedom associated with the gluon\footnote{These degrees of freedom are identified with scalars and are therefore referred to as $\epsilon$ scalars.} which do not have a supersymmetric partner.
 Therefore DREG violates supersymmetry.
@@
 it preserves supersymmetry.\footnote{It is not clear whether DRED preserves supersymmetry at all orders in perturbation theory\cite{Jack:1997sr} but it does preserve supersymmetry at 1-loop level\cite{Hollik:2001cz}.} DRED promotes only loop momenta to $D$ dimensions.
-All other quantities which are $D$ dimensional in DREG stay in 4 dimensions.
-The most important difference is the contraction of the metric tensor with itself equals four
+All other quantities which are $D$ dimensional in DREG stay in four dimensions.
+The most important difference is that the contraction of the metric tensor with itself equals four
 \begin{align}
@@
 A formal introduction of $\Gamma$ can be found in~\cite{Peskin}.
-In short $\Gamma$ can be viewed as a generalization of the classical action $\Gamma_{\mathrm{cl}} = \int \mathcal{L}_{\mathrm{cl}}$ by quantum effects:
+In short, $\Gamma$ can be viewed as a generalization of the classical action $\Gamma_{\mathrm{cl}} = \int \mathcal{L}_{\mathrm{cl}}$ by quantum effects:
 \begin{align}
-\Gamma = \Gamma_{\mathrm{cl}} + \mathcal{O}(\hbar)
+\Gamma = \Gamma_{\mathrm{cl}} + \mathcal{O}(\hbar).
 \end{align}
 This means that in addition to the vertices in the classical Lagrangian, new vertices arise due to loop effects.
-As already alluded to, loop corrections might a priori not be finite and then need to be rendered finite by the addition of counterterms.
+As already alluded to, loop corrections might a priori not be finite and then need to be rendered ultraviolet finite by the addition of counterterms.
 For $\mathcal{O}(\hbar)$ corrections one writes
 \begin{align}
-\Gamma^{(\leq 1)} \to \Gamma^{(\leq 1)} + \Gamma^{(1),\ \mathrm{ct}}
+\Gamma^{(\leq 1)} \to \Gamma^{(\leq 1)} + \Gamma^{(1),\mathrm{ct}}
 \end{align} 
 These counterterms depend on the regularization (and renormalization) scheme.
-If one chooses to work with DREG, supersymmetry will not be preserved at 1-loop order, i.e.
+If one chooses to work with DREG, which is done in this thesis, supersymmetry will not be preserved at 1-loop order, i.e.
 $\Gamma^{(\leq 1)}_{\mathrm{DREG}}$ is not supersymmetric.
-To maintain supersymmetry invariance of the renormalized effective action, the counterterms will not only consist of supersymmetric counterterms $\Gamma^{(1),\ \mathrm{ct,\ sym}}_{\mathrm{DREG}}$ but also of counterterms restoring supersymmetry $\Gamma^{(1),\ \mathrm{ct,\ trans}}_{\mathrm{DREG}}$.
+To maintain supersymmetry invariance of the renormalized effective action, the counterterms will not only consist of supersymmetric counterterms $\Gamma^{(1),\ \mathrm{ct,sym}}_{\mathrm{DREG}}$ but also of counterterms restoring supersymmetry $\Gamma^{(1),\mathrm{ct,trans}}_{\mathrm{DREG}}$.
 \begin{align}
-\Gamma^{(1),\ \mathrm{ct}}_{\mathrm{DREG}} = \Gamma^{(1),\ \mathrm{ct,\ sym}}_{\mathrm{DREG}} + \Gamma^{(1),\ \mathrm{ct,\ trans}}_{\mathrm{DREG}}
+\Gamma^{(1),\mathrm{ct}}_{\mathrm{DREG}} = \Gamma^{(1),\mathrm{ct,sym}}_{\mathrm{DREG}} + \Gamma^{(1),\mathrm{ct,trans}}_{\mathrm{DREG}}
 \end{align}
-Fortunately a supersymmetry conserving regularization scheme (at 1-loop level) is given by DRED \cite{Hollik:2001cz}. One way to acquire supersymmetry restoring counterterms is therefore given by
+Fortunately, a supersymmetry conserving regularization scheme (at 1-loop level) is given by DRED \cite{Hollik:2001cz}. One way to acquire supersymmetry restoring counterterms is therefore given by
 \begin{align}
-\Gamma^{(\leq 1)}_{\mathrm{DRED}} + \Gamma^{(1),\ \mathrm{ct}}_{\mathrm{DRED}} \overset{!}{=} \Gamma^{(\leq 1)}_{\mathrm{DREG}} + \Gamma^{(1),\ \mathrm{ct}}_{\mathrm{DREG}}.
+\Gamma^{(\leq 1)}_{\mathrm{DRED}} + \Gamma^{(1),\mathrm{ct}}_{\mathrm{DRED}} \overset{!}{=} \Gamma^{(\leq 1)}_{\mathrm{DREG}} + \Gamma^{(1),\mathrm{ct}}_{\mathrm{DREG}}.
 \end{align}
-Equating also the finite terms in $\Gamma^{(1),\ \mathrm{ct,\ sym}}$ in DRED and DREG the choice of the supersymmetry restoring counterterms is fixed by\cite{Varso, Stockinger:2011gp, Martin:1993yx}:
+Equating also the finite terms in $\Gamma^{(1),\mathrm{ct,sym}}$ in DRED and DREG the choice of the supersymmetry restoring counterterms is fixed by\cite{Varso, Stockinger:2011gp, Martin:1993yx}:
 \begin{align}
@@
 \eqref{eq:GammaCtRestore}.
-The only point where particularly care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms, due to different loop diagrams.
+The only point where particularly care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms:
+\begin{align}
+\delta g_s^{\mathrm{trans}} \neq \delta \hat{g}_s^{\mathrm{trans}}.
+\end{align}
+This is due to different loop diagrams, i.e. 
+\begin{align}
+\Gamma^{(1),\mathrm{ct,trans}}_{\mathrm{DREG},q_i \overline{q}_j G^a_\mu} \hspace{1cm} \mathrm{and} \hspace{1cm} \Gamma^{(1),\mathrm{ct,trans}}_{\mathrm{DREG},\tilde{q}_{Li} \overline{q}_j \tilde{g}^a}
+\end{align}
+are proportional to a different combination of $C(A)$ and $C(F)$. Furthermore there are different fields on the vertex, which also come with different supersymmetry restoring counterterms.\\
 Therefore one has to make a difference between these couplings at 1-loop level.
 In order to match $g_s$ to the experimentally measured coupling, it is renormalized in the  $\overline{\mathrm{MS}}$-scheme (with an additional manipulation for heavy particles, which will be explained in section \ref{sec:RenGaugeCoupling}).
-The Yukawa coupling $\hat{g}_s$ therefore needs to be added with the difference of the supersymmetry restoring counterterms from the $q\tilde{q}^\dagger\tilde{g}$ vertex and the $q\overline{q}G$ vertex at 1-loop in order to be renormalized in the same way.
-
-%An alternative procedure is used in \cite{Beenakker:1996ch}, where only one supersymmetry restoring counterterm, which translates between the renormalized gauge coupling $g_s$ and the renormalized Yukawa coupling $\hat{G}_s$ is needed.
-That is possible because the only supersymmetry violation comes from the gauge sector.
-For a comprehensive discussion of this issue see [Philipp Vasros Diplomarbeit and the paper with Dominik]\\
-%SUSY restoring is always already in $\delta Z^{DREG}$ included.
-Only important thing is the coupling: $g_s$ and $\hat{g}_s$ receive different SUSY restoring counterterm.
-Therefore one has to make a difference between these couplings at 1-loop level.
-In order to match $g_s$ to the experimentaly measured coupling it is renormalized in $\overline{\mathrm{MS}}$.
-The Yukawa coupling $\hat{g}_s$ therefore needs to be added with the difference of the SUSY-restoring counterterms at 1-loop in order to be renormalized the same way.
+The Yukawa coupling $\hat{g}_s$ needs therefore to be added with the difference of the supersymmetry restoring counterterms from the $\tilde{q}_L\overline{q}\tilde{g}$ vertex and the $q\overline{q}G$ vertex at 1-loop in order to be renormalized in the same way.
 
@@
 where $Z$ and $o$ are defined by the multiplicative renormalization transformation, introduced in eq.
-\eqref{eq:fieldtrafo} and \eqref{eq:fieldtrafo}.
+\eqref{eq:fieldtrafo} and \eqref{eq:parametertrafo}.
 The field and mass renormalization constants have been calculated in DREG in the on-shell scheme.
@@
 \subsubsection*{The $q\overline{q}G$ Vertex Correction Revisited}
-The diagrams from which the supersymmetry restoring contributions to the gauge coupling correction come from are shown in figure \ref{fig:GaugeCouplingCorrection} and evaluate to
+The diagrams from which the supersymmetry restoring contributions to the $q\overline{q}G$ vertex come from, are shown in figure \ref{fig:GaugeCouplingCorrection} and evaluate to
 \begin{align}
@@
 \end{align}
-where the second line shows the supersymmetry restoring counterterms. This yields
+where the second line shows the supersymmetry restoring counterterms to which they have to be equated to. Using the transition counterterms of the field yields
 \begin{align}
@@
 
-\subsubsection*{The $q\tilde{q}^\dagger\tilde{g}$ Vertex Correction}
-The supersymmetry restoring corrections to the Yukawa coupling originate from the diagram below.
+\subsubsection*{The $\tilde{q}_L\overline{q}\tilde{g}$ Vertex Correction}
+The supersymmetry restoring corrections to the $\tilde{q}_L \overline{q}\tilde{g}$ originate from the diagram in figure \ref{fig:YukawaCT}.
 \begin{figure}[!htbp]
@@
 	\draw[fermionbar](45:0.5)--(45:1.3);
-	\draw[scalarbar](-45:0.5)--(-45:1.3);
+	\draw[scalar](-45:0.5)--(-45:1.3);
 \end{tikzpicture}
-\caption{Diagram of the supersymmetry restoring correction of  the $q\tilde{q}\tilde{g}$ vertex}
+\caption{Diagram of the supersymmetry restoring correction of  the $q\tilde{q}\tilde{g}$ vertex}\label{fig:YukawaCT}
 \end{center}
@@
 \begin{align}
-i\Gamma^{\mathrm{(1),ct,trans}}_{\mathrm{DREG}, q_i\tilde{q}_j\tilde{g}^a} &= -ig_s \sqrt{2} P_L T^a_{ij}  \frac{g_s^2}{16\pi^2}C(A)\\
+i\Gamma^{\mathrm{(1),ct,trans}}_{\mathrm{DREG}, \tilde{q}_{Li}\overline{q}_j\tilde{g}^a} &= -ig_s \sqrt{2} P_L T^a_{ij}  \frac{g_s^2}{16\pi^2}C(A)\\
 &= -ig_s \sqrt{2} P_L T^a_{ij}  \left[ \frac{\delta \hat{g}_s^{\mathrm{trans}}}{g_s} + \frac{\delta Z^{\mathrm{trans}}_q + \delta Z^{\mathrm{trans}}_{\tilde{q}} + \delta Z^{\mathrm{trans}}_{\tilde{g}}}{2} \right].
 \end{align}
-The supersymmetry restoring part of the Yukawa renormalization constants is therefore
+Again, using the transition counterterms of the respective fields, one obtains
 \begin{align}
@@
 \end{align}
+The results have been checked with the \texttt{FormCalc} function \texttt{UVDivergentPart[expr]} which replaces the loop integrals in \texttt{expr} with its UV divergent part.\\
 Note that the renormalization constants $\delta m_{\tilde{g}}$, $\delta m^2_{\phi^0}$ and $\delta m^2_{\sigma^0}$ are not independent from each other as the masses of the gluino and the two sgluons arise  from only two parameters, i.e.
@@
 The derivation of the counterterm Feynman rules has been performed by the author whereas the implementation into the modelfile was mainly done by Philip Dießner, another member of the group.
-The renormalization constants for masses and fields are calculated by \texttt{FormCalc} functions like \textsc{MassRC} and \textsc{FieldRC}\cite{FormCalcManual}.
-Their result has been checked with the above calculated renormalization constants.\\
-Auszug von modelfile\\
-To keep track of all divergences, the calculation has been performed with the option: \textsc{Dimensions} $\to 0$.
-This is the only opportunity in \texttt{FormCalc} to really work in $D$ dimensions, i.e.
-the result contains a quantity $Dminus4$ which equals $-2\epsilon$ in DREG.
-The absolute matrix element coming from \texttt{FormCalc} is given in terms of scalar integrals, like defined in Appendix \ref{sec:Passarino}.\\
-To extract infrared divergences \texttt{LoopTools} has been used.
-This  tool provides the function \textsc{SetLambda} which can be set to 0, $-1$ or $-2$ to extract the finite part, single pole or double pole of  scalar integrals.
+The renormalization constants for masses and fields are calculated by \texttt{FormCalc} functions like \texttt{MassRC} and \texttt{FieldRC}\cite{FormCalcManual}.
+Their result has been checked with the above calculated renormalization constants.
+\begin{lstlisting}
+RenConst[dZFu1[gen_]] :=FieldRC[F[3,{gen}]][[1]]
+RenConst[dZFd1[gen_]] :=FieldRC[F[4,{gen}]][[1]]
+
+RenConst[dZSu1[gen_]] := FieldRC[S[13,{gen}]]	
+RenConst[dMSu1[gen_]] := MassRC[S[13,{gen}]]
+RenConst[dZSd1[gen_]] := FieldRC[S[14,{gen}]]	
+RenConst[dMSd1[gen_]] := MassRC[S[14,{gen}]]
+
+RenConst[dZGlL1] := xZfL1[F[15], 0]
+RenConst[dZGlR1] := xZfR1[F[15], 0]
+RenConst[dZbarGlL1] := dZGlR1
+RenConst[dZbarGlR1] := dZGlL1
+RenConst[dMGl1] := MassRC[F[15]]
+
+RenConst[dZgs1] := 0 - FiniteGs * g3*g3/(16*Pi*Pi)*(2*Log[(MassGlu/mu)^2]
+                     +Log[(MassSq/mu)^2]+1/3*Log[(MassFu[3]/mu)^2]
+                     +1/4*Log[(MasssigmaO/mu)^2]
+                     +1/4*Log[(MassphiO/mu)^2])
+dZgs1restore := FiniteGs * g3*g3/(12*Pi*Pi)
+
+RenConst[dZGG1] := FieldRC[V[5]]
+\end{lstlisting}
+To keep track of all divergences, the calculation in \texttt{FormCalc} has been performed with the option: \texttt{Dimension} $\to 0$ which is the only opportunity to really work in $D$ dimensions, i.e.
+the result contains a quantity \texttt{Dminus4} which equals $-2\epsilon$ in DREG.
+The absolute squared matrix element coming from \texttt{FormCalc} is then given in terms of scalar integrals, like defined in Appendix \ref{sec:Passarino}.
+To get a notion for the \texttt{FormCalc} output, the following line shows the  off-shell amplitude of the quark self-energy in terms of loop integrals and \texttt{Dminus4}
+%\begin{lstlistings}
+Amp[{{F[3, {1, Col1}], k[1], 0, {}}} -> {{F[3, {1, Col2}], k[2], 
+     0, {}}}][(1/(\[Pi]^2))
+  g3^2 ((1/6 + Dminus4/12) (B0i[bb0, Pair[k[1], k[1]], 0, 0] + 
+        B0i[bb1, Pair[k[1], k[1]], 0, 0]) - 
+     1/6 B0i[bb1, Pair[k[1], k[1]], MassGlu^2, MassSu[1]^2]) Mat[(
+SequenceForm["<", "u", 2, "|", 6, ",", 
+FormCalc`k[1], "|", "u", 1, ">"]) SUNT[Col1, Col2]] + (1/(\[Pi]^2))
+  g3^2 ((1/6 + Dminus4/12) (B0i[bb0, Pair[k[1], k[1]], 0, 0] + 
+        B0i[bb1, Pair[k[1], k[1]], 0, 0]) - 
+     1/6 B0i[bb1, Pair[k[1], k[1]], MassGlu^2, MassSu[4]^2]) Mat[(
+SequenceForm["<", "u", 2, "|", 7, ",", 
+FormCalc`k[1], "|", "u", 1, ">"]) SUNT[Col1, Col2]]]
+%\end{lstlistings}
+To extract infrared divergences, \texttt{LoopTools} has been used.
+This  tool provides the function \texttt{SetLambda} which can be set to 0, $-1$ or $-2$ to extract the finite part, single pole or double pole of  scalar integrals.
 This allows for numerically extracting the coefficients of $\epsilon^i$ with $i \in \left\{ 0,-1,-2 \right\}$ of the absolute squared matrix amplitude.
 The respective poles of $|\mathcal{M}^{\mathrm{V}}_{\mathrm{MRSSM}}(uu \to \tilde{u}_L\tilde{u}_R)|^2$ are shown in figure \ref{fig:MatrixElement}.
+Note, that the extraction of the single pole does not only involve setting the option \texttt{SetLamda} $\to-1$ and \texttt{Dminus4}$\to 0$, but also setting \texttt{SetLamda}$\to-2$ and \texttt{Dminus4} $\to -2$ and subtract the term obtained by \texttt{SetLamda}$\to-2$ and \texttt{Dminus4} $\to 0$.
+In doing so, one accounts for the contraction of double poles with terms of $\mathcal{\epsilon}$.
+The same logic implies to the extraction of finite terms.\\
+\\
 In addition the tree-level absolute squared matrix amplitude with leading order $\alpha_s$ is compared with its analogue with next-to-leading order $\alpha_s$ and virtual absolute squared matrix amplitude.
@@
 \begin{center}
-\includegraphics[scale=.5]{figures/MatrixElement_SE_Vertices_Boxes}
-\caption{bla}
+\includegraphics[scale=.5]{figures/MatrixElement_Poles.png}
+\caption{Coefficients of $\mathcal{O}(\epsilon^0)$, $\mathcal{O}(\epsilon^{-1})$ and $\mathcal{O}(\epsilon^{-2})$ terms of the absolute squared matrix element of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM as a function of the Mandelstam variable $t$.
+External helicities and colors are averaged.
+The parameters are fixed to $m_{\tilde{q}} = \mu = \unit[1000]{GeV}$, $m_{\tilde{g}} = \unit[2000]{GeV}$, $m_{\sigma} = \unit[5000]{GeV}$ and $\sqrt{s} = \unit[6000]{GeV}$ which is the partonic center of mass energy.}
 \end{center}
@@
 \begin{center}
-\includegraphics[scale=.5]{figures/MatrixElement_Poles.png}
+\includegraphics[scale=.5]{figures/MatrixElement_SE_Vertices_Boxes}
 \includegraphics[scale=.5]{figures/MatrixElement.png}
-\caption{The figure at the top shows the coefficients of $\mathcal{O}(\epsilon^0)$, $\mathcal{O}(\epsilon^{-1})$ and $\mathcal{O}(\epsilon^{-2})$ terms of the absolute squared matrix element of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM as a function of the Mandelstam variable $t$.
-External helicities and colors are averaged.
-The parameters are fixed to $m_{\tilde{q}} = \mu = \unit[1000]{GeV}$, $m_{\tilde{g}} = \unit[2000]{GeV}$, $m_{\sigma} = \unit[5000]{GeV}$ and $\sqrt{s} = \unit[6000]{GeV}$ which is the partnoic center of mass energy.\newline
+\caption{\newline
 The figure at the bottom shows the absolute squared matrix element of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM at tree-level with $\alpha_s = $ from the leading order parton density function $\mathtt{MMHT2014}$\cite{Harland-Lang:2014zoa}, and $\alpha_s = $ from the netxt-to-leading order parton density function as well as the contribution from the virtual absolute squared matrix element.}\label{fig:MatrixElement}

### 2016-07-09 Standardmodel.tex
changes, presumably mainly in Virt_Real chapter

@@
 Matter particles acquire mass via Yukawa coulings to the Higgs doublet.
-For up-type-quarks one uses that the charge conjugate of $\Phi$: $\Phi^C = i \sigma^2 \Phi^\ast$ also transforms as $\Phi$.
-The Yukawa Lagrangian is given by
+For up-type-quarks, one uses that the charge conjugate of $\Phi$: $\Phi^C = i \sigma^2 \Phi^\ast$ also transforms like a $SU(2)_L$ doublet.
+The gauge invariant Yukawa Lagrangian is therefore given by
 \begin{align}
@@
 \end{align}
-The quark mass matrices are not diagonal, which is the precondition of the violation of CP-invariance.\footnote{The actual CP-violating term is in the coupling term of quarks to the $W$-bosons.} One therefore has to distinguish between interaction and mass eigenstates of the quarks.
+The quark mass matrices are not diagonal, which is the precondition of the violation of CP invariance.\footnote{The actual CP-violating term is in the coupling term of quarks to the $W$-bosons.} One therefore has to distinguish between interaction and mass eigenstates of the quarks.
 The corresponding transformation matrix is the well known CKM-matrix \cite{Cabbibo:1964zsa, Kobayashi:1973fv}.

### 2016-07-09 TreeLevel.tex
changes, presumably mainly in Virt_Real chapter

@@
 This validates the negligence of sgluon production as in this case they are too heavy to significantly produce them at the LHC with $\sqrt{S} = \unit[13]{TeV}$.
-See \cite{Choi:2008ub, GoncalvesNetto:2012nt} for a calculation of the sgluon production cross section.
+See \cite{Choi:2008ub, GoncalvesNetto:2012nt, phdWojciech} for a calculation of the sgluon production cross section.
 \ignore{Feynman diagrams there are only ones, one can only produce sigma,sigma or phi,phi but not sigma,phi}
@@
 This in turn implies that the hadron consists, at the time of collision, of a definite number of partons which can be thought of as carrying a definite fraction of the hadron's  momentum $p_{\mathrm{Part}} = x p_{\mathrm{Had}}$ with $x \in \left\{0, 1 \right\}$.
-The parton density function $f_{P/H}(x)$ can therefore be understood as the probability of finding a parton $P$ within the hadron $H$ carrying $x$ of its momentum.
+The parton density function $f_{P/H}(x)$ can (at tree-level) therefore be understood as the probability of finding a parton $P$ within the hadron $H$ carrying $x$ of its momentum fraction.
 \begin{figure}[!htbp]
@@
 They actually depend on an arbitrary energy scale referred to as the factorization scale $\mu_F$.
-The $\mu_F$ evolution is given within the scope of perturbation theory by coupled integro-differential equations named after Gribov, Lipatov, Dokshitzer, Altarelli and Parisi: the DGLAP-equations.
+The $\mu_F$ evolution is given within the scope of perturbation theory by coupled integro-differential equations named after Gribov, Lipatov\cite{Gribov:1972ri}, Dokshitzer\cite{Dokshitzer:1977sg}, Altarelli and Parisi\cite{Altarelli:1977zs}: the DGLAP-equations.
 For further reading on parton density functions and factorization see \cite{dissertori2003quantum} and \cite{Collins:1989gx}.
@@
 %\\
-This section presents hadronic tree-level or (Born) cross sections of squark and gluino production for two colliding protons in both, the MSSM and the MRSSM.\\
+This section presents hadronic tree-level (Born) cross sections of squark and gluino production for two colliding protons in both, the MSSM and the MRSSM.\\
 Note that in the following all possible production channels are taken into account.
@@
 $ud \to \tilde{u}\tilde{d}$ is counted twice as the $d$-quark may come from either proton.
-This logic applies also to squark-antisquark production through a quark-antiquark pair.\\
+This applies also to squark-antisquark production through a quark-antiquark pair.\\
 The calculations have been performed by a $\texttt{C++}$ code which uses a library containing the absolute squared amplitudes for the processes in question.
-Note that the author has opted for the absolute squared amplitudes and not the partonic cross sections because this allows also for the calculation of partial differential cross sections.\\
+Note that the author has opted for the absolute squared amplitudes and not the partonic cross sections because this allows also for the calculation of partial differential cross sections, for possible future use.
+To perform the integration over the Mandelstam variable $t$ and $x_1$ and $x_2$, the routine ``Cuhre'' which is part of the \texttt{CUBA} library\cite{Hahn:2004fe} has been used\\
 The following paragraph discusses fig.
@@
 
-For the small mass ratio $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ and small squark masses the dominant contribution comes from gluino (antigluino) production.
-This is even more dominant in the MRSSM which can be explained by the above mentioned factor of 2 difference in the $GG \to \tilde{g}\tilde{g}(\overline{\tilde{g}})$ channel which comes from the distinguishable gluino and antigluino in the MRSSM.
-Furthermore there is the above mentioned destructive interference term in the $q\overline{q} \to \tilde{g}\tilde{g}(\overline{\tilde{g}})$ channel which makes the cross section in the MRSSM dominant over the one in the MSSM.\\
+For the small mass ratio $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ and small squark masses, the dominant contribution comes from gluino (antigluino) production.
+This is even more dominant in the MRSSM which can be explained by the above mentioned factor of two difference in the $GG \to \tilde{g}\tilde{g}(\overline{\tilde{g}})$ channel which comes from the distinguishable gluino and antigluino in the MRSSM.
+Furthermore there is the above mentioned destructive interference term in the $q\overline{q} \to \tilde{g}\tilde{g}(\overline{\tilde{g}})$ channel which makes the cross section for this process in the MRSSM dominant over the one in the MSSM.\\
 For a growing squark mass the previously subdominant gluino-squark production takes over and becomes dominant.
 A salient difference between the MSSM and the MRSSM is that squark production is strongly suppressed in the MRSSM.
-While in the MSSM it becomes dominant above about $\unit[1700]{GeV}$ it is subsubdominant for the whole displayed squark mass in the MRSSM.
+While in the MSSM it becomes dominant above about $\unit[1400]{GeV}$ it is subsubdominant for the whole displayed squark mass in the MRSSM.
 This suppression has also already been explained above.\\
@@
 For the MSSM one finds above $\unit[500]{GeV}$ a growing dominance of squark production.
-The same happens in the MRSSM but for a significantly higher squark mass of about $\unit[1300]{GeV}$.
+The same happens in the MRSSM but for a significantly higher squark mass of about $\unit[1200]{GeV}$.
 This suppression of squark production in the MRSSM increases with a growing gluino masses which can be seen when going from $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ to  $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ or even $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 5$ depicted in fig.
 \ref{fig:TreeXsection5}.
-This reflects the gluino mass dependence explained in detail in section \ref{sec:PartProcesses}.\\
+This reflects the gluino mass dependence explained in detail in section \ref{sec:PartProcesses}.
 See also \ref{fig:TreeXsection_fixed_m} for a visualization of this behavior.\\
-Note also that for sufficiently large squark masses squark production becomes the dominant process, see fig.
+Note also, that for sufficiently large squark masses squark production becomes the dominant process, see fig.
 \ref{fig:TreeXsection} and \ref{fig:TreeLevelSigma_0,9_2}.
@@
 The total cross section in the MRSSM is increasingly smaller than in the MSSM in particular from about $\unit[500]{GeV}$ onwards.
-The is because for masses below that the $GG \to \tilde{q}\tilde{q}^\dagger$ channel which is the same for both models is the dominant one.\\
+The is because for masses below that the $GG \to \tilde{q}\tilde{q}^\dagger$ channel, which is the same for both models, is the dominant one.\\
 When raising the gluino squark mass ratio further to $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 5$ the above described tendency continues.
-This is all processes including a gluino get even more negligible and squark production gets further suppressed.
-While in the MSSM it becomes dominant over $GG \to \tilde{q}\tilde{q}^\dagger$ at $m_{\tilde{q}} \approx \unit[1000]{GeV}$ it is subdominant in the MRSSM in the whole displayed mass range.
-even though it does not fall that steeply as the dominant channel.\\
+This is, all processes including a gluino get even more negligible and squark production gets further suppressed.
+While in the MSSM it becomes dominant over $GG \to \tilde{q}\tilde{q}^\dagger$ at $m_{\tilde{q}} \approx \unit[800]{GeV}$, it is subdominant in the MRSSM within the whole displayed mass range, even though it does not fall that steeply as the dominant channel.\\
 
@@
 \newpage
-The contour plots \ref{fig:ContourTree} underline the already announced difference between squark production in the MRSSM and the MSSM.
+The contour plots in fig.
+\ref{fig:ContourTree} underline the already announced difference between squark production in the MRSSM and the MSSM.
 While the cross sections for small gluino masses resemble each other closely, the cross section in the MRSSM gets increasingly suppressed with increasing gluino mass.
@@
 \end{figure}
+
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.5]{figures/MSSM+MRSSM_msg=2000}
+\includegraphics[scale=.5]{figures/MSSM+MRSSM_msq=1000}
+\caption{Comparison of squark production cross section including five flavors (also including $\tilde{q}^\dagger\tilde{q}^{\prime\dagger}$) in the MSSM and MRSSM at the LHC which $\sqrt{S} = \unit[13]{GeV}$ for fixed gluino mass (top) and fixed squark mass (bottom).
+The parton density functions and the renormalization and factorization scale are chosen as in fig.
+\ref{fig:TreeXsection}.}\label{fig:TreeXsection_fixed_m}
+\end{center}
+\end{figure}
+
 Fig.\ref{fig:TreeXsection_fixed_m} shows the Born cross section of squark production including all possible flavors for a fixed mass of the gluino $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and the squark $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).
@@
 $\Delta \sigma_{\mathrm{int}} < 1\text{\textperthousand}$.
+\newpage
 
-\begin{table}
+\begin{table}[H]
 \begin{center}
-\begin{tabular}{c|c|c|c}
-$m_{\tilde{g}}$ \textbackslash $m_{\tilde{q}}$ & $\unit[500]{GeV}$ & $\unit[1000]{GeV}$ & $\unit[1500]{GeV}$\\
-\hline
+\begin{tabular}{c?c|c|c}
+\backslashbox{$m_{\tilde{g}}$}{$m_{\tilde{q}}$} & $\unit[500]{GeV}$ & $\unit[1000]{GeV}$ & $\unit[1500]{GeV}$\\
+\hlinewd{2pt}
 & & & \\
@@
 %\vspace{1cm}
-\begin{table}
+\begin{table}[H]
 \begin{center}
-\begin{tabular}{c|c|c|c}
-$m_{\tilde{g}}$ \textbackslash $m_{\tilde{q}}$ & $\unit[500]{GeV}$ & $\unit[1000]{GeV}$ & $\unit[1500]{GeV}$\\
-\hline
+\begin{tabular}{c?c|c|c}
+\backslashbox{$m_{\tilde{g}}$}{$m_{\tilde{q}}$} & $\unit[500]{GeV}$ & $\unit[1000]{GeV}$ & $\unit[1500]{GeV}$\\
+\hlinewd{2pt}
 & & & \\
@@
 
-\begin{figure}[!htpb]
-\begin{center}
-\includegraphics[scale=.5]{figures/MSSM+MRSSM_msg=2000}
-\includegraphics[scale=.5]{figures/MSSM+MRSSM_msq=1000}
-\caption{Comparison of squark production cross section including five flavors (also including $\tilde{q}^\dagger\tilde{q}^{\prime\dagger}$) in the MSSM and MRSSM at the LHC which $\sqrt{S} = \unit[13]{GeV}$ for fixed gluino mass (top) and fixed squark mass (bottom).
-The parton density functions and the renormalization and factorization scale are chosen as in fig.
-\ref{fig:TreeXsection}.}\label{fig:TreeXsection_fixed_m}
-\end{center}
-\end{figure}
-As a summary of the comparison between MSSM and MRSSM gluino production one can say, that the gluino production is enhanced in the MRSSM due to distinguishable gluino and antigluino.
-In order to meet missing experimental evidence for supersymmerty this suggests that gluinos might be heavier than squarks in the MRSSM.
-Focusing on $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} \geq 2$ the most significant change between the considered models is the growing suppression of squark production for a increasing gluino mass.
+As a summary of the comparison between MSSM and MRSSM, one can say, that the gluino production is enhanced in the MRSSM due to distinguishable gluino and antigluino.
+In order to meet missing experimental evidence for supersymmerty, this suggests that gluinos might be heavier than squarks in the MRSSM.
+Focusing on $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} \geq 2$ the most significant change between the considered models is the growing suppression of squark production for an increasing gluino mass.
 This is why this channel is going to be investigated at next-to-leading order within this thesis.

### 2016-07-09 Virt_Real.tex
changes, presumably mainly in Virt_Real chapter

@@
 \section{Virtual and Real Corrections}\label{sec:VirtRealCorr}
-The results calculated in the previous chapter are not the full theoretical predictions for the different processes but only the first term in a perturbation series of $\alpha_s$.\\
-This section describes the necessary steps in the calculation of the squark production cross section at next-to-leading-order, i.e. its $\mathcal{O}(\alpha_s)$-correction.\\
+The results calculated in the previous chapter are not the full theoretical predictions for the cross sections of the different processes but only the first term in a perturbation series of $\alpha_s$.\\
+This section describes the necessary steps in the calculation of the squark production cross section at next-to-leading order, i.e. its $\mathcal{O}(\alpha_s)$-correction.\\
 \ignore{Reason validity of perturbation theory in this context.}
@@
 \subsection{Virtual Correction}
-According to quantum field theory the $\mathcal{O}(\alpha_s)$ correction to a tree level process includes the computation of one-loop diagrams such as shown in fig.
+According to quantum field theory the $\mathcal{O}(\alpha_s)$ correction to a tree-level process includes the computation of one-loop diagrams such as shown in fig.
 \ref{fig:1loopdiagrams}.
-To yield $\mathcal{O}(\alpha_s)$ corrections in the cross section the interference term between the one-loop amplitude $\mathcal{M}^{\mathrm{1L}}$ and the Born amplitude $\mathcal{M}^{\mathrm{B}}$ needs to be considered.
-However the virtual amplitude
+To yield $\mathcal{O}(\alpha_s)$ corrections in the cross section, the interference term between the one-loop amplitude $\mathcal{M}^{\mathrm{1L}}$ and the Born amplitude $\mathcal{M}^{\mathrm{B}}$ needs to be considered.
 \begin{align}
-\left( \mathcal{M}^{\mathrm{V}} \right)^2 = \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} + \mathcal{M}^{\mathrm{1L}} \mathcal{M}^{\mathrm{B}\ast} = 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right)
+\left| \mathcal{M}^{\mathrm{B}} + \mathcal{M}^{\mathrm{1L}} \right|^2 &= \left| \mathcal{M}^{\mathrm{B}} \right|^2 + \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} + \mathcal{M}^{\mathrm{1L}} \mathcal{M}^{\mathrm{B}\ast} + \left| \mathcal{M}^{\mathrm{1L}} \right|^2\nonumber\\
+&= \left| \mathcal{M}^{\mathrm{B}} \right|^2 + 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right) + \mathcal{O}(\mbox{2-loop})
 \end{align}
-contains divergences. These come from integrals over undetermined momentum and energy of particles running in loops.
+However, this term contains divergences. These come from integrals over undetermined momentum and energy of particles running in loops.
 \begin{figure}[!htbp]
@@
 \caption{A selection of diagrams contributing to the 1-loop matrix element for squark production.
-Each diagram is a representative of a certain diagram type.
-In the first line an example for a self-energy and a vertex-correction diagram is shown.
+Each diagram is a representative of a certain topology.
+In the first line, an example for a self-energy and a vertex-correction diagram is shown.
 The second line lists typical box-diagrams: a three-point box and a four-point box.}\label{fig:1loopdiagrams}
@@
 \end{figure}
-Due to their origin these divergences are referred to as ultraviolet (UV) and infrared divergences (IR).
+Due to their origin these divergences are referred to as ultraviolet (UV) or infrared divergences (IR).
 Ultraviolet divergences occur when loop momenta and energy tend to infinity which corresponds to arbitrary short distance interactions.
@@
 In this thesis the computation of amplitudes is performed in $D = 4-2\epsilon$ dimensions in order to regularize infinities.
-Ultraviolet divergences show then up as single poles in $\epsilon$.
+Ultraviolet divergences then show up as single poles in $\epsilon$.
 The renormalization will be discussed in detail in section \ref{sec:renMRSSM} and \ref{sec:LSZ}.\\
-Having removed the ultraviolet divergences the matrix element is not free of divergences as it comprises infrared divergences.
+Having removed the ultraviolet divergences the matrix element is not free of divergences as it still comprises infrared divergences.
 These split into soft and collinear (or mass) singularities\footnote{The names differ in the literature.
-Often infrared divergences are used as a synonym for soft divergences.} which cannot be removed by means of renormalization.
-These additional singularities show up as single and double poles of $\epsilon$ in the matrix element $\mathcal{M^{\mathrm{1L}}}$ and the virtual cross section which is obtained after performing the 2-body phase space  integration as in eq.
-\eqref{eq:sigma_tree} but over $\left(\mathcal{M^{\mathrm{V}}}\right)^2$:
+Often infrared divergences are used as a synonym for soft divergences.
+The name soft and collinear divergences is explained within the next section} which cannot be removed by means of renormalization.
+These additional singularities show up as single and double poles in $\epsilon$ in the matrix element $\mathcal{M^{\mathrm{1L}}}$ and the virtual cross section which is obtained after performing the 2-body phase space integration as in eq.
+\eqref{eq:sigma_tree} but over $2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right)$:
 \begin{align}
 \frac{\mbox{d}^2 \sigma^{\mathrm{V}}}{\mbox{d}t\ \mbox{d}u} =& \frac{K_{ab}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_1^2m_2^2}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_1^2m_2^2)\nonumber\\
-&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum \left(\mathcal{M}^{\mathrm{V}}\right)^2.\label{eq:diffsigma}
+&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right).\label{eq:diffsigma}
 \end{align}
-The single poles correspond to soft or collinear divergences whereas the double poles correspond to the coincidence of soft and collinear divergences.
+The single poles correspond to soft and collinear divergences whereas the double poles correspond to the coincidence of soft and collinear divergences.
 
@@
 A crucial thing to recognize in the calculation of the $\mathcal{O}(\alpha_s)$ correction to the squark production cross section is that not only virtual corrections but also real corrections give rise to this physical observable.
-This is because one does not measure the final state partons but the jets in which they hadronize in, due to confinement.
-This means that a radiation of a massless particle whose energy tends to zero or the radiation of a  particle which is collinear to one of the final state particles is in experiment measured as a two jet event even though there are three particles in the final state of the calculation.\\
+This is because one does not measure final state partons but jets, which consist of hadrons which in turn consist of partons.
+This means that the radiation of a massless particle whose energy tends to zero or the radiation of a particle which is collinear to one of the final state partons of the tree-level process can in experiment not be distinguished from the tree-level process, for both processes may give rise to the same number of jets.
+Ergo, the cross section of squark production at $\mathcal{O}(\alpha_s^3)$ is given by
+\begin{align}
+\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}},
+\end{align}
+where $\sigma^{\mathrm{R}}$ donates the cross section arising from real corrections.
 However, real corrections also contain divergences.
-Including these contributions to the cross section causes the cancellation of single poles coming from soft divergences and the cancellation of double poles.
-At this point the only singularities which are left in the cross section are the collinear ones.\\
+To see how these arise, consider the second diagram in fig.
+\ref{fig:RealGluon}.
+The propagator of the quark which radiates off a gluon gives a contribution of the form
+\begin{align}
+\frac{1}{(p_q + p_g)^2 - m_q^2} = \frac{1}{p_q \cdot p_g} = \frac{1}{2E_qE_g(1-\beta_q \cos \theta_{qg})} \hspace{2cm} \mathrm{with}\ \beta_q = \frac{|\vec{p}_q|}{E_q}
+\end{align}
+to the diagram in question.
+Here, $p_q$, $p_g$ ($E_q$, $E_g$) are the quark's and gluon's four-momentum (energy) and $\theta_{qg}$ is the angle between the quark's and gluon's three-momentum.
+One observes two potentially singular limits
+\begin{align}
+\mathrm{soft\ gluon:}& \hspace{1cm} E_g \to 0\\
+%& \hspace{1cm} E_q \to 0 \hspace{1cm} \mathrm{if}\ m_q \to 0\\
+\mathrm{collinear\ particles:}& \hspace{1cm} \theta_{qg} \to 0 \hspace{1cm} \mathrm{if}\ m_q \to 0.\label{eq:collLimit}
+\end{align}
+Including these singularities into the cross section causes the cancellation of single poles coming from the virtual cross section and the soft divergences coming from the real cross section as well as the cancellation of double poles.
+At this point the only singularities which are left in the sum of real and virtual cross section are collinear ones, coming from the real correction.
 \begin{figure}[!htbp]
@@
 \caption{A selection of real gluon emission diagrams contributing to squark production.
-Again each diagram is a representative of a certain diagram type.
+Each diagram is a representative of a certain diagram type.
 The first one is final state gluon emission, the second one initial state gluon radiation and the third one is the radiation of a gluon from a virtual particle within the diagram.}\label{fig:RealGluon}
 \end{center}
-\end{figure}
-To see how these are removed, consider the second diagram in fig. \ref{fig:RealGluon}. The propagator of the quark which radiates off a gluon gives a contribution of the form
+\end{figure}\\
+To see how these are removed, consider the collinear limit \eqref{eq:collLimit}.
+Within this limits the inner quark can almost be considered as on-shell which means that it may travel a long distance between the emission of a gluon and taking part in the actual interaction.
+This suggest that some divergences may come from the incoming hadron and are actually not associated with the hard interaction.
+In fact this turns out to be the case: The remaining collinear divergences have a generic form and can be absorbed into the parton density functions.
+Within the $\overline{\mathrm{MS}}$-scheme, the redefinition of parton density functions is given by:\cite{Harris:2001sx}
 \begin{align}
-\frac{1}{(p_q + p_g)^2 - m_q^2} = \frac{1}{p_q \cdot p_g} = \frac{1}{2E_qE_g(1-\beta_q \cos \theta_{qg})} \hspace{2cm} \mathrm{with}\ \beta_q = \frac{\vec{p}_q}{E_q}
+f_{P_i / H}(x,\mu_f) = f(x) + \left( -\frac{1}{\epsilon} \right)\left[ \frac{\alpha_s}{2\pi} \frac{\Gamma(1-\epsilon)}{\Gamma(1-2\epsilon)} \left( \frac{4\pi\mu_R^2}{\mu_F^2} \right)^\epsilon\right] \int_1^x\frac{\mathrm{d}z}{z} P_{P_i P_j}(z)f_{P_j / H}(\frac{x}{z}).
 \end{align}
-to the diagram in question.
-Here, $p_q$, $p_g$ ($E_q$, $E_g$) are the quark's and gluon's four-momentum (energy) and $\theta_{qg}$ is the angle between the quark's and gluon's three-momentum.
-One observes two potentially singular limits
-\begin{align}
-\mathrm{soft\ gluon:}& \hspace{1cm} E_g \to 0\\
-%& \hspace{1cm} E_q \to 0 \hspace{1cm} \mathrm{if}\ m_q \to 0\\
-\mathrm{collinear\ particles:}& \hspace{1cm} \theta_{qg} \to 0 \hspace{1cm} \mathrm{if}\ m_q \to 0.
-\end{align}
-Within these limits the inner quark can almost be considered as on-shell which means that it may travel a long distance between the emission of a gluon and taking part in the actual interaction.
-This suggest that some divergences may come from the incoming hadron and are actually not associated with the interaction.
-In fact this turns out to be the case: The remaining collinear divergences have a generic form (given in [...]) and can, by redefinition, be absorbed into the parton density functions.
-This procedure is referred to as mass factorization \cite{dissertori2003quantum}.
-In fact the Kinoshita-Lee-Naunberg-Theorem \cite{1962JMP.....3..650K},\cite{PhysRev.133.B1549} guarantees the finiteness of sufficiently inclusive observables.\\
-Figure \ref{fig:DivergenceSummary} summarizes the required steps to render the next-to-leading-order cross section finite.
+Here, the indices $P_i$ label partons, i.e.
+quarks or the gluon, and $H$ labels the hadron in which the partons are confined.
+$\Gamma(\hdots)$ is the Gamma function and $P_{P_i P_j}(x)$ are the Altarelli-Parisi-kernels\cite{Altarelli:1977zs} which are a measure for the propability of finding a parton $P_i$ with momentum fraction $x$ within a parton $P_j$.
+This procedure of removing collinear divergences is referred to as mass factorization \cite{dissertori2003quantum}.\\
+In fact, apart from this removal of collinear divergences, the Kinoshita-Lee-Naunberg-Theorem \cite{1962JMP.....3..650K},\cite{PhysRev.133.B1549} guarantees the finiteness of sufficiently inclusive observables, i.e.
+the cancellation of soft divergences between virtual and real corrections.\\
+Figure \ref{fig:DivergenceSummary} summarizes the required steps to render the next-to-leading order cross section finite.
 \begin{figure}[H]
@@
 	\node [block1a] at (0,-2) (Mvirtren) {$\mathcal{M}^{\mathrm{1L}}$ is IR-divergent};
-	\path [line, line width = 1] (Mvirt) --node[right] {renormalize} (Mvirtren);
+	\path [line, line width = 1] (Mvirt) --node[right] {renormalization} (Mvirtren);
 	\node [block1b] at (0,-4) (svirtren) {$\sigma^{\mathrm{virt}}$ is IR-divergent};
 	\node [block2b] at (6,-4) (sreal) {$\sigma^{\mathrm{real}}$ is IR-divergent};
-	\path [line, line width = 1] (Mvirtren) --node[right] {integrate phase space} (svirtren);
-	\path [line, line width = 1] (Mreal) --node[right] {integrate phase space} (sreal);
+	\path [line, line width = 1] (Mvirtren) --node[right] {phase space integration} (svirtren);
+	\path [line, line width = 1] (Mreal) --node[right] {phase space integration} (sreal);
 	\node [block2b] at (6, -6) (srealfac) {$\sigma^{\mathrm{real}}$ is IR-divergent};
@@
 \ref{fig:RealGluon}.
-In order to extract the singularities the so called ``two-cut phase space slicing method''[cite??] has been adopted.
-Within this approach the phase space has been divided into different regimes: a soft part ($S$), a hard collinear part ($HC$) and a hard non-collinear part ($H\overline{C}$):
+In order to extract the singularities the so called ``two-cut phase space slicing method''\cite{Harris:2001sx} has been adopted.
+Within this approach, the phase space has been divided into different regimes: a soft part ($S$), a hard collinear part ($HC$) and a hard non-collinear part ($H\overline{C}$):
 \begin{align}
@@
 \end{align}
-In the soft part the energy of the outgoing gluon is only integrated up to  $\delta_s \frac{\sqrt{s}}{2}$ where $\delta_s$ is a cut on which the final result must not depend on.
+In the soft part, the energy of the outgoing gluon is only integrated up to  $\delta_s \frac{\sqrt{s}}{2}$ where $\delta_s$ is a cut on which the final result must not depend on and $\sqrt{s}$ is the center of mass energy of the colliding partons.
 A second cut $\delta_c$ is introduced to separate the collinear from the non-collinear region.
-After deviding the phase space in the three mentioned part, each integration is performed analytically in $D = 4 - 2\epsilon$ dimensions.
+After dividing the phase space into the three mentioned parts, each integration is performed separately.
+In the parts containing divergences, i.e.
+the soft and hard collinear part, the integration over the gluons four-momentum is performed analytically in $D = 4 - 2\epsilon$ dimensions.
 After performing mass factorization and adding up all three contributions, the real corrections do not depend on the two cut parameters $\delta_s$ and $\delta_c$.

### 2016-07-09 figures/MatrixEl/MatrixEl.py

@@ -72,28 +72,28 @@ plt.rcParams.update({'font.size': 22})
 plt.xlabel(r"$t$ in $10^6$ GeV$^2$")#, size = 22)
 
 # plot without poles
-#plt.ylabel("(Absolute) Squared Matrix Element")
-#plt.axis([min(t/10**6) - 1.1,max(t/10**6) + 1.1,0,1.4])
-#plt.plot(t/10**6, matrix_LO_Tree, lw=2, ls="-", c='black', label = r"$\frac{1}{4\cdot 9}\sum|\mathcal{M}^{\mathrm{B}}_{\mathrm{MRSSM}}|^2$ mit LO $\alpha_s$")
-#plt.plot(t/10**6, matrix_NLO_Tree, lw=2, ls="--", c='red', label = r"$\frac{1}{4\cdot 9}\sum|\mathcal{M}^{\mathrm{B}}_{\mathrm{MRSSM}}|^2$ mit NLO $\alpha_s$")
-#plt.plot(t/10**6, matrix_NLO_Tree+matrix_NLO_Virt, lw=2, ls="-", c='red', label = r"$\frac{1}{4\cdot 9}\sum|\mathcal{M}^{\mathrm{B}}_{\mathrm{MRSSM}}|^2 + \frac{1}{4\cdot 9}\sum(\mathcal{M}^{\mathrm{V}}_{\mathrm{MRSSM}})^2$ mit NLO $\alpha_s$")
-#first_window.fill_between(t/10**6, matrix_NLO_Tree, matrix_NLO_Tree+matrix_NLO_Virt, 
-#facecolor=[1,90./100,90./100], color =[1,80./100,80./100], linestyle="-", label = r"$\frac{1}{4\cdot 9}\sum(\mathcal{M}^{\mathrm{V}}_{\mathrm{MRSSM}})^2$ mit NLO $\alpha_s$")
+plt.ylabel("(Absolute) Squared Matrix Element")
+plt.axis([min(t/10**6) - 1.1,max(t/10**6) + 1.1,0,1.4])
+plt.plot(t/10**6, matrix_LO_Tree, lw=2, ls="-", c='black', label = r"$\frac{1}{4\cdot 9}\sum|\mathcal{M}^{\mathrm{B}}_{\mathrm{MRSSM}}|^2$ mit LO $\alpha_s$")
[…]

### 2016-07-09 Renormalization.tex
modelfile explanation

@@
 \subsection{The Renormalized Matrix Element}
-After having renormalized the matrix element for squark production all UV-divergences are removed.
-This has been achieved by extending the model file, generated by \texttt{SARAH} with counterterm Feynman rules and the above calculated renormalization constants.
+This section explains how the renormalization of the RSQCD is implemented in the framework of the automated calculation and gives intermediate results in the form of the renormalized matrix element.
+
+\subsubsection{Implementation into the Model File}
+Within the automated calculation, the renormlization of the matrix element for squark production has been achieved by extending the model file, generated by \texttt{SARAH} with counterterm Feynman rules and renormalization constants.\\
 The derivation of the counterterm Feynman rules has been performed by the author whereas the implementation into the modelfile was mainly done by Philip Dießner, another member of the group.
+To explain the implementation, the quark-squark-gluino vertex is considered, as an example.
+\begin{lstlisting}[style=MyMathematica]
+C[F[3, {gt1, ct1}], F[15, {ct2}], -S[13, {gt3, ct3}]] == {{
+((-I)*g3*Lam[ct2, ct3, ct1]*(Conjugate[ZUL[gt1, 1]]*ZU[gt3, 1] + Conjugate[ZUL[gt1, 2]]*ZU[gt3, 2] + Conjugate[ZUL[gt1, 3]]*ZU[gt3, 3]))/Sqrt[2],
+((-I)*(dZFu1[gt1]/2+dZSu1[gt3]/2+dZGlL1/2+dZgs1+dZgs1restore)*g3*Lam[ct2, ct3, ct1]*(Conjugate[ZUL[gt1, 1]]*ZU[gt3, 1] + Conjugate[ZUL[gt1, 2]]*ZU[gt3, 2] + Conjugate[ZUL[gt1, 3]]*ZU[gt3, 3]))/Sqrt[2]
+}, {0,0}}
+\end{lstlisting}
+The names of the particles within the model are given in the \texttt{FeynArts} manual\cite{FeynArtsManual} when  \texttt{MSSMQCD.mod}, the QCD extention of the MSSM model file is explained:\\ 
+\mbox{\texttt{F[3,$\left\{ \right.$gt1, ct1$\left.\right\}$]}} is an up-type quark of the \texttt{gt1}'th generation with color \texttt{ct1} and \texttt{F[15,$\left\{ \right.$ct2$\left.\right\}$]} is a gluino with color \texttt{ct2}.
+However, in comparison to \cite{FeynArtsManual}, there is a slight difference in the definition of squarks.
+Whereas the MSSM modelfile \texttt{MSSMQCD.mod} has three indices to label squarks, the model file generated by \texttt{SARAH} uses only two: \texttt{-S[13,$\left\{ \right.$ gt3, ct3$\left.\right\}$]} labels an anti up-type squark of mass eigenstate \texttt{gt3} and color \texttt{ct3}.
+This means more specifically that \texttt{gt3}$\in \left\{ 1,2,3 \right\}$ labels the ``left-handed" squarks with increasing mass and \texttt{gt3}$\in \left\{ 4,5,6 \right\}$ the ``right-handed`'' squarks with increasing mass.\\
+The syntax of the model file, also described in \cite{FeynArtsManual}, is like $\left\{\left\{\mathrm{L},\mathrm{L}^{ct}\right\},\left\{\mathrm{R},\mathrm{R}^{ct}\right\}\right\}$, where the shortcuts are explained in table \ref{tab:Modelfille}.
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{c?c}
+Shortcut & Meaning\\
+\hlinewd{2pt}
+L & coupling proportional to the projector $P_L$ \\
+L$^\mathrm{ct}$ & counterterm for L \\
+R & coupling proportional to the projector $P_R$ \\
+R$^\mathrm{ct}$ & counterterm for R \\
+\end{tabular}
+\caption{Explanation of the vertex structure in the above given mode extract.}\label{tab:Modelfille}
+\end{center}
+\end{table}
+Within the above given extract of the model file, \texttt{Lam} are the Gell-Mann matrices and \texttt{ZU} and \texttt{ZUL} are mixing matrices which are equated to the unit matrix, as there is no squark mixing in the MRSSM and the CKM-matrix is also approximated with the unit matrix.\\
+Equipped with that knowledge, one sees that this Feynman rule is the Feynman rule \circled{16b} from Appendix \ref{sec:FeynmanRules}.\\
+\\
 The renormalization constants for masses and fields are calculated by \texttt{FormCalc} functions like \texttt{MassRC} and \texttt{FieldRC}\cite{FormCalcManual}. 
-Their result has been checked with the above calculated renormalization constants.
-\begin{lstlisting}
+\begin{lstlisting}[style=MyMathematica]
 RenConst[dZFu1[gen_]] :=FieldRC[F[3,{gen}]][[1]]
@@
 \end{lstlisting}
+The first two lines encode the field renormalization constant of up- and down-type quarks.
+The function \texttt{FieldRC} actually calculates two renormalization constants when the argument is a fermion field: the left- and right-handed part.
+But these terms are identical since electroweak interactions are not considered within the modelfile.
+It therefore suffices to just pick the first element of the list.
+This is indicated with the addendum $\texttt{[[1]]}$.\\
+The next block of the code provides the renormalization constants of up- and down-type squarks, before the ensuing block deals with the gluino.
+Here, the predefined function \texttt{xZfL1} (\texttt{xZfR1}) is used to extract the field renormalization constant of the left- (right-) handed component of the Dirac-spinor as they couple differently, like already discussed.\\
+Finally the gauge coupling renormalization and the supersymmetry restoring counterterm are implemented, before the gluon field is renormalized.
+The necessity of the parameter \texttt{FiniteGs} will be explained shortly.\\
+\\
+The parameter \texttt{FiniteGs} has been introduced as these terms should only contribute if \texttt{SetLambda}$\to 0$.
+In all other choices \texttt{FiniteGs} has to be replaced with zero instead of one.
+For more details on how the renormalization works within \texttt{FormCalc}, see the manual \cite{FormCalcManual}.\\
+
+After having renormalized the matrix element for squark production all UV-divergences are removed.\\
+
+Their result has been checked with the above calculated renormalization constants.\\
 To keep track of all divergences, the calculation in \texttt{FormCalc} has been performed with the option: \texttt{Dimension} $\to 0$ which is the only opportunity to really work in $D$ dimensions, i.e.
@@
 To get a notion for the \texttt{FormCalc} output, the following line shows the  off-shell amplitude of the quark self-energy in terms of loop integrals and \texttt{Dminus4}
-%\begin{lstlistings}
-Amp[{{F[3, {1, Col1}], k[1], 0, {}}} -> {{F[3, {1, Col2}], k[2], 
-     0, {}}}][(1/(\[Pi]^2))
-  g3^2 ((1/6 + Dminus4/12) (B0i[bb0, Pair[k[1], k[1]], 0, 0] + 
-        B0i[bb1, Pair[k[1], k[1]], 0, 0]) - 
-     1/6 B0i[bb1, Pair[k[1], k[1]], MassGlu^2, MassSu[1]^2]) Mat[(
-SequenceForm["<", "u", 2, "|", 6, ",", 
-FormCalc`k[1], "|", "u", 1, ">"]) SUNT[Col1, Col2]] + (1/(\[Pi]^2))
-  g3^2 ((1/6 + Dminus4/12) (B0i[bb0, Pair[k[1], k[1]], 0, 0] + 
-        B0i[bb1, Pair[k[1], k[1]], 0, 0]) - 
-     1/6 B0i[bb1, Pair[k[1], k[1]], MassGlu^2, MassSu[4]^2]) Mat[(
-SequenceForm["<", "u", 2, "|", 7, ",", 
-FormCalc`k[1], "|", "u", 1, ">"]) SUNT[Col1, Col2]]]
-%\end{lstlistings}
+\begin{lstlisting}[style=MyMathematicaOutput]
+Amp[{{F[3, {1, Col1}], k[1], 0, {}}} -> {{F[3, {1, Col2}], k[2], 0, {}}}]
+[(1/([Pi]^2)) g3^2 ((1/6 + Dminus4/12) (B0i[bb0, Pair[k[1], k[1]], 0, 0] 
++ B0i[bb1, Pair[k[1], k[1]], 0, 0]) - 1/6 B0i[bb1, Pair[k[1], k[1]], MassGlu^2, MassSu[1]^2]) Mat[([<u2|6 k[1]|u1>]) SUNT[Col1, Col2]] 
++ (1/([Pi]^2)) g3^2 ((1/6 + Dminus4/12) (B0i[bb0, Pair[k[1], k[1]], 0, 0] 
++ B0i[bb1, Pair[k[1], k[1]], 0, 0]) - 1/6 B0i[bb1, Pair[k[1], k[1]], MassGlu^2, MassSu[4]^2]) Mat[(<u2|7 k[1]|u1>]) SUNT[Col1, Col2]]]
+\end{lstlisting}
 To extract infrared divergences, \texttt{LoopTools} has been used.

### 2016-07-09 Masterarbeit.tex
Introduction, NEXT STEP: REDO PLOTS WITH SQUARK PRODUCTION AT TREE LEVEL WHICH DOES INCLUDE ALSO ud to susd, IN ADITION TO ds to sdsu
uncertainties for squark production in table
a lot of changes
rest of chapter about matrix element

@@
   \begin{singlespace}\begin{center}\large
-   Institut für Kern- und Teilchenphysik Physik \\
+   Institut für Kern- und Teilchenphysik \\
    Fachrichtung Physik \\
@@
 
+% Leerseite
+\thispagestyle{empty}
+\cleardoublepage
+
 % Gutachterseite
 \thispagestyle{empty}\vspace*{48em}
-Eingereicht am xx.~Monat~20xx\vspace{1.5em}
+Eingereicht am 15.~Juli~2016\vspace{1.5em}
 \par{\large\begin{tabular}{ll}
- 1. Gutachter: & Prof.~Dr.~XX \\
- 2. Gutachter: & Prof.~Dr.~YY \\
+ 1. Gutachter: & Prof.~Dr.~Dominik Stöckinger \\
+ 2. Gutachter: & Prof.~Dr.~Arno Straessner \\
 \end{tabular}}
 \newpage
+
+% Leerseite
+\thispagestyle{empty}
+\cleardoublepage
 
@@
 
+% Leerseite
+\thispagestyle{empty}
+\cleardoublepage
+
 \tableofcontents
@@
 \pagenumbering{arabic}
-\section{Introduction}
 \input{Introduction}

### 2016-07-09 Renormalization.tex
rest of chapter about matrix element

@@
 
-\subsection{The Renormalized Matrix Element}
+\subsection{The Renormalization of the Matrix Element}
 This section explains how the renormalization of the RSQCD is implemented in the framework of the automated calculation and gives intermediate results in the form of the renormalized matrix element.
@@
 It therefore suffices to just pick the first element of the list.
-This is indicated with the addendum $\texttt{[[1]]}$.\\
+This is achieved with the addendum $\texttt{[[1]]}$.\\
 The next block of the code provides the renormalization constants of up- and down-type squarks, before the ensuing block deals with the gluino.
-Here, the predefined function \texttt{xZfL1} (\texttt{xZfR1}) is used to extract the field renormalization constant of the left- (right-) handed component of the Dirac-spinor as they couple differently, like already discussed.\\
+Here, the predefined function \texttt{xZfL1} (\texttt{xZfR1}) is used to extract the field renormalization constant of the left- (right-) handed component of the Dirac-spinor.\\
 Finally the gauge coupling renormalization and the supersymmetry restoring counterterm are implemented, before the gluon field is renormalized.
 The necessity of the parameter \texttt{FiniteGs} will be explained shortly.\\
-\\
-The parameter \texttt{FiniteGs} has been introduced as these terms should only contribute if \texttt{SetLambda}$\to 0$.
-In all other choices \texttt{FiniteGs} has to be replaced with zero instead of one.
-For more details on how the renormalization works within \texttt{FormCalc}, see the manual \cite{FormCalcManual}.\\
-
-After having renormalized the matrix element for squark production all UV-divergences are removed.\\
-
-Their result has been checked with the above calculated renormalization constants.\\
-To keep track of all divergences, the calculation in \texttt{FormCalc} has been performed with the option: \texttt{Dimension} $\to 0$ which is the only opportunity to really work in $D$ dimensions, i.e.
+The result of these renormalization constants has been checked with the above calculated renormalization constants.
+
+\subsubsection{The Renormalized Matrix Element}
+After providing the model file with renormalization constants and counterterm Feynman rules, the matrix element for squark production can be renormalized.
+For more details on how the renormalization works within \texttt{FormCalc}, see the manual \cite{FormCalcManual}.
+To check whether all UV-divergences have been removed, the \texttt{FormCalc} function \texttt{UVDivergentPart} has been used.\\
+However, the matrix element still contains IR-divergences.
+To keep track of these divergences, the calculation in \texttt{FormCalc} has been performed with the option: \texttt{Dimension} $\to 0$ which is the only opportunity to really work in $D$ dimensions, i.e.
 the result contains a quantity \texttt{Dminus4} which equals $-2\epsilon$ in DREG.
@@
 To extract infrared divergences, \texttt{LoopTools} has been used.
-This  tool provides the function \texttt{SetLambda} which can be set to 0, $-1$ or $-2$ to extract the finite part, single pole or double pole of  scalar integrals.
-This allows for numerically extracting the coefficients of $\epsilon^i$ with $i \in \left\{ 0,-1,-2 \right\}$ of the absolute squared matrix amplitude.
-The respective poles of $|\mathcal{M}^{\mathrm{V}}_{\mathrm{MRSSM}}(uu \to \tilde{u}_L\tilde{u}_R)|^2$ are shown in figure \ref{fig:MatrixElement}.
-Note, that the extraction of the single pole does not only involve setting the option \texttt{SetLamda} $\to-1$ and \texttt{Dminus4}$\to 0$, but also setting \texttt{SetLamda}$\to-2$ and \texttt{Dminus4} $\to -2$ and subtract the term obtained by \texttt{SetLamda}$\to-2$ and \texttt{Dminus4} $\to 0$.
+This package provides the function \texttt{SetLambda} which can be set to 0, $-1$ or $-2$ to extract the finite part, $\frac{1}{\epsilon}$ pole or $\frac{1}{\epsilon^2}$ pole of scalar integrals in dimensioanl regularisation.
+\texttt{SetLambda} includes both, UV and IR poles.
+In fact, the function \texttt{SetUVDiv} controls whether UV divergences are kept (\texttt{SetUVDiv}$\to 1$) or discarded (\texttt{SetUVDiv}$\to 0$), which presents another check of UV-finiteness which has been performed.\\
+However, using \texttt{SetLambda} allows for numerically extracting the coefficients of $\epsilon^i$ with $i \in \left\{ 0,-1,-2 \right\}$ of the absolute squared matrix amplitude.
+The respective poles of $|\mathcal{M}^{\mathrm{V}}_{\mathrm{MRSSM}}(uu \to \tilde{u}_L\tilde{u}_R)|^2$ are shown in figure \ref{fig:MatrixElementPoles}.
+Note, that the extraction of the single pole does not only involve setting the option \texttt{SetLamda} $\to-1$ and \texttt{Dminus4}$\to 0$, but also setting \texttt{SetLamda}$\to -2$ and \texttt{Dminus4} $\to -2$ and subtracting the term obtained by \texttt{SetLamda}$\to-2$ and \texttt{Dminus4} $\to 0$.
 In doing so, one accounts for the contraction of double poles with terms of $\mathcal{\epsilon}$.
 The same logic implies to the extraction of finite terms.\\
-\\
-In addition the tree-level absolute squared matrix amplitude with leading order $\alpha_s$ is compared with its analogue with next-to-leading order $\alpha_s$ and virtual absolute squared matrix amplitude.
+Now it becomes clear, why the parameter \texttt{FiniteGs} has been introduced.
+As \texttt{SetLambda} only replaces the loop integrals but not every other term in an expression with the corresponding prefactor of $\epsilon^i$, \texttt{FiniteGs} needs to be set to zero when \texttt{SetLambda} is set to $-1$ or $-2$ and \texttt{FiniteGs}$\to 1$ when \texttt{SetLambda}$\to 0$.
+\begin{figure}[H]
+\begin{center}
+\includegraphics[scale=.5]{figures/MatrixElement_Poles.png}
+\caption{Coefficients of $\mathcal{O}(\epsilon^0)$, $\mathcal{O}(\epsilon^{-1})$ and $\mathcal{O}(\epsilon^{-2})$ terms of $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$ of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM as a function of the Mandelstam variable $t$.
+External helicities and colors are averaged.
+The parameters are fixed to $m_{\tilde{q}} = \mu = \unit[1000]{GeV}$, $m_{\tilde{g}} = \unit[2000]{GeV}$, $m_{\sigma} = \unit[5000]{GeV}$ and $\sqrt{s} = \unit[6000]{GeV}$ which is the partonic center of mass energy.}\label{fig:MatrixElementPoles}
+\end{center}
+\end{figure}
+The upper plot in figure \ref{fig:MatrixElement} shows the finite contributions from loop diagrams with different topology to $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$ as a function of the Mandelstam variable $t$ where $\frac{1}{4\cdot 9}$ is the averaging over final state spins and colors.
+The lower plot displays the tree-level absolute squared matrix amplitude with leading order $\alpha_s$ which is compared to its analogue with next-to-leading order $\alpha_s$ and virtual correction $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$.
 The latter is not given analytically.
-All $|\mathcal{M}|^2$ are color and spin averaged in the final state and summed over in the initial state.
-\begin{figure}[!htpb]
-\begin{center}
-\includegraphics[scale=.5]{figures/MatrixElement_Poles.png}
-\caption{Coefficients of $\mathcal{O}(\epsilon^0)$, $\mathcal{O}(\epsilon^{-1})$ and $\mathcal{O}(\epsilon^{-2})$ terms of the absolute squared matrix element of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM as a function of the Mandelstam variable $t$.
-External helicities and colors are averaged.
-The parameters are fixed to $m_{\tilde{q}} = \mu = \unit[1000]{GeV}$, $m_{\tilde{g}} = \unit[2000]{GeV}$, $m_{\sigma} = \unit[5000]{GeV}$ and $\sqrt{s} = \unit[6000]{GeV}$ which is the partonic center of mass energy.}
-\end{center}
-\end{figure}
-
+All terms are color and spin averaged in the final state and summed over in the initial state.
 \begin{figure}[!htpb]

### 2016-07-09 figures/MatrixEl/MatrixEl.py

@@ -72,28 +72,28 @@ plt.rcParams.update({'font.size': 22})
 plt.xlabel(r"$t$ in $10^6$ GeV$^2$")#, size = 22)
 
 # plot without poles
-plt.ylabel("(Absolute) Squared Matrix Element")
-plt.axis([min(t/10**6) - 1.1,max(t/10**6) + 1.1,0,1.4])
-plt.plot(t/10**6, matrix_LO_Tree, lw=2, ls="-", c='black', label = r"$\frac{1}{4\cdot 9}\sum|\mathcal{M}^{\mathrm{B}}_{\mathrm{MRSSM}}|^2$ mit LO $\alpha_s$")
-plt.plot(t/10**6, matrix_NLO_Tree, lw=2, ls="--", c='red', label = r"$\frac{1}{4\cdot 9}\sum|\mathcal{M}^{\mathrm{B}}_{\mathrm{MRSSM}}|^2$ mit NLO $\alpha_s$")
-plt.plot(t/10**6, matrix_NLO_Tree+matrix_NLO_Virt, lw=2, ls="-", c='red', label = r"$\frac{1}{4\cdot 9}\sum|\mathcal{M}^{\mathrm{B}}_{\mathrm{MRSSM}}|^2 + \frac{1}{4\cdot 9}\sum 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right)$ mit NLO $\alpha_s$")
-first_window.fill_between(t/10**6, matrix_NLO_Tree, matrix_NLO_Tree+matrix_NLO_Virt, 
-facecolor=[1,90./100,90./100], color =[1,80./100,80./100], linestyle="-", label = r"$\frac{1}{4\cdot 9}\sum 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right)$ mit NLO $\alpha_s$")
+#plt.ylabel("(Absolute) Squared Matrix Element")
+#plt.axis([min(t/10**6) - 1.1,max(t/10**6) + 1.1,0,1.4])
+#plt.plot(t/10**6, matrix_LO_Tree, lw=2, ls="-", c='black', label = r"$\frac{1}{4\cdot 9}\sum|\mathcal{M}^{\mathrm{B}}_{\mathrm{MRSSM}}|^2$ mit LO $\alpha_s$")
[…]

### 2016-07-09 NLO.tex
set up of the calculation

@@
 \subsection{The Squark Production Cross Section at Next-to-Leading Order}
-The squark production cross section at next-to-leading order is composed out of three contributions. These are the Born or tree-level cross section, the virtual correction and the real correction. 
+The squark production cross section at next-to-leading order is composed out of three contributions. These are the Born (tree-level) cross section, the virtual correction and the real correction. 
 \begin{align}
@@
 \end{align}
-All three contributions have to be calculated with next-to-leading parton density functions.\\
-It has been checked that for multiple different and quite distinct choices of the parameters $m_{\tilde{q}}$ and $m_{\tilde{g}}$, the double as well as the single poles of the virtual and real correction cancel up to machine precision.
-As the real corrections have been calculated analytically it is possible to quote the double pole.
-With
-\begin{align}
-\sigma^{\mathrm{R}}_{\mathrm{double\ pole}} = -\sigma^{\mathrm{V}}_{\mathrm{double\ pole}} = C(F)\frac{\alpha_s}{\pi}\sigma^{\mathrm{B}} \frac{1}{\epsilon^2}
-\end{align}
-it has a very succinct form. \\
+All three contributions have to be calculated with next-to-leading order parton density functions. The next section summaries how the calculation has been performed.
+
+\subsubsection{The Set Up of the calculation}
 The setup of the calculation is summarized in fig.
@@
 Both the virtual and the Born matrix amplitude have been generated with the \texttt{Mathematica} package \texttt{FeynArts}.
-To this end a modelfile generated by the \texttt{Mathematica} package \texttt{SARAH} has been adjusted by hand to include counterterm Feynman rules and the definition of those counterterms.
-The matrix amplitudes have been processed further to the absolute squared matrix amplitudes by the \texttt{Mathematica} package \texttt{FormCalc} which have then been converted to \texttt{C++} and stored in an output file.\\
-This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of the absolute squared matrix amplitudes numerically by using the package \texttt{LoopTools} \cite{Hahn:1998}.
+To this end a modelfile, generated by the \texttt{Mathematica} package \texttt{SARAH}, has been adjusted to include counterterm Feynman rules and appropriate renormalization constants.
+This procedure was explained in section \ref{sec:MatrixElRen}.
+The matrix amplitudes have been processed further to $\sum|\mathcal{M}^{\mathrm{B}}|^2$ and $ \sum 2\Re (\mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast})$ by the \texttt{Mathematica} package \texttt{FormCalc} before this output has then been converted to a \texttt{C++} readable code and stored in an output file.\\
+This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of $ \sum 2\Re (\mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast})$ numerically by using the package \texttt{LoopTools}.
 Finally the phase space integration and the integration over $x_1$ and $x_2$ is performed by the integration routine ``Cuhre'' which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}.
 The parton density functions are included using \texttt{LHAPDF6}\cite{Buckley:2014ana}\\
-The computation of the real correction has been done by Wojciech Kotlarski, another member of the group. Comment on how real corrections are processed.\\
+The computation of the real corrections have been done by Wojciech Kotlarski, another member of the group.
+To extract the singularities from the real corrections, the ``two cut phase space slicing method'' outlined in section \ref{sec:RealGluonRad}, has been used.
+For the soft and hard collinear limit, the absolute squared matrix element has been calculated with \texttt{FormCalc} and analytically integrated over the gluons four-momentum in $D$ dimensions in \texttt{Mathematica}.
+This has been exported to the \texttt{C++} code to perform the rest of the integration numerically with the \texttt{CUBA} library.
+The matrix element in the hard non-collinear regime has been imported from \texttt{MadGraph5}\cite{Alwall:2014hca}and the whole integration has been performed numerically by the \texttt{CUBA} library.
 \begin{figure}[!htbp]
@@
 	\node [block4] at (-1,0) (Mathematica) {Mathematica notebook};
-	\node [block1a] at (-1,-3) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{B}|^2}$};	
-	\node [block1a] at (-1,-1.5) (notebookV) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{1L}}$ \newline \texttt{FormCalc} $\to 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$};
+	\node [block1a] at (-1,-2.1) (notebookR) {soft/collinear limit: \newline \texttt{FeynArts} $\to \mathcal{M}^{\mathrm{R}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{R}|^2}$};
+	\node [block1a] at (-1,-7) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{B}|^2}$};	
+	\node [block1a] at (-1,-4.7) (notebookV) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{1L}}$ \newline \texttt{FormCalc} $\to$ \newline $2\sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$};
 	\node [block5a] at (7.5,0) (C++) {\texttt{C++} code};
-	\node [block5b] at (3.7,-3.5) (Born) {\underline{Born contribution} \newline \texttt{CUBA} $\to$ num. integration over $t, x_1, x_2$ to $\sigma^{\mathrm{B}}$};
-	\node [block5b] at (7.5,-2.7) (Virt) {\underline{Virtual correction}\newline \texttt{LoopTools} $\to$ computation \newline of $ 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$ \newline \texttt{CUBA} $\to$ num.
-integration over $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$};
-	\node [block5c] at (11.5,-3.3) (Real) {\underline{Real correction}\newline \texttt{MADGRAPH} $\to$ $\mathcal{M}^{\mathrm{R}}$, phase space slicing\newline \texttt{CUBA} $\to$ num.
-integration to $\sigma^{\mathrm{R}}$};
-	\path [line, line width = 1] (1.2,-3) -- (1.9,-3);
-	\path [line, line width = 1] (1.2,-1.5) -- (5.7,-1.5);
-	\node [block6a] at (7.5,-6.5) (Sigma) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}}$};
+	\node [block5b] at (3.7,-7.3) (Born) {\underline{Born contribution} \newline \texttt{CUBA} $\to$ \newline integration over \newline $t, x_1, x_2$ to $\sigma^{\mathrm{B}}$};
+	\node [block5b] at (7.5,-6.5) (Virt) {\underline{Virtual correction}\newline \texttt{LoopTools} $\to$ \newline computation of $ 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$ \newline \texttt{CUBA} $\to$ \newline integration over \newline $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$ };
+	\node [block5c] at (11.5,-4.6) (Real) {\underline{Real correction}\newline phase space slicing: \newline $\bullet$ soft/collinear part \newline from \texttt{Mathematica},\newline \texttt{CUBA} three dimen- \newline sional integration to $\sigma^{\mathrm{R}}_{\mathrm{S}}$ and $\sigma^{\mathrm{R}}_{\mathrm{HC}}$ \newline $\bullet$ hard non-collinear \newline part from \newline \texttt{MADGRAPH}, \newline  \texttt{CUBA} $\to$ seven \newline dimensional \newline integration to $\sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$ \newline $\sigma^{\mathrm{R}} = \sigma^{\mathrm{R}}_{\mathrm{S}} + \sigma^{\mathrm{R}}_{\mathrm{HC}} + \sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$};
+	\path [line, line width = 1] (1.2,-7.0) -- (1.9,-7.0);
+	\path [line, line width = 1] (1.2,-4.9) -- (5.7,-4.9);
+	\path [line, line width = 1] (1.2,-2.0) -- (9.5,-2.0);
+	\node [block6a] at (7.5,-10) (Sigma) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}} + \sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$};
 	\path [line, line width = 1] (Born) -- (Sigma);
 	\path [line, line width = 1] (Virt) -- (Sigma);
-	\path [line, line width = 1] (Real) -- (Sigma);
+	\path [line, line width = 1] (10,-8.45) -- (Sigma);
 \end{tikzpicture}
 \caption{This scheme illustrates the setup of the computation of the next-to-leading order cross section.
-The absolute squared matrix amplitudes of the Born or tree-level contribution and the virtual correction are generated by \texttt{Mathematica} packages and imported into a \texttt{C++} code.
+The (absolute) squared matrix amplitudes of the Born contribution the virtual correction and the real correction in the soft and/or collinear limit are generated by \texttt{Mathematica} packages and imported into a \texttt{C++} code.
+The amplitude from the real corrections is analytically integrated over the gluon's four momentum in $D$ dimensions.
 Loop integrals are evaluated numerically using \texttt{Looptools}.
-For all three contributions the \texttt{CUBA}-library was used for the phase space and $x_1$ and $x_2$ integration to arrive at the cross sections $\sigma^{\mathrm{B}}$, $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{V}}$.
-The real corrections have been calculated by Wojciech Kotlarski, another member of the group.}\label{fig:CalcSetup}
+For the hard non-collinear regime, the matrix amplitude of the real corrections is imported from \texttt{MadGraph5}.
+The \texttt{CUBA}-library was used for all three contributions to perform the remaining integration to arrive at the cross sections $\sigma^{\mathrm{B}}$, $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{R}}$.}\label{fig:CalcSetup}
 \end{center}
-\end{figure}
+\end{figure}\\
+It has been checked that for multiple different and quite distinct choices of the parameters $m_{\tilde{q}}$ and $m_{\tilde{g}}$, the double as well as the single poles of the virtual and real correction cancel up to machine precision.
+As the poles of the real corrections have been calculated analytically, it is possible to quote them.
+The double pole is actually proportional to the Born cross section:
+\begin{align}
+\sigma^{\mathrm{R}}_{\mathrm{double\ pole}} = -\sigma^{\mathrm{V}}_{\mathrm{double\ pole}} = C(F)\frac{\alpha_s}{\pi}\sigma^{\mathrm{B}} \frac{1}{\epsilon^2}.
+\end{align}
 

### 2016-07-09 Renormalization.tex
set up of the calculation

@@
 \begin{align}
-\beta(g_s,\epsilon) &= -\epsilon g_s \left( 1 + \frac{g_s^2}{16\pi^2} L \right) + \beta(g_s) + \mathcal{O}(\mathrm{2-loop})\\
-\beta(g_s) &= \frac{g_s^3}{16\pi^2} \beta_0^L + \mathcal{O}(\mathrm{2-loop}).
-\end{align}
-This is the beta function of QCD first found by Politzer \cite{Politzer:1973fx} Gross and Wilczek \cite{Gross:1973ju}.
+\beta(g_s,\epsilon) &= -\epsilon g_s \left( 1 + \frac{g_s^2}{16\pi^2} L \right) + \beta(g_s) + \mathcal{O}(\mbox{2-loop})\\
+\beta(g_s) &= \frac{g_s^3}{16\pi^2} \beta_0^L + \mathcal{O}(\mbox{2-loop}).
+\end{align}
+This is the beta function of QCD first found by Politzer \cite{Politzer:1973fx}, Gross and Wilczek \cite{Gross:1973ju}.
 This means that renormalizing $g_s$ in the way it is, decouples heavy particles from the $\beta$ function and allows to adopt $\alpha_s = \frac{g_s^2}{4\pi}$ from the parton density functions.
@@
 
-\subsection{The Renormalization of the Matrix Element}
+\subsection{The Renormalization of the Matrix Element}\label{sec:MatrixElRen}
 This section explains how the renormalization of the RSQCD is implemented in the framework of the automated calculation and gives intermediate results in the form of the renormalized matrix element.
@@
 [(1/([Pi]^2)) g3^2 ((1/6 + Dminus4/12) (B0i[bb0, Pair[k[1], k[1]], 0, 0] 
-+ B0i[bb1, Pair[k[1], k[1]], 0, 0]) - 1/6 B0i[bb1, Pair[k[1], k[1]], MassGlu^2, MassSu[1]^2]) Mat[([<u2|6 k[1]|u1>]) SUNT[Col1, Col2]] 
++ B0i[bb1, Pair[k[1], k[1]], 0, 0]) 
+- 1/6 B0i[bb1, Pair[k[1], k[1]], MassGlu^2, MassSu[1]^2]) 
+Mat[([<u2|6 k[1]|u1>]) SUNT[Col1, Col2]] 
 + (1/([Pi]^2)) g3^2 ((1/6 + Dminus4/12) (B0i[bb0, Pair[k[1], k[1]], 0, 0] 
-+ B0i[bb1, Pair[k[1], k[1]], 0, 0]) - 1/6 B0i[bb1, Pair[k[1], k[1]], MassGlu^2, MassSu[4]^2]) Mat[(<u2|7 k[1]|u1>]) SUNT[Col1, Col2]]]
++ B0i[bb1, Pair[k[1], k[1]], 0, 0]) 
+- 1/6 B0i[bb1, Pair[k[1], k[1]], MassGlu^2, MassSu[4]^2]) 
+Mat[(<u2|7 k[1]|u1>]) SUNT[Col1, Col2]]]
 \end{lstlisting}
-To extract infrared divergences, \texttt{LoopTools} has been used.
+To extract infrared divergences, \texttt{LoopTools}\cite{Hahn:1998} has been used.
 This package provides the function \texttt{SetLambda} which can be set to 0, $-1$ or $-2$ to extract the finite part, $\frac{1}{\epsilon}$ pole or $\frac{1}{\epsilon^2}$ pole of scalar integrals in dimensioanl regularisation.
@@
 \end{figure}
-The upper plot in figure \ref{fig:MatrixElement} shows the finite contributions from loop diagrams with different topology to $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$ as a function of the Mandelstam variable $t$ where $\frac{1}{4\cdot 9}$ is the averaging over final state spins and colors.
+The upper plot in figure \ref{fig:MatrixElement} shows the finite contributions from loop diagrams with different topology to $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$ as well as their sum as a function of the Mandelstam variable $t$ where $\frac{1}{4\cdot 9}$ is the averaging over final state spins and colors.
 The lower plot displays the tree-level absolute squared matrix amplitude with leading order $\alpha_s$ which is compared to its analogue with next-to-leading order $\alpha_s$ and virtual correction $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$.

### 2016-07-09 Virt_Real.tex
set up of the calculation

@@
 
-\subsubsection*{Real Gluon Radiation}
+\subsubsection{Real Gluon Radiation}\label{sec:RealGluonRad}
 A representative set of Feynman-diagrams for real gluon emission are shown in fig.
 \ref{fig:RealGluon}.
-In order to extract the singularities the so called ``two-cut phase space slicing method''\cite{Harris:2001sx} has been adopted.
+In order to extract the singularities the so called ``two cut phase space slicing method''\cite{Harris:2001sx} has been adopted.
 Within this approach, the phase space has been divided into different regimes: a soft part ($S$), a hard collinear part ($HC$) and a hard non-collinear part ($H\overline{C}$):
@@
 
-\subsubsection*{Real Quark Radiation}
+\subsubsection{Real Quark Radiation}
 As already mentioned before, adding up virtual and real gluon emission contributions results in the cancellation of divergences.

### 2016-07-10 NLO.tex
text in NLO chapter

@@
 \section{Squark Production at One-Loop}
+This section discusses the cross section for squark production at next-to-leading order $\sigma^{\mathrm{NLO}}$.
+To do so, the next section gives a justification why on-shell renormalization has been chosen in section \ref{sec:renMRSSM}.
+After that, the set up of the calculation of the different contributions to $\sigma^{\mathrm{NLO}}$ is explained.
+This includes a remark on how the calculation was sped up.
+Finally the results of the computation are presented in the form of $K$-factors.
+These are then compared to the ones in the MSSM before the thesis closes with an discussion of the behavior of $\sigma^{\mathrm{NLO}}$ in the limit of large sgluon masses.
 
 \subsection{The LSZ Theorem}\label{sec:LSZ}
-The LSZ theorem\cite{Lehmann:1954rq} or LSZ reduction formula prescribes how to obtain the S-matrix element, i.e.
+The LSZ theorem\cite{Lehmann:1954rq}, named after  Harry Lehmann, Kurt Symanzik and Wolfhart Zimmermann, or LSZ reduction formula prescribes how to obtain the S-matrix element, i.e.
 a physical observable, from the time ordered correlation function of the respective field operators.
@@
 \end{align}
-All three contributions have to be calculated with next-to-leading order parton density functions. The next section summaries how the calculation has been performed.
+All three contributions have to be calculated with next-to-leading order parton density functions and $\alpha_s$. The next section summaries how the calculation has been performed.
 
@@
 This procedure was explained in section \ref{sec:MatrixElRen}.
-The matrix amplitudes have been processed further to $\sum|\mathcal{M}^{\mathrm{B}}|^2$ and $ \sum 2\Re (\mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast})$ by the \texttt{Mathematica} package \texttt{FormCalc} before this output has then been converted to a \texttt{C++} readable code and stored in an output file.\\
-This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of $ \sum 2\Re (\mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast})$ numerically by using the package \texttt{LoopTools}.
-Finally the phase space integration and the integration over $x_1$ and $x_2$ is performed by the integration routine ``Cuhre'' which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}.
-The parton density functions are included using \texttt{LHAPDF6}\cite{Buckley:2014ana}\\
-The computation of the real corrections have been done by Wojciech Kotlarski, another member of the group.
-To extract the singularities from the real corrections, the ``two cut phase space slicing method'' outlined in section \ref{sec:RealGluonRad}, has been used.
-For the soft and hard collinear limit, the absolute squared matrix element has been calculated with \texttt{FormCalc} and analytically integrated over the gluons four-momentum in $D$ dimensions in \texttt{Mathematica}.
-This has been exported to the \texttt{C++} code to perform the rest of the integration numerically with the \texttt{CUBA} library.
-The matrix element in the hard non-collinear regime has been imported from \texttt{MadGraph5}\cite{Alwall:2014hca}and the whole integration has been performed numerically by the \texttt{CUBA} library.
-\begin{figure}[!htbp]
+The matrix amplitudes have been processed further to $\sum|\mathcal{M}^{\mathrm{B}}|^2$ and $ \sum 2\Re (\mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast})$ by the \texttt{Mathematica} package \texttt{FormCalc} before this output has then been converted to a \texttt{C++} readable code and stored in an output file.
+\begin{figure}[H]
 \begin{center}
@@
 	\node [block1a] at (-1,-2.1) (notebookR) {soft/collinear limit: \newline \texttt{FeynArts} $\to \mathcal{M}^{\mathrm{R}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{R}|^2}$};
-	\node [block1a] at (-1,-7) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{B}|^2}$};	
-	\node [block1a] at (-1,-4.7) (notebookV) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{1L}}$ \newline \texttt{FormCalc} $\to$ \newline $2\sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$};
+	\node [block1a] at (-1,-8) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{B}|^2}$};	
+	\node [block1a] at (-1,-5.7) (notebookV) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{1L}}$ \newline \texttt{FormCalc} $\to$ \newline $2\sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$};
 	\node [block5a] at (7.5,0) (C++) {\texttt{C++} code};
-	\node [block5b] at (3.7,-7.3) (Born) {\underline{Born contribution} \newline \texttt{CUBA} $\to$ \newline integration over \newline $t, x_1, x_2$ to $\sigma^{\mathrm{B}}$};
-	\node [block5b] at (7.5,-6.5) (Virt) {\underline{Virtual correction}\newline \texttt{LoopTools} $\to$ \newline computation of $ 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$ \newline \texttt{CUBA} $\to$ \newline integration over \newline $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$ };
-	\node [block5c] at (11.5,-4.6) (Real) {\underline{Real correction}\newline phase space slicing: \newline $\bullet$ soft/collinear part \newline from \texttt{Mathematica},\newline \texttt{CUBA} three dimen- \newline sional integration to $\sigma^{\mathrm{R}}_{\mathrm{S}}$ and $\sigma^{\mathrm{R}}_{\mathrm{HC}}$ \newline $\bullet$ hard non-collinear \newline part from \newline \texttt{MADGRAPH}, \newline  \texttt{CUBA} $\to$ seven \newline dimensional \newline integration to $\sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$ \newline $\sigma^{\mathrm{R}} = \sigma^{\mathrm{R}}_{\mathrm{S}} + \sigma^{\mathrm{R}}_{\mathrm{HC}} + \sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$};
-	\path [line, line width = 1] (1.2,-7.0) -- (1.9,-7.0);
-	\path [line, line width = 1] (1.2,-4.9) -- (5.7,-4.9);
+	\node [block5b] at (3.7,-8.3) (Born) {\underline{Born contribution} \newline \texttt{CUBA} $\to$ \newline integration over \newline $t, x_1, x_2$ to $\sigma^{\mathrm{B}}$};
+	\node [block5b] at (7.5,-7.35) (Virt) {\underline{Virtual correction}\newline \texttt{LoopTools} $\to$ \newline computation of $ 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$ \newline \texttt{CUBA} $\to$ \newline integration over \newline $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$ };
+	\node [block5c] at (11.5,-5.1) (Real) {\underline{Real correction}\newline phase space slicing: \newline $\bullet$ soft/collinear part \newline from \texttt{Mathematica},\newline \texttt{CUBA} three dimen- \newline sional integration to $\sigma^{\mathrm{R}}_{\mathrm{S}}$ and $\sigma^{\mathrm{R}}_{\mathrm{HC}}$ \newline $\bullet$ hard non-collinear \newline part from \newline \texttt{MADGRAPH}, \newline  \texttt{CUBA} $\to$ seven \newline dimensional \newline integration to $\sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$ \newline $\sigma^{\mathrm{R}} = \sigma^{\mathrm{R}}_{\mathrm{S}} + \sigma^{\mathrm{R}}_{\mathrm{HC}} + \sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$};
+	\path [line, line width = 1] (1.2,-8.0) -- (1.9,-8.0);
+	\path [line, line width = 1] (1.2,-5.9) -- (5.7,-5.9);
 	\path [line, line width = 1] (1.2,-2.0) -- (9.5,-2.0);
-	\node [block6a] at (7.5,-10) (Sigma) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}} + \sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$};
+	\node [block6a] at (7.5,-10.7) (Sigma) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}} + \sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$};
 	\path [line, line width = 1] (Born) -- (Sigma);
 	\path [line, line width = 1] (Virt) -- (Sigma);
-	\path [line, line width = 1] (10,-8.45) -- (Sigma);
+	\path [line, line width = 1] (9.6,-9.45) -- (Sigma);
 \end{tikzpicture}
@@
 \end{center}
-\end{figure}\\
+\end{figure}
+This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of $ \sum 2\Re (\mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast})$ numerically by using the package \texttt{LoopTools}.
+Finally the phase space integration and the integration over $x_1$ and $x_2$ is performed by the integration routine ``Cuhre'' which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}.
+The parton density functions are included using \texttt{LHAPDF6}\cite{Buckley:2014ana}\\
+The computation of the real corrections have been done by Wojciech Kotlarski, another member of the group.
+To extract the singularities from the real corrections, the ``two cut phase space slicing method'' outlined in section \ref{sec:RealGluonRad}, has been used.
+For the soft and hard collinear limit, the absolute squared matrix element has been calculated with \texttt{FormCalc} and analytically integrated over the gluons four-momentum in $D$ dimensions in \texttt{Mathematica}.
+This has been exported to the \texttt{C++} code to perform the rest of the integration numerically with the \texttt{CUBA} library.
+The matrix element in the hard non-collinear regime has been imported from \texttt{MadGraph5}\cite{Alwall:2014hca}and the whole integration has been performed numerically by the \texttt{CUBA} library.\\
 It has been checked that for multiple different and quite distinct choices of the parameters $m_{\tilde{q}}$ and $m_{\tilde{g}}$, the double as well as the single poles of the virtual and real correction cancel up to machine precision.
@@
 there are poles of the form $\frac{1}{\epsilon}$ and $\frac{1}{\epsilon^2}$.
-But these pole cancel completely.
+But these pole cancel exactly.
 On the other hand there are also prefactors from the phase space integral and the loop integral, with can be expanded in a power series in $\epsilon$.
@@
 \end{align}
-Here, the coefficients $A$, $B$ and $C$ are in general distinct in the virtual and real part, but $D$ and $E$ are the same as the poles of both contributions cancel exactly.\\
-Now some of the prefactors, namely $P_1$ and $P_2$, are the same in both contributions.
-Just keeping them like in eq.
-\eqref{eq:prefactoredecomp} would slow the computation of the real part down by a factor 5 because this part of the calculation is done analytically.
-Therefore a speed-up has been achieved by discarding the common prefactors at the cost of loosing track about the origin of the next-to-leading order correction.\\
-A common prefactor comes from the two-body phase space integral in eq. \eqref{eq:diffsigma}
+Here, the coefficients $A$, $B$ and $C$ are in general distinct in the virtual and real part, but $D$ and $E$ are the same as the poles of both contributions cancel.\\
+Some of the prefactors, namely $P_1$ and $P_2$, are the same in both contributions.
+Keeping them in eq.
+\eqref{eq:prefactoredecomp} would slow the computation of the real part down by about a factor of five because this part of the calculation is done analytically.
+Therefore a speed-up can been achieved by discarding the common prefactors at the cost of loosing track about the origin of the next-to-leading order correction.\\
+One common prefactor comes from the two-body phase space integral in eq. \eqref{eq:diffsigma}
 \begin{align}
@@
 \eqref{eq:LoopPrefactor} are the prefactors discarded in the computation.
-Instead the prefactor ???
-has been included in the virtual correction.
+Instead the prefactor $\left( 1 + \frac{\pi^2}{6}\epsilon^2 \right)$ has been included in the virtual correction.
 
@@
 A common way to describe next-to-leading order corrections is stating the $K$-factor, which is defined to be the ratio of the complete next-to-leading order cross section $\sigma^{\mathrm{NLO}}$, see eq.
-\eqref{eq:BVR} and the leading order cross section $\sigma^{\mathrm{LO}}$:
+\eqref{eq:BVR} and the leading order cross section $\sigma^{\mathrm{LO}}$, obtained using leading order parton desity functions and $\alpha_s$:
 \begin{align}
@@
 The process in question is described by $X \to Y$.
-Figure \ref{fig:1LXsection_fixed_m} shows the $K$-factor for the production of up-squarks in the MRSSM for varying masses of both the squark ($m_{\tilde{g}} = \unit[2000]{GeV}$) and the gluino $m_{\tilde{q}} = \unit[1000]{GeV}$.
+Figure \ref{fig:1LXsection_fixed_m} shows the $K$-factor for the production of up-squarks in the MRSSM for varying masses of both, the squark ($m_{\tilde{g}} = \unit[2000]{GeV}$) and the gluino $m_{\tilde{q}} = \unit[1000]{GeV}$.
 The mass of the pseudoscalar has been fixed to $m_{\sigma} = \unit[5000]{GeV}$ in both plots.
@@
 Note that the sum of virtual and real corrections gets negative for very light squarks.
-But this region of parameter space is already excluded phenomenologically.
+But this region of parameter space is already excluded experimentally.
 \begin{figure}[!htpb]
@@
 \end{figure}
-Calculate uncertainties for multiple points(pdf, scale, integration)
+Note further that within the real corrections, only gluon radiation is included.
+This is because quark radiation, as described in section \ref{sec:RealQuarkRad}, involves the treatment of on-shell singularities which have unfortunately not been dealt with, due to a limited time budget.
+However, \cite{Gavin:2013kga} suggests that quark radiation gives only a sub percent effect to the next-to-leading order cross section of squark production.
+Of course, this argument applies to the MSSM but as the only difference to the MRSSM comes from diagrams involving gluinos and sgluons it provides also a strong argument for the suppression of quark radiation in squark production in the MRSSM.
+In fact, sgluons do not appear at all in diagrams contributing to real corrections.
+Furthermore, the change from Majorana to Dirac gluinos can never imply an amplification of processes involving gluinos.
+The reason for this is, that if a gluino undergoes, due to its mass, a chirality flip, the right handed part of  it, namely the octino, does not couple to quarks and squarks.\\
+As the calculation of $\sigma^{\mathrm{NLO}}$ has, due to CPU-time, been performed with one percent accuracy, the effect of quark radiation is possibly not visible within the given results.
+Table ???
+shows the $\sigma^{\mathrm{LO}}$ and $\sigma^{\mathrm{NLO}}$ as they have been calculated by \texttt{C++} program.
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{c|c?c|c|c}
+$m_{\tilde{q}}$ in GeV & $m_{\tilde{q}}$ in GeV & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$\\
+\hlinewd{2pt}
+$500$ & $500$ & bla & bla & bla\\
+$500$ & $1000$ & bla & bla & bla\\
+$1000$ & $1000$ & bla & bla & bla\\
+$1000$ & $2000$ & bla & bla & bla\\
+$1500$ & $3000$ & bla & bla & bla
+\end{tabular}
+\caption{•}\label{tab:Modelfille}
+\end{center}
+\end{table}
+Calculate uncertainties for multiple/one points()(pdf,) scale\\
+For three different choices of $m_{\tilde{q}}$ and $m_{\tilde{g}}$, Philip Dießner checked the results by doing the calculation using \texttt{GoSam}\cite{Cullen:2014yla, Cullen:2011ac}.
 
 \subsubsection{$K$-factors for Squark Production in the MSSM}
+To compare the results of $K$-factors in the MRSSM to those in the MSSM, the cross sections in question have been calculated using the program \texttt{MadGraph5\_aMC@NLO}\cite{Alwall:2014hca} with the same parton density functions as before, i.e.
+\texttt{MMHT2014}\cite{Harland-Lang:2014zoa}.
+When generating the code for the pertaining processes, e.g.
+two protons to $\tilde{u}_L + \tilde{u}_R$, with
+\begin{lstlisting}[style=Mybash]
+generate p p > ul ur [QCD] $$go
+\end{lstlisting}
+the $s$-channel gluinos were omitted as \texttt{MadGraph5} does not deal with divergences coming from the gluino in the on-shell limit.
+But as already discussed, these contributions are only of sub percent order.
+In fact, comparing the results from \texttt{MadGraph5} with the program \texttt{Prospino2} shows good agreement of the next-to leading order cross sections:
+\begin{align}
+\sigma^{\mathrm{NLO}}_{\mathrm{MSSM,\texttt{MadGraph}}} = \unit[(9.49 \pm 0.03]{fb} \hspace{1cm}  \sigma^{\mathrm{NLO}}_{\mathrm{MSSM,\texttt{Prospino2}}} = \unit[9.48]{fb} + 1\%,
+\end{align}
+where the given uncertainty is the uncertainty of the integration over the phase space and the chosen parameters are: $m_{\tilde{q}} =\unit[1500]{GeV}$, $m_{\tilde{g}} = \unit[1000]{GeV}$, $\mu_F = \mu_R = m_{\tilde{q}}$ and $\sqrt{S} = \unit[13]{TeV}$.
 \begin{figure}[!htpb]
@@
 \includegraphics[scale=.5]{figures/MSSM_uu_susu_Kfactors_msq=1000GeV.png}
-\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).}\label{fig:1LXsection_fixed_m}
+\caption{Dependence of the $K$-factor for the process $pp \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).
+The cross section has been broken down to contributions coming from $pp \to \tilde{u}_L\tilde{u}_R$ and the from $pp \to \tilde{u}_L\tilde{u}_L$ channel.
+The latter equals the contributions coming from $pp \to \tilde{u}_R\tilde{u}_R$.}\label{fig:1LXsection_fixed_m}
 \end{center}
 \end{figure}
-Calculate uncertainties for multiple points(pdf, scale, integration)
-\texttt{MadGraph5\_aMC@NLO}\cite{Alwall:2014hca}
-When generating the code for the process in question, e.g. two protons to $\tilde{u}_L + \tilde{u}_R$, with
-\begin{lstlisting}[style=Mybash]
-generate p p > ul ur [QCD] $$go
-\end{lstlisting}
-the $s$-channel gluinos were omitted as MadGraph does not deal with divergences coming from the gluino in the on-shell limit.
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{c|c?c|c|c?c|c|c}
+\multicolumn{2}{c?}{} & \multicolumn{3}{c?}{$p + p \to \tilde{u}_L + \tilde{u}_R$} & \multicolumn{3}{c}{$p + p \to \tilde{u} + \tilde{u}$}\\
+\hlinewd{2pt}
+$m_{\tilde{q}}$ in GeV & $m_{\tilde{q}}$ in GeV & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$ & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$\\
+\hlinewd{2pt}
+$500$ & $500$ & bla & bla & bla & bla & bla & bla\\
+$500$ & $1000$ & bla & bla & bla & bla & bla & bla\\
+$1000$ & $1000$ & bla & bla & bla & bla & bla & bla\\
+$1000$ & $2000$ & bla & bla & bla & bla & bla & bla\\
+$1500$ & $3000$ & bla & bla & bla & bla & bla & bla
+\end{tabular}
+\caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$ and $pp \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM for a selected set of masses}\label{tab:Modelfille}
+\end{center}
+\end{table}
+Calculate uncertainties for multiple/ points(pdf, scale, integration)
 

### 2016-07-10 Renormalization.tex
text in NLO chapter

@@
 The absolute squared matrix element coming from \texttt{FormCalc} is then given in terms of scalar integrals, like defined in Appendix \ref{sec:Passarino}.
-To get a notion for the \texttt{FormCalc} output, the following line shows the off-shell amplitude of the quark self-energy in terms of loop integrals and \texttt{Dminus4}
+To display how the \texttt{FormCalc} output looks like, the following box shows the off-shell amplitude of the up-quark self-energy in terms of loop integrals and \texttt{Dminus4}.
 \begin{lstlisting}[style=MyMathematicaOutput]
@@
 \end{lstlisting}
+Here, \texttt{k[1]} and \texttt{k[2]} are the momenta of the in- and outgoing quark, \texttt{Col1} and \texttt{Col2} their respective color, \texttt{B0i[bb0,$\hdots$]} denotes the loop integral $B_0(\hdots)$ and \texttt{B0i[bb1,$\hdots$]} the loop integral $B_1(\hdots)$ , \texttt{Pair[k[1], k[1]]} labels the scalar product of the four vector \texttt{k[1]} with itself, \texttt{MassGlu} is the gluino mass, \texttt{MassSu[i]} with \texttt{i}$\in \left\{ 1,4 \right\}$ names the degenerate squark mass, \texttt{Mat[$\hdots$]} marks a function which calculates the helicity and color matrix element, \texttt{|u1>} and \texttt{|u2>} are the spinors of the in- and outgoing quark, \texttt{6} labels the right-handed projector $P_R$ and \texttt{SUNT} with only two indices is a Kronecker delta.\\
 To extract infrared divergences, \texttt{LoopTools}\cite{Hahn:1998} has been used.
@@
 \includegraphics[scale=.5]{figures/MatrixElement.png}
-\caption{\newline
-The figure at the bottom shows the absolute squared matrix element of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM at tree-level with $\alpha_s = $ from the leading order parton density function $\mathtt{MMHT2014}$\cite{Harland-Lang:2014zoa}, and $\alpha_s = $ from the netxt-to-leading order parton density function as well as the contribution from the virtual absolute squared matrix element.}\label{fig:MatrixElement}
+\caption{The figure at the bottom shows the absolute squared matrix element of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM at tree-level with $\alpha_s = $ from the leading order parton density function $\mathtt{MMHT2014}$\cite{Harland-Lang:2014zoa}, and $\alpha_s = $ from the netxt-to-leading order parton density function as well as the contribution from the virtual absolute squared matrix element.}\label{fig:MatrixElement}
 \end{center}

### 2016-07-10 Virt_Real.tex
text in NLO chapter

@@
 
-\subsubsection{Real Quark Radiation}
+\subsubsection{Real Quark Radiation}\ref{sec:RealQuarkRad}
 As already mentioned before, adding up virtual and real gluon emission contributions results in the cancellation of divergences.

### 2016-07-10 NLO.tex
text in NLO chapter

@@
 \hlinewd{2pt}
-$500$ & $500$ & bla & bla & bla\\
-$500$ & $1000$ & bla & bla & bla\\
-$1000$ & $1000$ & bla & bla & bla\\
-$1000$ & $2000$ & bla & bla & bla\\
-$1500$ & $3000$ & bla & bla & bla
+$500$ & $500$ & $966.4$ & $1441$ & $1.49$\\
+$500$ & $1000$ & $303.4$ & $383$ & $1.26$\\
+$1000$ & $1000$ & $42.63$ & $61.8$ & $1.45$\\
+$1000$ & $2000$ & $11.56$ & $14.3$ & $1.24$\\
+$1500$ & $3000$ & $0.9166$ & $1.13$ & $1.23$
 \end{tabular}
@@
 \hlinewd{2pt}
-$500$ & $500$ & bla & bla & bla & bla & bla & bla\\
-$500$ & $1000$ & bla & bla & bla & bla & bla & bla\\
-$1000$ & $1000$ & bla & bla & bla & bla & bla & bla\\
-$1000$ & $2000$ & bla & bla & bla & bla & bla & bla\\
-$1500$ & $3000$ & bla & bla & bla & bla & bla & bla
+$500$ & $500$ & $966.4$ & $1328$ & $1.37$ & $2333$ & $3102$ \ignore{1328+2*887} & $1.33$\\
+$500$ & $1000$ & $303.4$ & $352$ & $1.16$ & $1271$ & $1393$ \ignore{353 + 2*520} & $1.10$\\
+$1000$ & $1000$ & $42.63$ & $58.5$ & $1.37$ & $122.2$ & $161.3$ \ignore{58.5+2*51.4} & $1.32$\\
+$1000$ & $2000$ & $11.56$ & $13.3$ & $1.15$ & $66.36$ & $72.1$ \ignore{13.3+2*29.4} & $1.09$\\
+$1500$ & $3000$ & $0.9166$ & $1.05$ & $1.14$ & $7.045$ & $7.57$\ignore{1.05+2*3.26} & $1.07$
 \end{tabular}

### 2016-07-10 NLO.tex
Summary chapter

@@
 \end{tabular}
-\caption{•}\label{tab:Modelfille}
+\caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$  in the MRSSM for a selected set of masses.
+The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$ and the pseudoscalar mass is fixed to $m_{\mathrm{\sigma}} = \unit[5000]{GeV}$.}\label{tab:Modelfille}
 \end{center}
@@
 \end{lstlisting}
-the $s$-channel gluinos were omitted as \texttt{MadGraph5} does not deal with divergences coming from the gluino in the on-shell limit.
+the $s$-channel gluinos were omitted, with the addendum \texttt{\$\$go} as \texttt{MadGraph5} does not deal with divergences coming from the gluino in the on-shell limit.
 But as already discussed, these contributions are only of sub percent order.
-In fact, comparing the results from \texttt{MadGraph5} with the program \texttt{Prospino2} shows good agreement of the next-to leading order cross sections:
+In fact, comparing the results from \texttt{MadGraph5} with the ones obtain by using the  program \texttt{Prospino2}, which does include these contributions, shows good agreement of the next-to leading order cross sections of $pp \to \tilde{u}_L \tilde{u}_R$:
 \begin{align}
-\sigma^{\mathrm{NLO}}_{\mathrm{MSSM,\texttt{MadGraph}}} = \unit[(9.49 \pm 0.03]{fb} \hspace{1cm}  \sigma^{\mathrm{NLO}}_{\mathrm{MSSM,\texttt{Prospino2}}} = \unit[9.48]{fb} + 1\%,
+\sigma^{\mathrm{NLO}}_{\mathrm{MSSM,\texttt{MadGraph}}} = \unit[(9.49 \pm 0.03)]{fb} \hspace{1cm}  \sigma^{\mathrm{NLO}}_{\mathrm{MSSM,\texttt{Prospino2}}} = \unit[9.48]{fb} + 1\%,
 \end{align}
@@
 \begin{center}
-\includegraphics[scale=.5]{figures/MSSM_uu_susu_Kfactors_msg=2000GeV.png}
-\includegraphics[scale=.5]{figures/MSSM_uu_susu_Kfactors_msq=1000GeV.png}
+\includegraphics[scale=.55]{figures/MSSM_uu_susu_Kfactors_msg=2000GeV.png}
+\includegraphics[scale=.55]{figures/MSSM_uu_susu_Kfactors_msq=1000GeV.png}
 \caption{Dependence of the $K$-factor for the process $pp \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).
-The cross section has been broken down to contributions coming from $pp \to \tilde{u}_L\tilde{u}_R$ and the from $pp \to \tilde{u}_L\tilde{u}_L$ channel.
+The $K$-factors have been broken down to contributions coming from $pp \to \tilde{u}_L\tilde{u}_R$ and from $pp \to \tilde{u}_L\tilde{u}_L$.
 The latter equals the contributions coming from $pp \to \tilde{u}_R\tilde{u}_R$.}\label{fig:1LXsection_fixed_m}
@@
 \end{tabular}
-\caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$ and $pp \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM for a selected set of masses}\label{tab:Modelfille}
+\caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$ and $pp \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM for a selected set of masses.
+The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$.}\label{tab:Modelfille}
 \end{center}
@@
 \end{align}
+\begin{figure}[!htpb]
+\begin{center}
+\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV_msg=2000GeV.png}
+\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$ on the mass of the pseudoscalar sgluon.
+For $m_{\sigma} \approx \unit[10^5]{GeV}$ onwards want find a logarithmic scaling as predicted by \cite{Cheng:1997sq}.}
+\end{center}
+\end{figure}
 This is actually expected as an effective field theory of the MRSSM where the sgluon is integrated out is no longer supersymmetric.
@@
 (4) in \cite{Cheng:1997sq}.
-\begin{figure}[!htpb]
-\begin{center}
-\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV_msg=2000GeV.png}
-\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$ on the mass of the pseudoscalar sgluon.
-For $m_{\sigma} \approx \unit[10^5]{GeV}$ onwards want find a logarithmic scaling as predicted by \cite{Cheng:1997sq}.}
-\end{center}
-\end{figure}

### 2016-07-10 Summary.tex
Summary chapter

\section{Summary}

The Standard Model of particle physics describes the world's fundamental particles and the interactions among. It belongs to the best tested theory within physics but is on the other hand known to be incomplete.\\
Supersymmetry provides an attractive extension of the Standard Model. Within this thesis, a specific supersymmetric extension of the Standard Model - the Minimal $R$-Symmetric Supersymmetric Standard Model (MRSSM) - is studied. This is particularly appealing from the point of view of symmetries because it comprises the maximal possible symmetry group, a reasonable quantum field theory can have. The theorem stating this, is the Haag-Laopuszanski-Sohnius theorem. In contrast to the common notion, supersymmetry alone does not extent the Poincaré symmetry to the largest possible symmetry group. There is a further non-trivial extension by a global continuous symmetry, referred to as $R$-symmetry.\\
This thesis introduces an $R$-symmetric model in its minimal form. $R$-symmetry forbids terms which are allowed in the Minimal Supersymmetric Standard Model (MSSM). This includes the $A$-terms and the $\mu$-term which are responsible for squark mixing and flavor changing processes. But $R$-symmetry also prohibits Majorana mass terms for the gauginos. To be phenomenological viable, the MRSSM needs to accomodate Dirac gauginos. This requires the gauge sector of this model to be a $N=2$ supersymmetric theory which in turn implies further degrees of freedom.\\
Focusing on the strongly coupling sector, there is, apart from the ``usual'' gluino, another fermionic degree of freedom which is referred to the octino. The superpartner of this right handed part of the strongly coupling gaugino is a spin-0 particle: the scalar gluon (sgluon). As a matter of fact, there are two distinct real sgluons with distinct masses.\\ 
Within the framework of this thesis, the production cross section of squarks and gluinos in the MRSSM has been calculated at tree-level. To this end, Feynman rules for the strongly coupling sector of the MRSSM have been derived. The cross sections and intermediate results are given explicitly for each process. In comparison with the corresponding processes in the MSSM, it has been found that gluino production is enhanced by about a factor of two for gluino and antigluino are distinguishable particles, as opposed to in the MSSM. In order to meet the absence of signals alluding to supersymmetry at the LHC, this suggests that gluinos might be heavier than squarks if they should be realized in that way in nature. Focusing on this regime of parameter space, it has been found that the production of squarks and gluinos in the MRSSM is significantly lower, than in the MSSM. The most striking difference has been found in the production channel of squarks. Motivated by this fact, the next-to-leading order cross section for squark production has been calculated.\\
As this had not been done so far, it was not possible to use a tool like \texttt{MadGraph} or \texttt{Prospino} to perform the calculation. Instead, an own program needed to be devised to calculate the next-to-leading order cross section of squark production in the MRSSM in an automated way.\\
To this end a model file, generated by \texttt{Sarah}, which serves only for leading order processes has been adjusted manually to incorporate counter term Feynman rules. At this point, Philip Dießner did a major contribution when the model file was changed. After this, the model file has been provided with appropriate renormalization constants which are explicitly given in the thesis. This includes also a supersymmetry restoring counterterm. By means of this model file, renormalized one-loop corrections to the matrix element of squark production has been calculated in \texttt{Mathematica}, using the packages \texttt{FeynArts} and \texttt{FormCalc}. After this, the virtual contributions, which have been checked for ultraviolet-finiteness have been passed to a \texttt{C++} code and have been evaluated using the \texttt{Looptools} package. Finally, the phase space integration has been performed numerically using the \texttt{CUBA} library for parallelized numerical integration. However, the virtual corrections to the cross section are not infrared finite. To render the next-to-leading order cross section $\sigma^{\mathrm{NLO}}$ finite, real corrections need to be included. This has been done by Wojciech Kotlarski. After including them, $\sigma^{\mathrm{NLO}}$ has been found to contain no further divergences.\\
Equipped with this programm, the $K$-factors for up-squark production have been calculated as a function of the squark mass and a function of the gluino mass. As a result, the comparison of $K$-factors for squark production in the MRSSM and the MSSM showed that the very same are slightly larger in the MRSSM. But since the tree-level cross section of squark production in the MRSSM are, depending on the choice  of squark and gluino mass, about an order of magnitude smaller than in the MSSM, this renders the MRSSM to a perfectly viable extension of the Standard Model.\\
Among other advantages to the MSSM, it explains a suppressed cross section for the production of supersymmetric particles at the LHC.

### 2016-07-10 figures/MatrixEl/MatrixEl.py

@@ -72,13 +72,13 @@ plt.rcParams.update({'font.size': 22})
 plt.xlabel(r"$t$ in $10^6$ GeV$^2$")#, size = 22)
 
 # plot without poles
-#plt.ylabel("(Absolute) Squared Matrix Element")
-#plt.axis([min(t/10**6) - 1.1,max(t/10**6) + 1.1,0,1.4])
-#plt.plot(t/10**6, matrix_LO_Tree, lw=2, ls="-", c='black', label = r"$\frac{1}{4\cdot 9}\sum|\mathcal{M}^{\mathrm{B}}_{\mathrm{MRSSM}}|^2$ mit LO $\alpha_s$")
-#plt.plot(t/10**6, matrix_NLO_Tree, lw=2, ls="--", c='red', label = r"$\frac{1}{4\cdot 9}\sum|\mathcal{M}^{\mathrm{B}}_{\mathrm{MRSSM}}|^2$ mit NLO $\alpha_s$")
-#plt.plot(t/10**6, matrix_NLO_Tree+matrix_NLO_Virt, lw=2, ls="-", c='red', label = r"$\frac{1}{4\cdot 9}\sum|\mathcal{M}^{\mathrm{B}}_{\mathrm{MRSSM}}|^2 + \frac{1}{4\cdot 9}\sum 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right)$ mit NLO $\alpha_s$")
-#first_window.fill_between(t/10**6, matrix_NLO_Tree, matrix_NLO_Tree+matrix_NLO_Virt, 
-#facecolor=[1,90./100,90./100], color =[1,80./100,80./100], linestyle="-", label = r"$\frac{1}{4\cdot 9}\sum 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right)$ mit NLO $\alpha_s$")
+plt.ylabel("(Absolute) Squared Matrix Element")
+plt.axis([min(t/10**6) - 1.1,max(t/10**6) + 1.1,0,1.4])
+plt.plot(t/10**6, matrix_LO_Tree, lw=2, ls="-", c='black', label = r"$\frac{1}{4\cdot 9}\sum|\mathcal{M}^{\mathrm{B}}|^2$ mit LO $\alpha_s$")
[…]

### 2016-07-10 figures/One_Loop/MRSSM_uu_susu_Kfactors_msg=2000GeV.py

@@ -42,7 +42,7 @@ fig = plt.figure(1,figsize=(10, 9))
 
 first_window = plt.subplot(111)
 plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = 22)
-plt.ylabel(r"$K(uu \to \tilde{u}\tilde{u})$ ", size = 22)
+plt.ylabel(r"$K(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = 22)
 plt.xticks(fontsize = 20)
 plt.yticks(fontsize = 20)
 

### 2016-07-10 figures/One_Loop/MRSSM_uu_susu_Kfactors_msq=1000GeV.py

@@ -42,7 +42,7 @@ fig = plt.figure(1,figsize=(10, 9))
 
 first_window = plt.subplot(111)
 plt.xlabel(r"$m_{\tilde{g}}$ in GeV", size = 22)
-plt.ylabel(r"$K(uu \to \tilde{u}\tilde{u})$ ", size = 22)
+plt.ylabel(r"$K(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = 22)
 plt.xticks(fontsize = 20)
 plt.yticks(fontsize = 20)
 

### 2016-07-10 figures/One_Loop/MRSSM_uu_susu_Kfactors_msq=1000GeV_msg=2000GeV.py

@@ -37,7 +37,7 @@ fig = plt.figure(1,figsize=(10, 9))
 
 first_window = plt.subplot(111)
 plt.xlabel(r"$m_{\tilde{\sigma}}$ in GeV", size = 22)
-plt.ylabel(r"$K(uu \to \tilde{u}\tilde{u})$ ", size = 22)
+plt.ylabel(r"$K(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = 22)
 plt.xticks(fontsize = 20)
 plt.yticks(fontsize = 20)
 

### 2016-07-11 Renormalization.tex
some changes

@@
 
-RenConst[dZGlL1] := xZfL1[F[15], 0]
-RenConst[dZGlR1] := xZfR1[F[15], 0]
+RenConst[dZGlL1] := FieldRC[F[15]][[1]]
+RenConst[dZGlR1] := FieldRC[F[15]][[2]]
 RenConst[dZbarGlL1] := dZGlR1
@@
 It therefore suffices to just pick the first element of the list.
-This is achieved with the addendum $\texttt{[[1]]}$.\\
+This is achieved with the addendum \texttt{[[$1$]]}.\\
 The next block of the code provides the renormalization constants of up- and down-type squarks, before the ensuing block deals with the gluino.
-Here, the predefined function \texttt{xZfL1} (\texttt{xZfR1}) is used to extract the field renormalization constant of the left- (right-) handed component of the Dirac-spinor.\\
+Here, it is important to separate the calculation of the field renormalization constant of the left- (right-) handed component of the Dirac-spinor by adding \texttt{[[$1$]]} (\texttt{[[$2$]]}) at the end of \texttt{FieldRC[F[$15$]]} to pick the appropriate element of the list .\\
 Finally the gauge coupling renormalization and the supersymmetry restoring counterterm are implemented, before the gluon field is renormalized.

### 2016-07-11 figures/One_Loop/MSSM/MSSM_uu_susu_Kfactors_msg=2000GeV.py

@@ -59,13 +59,13 @@ K_min = 0
 K_max = 2
 
 fig = plt.figure(1,figsize=(12,8))
-font_size = 15
+font_size = 18
 #fig.suptitle(r'cross-sections for squark production at the LHC at $\sqrt{s}=13$TeV', fontsize=20)
 
 ############# first subplot #####################
 first_window = plt.subplot2grid((2,2), (0,0))
 plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
-plt.ylabel(r"$K(uu \to \tilde{u}_L\tilde{u}_R)$ ", size = font_size)
+plt.ylabel(r"$K(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = font_size)
 plt.xticks(fontsize = font_size)
 plt.yticks(fontsize = font_size)
 
@@ -87,7 +87,7 @@ plt.plot(m_gluino, sigma_NLO_1L_lr/sigma_LO_Tree_lr, lw=2, ls="-", c='blue')#, l
 ############# second subplot #####################
 second_window = plt.subplot2grid((2,2), (0,1))
 plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
-plt.ylabel(r"$K(uu \to \tilde{u}_L\tilde{u}_L)$ ", size = font_size)
+plt.ylabel(r"$K(pp \to \tilde{u}_L\tilde{u}_L)$ ", size = font_size)
 plt.xticks(fontsize = font_size)
 plt.yticks(fontsize = font_size)
 
@@ -110,7 +110,7 @@ plt.plot(m_gluino, sigma_NLO_1L_ll/sigma_LO_Tree_ll, lw=2, ls="-", c='blue')#, l
 ############# third subplot #####################
 third_window = plt.subplot2grid((2,2), (1,0), colspan = 2)
 plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
-plt.ylabel(r"$K(uu \to \tilde{u}\tilde{u})$ ", size = font_size)
+plt.ylabel(r"$K(pp \to \tilde{u}\tilde{u})$ ", size = font_size)
 plt.xticks(fontsize = font_size)
 plt.yticks(fontsize = font_size)
 

### 2016-07-11 figures/One_Loop/MSSM/MSSM_uu_susu_Kfactors_msq=1000GeV.py

@@ -59,13 +59,13 @@ K_min = 0
 K_max = 2
 
 fig = plt.figure(1,figsize=(12,8))
-font_size = 15
+font_size = 18
 #fig.suptitle(r'cross-sections for squark production at the LHC at $\sqrt{s}=13$TeV', fontsize=20)
 
 ############# first subplot #####################
 first_window = plt.subplot2grid((2,2), (0,0))
 plt.xlabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
-plt.ylabel(r"$K(uu \to \tilde{u}_L\tilde{u}_R)$ ", size = font_size)
+plt.ylabel(r"$K(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = font_size)
 plt.xticks(fontsize = font_size)
 plt.yticks(fontsize = font_size)
 
@@ -87,7 +87,7 @@ plt.plot(m_gluino, sigma_NLO_1L_lr/sigma_LO_Tree_lr, lw=2, ls="-", c='blue')#, l
 ############# second subplot #####################
 second_window = plt.subplot2grid((2,2), (0,1))
 plt.xlabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
-plt.ylabel(r"$K(uu \to \tilde{u}_L\tilde{u}_L)$ ", size = font_size)
+plt.ylabel(r"$K(pp \to \tilde{u}_L\tilde{u}_L)$ ", size = font_size)
 plt.xticks(fontsize = font_size)
 plt.yticks(fontsize = font_size)
 
@@ -110,7 +110,7 @@ plt.plot(m_gluino, sigma_NLO_1L_ll/sigma_LO_Tree_ll, lw=2, ls="-", c='blue')#, l
 ############# third subplot #####################
 third_window = plt.subplot2grid((2,2), (1,0), colspan = 2)
 plt.xlabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
-plt.ylabel(r"$K(uu \to \tilde{u}\tilde{u})$ ", size = font_size)
+plt.ylabel(r"$K(pp \to \tilde{u}\tilde{u})$ ", size = font_size)
 plt.xticks(fontsize = font_size)
 plt.yticks(fontsize = font_size)
 

### 2016-07-11 NLO.tex
some changes

@@
 To do so, the next section gives a justification why on-shell renormalization has been chosen in section \ref{sec:renMRSSM}.
-After that, the set up of the calculation of the different contributions to $\sigma^{\mathrm{NLO}}$ is explained.
+After that, the set up of the calculation, which has been performed by a \texttt{C++} program,  of the different contributions to $\sigma^{\mathrm{NLO}}$, is explained.
 This includes a remark on how the calculation was sped up.
@@
 \subsection{The LSZ Theorem}\label{sec:LSZ}
-The LSZ theorem\cite{Lehmann:1954rq}, named after  Harry Lehmann, Kurt Symanzik and Wolfhart Zimmermann, or LSZ reduction formula prescribes how to obtain the S-matrix element, i.e.
+The LSZ theorem\cite{Lehmann:1954rq} or LSZ reduction formula, named after  Harry Lehmann, Kurt Symanzik and Wolfhart Zimmermann, prescribes how to obtain the S-matrix element, i.e.
 a physical observable, from the time ordered correlation function of the respective field operators.
@@
 \begin{align}
-\int \mathrm{d}x\ \mathrm{e}^{ip x} \left\langle \Omega | \mathcal{T} \left[ \phi(x) \phi(0) \right] | \Omega\right\rangle &= \frac{i}{p^2-m_0^2} + \frac{i}{p^2-m_0^2} \left(\frac{i\Sigma(p^2)}{p^2-m_0^2}\right) + \frac{i}{p^2-m_0^2} \left(\frac{\Sigma(p^2)}{p^2-m_0^2}\right)^2 + \hdots\nonumber\\
+\int \mathrm{d}x\ \mathrm{e}^{ip x} \left\langle \Omega | \mathcal{T} \left[ \phi(x) \phi(0) \right] | \Omega\right\rangle &= \frac{i}{p^2-m_0^2} + \frac{i}{p^2-m_0^2} \left(\frac{\Sigma(p^2)}{p^2-m_0^2}\right) + \frac{i}{p^2-m_0^2} \left(\frac{\Sigma(p^2)}{p^2-m_0^2}\right)^2 + \hdots\nonumber\\
 &= \frac{i}{p^2 - m_0^2 - \Sigma(p^2)}.\label{eq:propagator}
@@
 \end{tikzpicture}
-\caption{Diagrammatic figure of a ``full' $(n+m)$-point function. Apart from the ``full'' propagators there is the ``full'' amputated $(n+m)$-point function}
+\caption{Diagrammatic figure of a ``full'' $(n+m)$-point function. Apart from the ``full'' propagators there is the ``full'' amputated $(n+m)$-point function}
 \end{center}
@@
 \end{figure}\\
-Now it becomes visible why the renormalization in the on-shell scheme
+Now it becomes clear, why the renormalization in the on-shell scheme
 \begin{align}
@@
 \end{align}
-introduces no further manipulation when turning from the correlation function to the S-matrix-element because $Z = 1$ in on-shell renormalization.
+introduces no further modification, when turning from the Green function to the S-matrix-element because $Z = 1$ in on-shell renormalization.
 Furthermore the on-shell condition for the mass renormalization
@@
 \subsection{The Squark Production Cross Section at Next-to-Leading Order}
-The squark production cross section at next-to-leading order is composed out of three contributions. These are the Born (tree-level) cross section, the virtual correction and the real correction. 
+The squark production cross section at next-to-leading order is composed out of three contributions. These are the Born (tree-level) cross section, the virtual and the real corrections. 
 \begin{align}
@@
 \end{align}
-All three contributions have to be calculated with next-to-leading order parton density functions and $\alpha_s$. The next section summaries how the calculation has been performed.
+All three contributions have to be calculated with next-to-leading order parton density functions and $\alpha_s$.
+The next section summaries how the calculation has been automated within a \texttt{C++} program.
 
-\subsubsection{The Set Up of the calculation}
+\subsubsection{The Setup of the Calculation}
 The setup of the calculation is summarized in fig.
@@
 Both the virtual and the Born matrix amplitude have been generated with the \texttt{Mathematica} package \texttt{FeynArts}.
-To this end a modelfile, generated by the \texttt{Mathematica} package \texttt{SARAH}, has been adjusted to include counterterm Feynman rules and appropriate renormalization constants.
-This procedure was explained in section \ref{sec:MatrixElRen}.
-The matrix amplitudes have been processed further to $\sum|\mathcal{M}^{\mathrm{B}}|^2$ and $ \sum 2\Re (\mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast})$ by the \texttt{Mathematica} package \texttt{FormCalc} before this output has then been converted to a \texttt{C++} readable code and stored in an output file.
+To this end a modelfile, generated by the \texttt{Mathematica} package \texttt{SARAH}, has been adjusted appropriately as described in section \ref{sec:ModelFileImplementation}.
+The matrix amplitudes have been processed further to $\sum|\mathcal{M}^{\mathrm{B}}|^2$ and $ \sum 2\Re (\mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast})$ by the \texttt{Mathematica} package \texttt{FormCalc} before this output has then been converted to a \texttt{C++} readable code.
 \begin{figure}[H]
@@
 \end{figure}
-This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of $ \sum 2\Re (\mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast})$ numerically by using the package \texttt{LoopTools}.
+This \texttt{C++} output is in turn invoked by the main program which evaluates the scalar integrals of $ \sum 2\Re (\mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast})$ numerically by using the package \texttt{LoopTools}.
 Finally the phase space integration and the integration over $x_1$ and $x_2$ is performed by the integration routine ``Cuhre'' which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}.
-The parton density functions are included using \texttt{LHAPDF6}\cite{Buckley:2014ana}\\
+The parton density functions are included using \texttt{LHAPDF6}\cite{Buckley:2014ana}.\\
 The computation of the real corrections have been done by Wojciech Kotlarski, another member of the group.
 To extract the singularities from the real corrections, the ``two cut phase space slicing method'' outlined in section \ref{sec:RealGluonRad}, has been used.
-For the soft and hard collinear limit, the absolute squared matrix element has been calculated with \texttt{FormCalc} and analytically integrated over the gluons four-momentum in $D$ dimensions in \texttt{Mathematica}.
+For the soft and hard collinear limit, the absolute squared matrix element has been calculated with \texttt{FormCalc} and analytically integrated over the gluon's four-momentum in $D$ dimensions in \texttt{Mathematica}.
 This has been exported to the \texttt{C++} code to perform the rest of the integration numerically with the \texttt{CUBA} library.
-The matrix element in the hard non-collinear regime has been imported from \texttt{MadGraph5}\cite{Alwall:2014hca}and the whole integration has been performed numerically by the \texttt{CUBA} library.\\
+The matrix element in the hard non-collinear regime has been imported from \texttt{MadGraph5}\cite{Alwall:2014hca} and the whole integration has been performed numerically by the \texttt{CUBA} library.\\
+\\
 It has been checked that for multiple different and quite distinct choices of the parameters $m_{\tilde{q}}$ and $m_{\tilde{g}}$, the double as well as the single poles of the virtual and real correction cancel up to machine precision.
-As the poles of the real corrections have been calculated analytically, it is possible to quote them.
-The double pole is actually proportional to the Born cross section:
+Regarding the virtual corrections, this has been done by numerically extracting the $\frac{1}{\epsilon}$ and $\frac{1}{\epsilon^2}$ coefficient of loop integrals (see the discussion in section \ref{sec:SetLambdaExplanation} for more details).\\
+As the poles of the real corrections have been calculated analytically, it is possible to quote them. The double pole is actually proportional to the Born cross section:
 \begin{align}
@@
 This is because quark radiation, as described in section \ref{sec:RealQuarkRad}, involves the treatment of on-shell singularities which have unfortunately not been dealt with, due to a limited time budget.
-However, \cite{Gavin:2013kga} suggests that quark radiation gives only a sub percent effect to the next-to-leading order cross section of squark production.
-Of course, this argument applies to the MSSM but as the only difference to the MRSSM comes from diagrams involving gluinos and sgluons it provides also a strong argument for the suppression of quark radiation in squark production in the MRSSM.
+However, \cite{Gavin:2013kga} suggests that quark radiation gives only a sub percent effect to the next-to-leading order cross section of squark production when $m_{\tilde{g}} < m_{\tilde{q}}$.
+Of course, this argument applies to the MSSM but as the only difference to the MRSSM comes from diagrams involving gluinos and sgluons it provides also a strong argument for the suppression of quark radiation in the MRSSM.
 In fact, sgluons do not appear at all in diagrams contributing to real corrections.
 Furthermore, the change from Majorana to Dirac gluinos can never imply an amplification of processes involving gluinos.
-The reason for this is, that if a gluino undergoes, due to its mass, a chirality flip, the right handed part of  it, namely the octino, does not couple to quarks and squarks.\\
+The reason for this is, that if a gluino undergoes, due to its mass, a chirality flip, the right handed part of it, namely the octino, does not couple to quarks and squarks.
+However, the effect of quark radiation is thought to increase when $m_{\tilde{g}} > m_{\tilde{q}}$.
+This is quantified within the next chapter, when squark production is discussed in the MSSM.
+Nonetheless, quark radiation is by no means to be thought of a dominant contribution to squark production at next-to-leading order.\\
 As the calculation of $\sigma^{\mathrm{NLO}}$ has, due to CPU-time, been performed with one percent accuracy, the effect of quark radiation is possibly not visible within the given results.
-Table ???
-shows the $\sigma^{\mathrm{LO}}$ and $\sigma^{\mathrm{NLO}}$ as they have been calculated by \texttt{C++} program.
+Table \ref{tab:MRSSMKfactors} shows $\sigma^{\mathrm{LO}}$ and $\sigma^{\mathrm{NLO}}$ as they have been calculated by the devised \texttt{C++} program.
 \begin{table}[H]
@@
 \begin{tabular}{c|c?c|c|c}
-$m_{\tilde{q}}$ in GeV & $m_{\tilde{q}}$ in GeV & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$\\
+$m_{\tilde{q}}$ in GeV & $m_{\tilde{g}}$ in GeV & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$\\
 \hlinewd{2pt}
@@
 \caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$  in the MRSSM for a selected set of masses.
-The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$ and the pseudoscalar mass is fixed to $m_{\mathrm{\sigma}} = \unit[5000]{GeV}$.}\label{tab:Modelfille}
+The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$ and the pseudoscalar mass is fixed to $m_{\mathrm{\sigma}} = \unit[5000]{GeV}$.}\label{tab:MRSSMKfactors}
 \end{center}
 \end{table}
-Calculate uncertainties for multiple/one points()(pdf,) scale\\
-For three different choices of $m_{\tilde{q}}$ and $m_{\tilde{g}}$, Philip Dießner checked the results by doing the calculation using \texttt{GoSam}\cite{Cullen:2014yla, Cullen:2011ac}.
+It can be seen that the $K$-factors depend strongly on the ratio $\frac{m_{\tilde{g}}}{m_{\tilde{q}}}$ but not strongly on the masses itself.\\
+For three different choices of $m_{\tilde{q}}$ and $m_{\tilde{g}}$, Philip Dießner checked the results by doing the calculation using \texttt{GoSam}\cite{Cullen:2014yla, Cullen:2011ac} and \texttt{MadGraph}.
 
@@
 the $s$-channel gluinos were omitted, with the addendum \texttt{\$\$go} as \texttt{MadGraph5} does not deal with divergences coming from the gluino in the on-shell limit. 
-But as already discussed, these contributions are only of sub percent order.
-In fact, comparing the results from \texttt{MadGraph5} with the ones obtain by using the  program \texttt{Prospino2}, which does include these contributions, shows good agreement of the next-to leading order cross sections of $pp \to \tilde{u}_L \tilde{u}_R$:
-\begin{align}
-\sigma^{\mathrm{NLO}}_{\mathrm{MSSM,\texttt{MadGraph}}} = \unit[(9.49 \pm 0.03)]{fb} \hspace{1cm}  \sigma^{\mathrm{NLO}}_{\mathrm{MSSM,\texttt{Prospino2}}} = \unit[9.48]{fb} + 1\%,
-\end{align}
-where the given uncertainty is the uncertainty of the integration over the phase space and the chosen parameters are: $m_{\tilde{q}} =\unit[1500]{GeV}$, $m_{\tilde{g}} = \unit[1000]{GeV}$, $\mu_F = \mu_R = m_{\tilde{q}}$ and $\sqrt{S} = \unit[13]{TeV}$.
 \begin{figure}[!htpb]
 \begin{center}
-\includegraphics[scale=.55]{figures/MSSM_uu_susu_Kfactors_msg=2000GeV.png}
-\includegraphics[scale=.55]{figures/MSSM_uu_susu_Kfactors_msq=1000GeV.png}
+\includegraphics[scale=.47]{figures/MSSM_uu_susu_Kfactors_msg=2000GeV.png}
+\includegraphics[scale=.47]{figures/MSSM_uu_susu_Kfactors_msq=1000GeV.png}
 \caption{Dependence of the $K$-factor for the process $pp \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).
@@
 \end{figure}
+As already discussed, these contributions are only of sub percent order when $m_{\tilde{q}} > m_{\tilde{g}}$\cite{Gavin:2013kga} but increase for $m_{\tilde{g}} > m_{\tilde{q}}$ as indicated in table \ref{tab:MSSMMadGraphProspino}, which compares $\sigma^{\mathrm{NLO}}$ obtained using \texttt{MadGraph5} and the program \texttt{Prospino2}\cite{Beenakker:1996ed} for both scenarios.
+\begin{table}
+\begin{center}
+\begin{tabular}{c|c?c?c}
+$m_{\tilde{q}}$ in GeV & $m_{\tilde{g}}$ in GeV & $\sigma^{\mathrm{NLO}}_{\texttt{MadGraph}}$ in fb & $\sigma^{\mathrm{NLO}}_{\texttt{Prospino2}}$ in fb \\
+\hlinewd{2pt}
+$1500$ & $1000$ & $9.49 \pm 0.03$ & $9.48 \pm 1\%$ \\
+$1000$ & $2000$ & $13.32 \pm 0.05$ & $13.9 \pm 0.8\%$ 
+\end{tabular}
+\caption{$\sigma^{\mathrm{NLO}}(pp \to \tilde{u}_L\tilde{u}_R)$ in the MSSM obtained from \texttt{MadGraph5} and \texttt{Prospino2} for a selected set of masses.
+The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$.
+Within the \texttt{MadGraph5} calculation, the $s$-channel gluino diagrams have been discarded.
+This becomes relevant only when $m_{\tilde{g}} > m_{\tilde{q}}$.}\label{tab:MSSMMadGraphProspino}
+\end{center}
+\end{table}
+
+In fact, comparing $\sigma^{\mathrm{NLO}}(pp \to \tilde{u}_L\tilde{u}_R)$ from \texttt{MadGraph5} with the ones obtain by using \texttt{Prospino2}, which does include quark radiation, shows good agreement for the case $m_{\tilde{g}} < m_{\tilde{q}}$ but a small deviation for $m_{\tilde{g}} > m_{\tilde{q}}$.
+The given uncertainties are the uncertainties of the integration over the phase space and the chosen parameters are: $m_{\tilde{q}} =\unit[1500]{GeV}$, $m_{\tilde{g}} = \unit[1000]{GeV}$, $\mu_F = \mu_R = m_{\tilde{q}}$ and $\sqrt{S} = \unit[13]{TeV}$.\\
+Table \ref{tab:KfactorsMSSM} displays the leading order and next-to-leading order cross section of up-squark production in the MSSM.
+The total cross section for the production of all possible channels $\left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$ is broken down to the contribution, coming from the channel $\tilde{u}_L\tilde{u}_R$ whose tree-level cross section is the same as in the MRSSM.
+
 \begin{table}[H]
@@
 \begin{tabular}{c|c?c|c|c?c|c|c}
-\multicolumn{2}{c?}{} & \multicolumn{3}{c?}{$p + p \to \tilde{u}_L + \tilde{u}_R$} & \multicolumn{3}{c}{$p + p \to \tilde{u} + \tilde{u}$}\\
+\multicolumn{2}{c?}{} & \multicolumn{3}{c?}{$p + p \to \tilde{u}_L + \tilde{u}_R$} & \multicolumn{3}{c}{$p + p \to \tilde{u} + \tilde{u}$} \\
 \hlinewd{2pt}
-$m_{\tilde{q}}$ in GeV & $m_{\tilde{q}}$ in GeV & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$ & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$\\
+$m_{\tilde{q}}$ in GeV & $m_{\tilde{g}}$ in GeV & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$ & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$\\
 \hlinewd{2pt}
@@
 \caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$ and $pp \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM for a selected set of masses.
-The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$.}\label{tab:Modelfille}
+The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$.}\label{tab:KfactorsMSSM}
 \end{center}
 \end{table}
-Calculate uncertainties for multiple/ points(pdf, scale, integration)
+
+Again, it is clearly visible that the $K$-factors depend rather strongly on the ratio $\frac{m_{\mathrm{g}}}{m_{\mathrm{q}}}$ but not so much on the masses itself.
+Comparing with the results from the MRSSM \ref{tab:MRSSMKfactors}, one can state that the $K$-factors of the MRSSM are slightly larger.
+This might be the case, as there are additional degrees of freedom in the $R$-symmetric model, namely the octino which enters the gluino self-energy contributions (see second diagram from the right in \ref{fig:GluinoSE}) and the sgluons which enters there and in box diagrams (see lower right diagram in \ref{fig:1loopdiagrams}).
+The dependence on the sgluon mass is discussed within the next chapter
+%Calculate uncertainties for multiple/ points(pdf, scale, integration)
 
@@
 \end{align}
-\begin{figure}[!htpb]
+
+\begin{figure}[H]
 \begin{center}

### 2016-07-11 Renormalization.tex
some changes

--- 2016-07-09 Renormalization.tex
@@
 After that, the renormalization constant of the strong gauge coupling $g_s$ is computed in a mixture of $\overline{\mathrm{MS}}$- and zero-momentum subtraction scheme.
-This was done because the gauge coupling of the parton density functions is given in the $\overline{\mathrm{MS}}$-scheme but does not include heavy particles, such as the top-quark or supersymmetric particles in its $\beta$-function.
+This is done because the gauge coupling of the parton density functions \texttt{MMHT2014} is given in the $\overline{\mathrm{MS}}$-scheme but does not include heavy particles, such as the top-quark or supersymmetric particles in its $\beta$-function.
 However renormalizing these heavy particles in the zero-momentum subtraction, implies that the $\beta$-function of $g_s$ is exactly the one from QCD.
 This is shown in section \ref{sec:beta_function}.
-After that, a fact already discussed in section \ref{sec:RegSchemeDep} is revisited: dimensinal regularization breaks supersymmetry.
+Afterwards, the fact that dimensinal regularization breaks supersymmetry, which is already discussed in section \ref{sec:RegSchemeDep}, is revisited.
 Section \ref{sec:SUSYrestore} describes the calculation of an additional counterterm which restores supersymmetry within the renomalization.
 Finally, the UV-divergent parts of all renormalization constants in the RSQCD are given.
-These might prove useful, when someone is to check for UV-finiteness of a Green-function or a physical observable.
+These might prove useful in checks for UV-finiteness of a Green-function or a physical observable.
 The chapter closes with a discussion of the renormalized matrix amplitude.
@@
 Dimensional reduction (DRED) was introduced to rectify the imperfections of DREG, i.e.
-it preserves supersymmetry.\footnote{It is not clear whether DRED preserves supersymmetry at all orders in perturbation theory\cite{Jack:1997sr} but it does preserve supersymmetry at 1-loop level\cite{Hollik:2001cz}.} DRED promotes only loop momenta to $D$ dimensions.
+it introduces no mismatch of degrees of freedom.\footnote{It is not clear whether DRED preserves supersymmetry at all orders in perturbation theory\cite{Jack:1997sr} but it does preserve supersymmetry at 1-loop level\cite{Hollik:2001cz}.} DRED promotes only momenta to $D$ dimensions.
 All other quantities which are $D$ dimensional in DREG stay in four dimensions.
@@
 \subsection{Regularization Scheme Dependences}\label{sec:RegSchemeDep}
-To discuss the subject of this and ensuing subsections, it is useful to introduce the effective action $\Gamma$.
+To discuss the subject of this section, it is useful to introduce the effective action $\Gamma$.
 A formal introduction of $\Gamma$ can be found in~\cite{Peskin}.
@@
 \begin{align}
-\Gamma^{(\leq 1)} \to \Gamma^{(\leq 1)} + \Gamma^{(1),\mathrm{ct}}
+\Gamma^{(\leq 1)} \to \Gamma^{(\leq 1)} + \Gamma^{(1),\mathrm{ct}}.
 \end{align} 
@@
 \end{align}
-This is due to different loop diagrams, i.e. 
-\begin{align}
-\Gamma^{(1),\mathrm{ct,trans}}_{\mathrm{DREG},q_i \overline{q}_j G^a_\mu} \hspace{1cm} \mathrm{and} \hspace{1cm} \Gamma^{(1),\mathrm{ct,trans}}_{\mathrm{DREG},\tilde{q}_{Li} \overline{q}_j \tilde{g}^a}
-\end{align}
-are proportional to a different combination of $C(A)$ and $C(F)$. Furthermore there are different fields on the vertex, which also come with different supersymmetry restoring counterterms.\\
-Therefore one has to make a difference between these couplings at 1-loop level.
-In order to match $g_s$ to the experimentally measured coupling, it is renormalized in the  $\overline{\mathrm{MS}}$-scheme (with an additional manipulation for heavy particles, which will be explained in section \ref{sec:RenGaugeCoupling}).
-The Yukawa coupling $\hat{g}_s$ needs therefore to be added with the difference of the supersymmetry restoring counterterms from the $\tilde{q}_L\overline{q}\tilde{g}$ vertex and the $q\overline{q}G$ vertex at 1-loop in order to be renormalized in the same way.
+This is due to different loop diagrams, i.e.\footnote{The fields as subscript on the effective action denote the derivative with respect to them.
+The quantity $i\Gamma_{\phi_1 \hdots \phi_N}^{(n)}$ labels the one-particle irreducible Green function of the $\phi_1 \hdots \phi_N$ vertex at $n$-loop-level.}
+\begin{align}
+i\Gamma^{(1),\mathrm{ct,trans}}_{\mathrm{DREG},q_i \overline{q}_j G^a_\mu} \hspace{1cm} \mathrm{and} \hspace{1cm} i\Gamma^{(1),\mathrm{ct,trans}}_{\mathrm{DREG},\tilde{q}_{Li} \overline{q}_j \tilde{g}^a}
+\end{align}
+are proportional to a different combination of $C(A)$ and $C(F)$. Furthermore there are different fields on the vertices, which also come with different supersymmetry restoring counterterms.\\
+Therefore one has to distinguish between these couplings at 1-loop level.
+In order to match $g_s$ to the experimentally measured coupling from the parton density functions, it is renormalized in the  $\overline{\mathrm{MS}}$-scheme (with an additional manipulation for heavy particles, which will be explained in section \ref{sec:RenGaugeCoupling}).
+One therefore needs to add the difference of $\delta \hat{g}_s^{\mathrm{trans}}$ and $\delta g_s^{\mathrm{trans}}$ to the renormalization constant of the Yukawa coupling $\hat{g}_s$ in order to renormalized $g_s$ and $\hat{g}_s$ in the same way.
 
 \subsection{On-Shell Renormalization}\label{sec:QuarkSE}
-A part of the computation of the cross section at next-to-leading order is the calculation of renormalization constants. 
+One part of the computation of the cross section at next-to-leading order is the calculation of renormalization constants. 
 Field renormalization constants $\delta Z$ and parameter renormalization constants $\delta o$ with $o \in \left\{ g, m \right\}$ are defined by
@@
 The field and mass renormalization constants have been calculated in DREG in the on-shell scheme.
-This has the advantage that when turning to the cross section no manipulation of the Green function to the S-matrix element has to be done, see section \ref{sec:LSZ}.\\
+This has the advantage that when turning to the cross section no modification of the Green function to the S-matrix element has to be done.
+This is discussed in more detail in section \ref{sec:LSZ}.\\
 The calculation has partially been performed by hand but was always checked with the mathematica output generated by the packages  \texttt{FeynArts} \cite{Hahn:2000} and \texttt{FormCalc} \cite{ChokoufeNejad:2013qja, Hahn:1998yk} which used a model file generated by \texttt{SARAH}\cite{Staub:2013tta, Staub:2012pb, Staub:2010jh, Staub:2009bi}.\\
-The renormalization constants are given in terms of Passarino-Veltman integrals whose definition may be found in Appendix \ref{sec:Passarino}.
+The renormalization constants are given in terms of Passarino-Veltman integrals whose definition can be found in Appendix \ref{sec:Passarino}.
 
 \subsubsection*{The Quark Self-Energy}
-The quark self-energy splits into contribution from the Standard Model as well as a supersymmetric analogue which is already present in the MSSM.
+The quark self-energy (depicted in fig. \ref{fig:QuarkSelfEnergy}) splits into contribution from the Standard Model as well as a supersymmetric analogue which is already present in the MSSM.
 \begin{figure}[!htbp]
@@
 \begin{align}
-\frac{\partial}{\partial \slashed{p}} \left[ \Re (\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j}) + \Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}  \right]_{p^2 = 0} = 0
-\end{align}
-where $\Re (\hdots)$ denotes the real part of $\hdots$ one finds
+\frac{\partial}{\partial \slashed{p}} \left[ \Re (\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j}) + \Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}  \right]_{p^2 = 0} = 0,
+\end{align}
+where $\Re (\hdots)$ denotes the real part of $\hdots$, one finds
 \begin{align}
@@
 Note that the Standard Model contribution to the quark renormalization constant equals zero as it is propotional to $B_0(0,0,0)$ and $B_1(0,0,0)$.
-These integrals have no mass scale and are due to their definition of their scaling in $D$ dimensions\cite{Collins:105730} defined to be zero.
+These integrals have no mass scale and are due to their definition of their scaling in $D$ dimensions\cite{Collins:105730} equal to be zero.
 Pictorially this may be understood as a cancellation of a positive UV-divergent part and a negative IR-divergent part.
@@
 \subsubsection*{The Squark Self-Energy}
-The contributions to the self-energy of the left- and right-handed squark are the same for electroweak effects are neglected.
+The contributions to the self-energy, shown in fig.
+\ref{fig:SquarkSE}, of the left- and right-handed squark are the same because electroweak effects are neglected.
 Therefore to avoid unnecessary labeling $\Gamma_{\tilde{q}\tilde{q}^\dagger}$ stands in the following for $\Gamma_{\tilde{q}_L\tilde{q}_L^\dagger} = \Gamma_{\tilde{q}_R\tilde{q}_R^\dagger}$.
+The one-particle irreducible Green function of the squark is given by
 \begin{figure}[!htbp]
@@
 \end{tikzpicture}
-\caption{Diagrammatic contributions to the self-energy of the squark at 1-loop level.}
+\caption{Diagrammatic contributions to the self-energy of the squark at 1-loop level.}\label{fig:SquarkSE}
 \end{center}
@@
 \begin{align}
-\delta Z_{\tilde{q}} &= \frac{g_s^2}{16\pi^2}C(F) \Re \left[ 4B_1(p^2,0,m_{\tilde{g}}^2) + 2B_1(B_1(p^2,0,m_{\tilde{q}}^2)) + 3B_0(p^2,0,m_{\tilde{q}}^2) \right.\nonumber\\
+\delta Z_{\tilde{q}} &= \frac{g_s^2}{16\pi^2}C(F) \Re \left[ 4B_1(p^2,0,m_{\tilde{g}}^2) + 2B_1(p^2,0,m_{\tilde{q}}^2) + 3B_0(p^2,0,m_{\tilde{q}}^2) \right.\nonumber\\
 & + 4m_{\tilde{q}}^2 \frac{\partial}{\partial p^2}B_1(p^2,0,m_{\tilde{g}}^2) - 4m_{\tilde{g}}^2\frac{\partial}{\partial p^2}B_0(p^2,m_{\phi^0}^2,m_{\tilde{q}}^2) + 2m_{\tilde{q}}^2 \frac{\partial}{\partial p^2}B_1(p^2,0,m_{\tilde{q}}^2)\nonumber\\
@@
 From the Lagrangian \eqref{eq:L_RSQCD} one can see that the couplings of the two particles are quite distinct.
-This is reflected by different field renormalization constants of the left- and right-handed part of the gluino.
+This is reflected by different field renormalization constants of the left- and right-handed part of the gluino (see eq.
+\eqref{eq:fieldtrafo}).
 \begin{figure}[!htbp]
@@
 \end{tikzpicture}
-\caption{diagrammatic contributions to the self-energy of the squark at 1-loop level}
+\caption{diagrammatic contributions to the self-energy of the squark at 1-loop level}\label{fig:GluinoSE}
 \end{center}
 \end{figure}
-As for the quarks the fermion (and momentum) flow is from the right to the left.
+As for the quarks, the fermion (and momentum) flow in a diagram is from the right to the left. The one-particle irreducible Green function is given by
 \begin{align}
@@
 & + C(A)\left( (B_0(p^2,m_{\tilde{g}}^2,m_{\phi^0}^2) - B_0(p^2,m_{\tilde{g}}^2,m_{\sigma^0}^2))m_{\tilde{g}} - (B_1(p^2,m_{\tilde{g}}^2,m_{\phi^0}^2) + B_1(p^2,m_{\tilde{g}}^2,m_{\sigma^0}^2))\slashed{p} \right) \nonumber\\
-&\left.+ C(A)\left( (2 - 4 B_0(p^2,0,m_{\tilde{g}}^2)) m_{\tilde{g}} - (1-2(B_0(p^2,0,m_{\tilde{g}}^2) + B_1(p^2,0,m_{\tilde{g}}^2)))\slashed{p} \right)\right]
-\end{align}
-Where $n_f = 6$ is the number of quark flavors.\\
+&\left.+ C(A)\left( (2 - 4 B_0(p^2,0,m_{\tilde{g}}^2)) m_{\tilde{g}} - (1-2(B_0(p^2,0,m_{\tilde{g}}^2) + B_1(p^2,0,m_{\tilde{g}}^2)))\slashed{p} \right)\right],
+\end{align}
+where $n_f = 6$ is the number of quark flavors.\\
 The counterterm Feynman rule derived from multiplicative renormalization reads\\
@@
 & \frac{\partial}{\partial (P_L\slashed{p})} \left[ \Re (\Gamma^{\mathrm{1L}}_{\tilde{g}^a \overline{\tilde{g}}^b}) + \Gamma^{\mathrm{1L,ct}}_{\tilde{g}^a \overline{\tilde{g}}^b}  \right]_{\slashed{p} = m_{\tilde{g}}} = 0,
-&& \frac{\partial}{\partial (P_R\slashed{p})} \left[ \Re (\Gamma^{\mathrm{1L}}_{\tilde{g}^a \overline{\tilde{g}}^b}) + \Gamma^{\mathrm{1L,ct}}_{\tilde{g}^a \overline{\tilde{g}}^b}  \right]_{\slashed{p} = m_{\tilde{g}}} = 0
+&& \frac{\partial}{\partial (P_R\slashed{p})} \left[ \Re (\Gamma^{\mathrm{1L}}_{\tilde{g}^a \overline{\tilde{g}}^b}) + \Gamma^{\mathrm{1L,ct}}_{\tilde{g}^a \overline{\tilde{g}}^b}  \right]_{\slashed{p} = m_{\tilde{g}}} = 0,
 \end{align}
@@
 \end{align}
-As for the quark there are constant terms amid the Passarino-Veltman integrals. These arise only in DREG but and not in DRED. The transition counterterms are
+As for the quark there are constant terms amid the Passarino-Veltman integrals. These arise only in DREG but not in DRED. The transition counterterms are
 \begin{align}
@@
 This may be understood in the path integral approach of quantum field theory\cite{Peskin}: When considering a certain process, the Green function corresponding to this process, can be expressed as a path integral over fields within the theory.
-The field of virtual particles does not occur next to the path integral measure, in contrast to the fields of external particles.
+The field of virtual particles occurs, in contrast to the fields of external particles, only in the exponential.
 This means, that rescaling a field of an inner particle has no influence on the Green function.
@@
 Extracting $\delta g_s$ from the quark-quark-gluon vertex requires not only the computation of $i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_jG^\mu_a}$ but also the (re)evaluation of auxiliary field renormalization constants $\delta Z_q^{\mathrm{aux}}$ and $\delta Z_G^{\mathrm{aux}}$ in the above mentioned scheme.
-These will not be the same as the on-shell scheme.
+These will not be the same as in the on-shell scheme.
 
 \subsubsection*{The Quark Self-Energy Revisited}
-The quark self-energy has two contribution which are shown in figure \ref{fig:QuarkSelfEnergy}.
+The quark self-energy has two contributions which are shown in figure \ref{fig:QuarkSelfEnergy}.
 The first one corresponds to light particles the second one to heavy particles: $i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j} = i\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j} + i\Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}$.
@@
 It is therefore common to define $\Delta_\epsilon = \frac{1}{\epsilon} -\gamma_{\mathrm{E}} + \ln 4\pi$.} part is kept.
-The self energy corresponding to the heavy particles is taken at zero momentum $p^2=0$.
-\begin{align}
-\left.i\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j}\right|_{\mathrm{UV-div}} &= i C(F) \frac{g_s^2}{16\pi^2} \Delta_\epsilon \slashed{p} \delta_{ij}\\
-i\Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}(p^2=0) &= -i C(F) \frac{g_s^2}{16\pi^2} 2B_1(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\slashed{p}\delta_{ij}
+The self energy corresponding to the heavy particles is evaluated at zero momentum $p^2=0$
+\begin{align}
+\left.i\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j}\right|_{\mathrm{UV-div}} &= i C(F) \frac{g_s^2}{16\pi^2} \Delta_\epsilon \slashed{p} \delta_{ij},\\
+i\Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}(p^2=0) &= -i C(F) \frac{g_s^2}{16\pi^2} 2B_1(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\slashed{p}\delta_{ij}.
 \end{align}
@@
 \subsubsection*{The Gluon Self-Energy}
-As for the quark self-energy there are again contributions to the self-energy originating from light and heavy particles. Again these are differently dealt with.
+As for the quark self-energy there are again contributions to the self-energy originating from light and heavy particles.
+Again these are differently dealt with.
+The ultraviolet divergent one-particle irreducible Green function is given by
 \begin{align}
@@
 &+\left. \frac{C(A)}{12}(19 p^2g^{\mu\nu} - 22 p^\mu p^\nu) \right]\delta_{ab}\nonumber\\
-&=i\frac{g_s^2}{16\pi^2} \Delta_\epsilon \left[ - \frac{4 (n_{f}-1)}{3} T(F) + \frac{5}{3} C(A) \right](p^2g^{\mu\nu}-p^\mu p^\nu)\delta_{ab}
+&=i\frac{g_s^2}{16\pi^2} \Delta_\epsilon \left[ - \frac{4 (n_{f}-1)}{3} T(F) + \frac{5}{3} C(A) \right](p^2g^{\mu\nu}-p^\mu p^\nu)\delta_{ab}.
 \end{align}
 Both the contribution from the gluon loop and the one from the ghost loop are not proportional to $(p^2g^{\mu\nu}-p^\mu p^\nu)$ but their sum is.
+This transversal form is an implication of gauge invariance\cite{dissertori2003quantum}.
 \begin{figure}[!htbp]
@@
 \end{figure}
-The heavy particle contributions are calculated in the zero-momentum subtraction
+The heavy particle contributions are calculated in the zero-momentum subtraction:
 \begin{align}
@@
 &-\frac{1}{6} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\phi^0}^2}{\mu^2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu)  \nonumber\\
-&\left.-\frac{1}{6} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\phi^0}^2}{\mu^2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) \right]
+&\left.-\frac{1}{6} C(A) \left( \Delta_\epsilon - \ln \frac{m_{\phi^0}^2}{\mu^2} \right)(p^2g^{\mu\nu}-p^\mu p^\nu) \right].
 \end{align}
@@
 \end{align}
-where the first squared brackets come from light and the second one from heavy particles running in the loop.
+where the first squared bracket comes from light and the second one from heavy particles running in the loop.
 
 \subsubsection*{The $q\overline{q}G$ Vertex Correction}
-As for the self energies the vertex correction is composed of loops from light particles from the Standard Model and additional heavy particle loops.
+Like the self-energies, the vertex corrections are composed of loops from light particles from the Standard Model and additional heavy particle loops.
 \begin{figure}[!htbp]
@@
 \end{tikzpicture}
-\caption{Contribution from light (Standard Model) particles to the $q\overline{q}G$ vertex correction}\label{fig:GaugeCouplingCorrection}
+\caption{Contribution from light (Standard Model) particles to the $q\overline{q}G$ vertex correction}\label{fig:GaugeCouplingCorrectionL}
 \end{center}
 \end{figure}
-The contributions from Standard Model particles to the $q\overline{q}G$ yield
+The contributions from Standard Model particles (shown in fig. \ref{fig:GaugeCouplingCorrectionL}) to the $q\overline{q}G$ yield
 \begin{align}
@@
 \eqref{eq:qqGlight} corresponds to the first diagram in fig.
-\ref{fig:GaugeCouplingCorrection} whereas the term with the prefactor $C(A)$ corresponds to the second diagram.
+\ref{fig:GaugeCouplingCorrectionL} whereas the term with the prefactor $C(A)$ corresponds to the second diagram.
 \begin{figure}[!htbp]
@@
 \end{tikzpicture}
-\caption{Contribution from heavy particles to the $q\overline{q}G$ vertex correction.}
+\caption{Contribution from heavy particles to the $q\overline{q}G$ vertex correction.}\label{fig:GaugeCouplingCorrectionH}
 \end{center}
 \end{figure}
-The 3-point-function with only heavy particles running in the loop evaluates to
+The three-point-function with only heavy particles running in the loop (displayed in fig. \ref{fig:GaugeCouplingCorrectionH}) evaluates to
 \begin{align}
@@
 &\hspace{3.3cm} + \left. C(A)\left( B_0(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2) -2C_{00}(0, 0, 0, m_{\tilde{g}}^2, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\right) \right]\nonumber\\
-&= ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} 2C(F)B_1(0,m_{\tilde{g}}^2,m_{\tilde{q}}^2)
+&= ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} 2C(F)B_1(0,m_{\tilde{g}}^2,m_{\tilde{q}}^2).
 \end{align}
@@
 But $\mu$ is no physical parameter but can be absorped into the fields and parameters.
-To this end one defines
-\begin{align}
-g_{sB}(g_s, \mu) = \mu^\epsilon g_s \left( 1 + \frac{\delta g_s}{g_s} \right)
+To this end one defines the bare coupling
+\begin{align}
+g_{sB}(g_s, \mu) = \mu^\epsilon g_s \left( 1 + \frac{\delta g_s}{g_s} \right),
 \end{align}
@@
 \end{align*}
-so that 
+for contributions from light and heavy particles, so that 
 \begin{align}
@@
 \end{align}
-This is the beta function of QCD first found by Politzer \cite{Politzer:1973fx}, Gross and Wilczek \cite{Gross:1973ju}.
+This is the $\beta$ function of QCD first found by Politzer \cite{Politzer:1973fx}, Gross and Wilczek \cite{Gross:1973ju}.
 This means that renormalizing $g_s$ in the way it is, decouples heavy particles from the $\beta$ function and allows to adopt $\alpha_s = \frac{g_s^2}{4\pi}$ from the parton density functions.
@@
 \subsubsection*{The $q\overline{q}G$ Vertex Correction Revisited}
-The diagrams from which the supersymmetry restoring contributions to the $q\overline{q}G$ vertex come from, are shown in figure \ref{fig:GaugeCouplingCorrection} and evaluate to
+The diagrams from which the supersymmetry restoring contributions to the $q\overline{q}G$ vertex come, are shown in figure \ref{fig:GaugeCouplingCorrection} and evaluate to
 \begin{align}
@@
 \subsection{$\overline{\mathrm{MS}}$ - Renormalization}\label{sec:MSRen}
-To quickly check for UV-finiteness of a Greenfunction or a physical observable it is useful to have the extracted UV-divergences of the renormalization constants at hand.
-How these are obtained is described in \ref{sec:Passarino}.
-\begin{align}
-& \delta Z_{\tilde{g}}^L = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} 2\left[ T(F) n_f + C(A) \right] &&  \delta Z_{\tilde{g}}^R = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} 2 C(A)\nonumber\\
-& \delta m_{\tilde{g}} = \frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} \left[ T(F) n_f - 2C(A) \right] m_{\tilde{g}}\nonumber\\
-& \delta Z_{\tilde{q}} = 0 && \delta m_{\tilde{q}}^2 = 0\nonumber\\
-&\frac{\delta g_s}{g_s} = \frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}}\left[ T(F) n_f - C(A) \right] = 0\nonumber\\
-& \delta Z_{\phi^0} = 0 && \delta m_{\phi^0}^2 = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}}\left[ 8T(F)n_f - 16C(A) \right]m_{\tilde{g}}^2\nonumber\\
-& \delta Z_{\sigma^0} = 0 && \delta m_{\sigma^0}^2 = 0\nonumber\\
-& \delta Z_{G} = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} 2T(F) n_f
+To check quickly for UV-finiteness of a Greenfunction or a physical observable it is useful to have the extracted UV-divergences of the renormalization constants at hand.
+How these are obtained is described in \ref{sec:Passarino} and evaluate to
+\begin{align}
+& \delta Z_{\tilde{g}}^L = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} 2\left[ T(F) n_f + C(A) \right], &&  \delta Z_{\tilde{g}}^R = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} 2 C(A),\nonumber\\
+& \delta m_{\tilde{g}} = \frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} \left[ T(F) n_f - 2C(A) \right] m_{\tilde{g}},\nonumber\\
+& \delta Z_{\tilde{q}} = 0, && \delta m_{\tilde{q}}^2 = 0,\nonumber\\
+&\frac{\delta g_s}{g_s} = \frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}}\left[ T(F) n_f - C(A) \right] = 0,\nonumber\\
+& \delta Z_{\phi^0} = 0, && \delta m_{\phi^0}^2 = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}}\left[ 8T(F)n_f - 16C(A) \right]m_{\tilde{g}}^2,\nonumber\\
+& \delta Z_{\sigma^0} = 0, && \delta m_{\sigma^0}^2 = 0,\nonumber\\
+& \delta Z_{G} = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} 2T(F) n_f.
 \end{align}
@@
 Note that the renormalization constants $\delta m_{\tilde{g}}$, $\delta m^2_{\phi^0}$ and $\delta m^2_{\sigma^0}$ are not independent from each other as the masses of the gluino and the two sgluons arise  from only two parameters, i.e.
-$m_{\tilde{g}}$ and $m_{\sigma}^2$ from the softly breaking part of the Lagrangian, eq.
+$m_{\tilde{g}}$ and $m_{\sigma}^2$ from the soft breaking part of the Lagrangian, eq.
 \eqref{eq:L_RSQCD}.
-In additions it happens that the particle content of RSQCD is such that $\frac{\delta g_s}{g_s} = 0$.
-This means that the $\beta$ function of $g_s$ equals zero at 1-loop-level if one does not choose to decouple heavy particles from the running as has been done in this thesis.
+In addition, it happens that the particle content of RSQCD is such that $\frac{\delta g_s}{g_s} = 0$.
+This means that the $\beta$ function of $g_s$ equals zero at 1-loop-level if one does not choose to decouple heavy particles from the running as it is done in this thesis.
 However at 2-loop-level there is a non-zero $\beta$ function of $g_s$, which has been calculated by \texttt{SARAH}.
@@
 \subsection{The Renormalization of the Matrix Element}\label{sec:MatrixElRen}
-This section explains how the renormalization of the RSQCD is implemented in the framework of the automated calculation and gives intermediate results in the form of the renormalized matrix element.
-
-\subsubsection{Implementation into the Model File}
-Within the automated calculation, the renormlization of the matrix element for squark production has been achieved by extending the model file, generated by \texttt{SARAH} with counterterm Feynman rules and renormalization constants.\\
-The derivation of the counterterm Feynman rules has been performed by the author whereas the implementation into the modelfile was mainly done by Philip Dießner, another member of the group.
-To explain the implementation, the quark-squark-gluino vertex is considered, as an example.
+This section explains how the renormalization of the matrix element of squark production is implemented in the framework of the automated calculation and gives intermediate results in the form of the renormalized matrix element.
+
+\subsubsection{Implementation into the Model File}\label{sec:ModelFileImplementation}
+Within the automated calculation, the renormalization of the matrix element of squark production has been achieved by extending the model file, generated by \texttt{SARAH} with counterterm Feynman rules and renormalization constants.\\
+The derivation of the counterterm Feynman rules has been performed by the author whereas the implementation into the model file was mainly done by Philip Dießner, another member of the group.
+To explain the implementation, the code extract describing the quark-squark-gluino vertex is considered, as an example.
 \begin{lstlisting}[style=MyMathematica]
@@
 \end{lstlisting}
+The syntax of the vertex, also described in \cite{FeynArtsManual}, is like $\left\{\left\{\mathrm{L},\mathrm{L}^{ct}\right\},\left\{\mathrm{R},\mathrm{R}^{ct}\right\}\right\}$, where the shortcuts are explained in table \ref{tab:Modelfille}.
 The names of the particles within the model are given in the \texttt{FeynArts} manual\cite{FeynArtsManual} when  \texttt{MSSMQCD.mod}, the QCD extention of the MSSM model file is explained:\\ 
-\mbox{\texttt{F[3,$\left\{ \right.$gt1, ct1$\left.\right\}$]}} is an up-type quark of the \texttt{gt1}'th generation with color \texttt{ct1} and \texttt{F[15,$\left\{ \right.$ct2$\left.\right\}$]} is a gluino with color \texttt{ct2}.
-However, in comparison to \cite{FeynArtsManual}, there is a slight difference in the definition of squarks.
-Whereas the MSSM modelfile \texttt{MSSMQCD.mod} has three indices to label squarks, the model file generated by \texttt{SARAH} uses only two: \texttt{-S[13,$\left\{ \right.$ gt3, ct3$\left.\right\}$]} labels an anti up-type squark of mass eigenstate \texttt{gt3} and color \texttt{ct3}.
-This means more specifically that \texttt{gt3}$\in \left\{ 1,2,3 \right\}$ labels the ``left-handed" squarks with increasing mass and \texttt{gt3}$\in \left\{ 4,5,6 \right\}$ the ``right-handed`'' squarks with increasing mass.\\
-The syntax of the model file, also described in \cite{FeynArtsManual}, is like $\left\{\left\{\mathrm{L},\mathrm{L}^{ct}\right\},\left\{\mathrm{R},\mathrm{R}^{ct}\right\}\right\}$, where the shortcuts are explained in table \ref{tab:Modelfille}.
+However, \mbox{\texttt{F[3,$\left\{ \right.$gt1, ct1$\left.\right\}$]}} is an up-type quark of the \texttt{gt1}'th generation with color \texttt{ct1} and \texttt{F[15,$\left\{ \right.$ct2$\left.\right\}$]} is a gluino with color \texttt{ct2}.
+In comparison to \cite{FeynArtsManual}, there is a slight difference in the definition of squarks.
+Whereas the MSSM model file, \texttt{MSSMQCD.mod}, has three indices to label squarks, the model file generated by \texttt{SARAH} uses only two: \texttt{-S[13,$\left\{ \right.$ gt3, ct3$\left.\right\}$]} denotes an anti up-type squark of mass eigenstate \texttt{gt3} and color \texttt{ct3}.
+This means more specifically that \texttt{gt3}$\in \left\{ 1,2,3 \right\}$ labels the ``left-handed" squarks with increasing mass and \texttt{gt3}$\in \left\{ 4,5,6 \right\}$ the ``right-handed`'' squarks with increasing mass.
 \begin{table}[H]
@@
 \end{tabular}
-\caption{Explanation of the vertex structure in the above given mode extract.}\label{tab:Modelfille}
+\caption{Explanation of the shortcuts describing the vertex structure in the above given mode extract.}\label{tab:Modelfille}
 \end{center}
 \end{table}
+
 Within the above given extract of the model file, \texttt{Lam} are the Gell-Mann matrices and \texttt{ZU} and \texttt{ZUL} are mixing matrices which are equated to the unit matrix, as there is no squark mixing in the MRSSM and the CKM-matrix is also approximated with the unit matrix.\\
@@
 \\
-The renormalization constants for masses and fields are calculated by \texttt{FormCalc} functions like \texttt{MassRC} and \texttt{FieldRC}\cite{FormCalcManual}. 
+The renormalization constants for masses and fields are calculated by the \texttt{FormCalc} functions \texttt{MassRC} and \texttt{FieldRC}\cite{FormCalcManual}. 
 \begin{lstlisting}[style=MyMathematica]
@@
 The function \texttt{FieldRC} actually calculates two renormalization constants when the argument is a fermion field: the left- and right-handed part.
-But these terms are identical since electroweak interactions are not considered within the modelfile.
-It therefore suffices to just pick the first element of the list.
-This is achieved with the addendum $\texttt{[[1]]}$.\\
-The next block of the code provides the renormalization constants of up- and down-type squarks, before the ensuing block deals with the gluino.
-Here, the predefined function \texttt{xZfL1} (\texttt{xZfR1}) is used to extract the field renormalization constant of the left- (right-) handed component of the Dirac-spinor.\\
-Finally the gauge coupling renormalization and the supersymmetry restoring counterterm are implemented, before the gluon field is renormalized.
-The necessity of the parameter \texttt{FiniteGs} will be explained shortly.\\
-The result of these renormalization constants has been checked with the above calculated renormalization constants.
-
-\subsubsection{The Renormalized Matrix Element}
+But these terms are identical since electroweak interactions are not considered within the model file.
+It therefore suffices to just pick the first element of the list by adding \texttt{[[$1$]]} to the two-component list.\\
+The next block of the code provides the renormalization constants of up- and down-type squarks and the ensuing block deals with the gluino.
+Here, it is important to separate the calculation of the field renormalization constant of the left- and right-handed component of the Dirac-spinor by adding \texttt{[[$1$]]} or \texttt{[[$2$]]} at the end of \texttt{FieldRC[F[$15$]]} to pick the appropriate element of the list.\\
+Finally, the gauge coupling renormalization and the supersymmetry restoring counterterm are implemented, before the gluon field is renormalized.
+The necessity of the parameter \texttt{FiniteGs} will be explained in the next section.\\
+These renormalization constants have been checked with the above calculated renormalization constants.
+
+\subsubsection{The Renormalized Matrix Element}\label{sec:SetLambdaExplanation}
 After providing the model file with renormalization constants and counterterm Feynman rules, the matrix element for squark production can be renormalized.
@@
 the result contains a quantity \texttt{Dminus4} which equals $-2\epsilon$ in DREG.
-The absolute squared matrix element coming from \texttt{FormCalc} is then given in terms of scalar integrals, like defined in Appendix \ref{sec:Passarino}.
-To get a notion for the \texttt{FormCalc} output, the following line shows the off-shell amplitude of the quark self-energy in terms of loop integrals and \texttt{Dminus4}
+The expression $\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$ coming from \texttt{FormCalc} is then given in terms of scalar integrals, like defined in Appendix \ref{sec:Passarino}.
+To display how the \texttt{FormCalc} output looks like, the following box shows the off-shell amplitude of the up-quark self-energy in terms of loop integrals and \texttt{Dminus4}.
 \begin{lstlisting}[style=MyMathematicaOutput]
@@
 \end{lstlisting}
-To extract infrared divergences, \texttt{LoopTools}\cite{Hahn:1998} has been used.
-This package provides the function \texttt{SetLambda} which can be set to 0, $-1$ or $-2$ to extract the finite part, $\frac{1}{\epsilon}$ pole or $\frac{1}{\epsilon^2}$ pole of scalar integrals in dimensioanl regularisation.
-\texttt{SetLambda} includes both, UV and IR poles.
+Here, \texttt{k[1]} and \texttt{k[2]} are the momenta of the in- and outgoing quark, \texttt{Col1} and \texttt{Col2} their respective color, \texttt{B0i[bb0,$\hdots$]} denotes the loop integral $B_0(\hdots)$ and \texttt{B0i[bb1,$\hdots$]} the loop integral $B_1(\hdots)$ , \texttt{Pair[k[1], k[1]]} labels the scalar product of the four vector \texttt{k[1]} with itself, \texttt{MassGlu} is the gluino mass, \texttt{MassSu[i]} with \texttt{i}$\in \left\{ 1,4 \right\}$ names the degenerate squark mass, \texttt{Mat[$\hdots$]} marks a container which stores the helicity and color matrix element, \texttt{|u1>} and \texttt{|u2>} are the spinors of the in- and outgoing quark, \texttt{6} labels the right-handed projector $P_R$ and \texttt{SUNT} with only two indices is a Kronecker delta in color space.\\
+To extract infrared divergences, \texttt{LoopTools}\cite{Hahn:1998} is used.
+This package provides the function \texttt{SetLambda} which can be set to 0, $-1$ or $-2$ to extract the finite part, $\frac{1}{\epsilon}$ pole or $\frac{1}{\epsilon^2}$ pole of scalar integrals in dimensional regularisation.
+This means, when all arguments of a scalar integral are provided numerically, the integral is replaced with the coefficient of $\epsilon^i$, where $i \in \left\{ 0,-1,-2 \right\}$ is set by \texttt{SetLambda}.
+The so extracted divergences include both, UV and IR poles.
 In fact, the function \texttt{SetUVDiv} controls whether UV divergences are kept (\texttt{SetUVDiv}$\to 1$) or discarded (\texttt{SetUVDiv}$\to 0$), which presents another check of UV-finiteness which has been performed.\\
-However, using \texttt{SetLambda} allows for numerically extracting the coefficients of $\epsilon^i$ with $i \in \left\{ 0,-1,-2 \right\}$ of the absolute squared matrix amplitude.
-The respective poles of $|\mathcal{M}^{\mathrm{V}}_{\mathrm{MRSSM}}(uu \to \tilde{u}_L\tilde{u}_R)|^2$ are shown in figure \ref{fig:MatrixElementPoles}.
+The respective poles of $\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})(uu \to \tilde{u}_L\tilde{u}_R)$ are shown in figure \ref{fig:MatrixElementPoles}.
+Observe, that the single pole is positive for all values of the Mandelstam variable $t$.
+This is because infrared integrals are rendered finite when $\epsilon<0$ \ignore{($D$ > 4)}.
+This means that the single pole is actually negative and can cancel with the single pole from the real corrections which is forced to be positive as it origins from an absolute square.
+\begin{figure}[!htbp]
+\begin{center}
+\includegraphics[scale=.5]{figures/MatrixElement_Poles.png}
+\caption{Coefficients of $\mathcal{O}(\epsilon^0)$, $\mathcal{O}(\epsilon^{-1})$ and $\mathcal{O}(\epsilon^{-2})$ terms of $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$ of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM as a function of the Mandelstam variable $t$.
+Final state helicities and colors are averaged.
+The parameters are fixed to $m_{\tilde{q}} = \mu = \unit[1000]{GeV}$, $m_{\tilde{g}} = \unit[2000]{GeV}$, $m_{\sigma} = \unit[5000]{GeV}$ and $\sqrt{s} = \unit[6000]{GeV}$ which is the partonic center-of-mass energy.}\label{fig:MatrixElementPoles}
+\end{center}
+\end{figure}\\
 Note, that the extraction of the single pole does not only involve setting the option \texttt{SetLamda} $\to-1$ and \texttt{Dminus4}$\to 0$, but also setting \texttt{SetLamda}$\to -2$ and \texttt{Dminus4} $\to -2$ and subtracting the term obtained by \texttt{SetLamda}$\to-2$ and \texttt{Dminus4} $\to 0$.
 In doing so, one accounts for the contraction of double poles with terms of $\mathcal{\epsilon}$.
-The same logic implies to the extraction of finite terms.\\
+The same applies to the extraction of finite terms.
+This is summarized schematically in table \ref{tab:poles}.
+
+\begin{table}[!htpb]
+\begin{center}
+\begin{tabular}{c?c?c}
+$\epsilon^i$ & Contribution & Settings in \texttt{FormCalc}\\
+\hlinewd{2pt}
+$\epsilon^{-2}$ & $\epsilon^{-2}$ & (\texttt{SetLambda} $\to -2$, \texttt{Dminus4} $\to 0$) \\
+\hline
+$\epsilon^{-1}$ & $\epsilon^{-1}$ & (\texttt{SetLambda} $\to -1$, \texttt{Dminus4} $\to 0$) \\
+  & $+\mathcal{O}(\epsilon)\cdot\epsilon^{-1}$ & $+$(\texttt{SetLambda} $\to -2$, \texttt{Dminus4} $\to -2$) \\
+  & & $-$(\texttt{SetLambda} $\to -2$, \texttt{Dminus4} $\to 0$)\\
+\hline
+$\epsilon^{0}$ & $\epsilon^{0}$ & (\texttt{SetLambda} $\to 0$, \texttt{Dminus4} $\to 0$) \\
+  & $+\mathcal{O}(\epsilon)\cdot\epsilon^{-1}$ & $+$(\texttt{SetLambda} $\to -1$, \texttt{Dminus4} $\to -2$) \\
+  & & $-$(\texttt{SetLambda} $\to -1$, \texttt{Dminus4} $\to 0$)
+\end{tabular}
+\caption{The table shows what settings need to be adjusted in \texttt{FormCalc} to extract double and single poles as well as finite terms of an expression in \texttt{Mathematica} which contains loop-integrals.}\label{tab:poles}
+\end{center}
+\end{table}
+
 Now it becomes clear, why the parameter \texttt{FiniteGs} has been introduced.
-As \texttt{SetLambda} only replaces the loop integrals but not every other term in an expression with the corresponding prefactor of $\epsilon^i$, \texttt{FiniteGs} needs to be set to zero when \texttt{SetLambda} is set to $-1$ or $-2$ and \texttt{FiniteGs}$\to 1$ when \texttt{SetLambda}$\to 0$.
-\begin{figure}[H]
-\begin{center}
-\includegraphics[scale=.5]{figures/MatrixElement_Poles.png}
-\caption{Coefficients of $\mathcal{O}(\epsilon^0)$, $\mathcal{O}(\epsilon^{-1})$ and $\mathcal{O}(\epsilon^{-2})$ terms of $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$ of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM as a function of the Mandelstam variable $t$.
-External helicities and colors are averaged.
-The parameters are fixed to $m_{\tilde{q}} = \mu = \unit[1000]{GeV}$, $m_{\tilde{g}} = \unit[2000]{GeV}$, $m_{\sigma} = \unit[5000]{GeV}$ and $\sqrt{s} = \unit[6000]{GeV}$ which is the partonic center of mass energy.}\label{fig:MatrixElementPoles}
-\end{center}
-\end{figure}
+As \texttt{SetLambda} only replaces the loop integrals but not every other term in an expression with the corresponding prefactor of $\epsilon^i$, \texttt{FiniteGs} needs to be set to zero when \texttt{SetLambda} is set to $-1$ or $-2$ and \texttt{FiniteGs}$\to 1$ when \texttt{SetLambda}$\to 0$.\\
 The upper plot in figure \ref{fig:MatrixElement} shows the finite contributions from loop diagrams with different topology to $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$ as well as their sum as a function of the Mandelstam variable $t$ where $\frac{1}{4\cdot 9}$ is the averaging over final state spins and colors.
-The lower plot displays the tree-level absolute squared matrix amplitude with leading order $\alpha_s$ which is compared to its analogue with next-to-leading order $\alpha_s$ and virtual correction $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$.
+The lower plot displays the tree-level absolute squared matrix amplitude with leading order $\alpha_s$ which is compared to its analogue with next-to-leading order $\alpha_s$ and the virtual correction $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$.
 The latter is not given analytically.
-All terms are color and spin averaged in the final state and summed over in the initial state.
+It can be seen that the virtual corrections are relatively constant.
+Referring to eq.
+\eqref{eq:t}, this suggests that in this case, virtual corrections do enhance the differential cross section in all directions of the beam axis relatively uniformly.
 \begin{figure}[!htpb]
@@
 \includegraphics[scale=.5]{figures/MatrixElement.png}
-\caption{\newline
-The figure at the bottom shows the absolute squared matrix element of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM at tree-level with $\alpha_s = $ from the leading order parton density function $\mathtt{MMHT2014}$\cite{Harland-Lang:2014zoa}, and $\alpha_s = $ from the netxt-to-leading order parton density function as well as the contribution from the virtual absolute squared matrix element.}\label{fig:MatrixElement}
+\caption{The figure at the bottom shows the absolute squared matrix element of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM at tree-level with $\alpha_s = 0.135$ from the leading order parton density function $\mathtt{MMHT2014}$\cite{Harland-Lang:2014zoa}, and $\alpha_s = 0.12$ from the next-to-leading order parton density function as well as the contribution from the virtual absolute squared matrix element.\newline
+The figure at the top shows the different contributions and their sum to the virtual corrections. The used parameters are given under fig. \ref{fig:MatrixElementPoles}.}\label{fig:MatrixElement}
 \end{center}

### 2016-07-11 Summary.tex
some changes

@@
 This has been done by Wojciech Kotlarski.
-After including them, $\sigma^{\mathrm{NLO}}$ has been found to contain no further divergences.\\
-Equipped with this programm, the $K$-factors for up-squark production have been calculated as a function of the squark mass and a function of the gluino mass.
+After including them, $\sigma^{\mathrm{NLO}}$ has been found to contain no further divergences.
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{c|c?c|c|c?c|c|c}
+\multicolumn{2}{c?}{} & \multicolumn{3}{c?}{MRSSM: $p + p \to \tilde{u}_L + \tilde{u}_R$} & \multicolumn{3}{c}{MSSM: $p + p \to \tilde{u} + \tilde{u}$}\\
+\hlinewd{2pt}
+$m_{\tilde{q}}$ in GeV & $m_{\tilde{g}}$ in GeV & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$ & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$\\
+\hlinewd{2pt}
+$500$ & $500$ & $966.4$ & $1441$ & $1.49$ & $2333$ & $3102$ & $1.33$\\
+$500$ & $1000$ & $303.4$ & $383$ & $1.26$ & $1271$ & $1393$ & $1.10$\\
+$1000$ & $1000$ & $42.63$ & $61.8$ & $1.45$ & $122.2$ & $161.3$ & $1.32$\\
+$1000$ & $2000$ & $11.56$ & $14.3$ & $1.24$ & $6.36$ & $72.1$ & $1.09$\\
+$1500$ & $3000$ & $0.9166$ & $1.13$ & $1.23$ & $7.045$ & $7.57$ & $1.07$
+\end{tabular}
+\caption{Total hadronic cross section for the production of up-squarks in the MRSSM and the MSSM at leading order and next-to-leading order.
+Also given are the $K$-factors.
+As a consequence of $R$-charge conservation, the only allowed channel in the MRSSM is $\tilde{u}_L + \tilde{u}_R$ production, whereas in the MSSM also $\tilde{u}_L + \tilde{u}_L$ and $\tilde{u}_R + \tilde{u}_R$ production is allowed.\newline
+The results are shown for a selected set of masses.
+The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$ and within the MRSSM the pseudoscalar mass is fixed to $m_{\mathrm{\sigma}} = \unit[5000]{GeV}$.}\label{tab:MRSSMKfactors}
+\end{center}
+\end{table}
+Equipped with this program, the $K$-factors for up-squark production have been calculated as a function of the squark mass and a function of the gluino mass.
 As a result, the comparison of $K$-factors for squark production in the MRSSM and the MSSM showed that the very same are slightly larger in the MRSSM.

### 2016-07-11 Virt_Real.tex
some changes

--- 2016-07-09 Virt_Real.tex
@@
 \section{Virtual and Real Corrections}\label{sec:VirtRealCorr}
-The results calculated in the previous chapter are not the full theoretical predictions for the cross sections of the different processes but only the first term in a perturbation series of $\alpha_s$.\\
+The results calculated in the previous chapter are not the full theoretical predictions for the cross sections of the various processes but only the first term in a perturbation series of $\alpha_s$.\\
+To provide accurate predictions, it is necessary that correction to the leading order are small.
+This implies that $\alpha_s$, which depends strongly on the energy scale, needs to fulfill $\alpha_s < 1$.
+It is known that $\alpha_s$ becomes of $\mathcal{O}(1)$ and larger when the energy scale is of $\mathcal{O}(\unit[200]{MeV})$ and smaller.\cite{dissertori2003quantum} Fortunately squark production is a process which involves large enough energy to maintain the validity of perturbation theory as the typical energy scale involved, is the mass of squarks which certainly fulfills $m_{\tilde{q}} > \unit[500]{GeV}$.\\
 This section describes the necessary steps in the calculation of the squark production cross section at next-to-leading order, i.e. its $\mathcal{O}(\alpha_s)$-correction.\\
@@
 \begin{align}
-& \phi^0 / \sigma^0 \to \sqrt{Z_{\phi^0 / \sigma^0}}\phi^0 / \sigma^0 && \tilde{q}_{L/R} \to \sqrt{Z_{\tilde{q}_{L/R}}}\tilde{q}_{L/R}\nonumber\\
-& P_L \tilde{g} \to \sqrt{Z_{\tilde{g}}^L} P_L \tilde{g} && P_R \tilde{g} \to \sqrt{Z_{\tilde{g}}^R} P_R \tilde{g}\nonumber\\
-& q \to \sqrt{Z_q}q && G_\mu \to \sqrt{Z_G} G_\mu && \label{eq:fieldtrafo}\\
-& g_s \to g_{s\ \mathrm{bare}} && m_{\tilde{q}}^2 \to m_{\tilde{q}\ \mathrm{bare}}^2\nonumber\\
-&  m_{\sigma}^2 \to m_{\sigma\ \mathrm{bare}}^2 && m_{\tilde{g}} \to m_{\tilde{g}\ \mathrm{bare}}\label{eq:parametertrafo}
+& \phi^0 / \sigma^0 \to \sqrt{Z_{\phi^0 / \sigma^0}}\phi^0 / \sigma^0, && \tilde{q}_{L/R} \to \sqrt{Z_{\tilde{q}_{L/R}}}\tilde{q}_{L/R}, \nonumber\\
+& P_L \tilde{g} \to \sqrt{Z_{\tilde{g}}^L} P_L \tilde{g}, && P_R \tilde{g} \to \sqrt{Z_{\tilde{g}}^R} P_R \tilde{g},\nonumber\\
+& q \to \sqrt{Z_q}q && G_\mu \to \sqrt{Z_G} G_\mu, && \label{eq:fieldtrafo}\\
+& g_s \to g_{s\ \mathrm{bare}}, && m_{\tilde{q}}^2 \to m_{\tilde{q}\ \mathrm{bare}}^2, \nonumber\\
+&  m_{\sigma}^2 \to m_{\sigma\ \mathrm{bare}}^2, && m_{\tilde{g}} \to m_{\tilde{g}\ \mathrm{bare}}.\label{eq:parametertrafo}
 \end{align}
@@
 \end{align}
-where $\sigma^{\mathrm{R}}$ donates the cross section arising from real corrections.
+where $\sigma^{\mathrm{R}}$ denotes the cross section arising from real corrections.
 However, real corrections also contain divergences.
@@
 
-\subsubsection{Real Quark Radiation}
+\subsubsection{Real Quark Radiation}\label{sec:RealQuarkRad}
 As already mentioned before, adding up virtual and real gluon emission contributions results in the cancellation of divergences.
@@
 \end{figure}
-These contributions do not comprise soft divergences.
+These contributions do not comprise soft divergences, as they are associated with a different initial state and the factorization theorem guarantees the absences of soft divergences in each initial state separately.
+In other words, real correction, coming from an initial state with quark and gluon, cannot contribute to the cancellation of soft divergences with virtual correction which are associated with two quarks in the initial state.\\
 A split-up of space space in a soft and a hard part is therefore not needed.

### 2016-07-12 NLO.tex
K factor MSSM contour plot

@@
 \end{align}
-for the full propagators one notices the same singularity as in eq. \eqref{eq:LSZ}. If one now compares the coefficients of these poles in eq. \eqref{eq:LSZ} one finds
+for the full propagators one notices the same singularity as in eq. \eqref{eq:LSZ}. Comparing the coefficients of these poles in eq. \eqref{eq:LSZ} one obtains
 \begin{figure}[!htbp]
@@
 On the other hand there are also prefactors from the phase space integral and the loop integral, with can be expanded in a power series in $\epsilon$.
-In short, the virtual and real correction to the cross section can be expressed with some coefficients $A - E$, which are functions of the parameters $m_{\tilde{g}}$ and $m_{\tilde{q}}$, in the following way
+In short, the virtual and real correction to the cross section can be expressed with some coefficients $A$ - $E$, which are functions of the parameters $m_{\tilde{g}}$, $m_{\tilde{q}}$ and $m_{\sigma}$, in the following way:
 \begin{align}
@@
 \end{align}
-In addition the prefactor of a loop integral defined in \texttt{LoopTools} differs from the one usually, and therefore also here, used.
+In addition the prefactor of a loop integral defined in \texttt{LoopTools} differs from the one usually (and therefore also here) used.
 The \texttt{LoopTools} definition\cite{LoopToolsManual} of a loop integral is
@@
 \eqref{eq:LoopInt}.
-The right hand side of eq.
+Without going into detail why these factors are chosen, the right hand side of eq.
 \eqref{eq:PhasePrefactor} and eq.
@@
 Instead the prefactor $\left( 1 + \frac{\pi^2}{6}\epsilon^2 \right)$ has been included in the virtual correction.
+Therefore $P_1$ and $P_2$ are chosen like
+\begin{align}
+P_1 &=  2\ln 4\pi - 2\gamma_E - \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} \\
+P_2 &=  -\ln 4\pi \cdot\ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} + \frac{1}{2} \ln^2 \frac{tu - m_{\tilde{q}}^4}{\mu^2 s}  + \gamma_E^2 - \frac{\pi^2}{3} + \ln^2 4\pi - 2\gamma_E\ln 4\pi + \gamma_E \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s}  \nonumber
+\end{align}
 
@@
 A common way to describe next-to-leading order corrections is stating the $K$-factor, which is defined to be the ratio of the complete next-to-leading order cross section $\sigma^{\mathrm{NLO}}$, see eq.
-\eqref{eq:BVR} and the leading order cross section $\sigma^{\mathrm{LO}}$, obtained using leading order parton desity functions and $\alpha_s$:
+\eqref{eq:BVR} and the leading order cross section $\sigma^{\mathrm{LO}}$, obtained using leading order parton density functions and $\alpha_s$:
 \begin{align}
@@
 \end{align}
-The process in question is described by $X \to Y$.
-Figure \ref{fig:1LXsection_fixed_m} shows the $K$-factor for the production of up-squarks in the MRSSM for varying masses of both, the squark ($m_{\tilde{g}} = \unit[2000]{GeV}$) and the gluino $m_{\tilde{q}} = \unit[1000]{GeV}$.
+Here, $X$ denotes the initial state and $Y$ the final state.
+Figure \ref{fig:1LXsection_fixed_m} shows the $K$-factors for the production of up-squarks in the MRSSM for varying masses of both, the squark ($m_{\tilde{g}} = \unit[2000]{GeV}$) and the gluino $m_{\tilde{q}} = \unit[1000]{GeV}$.
 The mass of the pseudoscalar has been fixed to $m_{\sigma} = \unit[5000]{GeV}$ in both plots.
+In addition to the $K$-factor, the contributions to it are split into the ones coming from the Born cross section\footnote{The contribution of the Born cross section to the $K$-factor is smaller as one as it has been calculated with next-to-leading order parton density functions.} and real and virtual corrections.\\
 It can be seen that the  $K$-factor increases with increasing squark mass and decreases with increasing gluino mass.
-Note that the sum of virtual and real corrections gets negative for very light squarks.
+Note, that the sum of virtual and real corrections gets negative for very light squarks.
 But this region of parameter space is already excluded experimentally.
-\begin{figure}[!htpb]
+\begin{figure}[H]
 \begin{center}
-\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msg=2000GeV.png}
-\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV.png}
+\includegraphics[scale=.4]{figures/MRSSM_uu_susu_Kfactors_msg=2000GeV.png}
+\includegraphics[scale=.4]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV.png}
 \caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).}\label{fig:1LXsection_fixed_m}
@@
 \end{figure}
-Note further that within the real corrections, only gluon radiation is included.
+Note further, that within the real corrections, only gluon radiation is included.
 This is because quark radiation, as described in section \ref{sec:RealQuarkRad}, involves the treatment of on-shell singularities which have unfortunately not been dealt with, due to a limited time budget.
@@
 Furthermore, the change from Majorana to Dirac gluinos can never imply an amplification of processes involving gluinos.
-The reason for this is, that if a gluino undergoes, due to its mass, a chirality flip, the right handed part of it, namely the octino, does not couple to quarks and squarks.
+The reason for this is, that if a gluino undergoes, due to its mass, a chirality flip, the right handed part of it, namely the octino, does neither couple to quarks nor to squarks.
 However, the effect of quark radiation is thought to increase when $m_{\tilde{g}} > m_{\tilde{q}}$.
-This is quantified within the next chapter, when squark production is discussed in the MSSM.
+This is quantified within the next section, when squark production is discussed in the MSSM.
 Nonetheless, quark radiation is by no means to be thought of a dominant contribution to squark production at next-to-leading order.\\
-As the calculation of $\sigma^{\mathrm{NLO}}$ has, due to CPU-time, been performed with one percent accuracy, the effect of quark radiation is possibly not visible within the given results.
 Table \ref{tab:MRSSMKfactors} shows $\sigma^{\mathrm{LO}}$ and $\sigma^{\mathrm{NLO}}$ as they have been calculated by the devised \texttt{C++} program.
@@
 \caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$  in the MRSSM for a selected set of masses.
-The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$ and the pseudoscalar mass is fixed to $m_{\mathrm{\sigma}} = \unit[5000]{GeV}$.}\label{tab:MRSSMKfactors}
+The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$ and the pseudoscalar mass is fixed to $m_{\mathrm{\sigma}} = \unit[5000]{GeV}$.
+For $\sigma^{\mathrm{LO}}$
+\texttt{MMHT2014}(LHAPDF ID: 25000) parton density functions has been used, whereas $\sigma^{\mathrm{NLO}}$ used
+\texttt{MMHT2014}(LHAPDF ID: 25100)}\label{tab:MRSSMKfactors}
 \end{center}
 \end{table}
-It can be seen that the $K$-factors depend strongly on the ratio $\frac{m_{\tilde{g}}}{m_{\tilde{q}}}$ but not strongly on the masses itself.\\
-For three different choices of $m_{\tilde{q}}$ and $m_{\tilde{g}}$, Philip Dießner checked the results by doing the calculation using \texttt{GoSam}\cite{Cullen:2014yla, Cullen:2011ac} and \texttt{MadGraph}.
+It can be seen that the $K$-factors depend strongly on the ratio $\frac{m_{\tilde{g}}}{m_{\tilde{q}}}$ but not that strongly on the masses itself.\\
+For three different choices of $m_{\tilde{q}}$ and $m_{\tilde{g}}$, Philip Dießner checked the results up to permille accuracy by doing the calculation using \texttt{GoSam}\cite{Cullen:2014yla, Cullen:2011ac} and \texttt{MadGraph5\_aMC@NLO}\cite{Alwall:2014hca} on the basis of the same model file.
 
 \subsubsection{$K$-factors for Squark Production in the MSSM}
-To compare the results of $K$-factors in the MRSSM to those in the MSSM, the cross sections in question have been calculated using the program \texttt{MadGraph5\_aMC@NLO}\cite{Alwall:2014hca} with the same parton density functions as before, i.e.
-\texttt{MMHT2014}\cite{Harland-Lang:2014zoa}.
+To compare the results of $K$-factors in the MRSSM to those in the MSSM, the cross sections in question have been calculated using the program \texttt{MadGraph5\_aMC@NLO} with the same parton density functions as before, i.e.
+\texttt{MMHT2014}.
 When generating the code for the pertaining processes, e.g.
@@
 As already discussed, these contributions are only of sub percent order when $m_{\tilde{q}} > m_{\tilde{g}}$\cite{Gavin:2013kga} but increase for $m_{\tilde{g}} > m_{\tilde{q}}$ as indicated in table \ref{tab:MSSMMadGraphProspino}, which compares $\sigma^{\mathrm{NLO}}$ obtained using \texttt{MadGraph5} and the program \texttt{Prospino2}\cite{Beenakker:1996ed} for both scenarios.
-\begin{table}
+
+\begin{table}[H]
 \begin{center}
@@
 \hlinewd{2pt}
-$1500$ & $1000$ & $9.49 \pm 0.03$ & $9.48 \pm 1\%$ \\
-$1000$ & $2000$ & $13.32 \pm 0.05$ & $13.9 \pm 0.8\%$ 
+$1500$ & $1000$ & $9.49 \pm 0.03$ & $9.48 \pm 0.09$ \\
+$1000$ & $2000$ & $13.32 \pm 0.05$ & $13.89 \pm 0.11\%$ 
 \end{tabular}
@@
 
-In fact, comparing $\sigma^{\mathrm{NLO}}(pp \to \tilde{u}_L\tilde{u}_R)$ from \texttt{MadGraph5} with the ones obtain by using \texttt{Prospino2}, which does include quark radiation, shows good agreement for the case $m_{\tilde{g}} < m_{\tilde{q}}$ but a small deviation for $m_{\tilde{g}} > m_{\tilde{q}}$.
-The given uncertainties are the uncertainties of the integration over the phase space and the chosen parameters are: $m_{\tilde{q}} =\unit[1500]{GeV}$, $m_{\tilde{g}} = \unit[1000]{GeV}$, $\mu_F = \mu_R = m_{\tilde{q}}$ and $\sqrt{S} = \unit[13]{TeV}$.\\
+In fact, comparing $\sigma^{\mathrm{NLO}}(pp \to \tilde{u}_L\tilde{u}_R)$ from \texttt{MadGraph5} with the one obtained by using \texttt{Prospino2}, which does include quark radiation, shows good agreement for the case $m_{\tilde{g}} < m_{\tilde{q}}$ but a small deviation for $m_{\tilde{g}} > m_{\tilde{q}}$.
+The given uncertainties are the uncertainties of the integration over the phase space and the chosen parameters are: $\mu_F = \mu_R = m_{\tilde{q}}$ and $\sqrt{S} = \unit[13]{TeV}$.\\
+Figure \ref{fig:1LXsection_fixed_m} shows the $K$-factors for squark production in the MSSM, broken down to $K$-factors for ``chirality'' like ($\tilde{u}_L \tilde{u}_L$) and unlike squarks $\tilde{u}_L \tilde{u}_R$.
+It can be seen, that the mass dependence of $K(pp \to \tilde{u}_L \tilde{u}_R)$ in the MSSM is quite similar to the one in the MRSSM and that the MSSM $K$-factors are slightly smaller than in the MSSM.
+However, the $K$-factors for ``chirality'' like squarks are distinctly larger.
+The mass dependence of them is quite the same as for the  $pp \to \tilde{u}_L \tilde{u}_R$ channel.
+The only difference is a local maximum of the $K$-factor as a function of the gluino mass at $m_{\tilde{g}} \approx \unit[500]{GeV}$.
+Adding the cross sections for the three possible channels $\tilde{u}_L \tilde{u}_R$, $\tilde{u}_L \tilde{u}_L$ and $\tilde{u}_R \tilde{u}_R$ together one ends up with $K$-factors which have the same mass dependence as in the MRSSM but which can, depending on the chosen parameters, be significantly smaller.\\
 Table \ref{tab:KfactorsMSSM} displays the leading order and next-to-leading order cross section of up-squark production in the MSSM.
@@
 Again, it is clearly visible that the $K$-factors depend rather strongly on the ratio $\frac{m_{\mathrm{g}}}{m_{\mathrm{q}}}$ but not so much on the masses itself.
-Comparing with the results from the MRSSM \ref{tab:MRSSMKfactors}, one can state that the $K$-factors of the MRSSM are slightly larger.
+Comparing with the results from the MRSSM in table \ref{tab:MRSSMKfactors}, one can state that the $K$-factors of the MRSSM are slightly larger.
 This might be the case, as there are additional degrees of freedom in the $R$-symmetric model, namely the octino which enters the gluino self-energy contributions (see second diagram from the right in \ref{fig:GluinoSE}) and the sgluons which enters there and in box diagrams (see lower right diagram in \ref{fig:1loopdiagrams}).
@@
 \subsection{The Cross Section in the Limit of Large Sgluon Masses}
-The cross section for squark production does not exist in the limit of an infinitely large sgluon mass, instead it was found that it diverges logarithmically.\\
+The cross section for squark production does not exist in the limit of an infinitely large sgluon mass, instead it was found that it diverges logarithmically:
 \begin{align}
-\lim_{m_{\sigma}\to\infty} \sigma(qq \to \tilde{q}\tilde{q}) \sim \ln \frac{m_{\sigma}^2}{\mu^2}
+\lim_{m_{\sigma}\to\infty} \sigma(qq \to \tilde{q}\tilde{q}) \sim \ln \frac{m_{\sigma}^2}{\mu^2}.
 \end{align}
@@
 Integrating out only the sgluon means that the octino misses its superpartner in the effective field theory.
-In this case the decoupling theorem \cite{Appelquist:1974tg} does no longer hold.\\
-It is even possible to predict the  logarithmic scaling of $\sigma(qq \to \tilde{q}\tilde{q})$ quantitatively.
+In this case the decoupling theorem \cite{Appelquist:1974tg} does no longer hold\footnote{It is even possible to predict the  logarithmic scaling of $\sigma(qq \to \tilde{q}\tilde{q})$ quantitatively.
 The coefficient of the logarithm is proportional to the difference of the one-loop $\beta$ function coefficients of $g_s$ and $\hat{g}_s$ in the effective theory with the heavy particle integrated out, see eq.
-(4) in \cite{Cheng:1997sq}.
+(4) in \cite{Cheng:1997sq}.}.

### 2016-07-12 figures/NLOContour/MRSSM_uu_susu.py

@@ -1,0 +1,77 @@
+# -*- coding: utf-8 -*-
+"""
+plot of cross section as contour with squark and gluino mass as axis
+only u-squarks, no antisquarks
+"""
+
+from matplotlib import pyplot as plt
+import numpy as np
+from matplotlib.colors import LogNorm
+
+                          
+def nans(shape, dtype=float):
+    """grid of shape full nan"""
+    a = np.empty(shape, dtype)
+    a.fill(np.nan)
+    return a
+
+# grid size
+N = 10 
+
+def contourdata():
+    """
+    
+    """
+    mass_sq = np.linspace(100, 2000, num=N)
+    mass_glu = np.linspace(100, 3000, num=N)
+    # note reverse ordering for yi and xi because of the way   
+    # shape works in numpy                                                  
+    sigma = nans((len(mass_sq),len(mass_glu)))  
+    myfile = open('MRSSM_1L_uu_suLsuR.txt', 'r')     
+    i = 0
+    for line in myfile:
+        data = line.split()
+        for j in range(0,N):
+            sigma[j][i] = data[j]
+        i += 1   
+    myfile.close()
+    
+    v = 10**np.linspace(-1, 7, 9, endpoint=True)
+    fig = plt.figure(1,figsize=(9, 8)) 
+    ax1 = plt.axes()
+    font_size = 18
+    plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
+    plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
+    plt.xticks(fontsize = font_size)
+    plt.yticks(fontsize = font_size)
+    cf=ax1.contourf(mass_sq, mass_glu, sigma, v, norm = LogNorm(), vmin=1, vmax =10**6)
+    levels1 = [1, 10**3, 10**4, 10**5, 10**6]
+    cl1 = plt.contour(cf, levels=levels1,
+                  colors='k',
+                  linewidths=(1,),
+                  hold='on')    
+    levels2 = [10,100]
+    cl2 = plt.contour(cf, levels=levels2,
+                  colors='k',
+                  linewidths=(2,),
+                  hold='on')
+    levels3 = [20,50]
+    cl3 = plt.contour(cf, levels=levels3,
+                  colors='k',
+                  linestyles='dashed',
+                  linewidths=(1,),
[…]

### 2016-07-12 figures/NLOContour/MSSM_uu_susu.py

@@ -1,0 +1,100 @@
+# -*- coding: utf-8 -*-
+"""
+plot of cross section as contour with squark and gluino mass as axis
+only u-squarks, no antisquarks
+"""
+
+from matplotlib import pyplot as plt
+import numpy as np
+from matplotlib.colors import LogNorm
+
+                          
+def nans(shape, dtype=float):
+    """grid of shape full nan"""
+    a = np.empty(shape, dtype)
+    a.fill(np.nan)
+    return a
+
+# grid size
+N = 10 
+
+def contourdata():
+    """
+    
+    """
+    mass_sq = np.linspace(100, 2000, num=N)
+    mass_glu = np.linspace(100, 3000, num=N)
+    # note reverse ordering for yi and xi because of the way   
+    # shape works in numpy    
+                                                  
+    sigmaLR = nans((len(mass_sq),len(mass_glu)))  
+    myfile = open('MSSM_1L_uu_suLsuR.txt', 'r')     
+    i = 0
+    for line in myfile:
+        data = line.split()
+        for j in range(0,N):
+            sigmaLR[j][i] = data[j]
+        i += 1   
+    myfile.close()
+    
+    sigmaLL = nans((len(mass_sq),len(mass_glu)))  
+    myfile = open('MSSM_1L_uu_suLsuL.txt', 'r')     
+    i = 0
+    for line in myfile:
+        data = line.split()
+        for j in range(0,N):
+            sigmaLL[j][i] = data[j]
+        i += 1   
+    myfile.close()
+    
+    #sigmaTree = nans((len(mass_sq),len(mass_glu)))  
+    #myfile = open('MSSM_Tree_uu_susu.txt', 'r')     
+    #i = 0
+    #for line in myfile:
+    #    data = line.split()
+    #    for j in range(0,N):
+    #        sigmaTree[j][i] = data[j]
+    #    i += 1   
+    #myfile.close()
+    
+	
+    sigma = (sigmaLR + 2*sigmaLL)#/sigmaTree
+    v = 10**np.linspace(-1, 7, 9, endpoint=True)
+    fig = plt.figure(1,figsize=(9, 8)) 
+    ax1 = plt.axes()
+    font_size = 18
+    plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
+    plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
[…]

### 2016-07-12 figures/NLOContour/MSSM_uu_susu_Kfactor.py

@@ -1,0 +1,84 @@
+# -*- coding: utf-8 -*-
+"""
+plot of cross section as contour with squark and gluino mass as axis
+only u-squarks, no antisquarks
+"""
+
+from matplotlib import pyplot as plt
+import numpy as np
+from matplotlib.colors import LogNorm
+
+                          
+def nans(shape, dtype=float):
+    """grid of shape full nan"""
+    a = np.empty(shape, dtype)
+    a.fill(np.nan)
+    return a
+
+# grid size
+N = 10 
+
+def contourdata():
+    """
+    
+    """
+    mass_sq = np.linspace(100, 2000, num=N)
+    mass_glu = np.linspace(100, 3000, num=N)
+    # note reverse ordering for yi and xi because of the way   
+    # shape works in numpy    
+                                                  
+    sigmaLR = nans((len(mass_sq),len(mass_glu)))  
+    myfile = open('MSSM_1L_uu_suLsuR.txt', 'r')     
+    i = 0
+    for line in myfile:
+        data = line.split()
+        for j in range(0,N):
+            sigmaLR[j][i] = data[j]
+        i += 1   
+    myfile.close()
+    
+    sigmaLL = nans((len(mass_sq),len(mass_glu)))  
+    myfile = open('MSSM_1L_uu_suLsuL.txt', 'r')     
+    i = 0
+    for line in myfile:
+        data = line.split()
+        for j in range(0,N):
+            sigmaLL[j][i] = data[j]
+        i += 1   
+    myfile.close()
+    
+    sigmaTree = nans((len(mass_sq),len(mass_glu)))  
+    myfile = open('MSSM_Tree_uu_susu.txt', 'r')     
+    i = 0
+    for line in myfile:
+        data = line.split()
+        for j in range(0,N):
+            sigmaTree[j][i] = data[j]
+        i += 1   
+    myfile.close()
+    
+    K = (sigmaLR + 2*sigmaLL)/sigmaTree
+    v = np.linspace(0.5, 1.7, 13, endpoint=True)
+    fig = plt.figure(1,figsize=(9, 8)) 
+    ax1 = plt.axes()
+    font_size = 18
+    plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
+    plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
[…]

### 2016-07-13 Appendix.tex
K factor MRSSM contour plot

@@
 
-\subsection{Weyl basis and 2-spinor notation}\label{sec:2spinor_notation}
+\subsection{Weyl Basis and 2-Spinor Notation}\label{sec:2spinor_notation}
 As representation of the $\gamma$-matrices the Weyl or chiral representation is chosen:
@@
 
-\subsection{Anticommuting numbers}\label{sec:AnticommNumbers}
+\subsection{Anticommuting Numbers}\label{sec:AnticommNumbers}
 Anticommuting numbers $\theta^\alpha$ are also referred to as Grassmann numbers and are defined by $\theta^\alpha\theta^\beta = -\theta^\beta\theta^\alpha$ and commute with ordinary numbers.\\
@@
 
-\subsection{Feynman rules for the RSQCD}\label{sec:FeynmanRules}
+\subsection{Feynman Rules for the RSQCD}\label{sec:FeynmanRules}
 The following Feynman rules are derived from the Lagrangian of the R-symmetric supersymmetric quantum chromodynamics (RSQCD) eq.

### 2016-07-13 Introduction.tex
K factor MRSSM contour plot

--- 2016-04-24 Introduction.tex
@@
-motivation: aesthetic: Coleman-Mandula --> Haag-Lopuszanski-Sohnius-Theorem\\
-plots for exclusion of squarks in specific SUSY scenarios (from Michael) --> R-Symmetry could be possible explanation for that because:\\
-MSSM-Lagrangian --> trafo rules for superfields under R-symm --> forbidden terms in MRSSM (write down Lagrangian for R-symmetric SUSYQCD)\\
-suppression of squark production in MRSSM by less diagrams ($m_{gluino}^{-4}$ suppression at low energies in MRSSM and only $m_{gluino}^{-2}$ suppression in MSSM)\\
-R-charges of all fields (show in diagram!) --> only if R-charges of final / initial particles are zero, a diagram is allowed in R-symm. model\\
-references to build in
-\begin{itemize}
-\item "Matching Squark Pair Production at NLO with Parton Showers" from Gavin, Hangst, Krämer, Mühlleitner,.. for complete treatment of NLO calculation\\
-\item "dIRAC gAUGINOS IN susy - sUPPRESSED jETS + <met sIGNALS: a sNOWMASS wHITEPAPER" FROM kRIBS, mARTIN for Squark production at LO, allude to same result\\
-\item "Dirac Gaugino Masses and supersoft SUSY breaking" from Fox, Weiner, Nelson for the introduction of the MRSSM
-\end{itemize}
+\section{Introduction}
+The Standard Model of particle physics is a quantum field theory which relies on the principle of gauge invariance.
+It describes the world's fundamental particles and the interactions among them and predicts the most accurately measured observables in physics.\\
+Besides these triumphs, it is known to be incomplete for example for not including dark matter or a description of gravity.
+Because of these and other flaws, one studies extensions of the Standard Model.
+One mathematically very appealing extension is the concept of supersymmetry.
+Within this framework one often studies the Minimal Supersymmetric Standard Model (MSSM).
+This theory provides a candidate for dark matter and elegant solutions of e.g.
+the hierarchy problem.
+However the MSSM does not come without problems.
+One of these is that supersymmetric particles have not been discovered so far.
+This is  actually reasoned by introducing supersymmetry breaking.
+However, in order to still solve the hierarchy problem, supersymmetry breaking should not be too large.
+According to searches for supersymmetry at the Large Hadron Collider, supersymmetric particles are at the moment on the verge on being too heavy for the MSSM to solve the hierarchy problem without loosing its attractiveness.\\
+A non-trivial extension of supersymmetry - $R$-symmetry - may explain this and other issues.
+$R$-symmetry is, according to the Haag-Lopuszanski-Sohnius theorem, the only viable extension of the supersymmetry group of the MSSM.
+This is, the combination of Poincaré symmetry, supersymmetry and $R$-symmetry is the maximal symmetry a reasonable quantum field theory can have.\\
+\ignore{Imposing supersymmetry and $R$-symmetry on the Standard Model, gives - according to the Haag-Lopuszanski-Sohnius theorem - the maximal symmetry group a reasonable quantum field theory can have.\\}
+Motivated be these facts, the Minimal $R$-Symmetric Supersymmetric Standard Model (MRSSM) is the subject of investigations within this thesis.
+More specifically, the production cross section of strongly interacting supersymmetric particles in the MRSSM is studied.
+It will turn out that there are significant changes in the production of squarks and gluinos when turning from the MSSM to the MRSSM.\\
+This thesis starts with summarizing the main aspects of the Standard Model before the concept of supersymmetry and $R$-symmetry is introduced.
+This includes the introduction of the models which incorporate the minimal form of the symmetry in question.
+Section \ref{sec:SquarkGluinoTree} compares the production cross section of squark and gluinos in both models at \mbox{tree-level}.
+After identifying an attractive region of parameter space in the MRSSM, it will turn out that the most interesting difference manifests in the channel of squark production.
+As there are no programs available with whom next-to-leading order cross sections within the MRSSM can be calculated, the rest of the thesis focuses on the next-to-leading order calculation of the squark production cross section.
+: Section \ref{sec:VirtRealCorr} discusses the golden thread of the calculation of a next-to-leading order cross section including massless external particles before section \ref{sec:renMRSSM} gives detailed information about the renormalization of the MRSSM.
+This includes the explicit form of required renormalization constants, reaching form the on-shell scheme over a mixture of $\overline{\mathrm{MS}}$- and zero-momentum subtraction scheme to supersymmetry restoring counterterms.
+This section also discusses how renormalized one-loop matrix elements are generated as an input for a program which calculates the squark production cross section in the MRSSM.
+The thesis closes with an explanation on how this very program is constructed and the representation of the next-to-leading order cross section for squark production in the form of $K$-factors.
+
+%motivation: aesthetic: Coleman-Mandula --> Haag-Lopuszanski-Sohnius-Theorem\\
+%plots for exclusion of squarks in specific SUSY scenarios (from Michael) --> R-Symmetry could be possible explanation for that because:\\
+%MSSM-Lagrangian --> trafo rules for superfields under R-symm --> forbidden terms in MRSSM (write down Lagrangian for R-symmetric SUSYQCD)\\
+%suppression of squark production in MRSSM by less diagrams ($m_{gluino}^{-4}$ suppression at low energies in MRSSM and only $m_{gluino}^{-2}$ suppression in MSSM)\\
+%R-charges of all fields (show in diagram!) --> only if R-charges of final / initial particles are zero, a diagram is allowed in R-symm. model\\
+%references to build in
+%\begin{itemize}
+%\item "Matching Squark Pair Production at NLO with Parton Showers" from Gavin, Hangst, Krämer, Mühlleitner,.. for complete treatment of NLO calculation\\
+%\item "dIRAC gAUGINOS IN susy - sUPPRESSED jETS + <met sIGNALS: a sNOWMASS wHITEPAPER" FROM kRIBS, mARTIN for Squark production at LO, allude to same result\\
+%\item "Dirac Gaugino Masses and supersoft SUSY breaking" from Fox, Weiner, Nelson for the introduction of the MRSSM
+%\end{itemize}

### 2016-07-13 NLO.tex
K factor MRSSM contour plot

@@
 All three contributions have to be calculated with next-to-leading order parton density functions and $\alpha_s$.
+There are five mass scales: the squark mass $m_{\tilde{q}}$, the gluino mass $m_{\tilde{g}}$, the center of mass energy of the colliding protons $\sqrt{S}$, the top-quark mass which is fixed to $m_t = \unit[172]{GeV}$ and the mass of the pseudoscalar $m_{\sigma}$.
 The next section summaries how the calculation has been automated within a \texttt{C++} program.
@@
 Both the virtual and the Born matrix amplitude have been generated with the \texttt{Mathematica} package \texttt{FeynArts}.
-To this end a modelfile, generated by the \texttt{Mathematica} package \texttt{SARAH}, has been adjusted appropriately as described in section \ref{sec:ModelFileImplementation}.
+To this end a model file, generated by the \texttt{Mathematica} package \texttt{SARAH}, has been adjusted appropriately as described in section \ref{sec:ModelFileImplementation}.
 The matrix amplitudes have been processed further to $\sum|\mathcal{M}^{\mathrm{B}}|^2$ and $ \sum 2\Re (\mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast})$ by the \texttt{Mathematica} package \texttt{FormCalc} before this output has then been converted to a \texttt{C++} readable code.
@@
 	\path [line, line width = 1] (Virt) -- (Sigma);
-	\path [line, line width = 1] (9.6,-9.45) -- (Sigma);
+	\path [line, line width = 1] (9.5,-9.45) -- (Sigma);
 \end{tikzpicture}
@@
 Regarding the virtual corrections, this has been done by numerically extracting the $\frac{1}{\epsilon}$ and $\frac{1}{\epsilon^2}$ coefficient of loop integrals (see the discussion in section \ref{sec:SetLambdaExplanation} for more details).\\
-As the poles of the real corrections have been calculated analytically, it is possible to quote them. The double pole is actually proportional to the Born cross section:
+The poles of the real corrections have been calculated analytically. The double pole is actually proportional to the Born cross section:
 \begin{align}
@@
 \end{align}
+The single pole is not that succinct and therefore not quoted here.
 
@@
 Keeping them in eq.
-\eqref{eq:prefactoredecomp} would slow the computation of the real part down by about a factor of five because this part of the calculation is done analytically.
+\eqref{eq:prefactoredecomp}, would slow the computation of the real part down by a factor of about five because this part of the calculation is done analytically.
 Therefore a speed-up can been achieved by discarding the common prefactors at the cost of loosing track about the origin of the next-to-leading order correction.\\
@@
 Here, $X$ denotes the initial state and $Y$ the final state.
-Figure \ref{fig:1LXsection_fixed_m} shows the $K$-factors for the production of up-squarks in the MRSSM for varying masses of both, the squark ($m_{\tilde{g}} = \unit[2000]{GeV}$) and the gluino $m_{\tilde{q}} = \unit[1000]{GeV}$.
+Figure \ref{fig:1LXsection_fixed_m_MRSSM} shows the $K$-factors for the production of up-squarks in the MRSSM for varying masses of both, the squark \mbox{($m_{\tilde{g}} = \unit[2000]{GeV}$)} and the gluino ($m_{\tilde{q}} = \unit[1000]{GeV}$).
 The mass of the pseudoscalar has been fixed to $m_{\sigma} = \unit[5000]{GeV}$ in both plots.
-In addition to the $K$-factor, the contributions to it are split into the ones coming from the Born cross section\footnote{The contribution of the Born cross section to the $K$-factor is smaller as one as it has been calculated with next-to-leading order parton density functions.} and real and virtual corrections.\\
+In addition, the contributions to the $K$-factor are split into the ones coming from the Born cross section\footnote{The contribution of the Born cross section to the $K$-factor is smaller than one as it has been calculated with next-to-leading order parton density functions.} and real and virtual corrections.\\
 It can be seen that the  $K$-factor increases with increasing squark mass and decreases with increasing gluino mass.
@@
 \includegraphics[scale=.4]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV.png}
-\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).}\label{fig:1LXsection_fixed_m}
+\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).
+The other parameters are $\sqrt{S} = \unit[13]{TeV}$, $m_{\tilde{\sigma}} = \unit[5000]{GeV}$ and $\mu_R = \mu_F = m_{\tilde{q}}$.
+The used parton density function are the one from table \ref{tab:MRSSMKfactors}.
+The missing smoothness of the plot originates from the uncertainty of the integration.}\label{fig:1LXsection_fixed_m_MRSSM}
 \end{center}
@@
 Furthermore, the change from Majorana to Dirac gluinos can never imply an amplification of processes involving gluinos.
-The reason for this is, that if a gluino undergoes, due to its mass, a chirality flip, the right handed part of it, namely the octino, does neither couple to quarks nor to squarks.
+The reason for this is that if a gluino undergoes, due to its mass, a chirality flip, the right handed part of it, namely the octino, does neither couple to quarks nor to squarks.
 However, the effect of quark radiation is thought to increase when $m_{\tilde{g}} > m_{\tilde{q}}$.
@@
 \hlinewd{2pt}
-$500$ & $500$ & $966.4$ & $1441$ & $1.49$\\
+$500$ & $500$ & $966.4$ & $1440$ & $1.49$\\
 $500$ & $1000$ & $303.4$ & $383$ & $1.26$\\
@@
 \caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$  in the MRSSM for a selected set of masses.
-The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$ and the pseudoscalar mass is fixed to $m_{\mathrm{\sigma}} = \unit[5000]{GeV}$.
-For $\sigma^{\mathrm{LO}}$
-\texttt{MMHT2014}(LHAPDF ID: 25000) parton density functions has been used, whereas $\sigma^{\mathrm{NLO}}$ used
-\texttt{MMHT2014}(LHAPDF ID: 25100)}\label{tab:MRSSMKfactors}
+The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$ and the pseudoscalar mass is fixed to \mbox{$m_{\mathrm{\sigma}} = \unit[5000]{GeV}$}.
+For $\sigma^{\mathrm{LO}}$ parton density functions \texttt{MMHT2014}(LHAPDF ID: $25000$) has been used, whereas for $\sigma^{\mathrm{NLO}}$ \texttt{MMHT2014}(LHAPDF ID: $25100$) was used.}\label{tab:MRSSMKfactors}
 \end{center}
@@
 It can be seen that the $K$-factors depend strongly on the ratio $\frac{m_{\tilde{g}}}{m_{\tilde{q}}}$ but not that strongly on the masses itself.\\
-For three different choices of $m_{\tilde{q}}$ and $m_{\tilde{g}}$, Philip Dießner checked the results up to permille accuracy by doing the calculation using \texttt{GoSam}\cite{Cullen:2014yla, Cullen:2011ac} and \texttt{MadGraph5\_aMC@NLO}\cite{Alwall:2014hca} on the basis of the same model file.
+For three different choices of $m_{\tilde{q}}$ and $m_{\tilde{g}}$, Philip Dießner checked the results up to permille accuracy by doing the calculation using \texttt{GoSam}\cite{Cullen:2014yla, Cullen:2011ac} and \texttt{MadGraph5\_aMC@NLO}\cite{Alwall:2014hca} on the basis of the same model file.\\
+The next-to-leading order cross sections of this chapter bear a relative uncertainty of one percent due to the numerical integration.
+The uncertainty which corresponds to the variation of the scales $\mu_R$ and $\mu_F$, see section \ref{sec:tree-level_cross_sections}, are evaluate to around 15\%.
 
@@
 \caption{Dependence of the $K$-factor for the process $pp \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).
-The $K$-factors have been broken down to contributions coming from $pp \to \tilde{u}_L\tilde{u}_R$ and from $pp \to \tilde{u}_L\tilde{u}_L$.
-The latter equals the contributions coming from $pp \to \tilde{u}_R\tilde{u}_R$.}\label{fig:1LXsection_fixed_m}
+The parameters are chosen like in fig.
+\ref{fig:1LXsection_fixed_m_MRSSM}.The $K$-factors have been broken down to contributions coming from $pp \to \tilde{u}_L\tilde{u}_R$ and from $pp \to \tilde{u}_L\tilde{u}_L$.
+The latter equals the contributions coming from $pp \to \tilde{u}_R\tilde{u}_R$.
+The missing smoothness of the plot originates from the uncertainty of the integration.}\label{fig:1LXsection_fixed_m_MSSM}
 \end{center}
@@
 $1500$ & $1000$ & $9.49 \pm 0.03$ & $9.48 \pm 0.09$ \\
-$1000$ & $2000$ & $13.32 \pm 0.05$ & $13.89 \pm 0.11\%$ 
+$1000$ & $2000$ & $13.32 \pm 0.05$ & $13.89 \pm 0.11$ 
 \end{tabular}
@@
 The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$.
+The stated uncertainties originate from the phase space integration.
 Within the \texttt{MadGraph5} calculation, the $s$-channel gluino diagrams have been discarded.
@@
 The given uncertainties are the uncertainties of the integration over the phase space and the chosen parameters are: $\mu_F = \mu_R = m_{\tilde{q}}$ and $\sqrt{S} = \unit[13]{TeV}$.\\
-Figure \ref{fig:1LXsection_fixed_m} shows the $K$-factors for squark production in the MSSM, broken down to $K$-factors for ``chirality'' like ($\tilde{u}_L \tilde{u}_L$) and unlike squarks $\tilde{u}_L \tilde{u}_R$.
+Figure \ref{fig:1LXsection_fixed_m_MSSM} shows the $K$-factors for squark production in the MSSM, broken down to $K$-factors for ``chirality'' like ($\tilde{u}_L \tilde{u}_L$) and unlike squarks ($\tilde{u}_L \tilde{u}_R$).
 It can be seen, that the mass dependence of $K(pp \to \tilde{u}_L \tilde{u}_R)$ in the MSSM is quite similar to the one in the MRSSM and that the MSSM $K$-factors are slightly smaller than in the MSSM.
@@
 The mass dependence of them is quite the same as for the  $pp \to \tilde{u}_L \tilde{u}_R$ channel.
-The only difference is a local maximum of the $K$-factor as a function of the gluino mass at $m_{\tilde{g}} \approx \unit[500]{GeV}$.
-Adding the cross sections for the three possible channels $\tilde{u}_L \tilde{u}_R$, $\tilde{u}_L \tilde{u}_L$ and $\tilde{u}_R \tilde{u}_R$ together one ends up with $K$-factors which have the same mass dependence as in the MRSSM but which can, depending on the chosen parameters, be significantly smaller.\\
+The only difference is a local maximum of the $K$-factor as a function of the gluino mass at $m_{\tilde{g}} \approx \unit[500]{GeV}$, where $m_{\tilde{q}} = \unit[1000]{GeV}$.
+Adding the cross sections for the three possible channels $\tilde{u}_L \tilde{u}_R$, $\tilde{u}_L \tilde{u}_L$ and $\tilde{u}_R \tilde{u}_R$ together one ends up with $K$-factors which have the very similar mass dependence as in the MRSSM but which can, depending on the chosen parameters, be significantly smaller.\\
 Table \ref{tab:KfactorsMSSM} displays the leading order and next-to-leading order cross section of up-squark production in the MSSM.
@@
 Comparing with the results from the MRSSM in table \ref{tab:MRSSMKfactors}, one can state that the $K$-factors of the MRSSM are slightly larger.
-This might be the case, as there are additional degrees of freedom in the $R$-symmetric model, namely the octino which enters the gluino self-energy contributions (see second diagram from the right in \ref{fig:GluinoSE}) and the sgluons which enters there and in box diagrams (see lower right diagram in \ref{fig:1loopdiagrams}).
-The dependence on the sgluon mass is discussed within the next chapter
-%Calculate uncertainties for multiple/ points(pdf, scale, integration)
+This might be the case, as there are additional degrees of freedom in the $R$-symmetric model, namely the octino which enters the gluino self-energy contributions (see second diagram from the right in \ref{fig:GluinoSE}) and sgluons which enter box diagrams (see lower right diagram in \ref{fig:1loopdiagrams}).
+The dependence on the sgluon mass is discussed within the next section.\\
+The uncertainties of next-to-leading order cross sections, due to the phase space integration, within this section are of percent order.
+The uncertainty which corresponds to the scale variation does not increase 15\%.
 
@@
 \caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$ on the mass of the pseudoscalar sgluon.
-For $m_{\sigma} \approx \unit[10^5]{GeV}$ onwards want find a logarithmic scaling as predicted by \cite{Cheng:1997sq}.}
+For $m_{\sigma} \approx \unit[10^5]{GeV}$ onwards want find a logarithmic scaling as predicted by \cite{Cheng:1997sq}.}\label{fig:SgluonMassDependence}
 \end{center}
@@
 (4) in \cite{Cheng:1997sq}.}.
+The logarithmic scaling of the cross section as a function of the mass of the pseudoscalar is shown in fig. \ref{fig:SgluonMassDependence}.

### 2016-07-13 Renormalization.tex
K factor MRSSM contour plot

@@
 \includegraphics[scale=.5]{figures/MatrixElement_Poles.png}
-\caption{Coefficients of $\mathcal{O}(\epsilon^0)$, $\mathcal{O}(\epsilon^{-1})$ and $\mathcal{O}(\epsilon^{-2})$ terms of $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$ of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM as a function of the Mandelstam variable $t$.
+\caption{Coefficients of $\mathcal{O}(\epsilon^0)$, $\mathcal{O}(\epsilon^{-1})$ and $\mathcal{O}(\epsilon^{-2})$ terms of the dimensionless quantity $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$ of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM as a function of the Mandelstam variable $t$.
 Final state helicities and colors are averaged.
-The parameters are fixed to $m_{\tilde{q}} = \mu = \unit[1000]{GeV}$, $m_{\tilde{g}} = \unit[2000]{GeV}$, $m_{\sigma} = \unit[5000]{GeV}$ and $\sqrt{s} = \unit[6000]{GeV}$ which is the partonic center-of-mass energy.}\label{fig:MatrixElementPoles}
+The parameters are fixed to $m_{\tilde{q}} = \mu_R = \unit[1000]{GeV}$, $m_{\tilde{g}} = \unit[2000]{GeV}$, $m_{\sigma} = \unit[5000]{GeV}$ and $\sqrt{s} = \unit[6000]{GeV}$ which is the partonic center-of-mass energy.}\label{fig:MatrixElementPoles}
 \end{center}

### 2016-07-13 Standardmodel.tex
K factor MRSSM contour plot

@@
 It is a gauge quantum field theory and therefore characterized by its invariance under symmetry groups.
-The Standard Model contains different fields, whose quantized excitations are interpreted as all known particles.\\
+The Standard Model contains different fields, whose quantized excitations are interpreted as particles.\\
 This chapter summarizes the most important aspects of the Standard Model.
@@
 \subsection{Symmetries and Transformations}
-\subsubsection*{Space-time Symmetries}
-The Standard Model is defined on Minkowski space, whose coordinates are label with $x^\mu$ $\mu \in \left\{0,1,2,4\right\}$.
+\subsubsection*{Space-Time Symmetries}
+The Standard Model is defined on Minkowski space, whose coordinates are labeled with $x^\mu$ $\mu \in \left\{0,1,2,4\right\}$.
 As a relativistic theory it is invariant under Poincaré transformations, i.e.
-it is invariant under Lorentz-transformations (with generators $J^{\mu\nu}$) and translations (with generators $P^\mu$) in spacetime.
+it is invariant under Lorentz-transformations (with generators $J^{\mu\nu}$) and translations (with generators $P^\mu$) in space-time.
 The set of all Poincaré transformations form the Poincaré group, which is a Lie group.
-Its generators obey the Poincaré-algebra
+Its generators obey the Poincaré algebra
 \begin{align}
@@
 \end{align}
-The fields of the Standard Model transform in different representations of the Poincaré-group \cite{book:17018}.
+The fields of the Standard Model transform in different representations of the Poincaré group \cite{book:17018}.
 
@@
 where $U(x)$ is an element of the gauge group in question.
-Because the gauge group is an unitary matrix Lie group, it can be written in the form $U(x)=\mathrm{exp}(-igT^a\theta^a(x))$.
+Because the gauge group is an unitary matrix Lie group, it can be written like $U(x)=\mathrm{exp}(-igT^a\theta^a(x))$.
 Here, $T^a$ are the self-adjoint generators of the associated Lie algebra which obey
@@
 \end{align}
-with $f_{abc}$ the structure constants of a Lie algebra, $g$ is the coupling constant of the gauge group and $\theta^a(x)$ are local parameters.\\
-As the parameters of the gauge group are local, the derivative in \eqref{eq:DiracLagrangian} spoils gauge invariance.
+with $f_{abc}$ being the structure constants of a Lie algebra, $g$ is the coupling constant of the gauge group and $\theta^a(x)$ are local parameters.\\
+As the parameters of the gauge group are local, the derivative in eq.
+\eqref{eq:DiracLagrangian} spoils gauge invariance.
 In order to rectify the gauge invariance of the Lagrangian, one introduces a further field for each index $a$ of the generators, the gauge vector $G^{a\mu}$.
@@
 $f_{abc} \neq 0$, there are self interactions among the spin-1 particles.\\
-The gauge group of the Standard Model is a direct product of the three gauge groups\footnote{The subscript stands for the associated charge of the groups respectively: $Y$ for hypercharge, $L$ for left handedness (weak Isospin $I_3$) and $C$ for color}: $U(1)_Y$, $SU(2)_L$ and $SU(3)_C$.
+The gauge group of the Standard Model is a direct product of the three gauge groups\footnote{The subscripts stand for the associated charge of the respective groups: $Y$ for hypercharge, $L$ for left handedness (weak Isospin $I_3$) and $C$ for color}: $U(1)_Y$, $SU(2)_L$ and $SU(3)_C$.
 The elements $U(x)$ of those are given in table \ref{tab:SM_transformations}.\\
-These gauge groups give rise to 3 forces: the strong force, the weak force and the electromagnetic force.
+These gauge groups give rise to three forces: the strong force, the weak force and the electromagnetic force.
 \begin{table}[H]

### 2016-07-13 figures/Contour_Plots/MRSSM_TreeLevel.py

@@ -64,7 +64,7 @@ def contourdata():
     plt.clabel(cl2, fmt='%2.1f', colors='k', fontsize = font_size)
     plt.clabel(cl3, fmt='%2.1f', colors='k', fontsize = font_size)
     cbar = fig.colorbar(cf, orientation='horizontal')
-    cbar.ax.set_xlabel(r'$\sigma^{\mathrm{B}}_{\mathrm{MRSSM}}(qq \to \tilde{q}\tilde{q})$ in fb', size = font_size)
+    cbar.ax.set_xlabel(r'$\sigma^{\mathrm{B}}_{\mathrm{MRSSM}}(pp \to \tilde{q}\tilde{q})$ in fb', size = font_size)
     cbar.ax.tick_params(labelsize=font_size)
     cbar.add_lines(cl1)
     cbar.add_lines(cl2, erase=False)

### 2016-07-13 figures/Contour_Plots/MRSSM_TreeLevel_qq_sqsq.py

@@ -66,7 +66,7 @@ def contourdata():
     plt.clabel(cl3, fmt='%2.1f', inline=1, colors='k', fontsize = font_size, manual=manual_locations3)
     
     cbar = fig.colorbar(cf, ticks=v, orientation='horizontal')
-    cbar.ax.set_xlabel(r'$\sigma^{\mathrm{B}}_{\mathrm{MRSSM}}(qq \to \tilde{q}\tilde{q})$ in fb', size = font_size)
+    cbar.ax.set_xlabel(r'$\sigma^{\mathrm{B}}_{\mathrm{MRSSM}}(pp \to \tilde{q}\tilde{q})$ in fb', size = font_size)
     cbar.ax.tick_params(labelsize=font_size)
     cbar.add_lines(cl1)
     cbar.add_lines(cl2, erase=False)

### 2016-07-13 figures/Contour_Plots/MSSM_TreeLevel_qq_sqsq.py

@@ -65,7 +65,7 @@ def contourdata():
     plt.clabel(cl2, fmt='%2.1f', colors='k', fontsize = font_size, manual=manual_locations2)
     plt.clabel(cl3, fmt='%2.1f', colors='k', fontsize = font_size, manual=manual_locations2)
     cbar = fig.colorbar(cf, ticks=v, orientation='horizontal')
-    cbar.ax.set_xlabel(r'$\sigma^{\mathrm{B}}_{\mathrm{MSSM}}(qq \to \tilde{q}\tilde{q})$ in fb', size = font_size)
+    cbar.ax.set_xlabel(r'$\sigma^{\mathrm{B}}_{\mathrm{MSSM}}(pp \to \tilde{q}\tilde{q})$ in fb', size = font_size)
     cbar.ax.tick_params(labelsize=font_size)
     cbar.add_lines(cl1)
     cbar.add_lines(cl2, erase=False)

### 2016-07-13 figures/NLOContour/MRSSM_uu_susu_Kfactor.py

@@ -25,30 +25,19 @@ def contourdata():
     mass_sq = np.linspace(100, 2000, num=N)
     mass_glu = np.linspace(100, 3000, num=N)
     # note reverse ordering for yi and xi because of the way   
-    # shape works in numpy    
-                                                  
-    sigmaLR = nans((len(mass_sq),len(mass_glu)))  
-    myfile = open('MSSM_1L_uu_suLsuR.txt', 'r')     
+    # shape works in numpy                                                  
+    sigmaNLO = nans((len(mass_sq),len(mass_glu)))  
+    myfile = open('MRSSM_1L_uu_suLsuR.txt', 'r')     
     i = 0
     for line in myfile:
         data = line.split()
         for j in range(0,N):
-            sigmaLR[j][i] = data[j]
-        i += 1   
-    myfile.close()
-    
-    sigmaLL = nans((len(mass_sq),len(mass_glu)))  
-    myfile = open('MSSM_1L_uu_suLsuL.txt', 'r')     
-    i = 0
-    for line in myfile:
-        data = line.split()
-        for j in range(0,N):
-            sigmaLL[j][i] = data[j]
+            sigmaNLO[j][i] = data[j]
         i += 1   
     myfile.close()
     
     sigmaTree = nans((len(mass_sq),len(mass_glu)))  
-    myfile = open('MSSM_Tree_uu_susu.txt', 'r')     
+    myfile = open('MRSSM_Tree_uu_suLsuR.txt', 'r')     
     i = 0
     for line in myfile:
         data = line.split()
@@ -57,7 +46,7 @@ def contourdata():
         i += 1   
     myfile.close()
     
-    K = (sigmaLR + 2*sigmaLL)/sigmaTree
+    K = sigmaNLO/sigmaTree
     v = np.linspace(0.5, 2, 16, endpoint=True)
     v2 = np.linspace(0.5, 1.9, 8, endpoint=True)
     fig = plt.figure(1,figsize=(9, 8)) 
@@ -67,18 +56,19 @@ def contourdata():
     plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
     plt.xticks(fontsize = font_size)
     plt.yticks(fontsize = font_size)
-    cf=ax1.contourf(mass_sq, mass_glu, K, v, vmin=0.5, vmax = 2)
-    
[…]

### 2016-07-13 figures/One_Loop/MRSSM_uu_susu_Kfactors_msg=2000GeV.py

@@ -42,7 +42,7 @@ fig = plt.figure(1,figsize=(10, 9))
 
 first_window = plt.subplot(111)
 plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = 22)
-plt.ylabel(r"$K(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = 22)
+plt.ylabel(r"$K_{\mathrm{MRSSM}}(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = 22)
 plt.xticks(fontsize = 20)
 plt.yticks(fontsize = 20)
 

### 2016-07-13 figures/One_Loop/MRSSM_uu_susu_Kfactors_msq=1000GeV.py

@@ -42,7 +42,7 @@ fig = plt.figure(1,figsize=(10, 9))
 
 first_window = plt.subplot(111)
 plt.xlabel(r"$m_{\tilde{g}}$ in GeV", size = 22)
-plt.ylabel(r"$K(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = 22)
+plt.ylabel(r"$K_{\mathrm{MRSSM}}(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = 22)
 plt.xticks(fontsize = 20)
 plt.yticks(fontsize = 20)
 

### 2016-07-13 figures/One_Loop/MRSSM_uu_susu_Kfactors_msq=1000GeV_msg=2000GeV.py

@@ -37,7 +37,7 @@ fig = plt.figure(1,figsize=(10, 9))
 
 first_window = plt.subplot(111)
 plt.xlabel(r"$m_{\tilde{\sigma}}$ in GeV", size = 22)
-plt.ylabel(r"$K(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = 22)
+plt.ylabel(r"$K_{\mathrm{MRSSM}}(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = 22)
 plt.xticks(fontsize = 20)
 plt.yticks(fontsize = 20)
 

### 2016-07-13 figures/One_Loop/MSSM/MSSM_uu_susu_Kfactors_msg=2000GeV.py

@@ -65,7 +65,7 @@ font_size = 18
 ############# first subplot #####################
 first_window = plt.subplot2grid((2,2), (0,0))
 plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
-plt.ylabel(r"$K(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = font_size)
+plt.ylabel(r"$K_{\mathrm{MSSM}}(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = font_size)
 plt.xticks(fontsize = font_size)
 plt.yticks(fontsize = font_size)
 
@@ -87,7 +87,7 @@ plt.plot(m_gluino, sigma_NLO_1L_lr/sigma_LO_Tree_lr, lw=2, ls="-", c='blue')#, l
 ############# second subplot #####################
 second_window = plt.subplot2grid((2,2), (0,1))
 plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
-plt.ylabel(r"$K(pp \to \tilde{u}_L\tilde{u}_L)$ ", size = font_size)
+plt.ylabel(r"$K_{\mathrm{MSSM}}(pp \to \tilde{u}_L\tilde{u}_L)$ ", size = font_size)
 plt.xticks(fontsize = font_size)
 plt.yticks(fontsize = font_size)
 
@@ -110,7 +110,7 @@ plt.plot(m_gluino, sigma_NLO_1L_ll/sigma_LO_Tree_ll, lw=2, ls="-", c='blue')#, l
 ############# third subplot #####################
 third_window = plt.subplot2grid((2,2), (1,0), colspan = 2)
 plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
-plt.ylabel(r"$K(pp \to \tilde{u}\tilde{u})$ ", size = font_size)
+plt.ylabel(r"$K_{\mathrm{MSSM}}(pp \to \tilde{u}\tilde{u})$ ", size = font_size)
 plt.xticks(fontsize = font_size)
 plt.yticks(fontsize = font_size)
 

### 2016-07-13 figures/One_Loop/MSSM/MSSM_uu_susu_Kfactors_msq=1000GeV.py

@@ -65,7 +65,7 @@ font_size = 18
 ############# first subplot #####################
 first_window = plt.subplot2grid((2,2), (0,0))
 plt.xlabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
-plt.ylabel(r"$K(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = font_size)
+plt.ylabel(r"$K_{\mathrm{MSSM}}(pp \to \tilde{u}_L\tilde{u}_R)$ ", size = font_size)
 plt.xticks(fontsize = font_size)
 plt.yticks(fontsize = font_size)
 
@@ -87,7 +87,7 @@ plt.plot(m_gluino, sigma_NLO_1L_lr/sigma_LO_Tree_lr, lw=2, ls="-", c='blue')#, l
 ############# second subplot #####################
 second_window = plt.subplot2grid((2,2), (0,1))
 plt.xlabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
-plt.ylabel(r"$K(pp \to \tilde{u}_L\tilde{u}_L)$ ", size = font_size)
+plt.ylabel(r"$K_{\mathrm{MSSM}}(pp \to \tilde{u}_L\tilde{u}_L)$ ", size = font_size)
 plt.xticks(fontsize = font_size)
 plt.yticks(fontsize = font_size)
 
@@ -110,7 +110,7 @@ plt.plot(m_gluino, sigma_NLO_1L_ll/sigma_LO_Tree_ll, lw=2, ls="-", c='blue')#, l
 ############# third subplot #####################
 third_window = plt.subplot2grid((2,2), (1,0), colspan = 2)
 plt.xlabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
-plt.ylabel(r"$K(pp \to \tilde{u}\tilde{u})$ ", size = font_size)
+plt.ylabel(r"$K_{\mathrm{MSSM}}(pp \to \tilde{u}\tilde{u})$ ", size = font_size)
 plt.xticks(fontsize = font_size)
 plt.yticks(fontsize = font_size)
 

### 2016-07-13 Appendix.tex
K factors in thesis

@@
 \subsection{Constants of the Color Algebra $SU(N)$}\label{sec:coloralgebra}
-[Marina von Steinkirch]\\
-Tha Casimir operator $C(R)\mathbbm{1}$ of a semi-simple Lie algebra in the irreducible representation $R$ is given by
+Tha Casimir operator $C(R)\mathbbm{1}$ of a semi-simple Lie algebra in the irreducible representation $R$ is given by\cite{Marina}
 \begin{align}
@@
 \end{align}
-where $T^a(R)$ is the $a$-th generator of the matrix valued representation $R$, $g^{ab}$ is the metric of group, $C(R)$ is the Quadratic Casimir invariant of the representation $R$ and $\mathbbm{1}$ is the identity in the representation space.\\
+where $T^a(R)$ is the $a$-th generator of the matrix valued representation $R$, $g^{ab}$ is the metric of the group, $C(R)$ is the quadratic Casimir invariant of the representation $R$ and $\mathbbm{1}$ is the identity in the representation space.\\
 Apart from $C(R)$ it is common to define the Dynkin-Index $T(R)$:
@@
 
-\subsection{Weyl Basis and 2-Spinor Notation}\label{sec:2spinor_notation}
+\subsection{Weyl Basis and Two-Spinor Notation}\label{sec:2spinor_notation}
 As representation of the $\gamma$-matrices the Weyl or chiral representation is chosen:
@@
 \begin{align}
-P_L = \frac{1}{2}(\mathbbm{1}_4 - \gamma_5)\begin{pmatrix}
+P_L = \frac{1}{2}(\mathbbm{1}_4 - \gamma_5) = \begin{pmatrix}
 \mathbbm{1}_2 && 0\\
@@
 \end{pmatrix} && 
-P_R = \frac{1}{2}(\mathbbm{1}_4 + \gamma_5)\begin{pmatrix}
+P_R = \frac{1}{2}(\mathbbm{1}_4 + \gamma_5) = \begin{pmatrix}
 0 && 0\\
@@
 \end{align}
-The representation of generators of the Lorentz group on 4-spinor space are composed of the above matrices.
-Because of the block form of those it is not surprising that the representation on 4-spinor space is reducible to two representations on 2-spinor (Weyl spinor) spaces.
-It is therefore sensible to decompose a 4 spinor into a left and a right handed Weyl spinor\footnote{The projectors in the chiral basis (eq.
+The representation of generators of the Lorentz group on four-spinor space is composed of the matrices above.
+Because of the block form of those it, is not surprising that the representation on four-spinor space is reducible to two representations on two-spinor (Weyl spinor) spaces.
+It is therefore sensible to decompose a four-spinor into a left and a right handed Weyl spinor\footnote{The projectors in the chiral basis (eq.
 \ref{eq:projectors}) explain the names left and right handed Weyl spinors.}
@@
 \end{align}
-where $\alpha,\dot{\alpha} \in \left\{ 1,2 \right\}$. Left handed Weyl spinors are labeled with undotted and right handed Weyl spinors with dotted indices. One distinguishes 4 different Weyl spinors:
+where $\alpha,\dot{\alpha} \in \left\{ 1,2 \right\}$.
+Left handed Weyl spinors are labeled with undotted and right handed Weyl spinors with dotted indices.
+One distinguishes four different Weyl spinors:
 \begin{align}
@@
 \end{align}
-By virtue of the antisymmetry of $\epsilon$ one finds the Lorentz invariant products:
+By virtue of the antisymmetry of $\epsilon^{\alpha \beta}$ one finds the Lorentz invariant products:
 \begin{align}
@@
 \end{align}
-To make the index structure of the Pauli matrices explicit one writes $\sigma^\mu_{\alpha\dot{\alpha}}$ and $\overline{\sigma}^{\mu\dot{\alpha}\alpha}$ for the formulae in \ref{eq:Pauli}.
-For the definition of the supersymmetry algebra in section \ref{sec:SUSYalgebra} the representation of the generators of the Lorentz group on the left and right handed Weyl spinor space are introduced:
+To make the index structure of the Pauli matrices explicit, one writes $\sigma^\mu_{\alpha\dot{\alpha}}$ and $\overline{\sigma}^{\mu\dot{\alpha}\alpha}$ for the formulae in \ref{eq:Pauli}.
+For the definition of the supersymmetry algebra in section \ref{sec:SUSYalgebra} the representation of the generators of the Lorentz group on the left and right handed Weyl spinor space is introduced:
 \begin{align}
@@
 
-With the definition of bared and charge conjugated 4-spinors\footnote{$\Psi^T$ denotes the transpose of the spinor $\Psi$ and $\Psi^\dagger$ is the Hermitian adjoint of $\Psi$.}
+With the definition of overlined and charge conjugated four-spinors\footnote{$\Psi^T$ denotes the transpose of the spinor $\Psi$ and $\Psi^\dagger$ is the Hermitian adjoint of $\Psi$.}
 \begin{align}
@@
 \subsection{Anticommuting Numbers}\label{sec:AnticommNumbers}
-Anticommuting numbers $\theta^\alpha$ are also referred to as Grassmann numbers and are defined by $\theta^\alpha\theta^\beta = -\theta^\beta\theta^\alpha$ and commute with ordinary numbers.\\
+Anticommuting numbers $\theta^\alpha$ are also referred to as Grassmann numbers and are defined by $\theta^\alpha\theta^\beta = -\theta^\beta\theta^\alpha$ and commute with ordinary c-numbers.\\
 They occur in superspace formalism in the form of 2 tuples, i.e. $\theta^\alpha$ with $\alpha=1,2$. The complex conjugate of this tuple is denoted with $\overline{\theta}^{\dot{\alpha}}$. 
@@
 \end{align}
-where the first line mirrows the claim of translation invariance. One furthermore introduces the shortcuts
+where the first line mirrors the claim of translation invariance. One furthermore introduces the shortcuts
 \begin{align}
@@
 \begin{align}
-\left\{ Q_\alpha, \mathcal{D}_\beta \right\} = \left\{ \overline{Q}_{\dot{\alpha}}, \mathcal{D}_\beta \right\} = \left\{ Q_\alpha, \mathcal{\mathcal{D}}_{\dot{\beta}} \right\} = \left\{ \overline{Q}_{\dot{\alpha}}, \mathcal{\mathcal{D}}_{\dot{\beta}} \right\} = 0
+\left\{ Q_\alpha, \mathcal{D}_\beta \right\} = \left\{ \overline{Q}_{\dot{\alpha}}, \mathcal{D}_\beta \right\} = \left\{ Q_\alpha, \mathcal{\mathcal{D}}_{\dot{\beta}} \right\} = \left\{ \overline{Q}_{\dot{\alpha}}, \mathcal{\mathcal{D}}_{\dot{\beta}} \right\} = 0.
 \end{align}
@@
 In addition the gluon-quark-squark vertex is different in RSQCD for the gauginos are Dirac fermions.
-Note that for calculations involving fermions one needs to go in the opposite direction of the fermion flow which is given by a curved arrow next to the diagrams in fig.
+Note that for calculations involving fermions one needs to multiply the Feynman rules in the opposite direction of the fermion flow which is given by a curved arrow next to the diagrams in fig.
 \ref{fig:secondFeynmanRules} and does not always agree with the flow of fermion number given by the direction of the Dirac propagator.
@@
 \begin{align}
-\frac{i}{16\pi^2} A_0(m^2) &= \int_l \frac{1}{l^2-m^2}\nonumber\\
-\frac{i}{16\pi^2} B_{0,\mu,\mu\nu}(p^2,m_1^2,m_2^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p)^2-m_2^2]}\\
+\frac{i}{16\pi^2} A_0(m^2) &= \int_l \frac{1}{l^2-m^2},\nonumber\\
+\frac{i}{16\pi^2} B_{0,\mu,\mu\nu}(p^2,m_1^2,m_2^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p)^2-m_2^2]},\\
 \frac{i}{16\pi^2} C_{0,\mu,\mu\nu}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p_1)^2-m_2^2][(l+p_1+p_2)^2-m_3^2]}.\nonumber\label{eq:LoopInt}
@@
 \begin{align}
-B_\mu &:= p_\mu B_1\nonumber\\
-B_{\mu\nu} &:= g_{\mu\nu}B_{00} + p_\mu p_\nu B_{11}\nonumber\\
-C_\mu &= p_{1\mu}C_1 + p_{2\mu}C_2\\
-C_{\mu\nu} &:= g_{\mu\nu}C_{00} + p_{1\mu}p_{1\nu}C_{11} + p_{2\mu}p_{2\nu}C_{22} + (p_{1\mu}p_{2\nu} + p_{2\mu}p_{1\nu})C_{12}\nonumber
+B_\mu &:= p_\mu B_1,\nonumber\\
+B_{\mu\nu} &:= g_{\mu\nu}B_{00} + p_\mu p_\nu B_{11},\nonumber\\
+C_\mu &= p_{1\mu}C_1 + p_{2\mu}C_2,\\
+C_{\mu\nu} &:= g_{\mu\nu}C_{00} + p_{1\mu}p_{1\nu}C_{11} + p_{2\mu}p_{2\nu}C_{22} + (p_{1\mu}p_{2\nu} + p_{2\mu}p_{1\nu})C_{12}.\nonumber
 \end{align}
-In the the special case of vanishing momenta the integrals take a succinct form. %The following formulae show some of these special cases.
+The $A$-integral reads
 \begin{align}
-A_0(m^2) = m^2\left( \Delta_\epsilon -\ln \frac{m^2}{\mu^2} + 1 \right) + \mathcal{O}(\epsilon)
+A_0(m^2) = m^2\left( \Delta_\epsilon -\ln \frac{m^2}{\mu^2} + 1 \right) + \mathcal{O}(\epsilon).
 \end{align}
-where the typical UV-divergent constant $\Delta_\epsilon = \frac{1}{\epsilon} - \gamma_E+\ln 4\pi$ is defined. It comprises the Euler-Mascheroni constant $\gamma_{\mathrm{E}}$.
+where the typical UV-divergent constant $\Delta_\epsilon = \frac{1}{\epsilon} - \gamma_E+\ln 4\pi$ is defined.
+It comprises the Euler-Mascheroni constant $\gamma_{\mathrm{E}}$.
+In the special case of vanishing momenta, the further integrals take a succinct form.
+Some formulae which are needed for the calculation of renormalization constants are
 \begin{align}
-B_0(0,m_1^2,m_2^2) &= \frac{A_0(m_1^2)-A_0(m_2^2)}{m_1^2-m_2^2} = \Delta_\epsilon + 1 -\frac{m_1^2\ln \frac{m_1^2}{\mu^2}-m_2^2\ln \frac{m_2^2}{\mu^2}}{m_1^2-m_2^2} + \mathcal{O}(\epsilon)\\
-B_0(0,m^2,m^2) &= \frac{\partial}{\partial m^2} A_0(m^2) = \Delta_\epsilon -\ln \frac{m^2}{\mu^2} + \mathcal{O}(\epsilon)\\
-B_0(0,0,0) &= 0\\
-B_1(0,m_1^2,m_2^2) &= -\frac{\Delta_\epsilon}{2} + \frac{1}{2}\ln \frac{m_1^2}{\mu^2} + \frac{-3+4t-t^2-4t \ln t +2t^2 \ln t}{4(t-1)^2} + \mathcal{O}(\epsilon)\label{eq:B1}\\
-B_1(0,0,0) &= 0
+B_0(0,m_1^2,m_2^2) &= \frac{A_0(m_1^2)-A_0(m_2^2)}{m_1^2-m_2^2} = \Delta_\epsilon + 1 -\frac{m_1^2\ln \frac{m_1^2}{\mu^2}-m_2^2\ln \frac{m_2^2}{\mu^2}}{m_1^2-m_2^2} + \mathcal{O}(\epsilon),\\
+B_0(0,m^2,m^2) &= \frac{\partial}{\partial m^2} A_0(m^2) = \Delta_\epsilon -\ln \frac{m^2}{\mu^2} + \mathcal{O}(\epsilon),\\
+B_0(0,0,0) &= 0,\\
+B_1(0,m_1^2,m_2^2) &= -\frac{\Delta_\epsilon}{2} + \frac{1}{2}\ln \frac{m_1^2}{\mu^2} + \frac{-3+4t-t^2-4t \ln t +2t^2 \ln t}{4(t-1)^2} + \mathcal{O}(\epsilon),\label{eq:B1}\\
+B_1(0,0,0) &= 0.
 \end{align}
-The scaleless integrals are defined to be zero due to their definition  on how they scale in $D$ dimensions\cite{Collins:105730}.
+The scaleless integrals equal to zero due to their definition on how they scale in $D$ dimensions\cite{Collins:105730}.
 The parameter $t$ is given by $\frac{m_2^2}{m_1^2}$.
-As can be seen from \ref{eq:B1} $B_1$ is in contrast to $B_0$ not symmetric in its masses but it can be shown [Romao] that
+As can be seen from \ref{eq:B1} $B_1$ is in contrast to $B_0$ not symmetric in its masses but it can be shown\cite{Romao} that
 \begin{align}
-B_1(p^2,m_1^2,m_2^2) = -(B_0(p^2,m_2^2,m_1^2) + B_1(p^2,m_2^2,m_1^2))
+B_1(p^2,m_1^2,m_2^2) = -(B_0(p^2,m_2^2,m_1^2) + B_1(p^2,m_2^2,m_1^2)).
 \end{align}
@@
 \end{align} 
-and Passarino-Veltman decomposition \cite{Passarino:1978jh} one can determine the UV-divergent part of all $B$ and $C$ integrals.
-In chapter \ref{sec:MSRen} this was necessary in order to obtain the renormalization constants in the $\overline{\mathrm{MS}}$-scheme.
-Infrared and collinear singularities arise from the special case where one or multiple masses tend to zero.
-These poles can be regularized with a small mass cutoff $\Lambda$ leading singularities of the form $\ln \Lambda$ or dimensionally which leads to $\epsilon$-poles as in the treatment of UV-divergences.
-In the latter case the integral first needs to undergo the limit to zero masses and than being evaluated.\\
-The following list shows all necessary integrals needed to determine the renormalization constants in \ref{sec:MSRen}.
+and Passarino-Veltman decomposition, \cite{Passarino:1978jh} one can determine the UV-divergent part of all $B$ and $C$ integrals.
+In chapter \ref{sec:MSRen} this is necessary in order to obtain the renormalization constants in the $\overline{\mathrm{MS}}$-scheme.
+Infrared and collinear singularities arise from the special case where one or multiple masses and momenta tend to zero.
+These poles can be regularized with a small mass cutoff $\Lambda$ leading to singularities of the form $\ln \Lambda$ or dimensionally which leads to $\epsilon$-poles as in the treatment of UV-divergences.
+In the latter case the integral first needs to undergo the limit to zero masses and evaluated afterwards.\\
+The following list shows all necessary integrals needed to determine the renormalization constants in \ref{sec:MSRen}:
 \begin{align}
-\left.A_0(m^2)\right|_{\mathrm{UV-div}} &= m^2 \Delta_\epsilon\\
-\left.B_0(p^2,m_1^2,m_2^2)\right|_{\mathrm{UV-div}} &= \Delta_\epsilon\\
-\left.B_1(p^2,m_1^2,m_2^2)\right|_{\mathrm{UV-div}} &= -\frac{1}{2}\Delta_\epsilon\\
-\left.C_{00}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2)\right|_{\mathrm{UV-div}} &= \frac{1}{4}\Delta_\epsilon
+\left.A_0(m^2)\right|_{\mathrm{UV-div}} &= m^2 \Delta_\epsilon,\\
+\left.B_0(p^2,m_1^2,m_2^2)\right|_{\mathrm{UV-div}} &= \Delta_\epsilon, \\
+\left.B_1(p^2,m_1^2,m_2^2)\right|_{\mathrm{UV-div}} &= -\frac{1}{2}\Delta_\epsilon,\\
+\left.C_{00}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2)\right|_{\mathrm{UV-div}} &= \frac{1}{4}\Delta_\epsilon.
 \end{align}
@@
 
-\subsection{Cross section and Phase Space Integration}\label{sec:cross_section}
+\subsection{Cross Section and Phase Space Integration}\label{sec:cross_section}
 Once the Feynman amplitude $\mathcal{M}$ for a $2 \to N$ body scattering\footnote{with kinematics $k_a + k_b \to p_1 + \hdots p_N$} is computed one can calculate physical observables with it.
@@
 where $K_{ab}$ encodes the averaging over initial state helicities and colors.
-Specifying to the center-of-mass frame and assuming that $\sum|\mathcal{M}|^2$ is only a function of the modulus of one of the final state particle's 3-momentum $ |\vec{p}_i|$ and the angle $\theta$ between $\vec{k}_a$ and $\vec{p}_1$ one can write
+Specifying to the center-of-mass frame and using that $\sum|\mathcal{M}|^2$ is only a function of the modulus of one of the final state particle's three-momentum $ |\vec{p}_i|$ and the angle $\theta$ between $\vec{k}_a$ and $\vec{p}_1$ one can write
 \begin{align}
@@
 \end{align}
-In the second line the integral over the D-dimensional hypersphere 
+In the second line the integral over the $D$-dimensional hypersphere 
 \begin{align}

### 2016-07-13 MSSM.tex
K factors in thesis

@@
 Supersymmetry provides a possible extension of the Standard Model.
-It constitutes a mathematically very aesthetic solution of the above mentioned problems\footnote{In its minimal extension to the Standard Model supersymmetry does not incorporate gravity but many quantum gravity models are supersymmetric}.
+It constitutes a mathematically very aesthetic solution of the above mentioned problems\footnote{In its minimal extension to the Standard Model supersymmetry does not incorporate gravity but many quantum gravity models are supersymmetric.}.
 This section explains briefly the mechanism of supersymmetry and the minimal supersymmetric extension of the Standard Model (MSSM).
@@
 \subsection{Supersymmetry as an Extention of the Poincaré Symmetry}\label{sec:SUSYalgebra}
-As already seen in the previous chapter symmetries are of vital importance when studying particle physics.
+As already seen in the previous chapter, symmetries are of vital importance when studying particle physics.
 Coleman and Mandula \cite{Coleman:1967ad} found that for any reasonable quantum field theory space-time and internal symmetries, i.e.
@@
 \end{align}
-As $J^{\mu\nu}$ is the generalized angular momentum operator the last line in eq.
+As $J^{\mu\nu}$ is the generalized angular momentum operator, the last line in eq.
 \eqref{eq:SUSYalgebra} implies that $Q_\alpha$ is a spin-$\frac{1}{2}$ operator.
@@
 A representation in the form of differential operators can be given by introducing superspace.
-Superspace is a manifold obtained by enlarging Minkowski space, whose coordinates are label with $x^\mu$, with four anticommuting numbers: $\theta^\alpha$ and $\overline{\theta}^{\dot{\alpha}}$, where $\alpha,\ \dot{\alpha} \in \left\{ 1,2 \right\}$ (see Appendix \ref{sec:AnticommNumbers} for the definition of anticommuting numbers).
+Superspace is a manifold obtained by enlarging Minkowski space, whose coordinates are labeled with $x^\mu$, with four anticommuting numbers: $\theta^\alpha$ and $\overline{\theta}^{\dot{\alpha}}$, where $\alpha,\ \dot{\alpha} \in \left\{ 1,2 \right\}$ (see Appendix \ref{sec:AnticommNumbers} for the definition of anticommuting numbers).
 A representation of the superalgebra reads
@@
 Superfields are functions on superspace.\\
-The superfields\footnote{Superfield are throughout this thesis labeled with a hat.} relevant for the MSSM are the chiral superfield $\hat{\Phi}$, the antichiral superfield $\hat{\overline{\Phi}}$ and the vector superfield $\hat{V}$.
+The superfields\footnote{Superfields are labeled with a hat throughout this thesis.} relevant for the MSSM are the chiral superfield $\hat{\Phi}$, the antichiral superfield $\hat{\overline{\Phi}}$ and the vector superfield $\hat{V}$.
 Chiral superfields are defined by the restriction $\overline{\mathcal{D}}_{\dot{\alpha}}\hat{\Phi} = 0$, antichiral superfields by $\mathcal{D}_\alpha\hat{\overline{\Phi}} = 0$ (see Appendix \ref{sec:AnticommNumbers} for the definition of chiral covariant derivatives) and vector superfields by the condition of being real $\hat{V}^\dagger = \hat{V}$.\\
-All superfields can be decomposed into component fields on Minkowski space. The component decomposition of the above fields read\footnote{For tho vector superfield Wess-Zumino-gauge is applied.}
+All superfields can be decomposed into component fields on Minkowski space. The component decomposition of the above fields read\footnote{For the vector superfield Wess-Zumino-gauge is applied.}
 \begin{align}
@@
 where $\hat{\Lambda} = \hat{\Lambda}^aT^a$ and $\hat{V} = \hat{V}^aT^a$.
-$\hat{\Lambda}^a$ is an arbitrary chiral superfield, the $T^a$ are the generetors of the gauge group in question and $g$ is the gauge coupling constant of the gauge group.\\
+$\hat{\Lambda}^a$ is an arbitrary chiral superfield, the $T^a$ are the generators of the gauge group in question and $g$ is the gauge coupling constant of the gauge group.\\
 One can therefore construct the important gauge invariant term $\int\mathrm{d}^4\theta\ \hat{\overline{\Phi}}\mathrm{e}^{2g\hat{V}}\hat{\Phi}$.
@@
 The superpartners of bosons have spin $\frac{1}{2}$ and get an additional ``-ino'' at the end of their name, e.g.
-higgsino as the superpartner of the Higgs or bino as superpartner of the $B$-boson.\\
+Higgsino as the superpartner of the Higgs or bino as superpartner of the $B$-boson.\\
 Apart from this doubling of the field content of the Standard Model, there is one modification within the Higgs sector, i.e.
@@
 The first two lines show the decomposition of the generic superfields (cf.
-subsection \eqref{eq:superfielddecomp}).\newline
-The third column shows the representation (for $SU(3)_C$ and $SU(2)_L$) in which the fields transform and in which the generator in the covariant derivative needs to be inserted as well as the charges of the fields for $U(1)_Y$.
+eq.
+\eqref{eq:superfielddecomp}).\newline
+The third column shows the representation in which the fields transform under  $SU(3)_C$ and $SU(2)_L$ transformations and in which the generator in the covariant derivative needs to be inserted as well as the charges of the fields for $U(1)_Y$.
 For $SU(3)_C$ the ``8'' refers to the adjoint representation (see Appendix \ref{sec:coloralgebra}), the ``3'' to the fundamental and the ``3$^\ast$'' to the antifundamental representation $T^a_{antifund} = -\frac{\lambda^a}{2}$.
@@
 Apart from the kinetic and minimal coupling terms in the first four lines of eq.
-\eqref{eq:L_MSSM} and the softly breaking part of the Lagrangian in the last line of eq.
+\eqref{eq:L_MSSM} and the soft breaking part of the Lagrangian in the last line of eq.
 \eqref{eq:L_MSSM} which will be discussed in section \ref{sec:SUSYBreaking}, there is a superpotential $W_{\mathrm{MSSM}}$:
@@
 After eliminating auxiliary fields the Higgs potential is generated.
-In contrast to the Standard Model the quadrilinear term in the Higgs potential is given in terms of the gauge couplings and therefore no independent parameter.
+In contrast to the Standard Model, the quadrilinear term in the Higgs potential is given in terms of the gauge couplings and is therefore no independent parameter.
 From the Higgs potential both $H_u$ and $H_d$ acquire a vacuum expectation value:
@@
 \eqref{eq:W_MSSM}) lead to masses of the fermions.\footnote{Note the sum convention of $SU_{\mathrm{L}}(2)$ doublets: $\hat{H}_u \hat{Q} =  (\hat{H}_u)_{\alpha}\hat{Q}_\beta \epsilon^{\alpha\beta}$ to ensure gauge invariance (see Appendix \ref{sec:2spinor_notation} for the definition of $\epsilon^{\alpha\beta}$).
-This convention was not used in the Standard Model.} Apart from that there are also other terms like quark-squark-higgsino interactions.
+This convention was not used in the Standard Model.} Apart from that there are also other terms like quark-squark-Higgsino interactions.
 In addition there is the $\mu$-term which is responsible for Higgsino and Higgs masses.\\
@@
 \end{align}
-The softly breaking terms in the MSSM comprise masses of the squarks, sleptons, Higgs-bosons and gauginos.
+The soft breaking terms in the MSSM comprise masses of the squarks, sleptons, Higgs-bosons and gauginos.
 The last line in eq.
@@
 There are fields in the MSSM which are no eigenstate of the mass operator $P^\mu P_\mu$ but have a mass matrix which is non-diagonal.
-This is true for neutral higgsinos and gauginos which mix to neutralinos and charged higgsinos and gauginos which mix to charginos to yield physical particles with definite mass.
+This is true for neutral Higgsinos and gauginos which mix to neutralinos and charged Higgsinos and gauginos which mix to charginos to yield physical particles with definite mass.
 However, for this thesis only the mass matrix for electrically charged sfermions is given because this will change significantly when introducing $R$-symmetry in the next section.
@@
 \end{align}
-The diagonal terms are given by the sum of the fermion mass squared $m_f^2$, the appropriate soft breaking term, e.g.
-$M_{\tilde{Q}}^2$ for left handed squarks and a contribution from the elimination of $D$-fields.
-In fact this last term splits the masses of fermions and sfermions already without explicit supersymmetry breaking.
+The diagonal terms are given by the sum of the fermion mass squared $m_f^2$, the appropriate soft breaking term (e.g.
+$M_{\tilde{Q}}^2$ for left handed squarks) and a contribution from the elimination of $D$-fields.
+In fact, this last term splits the masses of fermions and sfermions already without explicit supersymmetry breaking.
 This is because the generation of fermion masses requires the breaking of gauge symmetry which is not possible without breaking supersymmetry.
@@
 \end{align}
-with $\cot \beta$ for up-type squarks and $\tan \beta$ for down-type sfermions and $A_f \in \left\{ A_d, A_u, A_e \right\}$.
+with $\cot \beta$ for up-type sfermions and $\tan \beta$ for down-type sfermions and $A_f \in \left\{ A_d, A_u, A_e \right\}$.
 

### 2016-07-13 NLO.tex
K factors in thesis

@@
 All three contributions have to be calculated with next-to-leading order parton density functions and $\alpha_s$.
-There are five mass scales: the squark mass $m_{\tilde{q}}$, the gluino mass $m_{\tilde{g}}$, the center of mass energy of the colliding protons $\sqrt{S}$, the top-quark mass which is fixed to $m_t = \unit[172]{GeV}$ and the mass of the pseudoscalar $m_{\sigma}$.
+There are seven mass scales: the squark mass $m_{\tilde{q}}$, the gluino mass $m_{\tilde{g}}$, the center of mass energy of the colliding protons which is set to $\sqrt{S} = \unit[13]{TeV}$, the top-quark mass which is fixed to $m_t = \unit[172]{GeV}$, the mass of the pseudoscalar $m_{\sigma}$ and the renormalization and factorization scale.
+They have been set to $\mu_F = \mu_R = m_{\tilde{q}}$.
 The next section summaries how the calculation has been automated within a \texttt{C++} program.
@@
 
-\subsubsection{Remark on Prefactors in the Calculation}
+\subsubsection{Remark on Prefactors in the Calculation}\label{sec:prefactors}
 For the discussion of results it will not been distinguished between virtual and real corrections.
@@
 \includegraphics[scale=.4]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV.png}
-\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).
-The other parameters are $\sqrt{S} = \unit[13]{TeV}$, $m_{\tilde{\sigma}} = \unit[5000]{GeV}$ and $\mu_R = \mu_F = m_{\tilde{q}}$.
+\caption{Dependence of the $K$-factor for the process $pp \to \tilde{u}_L\tilde{u}_R$ in the MRSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).
+The mass of the pseudoscalar is $m_{\sigma} = \unit[5000]{GeV}$.
 The used parton density function are the one from table \ref{tab:MRSSMKfactors}.
@@
 \caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$  in the MRSSM for a selected set of masses.
-The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$ and the pseudoscalar mass is fixed to \mbox{$m_{\mathrm{\sigma}} = \unit[5000]{GeV}$}.
-For $\sigma^{\mathrm{LO}}$ parton density functions \texttt{MMHT2014}(LHAPDF ID: $25000$) has been used, whereas for $\sigma^{\mathrm{NLO}}$ \texttt{MMHT2014}(LHAPDF ID: $25100$) was used.}\label{tab:MRSSMKfactors}
+The pseudoscalar mass is fixed to \mbox{$m_{\mathrm{\sigma}} = \unit[5000]{GeV}$}.
+For $\sigma^{\mathrm{LO}}$ parton density functions \texttt{MMHT2014LO} (LHAPDF ID: $25000$) is used, whereas for $\sigma^{\mathrm{NLO}}$ \texttt{MMHT2014NLO} (LHAPDF ID: $25100$) is used.}\label{tab:MRSSMKfactors}
 \end{center}
 \end{table}
-It can be seen that the $K$-factors depend strongly on the ratio $\frac{m_{\tilde{g}}}{m_{\tilde{q}}}$ but not that strongly on the masses itself.\\
+It can be seen that the $K$-factors depend strongly on the ratio $\frac{m_{\tilde{q}}}{m_{\tilde{g}}}$ but not that strongly on the masses itself.
+This is also depicted in fig.
+\ref{fig:Kfactor_MRSSM} which shows the $K$-factors in the $m_{\tilde{q}}$-$m_{\tilde{g}}$ plane.
+The contour lines follow approximately rays from the origin.
+By performing the calculation without the shuffling of prefactors as explained in section \ref{sec:prefactors}, the raising of the $K$-factors for increasing values of $\frac{m_{\tilde{q}}}{m_{\tilde{g}}}$ has been traced down to the real corrections.
+As quark radiation is not included, this effect can further be pinned down to originate from the diagrams in fig.
+\ref{fig:RealGluon}.
+However, at least for small $m_{\tilde{g}}$, fig.
+\ref{fig:Kfactor_MRSSM} suggests that the $K$-factors drop again for increasing $m_{\tilde{q}}$.
+\begin{figure}[H]
+\begin{center}
+\includegraphics[scale=.6]{figures/Kfactor_MRSSM.png}
+\caption{Contour plot of the $K$-factor of up-squark production in the MRSSM.
+The pseudoscalar mass is set to $m_{\sigma} = \unit[5000]{GeV}$.
+The used parton density functions are the same as in table \ref{tab:MRSSMKfactors}.}\label{fig:Kfactor_MRSSM}
+\end{center}
+\end{figure}
 For three different choices of $m_{\tilde{q}}$ and $m_{\tilde{g}}$, Philip Dießner checked the results up to permille accuracy by doing the calculation using \texttt{GoSam}\cite{Cullen:2014yla, Cullen:2011ac} and \texttt{MadGraph5\_aMC@NLO}\cite{Alwall:2014hca} on the basis of the same model file.\\
@@
 \begin{center}
-\includegraphics[scale=.47]{figures/MSSM_uu_susu_Kfactors_msg=2000GeV.png}
-\includegraphics[scale=.47]{figures/MSSM_uu_susu_Kfactors_msq=1000GeV.png}
+\includegraphics[scale=.46]{figures/MSSM_uu_susu_Kfactors_msg=2000GeV.png}
+\includegraphics[scale=.46]{figures/MSSM_uu_susu_Kfactors_msq=1000GeV.png}
 \caption{Dependence of the $K$-factor for the process $pp \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).
-The parameters are chosen like in fig.
-\ref{fig:1LXsection_fixed_m_MRSSM}.The $K$-factors have been broken down to contributions coming from $pp \to \tilde{u}_L\tilde{u}_R$ and from $pp \to \tilde{u}_L\tilde{u}_L$.
+The used parton density functions are the same as in table \ref{tab:MRSSMKfactors}.
+The $K$-factors have been broken down to contributions coming from $pp \to \tilde{u}_L\tilde{u}_R$ and from $pp \to \tilde{u}_L\tilde{u}_L$.
 The latter equals the contributions coming from $pp \to \tilde{u}_R\tilde{u}_R$.
@@
 \caption{$\sigma^{\mathrm{NLO}}(pp \to \tilde{u}_L\tilde{u}_R)$ in the MSSM obtained from \texttt{MadGraph5} and \texttt{Prospino2} for a selected set of masses.
-The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$.
+\texttt{MadGraph5} uses parton density function given in \ref{tab:MRSSMKfactors} whereas \texttt{Prospino2} uses \texttt{CTEQ6L1} parton density functions\cite{Pumplin:2002vw} for leading order calculations and \texttt{CTEQ66}\cite{Nadolsky:2008zw} for next-to-leading order calculations.
 The stated uncertainties originate from the phase space integration.
@@
 \end{tabular}
-\caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$ and $pp \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM for a selected set of masses.
-The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$.}\label{tab:KfactorsMSSM}
+\caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$ and $pp \to \tilde{u}\tilde{u}$, where \mbox{$\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$,} in the MSSM for a selected set of masses.
+The used parton density functions are the same as in table \ref{tab:MRSSMKfactors}.}\label{tab:KfactorsMSSM}
 \end{center}
 \end{table}
-
-Again, it is clearly visible that the $K$-factors depend rather strongly on the ratio $\frac{m_{\mathrm{g}}}{m_{\mathrm{q}}}$ but not so much on the masses itself.
+\begin{figure}[H]
+\begin{center}
+\includegraphics[scale=.6]{figures/Kfactor_MSSM.png}
+\caption{Contour plot of the $K$-factor of the process  $pp \to \tilde{u}_L\tilde{u}_R$ and $pp \to \tilde{u}\tilde{u}$, where \mbox{$\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$,} in the MSSM.
+The used parton density functions are the same as in table \ref{tab:MRSSMKfactors}.}\label{fig:Kfactor_MSSM}
+\end{center}
+\end{figure}
+Again, it is clearly visible that the $K$-factors depend rather strongly on the ratio $\frac{m_{\mathrm{g}}}{m_{\mathrm{q}}}$ but not so much on the masses itself (see also fig.
+\ref{fig:Kfactor_MSSM}).
+As the real corrections are identical to those in the MRSSM, it is again these very real corrections which are responsible for an enhancement of the $K$-factor for large values of  $\frac{m_{\mathrm{g}}}{m_{\mathrm{q}}}$.
 Comparing with the results from the MRSSM in table \ref{tab:MRSSMKfactors}, one can state that the $K$-factors of the MRSSM are slightly larger.
@@
 \subsection{The Cross Section in the Limit of Large Sgluon Masses}
+\begin{figure}[H]
+\begin{center}
+\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV_msg=2000GeV.png}
+\caption{Dependence of the $K$-factor for the process $pp \to \tilde{u}\tilde{u}$ on the mass of the pseudoscalar sgluon.
+Squark and gluino mass have been fixed to $m_{\tilde{q}} = \unit[1000]{GeV}$ and $m_{\tilde{g}} = \unit[2000]{GeV}$ .
+The used parton density functions are the same as in table \ref{tab:MRSSMKfactors}.
+For $m_{\sigma} \approx \unit[10^5]{GeV}$ onwards, one finds a logarithmic scaling as predicted by \cite{Cheng:1997sq}.}\label{fig:SgluonMassDependence}
+\end{center}
+\end{figure}
 The cross section for squark production does not exist in the limit of an infinitely large sgluon mass, instead it was found that it diverges logarithmically:
@@
 \end{align}
-
-\begin{figure}[H]
-\begin{center}
-\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV_msg=2000GeV.png}
-\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$ on the mass of the pseudoscalar sgluon.
-For $m_{\sigma} \approx \unit[10^5]{GeV}$ onwards want find a logarithmic scaling as predicted by \cite{Cheng:1997sq}.}\label{fig:SgluonMassDependence}
-\end{center}
-\end{figure}
 This is actually expected as an effective field theory of the MRSSM where the sgluon is integrated out is no longer supersymmetric.

### 2016-07-13 RSymmetry.tex
K factors in thesis

@@
 If one inserts the component decomposition eq.
-\eqref{eq:superfielddecomp} of the superfields one can read off the $R$-charges of the component fields.
+\eqref{eq:superfielddecomp} of the superfields one can read off the $R$-charges of the component fields, see table \ref{tab:Rcharges}.
 \begin{table}
@@
 \end{tabular}
-\caption{This table shows the R-charges of a generic chiral and vector superfield.}
+\caption{This table shows the R-charges of a generic chiral and vector superfield.}\label{tab:Rcharges}
 \end{center}
@@
 \caption{This table lists the $R$-charges of all superfields and their components in the MRSSM.
-The fields of the $R$-Higgs and the adjoint chiral superfields are not present in the MSSM}\label{tab:R_charges_MRSSM}
+The fields of the $R$-Higgs and the adjoint chiral superfields are not present in the MSSM.}\label{tab:R_charges_MRSSM}
 \end{center}
@@
 The gauge, matter and $H$-Higgs fields are the fields of the MSSM.
-Below the horizontal line one finds the fields which are not present in the MSSM, i.e.
+Below the thin horizontal line, one finds the fields which are not present in the MSSM, i.e.
 the $R$-Higgs and adjoint chiral fields.
@@
 \end{align}
-where $\chi$ is another Weyl-spinor. This means that the 4-spinor of every gaugino is a Dirac- instead of a Majorana-spinor, e.g. for the gluino:
+where $\chi$ is another Weyl-spinor. This means that the four-spinor of every gaugino is a Dirac- instead of a Majorana-spinor, e.g. for the gluino:
 \begin{align}
@@
 the additional Weyl fermion comes from a chiral superfield.
-In order to maintain gauge invariance this chiral superfield has to transform in the adjoint representation, hence the name adjoint chiral in table \ref{tab:R_charges_MRSSM}.
+In order to maintain gauge invariance, this chiral superfield has to transform in the adjoint representation, hence the name adjoint chiral in table \ref{tab:R_charges_MRSSM}.
 To fix notation the component decomposition of the eight chiral supermultiplets assosiated to the gluons is given by
@@
 It is this last feature which is going to be observed further in this thesis.
-To this end the colored sector of the MRSSM in now considered in more detail.
+To this end the colored sector of the MRSSM is now considered in more detail.
 
@@
 \end{align}
-where $D^a$ is still real as the purely imaginary parts to not contribute by virtue of the antisymmetry of the structure constants.
-After eliminating the auxiliary fields the complete Lagrangian reads in 4 spinor notation\footnote{How a 4 spinor is composed of Weyl-spinors is given in the Appendix \ref{sec:2spinor_notation}}
+where $D^a$ is still real as the purely imaginary parts do not contribute by virtue of the antisymmetry of the structure constants.
+After eliminating the auxiliary fields the complete Lagrangian reads in four.spinor notation\footnote{How a four-spinor is composed of Weyl-spinors is given in the Appendix \ref{sec:2spinor_notation}.}
 \begin{align}

### 2016-07-13 Renormalization.tex
K factors in thesis

@@
 Final state helicities and colors are averaged.
-The parameters are fixed to $m_{\tilde{q}} = \mu_R = \unit[1000]{GeV}$, $m_{\tilde{g}} = \unit[2000]{GeV}$, $m_{\sigma} = \unit[5000]{GeV}$ and $\sqrt{s} = \unit[6000]{GeV}$ which is the partonic center-of-mass energy.}\label{fig:MatrixElementPoles}
+The parameters are fixed to \mbox{$m_{\tilde{q}} = \mu_R = \unit[1000]{GeV}$,} $m_{\tilde{g}} = \unit[2000]{GeV}$, $m_{\sigma} = \unit[5000]{GeV}$ and $\sqrt{s} = \unit[6000]{GeV}$ which is the partonic center-of-mass energy.}\label{fig:MatrixElementPoles}
 \end{center}
@@
 \includegraphics[scale=.5]{figures/MatrixElement.png}
-\caption{The figure at the bottom shows the absolute squared matrix element of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM at tree-level with $\alpha_s = 0.135$ from the leading order parton density function $\mathtt{MMHT2014}$\cite{Harland-Lang:2014zoa}, and $\alpha_s = 0.12$ from the next-to-leading order parton density function as well as the contribution from the virtual absolute squared matrix element.\newline
-The figure at the top shows the different contributions and their sum to the virtual corrections. The used parameters are given under fig. \ref{fig:MatrixElementPoles}.}\label{fig:MatrixElement}
+\caption{The figure at the bottom shows the absolute squared matrix element of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM at tree-level with $\alpha_s(m_Z) = 0.135$ from the leading order parton density functions $\mathtt{MMHT2014}$, and $\alpha_s(m_Z) = 0.12$ from the next-to-leading order parton density function as well as the contribution from the virtual corrections to it.\newline
+The figure at the top shows the different contributions to the virtual corrections as well as their sum.
+The used parameters are given under fig.
+\ref{fig:MatrixElementPoles}.}\label{fig:MatrixElement}
 \end{center}

### 2016-07-13 Standardmodel.tex
K factors in thesis

@@
 In the Standard Model different matter particles take part in different interactions, i.e. their corresponding spinor couples to different gauge vectors.\\
-If a spinor couples to a certain gauge vector, it transforms  non-trivially (like indicated in table \ref{tab:SM_transformations}) under the gauge group which is associated with this gauge vector.\footnote{In the Standard Model all matter particles transform in the fundamental (or trivial) representation of gauge groups.} This means if a particle couples to a certain force its charge which is associated with this force is non-zero.\\
+If a spinor couples to a certain gauge vector, it transforms  non-trivially under the gauge group which is associated with this gauge vector.\footnote{In the Standard Model all matter particles transform in the fundamental (or trivial) representation of gauge groups.} This means if a particle couples to a certain force, its charge associated with it is non-zero.\\
 The charges of a particle related to a force are defined as the eigenvalues of the generators which correspond to the force.
@@
 As for the quarks only the left handed components interact weakly and there are six leptons which are classified into three generations (see table \ref{tab:generations}).
-In each generation is a lepton with a negative electrical charged and an electrically neutral lepton.
+In each generation is a lepton with a negative electrical charge and an electrically neutral lepton.
 The latter ones are referred to as neutrinos.
@@
 The former are called electron, muon and tau.
-Each left handed leptons with an electric charge is assembled with its neutrino in a doublet.
+Each left handed lepton with a negative electric charge is assembled with its neutrino in a doublet.
 \begin{table}[H]
@@
 Quarks and leptons are the matter particles of the Standard Model.
-They are listed together with their charges for the different forces in table \ref{tab:SMfieldcontent}.
-There is the color for strong interactions, the third component of the weak isospin $I_3$ for weak interactions (the eigenvalue of the third generator of the $SU(2)_L$) and the half of the hypercharge $\frac{Y}{2}$ to obtain the electric charge $Q$ via the Gell-Mann–Nishijima formula: $Q = I_3 + \frac{Y}{2}$.\\
+They are listed in table \ref{tab:SMfieldcontent} including their charges for the different forces.
+Those are the color for strong interactions, the third component of the weak isospin $I_3$ for weak interactions (the eigenvalue of the third generator of the $SU(2)_L$) and the half of the hypercharge $\frac{Y}{2}$ to obtain the electric charge $Q$ via the Gell-Mann–Nishijima formula: $Q = I_3 + \frac{Y}{2}$.\\
 Because the left- and right-handed parts of spinors transform differently under the $SU_L(2)$ they are listed separately. All quarks occur with three different colors.\\
@@
 \end{tabular}
-\caption{The gauge fields and their coupling constants before and after electro weak symmetry breaking (EWSB).
+\caption{The gauge fields and their coupling constants before and after electro weak symmetry breaking (EWSB), see section \ref{sec:EWSB}.
 The Gluon field is not affected by EWSB.
@@
 This mixing procedure is explained in section \ref{sec:EWSB}.\\
-For the moment being the coupling constants and gauge fields before and after this mixing are quoted in table \ref{tab:force_particles}.\bigbreak
+For the moment being, the coupling constants and gauge fields before and after this mixing are quoted in table \ref{tab:force_particles}.\bigbreak
 The Lagrangian of the SM is built up by qualitatively different terms. Firstly there are the kinetic and minimal coupling terms of the matter fields 
@@
 \end{align}
-The ghost Lagrangian corresponding to the electroweak sector is not needed within this thesis and due to its lengthy form not quoted here. It can found in \cite{book:811554}. %[S622]
+The ghost Lagrangian corresponding to the electroweak sector is not needed within this thesis and due to its lengthy form not quoted here. It can be found in \cite{book:811554}. %[S622]
 In eq.

### 2016-07-13 Summary.tex
K factors in thesis

@@
 The results are shown for a selected set of masses.
-The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$ and within the MRSSM the pseudoscalar mass is fixed to $m_{\mathrm{\sigma}} = \unit[5000]{GeV}$.}\label{tab:MRSSMKfactors}
+The center-of-mass energy is $\sqrt{S} = \unit[13]{TeV}$ and within the MRSSM the pseudoscalar mass is fixed to $m_{\mathrm{\sigma}} = \unit[5000]{GeV}$.}\label{tab:Kfactors}
 \end{center}

### 2016-07-13 TreeLevel.tex
some changes
K factors in thesis

@@
 \section{Squark and Gluino Production at Tree Level}\label{sec:SquarkGluinoTree}
-This chapter considers the production of strongly interacting supersymmetric particles in the MRSSM\footnote{In fact only the RSQCD is considered as contribution coming from the electroweak sector scale with $\alpha_w = \frac{g_w^2}{4\pi}$ or $\alpha_{\mathrm{em}} = \frac{e^2}{4\pi}$ and are therefore significantly smaller than contribution from the strongly interacting sector which scale with $\alpha_s = \frac{g_s^2}{4\pi}$.} The various processes and their associated cross section are compared to their analogues in the MSSM.\\
+This chapter considers the production of strongly interacting supersymmetric particles in the MRSSM.\footnote{In fact only the RSQCD is considered as contribution coming from the electroweak sector scale with $\mathcal{O(\alpha_w^2)}$ where $\alpha_w = \frac{g_w^2}{4\pi}$ or $\mathcal{O(\alpha_em^2)}$ where $\alpha_{\mathrm{em}} = \frac{e^2}{4\pi}$ and are therefore significantly smaller than contribution from the strongly interacting sector which scale with $\mathcal{O(\alpha_s^2)}$ where $\alpha_s = \frac{g_s^2}{4\pi}$.} The various processes and their associated cross sections are compared to their analogues in the MSSM.\\
 The production of sgluons is not included in the following analysis.
@@
 soft breaking parameter $m_\sigma = \unit[5]{TeV}$, is considered.
-This validates the negligence of sgluon production as in this case they are too heavy to significantly produce them at the LHC with $\sqrt{S} = \unit[13]{TeV}$.
+This validates the negligence of sgluon production as in this case they are too heavy to produce them significantly at the LHC with $\sqrt{S} = \unit[13]{TeV}$.
 See \cite{Choi:2008ub, GoncalvesNetto:2012nt, phdWojciech} for a calculation of the sgluon production cross section.
-\ignore{Feynman diagrams there are only ones, one can only produce sigma,sigma or phi,phi but not sigma,phi}
-Section \ref{sec:PartProcesses} gives analytic results for the parton reaction before the next section describes how the hadronic cross section is obtained.
+\ignore{Feynman diagrams there are only ones, one can only produce sigma,sigma or phi,phi but not sigma,phi}Section \ref{sec:PartProcesses} gives analytic results for the parton reaction before the next section describes how the hadronic cross section is obtained.
 Section \ref{sec:tree-level_cross_sections} presents the hadronic cross section of all considered processes for various choices of squark and gluino mass.
-In particular, squark production is considered more closely.
+In particular, squark production is considered in detail.
 This includes the statement of uncertainties of the calculation.
@@
 The processes $GG \to \tilde{q}\overline{\tilde{q}}$ and $qG \to \tilde{q}\tilde{g}$ are identical to those in the MSSM.
-The processes $q\overline{q} \to \tilde{q}\overline{\tilde{q}}$ and $qq \to \tilde{q}\tilde{q}$ involve the production of less chiralities than in the MSSM.
-Also in the $q\tilde{q} \to \tilde{g}\overline{\tilde{g}}$ channel only half of the t-channel squark chiralities occur in the MRSSM.
+The processes $q\overline{q} \to \tilde{q}\overline{\tilde{q}}$ and $qq \to \tilde{q}\tilde{q}$ involve the production of less ``chiralities'' than in the MSSM.
+Also in the $q\tilde{q} \to \tilde{g}\overline{\tilde{g}}$ channel only half of the t-channel squark ``chiralities'' occur in the MRSSM.
 (Anti-)Gluino production via initial gluons $GG \to \tilde{g}\overline{\tilde{g}}$ proceeds via the same diagrams like in the MSSM but its cross section is twice as much in the MRSSM for gluino and antigluino are distinguishable particles.}\label{fig:TreeDiagrams}
@@
 \end{figure}
+The tree-level Feynman diagrams for squark and gluino production in the MRSSM are shown in fig.
+\ref{fig:TreeDiagrams}.
+On the partonic level there are six different channels.
+For squark-antisquark  and gluino-antigluino production there are two possible partonic reactions respectively.\\
 For the following calculation the top quark is excluded from the initial state as it is too heavy to be significantly present in protons. %Therefore its pdf is approximately zero. 
@@
 One therefore deals with $n_f-1 = 5$ quark flavors.
-In view of the renormalization and mass factorization to be performed at the 1-loop level, the results are calculated in (conventional) dimensional regularization (see section \ref{sec:RegSchemes}) and are therefore given in $D = 4 - 2\epsilon$ dimensions.
+In view of the renormalization and mass factorization to be performed at the one-loop level, the results are calculated in (conventional) dimensional regularization (see section \ref{sec:RegSchemes}) and are therefore given in $D = 4 - 2\epsilon$ dimensions.
 Furthermore it has been distinguished between the gauge coupling $g_s$ from the gluon-quark-quark vertex and its supersymmetric analogue $\hat{g}_s$ from the gluino-squark-quark vertex.
@@
 However, the loop corrections to their corresponding vertex differ in dimensional regularization by a finite amount, as will be shown in section \ref{sec:renMRSSM}.
-To rectify this, an additional finite (supersymmetry restoring) counterterm needs to be added to one of renormalization constants of $g_s$ or $\hat{g}_s$.
+To rectify this, an additional finite (supersymmetry restoring) counterterm needs to be added to one of the renormalization constants of $g_s$ or $\hat{g}_s$.
 This will be done in \ref{sec:SUSYrestore}.\\
@@
 \sum|\mathcal{M}^B|^2(q\overline{q} \to \tilde{g}\overline{\tilde{g}}) &=  8 N_c^2 C(F) g_s^4 \left[ \frac{2m_{\tilde{g}}^2 s + t_{\tilde{g}}^2 + u_{\tilde{g}}^2}{s^2} -\epsilon \right]\nonumber\\
-& + 4 N_c^2 C(F) g_s^2 \hat{g}_s^2 \left[ \frac{m_{\tilde{g}}^2 s + t_{\tilde{g}}^2}{s t_{\tilde{q}}} + \frac{m_{\tilde{g}}^2 s + u_{\tilde{g}}^2}{su_{\tilde{q}}} + \epsilon\left( \frac{t_{\tilde{g}}}{t_{\tilde{q}}} + \frac{u_{\tilde{g}}}{u_{\tilde{q}}} \right) \right]\nonumber\\
+& + 4 N_c^2 C(F) g_s^2 \hat{g}_s^2 \left[ \frac{m_{\tilde{g}}^2 s + t_{\tilde{g}}^2}{s t_{\tilde{q}}} + \frac{m_{\tilde{g}}^2 s + u_{\tilde{g}}^2}{su_{\tilde{q}}} + \epsilon\left( \frac{t_{\tilde{g}}}{t_{\tilde{q}}} + \frac{u_{\tilde{g}}}{u_{\tilde{q}}} \right) \right], \nonumber\\
 & + 2C(F)(N_c^2-1) \hat{g}^4_s \left( \frac{t_{\tilde{g}}^2}{t_{\tilde{q}}^2} + \frac{u_{\tilde{g}}^2}{u_{\tilde{q}}^2} \right)\\
@@
 \end{align}
-The absolute squared amplitudes have been checked with the mathematica output generated by the packages  \texttt{FeynArts} \cite{Hahn:2000} and \texttt{FormCalc} \cite{ChokoufeNejad:2013qja, Hahn:1998yk} which used a model file for the MRSSM generated by \texttt{SARAH}\cite{Staub:2013tta, Staub:2012pb, Staub:2010jh, Staub:2009bi}.\\
+The constants $C(A)$, $C(F)$ of the color algebra $SU(N_c)$ with $N_c = 3$ are given in Appendix \ref{sec:coloralgebra}.\\
+The absolute squared amplitudes have been checked with the \texttt{Mathematica} output generated by the packages  \texttt{FeynArts} \cite{Hahn:2000} and \texttt{FormCalc} \cite{ChokoufeNejad:2013qja, Hahn:1998yk} which used a model file for the MRSSM generated by \texttt{SARAH}\cite{Staub:2013tta, Staub:2012pb, Staub:2010jh, Staub:2009bi}.\\
 Having calculated the absolute squared Feynman amplitudes one obtains the partonic cross sections (see Appendix \ref{sec:cross_section}) via
@@
 
-\subsubsection*{The process $q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger$}
-The production of a squark and an antisquark through a quark and an antiquark in the initial state originates from two types of Feynman diagrams.
+\subsubsection*{The Process $q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger$}
+The production of a squark and an antisquark through a quark and an antiquark in the initial state originates from two types of Feynman diagrams, see fig.
+\ref{fig:squarkantisquark}.
 The first one has an $s$-channel gluon and is the same in the MSSM and in the MRSSM.
@@
 \end{tikzpicture}
-\caption{Tree level diagrams for $q\overline{q} \to \tilde{q}\tilde{q}^\dagger$}
+\caption{Tree level diagrams for $q\overline{q} \to \tilde{q}\tilde{q}^\dagger$}\label{fig:squarkantisquark}
 \end{center}
@@
 Consequently contributions from the $t$-channel diagrams are suppressed in the MRSSM in comparison to the MSSM.
-As visible in fig.
+As shown in fig.
 \ref{fig:TreeXsection} this suppression grows with the masses.
@@
 
-\subsubsection*{The process $GG \to \tilde{q}\tilde{q}^\dagger$}
-This process has the same cross section as in the MSSM for also in the MSSM only like chirality squark and antisquark $\tilde{q}_A\tilde{q}_A^\dagger$ with $A \in \left\{L,R\right\}$ can be produced.
+\subsubsection*{The Process $GG \to \tilde{q}\tilde{q}^\dagger$}
+This process has the same cross section as in the MSSM for also in the MSSM only ``chirality'' like squark and antisquark $\tilde{q}_A\tilde{q}_A^\dagger$ with $A \in \left\{L,R\right\}$ can be produced.
 
-\subsubsection*{The process $q_i q_j \to \tilde{q}\tilde{q}$}
-In the MRSSM only the production of unlike chirality squarks $\tilde{q}_L \tilde{q}_R$ is allowed whilst in the MSSM also like chirality squarks can be produced.
+\subsubsection*{The Process $q_i q_j \to \tilde{q}\tilde{q}$}
+In the MRSSM only the production of ``chirality'' unlike squarks $\tilde{q}_L \tilde{q}_R$ is allowed whilst in the MSSM also ``chirality'' like squarks can be produced.
 This is again a consequence of the conservation of R-charge.
@@
 Therefore for small momenta of the gluino compared to the gluino mass one gets $\mathcal{M}$ $\sim m_{\tilde{g}}^{-2}$ in the MRSSM while in the MSSM one finds a suppression proportional to $m_{\tilde{g}}^{-1}$.\\
-When considering squark production, one has to sum over all $|\mathcal{M}|^2$ with different helicity.
+When considering squark production, one has to sum $|\mathcal{M}|^2$ over all helicities.
 The diagrams for those different final state helicities are shown for flavor like squark production in tab.
@@
 \ref{tab:squark_unlikeflavor} for the MSSM and the MRSSM.
-To avoid double counting one needs to weight $|\mathcal{M}|^2(qq\to \tilde{q}_L\tilde{q}_L)$ and $|\mathcal{M}|^2(qq\to \tilde{q}_R\tilde{q}_R)$ with a statistical factor of $\frac{1}{2}$ as one integrates over the momenta of both particles in $t$- and $u$-channel diagram to arrive at the cross section.
+To avoid double counting, one needs to weight $|\mathcal{M}|^2(qq\to \tilde{q}_L\tilde{q}_L)$ and $|\mathcal{M}|^2(qq\to \tilde{q}_R\tilde{q}_R)$ with a statistical factor of $\frac{1}{2}$ as one integrates over the momenta of both particles in $t$- and $u$-channel diagrams to arrive at the cross section.
 \begin{table}[!htpb]
@@
 \caption{All Feynman diagrams contributing to flavor like squark production in the MSSM and the MRSSM for the example of $u$-quarks.
-For the MSSM the absolute squared Feynman amplitudes from the diagrams with chirality like squarks need to be weighted with a factor of $\frac{1}{2}$.}\label{tab:squark_likeflavor}
+For the MSSM the absolute squared Feynman amplitudes from the diagrams with ``chirality'' like squarks need to be weighted with a factor of $\frac{1}{2}$.}\label{tab:squark_likeflavor}
 \end{center}
@@
 \end{table}\\
-Because of the absence of chirality like squarks in the final state in the MRSSM (and a missing interference of the two diagrams in tab.
+Because of the absence of ``chirality'' like squarks in the final state in the MRSSM (and a missing interference of the two diagrams in tab.
 \ref{tab:squark_likeflavor} in the column of the MRSSM), the partonic cross section of flavor like and unlike squarks is the same in the MRSSM, i.e.
@@
 
-\subsubsection*{The process $q \overline{q} \to \tilde{g}\overline{\tilde{g}}$}
+\subsubsection*{The Process $q \overline{q} \to \tilde{g}\overline{\tilde{g}}$}
 In contrast to the MSSM no statistical factor of $\frac{1}{2}$ is taken into account when turning from $|\mathcal{M}|^2$ to $\sigma$.
@@
 Still in comparison to the MSSM cross section \cite[p.9]{Beenakker:1996ch} only the first line in eq.
-\eqref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines originate from an $t$ or $u$ channel squark which occurs in only one instead of two chiralities.
+\eqref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines originate from an $t$ or $u$ channel squark which occurs in only one instead of two ``chiralities''.
 Furthermore an interference term from the $t$ and $u$ channel diagram which occurs in the MSSM is absent in the MRSSM.
@@
 
-\subsubsection*{The process $GG \to \tilde{g}\overline{\tilde{g}}$}
+\subsubsection*{The Process $GG \to \tilde{g}\overline{\tilde{g}}$}
 As in the previous process, the MRSSM cross section for $GG \to \tilde{g}\overline{\tilde{g}}$ receives no statistical factor of $\frac{1}{2}$ like in the MSSM.
@@
 
-\subsubsection*{The process $q G \to \tilde{q} \tilde{g}$}
+\subsubsection*{The Process $q G \to \tilde{q} \tilde{g}$}
 This process is exactly the same in the MSSM and MRSSM for there are two differences between the models which exactly cancel each other: Firstly in the MRSSM there is not only the production of a squark and a gluino but also the production of a squark and an antigluino.
@@
 Fortunately the hadronic cross section for the production of a final state $X$, e.g.
-$X = \tilde{q} \tilde{q}$, can be obtained by convolving the partonic cross section with parton density functions of the initial hadrons.
+$X = \tilde{q} \tilde{q}$, can be obtained by convolving the partonic cross section with parton density functions of the initial hadrons:
 \begin{align}
-\sigma^\mathrm{B}_{\mathrm{Had}}(P_1 P_2 \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_{P_1/H_1}(x_1) f_{P_2/H_2}(x_2)\ \sigma^\mathrm{B}_{\mathrm{Part}} (P_1 P_2 \to X, s = x_ 1x_2 S).
+\sigma^\mathrm{B}_{\mathrm{Had}}(P_1 P_2 \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_{P_1/H_1}(x_1) f_{P_2/H_2}(x_2)\ \sigma^\mathrm{B}_{\mathrm{Part}} (P_1 P_2 \to X, s = x_ 1x_2 S).\label{eq:facTheorem}
 \end{align}
@@
 The hadrons center-of-mass energy is denoted with $\sqrt{S}$ where $\sqrt{s} = \sqrt{S x_1 x_2}$ denotes the partons center-of-mass energy.\\
-As the production of the final state $X$ may proceed via various initial partons, one has to sum over all possible possibilities arising from the initial hadrons $H_1$ and $H_2$:
+As the production of the final state $X$ may proceed via various initial partons, one has to sum over all possibilities arising from the initial hadrons $H_1$ and $H_2$:
 \begin{align}
-\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(P_i P_j \to X)m
+\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(P_i P_j \to X)
 \end{align}
@@
 virtual quark-antiquark pairs.} which are permanently interacting which each other.
-Now consider two colliding hadrons in their center-of-mass frame.
+Now consider two colliding hadrons at high energies in their center-of-mass frame.
 Due to Lorentz contraction the hadrons appear as thin discs and the parton's mutual interactions are time-delayed within this frame.
-This effectively means that a hadron at the time of collision is virtually frozen.\\ % maybe picture of colliding discs\\
-This in turn implies that the hadron consists, at the time of collision, of a definite number of partons which can be thought of as carrying a definite fraction of the hadron's  momentum $p_{\mathrm{Part}} = x p_{\mathrm{Had}}$ with $x \in \left\{0, 1 \right\}$.
+This effectively means that a hadron at the time of collision is virtually frozen in the approximate infinite momentum frame.\\ % maybe picture of colliding discs\\
+This in turn implies that the hadron consists, at the time of collision, of a definite number of partons which can be thought of as carrying a definite fraction of the hadron's  momentum $p_{\mathrm{Part}} = x p_{\mathrm{Had}}$ with $x \in \left(0, 1 \right)$.
 The parton density function $f_{P/H}(x)$ can (at tree-level) therefore be understood as the probability of finding a parton $P$ within the hadron $H$ carrying $x$ of its momentum fraction.
@@
 The parton density function is multiplied by $x$ in order to counteract its peak at $x \to 0$.
-The parton density function is given at two different factorisaction scales $\mu_F = Q$}\label{fig:pdfs}
+The parton density function is given at two different factorisaction scales $\mu_F = Q$.}\label{fig:pdfs}
 \end{center}
@@
 The ratio of the gluino and squark mass is fixed to 2.
-The parton densities used are $\mathtt{MMHT2014}$ LO with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}.
+The parton densities used are $\mathtt{MMHT2014LO}$ (LHAPDFID:$25000$) with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}.
 As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}
@@
 Fig.\ref{fig:TreeXsection} shows the hadronic cross section for the production of various squarks in the MRSSM.
-These can only be produced by their non supersymmetric partner, e.g.
+These can only be produced by their Standard Model partner, e.g.
 two up-squarks can only be produced by two up-quarks.
@@
 $\tilde{q}^\dagger\tilde{q}^\dagger$ and $\tilde{q}^\dagger\tilde{g}\left( \overline{\tilde{g}} \right)$, are included.
-In addition, squark production counts thoses processes twice which involve flavor unlike quarks, e.g.
+In addition, squark production counts those processes twice which involve flavor unlike quarks, e.g.
 $ud \to \tilde{u}\tilde{d}$ is counted twice as the $d$-quark may come from either proton.
@@
 Note that the author has opted for the absolute squared amplitudes and not the partonic cross sections because this allows also for the calculation of partial differential cross sections, for possible future use.
-To perform the integration over the Mandelstam variable $t$ and $x_1$ and $x_2$, the routine ``Cuhre'' which is part of the \texttt{CUBA} library\cite{Hahn:2004fe} has been used\\
+To perform the integration over the Mandelstam variable $t$ and $x_1$ and $x_2$, the routine ``Cuhre'' which is part of the \texttt{CUBA} library\cite{Hahn:2004fe} is used.\\
 The following paragraph discusses fig.
@@
 The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row).
-In the final state it has been summed over all squark flavors expect for $t$-squarks.
+In the final state it has been summed over all squark flavors exept for $t$-squarks.
 For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
-The parton densities used are $\mathtt{MMHT2014}$ LO with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}.
+The parton densities used are $\mathtt{MMHT2014LO}$ (LHAPDFID:$25000$) with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}.
 As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}
@@
 \includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
-\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC with $\sqrt{S} = \unit[13]{GeV}$.
+\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC with \mbox{$\sqrt{S} = \unit[13]{GeV}$}.
 The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row).
-In the final state it has been summed over all squark flavors expect for $t$-quarks.
+In the final state it has been summed over all squark flavors exept for $t$-quarks.
 For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
@@
 Furthermore there is the above mentioned destructive interference term in the $q\overline{q} \to \tilde{g}\tilde{g}(\overline{\tilde{g}})$ channel which makes the cross section for this process in the MRSSM dominant over the one in the MSSM.\\
-For a growing squark mass the previously subdominant gluino-squark production takes over and becomes dominant.
+For a increasing squark mass, the previously subdominant gluino-squark production takes over and becomes dominant.
 A salient difference between the MSSM and the MRSSM is that squark production is strongly suppressed in the MRSSM.
-While in the MSSM it becomes dominant above about $\unit[1400]{GeV}$ it is subsubdominant for the whole displayed squark mass in the MRSSM.
+While in the MSSM it becomes dominant above  $\approx \unit[1400]{GeV}$ it is subsubdominant for the whole displayed squark mass in the MRSSM.
 This suppression has also already been explained above.\\
@@
 \includegraphics[scale=.45]{figures/rel_weights_mr=5_MSSM+MRSSM}
-\caption{Hadronic cross section for squark and gluino production (in the first row) and relative contributions of the indicated final states on the total hadronic cross section (in the second row) in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC which $\sqrt{S} = \unit[13]{GeV}$.
-The ratio of gluino and squark mass is fixed to 5.
-In the final state it has been summed over all squark flavors expect for staus.
+\caption{Hadronic cross section for squark and gluino production (in the first row) and relative contributions of the indicated final states to the total hadronic cross section (in the second row) in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC with $\sqrt{S} = \unit[13]{GeV}$.
+The ratio of gluino and squark mass is fixed to $5$.
+In the final state it has been summed over all squark flavors exept for staus.
 For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included.
@@
 The contour plots in fig.
-\ref{fig:ContourTree} underline the already announced difference between squark production in the MRSSM and the MSSM.
-While the cross sections for small gluino masses resemble each other closely, the cross section in the MRSSM gets increasingly suppressed with increasing gluino mass.
+\ref{fig:ContourTree} underline the already mentioned difference between squark production in the MRSSM and the MSSM.
+While the cross sections for small gluino masses resemble each other closely, the cross section in the MRSSM gets increasingly suppressed with rising gluino mass.
 \begin{figure}[!htpb]
@@
 \includegraphics[scale=.55]{figures/contour_MSSM_squarks}
-\caption{The squark production cross section including five flavors (also including $\tilde{q}^\dagger\tilde{q}^{\prime\dagger}$) in the MRSSM (top) and MSSM (bottom) at the LHC which $\sqrt{S} = \unit[13]{GeV}$.
+\caption{The squark (and antisquark) production cross section including five flavors in the MRSSM (top) and MSSM (bottom) at the LHC with $\sqrt{S} = \unit[13]{GeV}$.
 The parton density functions and the renormalization and factorization scale are chosen as in fig.
@@
 \includegraphics[scale=.5]{figures/MSSM+MRSSM_msq=1000}
-\caption{Comparison of squark production cross section including five flavors (also including $\tilde{q}^\dagger\tilde{q}^{\prime\dagger}$) in the MSSM and MRSSM at the LHC which $\sqrt{S} = \unit[13]{GeV}$ for fixed gluino mass (top) and fixed squark mass (bottom).
+\caption{Comparison of squark (and antisquark) production cross section including five flavors in the MSSM and MRSSM at the LHC with $\sqrt{S} = \unit[13]{GeV}$ for fixed gluino mass (top) and fixed squark mass (bottom).
 The parton density functions and the renormalization and factorization scale are chosen as in fig.
@@
 Fig.\ref{fig:TreeXsection_fixed_m} shows the Born cross section of squark production including all possible flavors for a fixed mass of the gluino $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and the squark $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).
-The figure includes errors of the calculation which come from the parton density functions and the renormalization and factorization scale.\\
+The figure includes uncertainty of the calculation which come from the parton density functions and the renormalization and factorization scale.\\
 The 68\% uncertainty from the central value pdf-set is obtained by performing the calculation with all eigenvector sets of the central value and taking the minimum and maximum at each point as deviations from the calculation with the central set.\\
@@
 \caption{Squark production cross section at tree-level (including five flavors and also the production of antisquarks) in the MRSSM for various squark and gluino masses.
+The parton density functions and the renormalization and factorization scale are chosen as in fig.
+\ref{fig:TreeXsection}.
 The uncertainty of the numerical integration is lower than one permille.
@@
 \end{tabular}
-\caption{Same content as in \ref{tab:squarkMRSSM} but for the MSSM.}
+\caption{Same content as in table \ref{tab:squarkMRSSM} but for the MSSM.}
 \end{center}
@@
 As a summary of the comparison between MSSM and MRSSM, one can say, that the gluino production is enhanced in the MRSSM due to distinguishable gluino and antigluino.
-In order to meet missing experimental evidence for supersymmerty, this suggests that gluinos might be heavier than squarks in the MRSSM.
+In order to meet missing experimental evidence for supersymmerty, this suggests that in the MRSSM gluinos might be heavier than squarks.
 Focusing on $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} \geq 2$ the most significant change between the considered models is the growing suppression of squark production for an increasing gluino mass.

### 2016-07-13 Virt_Real.tex
K factor MRSSM contour plot
K factors in thesis

@@
 
-\subsection{Virtual Correction}
+\subsection{Virtual Corrections}
 According to quantum field theory the $\mathcal{O}(\alpha_s)$ correction to a tree-level process includes the computation of one-loop diagrams such as shown in fig.
@@
 \begin{align}
-f_{P_i / H}(x,\mu_f) = f(x) + \left( -\frac{1}{\epsilon} \right)\left[ \frac{\alpha_s}{2\pi} \frac{\Gamma(1-\epsilon)}{\Gamma(1-2\epsilon)} \left( \frac{4\pi\mu_R^2}{\mu_F^2} \right)^\epsilon\right] \int_1^x\frac{\mathrm{d}z}{z} P_{P_i P_j}(z)f_{P_j / H}(\frac{x}{z}).
+f_{P_i / H}(x,\mu_f) = f(x) + \left( -\frac{1}{\epsilon} \right)\left[ \frac{\alpha_s}{2\pi} \frac{\Gamma(1-\epsilon)}{\Gamma(1-2\epsilon)} \left( \frac{4\pi\mu_R^2}{\mu_F^2} \right)^\epsilon\right] \int_1^x\frac{\mathrm{d}z}{z} P_{P_i P_j}(z)f_{P_j / H}(\frac{x}{z}).\label{eq:renpdf}
 \end{align}
@@
 \end{figure}
-These contributions do not comprise soft divergences, as they are associated with a different initial state and the factorization theorem guarantees the absences of soft divergences in each initial state separately.
-In other words, real correction, coming from an initial state with quark and gluon, cannot contribute to the cancellation of soft divergences with virtual correction which are associated with two quarks in the initial state.\\
+These contributions do not comprise soft divergences, as they are associated with a different initial state and the factorization theorem guarantees the absences of soft divergences in each initial state separately\cite{dissertori2003quantum}.
+This can be seen by inspecting eq.
+\eqref{eq:facTheorem} with the leading order parton density function replaced by the renormalized parton density function from eq.
+\eqref{eq:renpdf}.
+As the left hand side of eq.
+\eqref{eq:facTheorem} is free of soft (and collinear) divergences, also the right hand side has to be infrared finite.
+Furthermore, the renormalized parton density functions are free of soft divergences, so the partonic cross section in eq.
+\eqref{eq:facTheorem} needs also be be free of soft divergences.
+In other words, real corrections, coming from an initial state with quark and gluon, cannot contribute to the cancellation of soft divergences with virtual corrections which are associated with two quarks in the initial state.\\
 A split-up of space space in a soft and a hard part is therefore not needed.

### 2016-07-13 figures/One_Loop/MRSSM_uu_susu_Kfactors_msg=2000GeV.py

@@ -14,6 +14,7 @@ m_squark = np.array([], dtype=float);
 sigma_LO_Tree = np.array([], dtype=float);
 sigma_NLO_Tree = np.array([], dtype=float);
 sigma_NLO_1L   = np.array([], dtype=float);
+sigma_Virt   = np.array([], dtype=float);
 
 
 f_Tree = open('MRSSM_Tree_uu_susu_msg=2000GeV.txt', 'r')
@@ -32,6 +33,17 @@ for lines in f_1L.readlines():
     sigma_NLO_Tree = np.append(sigma_NLO_Tree, float(lines.split()[1]))
     sigma_NLO_1L = np.append(sigma_NLO_1L, float(lines.split()[2]))    
 f_1L.close()
+
+#######################
+
+f_1L = open('MRSSM_Virt_uu_susu_msg=2000GeV.txt', 'r')
+discard = f_1L.readline()
+for lines in f_1L.readlines():
+    discard = np.append(m_squark, float(lines.split()[0]))
+    sigma_Virt = np.append(sigma_Virt, float(lines.split()[1]))
+f_1L.close()
+
+#######################
 
 K_min = 0
 K_max = 2
@@ -61,7 +73,10 @@ facecolor=[1,70./100,70./100], color =[1,80./100,80./100], linestyle="-", label 
 first_window.fill_between(m_squark, sigma_NLO_Tree/sigma_LO_Tree, sigma_NLO_1L/sigma_LO_Tree, 
 facecolor=[1,90./100,90./100], color =[1,80./100,80./100], linestyle="-", label = "Real and virtual corrections")
 
-plt.plot(m_squark, sigma_NLO_1L/sigma_LO_Tree, lw=2, ls="-", c='red')#, label = "1L")
+plt.plot(m_squark, sigma_NLO_1L/sigma_LO_Tree, lw=2, ls="-", c='red', label = "total $K$-factor")
+#################
+#plt.plot(m_squark, sigma_Virt/sigma_LO_Tree, lw=2, ls="-", c='k',label="virtual contribution")
+#################
 
 plt.legend(loc='best',prop={'size':22})
 

### 2016-07-13 figures/One_Loop/MRSSM_uu_susu_Kfactors_msq=1000GeV.py

@@ -61,7 +61,7 @@ facecolor=[1,70./100,70./100], color =[1,80./100,80./100], linestyle="-", label 
 first_window.fill_between(m_squark, sigma_NLO_Tree/sigma_LO_Tree, sigma_NLO_1L/sigma_LO_Tree, 
 facecolor=[1,90./100,90./100], color =[1,80./100,80./100], linestyle="-", label = "Real and virtual corrections")
 
-plt.plot(m_squark, sigma_NLO_1L/sigma_LO_Tree, lw=2, ls="-", c='red')#, label = "1L")
+plt.plot(m_squark, sigma_NLO_1L/sigma_LO_Tree, lw=2, ls="-", c='red', label = "total $K$-factor")
 #plt.plot(m_squark, sigma_NLO_Tree/sigma_LO_Tree, lw=2, ls="--", c='blue')#, label = "1L")
 #plt.plot(m_squark, sigma_NLO_Virt/sigma_LO_Tree, lw=2, ls="--", c='red')#, label = "1L")
 #plt.plot(m_squark, sigma_NLO_Real/sigma_LO_Tree, lw=2, ls="--", c='green')#, label = "1L")

### 2016-07-13 figures/One_Loop/MRSSM_uu_susu_Kfactors_msq=1000GeV_msg=2000GeV.py

@@ -53,7 +53,7 @@ facecolor=[1,70./100,70./100], color =[1,80./100,80./100], linestyle="-", label 
 first_window.fill_between(m_sgluon, sigma_NLO_Tree/sigma_LO_Tree, sigma_NLO_1L/sigma_LO_Tree, 
 facecolor=[1,90./100,90./100], color =[1,80./100,80./100], linestyle="-", label = "Real and virtual corrections")
 
-plt.plot(m_sgluon, sigma_NLO_1L/sigma_LO_Tree, lw=2, ls="-", c='red')
+plt.plot(m_sgluon, sigma_NLO_1L/sigma_LO_Tree, lw=2, ls="-", c='red', label = "total $K$-factor")
 
 plt.legend(loc=4,prop={'size':22})
 

### 2016-07-13 figures/One_Loop/MSSM/MSSM_uu_susu_Kfactors_msg=2000GeV.py

@@ -127,7 +127,7 @@ facecolor=[70./100,70./100,1], color =[80./100,80./100,1], linestyle="-", label 
 third_window.fill_between(m_gluino, (sigma_NLO_Tree_lr + 2*sigma_NLO_Tree_ll)/(sigma_LO_Tree_lr + 2*sigma_LO_Tree_ll), (sigma_NLO_1L_lr + 2*sigma_NLO_1L_ll)/(sigma_LO_Tree_lr + 2*sigma_LO_Tree_ll), 
 facecolor=[90./100,90./100,1], color =[80./100,80./100,1], linestyle="-", label = "Real and virtual corrections")
 
-plt.plot(m_gluino, (sigma_NLO_1L_lr + 2*sigma_NLO_1L_ll)/(sigma_LO_Tree_lr + 2*sigma_LO_Tree_ll), lw=2, ls="-", c='blue')#, label = "1L")
+plt.plot(m_gluino, (sigma_NLO_1L_lr + 2*sigma_NLO_1L_ll)/(sigma_LO_Tree_lr + 2*sigma_LO_Tree_ll), lw=2, ls="-", c='blue', label = "total $K$-factor")
 
 plt.legend(loc='best',prop={'size':font_size})
 

### 2016-07-13 Appendix.tex
Becky's remarks

@@
 \begin{align}
-g^{ab} T^a(R)T^b(R) = C(R)\mathbbm{1} \label{eq:Casimir}
+g^{ab} T^a(R)T^b(R) = C(R)\mathbbm{1}, \label{eq:Casimir}
 \end{align}
@@
 \begin{align}
-C(R) \cdot \mathrm{dim}(R) = T(R) \cdot \mathrm{dim}(G)
+C(R) \cdot \mathrm{dim}(R) = T(R) \cdot \mathrm{dim}(G),
 \end{align}
 where $\mathrm{dim}(G)$ is the dimension of the group and $\mathrm{dim}(R)$ is the dimension of the irreducible representation $R$.\\
-In the case of $SU(N)$ one has a diagonal metric $g^{ab} = \delta^{ab}$ and therefore \ref{eq:Casimir} turns to
+In the case of $SU(N)$ one has a diagonal metric $g^{ab} = \delta^{ab}$ and therefore eq. \ref{eq:Casimir} turns to
 \begin{align}
@@
 \end{align}
-and one can write down the following useful formulae for the fundamental representation $R=F$: $T^a_{ij} = \frac{\lambda^a_{ij}}{2}$ and the adjoint representation $R=A$: $(T^a_{ij})^{adj} = -if_{aij}$
+and one can write down the following useful formulae for the fundamental representation $R=F$: $T^a_{ij} = \frac{\lambda^a_{ij}}{2}$ and the adjoint representation $R=A$: $(T^a_{ij})^{adj} = -if_{aij}$:
 \begin{align}
-T^a_{ik} T^a_{kj} &= C(F)\mathbbm{1}_{ij} && \mbox{with}\ C(F) = \frac{N^2-1}{2N} = \frac{4}{3}\nonumber\\
-f^{abc} f^{dbc} &= C(A)\delta^{ad} && \mbox{with}\ C(A) = N = 3\nonumber\\
-\mathrm{Tr}\left[T^aT^b\right] &= T(F)\delta^{ab} && \mbox{with}\ T(F) = \frac{1}{2}\label{eq:DynkinIndex}
+T^a_{ik} T^a_{kj} &= C(F)\mathbbm{1}_{ij} && \mbox{with}\ C(F) = \frac{N^2-1}{2N} = \frac{4}{3},\nonumber\\
+f^{abc} f^{dbc} &= C(A)\delta^{ad} && \mbox{with}\ C(A) = N = 3,\nonumber\\
+\mathrm{Tr}\left[T^aT^b\right] &= T(F)\delta^{ab} && \mbox{with}\ T(F) = \frac{1}{2},\label{eq:DynkinIndex}
 \end{align}
@@
 \overline{\sigma}^\mu && 0
-\end{pmatrix} &&
+\end{pmatrix}, &&
 \gamma_5 = \begin{pmatrix}
@@
 0 && \mathbbm{1}_2
-\end{pmatrix}
+\end{pmatrix}.
 \end{align}
@@
 0 && 0
-\end{pmatrix} && 
+\end{pmatrix}, && 
 P_R = \frac{1}{2}(\mathbbm{1}_4 + \gamma_5) = \begin{pmatrix}
@@
 0 && \mathbbm{1}_2
-\end{pmatrix}\label{eq:projectors}
+\end{pmatrix}.\label{eq:projectors}
 \end{align}
@@
 It is therefore sensible to decompose a four-spinor into a left and a right handed Weyl spinor\footnote{The projectors in the chiral basis (eq.
-\ref{eq:projectors}) explain the names left and right handed Weyl spinors.}
+\eqref{eq:projectors}) explain the names left and right handed Weyl spinors.}
 \begin{align}
@@
 \psi^\alpha, \hspace{1cm} 
-\overline{\psi}^{\dot{\alpha}} = (\psi^\alpha)^\ast, \hspace{1cm} \psi_\alpha = \epsilon_{\alpha\beta}\psi^\beta, \hspace{1cm} \mathrm{and} \hspace{1cm} \psi_{\dot{\alpha}} = \epsilon_{\dot{\alpha}\dot{\beta}}\psi^{\dot{\beta}} = (\psi_\alpha)^\ast,
+\overline{\psi}^{\dot{\alpha}} = (\psi^\alpha)^\ast, \hspace{1cm} \psi_\alpha = \epsilon_{\alpha\beta}\psi^\beta \hspace{1cm} \mathrm{and} \hspace{1cm} \psi_{\dot{\alpha}} = \epsilon_{\dot{\alpha}\dot{\beta}}\psi^{\dot{\beta}} = (\psi_\alpha)^\ast,
 \end{align}
@@
 \begin{align}
-\epsilon^{\alpha\beta} = \epsilon_{\beta\alpha},\ \epsilon^{\dot{\alpha}\dot{\beta}} = \epsilon_{\dot{\beta}\dot{\alpha}} \hspace{3cm} \mathrm{and} \hspace{3cm} \epsilon_{12} = \epsilon_{\dot{1}\dot{2}}= 1.
+\epsilon^{\alpha\beta} = \epsilon_{\beta\alpha},\ \epsilon^{\dot{\alpha}\dot{\beta}} = \epsilon_{\dot{\beta}\dot{\alpha}} \hspace{1cm} \mathrm{and} \hspace{1cm} \epsilon_{12} = \epsilon_{\dot{1}\dot{2}}= 1.
 \end{align}
@@
 \psi\chi &:= \psi^\alpha\chi_\alpha = -\chi_\alpha\psi^\alpha = \chi^\alpha\psi_\alpha = \chi\psi,\nonumber\\
-\overline{\psi}\overline{\chi} &:= \overline{\psi}_{\dot{\alpha}} \overline{\chi}^{\dot{\alpha}} = -\overline{\chi}^{\dot{\alpha}}\overline{\psi}_{\dot{\alpha}} = \overline{\chi}_{\dot{\alpha}}\overline{\psi}^{\dot{\alpha}} = \overline{\chi}\overline{\psi} \label{eq:Weylspinorproduct}
+\overline{\psi}\overline{\chi} &:= \overline{\psi}_{\dot{\alpha}} \overline{\chi}^{\dot{\alpha}} = -\overline{\chi}^{\dot{\alpha}}\overline{\psi}_{\dot{\alpha}} = \overline{\chi}_{\dot{\alpha}}\overline{\psi}^{\dot{\alpha}} = \overline{\chi}\overline{\psi}.
+\label{eq:Weylspinorproduct}
 \end{align}
-To make the index structure of the Pauli matrices explicit, one writes $\sigma^\mu_{\alpha\dot{\alpha}}$ and $\overline{\sigma}^{\mu\dot{\alpha}\alpha}$ for the formulae in \ref{eq:Pauli}.
+To make the index structure of the Pauli matrices explicit, one writes $\sigma^\mu_{\alpha\dot{\alpha}}$ and $\overline{\sigma}^{\mu\dot{\alpha}\alpha}$ for the formulae in eq.
+\eqref{eq:Pauli}.
 For the definition of the supersymmetry algebra in section \ref{sec:SUSYalgebra} the representation of the generators of the Lorentz group on the left and right handed Weyl spinor space is introduced:
 \begin{align}
-\frac{1}{2}(\sigma^{\mu\nu})_\alpha^{\ \beta} := \frac{i}{4}(\sigma^\mu\overline{\sigma}^\nu - \sigma^\nu\overline{\sigma}^\mu)_\alpha^{\ \beta}\nonumber\\
-\frac{1}{2}(\overline{\sigma}^{\mu\nu})^{\dot{\alpha}}_{\ \dot{\beta}} := \frac{i}{4}(\overline{\sigma}^\mu\sigma^\nu - \overline{\sigma}^\nu\sigma^\mu)^{\dot{\alpha}}_{\ \dot{\beta}}
+\frac{1}{2}(\sigma^{\mu\nu})_\alpha^{\ \beta} := \frac{i}{4}(\sigma^\mu\overline{\sigma}^\nu - \sigma^\nu\overline{\sigma}^\mu)_\alpha^{\ \beta},\nonumber\\
+\frac{1}{2}(\overline{\sigma}^{\mu\nu})^{\dot{\alpha}}_{\ \dot{\beta}} := \frac{i}{4}(\overline{\sigma}^\mu\sigma^\nu - \overline{\sigma}^\nu\sigma^\mu)^{\dot{\alpha}}_{\ \dot{\beta}}.
 \end{align}
@@
 \begin{align}
-&\overline{\Psi} := \Psi^\dagger \gamma^0, && \Psi^C := i\gamma^2\gamma^0 \overline{\Psi}^T  
+&\overline{\Psi} := \Psi^\dagger \gamma^0, && \Psi^C := i\gamma^2\gamma^0 \overline{\Psi}^T, 
 \end{align}
@@
 \end{align}
-The 4-spinor of an arbitrary quark $q$ is given in terms of Weyl spinors $q_L$ and $\overline{q}_R$ by
+The four-spinor of an arbitrary quark $q$ is given in terms of Weyl spinors $q_L$ and $\overline{q}_R$ by
 \begin{align}
@@
 \overline{q}_R
-\end{pmatrix}
+\end{pmatrix},
 \end{align}
-whereas the 4-spinor of the Dirac gauginos is given in terms of the Weyl spinors $\lambda$ and $\overline{\chi}$\footnote{$\lambda$ is the superpartner of the gluon, called the gluino and $\overline{\chi}$ is the Weyl spinor of the chiral superfield which is associated with the gluon, called the octino.}
+whereas the four-spinor of the Dirac gauginos is given in terms of the Weyl spinors $\lambda$ and $\overline{\chi}$:\footnote{$\lambda$ is the superpartner of the gluon, called the gluino and $\overline{\chi}$ is the Weyl spinor of the chiral superfield which is associated with the gluon, referred to as the octino.}
 \begin{align}
@@
 i \overline{\chi}^a
-\end{pmatrix}
+\end{pmatrix}.
 \end{align}
@@
 \subsection{Anticommuting Numbers}\label{sec:AnticommNumbers}
-Anticommuting numbers $\theta^\alpha$ are also referred to as Grassmann numbers and are defined by $\theta^\alpha\theta^\beta = -\theta^\beta\theta^\alpha$ and commute with ordinary c-numbers.\\
-They occur in superspace formalism in the form of 2 tuples, i.e. $\theta^\alpha$ with $\alpha=1,2$. The complex conjugate of this tuple is denoted with $\overline{\theta}^{\dot{\alpha}}$. 
+Anticommuting numbers $\theta^\alpha$ are also referred to as Grassmann numbers. These are defined by $\theta^\alpha\theta^\beta = -\theta^\beta\theta^\alpha$ and commute with ordinary c-numbers.\\
+They occur in superspace formalism in the form of two-tuples, i.e.
+$\theta^\alpha$ with $\alpha \in \left\{1,2\right\}$.
+The complex conjugate of this tuple is denoted with $\overline{\theta}^{\dot{\alpha}}$.
 Derivatives are defined by
 \begin{align}
-\partial^\alpha \theta_\beta := \frac{\partial}{\partial \theta_\alpha} \theta_\beta := \delta^\alpha_\beta \hspace{4cm} \partial_\alpha \theta^\beta := \frac{\partial}{\partial \theta^\alpha} \theta^\beta := \delta_\alpha^\beta\nonumber\\
-\overline{\partial}^{\dot{\alpha}} \overline{\theta}_{\dot{\beta}} := \frac{\partial}{\partial \overline{\theta}_{\dot{\alpha}}} \overline{\theta}_{\dot{\beta}} := \delta^{\dot{\alpha}}_{\dot{\beta}} \hspace{4cm} \overline{\partial}_{\dot{\alpha}} \overline{\theta}^{\dot{\beta}} := \frac{\partial}{\partial \overline{\theta}^{\dot{\alpha}}} \overline{\theta}^{\dot{\beta}} := \delta_{\dot{\alpha}}^{\dot{\beta}}
+\partial^\alpha \theta_\beta := \frac{\partial}{\partial \theta_\alpha} \theta_\beta := \delta^\alpha_\beta, \hspace{4cm} \partial_\alpha \theta^\beta := \frac{\partial}{\partial \theta^\alpha} \theta^\beta := \delta_\alpha^\beta,\nonumber\\
+\overline{\partial}^{\dot{\alpha}} \overline{\theta}_{\dot{\beta}} := \frac{\partial}{\partial \overline{\theta}_{\dot{\alpha}}} \overline{\theta}_{\dot{\beta}} := \delta^{\dot{\alpha}}_{\dot{\beta}}, \hspace{4cm} \overline{\partial}_{\dot{\alpha}} \overline{\theta}^{\dot{\beta}} := \frac{\partial}{\partial \overline{\theta}^{\dot{\alpha}}} \overline{\theta}^{\dot{\beta}} := \delta_{\dot{\alpha}}^{\dot{\beta}},
 \end{align}
@@
 \begin{align}
-\partial_\alpha = -\epsilon_{\alpha\beta}\partial^\beta \hspace{4cm} \partial_{\dot{\alpha}} = -\epsilon_{\dot{\alpha}\dot{\beta}}\partial^{\dot{\beta}}.
+\partial_\alpha = -\epsilon_{\alpha\beta}\partial^\beta, \hspace{4cm} \partial_{\dot{\alpha}} = -\epsilon_{\dot{\alpha}\dot{\beta}}\partial^{\dot{\beta}}.
 \end{align}
@@
 \int \mathrm{d}\theta^2 &:= \int\frac{1}{4}\epsilon_{\alpha\beta} \mathrm{d}\theta^\alpha\mathrm{d}\theta^\beta, \hspace{1cm}
-\int \mathrm{d}\overline{\theta}^2 := \int\frac{1}{4}\epsilon_{\dot{\alpha}\dot{\beta}} \mathrm{d}\theta^{\dot{\alpha}}\mathrm{d}\theta^{\dot{\beta}}, \hspace{1cm} \mathrm{and} \nonumber\\
+\int \mathrm{d}\overline{\theta}^2 := \int\frac{1}{4}\epsilon_{\dot{\alpha}\dot{\beta}} \mathrm{d}\theta^{\dot{\alpha}}\mathrm{d}\theta^{\dot{\beta}} \hspace{1cm} \mathrm{and} \nonumber\\
 \int \mathrm{d}^4\theta &:= \int \mathrm{d}\theta^2\mathrm{d}\overline{\theta}^2.
 \end{align}
-For the definition of (anti-)chiral superfields and the field strength chiral superfields it proves useful to introduce supersymmetry (or chiral) covariant derivatives 
+For the definition of (anti-)chiral superfields and the field strength chiral superfields, it proves useful to introduce supersymmetry (or chiral) covariant derivatives :
 \begin{align}
-&\mathcal{D}_\alpha := \frac{\partial}{\partial \theta^\alpha} - i(\sigma^\mu\overline{\theta})_\alpha\partial_\mu && \mathcal{D}^{\dot{\alpha}} := \frac{\partial}{\partial \overline{\theta}_{\dot{\alpha}}} - i(\overline{\sigma}^\mu\theta)^{\dot{\alpha}} \partial_\mu\nonumber\\
-&D^\alpha := \epsilon^{\alpha\beta} D_\beta = -\frac{\partial}{\partial \theta_\alpha} + i(\overline{\theta} \overline{\sigma}^\mu)^\alpha \partial_\mu && \mathcal{D}_{\dot{\alpha}} := \epsilon_{\dot{\alpha}\dot{\beta}} \mathcal{D}^{\dot{\beta}} = -\frac{\partial}{\partial \overline{\theta}^{\dot{\alpha}}} + i(\sigma^\mu\theta)_{\dot{\alpha}} \partial_\mu.
+&\mathcal{D}_\alpha := \frac{\partial}{\partial \theta^\alpha} - i(\sigma^\mu\overline{\theta})_\alpha\partial_\mu, && \mathcal{D}^{\dot{\alpha}} := \frac{\partial}{\partial \overline{\theta}_{\dot{\alpha}}} - i(\overline{\sigma}^\mu\theta)^{\dot{\alpha}} \partial_\mu,\nonumber\\
+&D^\alpha := \epsilon^{\alpha\beta} D_\beta = -\frac{\partial}{\partial \theta_\alpha} + i(\overline{\theta} \overline{\sigma}^\mu)^\alpha \partial_\mu, && \mathcal{D}_{\dot{\alpha}} := \epsilon_{\dot{\alpha}\dot{\beta}} \mathcal{D}^{\dot{\beta}} = -\frac{\partial}{\partial \overline{\theta}^{\dot{\alpha}}} + i(\sigma^\mu\theta)_{\dot{\alpha}} \partial_\mu.
 \end{align}
-By construction they are supersymmetry invariant, i.e. they fulfill the following anticommutation relations with the supersymmetry generators from eq. \ref{eq:SUSYGen}:
+By construction they are supersymmetry invariant, i.e. they fulfill the following anticommutation relations with the supersymmetry generators from eq. \eqref{eq:SUSYGen}:
 \begin{align}
@@
 \subsection{Feynman Rules for the RSQCD}\label{sec:FeynmanRules}
-The following Feynman rules are derived from the Lagrangian of the R-symmetric supersymmetric quantum chromodynamics (RSQCD) eq.
-\ref{eq:L_RSQCD}.
+The following Feynman rules (fig.
+\ref{fig:firstFeynmanRules} - \ref{fig:thirdFeynmanRules}) are derived from the Lagrangian of the $R$-symmetric supersymmetric quantum chromodynamics (RSQCD) eq.
+\eqref{eq:L_RSQCD}.
 When compared with the Feynman rules of the supersymmetric QCD the diagrams involving scalar gluons are new.
@@
 \caption{In the Feynman diagrams of the propagators the momentum is flowing from the right to the left hand side. The gluon propagator is given in Feynman gauge.\newline
-In the Feynman diagrams of the vertices all momenta flow towards the vertex, i.e. in diagram 9 $-p_1$ is flowing towards the vertex.\newline
+In the Feynman diagrams of the vertices all momenta flow towards the vertex, i.e. in diagram 9: $-p_1$ flows towards the vertex.\newline
 The indices $A,B \in \left\{ L,R \right\}$ label the left/right ``handedness'' of the squarks.
@@
 Applying a flipping rule to a vertex one has to reverse the curved arrow, i.e.
-the fermion flow and replace $\Psi$ with $\bar{\Psi}^C$.
+the fermion flow and replace $\Psi$ with $\overline{\Psi}^C$.
 In addition one has to add a minus sign for Feynman rule 13.}\label{fig:secondFeynmanRules}
@@
 \end{tikzpicture}
+\caption{Feynman rules involving only sgluons and other scalar fields.}\label{fig:thirdFeynmanRules}
 \end{center}
@@
 \frac{i}{16\pi^2} B_{0,\mu,\mu\nu}(p^2,m_1^2,m_2^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p)^2-m_2^2]},\\
-\frac{i}{16\pi^2} C_{0,\mu,\mu\nu}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p_1)^2-m_2^2][(l+p_1+p_2)^2-m_3^2]}.\nonumber\label{eq:LoopInt}
+\frac{i}{16\pi^2} C_{0,\mu,\mu\nu}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p_1)^2-m_2^2][(l+p_1+p_2)^2-m_3^2]},\nonumber\label{eq:LoopInt}
 \end{align}
 with the shortcut $\int_l = \mu^{2\epsilon}\int\frac{\mathrm{d}^D l}{(2\pi)^D}$.
-Furthermore there are supressed $\varepsilon$'s which prescripe how the poles in the complex plane are avoided.
+Furthermore there are suppressed $\varepsilon$'s which prescribe how the poles in the complex plane are avoided.
 They are hidden in the infinitesimal shift of the masses: $m_i^2 \to m_i^2 - i \varepsilon$.\\
@@
 The parameter $t$ is given by $\frac{m_2^2}{m_1^2}$.
-As can be seen from \ref{eq:B1} $B_1$ is in contrast to $B_0$ not symmetric in its masses but it can be shown\cite{Romao} that
+As can be seen from eq.
+\eqref{eq:B1}, $B_1$ is, in contrast to $B_0$, not symmetric in its masses but it can be shown\cite{Romao} that
 \begin{align}
@@
 \end{align}
-Inserting \ref{eq:PhaseTrafo} into \ref{eq:DPhi2} and using $2|\vec{k}_a| = \sqrt{s} = E_1 + E_2$ gives
+Inserting eq. \eqref{eq:PhaseTrafo} into eq. \eqref{eq:DPhi2} and using $2|\vec{k}_a| = \sqrt{s} = E_1 + E_2$ gives
 \begin{align}
@@
 \end{align}
-where the $\Theta$-function comes from the bounds of $|\vec{p}_1|$ and $\theta$ visible in \ref{eq:DPhi2} and the combination of \ref{eq:t} and \ref{eq:u}.
+where the $\Theta$-function comes from the bounds of $|\vec{p}_1|$ and $\theta$, visible in eq.
+\eqref{eq:DPhi2} and the combination of eq.
+\eqref{eq:t} and eq.
+\eqref{eq:u}.
 Working in $D=4-2\epsilon$ dimensions and inserting $\Theta(s-4m^2)$ with $m = \frac{m_1 + m_2}{2}$ to account for the production threshold one finds

### 2016-07-13 NLO.tex
Becky's remarks

@@
 To do so, the next section gives a justification why on-shell renormalization has been chosen in section \ref{sec:renMRSSM}.
-After that, the set up of the calculation, which has been performed by a \texttt{C++} program,  of the different contributions to $\sigma^{\mathrm{NLO}}$, is explained.
+After that, the setup of the calculation of the different contributions to $\sigma^{\mathrm{NLO}}$, which has been performed by a \texttt{C++} program, is explained.
 This includes a remark on how the calculation was sped up.
 Finally the results of the computation are presented in the form of $K$-factors.
-These are then compared to the ones in the MSSM before the thesis closes with an discussion of the behavior of $\sigma^{\mathrm{NLO}}$ in the limit of large sgluon masses.
+These are then compared to the ones in the MSSM before the thesis closes with a discussion of the behavior of $\sigma^{\mathrm{NLO}}$ in the limit of large sgluon masses.
 
@@
 \\
-Considering a physical process with kinematics $\vec{k}_1 \hdots \vec{k}_n \to \vec{p}_1 \hdots \vec{p}_m$ and taking for the sake of simplicity only one scalar field $\phi$ the Fourier transform of the time ordered product of a correlation function is related to the corresponding S-matrix element like\footnote{In this subsection the $\sim$ indicates that the poles on either side are the same provided that all momenta are close to their mass shell, i.e.
+Considering a physical process with kinematics $\vec{k}_1 \hdots \vec{k}_n \to \vec{p}_1 \hdots \vec{p}_m$ and taking only one scalar field $\phi$ for the sake of simplicity, the Fourier transform of the time ordered product of a correlation function is related to the corresponding S-matrix element like\footnote{In this section, $\sim$ indicates that the poles on either side are the same provided that all four-momenta are close to their mass shell, i.e.
 $p_i^0 \to E_{\vec{p}_i}$ and $k_j^0 \to E_{\vec{k}_j}$.}
@@
 \prod_{i=1}^n \int \mathrm{d}x_i\ \mathrm{e}^{ip_i x_i} \prod_{j=1}^m \int \mathrm{d}y_j\ \mathrm{e}^{ik_j y_j} \left\langle \Omega | \mathcal{T} \left[ \phi(x_1) \hdots \phi(x_n) \phi(y_1) \hdots \phi(y_m) \right] | \Omega\right\rangle \nonumber\\
-\sim \prod_{i=1}^n \frac{i\sqrt{Z}}{p_i^2 - m^2 + i\epsilon} \prod_{j=1}^m \frac{i\sqrt{Z}}{k_j^2 - m^2 + i\epsilon} \left\langle \left.\left.\vec{p}_1 \hdots \vec{p}_n \right| S \right| \vec{k}_1 \hdots \vec{k}_m \right\rangle .\label{eq:LSZ}
+\sim \prod_{i=1}^n \frac{i\sqrt{Z}}{p_i^2 - m^2 + i\epsilon} \prod_{j=1}^m \frac{i\sqrt{Z}}{k_j^2 - m^2 + i\epsilon} \left\langle \vec{p}_1 \hdots \vec{p}_n \left| S \left| \vec{k}_1 \hdots \vec{k}_m \right\rangle\right.\right.
+.\label{eq:LSZ}
 \end{align}
-Here $\mathcal{T}$ denotes the time ordering operator, $\left.| \Omega \right\rangle$ is the ground state of the interacting theory and $\sqrt{Z}$ is the residue of the single particle pole in the two-point function
+Here $\mathcal{T}$ denotes the time ordering operator, $\left.| \Omega \right\rangle$ is the ground state of the interacting theory and $\sqrt{Z}$ is the residue of the single particle pole\footnote{Note that this does not coincide with the renormalization constant $Z$ in eq.
+\eqref{eq:renconst}.} in the ``full'' two-point function
 \begin{align}
@@
 \end{align}
+which is diagrammatically shown in fig. \ref{fig:fullpropagator}.
 \begin{figure}[!htbp]
@@
 \end{tikzpicture}
-\caption{Diagrammatic figure of the two-point function of a scalar field: The propagator in an interaction theory can be calculated in a perturbation series in the coupling constant.}\label{fig:fullpropagator}
+\caption{Diagrammatic figure of the ``full'' two-point function of a scalar field: The propagator in an interaction theory can be calculated in a perturbation series in the coupling constant.}\label{fig:fullpropagator}
 \end{center}
@@
 \begin{align}
-\left[ p^2 - m_0^2 - \Sigma(p^2)\right]_{p^2 = m^2} = 0
+\left[ p^2 - m_0^2 - \Sigma(p^2)\right]_{p^2 = m^2} = 0.
 \end{align}
@@
 \begin{align}
-p^2 - m_0^2 - \Sigma(p^2) = (p^2 - m^2)\left( 1 - \frac{\partial \Sigma(p^2)}{\partial p^2} \right)_{p^2 = m^2} + \mathcal{O}((p^2 - m^2)^2).
+p^2 - m_0^2 - \Sigma(p^2) = \left.(p^2 - m^2)\left( 1 - \frac{\partial \Sigma(p^2)}{\partial p^2} \right)\right|_{p^2 = m^2} + \mathcal{O}((p^2 - m^2)^2).
 \end{align}
@@
 \begin{align}
-Z = \left( 1 - \frac{\partial \Sigma(p^2)}{\partial p^2} \right)_{p^2 = m^2}^{-1}.
+Z = \left.\left( 1 - \frac{\partial \Sigma(p^2)}{\partial p^2} \right)^{-1}\right|_{p^2 = m^2}.
 \end{align}
-Now considers the full $(n+m)$-point function in scalar theory.
+Now consider the full $(n+m)$-point function, depicted in fig.
+\ref{fig:fullvertex}, in scalar theory.
 One can decompose it into an amputated $(n+m)$-point function and ``full'' propagators like written in eq.
@@
 \end{tikzpicture}
-\caption{Diagrammatic figure of a ``full'' $(n+m)$-point function. Apart from the ``full'' propagators there is the ``full'' amputated $(n+m)$-point function}
+\caption{Diagrammatic figure of a ``full'' $(n+m)$-point function. Apart from the ``full'' propagators there is the ``full'' amputated $(n+m)$-point function.}\label{fig:fullvertex}
 \end{center}
@@
 \end{align}
-for the full propagators one notices the same singularity as in eq. \eqref{eq:LSZ}. Comparing the coefficients of these poles in eq. \eqref{eq:LSZ} one obtains
+for the full propagators, one notices the same singularity as in eq. \eqref{eq:LSZ}. Comparing the coefficients of these poles in eq. \eqref{eq:LSZ}, one obtains
 \begin{figure}[!htbp]
@@
 \begin{tikzpicture}[line width=2.0 pt, scale=1.3, arrow/.style={thick,->,shorten >=2pt,shorten <=2pt,>=stealth}]
-	\node at (-4,0) {$\left\langle \left.\left.\vec{p}_1 \hdots \vec{p}_n \right| S \right| \vec{k}_1 \hdots \vec{k}_m \right\rangle =\sqrt{Z}^{n+m} \cdot$};
+	\node at (-4,0) {$\left\langle \vec{p}_1 \hdots \vec{p}_n \left| S \left| \vec{k}_1 \hdots \vec{k}_m \right\rangle \right.\right. =\sqrt{Z}^{n+m} \cdot$};
 	\draw (0,0) circle (.75);
@@
 	\draw[fill=black] (-100:1.1) circle (.01);
-\end{tikzpicture}
+\end{tikzpicture}.
 \end{center}
@@
 \end{align}
-introduces no further modification, when turning from the Green function to the S-matrix-element because $Z = 1$ in on-shell renormalization.
+introduces no further modification, when turning from the Green function to the S-matrix-element.
+The residues of the propagator are $Z = 1$ in on-shell renormalization.
 Furthermore the on-shell condition for the mass renormalization
 \begin{align}
-\Sigma(p^2)|_{p^2 = m^2} = 0
+\left.\Sigma(p^2)\right|_{p^2 = m^2} = 0
 \end{align}
@@
 They have been set to $\mu_F = \mu_R = m_{\tilde{q}}$.
-The next section summaries how the calculation has been automated within a \texttt{C++} program.
+The next section summarizes how the calculation has been automated within a \texttt{C++} program.
 
@@
 	\node [block4] at (-1,0) (Mathematica) {Mathematica notebook};
-	\node [block1a] at (-1,-2.1) (notebookR) {soft/collinear limit: \newline \texttt{FeynArts} $\to \mathcal{M}^{\mathrm{R}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{R}|^2}$};
-	\node [block1a] at (-1,-8) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{B}|^2}$};	
+	\node [block1a] at (-1,-2.1) (notebookR) {soft/collinear limit: \newline \texttt{FeynArts} $\to \mathcal{M}^{\mathrm{R}}$ \newline \texttt{FormCalc} $\to$ $\sum |\mathcal{M}^{\mathrm{R}|^2}$};
+	\node [block1a] at (-1,-8) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to$ $\sum |\mathcal{M}^{\mathrm{B}|^2}$};	
 	\node [block1a] at (-1,-5.7) (notebookV) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{1L}}$ \newline \texttt{FormCalc} $\to$ \newline $2\sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$};
@@
 	\node [block5b] at (3.7,-8.3) (Born) {\underline{Born contribution} \newline \texttt{CUBA} $\to$ \newline integration over \newline $t, x_1, x_2$ to $\sigma^{\mathrm{B}}$};
-	\node [block5b] at (7.5,-7.35) (Virt) {\underline{Virtual correction}\newline \texttt{LoopTools} $\to$ \newline computation of $ 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$ \newline \texttt{CUBA} $\to$ \newline integration over \newline $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$ };
-	\node [block5c] at (11.5,-5.1) (Real) {\underline{Real correction}\newline phase space slicing: \newline $\bullet$ soft/collinear part \newline from \texttt{Mathematica},\newline \texttt{CUBA} three dimen- \newline sional integration to $\sigma^{\mathrm{R}}_{\mathrm{S}}$ and $\sigma^{\mathrm{R}}_{\mathrm{HC}}$ \newline $\bullet$ hard non-collinear \newline part from \newline \texttt{MADGRAPH}, \newline  \texttt{CUBA} $\to$ seven \newline dimensional \newline integration to $\sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$ \newline $\sigma^{\mathrm{R}} = \sigma^{\mathrm{R}}_{\mathrm{S}} + \sigma^{\mathrm{R}}_{\mathrm{HC}} + \sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$};
+	\node [block5b] at (7.5,-7.35) (Virt) {\underline{Virtual corrections}\newline \texttt{LoopTools} $\to$ \newline computation of $ 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$ \newline \texttt{CUBA} $\to$ \newline integration over \newline $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$ };
+	\node [block5c] at (11.5,-5.1) (Real) {\underline{Real corrections}\newline phase space slicing: \newline $\bullet$ soft/collinear part \newline from \texttt{Mathematica},\newline \texttt{CUBA} three dimen- \newline sional integration to $\sigma^{\mathrm{R}}_{\mathrm{S}}$ and $\sigma^{\mathrm{R}}_{\mathrm{HC}}$ \newline $\bullet$ hard non-collinear \newline part from \newline \texttt{MADGRAPH}, \newline  \texttt{CUBA} $\to$ seven \newline dimensional \newline integration to $\sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$ \newline $\sigma^{\mathrm{R}} = \sigma^{\mathrm{R}}_{\mathrm{S}} + \sigma^{\mathrm{R}}_{\mathrm{HC}} + \sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$};
 	\path [line, line width = 1] (1.2,-8.0) -- (1.9,-8.0);
@@
 \caption{This scheme illustrates the setup of the computation of the next-to-leading order cross section.
-The (absolute) squared matrix amplitudes of the Born contribution the virtual correction and the real correction in the soft and/or collinear limit are generated by \texttt{Mathematica} packages and imported into a \texttt{C++} code.
-The amplitude from the real corrections is analytically integrated over the gluon's four momentum in $D$ dimensions.
+The (absolute) squared matrix amplitudes of the Born contribution the virtual corrections and the real corrections in the soft and/or collinear limit are generated by \texttt{Mathematica} packages and imported into a \texttt{C++} code.
+The amplitude from the real corrections is in the soft and collinear limit analytically integrated over the gluon's four-momentum in $D$ dimensions.
 Loop integrals are evaluated numerically using \texttt{Looptools}.
@@
 The parton density functions are included using \texttt{LHAPDF6}\cite{Buckley:2014ana}.\\
-The computation of the real corrections have been done by Wojciech Kotlarski, another member of the group.
-To extract the singularities from the real corrections, the ``two cut phase space slicing method'' outlined in section \ref{sec:RealGluonRad}, has been used.
+The computation of the real corrections has been done by Wojciech Kotlarski, another member of the group.
+To extract the singularities from the real corrections, the ``two cut phase space slicing method'', outlined in section \ref{sec:RealGluonRad}, has been used.
 For the soft and hard collinear limit, the absolute squared matrix element has been calculated with \texttt{FormCalc} and analytically integrated over the gluon's four-momentum in $D$ dimensions in \texttt{Mathematica}.
@@
 \\
-It has been checked that for multiple different and quite distinct choices of the parameters $m_{\tilde{q}}$ and $m_{\tilde{g}}$, the double as well as the single poles of the virtual and real correction cancel up to machine precision.
+It has been checked for multiple different and quite distinct choices of the parameters $m_{\tilde{q}}$ and $m_{\tilde{g}}$ that the double as well as the single poles of the virtual and real corrections cancel up to machine precision.
 Regarding the virtual corrections, this has been done by numerically extracting the $\frac{1}{\epsilon}$ and $\frac{1}{\epsilon^2}$ coefficient of loop integrals (see the discussion in section \ref{sec:SetLambdaExplanation} for more details).\\
@@
 \subsubsection{Remark on Prefactors in the Calculation}\label{sec:prefactors}
-For the discussion of results it will not been distinguished between virtual and real corrections.
-This is because they have not been separated strictly in the calculation: As already discussed both $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{R}}$ are divergent, i.e.
+For the discussion of results it will not be distinguished between virtual and real corrections.
+This is because they have not been separated strictly in the calculation: As already discussed, both $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{R}}$ are divergent, i.e.
 there are poles of the form $\frac{1}{\epsilon}$ and $\frac{1}{\epsilon^2}$.
 But these pole cancel exactly.
-On the other hand there are also prefactors from the phase space integral and the loop integral, with can be expanded in a power series in $\epsilon$.
+On the other hand there are also prefactors from the phase space integral and the loop integral, which can be expanded in a power series in $\epsilon$.
 In short, the virtual and real correction to the cross section can be expressed with some coefficients $A$ - $E$, which are functions of the parameters $m_{\tilde{g}}$, $m_{\tilde{q}}$ and $m_{\sigma}$, in the following way:
@@
 Keeping them in eq.
-\eqref{eq:prefactoredecomp}, would slow the computation of the real part down by a factor of about five because this part of the calculation is done analytically.
-Therefore a speed-up can been achieved by discarding the common prefactors at the cost of loosing track about the origin of the next-to-leading order correction.\\
-One common prefactor comes from the two-body phase space integral in eq. \eqref{eq:diffsigma}
+\eqref{eq:prefactoredecomp} would slow the computation of the real part down by a factor of about five because this part of the calculation is done analytically.
+Therefore a speed-up can be achieved by discarding the common prefactors at the cost of loosing track about the origin of the next-to-leading order corrections.\\
+One common prefactor comes from the two-body phase space integral in eq. \eqref{eq:diffsigma}:
 \begin{align}
@@
 \end{align}
-In addition the prefactor of a loop integral defined in \texttt{LoopTools} differs from the one usually (and therefore also here) used.
+In addition, the prefactor of a loop integral defined in \texttt{LoopTools} differs from the one usually (and therefore also here) used.
 The \texttt{LoopTools} definition\cite{LoopToolsManual} of a loop integral is
@@
 \end{align}
-where $T^1$ is an $A$-integral, $T^2$ is an $B$-integral, etc.
+where $T^1$ is an $A$-integral, $T^2$ is a $B$-integral, etc.
 and $r_\Gamma = \frac{\Gamma(1-\epsilon)^2\Gamma(1+\epsilon)}{\Gamma(1-2\epsilon)}$, where $\Gamma(z)$ is the Gamma function.
@@
 \eqref{eq:LoopPrefactor} are the prefactors discarded in the computation.
-Instead the prefactor $\left( 1 + \frac{\pi^2}{6}\epsilon^2 \right)$ has been included in the virtual correction.
+Instead, the prefactor $\left( 1 + \frac{\pi^2}{6}\epsilon^2 \right)$ has been included in the virtual correction.
 Therefore $P_1$ and $P_2$ are chosen like
 \begin{align}
-P_1 &=  2\ln 4\pi - 2\gamma_E - \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} \\
-P_2 &=  -\ln 4\pi \cdot\ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} + \frac{1}{2} \ln^2 \frac{tu - m_{\tilde{q}}^4}{\mu^2 s}  + \gamma_E^2 - \frac{\pi^2}{3} + \ln^2 4\pi - 2\gamma_E\ln 4\pi + \gamma_E \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s}  \nonumber
+P_1 &=  2\ln 4\pi - 2\gamma_E - \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s},\\
+P_2 &=  -\ln 4\pi \cdot\ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} + \frac{1}{2} \ln^2 \frac{tu - m_{\tilde{q}}^4}{\mu^2 s}  + \gamma_E^2 - \frac{\pi^2}{3} + \ln^2 4\pi - 2\gamma_E\ln 4\pi + \gamma_E \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s}.
+\nonumber
 \end{align}
@@
 It can be seen that the  $K$-factor increases with increasing squark mass and decreases with increasing gluino mass.
-Note, that the sum of virtual and real corrections gets negative for very light squarks.
+Note that the sum of virtual and real corrections gets negative for very light squarks.
 But this region of parameter space is already excluded experimentally.
@@
 \end{figure}
-Note further, that within the real corrections, only gluon radiation is included.
+Note further that within the real corrections, only gluon radiation is included.
 This is because quark radiation, as described in section \ref{sec:RealQuarkRad}, involves the treatment of on-shell singularities which have unfortunately not been dealt with, due to a limited time budget.
 However, \cite{Gavin:2013kga} suggests that quark radiation gives only a sub percent effect to the next-to-leading order cross section of squark production when $m_{\tilde{g}} < m_{\tilde{q}}$.
-Of course, this argument applies to the MSSM but as the only difference to the MRSSM comes from diagrams involving gluinos and sgluons it provides also a strong argument for the suppression of quark radiation in the MRSSM.
+Of course, this argument applies to the MSSM but as the only difference to the MRSSM comes from diagrams involving gluinos and sgluons, it provides also a strong argument for the suppression of quark radiation in the MRSSM.
 In fact, sgluons do not appear at all in diagrams contributing to real corrections.
 Furthermore, the change from Majorana to Dirac gluinos can never imply an amplification of processes involving gluinos.
-The reason for this is that if a gluino undergoes, due to its mass, a chirality flip, the right handed part of it, namely the octino, does neither couple to quarks nor to squarks.
+The reason for this is that if a gluino undergoes a chirality flip, due to its mass, the right handed part of it, namely the octino, does neither couple to quarks nor to squarks.
 However, the effect of quark radiation is thought to increase when $m_{\tilde{g}} > m_{\tilde{q}}$.
-This is quantified within the next section, when squark production is discussed in the MSSM.
+This is quantified within the next section, when squark production in the MSSM is discussed.
 Nonetheless, quark radiation is by no means to be thought of a dominant contribution to squark production at next-to-leading order.\\
@@
 The pseudoscalar mass is fixed to \mbox{$m_{\mathrm{\sigma}} = \unit[5000]{GeV}$}.
-For $\sigma^{\mathrm{LO}}$ parton density functions \texttt{MMHT2014LO} (LHAPDF ID: $25000$) is used, whereas for $\sigma^{\mathrm{NLO}}$ \texttt{MMHT2014NLO} (LHAPDF ID: $25100$) is used.}\label{tab:MRSSMKfactors}
+For the calulation of $\sigma^{\mathrm{LO}}$ \texttt{MMHT2014LO} (LHAPDF ID: $25000$) are used as parton density functions, whereas for $\sigma^{\mathrm{NLO}}$ \texttt{MMHT2014NLO} (LHAPDF ID: $25100$) are used.}\label{tab:MRSSMKfactors}
 \end{center}
 \end{table}
-It can be seen that the $K$-factors depend strongly on the ratio $\frac{m_{\tilde{q}}}{m_{\tilde{g}}}$ but not that strongly on the masses itself.
+It can be seen that the $K$-factors depend strongly on the ratio $\frac{m_{\tilde{q}}}{m_{\tilde{g}}}$ but not that strongly on the masses themselves.
 This is also depicted in fig.
@@
 Figure \ref{fig:1LXsection_fixed_m_MSSM} shows the $K$-factors for squark production in the MSSM, broken down to $K$-factors for ``chirality'' like ($\tilde{u}_L \tilde{u}_L$) and unlike squarks ($\tilde{u}_L \tilde{u}_R$).
-It can be seen, that the mass dependence of $K(pp \to \tilde{u}_L \tilde{u}_R)$ in the MSSM is quite similar to the one in the MRSSM and that the MSSM $K$-factors are slightly smaller than in the MSSM.
+It can be seen, that the mass dependence of $K(pp \to \tilde{u}_L \tilde{u}_R)$ in the MSSM is quite similar to the one in the MRSSM and that the $K$-factors are slightly smaller than in the MSSM.
 However, the $K$-factors for ``chirality'' like squarks are distinctly larger.
@@
 \end{figure}
-Again, it is clearly visible that the $K$-factors depend rather strongly on the ratio $\frac{m_{\mathrm{g}}}{m_{\mathrm{q}}}$ but not so much on the masses itself (see also fig.
+Again, it is clearly visible that the $K$-factors depend rather strongly on the ratio $\frac{m_{\mathrm{g}}}{m_{\mathrm{q}}}$ but not that strongly on the masses themselves (see also fig.
 \ref{fig:Kfactor_MSSM}).
@@
 Comparing with the results from the MRSSM in table \ref{tab:MRSSMKfactors}, one can state that the $K$-factors of the MRSSM are slightly larger.
-This might be the case, as there are additional degrees of freedom in the $R$-symmetric model, namely the octino which enters the gluino self-energy contributions (see second diagram from the right in \ref{fig:GluinoSE}) and sgluons which enter box diagrams (see lower right diagram in \ref{fig:1loopdiagrams}).
+This might be the case, as there are additional degrees of freedom in the $R$-symmetric model, namely the octino which enters the gluino self-energy contributions (see second diagram from the right in fig.
+\ref{fig:GluinoSE}) and sgluons which enter box diagrams (see lower right diagram in fig.
+\ref{fig:1loopdiagrams}).
 The dependence on the sgluon mass is discussed within the next section.\\
 The uncertainties of next-to-leading order cross sections, due to the phase space integration, within this section are of percent order.
-The uncertainty which corresponds to the scale variation does not increase 15\%.
+The uncertainty which corresponds to the scale variation does not exceed 15\%.
 

### 2016-07-13 RSymmetry.tex
Becky's remarks

@@
 These occur for the following reason.\\
-In the MSSM the gauginos are Majorana particles. Their mass terms  reads in 2-spinor notation
+In the MSSM the gauginos are Majorana particles. Their mass terms  reads in two-spinor notation
 \begin{align}
@@
 \end{align}
-where $\chi$ is another Weyl-spinor. This means that the four-spinor of every gaugino is a Dirac- instead of a Majorana-spinor, e.g. for the gluino:
+where $\chi$ is another Weyl spinor. This means that the four-spinor of every gaugino is a Dirac  instead of a Majorana spinor, e.g. for the gluino:
 \begin{align}
@@
 \end{align}
-In order to get a $R$-symmetric mass term on has to choose the $R$-charge of the new Weyl-spinor $\chi$ to be the opposite of $\lambda$.\\
+In order to get a $R$-symmetric mass term on has to choose the $R$-charge of the new Weyl spinor $\chi$ to be the opposite of $\lambda$.\\
 This explains the necessity of enlarging the field content if one imposes $R$-symmetry.\\
@@
 \end{align}
-Observe that there is no 3 sgluon vertex, because of the antisymmetry of the structure constants $f^{abc}$.
+Observe that there is no three sgluon vertex, because of the antisymmetry of the structure constants $f^{abc}$.
 As already alluded to there are two distinct sgluons with different masses.

### 2016-07-13 Renormalization.tex
Becky's remarks

@@
 This section discusses the removal of ultraviolet divergences in the amplitude of squark production at 1-loop level in the RSQCD.
-After a very brief introduction and discussion of the regularization schemes, field and mass renormalization constants are calculated, using dimensional regularization, in the on-shell scheme.
+After a very brief introduction and discussion of the regularization schemes, field and mass renormalization constants are calculated in the on-shell scheme, using dimensional regularization.
 After that, the renormalization constant of the strong gauge coupling $g_s$ is computed in a mixture of $\overline{\mathrm{MS}}$- and zero-momentum subtraction scheme.
@@
 \begin{align}
-Z = 1 + \delta Z \hspace{3cm} o_{\mathrm{bare}} = o + \delta o
-\end{align}
-where $Z$ and $o$ are defined by the multiplicative renormalization transformation, introduced in eq.
+Z = 1 + \delta Z \hspace{3cm} o_{\mathrm{bare}} = o + \delta o\label{eq:renconst}
+\end{align}
+where $Z$ and $o_{\mathrm{bare}}$ are defined by the multiplicative renormalization transformation, introduced in eq.
 \eqref{eq:fieldtrafo} and \eqref{eq:parametertrafo}.
 The field and mass renormalization constants have been calculated in DREG in the on-shell scheme.
-This has the advantage that when turning to the cross section no modification of the Green function to the S-matrix element has to be done.
+The advantage of this is that when turning to the cross section no modification of the Green function to the S-matrix element has to be done.
 This is discussed in more detail in section \ref{sec:LSZ}.\\
@@
 \subsubsection*{The Squark Self-Energy}
-The contributions to the self-energy, shown in fig.
-\ref{fig:SquarkSE}, of the left- and right-handed squark are the same because electroweak effects are neglected.
+The contributions to the self-energy of the left- and right-handed squark, shown in fig.
+\ref{fig:SquarkSE}, are the same because electroweak effects are neglected.
 Therefore to avoid unnecessary labeling $\Gamma_{\tilde{q}\tilde{q}^\dagger}$ stands in the following for $\Gamma_{\tilde{q}_L\tilde{q}_L^\dagger} = \Gamma_{\tilde{q}_R\tilde{q}_R^\dagger}$.
@@
 The left-handed part $\lambda^a$ is associated with the superpartner of the gluon and therefore the ``actual'' gluino whereas the right-handed part $\overline{\chi}^a$ was introduced to assign a Dirac-mass to the gluino and may be referred to as the octino.\\
-From the Lagrangian \eqref{eq:L_RSQCD} one can see that the couplings of the two particles are quite distinct.
+From the Lagrangian in eq.
+\eqref{eq:L_RSQCD} one can see that the couplings of the two particles are quite distinct.
 This is reflected by different field renormalization constants of the left- and right-handed part of the gluino (see eq.
@@
 \end{tikzpicture}
-\caption{diagrammatic contributions to the self-energy of the squark at 1-loop level}\label{fig:GluinoSE}
+\caption{Diagrammatic contributions to the self-energy of the squark at 1-loop level}\label{fig:GluinoSE}
 \end{center}
@@
 \end{align}
-Where $\delta Z^R_{\tilde{g}}$ drops out already in $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ as the octino does neither couple to quarks nor to squarks.
+$\delta Z^R_{\tilde{g}}$ drops out already in $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ as the octino does neither couple to quarks nor to squarks.
 The renormalization constant of the actual gluino $\delta Z^L_{\tilde{g}}$ drops out when $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ and $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}}$ are added.
@@
 This may be understood in the path integral approach of quantum field theory\cite{Peskin}: When considering a certain process, the Green function corresponding to this process, can be expressed as a path integral over fields within the theory.
-The field of virtual particles occurs, in contrast to the fields of external particles, only in the exponential.
-This means, that rescaling a field of an inner particle has no influence on the Green function.
+The field of virtual particles occurs only in the exponential, in contrast to the fields of external particles.
+This means that rescaling a field of an inner particle has no influence on the Green function.
 Ergo the field renormalization constants of any virtual particle must always drop out when considering a certain process.
@@
 The quark self-energy has two contributions which are shown in figure \ref{fig:QuarkSelfEnergy}.
-The first one corresponds to light particles the second one to heavy particles: $i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j} = i\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j} + i\Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}$.
+The first one corresponds to light particles and the second one to heavy particles: $i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j} = i\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j} + i\Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}$.
 For light particles only the UV-divergent\footnote{In contrast to the MS-scheme in the $\overline{\mathrm{MS}}$-scheme not only the pure ultraviolet divergence but also two additional transcendent numbers are subtracted.
@@
 	\draw[gluon](0:0.5)--(0:1.3);
+	\node at (1.8,0) {+};
 \end{scope}
@@
 \end{tikzpicture}
-\caption{Contribution to the self-energy of the gluon originating from light particles}\label{fig:lightGluonSelfEnergy}
+\caption{Contribution to the self-energy of the gluon originating from light particles.}\label{fig:lightGluonSelfEnergy}
 \end{center}
@@
 \subsubsection*{The Gluon Self-Energy}
-As for the quark self-energy there are again contributions to the self-energy originating from light and heavy particles.
+As for the quark self-energy, there are again contributions to the self-energy of the gluon originating from light and heavy particles.
 Again these are differently dealt with.
@@
 \end{tikzpicture}
-\caption{Contribution to the self-energy of the gluon originating from heavy particles, in the last diagram either $\phi^0$ or $\sigma^0$ are running in the loop}
+\caption{Contribution to the self-energy of the gluon originating from heavy particles, in the last diagram either $\phi^0$ or $\sigma^0$ are running in the loop.}
 \end{center}
@@
 \end{tikzpicture}
-\caption{Contribution from light (Standard Model) particles to the $q\overline{q}G$ vertex correction}\label{fig:GaugeCouplingCorrectionL}
+\caption{Contribution from light (Standard Model) particles to the $q\overline{q}G$ vertex correction.}\label{fig:GaugeCouplingCorrectionL}
 \end{center}
@@
 &\hspace{3.3cm} + \left. C(A)\left( B_0(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2) -2C_{00}(0, 0, 0, m_{\tilde{g}}^2, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\right) \right]\nonumber\\
-&= ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} 2C(F)B_1(0,m_{\tilde{g}}^2,m_{\tilde{q}}^2).
-\end{align}
-The argument $p_i^2=0$ of the vertex function denotes, that all external particles are taken on shell, i.e. at zero momentum.\\
-In the second line identities from \ref{sec:Passarino} have been used. The renormalization condition for the counterterm of the gauge coupling $\delta g_s$ reads
+&= ig_s T^a_{ij} \gamma^\mu \frac{g_s^2}{16\pi^2} 2C(F)B_1(0,m_{\tilde{g}}^2,m_{\tilde{q}}^2).\label{eq:something}
+\end{align}
+The argument $p_i^2=0$ of the vertex function denotes that all external particles are taken on shell, i.e. at zero momentum.\\
+In the second line of eq. \eqref{eq:something} identities from section \ref{sec:Passarino} have been used. The renormalization condition for the counterterm of the gauge coupling $\delta g_s$ reads
 \begin{align}
@@
 Writing down the action of a theory in $D$ dimensions, one needs to introduce an energy scale $\mu$ in order to keep the action dimensionless.
-But $\mu$ is no physical parameter but can be absorped into the fields and parameters.
-To this end one defines the bare coupling
+For $\mu$ not being a physical parameter it can be absorbed into the fields and parameters.
+To this end, one defines the bare coupling
 \begin{align}
@@
 This is the $\beta$ function of QCD first found by Politzer \cite{Politzer:1973fx}, Gross and Wilczek \cite{Gross:1973ju}.
-This means that renormalizing $g_s$ in the way it is, decouples heavy particles from the $\beta$ function and allows to adopt $\alpha_s = \frac{g_s^2}{4\pi}$ from the parton density functions.
+This means that renormalizing $g_s$ in the way it is decouples heavy particles from the $\beta$ function and allows to adopt $\alpha_s = \frac{g_s^2}{4\pi}$ from the parton density functions.
 
 \subsection{Supersymmetry Restoring Counterterm}\label{sec:SUSYrestore}
-As already discussed in section \ref{sec:RegSchemeDep} care is required in terms of supersymmetry restoring when renormalizing  the gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$.
+As already discussed in section \ref{sec:RegSchemeDep}, care is required in terms of supersymmetry restoring when renormalizing  the gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$.
 In doing so one needs the already calculated transition counterterms of the quark, squark and gluino from eq.
@@
 \subsubsection*{The $q\overline{q}G$ Vertex Correction Revisited}
-The diagrams from which the supersymmetry restoring contributions to the $q\overline{q}G$ vertex come, are shown in figure \ref{fig:GaugeCouplingCorrection} and evaluate to
+The diagrams from which the supersymmetry restoring contributions to the $q\overline{q}G$ vertex come from are shown in figure \ref{fig:GaugeCouplingCorrectionL} and evaluate to
 \begin{align}
@@
 \subsubsection*{The $\tilde{q}_L\overline{q}\tilde{g}$ Vertex Correction}
-The supersymmetry restoring corrections to the $\tilde{q}_L \overline{q}\tilde{g}$ originate from the diagram in figure \ref{fig:YukawaCT}.
+The supersymmetry restoring corrections to the $\tilde{q}_L \overline{q}\tilde{g}$ vertex originate from the diagram in figure \ref{fig:YukawaCT}.
 \begin{figure}[!htbp]
@@
 \end{align}
-In short this means that the gauge coupling $g_s$ is renormalized with $\delta g_s$ given in \eqref{eq:deltaGs} and the Yukawa coupling $\hat{g}_s$ is renormilzed with $\delta \hat{g}_s = \delta g_s + \delta g_s^{\mathrm{restore}}$.\\
+In short, this means that the gauge coupling $g_s$ is renormalized with $\delta g_s$ given in eq.
+\eqref{eq:deltaGs} and the Yukawa coupling $\hat{g}_s$ is renormalized with $\delta \hat{g}_s = \delta g_s + \delta g_s^{\mathrm{restore}}$.\\
 The finite correction $\delta g_s^{\mathrm{restore}}$ is the same as in supersymmetric QCD which should not surprise too much as all its contributions originate from loops with gluons.% So there are no new contributions in RSQCD with respect to SQCD.
@@
 To check quickly for UV-finiteness of a Greenfunction or a physical observable it is useful to have the extracted UV-divergences of the renormalization constants at hand.
-How these are obtained is described in \ref{sec:Passarino} and evaluate to
+How these are obtained is described in section \ref{sec:Passarino}.
+They evaluate to:
 \begin{align}
@@
 \subsection{The Renormalization of the Matrix Element}\label{sec:MatrixElRen}
-This section explains how the renormalization of the matrix element of squark production is implemented in the framework of the automated calculation and gives intermediate results in the form of the renormalized matrix element.
+This section explains how the renormalization of the matrix element of squark production is implemented in the framework of the automated calculation and gives intermediate results in form of the renormalized matrix element.
 
 \subsubsection{Implementation into the Model File}\label{sec:ModelFileImplementation}
-Within the automated calculation, the renormalization of the matrix element of squark production has been achieved by extending the model file, generated by \texttt{SARAH} with counterterm Feynman rules and renormalization constants.\\
+Within the automated calculation, the renormalization of the matrix element of squark production has been achieved by extending the model file generated by \texttt{SARAH} with counterterm Feynman rules and renormalization constants.\\
 The derivation of the counterterm Feynman rules has been performed by the author whereas the implementation into the model file was mainly done by Philip Dießner, another member of the group.
@@
 The syntax of the vertex, also described in \cite{FeynArtsManual}, is like $\left\{\left\{\mathrm{L},\mathrm{L}^{ct}\right\},\left\{\mathrm{R},\mathrm{R}^{ct}\right\}\right\}$, where the shortcuts are explained in table \ref{tab:Modelfille}.
-The names of the particles within the model are given in the \texttt{FeynArts} manual\cite{FeynArtsManual} when  \texttt{MSSMQCD.mod}, the QCD extention of the MSSM model file is explained:\\ 
+The names of the particles within the model are given in the \texttt{FeynArts} manual\cite{FeynArtsManual} when  \texttt{MSSMQCD.mod}, the QCD extention of the MSSM model file, is explained.\\ 
 However, \mbox{\texttt{F[3,$\left\{ \right.$gt1, ct1$\left.\right\}$]}} is an up-type quark of the \texttt{gt1}'th generation with color \texttt{ct1} and \texttt{F[15,$\left\{ \right.$ct2$\left.\right\}$]} is a gluino with color \texttt{ct2}.
@@
 Whereas the MSSM model file, \texttt{MSSMQCD.mod}, has three indices to label squarks, the model file generated by \texttt{SARAH} uses only two: \texttt{-S[13,$\left\{ \right.$ gt3, ct3$\left.\right\}$]} denotes an anti up-type squark of mass eigenstate \texttt{gt3} and color \texttt{ct3}.
-This means more specifically that \texttt{gt3}$\in \left\{ 1,2,3 \right\}$ labels the ``left-handed" squarks with increasing mass and \texttt{gt3}$\in \left\{ 4,5,6 \right\}$ the ``right-handed`'' squarks with increasing mass.
+This means more specifically that \texttt{gt3}$\in \left\{ 1,2,3 \right\}$ labels the ``left-handed" squarks with increasing mass and \texttt{gt3}$\in \left\{ 4,5,6 \right\}$ the ``right-handed'' squarks with increasing mass.
 \begin{table}[H]
@@
 The next block of the code provides the renormalization constants of up- and down-type squarks and the ensuing block deals with the gluino.
-Here, it is important to separate the calculation of the field renormalization constant of the left- and right-handed component of the Dirac-spinor by adding \texttt{[[$1$]]} or \texttt{[[$2$]]} at the end of \texttt{FieldRC[F[$15$]]} to pick the appropriate element of the list.\\
+Here it is important to separate the calculation of the field renormalization constant of the left- and right-handed component of the Dirac-spinor by adding \texttt{[[$1$]]} or \texttt{[[$2$]]} at the end of \texttt{FieldRC[F[$15$]]} to pick the appropriate element of the list.\\
 Finally, the gauge coupling renormalization and the supersymmetry restoring counterterm are implemented, before the gluon field is renormalized.
@@
 The respective poles of $\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})(uu \to \tilde{u}_L\tilde{u}_R)$ are shown in figure \ref{fig:MatrixElementPoles}.
-Observe, that the single pole is positive for all values of the Mandelstam variable $t$.
+Observe that the single pole is positive for all values of the Mandelstam variable $t$.
 This is because infrared integrals are rendered finite when $\epsilon<0$ \ignore{($D$ > 4)}.
@@
 \end{figure}\\
-Note, that the extraction of the single pole does not only involve setting the option \texttt{SetLamda} $\to-1$ and \texttt{Dminus4}$\to 0$, but also setting \texttt{SetLamda}$\to -2$ and \texttt{Dminus4} $\to -2$ and subtracting the term obtained by \texttt{SetLamda}$\to-2$ and \texttt{Dminus4} $\to 0$.
+Note that the extraction of the single pole does not only involve setting the option \mbox{\texttt{SetLamda} $\to-1$} and \texttt{Dminus4}$\to 0$, but also setting \texttt{SetLamda}$\to -2$ and \texttt{Dminus4} $\to -2$ and subtracting the term obtained by \texttt{SetLamda}$\to-2$ and \texttt{Dminus4} $\to 0$.
 In doing so, one accounts for the contraction of double poles with terms of $\mathcal{\epsilon}$.
@@
 Referring to eq.
-\eqref{eq:t}, this suggests that in this case, virtual corrections do enhance the differential cross section in all directions of the beam axis relatively uniformly.
+\eqref{eq:t}, this suggests that in this case virtual corrections do enhance the differential cross section in all directions of the beam axis relatively uniformly.
 \begin{figure}[!htpb]
@@
 \includegraphics[scale=.5]{figures/MatrixElement.png}
-\caption{The figure at the bottom shows the absolute squared matrix element of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM at tree-level with $\alpha_s(m_Z) = 0.135$ from the leading order parton density functions $\mathtt{MMHT2014}$, and $\alpha_s(m_Z) = 0.12$ from the next-to-leading order parton density function as well as the contribution from the virtual corrections to it.\newline
+\caption{The figure at the bottom shows the absolute squared matrix element of $uu \to \tilde{u}_L\tilde{u}_R$ in the MRSSM at tree-level with $\alpha_s(m_Z) = 0.135$ from the leading order parton density functions $\mathtt{MMHT2014}$ and $\alpha_s(m_Z) = 0.12$ from the next-to-leading order parton density function as well as the contribution from the virtual corrections to it.\newline
 The figure at the top shows the different contributions to the virtual corrections as well as their sum.

### 2016-07-13 Summary.tex
Becky's remarks

@@
 
-The Standard Model of particle physics describes the world's fundamental particles and the interactions among.
+The Standard Model of particle physics describes the world's fundamental particles and the interactions among them.
 It belongs to the best tested theory within physics but is on the other hand known to be incomplete.\\
@@
 Within this thesis, a specific supersymmetric extension of the Standard Model - the Minimal $R$-Symmetric Supersymmetric Standard Model (MRSSM) - is studied.
-This is particularly appealing from the point of view of symmetries because it comprises the maximal possible symmetry group, a reasonable quantum field theory can have.
-The theorem stating this, is the Haag-Laopuszanski-Sohnius theorem.
+This is particularly appealing from the point of view of symmetries because it comprises the maximal possible symmetry group a reasonable quantum field theory can have.
+The theorem stating this is the Haag-Laopuszanski-Sohnius theorem.
 In contrast to the common notion, supersymmetry alone does not extent the Poincaré symmetry to the largest possible symmetry group.
@@
 The cross sections and intermediate results are given explicitly for each process.
-In comparison with the corresponding processes in the MSSM, it has been found that gluino production is enhanced by about a factor of two for gluino and antigluino are distinguishable particles, as opposed to in the MSSM.
+In comparison to the corresponding processes in the MSSM, it has been found that gluino production is enhanced by a factor of about two because gluino and antigluino are distinguishable particles, as opposed to in the MSSM.
 In order to meet the absence of signals alluding to supersymmetry at the LHC, this suggests that gluinos might be heavier than squarks if they should be realized in that way in nature.
-Focusing on this regime of parameter space, it has been found that the production of squarks and gluinos in the MRSSM is significantly lower, than in the MSSM.
+Focusing on this regime of parameter space, it has been found that the production of squarks and gluinos in the MRSSM is significantly lower than in the MSSM.
 The most striking difference has been found in the production channel of squarks.
@@
 As this had not been done so far, it was not possible to use a tool like \texttt{MadGraph} or \texttt{Prospino} to perform the calculation.
-Instead, an own program needed to be devised to calculate the next-to-leading order cross section of squark production in the MRSSM in an automated way.\\
-To this end a model file, generated by \texttt{Sarah}, which serves only for leading order processes has been adjusted manually to incorporate counter term Feynman rules.
+Instead, a new program needed to be devised to calculate the next-to-leading order cross section of squark production in the MRSSM in an automated way.\\
+To this end, a model file generated by \texttt{Sarah}, which serves only for leading order processes, has been adjusted manually to incorporate counter term Feynman rules.
 At this point, Philip Dießner did a major contribution when the model file was changed.
 After this, the model file has been provided with appropriate renormalization constants which are explicitly given in the thesis.
-This includes also a supersymmetry restoring counterterm.
-By means of this model file, renormalized one-loop corrections to the matrix element of squark production has been calculated in \texttt{Mathematica}, using the packages \texttt{FeynArts} and \texttt{FormCalc}.
-After this, the virtual contributions, which have been checked for ultraviolet-finiteness have been passed to a \texttt{C++} code and have been evaluated using the \texttt{Looptools} package.
+This also includes  a supersymmetry restoring counterterm.
+By means of this model file, renormalized one-loop corrections to the matrix element of squark production have been calculated in \texttt{Mathematica}, using the packages \texttt{FeynArts} and \texttt{FormCalc}.
+After this, the virtual contributions, which have been checked for ultraviolet-finiteness, have been passed to a \texttt{C++} code and have been evaluated using the \texttt{Looptools} package.
 Finally, the phase space integration has been performed numerically using the \texttt{CUBA} library for parallelized numerical integration.
@@
 \end{tabular}
-\caption{Total hadronic cross section for the production of up-squarks in the MRSSM and the MSSM at leading order and next-to-leading order.
+\caption{Total hadronic cross section for the production of up-squarks through protons in the MRSSM and the MSSM at leading order and next-to-leading order.
 Also given are the $K$-factors.
@@
 As a result, the comparison of $K$-factors for squark production in the MRSSM and the MSSM showed that the very same are slightly larger in the MRSSM.
-But since the tree-level cross section of squark production in the MRSSM are, depending on the choice  of squark and gluino mass, about an order of magnitude smaller than in the MSSM, this renders the MRSSM to a perfectly viable extension of the Standard Model.\\
+But since the tree-level cross section of squark production in the MRSSM is, depending on the choice  of squark and gluino mass, about an order of magnitude smaller than in the MSSM, this renders the MRSSM to a perfectly viable extension of the Standard Model.\\
 Among other advantages to the MSSM, it explains a suppressed cross section for the production of supersymmetric particles at the LHC.

### 2016-07-13 Virt_Real.tex
Becky's remarks

@@
 \section{Virtual and Real Corrections}\label{sec:VirtRealCorr}
-The results calculated in the previous chapter are not the full theoretical predictions for the cross sections of the various processes but only the first term in a perturbation series of $\alpha_s$.\\
-To provide accurate predictions, it is necessary that correction to the leading order are small.
-This implies that $\alpha_s$, which depends strongly on the energy scale, needs to fulfill $\alpha_s < 1$.
-It is known that $\alpha_s$ becomes of $\mathcal{O}(1)$ and larger when the energy scale is of $\mathcal{O}(\unit[200]{MeV})$ and smaller.\cite{dissertori2003quantum} Fortunately squark production is a process which involves large enough energy to maintain the validity of perturbation theory as the typical energy scale involved, is the mass of squarks which certainly fulfills $m_{\tilde{q}} > \unit[500]{GeV}$.\\
+The results calculated in the previous chapter are not the complete theoretical predictions for the cross sections of the various processes but only the first term in a perturbation series of $\alpha_s$.\\
+To provide accurate predictions, it is necessary that corrections to the leading order are small.
+This implies that $\alpha_s$, which is strongly dependent on the energy scale, needs to fulfill $\alpha_s < 1$.
+It is known that $\alpha_s$ becomes of $\mathcal{O}(1)$ and larger when the energy scale is of $\mathcal{O}(\unit[200]{MeV})$ and smaller\cite{dissertori2003quantum}.
+Fortunately squark production is a process which involves large enough energy to maintain the validity of perturbation theory, as the typical energy scale involved, is the mass of squarks which certainly fulfills $m_{\tilde{q}} > \unit[500]{GeV}$.\\
 This section describes the necessary steps in the calculation of the squark production cross section at next-to-leading order, i.e. its $\mathcal{O}(\alpha_s)$-correction.\\
@@
 \ref{fig:1loopdiagrams}.
-To yield $\mathcal{O}(\alpha_s)$ corrections in the cross section, the interference term between the one-loop amplitude $\mathcal{M}^{\mathrm{1L}}$ and the Born amplitude $\mathcal{M}^{\mathrm{B}}$ needs to be considered.
+To yield $\mathcal{O}(\alpha_s)$ corrections in the cross section, the interference term between the one-loop amplitude $\mathcal{M}^{\mathrm{1L}}$ and the Born amplitude $\mathcal{M}^{\mathrm{B}}$ needs to be considered:
 \begin{align}
 \left| \mathcal{M}^{\mathrm{B}} + \mathcal{M}^{\mathrm{1L}} \right|^2 &= \left| \mathcal{M}^{\mathrm{B}} \right|^2 + \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} + \mathcal{M}^{\mathrm{1L}} \mathcal{M}^{\mathrm{B}\ast} + \left| \mathcal{M}^{\mathrm{1L}} \right|^2\nonumber\\
-&= \left| \mathcal{M}^{\mathrm{B}} \right|^2 + 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right) + \mathcal{O}(\mbox{2-loop})
+&= \left| \mathcal{M}^{\mathrm{B}} \right|^2 + 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right) + \mathcal{O}(\mbox{2-loop}).
 \end{align}
@@
 \end{figure}
-Due to their origin these divergences are referred to as ultraviolet (UV) or infrared divergences (IR).
+Due to their origin these divergences are referred to as ultraviolet (UV) or infrared (IR) divergences.
 Ultraviolet divergences occur when loop momenta and energy tend to infinity which corresponds to arbitrary short distance interactions.
@@
 Often infrared divergences are used as a synonym for soft divergences.
-The name soft and collinear divergences is explained within the next section} which cannot be removed by means of renormalization.
+The name soft and collinear divergences is explained within the next section.} which cannot be removed by means of renormalization.
 These additional singularities show up as single and double poles in $\epsilon$ in the matrix element $\mathcal{M^{\mathrm{1L}}}$ and the virtual cross section which is obtained after performing the 2-body phase space integration as in eq.
@@
 This is because one does not measure final state partons but jets, which consist of hadrons which in turn consist of partons.
-This means that the radiation of a massless particle whose energy tends to zero or the radiation of a particle which is collinear to one of the final state partons of the tree-level process can in experiment not be distinguished from the tree-level process, for both processes may give rise to the same number of jets.
+This means that the radiation of a massless particle whose energy tends to zero or the radiation of a particle which is collinear to one of the final state partons of the tree-level process can not be distinguished from the tree-level process in experiment, for both processes may give rise to the same number of jets.
 Ergo, the cross section of squark production at $\mathcal{O}(\alpha_s^3)$ is given by
@@
 \end{figure}\\
-To see how these are removed, consider the collinear limit \eqref{eq:collLimit}.
+To see how these are removed, consider the collinear limit in \eqref{eq:collLimit}.
 Within this limits the inner quark can almost be considered as on-shell which means that it may travel a long distance between the emission of a gluon and taking part in the actual interaction.
-This suggest that some divergences may come from the incoming hadron and are actually not associated with the hard interaction.
-In fact this turns out to be the case: The remaining collinear divergences have a generic form and can be absorbed into the parton density functions.
-Within the $\overline{\mathrm{MS}}$-scheme, the redefinition of parton density functions is given by:\cite{Harris:2001sx}
+This suggests that some divergences may come from the incoming hadron and are actually not associated with the hard interaction.
+In fact this turns out to be true: The remaining collinear divergences have a generic form and can be absorbed into the parton density functions.
+Within the $\overline{\mathrm{MS}}$-scheme, the redefinition of parton density functions is given by\cite{Harris:2001sx}:
 \begin{align}
@@
 This procedure of removing collinear divergences is referred to as mass factorization \cite{dissertori2003quantum}.\\
-In fact, apart from this removal of collinear divergences, the Kinoshita-Lee-Naunberg-Theorem \cite{1962JMP.....3..650K},\cite{PhysRev.133.B1549} guarantees the finiteness of sufficiently inclusive observables, i.e.
+In fact, apart from this removal of collinear divergences, the Kinoshita-Lee-Naunberg-Theorem \cite{1962JMP.....3..650K, PhysRev.133.B1549} guarantees the finiteness of sufficiently inclusive observables, i.e.
 the cancellation of soft divergences between virtual and real corrections.\\
@@
 	\path [line, line width = 1] (Mvirt) --node[right] {renormalization} (Mvirtren);
-	\node [block1b] at (0,-4) (svirtren) {$\sigma^{\mathrm{virt}}$ is IR-divergent};
-	\node [block2b] at (6,-4) (sreal) {$\sigma^{\mathrm{real}}$ is IR-divergent};
+	\node [block1b] at (0,-4) (svirtren) {$\sigma^{\mathrm{V}}$ is IR-divergent};
+	\node [block2b] at (6,-4) (sreal) {$\sigma^{\mathrm{R}}$ is IR-divergent};
 	\path [line, line width = 1] (Mvirtren) --node[right] {phase space integration} (svirtren);
 	\path [line, line width = 1] (Mreal) --node[right] {phase space integration} (sreal);
-	\node [block2b] at (6, -6) (srealfac) {$\sigma^{\mathrm{real}}$ is IR-divergent};
+	\node [block2b] at (6, -6) (srealfac) {$\sigma^{\mathrm{R}}$ is IR-divergent};
 	\path [line, line width = 1] (sreal) --node[right] {mass factorization} (srealfac);
-	\node [block3] at (3,-8) (snlo) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{virt}} + \sigma^{\mathrm{real}}$ is finite};
+	\node [block3] at (3,-8) (snlo) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}}$ is finite};
 	\path [line, line width = 1] (srealfac) -- (snlo);
@@
 Within the virtual corrections, UV-divergences of the loop diagrams are removed on the level of the matrix element.
-The matrix element of the real correction becomes singular within certain regions of phase space.
+The matrix element of the real corrections become singular within certain regions of phase space.
 Collinear divergences can be removed by mass factorization.
-After this the poles of virtual and real corrections add up to zero.}\label{fig:DivergenceSummary}
+After this, the poles of virtual and real corrections add up to zero.}\label{fig:DivergenceSummary}
 \end{center}
@@
 \eqref{eq:facTheorem} is free of soft (and collinear) divergences, also the right hand side has to be infrared finite.
-Furthermore, the renormalized parton density functions are free of soft divergences, so the partonic cross section in eq.
-\eqref{eq:facTheorem} needs also be be free of soft divergences.
+Furthermore, the renormalized parton density functions are free of soft divergences, that is why the partonic cross section in eq.
+\eqref{eq:facTheorem} also needs to be free of soft divergences.
 In other words, real corrections, coming from an initial state with quark and gluon, cannot contribute to the cancellation of soft divergences with virtual corrections which are associated with two quarks in the initial state.\\
 A split-up of space space in a soft and a hard part is therefore not needed.
-However, there are collinear singularities, originating from initial state radiation like shown in the last diagram of \ref{fig:quarkradiation}, which again have to be removed by means of mass factorization.\\
+However, there are collinear singularities, originating from initial state radiation like shown in the last diagram of fig.
+\ref{fig:quarkradiation}, which again have to be removed by means of mass factorization.\\
 But there is another complication: The first and second diagram in fig.

### 2016-07-15 Introduction.tex
COMMITTED VERSION

@@
 The Standard Model of particle physics is a quantum field theory which relies on the principle of gauge invariance.
-It describes the world's fundamental particles and the interactions among them and predicts the most accurately measured observables in physics.\\
-Besides these triumphs, it is known to be incomplete for example for not including dark matter or a description of gravity.
+It describes all known fundamental particles and the non-gravitational interactions among them and predicts the most accurately measured observables in physics.\\
+Besides these successes, it is known to be incomplete for example for not including dark matter or a description of gravity.
 Because of these and other flaws, one studies extensions of the Standard Model.
@@
 Within this framework one often studies the Minimal Supersymmetric Standard Model (MSSM).
-This theory provides a candidate for dark matter and elegant solutions of e.g.
+This theory may provide a candidate for dark matter and elegant solutions of e.g.
 the hierarchy problem.
-However the MSSM does not come without problems.
+However, the MSSM does not come without problems.
 One of these is that supersymmetric particles have not been discovered so far.
@@
 However, in order to still solve the hierarchy problem, supersymmetry breaking should not be too large.
-According to searches for supersymmetry at the Large Hadron Collider, supersymmetric particles are at the moment on the verge on being too heavy for the MSSM to solve the hierarchy problem without loosing its attractiveness.\\
-A non-trivial extension of supersymmetry - $R$-symmetry - may explain this and other issues.
-$R$-symmetry is, according to the Haag-Lopuszanski-Sohnius theorem, the only viable extension of the supersymmetry group of the MSSM.
+According to searches for supersymmetry at the Large Hadron Collider (LHC), supersymmetric particles are at the moment on the verge of being too heavy for the MSSM to solve the hierarchy problem without losing its attractiveness.\\
+A non-trivial extension of supersymmetry -- $R$-symmetry -- may explain this and other issues.
+$R$-symmetry is, according to the Haag-{\L}opusza\'nski-Sohnius theorem, the only conceivable extension of the symmetry group of the MSSM.
 This is, the combination of Poincaré symmetry, supersymmetry and $R$-symmetry is the maximal symmetry a reasonable quantum field theory can have.\\
-\ignore{Imposing supersymmetry and $R$-symmetry on the Standard Model, gives - according to the Haag-Lopuszanski-Sohnius theorem - the maximal symmetry group a reasonable quantum field theory can have.\\}
-Motivated be these facts, the Minimal $R$-Symmetric Supersymmetric Standard Model (MRSSM) is the subject of investigations within this thesis.
+\ignore{Imposing supersymmetry and $R$-symmetry on the Standard Model, gives - according to the Haag-{\L}opusza\'nski-Sohnius theorem - the maximal symmetry group a reasonable quantum field theory can have.\\}
+Motivated by these facts, the Minimal $R$-Symmetric Supersymmetric Standard Model (MRSSM) is the subject of investigations within this thesis.
 More specifically, the production cross section of strongly interacting supersymmetric particles in the MRSSM is studied.
+This is because within supersymmetry strongly interacting particles are the ones which are most likely to be produced at the LHC should supersymmetry at all be realized in nature.
 It will turn out that there are significant changes in the production of squarks and gluinos when turning from the MSSM to the MRSSM.\\
-This thesis starts with summarizing the main aspects of the Standard Model before the concept of supersymmetry and $R$-symmetry is introduced.
+This thesis starts with summarizing the main aspects of the Standard Model before the concepts of supersymmetry and $R$-symmetry are introduced.
 This includes the introduction of the models which incorporate the minimal form of the symmetry in question.
-Section \ref{sec:SquarkGluinoTree} compares the production cross section of squark and gluinos in both models at \mbox{tree-level}.
+Section \ref{sec:SquarkGluinoTree} compares the production cross sections of squarks and gluinos in both models at \mbox{tree-level}.
 After identifying an attractive region of parameter space in the MRSSM, it will turn out that the most interesting difference manifests in the channel of squark production.
-As there are no programs available with whom next-to-leading order cross sections within the MRSSM can be calculated, the rest of the thesis focuses on the next-to-leading order calculation of the squark production cross section.
-: Section \ref{sec:VirtRealCorr} discusses the golden thread of the calculation of a next-to-leading order cross section including massless external particles before section \ref{sec:renMRSSM} gives detailed information about the renormalization of the MRSSM.
-This includes the explicit form of required renormalization constants, reaching form the on-shell scheme over a mixture of $\overline{\mathrm{MS}}$- and zero-momentum subtraction scheme to supersymmetry restoring counterterms.
+As there are no computer programs available with whom next-to-leading order cross sections within the MRSSM can be calculated, the rest of the thesis focuses on the next-to-leading order calculation of the squark production cross section.
+Section \ref{sec:VirtRealCorr} outlines the structure of the calculation of a next-to-leading order cross section including massless external particles before section \ref{sec:renMRSSM} gives detailed information about the renormalization of the MRSSM.
+This includes the explicit form of required renormalization constants, reaching from the on-shell scheme over a mixture of $\overline{\mathrm{MS}}$- and zero-momentum subtraction scheme to supersymmetry restoring counterterms.
 This section also discusses how renormalized one-loop matrix elements are generated as an input for a program which calculates the squark production cross section in the MRSSM.
-The thesis closes with an explanation on how this very program is constructed and the representation of the next-to-leading order cross section for squark production in the form of $K$-factors.
+The thesis closes with an explanation of how this very program is constructed and the representation of the next-to-leading order cross section for squark production in the form of $K$-factors.
 

### 2016-07-15 MSSM.tex
COMMITTED VERSION

@@
 Ergo, the symmetry groups of the Standard Model are the most general ones.\\
-This statement was corrected by the Haag-Lopuszanski-Sohnius theorem \cite{Haag:1974qh} which weakened the condition of the quantum field theory by allowing also for anticommuting symmetry generators.
+This statement was corrected by the Haag-{\L}opusza\'nski-Sohnius theorem \cite{Haag:1974qh} which weakened the condition of the quantum field theory by allowing also for anticommuting symmetry generators.
 This is, by introducing the generators $Q_\alpha$ and $\overline{Q}^{\dot{\alpha}}$ with $\alpha, \dot{\alpha} \in \left\{ 1,2 \right\}$, the Poincare-algebra eq.
@@
 These are necessary to avoid an anomaly in the electroweak gauge symmetry and to give masses to both up- and down-type quarks \cite[page 8]{Martin:1997ns}.\\
-Note that the ``chirality'' of sfermions is understood to be the chirality of their superpartners. Of course scalar particles have no handedness.
-\begin{table}
+Note that the ``chirality'' of sfermions is understood to be the chirality of their superpartners. Of course scalar particles have no chirality.
+\begin{table}[H]
 \begin{center}

### 2016-07-15 Masterarbeit.tex
Summary chapter
K factor MSSM contour plot
COMMITTED VERSION

@@
   \begin{singlespace}\begin{center}\large
-   Master-Arbeit \\ zur Erlangung des Hochschulgrades \\ 
+   Masterarbeit \\ zur Erlangung des Hochschulgrades \\ 
    Master of Science \\ 
@@
 % abstract page
-\begin{center}\large\bfseries Summary\end{center}
-Abstract \\ 
-English: flaws of the SM\\
-motivation: aesthetic: Coleman-Mandula --> Haag-Lopuszanski-Sohnius-Theorem\\
-\vspace{20em}
-Abstract \\ 
-Deutsch \\
+%\begin{center}\large\bfseries Summary\end{center}
+\section*{\centering{Kurzdarstellung}}
+Im Streben der Physik, die fundamentalen Bausteine der Natur zu beschreiben, stellt die Ent\-wicklung des Standardmodells der Teilchenphysik einen Meilenstein dar.
+Dieses beschreibt alle bekannten Elementarteilchen sowie deren nicht-gravitative Wechselwirkungen.
+Neben diesen Erfolgen ist aber auch bekannt, dass es unvollständig ist, da es keine Gravitation oder dunkle Materie beinhaltet.
+Supersymmetrie ist eine attraktive Erweiterung des Standardmodells, weil sie viele Probelme desselben auf eine elegante Weise löst.\\
+Diese Arbeit untersucht eine supersymmetrische Erweiterung des Standardmodells welche zusätzlich $R$-symmetrisch ist.
+Neben der Berechnung von Wirkungsquerschnitten von stark wechelwirkenden supersymmetrischen Teilchen in der führenden Ordnung werden Einschleifen\-korrekturen zum Produktionswirkungsquerschnitt von Squarks in diesem Model berechnet und phenomenologisch ausgewertet.
+\vspace{10em}
+\section*{\centering{Abstract}}
+In the ambition of understanding the fundamental mechanisms of nature, the Standard Model of particle physics constitutes a cornerstone in physics.
+It describes all known elementary particles and their non-gravitational interactions.
+Besides these successes it is known to be incomplete since it does not include gravity or dark matter.
+Supersymmetry is an attractive extension of the Standard Model as it solves many problems of it elegantly.\\
+Within this thesis, a supersymmetric model which also exhibits $R$-symmetry is considered.
+Besides the calculation of tree-level cross sections for the production of strongly interacting supersymmetric particles, also one-loop corrections to the production cross section of squarks are calculated and phenomenologically analyzed.
 \newpage
@@
 \newpage
-\section{Summary and Outlook}
+\input{Summary}
 \newpage
+% Leerseite
+%\thispagestyle{empty}
+\cleardoublepage
+
+%\appendix
 \input{Appendix}
@@
 \bibliography{references}
+\newpage
+\section*{\centering{Acknowledgements}}
+First of all I like to thank Dominik Stöckinger who enthused me with theoretical particle physics and provided me with this interesting topic.
+In addition, he was always available for helping discussions whenever I was in need of them.\\
+Special thanks go to Philip Dießner and Wojciech Kotlarski, who contributed significantly to results within this thesis.
+In addition I like to thank them, Markus Bach, Thomas Kwasnitza, Josua Unger and Tom Steudtner for many valuable discussions and support regarding physical questions as well as programming issues and a pleasant atmosphere in the office.
+Furthermore, I like to give them thanks for proofreading this thesis.\\
+I am particularly grateful for Rebecca Schmidt's support within the last month which enabled me to focus on my thesis. In addition I like to thank her for proofreading.\\
+Last but not least I would like to thank my family. Without them my physics studies would by no means have been possible in the way they were.
 \newpage
@@
 \vspace*{45em}
-Vorname Nachname \par
+\par
+Sebastian Liebschner\\
 Dresden, Juli 2016

### 2016-07-15 RSymmetry.tex
COMMITTED VERSION

@@
 $R$-symmetry is an additional continuous symmetry which extends  supersymmetry in a non-trivial way.
-This is actually covered in the Haag-Lopuszanski-Sohnius theorem \cite{Haag:1974qh} but often concealed.\\
+This is actually covered in the Haag-{\L}opusza\'nski-Sohnius theorem \cite{Haag:1974qh} but often concealed.\\
 This section introduces $R$-symmetry and discusses briefly a minimal viable extension of the MSSM including $R$-symmetry, the MRSSM.

### 2016-07-15 Renormalization.tex
COMMITTED VERSION

@@
 \end{align}
-where $\Re (\hdots)$ denotes the real part of $\hdots$, one finds
+where $\Re (\hdots)$ denotes the real part of $(\hdots)$, one finds
 \begin{align}
@@
 \subsubsection*{The Squark Self-Energy}
-The contributions to the self-energy of the left- and right-handed squark, shown in fig.
-\ref{fig:SquarkSE}, are the same because electroweak effects are neglected.
-Therefore to avoid unnecessary labeling $\Gamma_{\tilde{q}\tilde{q}^\dagger}$ stands in the following for $\Gamma_{\tilde{q}_L\tilde{q}_L^\dagger} = \Gamma_{\tilde{q}_R\tilde{q}_R^\dagger}$.
-The one-particle irreducible Green function of the squark is given by
 \begin{figure}[!htbp]
@@
 \end{center}
-\end{figure}\\
+\end{figure}
+The contributions to the self-energy of the left- and right-handed squark, shown in fig.
+\ref{fig:SquarkSE}, are the same because electroweak effects are neglected.
+Therefore to avoid unnecessary labeling $\Gamma_{\tilde{q}\tilde{q}^\dagger}$ stands in the following for $\Gamma_{\tilde{q}_L\tilde{q}_L^\dagger} = \Gamma_{\tilde{q}_R\tilde{q}_R^\dagger}$.
+The one-particle irreducible Green function of the squark is given by
 \begin{align}
@@
 \end{figure}
-As for the quarks, the fermion (and momentum) flow in a diagram is from the right to the left. The one-particle irreducible Green function is given by
+As for the quarks, the fermion (and momentum) flow in a diagram is from the right to the left.
+The Feynman diagrams for the gluino self-energy are shown in \ref{fig:GluinoSE}.
+The one-particle irreducible Green function is given by
 \begin{align}
@@
 In fact the field renormalization constants of the gluino are not needed as they drop out when summing up all three counterterm Feynman diagrams.
-This can be seen when writing down the matrix amplitudes for the counterterm Feynman diagrams shown in fig.
-\ref{fig:CounterTerm}:
-\begin{align}
-\mathcal{M}^{\mathrm{B}} &= -2g_s^2 \frac{\left\langle v_2 |P_R \slashed{k}_3|u_1\right\rangle}{t_{\tilde{g}}} T^a_{\delta \beta} T^a_{\gamma \alpha} + 2g_s^2 \frac{\left\langle v_2 |P_L \slashed{k}_3|u_1\right\rangle}{u_{\tilde{g}}} T^a_{\gamma\beta} T^a_{\delta\alpha}\\
-\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}} &= 2 \mathcal{M}^B  \left( \frac{\delta \hat{g}_s}{\hat{g}_s} + \frac{\delta Z_q}{2} + \frac{\delta Z^L_{\tilde{g}}}{2} + \frac{\delta Z_{\tilde{q}}}{2} \right)\\
-\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}} &= 2g_s^2 \left\langle v_2 \left| P_R\ i\frac{\slashed{p}+m_{\tilde{g}}}{t_{\tilde{g}}} \left[  i(\delta Z_{\tilde{g}}^L P_L + \delta Z_{\tilde{g}}^R P_R)\slashed{p}  \right.\right.\right.\nonumber\\
-& \hspace{2cm}\left.\left.\left.\left.
--i\left( \frac{\delta Z_{\tilde{g}}^L + \delta Z_{\tilde{g}}^R}{2}m_{\tilde{g}} + \delta m_{\tilde{g}} \right) \right]i\frac{\slashed{p}+m_{\tilde{g}}}{t_{\tilde{g}}} P_L \right|u_1\right\rangle\right|_{p = p_1-p_3} + \mathrm{u-channel}\nonumber\\
-&= -\mathcal{M}^B  \delta Z_{\tilde{g}}^L + 2  \frac{ m_{\tilde{g}}}{t_{\tilde{g}}} \left( -2g_s^2 \frac{\left\langle v_2 |P_R \slashed{k}_3|u_1\right\rangle}{t_{\tilde{g}}} T^a_{\delta \beta} T^a_{\gamma \alpha} \right)\delta m_{\tilde{g}}\nonumber\\
-& \hspace{2cm}+ 2 \frac{ m_{\tilde{g}}}{u_{\tilde{g}}} \left( 2g_s^2 \frac{\left\langle v_2 |P_L \slashed{k}_3|u_1\right\rangle}{u_{\tilde{g}}} T^a_{\gamma\beta} T^a_{\delta\alpha} \right)\delta m_{\tilde{g}}.
-\end{align}
-$\delta Z^R_{\tilde{g}}$ drops out already in $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ as the octino does neither couple to quarks nor to squarks.
-The renormalization constant of the actual gluino $\delta Z^L_{\tilde{g}}$ drops out when $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ and $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}}$ are added.
-This is also true in a more general case, i.e.
-the renormalization constants of virtual particles do always drop out.
-This may be understood in the path integral approach of quantum field theory\cite{Peskin}: When considering a certain process, the Green function corresponding to this process, can be expressed as a path integral over fields within the theory.
-The field of virtual particles occurs only in the exponential, in contrast to the fields of external particles.
-This means that rescaling a field of an inner particle has no influence on the Green function.
-Ergo the field renormalization constants of any virtual particle must always drop out when considering a certain process.
-\begin{figure}[!htbp]
+\begin{figure}[H]
 \begin{center}
@@
 \end{figure}
+This can be seen when writing down the matrix amplitudes for the counterterm Feynman diagrams shown in fig. \ref{fig:CounterTerm}:
+\begin{align}
+\mathcal{M}^{\mathrm{B}} &= -2g_s^2 \frac{\left\langle v_2 |P_R \slashed{k}_3|u_1\right\rangle}{t_{\tilde{g}}} T^a_{\delta \beta} T^a_{\gamma \alpha} + 2g_s^2 \frac{\left\langle v_2 |P_L \slashed{k}_3|u_1\right\rangle}{u_{\tilde{g}}} T^a_{\gamma\beta} T^a_{\delta\alpha}\\
+\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}} &= 2 \mathcal{M}^B  \left( \frac{\delta \hat{g}_s}{\hat{g}_s} + \frac{\delta Z_q}{2} + \frac{\delta Z^L_{\tilde{g}}}{2} + \frac{\delta Z_{\tilde{q}}}{2} \right)\\
+\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}} &= 2g_s^2 \left\langle v_2 \left| P_R\ i\frac{\slashed{p}+m_{\tilde{g}}}{t_{\tilde{g}}} \left[  i(\delta Z_{\tilde{g}}^L P_L + \delta Z_{\tilde{g}}^R P_R)\slashed{p}  \right.\right.\right.\nonumber\\
+& \hspace{2cm}\left.\left.\left.\left.
+-i\left( \frac{\delta Z_{\tilde{g}}^L + \delta Z_{\tilde{g}}^R}{2}m_{\tilde{g}} + \delta m_{\tilde{g}} \right) \right]i\frac{\slashed{p}+m_{\tilde{g}}}{t_{\tilde{g}}} P_L \right|u_1\right\rangle\right|_{p = p_1-p_3} + \mathrm{u-channel}\nonumber\\
+&= -\mathcal{M}^B  \delta Z_{\tilde{g}}^L + 2  \frac{ m_{\tilde{g}}}{t_{\tilde{g}}} \left( -2g_s^2 \frac{\left\langle v_2 |P_R \slashed{k}_3|u_1\right\rangle}{t_{\tilde{g}}} T^a_{\delta \beta} T^a_{\gamma \alpha} \right)\delta m_{\tilde{g}}\nonumber\\
+& \hspace{2cm}+ 2 \frac{ m_{\tilde{g}}}{u_{\tilde{g}}} \left( 2g_s^2 \frac{\left\langle v_2 |P_L \slashed{k}_3|u_1\right\rangle}{u_{\tilde{g}}} T^a_{\gamma\beta} T^a_{\delta\alpha} \right)\delta m_{\tilde{g}}.
+\end{align}
+$\delta Z^R_{\tilde{g}}$ drops out already in $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ as the octino does neither couple to quarks nor to squarks.
+The renormalization constant of the actual gluino $\delta Z^L_{\tilde{g}}$ drops out when $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ and $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}}$ are added.
+This is also true in a more general case, i.e.
+the renormalization constants of virtual particles do always drop out.
+This may be understood in the path integral approach of quantum field theory\cite{Peskin}: When considering a certain process, the Green function corresponding to this process, can be expressed as a path integral over fields within the theory.
+The field of virtual particles occurs only in the exponential, in contrast to the fields of external particles.
+This means that rescaling a field of an inner particle has no influence on the Green function.
+Ergo the field renormalization constants of any virtual particle must always drop out when considering a certain process.
 
@@
 
+\subsubsection*{The Gluon Self-Energy}
 \begin{figure}[!htbp]
@@
 \end{figure}
-
-\subsubsection*{The Gluon Self-Energy}
-As for the quark self-energy, there are again contributions to the self-energy of the gluon originating from light and heavy particles.
-Again these are differently dealt with.
-The ultraviolet divergent one-particle irreducible Green function is given by
-\begin{align}
-\left.i\Gamma^{\mathrm{1L,light}}_{G_\mu^a G_\nu^b}\right|_{\mathrm{UV-div}} &= i\frac{g_s^2}{16\pi^2}\Delta_\epsilon \left[ 0 - \frac{4 (n_{f}-1)}{3} T(F) (p^2g^{\mu\nu}-p^\mu p^\nu) + \frac{C(A)}{12}(p^2g^{\mu\nu} + 2 p^\mu p^\nu) \right.\nonumber\\
-&+\left. \frac{C(A)}{12}(19 p^2g^{\mu\nu} - 22 p^\mu p^\nu) \right]\delta_{ab}\nonumber\\
-&=i\frac{g_s^2}{16\pi^2} \Delta_\epsilon \left[ - \frac{4 (n_{f}-1)}{3} T(F) + \frac{5}{3} C(A) \right](p^2g^{\mu\nu}-p^\mu p^\nu)\delta_{ab}.
-\end{align}
-Both the contribution from the gluon loop and the one from the ghost loop are not proportional to $(p^2g^{\mu\nu}-p^\mu p^\nu)$ but their sum is.
-This transversal form is an implication of gauge invariance\cite{dissertori2003quantum}.
 \begin{figure}[!htbp]
@@
 \end{figure}
+As for the quark self-energy, there are again contributions to the self-energy of the gluon originating from light and heavy particles.
+Again these are differently dealt with.
+The ultraviolet divergent one-particle irreducible Green function is given by
+\begin{align}
+\left.i\Gamma^{\mathrm{1L,light}}_{G_\mu^a G_\nu^b}\right|_{\mathrm{UV-div}} &= i\frac{g_s^2}{16\pi^2}\Delta_\epsilon \left[ 0 - \frac{4 (n_{f}-1)}{3} T(F) (p^2g^{\mu\nu}-p^\mu p^\nu) + \frac{C(A)}{12}(p^2g^{\mu\nu} + 2 p^\mu p^\nu) \right.\nonumber\\
+&+\left. \frac{C(A)}{12}(19 p^2g^{\mu\nu} - 22 p^\mu p^\nu) \right]\delta_{ab}\nonumber\\
+&=i\frac{g_s^2}{16\pi^2} \Delta_\epsilon \left[ - \frac{4 (n_{f}-1)}{3} T(F) + \frac{5}{3} C(A) \right](p^2g^{\mu\nu}-p^\mu p^\nu)\delta_{ab}.
+\end{align}
+Both the contribution from the gluon loop and the one from the ghost loop are not proportional to $(p^2g^{\mu\nu}-p^\mu p^\nu)$ but their sum is.
+This transversal form is an implication of gauge invariance\cite{dissertori2003quantum}.
+
 The heavy particle contributions are calculated in the zero-momentum subtraction:
@@
 	\draw[fermionbar](45:0.5)--(45:1.3);
-	\draw[fermionbar](-45:0.5)--(-45:1.3);
+	\draw[fermion](-45:0.5)--(-45:1.3);
 	\node at (1.8,0) {=};
@@
 	\node at (0,0.5) {$q$};
-	\draw[fermionbar](180:0.5)--(-45:0.5);
+	\draw[fermion](180:0.5)--(-45:0.5);
 	\node at (0,-0.5) {$q$};
@@
 	\draw[fermionbar](45:0.5)--(45:1.3);
-	\draw[fermionbar](-45:0.5)--(-45:1.3);
+	\draw[fermion](-45:0.5)--(-45:1.3);
 	\node at (1.8,0) {+};
@@
 	\draw[fermionbar](45:0.5)--(45:1.3);
-	\draw[fermionbar](-45:0.5)--(-45:1.3);
+	\draw[fermion](-45:0.5)--(-45:1.3);
 \end{scope}
@@
 	\node at (0,0.5) {$\tilde{q}$};
-	\draw[scalarbar](180:0.5)--(-45:0.5);
+	\draw[scalar](180:0.5)--(-45:0.5);
 	\node at (0,-0.5) {$\tilde{q}$};
@@
 The derivation of the counterterm Feynman rules has been performed by the author whereas the implementation into the model file was mainly done by Philip Dießner, another member of the group.
-To explain the implementation, the code extract describing the quark-squark-gluino vertex is considered, as an example.
+To explain the implementation, the code extract describing the quark-squark-gluino vertex is considered as an example.
 \begin{lstlisting}[style=MyMathematica]
@@
 To display how the \texttt{FormCalc} output looks like, the following box shows the off-shell amplitude of the up-quark self-energy in terms of loop integrals and \texttt{Dminus4}.
-\begin{lstlisting}[style=MyMathematicaOutput]
+\begin{lstlisting}[style=MyMathematica]
 Amp[{{F[3, {1, Col1}], k[1], 0, {}}} -> {{F[3, {1, Col2}], k[2], 0, {}}}]

### 2016-07-15 Standardmodel.tex
COMMITTED VERSION

@@
 \section{The Standard Model}
-The Standard Model of particle physics is the commonly accepted theory describing the world's fundamental particles and their interactions.
+The Standard Model of particle physics is the commonly accepted theory describing all known fundamental particles and their non-gravitational interactions.
 It is a gauge quantum field theory and therefore characterized by its invariance under symmetry groups.

### 2016-07-15 Summary.tex
COMMITTED VERSION

@@
 
-The Standard Model of particle physics describes the world's fundamental particles and the interactions among them.
-It belongs to the best tested theory within physics but is on the other hand known to be incomplete.\\
+The Standard Model of particle physics describes all known fundamental particles and the non-gravitational interactions among them.
+It belongs to the best tested theories within physics but is on the other hand known to be incomplete.\\
 Supersymmetry provides an attractive extension of the Standard Model.
-Within this thesis, a specific supersymmetric extension of the Standard Model - the Minimal $R$-Symmetric Supersymmetric Standard Model (MRSSM) - is studied.
+Within this thesis, a specific supersymmetric extension of the Standard Model -- the Minimal $R$-Symmetric Supersymmetric Standard Model (MRSSM) -- is studied.
 This is particularly appealing from the point of view of symmetries because it comprises the maximal possible symmetry group a reasonable quantum field theory can have.
-The theorem stating this is the Haag-Laopuszanski-Sohnius theorem.
+The theorem stating this is the Haag-{\L}opusza\'nski-Sohnius theorem.
 In contrast to the common notion, supersymmetry alone does not extent the Poincaré symmetry to the largest possible symmetry group.
@@
 This thesis introduces an $R$-symmetric model in its minimal form.
-$R$-symmetry forbids terms which are allowed in the Minimal Supersymmetric Standard Model (MSSM).
-This includes the $A$-terms and the $\mu$-term which are responsible for squark mixing and flavor changing processes.
-But $R$-symmetry also prohibits Majorana mass terms for the gauginos.
-To be phenomenological viable, the MRSSM needs to accomodate Dirac gauginos.
-This requires the gauge sector of this model to be a $N=2$ supersymmetric theory which in turn implies further degrees of freedom.\\
-Focusing on the strongly coupling sector, there is, apart from the ``usual'' gluino, another fermionic degree of freedom which is referred to the octino.
+$R$-symmetry forbids some of the terms which are allowed in the Minimal Supersymmetric Standard Model (MSSM).
+These include the $A$-terms and the $\mu$-term which are responsible for squark mixing and flavor changing processes.
+Furthermore, $R$-symmetry also prohibits Majorana mass terms for the gauginos.
+To be phenomenologically viable, the MRSSM needs to accommodate Dirac gauginos.
+This requires the gauge sector of this model to be an $N=2$ supersymmetric theory which in turn implies further degrees of freedom.\\
+Focusing on the strongly coupling sector, there is, apart from the ``usual'' gluino, another fermionic degree of freedom which is referred to as octino.
 The superpartner of this right handed part of the strongly coupling gaugino is a spin-0 particle: the scalar gluon (sgluon).
@@
 The cross sections and intermediate results are given explicitly for each process.
-In comparison to the corresponding processes in the MSSM, it has been found that gluino production is enhanced by a factor of about two because gluino and antigluino are distinguishable particles, as opposed to in the MSSM.
-In order to meet the absence of signals alluding to supersymmetry at the LHC, this suggests that gluinos might be heavier than squarks if they should be realized in that way in nature.
-Focusing on this regime of parameter space, it has been found that the production of squarks and gluinos in the MRSSM is significantly lower than in the MSSM.
+In comparison to the corresponding processes in the MSSM, it has been found that gluino production is enhanced by a factor of about two because of gluino and antigluino being distinguishable particles, unlike in the MSSM.
+In order to meet the absence of signals alluding to supersymmetry at the Large Hadron Collider (LHC), this suggests that gluinos might be heavier than squarks if they should be realized as Dirac fermions in nature.
+Focusing on this regime of parameter space, it has been found that the production of squarks and gluinos in the MRSSM is significantly suppressed compared to the MSSM.
 The most striking difference has been found in the production channel of squarks.
@@
 Instead, a new program needed to be devised to calculate the next-to-leading order cross section of squark production in the MRSSM in an automated way.\\
-To this end, a model file generated by \texttt{Sarah}, which serves only for leading order processes, has been adjusted manually to incorporate counter term Feynman rules.
-At this point, Philip Dießner did a major contribution when the model file was changed.
+To this end, a model file generated by \texttt{Sarah}, which serves only for leading order processes, has been adjusted manually to incorporate counterterm Feynman rules.
+At this point, Philip Dießner contributed significantly by changing model file.
 After this, the model file has been provided with appropriate renormalization constants which are explicitly given in the thesis.
@@
 By means of this model file, renormalized one-loop corrections to the matrix element of squark production have been calculated in \texttt{Mathematica}, using the packages \texttt{FeynArts} and \texttt{FormCalc}.
-After this, the virtual contributions, which have been checked for ultraviolet-finiteness, have been passed to a \texttt{C++} code and have been evaluated using the \texttt{Looptools} package.
+After this, the virtual contributions, which had been checked for ultraviolet-finiteness, have been passed to a \texttt{C++} code and evaluated using the \texttt{Looptools} package.
 Finally, the phase space integration has been performed numerically using the \texttt{CUBA} library for parallelized numerical integration.
 However, the virtual corrections to the cross section are not infrared finite.
-To render the next-to-leading order cross section $\sigma^{\mathrm{NLO}}$ finite, real corrections need to be included.
+To render the next-to-leading order cross section $\sigma^{\mathrm{NLO}}$ finite, real corrections needed to be included.
 This has been done by Wojciech Kotlarski.
-After including them, $\sigma^{\mathrm{NLO}}$ has been found to contain no further divergences.
+After including them, $\sigma^{\mathrm{NLO}}$ has been found to contain no further divergences.\\
+Equipped with this program, the $K$-factors for up-squark production have been calculated as a function of the squark and of the gluino mass.
+Table \ref{tab:Kfactors} summarizes leading and next-to-leading order cross sections as well as the $K$-factors for up-squark production in the MRSSM and MSSM at the LHC for a selected set of masses.
 \begin{table}[H]
@@
 $1000$ & $1000$ & $42.63$ & $61.8$ & $1.45$ & $122.2$ & $161.3$ & $1.32$\\
-$1000$ & $2000$ & $11.56$ & $14.3$ & $1.24$ & $6.36$ & $72.1$ & $1.09$\\
+$1000$ & $2000$ & $11.56$ & $14.3$ & $1.24$ & $66.36$ & $72.1$ & $1.09$\\
 $1500$ & $3000$ & $0.9166$ & $1.13$ & $1.23$ & $7.045$ & $7.57$ & $1.07$
 \end{tabular}
-\caption{Total hadronic cross section for the production of up-squarks through protons in the MRSSM and the MSSM at leading order and next-to-leading order.
+\caption{Total hadronic cross sections for the production of up-squarks through protons in the MRSSM and the MSSM at leading and next-to-leading order.
 Also given are the $K$-factors.
-As a consequence of $R$-charge conservation, the only allowed channel in the MRSSM is $\tilde{u}_L + \tilde{u}_R$ production, whereas in the MSSM also $\tilde{u}_L + \tilde{u}_L$ and $\tilde{u}_R + \tilde{u}_R$ production is allowed.\newline
+As a consequence of $R$-charge conservation, the only allowed channel in the MRSSM is $\tilde{u}_L + \tilde{u}_R$ production, whereas in the MSSM also $\tilde{u}_L + \tilde{u}_L$ and $\tilde{u}_R + \tilde{u}_R$ production are allowed.\newline
 The results are shown for a selected set of masses.
@@
 \end{table}
-Equipped with this program, the $K$-factors for up-squark production have been calculated as a function of the squark mass and a function of the gluino mass.
-As a result, the comparison of $K$-factors for squark production in the MRSSM and the MSSM showed that the very same are slightly larger in the MRSSM.
+As a result, the comparison of $K$-factors for squark production in the MRSSM and the MSSM showed that they are slightly larger in the MRSSM.
 But since the tree-level cross section of squark production in the MRSSM is, depending on the choice  of squark and gluino mass, about an order of magnitude smaller than in the MSSM, this renders the MRSSM to a perfectly viable extension of the Standard Model.\\
-Among other advantages to the MSSM, it explains a suppressed cross section for the production of supersymmetric particles at the LHC.
+Among other advantages compared to the MSSM, it explains a suppressed cross section for the production of supersymmetric particles at the LHC.

### 2016-07-15 TreeLevel.tex
COMMITTED VERSION

@@
 \section{Squark and Gluino Production at Tree Level}\label{sec:SquarkGluinoTree}
-This chapter considers the production of strongly interacting supersymmetric particles in the MRSSM.\footnote{In fact only the RSQCD is considered as contribution coming from the electroweak sector scale with $\mathcal{O(\alpha_w^2)}$ where $\alpha_w = \frac{g_w^2}{4\pi}$ or $\mathcal{O(\alpha_em^2)}$ where $\alpha_{\mathrm{em}} = \frac{e^2}{4\pi}$ and are therefore significantly smaller than contribution from the strongly interacting sector which scale with $\mathcal{O(\alpha_s^2)}$ where $\alpha_s = \frac{g_s^2}{4\pi}$.} The various processes and their associated cross sections are compared to their analogues in the MSSM.\\
+This chapter considers the production of strongly interacting supersymmetric particles in the MRSSM.\footnote{In fact only the RSQCD is considered as contribution coming from the electroweak sector scale with $\mathcal{O}(\alpha_w^2)$ where $\alpha_w = \frac{g_w^2}{4\pi}$ or $\mathcal{O}(\alpha_{\mathrm{em}}^2)$ where $\alpha_{\mathrm{em}} = \frac{e^2}{4\pi}$ and are therefore significantly smaller than contribution from the strongly interacting sector which scale with $\mathcal{O}(\alpha_s^2)$ where $\alpha_s = \frac{g_s^2}{4\pi}$.} The various processes and their associated cross sections are compared to their analogues in the MSSM.\\
 The production of sgluons is not included in the following analysis.
@@
 \subsection{Partonic Processes and their Cross Section}\label{sec:PartProcesses}
-\begin{figure}[!htbp]
+The tree-level Feynman diagrams for squark and gluino production in the MRSSM are shown in fig.
+\ref{fig:TreeDiagrams}.
+On the partonic level there are six different channels.
+For squark-antisquark  and gluino-antigluino production there are two possible partonic reactions respectively.
+\begin{figure}[H]
 \begin{center}
@@
 \end{center}
-\end{figure}
-The tree-level Feynman diagrams for squark and gluino production in the MRSSM are shown in fig.
-\ref{fig:TreeDiagrams}.
-On the partonic level there are six different channels.
-For squark-antisquark  and gluino-antigluino production there are two possible partonic reactions respectively.\\
+\end{figure}\newpage
 For the following calculation the top quark is excluded from the initial state as it is too heavy to be significantly present in protons. %Therefore its pdf is approximately zero. 
@@
 \end{align}
+\newpage
 Applying the Feynman rules in the Appendix \ref{sec:FeynmanRules}, one obtains the following sums\footnote{The sum $\sum$ denotes the summation over all external spins and colors.} over absolute squared Feynman amplitudes:
@@
 \begin{align}
-\sigma^\mathrm{B}_{\mathrm{Had}}(P_1 P_2 \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_{P_1/H_1}(x_1) f_{P_2/H_2}(x_2)\ \sigma^\mathrm{B}_{\mathrm{Part}} (P_1 P_2 \to X, s = x_ 1x_2 S).\label{eq:facTheorem}
+\sigma^\mathrm{B}_{\mathrm{Had}}(P_1 P_2 \to X) = \int \mbox{d}x_1\  \mbox{d}x_2\ f_{P_1/H_1}(x_1) f_{P_2/H_2}(x_2)\ \sigma^\mathrm{B}_{\mathrm{Part}} (P_1 P_2 \to X, s = x_ 1x_2 S).\label{eq:facTheorem}
 \end{align}
@@
 \end{tabular}
-\caption{Same content as in table \ref{tab:squarkMRSSM} but for the MSSM.}
+\caption{Same content as in table \ref{tab:squarkMRSSM} but for the MSSM.}\label{tab:zweite}
 \end{center}
 \end{table}
-
+The cross sections for the production of squarks (and antisquarks) including five flavors are given for a representative set of masses in table \ref{tab:squarkMRSSM} for the MRSSM and in table \ref{tab:zweite} for the MSSM.
+In addition to the cross section, the relative uncertainty of the scale variation and the parton density functions are given.\\
 As a summary of the comparison between MSSM and MRSSM, one can say, that the gluino production is enhanced in the MRSSM due to distinguishable gluino and antigluino.

### 2016-07-15 Virt_Real.tex
COMMITTED VERSION

@@
 \subsection{Virtual Corrections}
-According to quantum field theory the $\mathcal{O}(\alpha_s)$ correction to a tree-level process includes the computation of one-loop diagrams such as shown in fig.
-\ref{fig:1loopdiagrams}.
-To yield $\mathcal{O}(\alpha_s)$ corrections in the cross section, the interference term between the one-loop amplitude $\mathcal{M}^{\mathrm{1L}}$ and the Born amplitude $\mathcal{M}^{\mathrm{B}}$ needs to be considered:
-\begin{align}
-\left| \mathcal{M}^{\mathrm{B}} + \mathcal{M}^{\mathrm{1L}} \right|^2 &= \left| \mathcal{M}^{\mathrm{B}} \right|^2 + \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} + \mathcal{M}^{\mathrm{1L}} \mathcal{M}^{\mathrm{B}\ast} + \left| \mathcal{M}^{\mathrm{1L}} \right|^2\nonumber\\
-&= \left| \mathcal{M}^{\mathrm{B}} \right|^2 + 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right) + \mathcal{O}(\mbox{2-loop}).
-\end{align}
-However, this term contains divergences. These come from integrals over undetermined momentum and energy of particles running in loops.
-\begin{figure}[!htbp]
+According to quantum field theory the $\mathcal{O}(\alpha_s)$ correction to a tree-level process includes the computation of one-loop diagrams such as shown in fig. \ref{fig:1loopdiagrams}. 
+\begin{figure}[H]
 \begin{center}
@@
 \end{figure}
+To yield $\mathcal{O}(\alpha_s)$ corrections in the cross section, the interference term between the one-loop amplitude $\mathcal{M}^{\mathrm{1L}}$ and the Born amplitude $\mathcal{M}^{\mathrm{B}}$ needs to be considered:
+\begin{align}
+\left| \mathcal{M}^{\mathrm{B}} + \mathcal{M}^{\mathrm{1L}} \right|^2 &= \left| \mathcal{M}^{\mathrm{B}} \right|^2 + \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} + \mathcal{M}^{\mathrm{1L}} \mathcal{M}^{\mathrm{B}\ast} + \left| \mathcal{M}^{\mathrm{1L}} \right|^2\nonumber\\
+&= \left| \mathcal{M}^{\mathrm{B}} \right|^2 + 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right) + \mathcal{O}(\mbox{2-loop}).
+\end{align}
+However, this term contains divergences. These come from integrals over undetermined momentum and energy of particles running in loops.
 Due to their origin these divergences are referred to as ultraviolet (UV) or infrared (IR) divergences.
@@
 \ref{fig:RealGluon}.
-The propagator of the quark which radiates off a gluon gives a contribution of the form
-\begin{align}
-\frac{1}{(p_q + p_g)^2 - m_q^2} = \frac{1}{p_q \cdot p_g} = \frac{1}{2E_qE_g(1-\beta_q \cos \theta_{qg})} \hspace{2cm} \mathrm{with}\ \beta_q = \frac{|\vec{p}_q|}{E_q}
-\end{align}
-to the diagram in question.
-Here, $p_q$, $p_g$ ($E_q$, $E_g$) are the quark's and gluon's four-momentum (energy) and $\theta_{qg}$ is the angle between the quark's and gluon's three-momentum.
-One observes two potentially singular limits
-\begin{align}
-\mathrm{soft\ gluon:}& \hspace{1cm} E_g \to 0\\
-%& \hspace{1cm} E_q \to 0 \hspace{1cm} \mathrm{if}\ m_q \to 0\\
-\mathrm{collinear\ particles:}& \hspace{1cm} \theta_{qg} \to 0 \hspace{1cm} \mathrm{if}\ m_q \to 0.\label{eq:collLimit}
-\end{align}
-Including these singularities into the cross section causes the cancellation of single poles coming from the virtual cross section and the soft divergences coming from the real cross section as well as the cancellation of double poles.
-At this point the only singularities which are left in the sum of real and virtual cross section are collinear ones, coming from the real correction.
-\begin{figure}[!htbp]
+\begin{figure}[H]
 \begin{center}
@@
 \end{center}
-\end{figure}\\
+\end{figure}
+The propagator of the quark which radiates off a gluon gives a contribution of the form
+\begin{align}
+\frac{1}{(p_q + p_g)^2 - m_q^2} = \frac{1}{p_q \cdot p_g} = \frac{1}{2E_qE_g(1-\beta_q \cos \theta_{qg})} \hspace{2cm} \mathrm{with}\ \beta_q = \frac{|\vec{p}_q|}{E_q}
+\end{align}
+to the diagram in question.
+Here, $p_q$, $p_g$ ($E_q$, $E_g$) are the quark's and gluon's four-momentum (energy) and $\theta_{qg}$ is the angle between the quark's and gluon's three-momentum.
+One observes two potentially singular limits
+\begin{align}
+\mathrm{soft\ gluon:}& \hspace{1cm} E_g \to 0\\
+%& \hspace{1cm} E_q \to 0 \hspace{1cm} \mathrm{if}\ m_q \to 0\\
+\mathrm{collinear\ particles:}& \hspace{1cm} \theta_{qg} \to 0 \hspace{1cm} \mathrm{if}\ m_q \to 0.\label{eq:collLimit}
+\end{align}
+Including these singularities into the cross section causes the cancellation of single poles coming from the virtual cross section and the soft divergences coming from the real cross section as well as the cancellation of double poles.
+At this point the only singularities which are left in the sum of real and virtual cross section are collinear ones, coming from the real correction.\\
 To see how these are removed, consider the collinear limit in \eqref{eq:collLimit}.
@@
 $\Gamma(\hdots)$ is the Gamma function and $P_{P_i P_j}(x)$ are the Altarelli-Parisi-kernels\cite{Altarelli:1977zs} which are a measure for the propability of finding a parton $P_i$ with momentum fraction $x$ within a parton $P_j$.
-This procedure of removing collinear divergences is referred to as mass factorization \cite{dissertori2003quantum}.\\
-In fact, apart from this removal of collinear divergences, the Kinoshita-Lee-Naunberg-Theorem \cite{1962JMP.....3..650K, PhysRev.133.B1549} guarantees the finiteness of sufficiently inclusive observables, i.e.
-the cancellation of soft divergences between virtual and real corrections.\\
-Figure \ref{fig:DivergenceSummary} summarizes the required steps to render the next-to-leading order cross section finite.
+This procedure of removing collinear divergences is referred to as mass factorization \cite{dissertori2003quantum}.
 \begin{figure}[H]
@@
 \end{figure}
+In fact, apart from this removal of collinear divergences, the Kinoshita-Lee-Naunberg-Theorem \cite{1962JMP.....3..650K, PhysRev.133.B1549} guarantees the finiteness of sufficiently inclusive observables, i.e.
+the cancellation of soft divergences between virtual and real corrections.\\
+Figure \ref{fig:DivergenceSummary} summarizes the required steps to render the next-to-leading order cross section finite.
 

### 2016-08-17 Appendix.tex
changes after submission

@@
 	\draw[gluon] (0,0)--(180:1);
-	\node at (45:1.3) {$\overline{q}i$};
+	\node at (45:1.3) {$\overline{q}_i$};
 	\node at (-45:1.3) {$q_j$};
@@
 \subsection{Passarino-Veltman Integrals}\label{sec:Passarino}
-The definition of the momenta within the Passarino-Veltman integrals in this thesis agrees with the one from \texttt{Looptools} \cite{Hahn:1998} convention.
+The definition of the momenta within the Passarino-Veltman integrals in this thesis agrees with the one from \texttt{Looptools} \cite{Hahn:1998}.
 The original paper \cite{Passarino:1978jh} uses slightly different conventions.
@@
 \begin{align}
-\frac{i}{16\pi^2} A_0(m^2) &= \int_l \frac{1}{l^2-m^2},\nonumber\\
-\frac{i}{16\pi^2} B_{0,\mu,\mu\nu}(p^2,m_1^2,m_2^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p)^2-m_2^2]},\\
-\frac{i}{16\pi^2} C_{0,\mu,\mu\nu}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p_1)^2-m_2^2][(l+p_1+p_2)^2-m_3^2]},\nonumber\label{eq:LoopInt}
+\frac{i}{16\pi^2} A_0(m^2) &:= \int_l \frac{1}{l^2-m^2},\nonumber\\
+\frac{i}{16\pi^2} B_{0,\mu,\mu\nu}(p^2,m_1^2,m_2^2) &:= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p)^2-m_2^2]},\\
+\frac{i}{16\pi^2} C_{0,\mu,\mu\nu}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2) &:= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p_1)^2-m_2^2][(l+p_1+p_2)^2-m_3^2]},\nonumber\label{eq:LoopInt}
 \end{align}
@@
 B_{\mu\nu} &:= g_{\mu\nu}B_{00} + p_\mu p_\nu B_{11},\nonumber\\
-C_\mu &= p_{1\mu}C_1 + p_{2\mu}C_2,\\
+C_\mu &:= p_{1\mu}C_1 + p_{2\mu}C_2,\\
 C_{\mu\nu} &:= g_{\mu\nu}C_{00} + p_{1\mu}p_{1\nu}C_{11} + p_{2\mu}p_{2\nu}C_{22} + (p_{1\mu}p_{2\nu} + p_{2\mu}p_{1\nu})C_{12}.\nonumber
@@
 It comprises the Euler-Mascheroni constant $\gamma_{\mathrm{E}}$.
+The relation between $\epsilon$ and the dimension $D$ is given by $D = 4-2\epsilon$.
 In the special case of vanishing momenta, the further integrals take a succinct form.

### 2016-08-17 Masterarbeit.tex
changes after submission

@@
 Neben diesen Erfolgen ist aber auch bekannt, dass es unvollständig ist, da es keine Gravitation oder dunkle Materie beinhaltet.
-Supersymmetrie ist eine attraktive Erweiterung des Standardmodells, weil sie viele Probelme desselben auf eine elegante Weise löst.\\
+Supersymmetrie ist eine attraktive Erweiterung des Standardmodells, weil sie viele Probleme desselben auf eine elegante Weise löst.\\
 Diese Arbeit untersucht eine supersymmetrische Erweiterung des Standardmodells welche zusätzlich $R$-symmetrisch ist.
-Neben der Berechnung von Wirkungsquerschnitten von stark wechelwirkenden supersymmetrischen Teilchen in der führenden Ordnung werden Einschleifen\-korrekturen zum Produktionswirkungsquerschnitt von Squarks in diesem Model berechnet und phenomenologisch ausgewertet.
+Neben der Berechnung von Wirkungsquerschnitten von stark wechselwirkenden supersymmetrischen Teilchen in der führenden Ordnung werden Einschleifen\-korrekturen zum Produktionswirkungsquerschnitt von Squarks in diesem Modell berechnet und phenomenologisch ausgewertet.
 \vspace{10em}
@@
 \section*{\centering{Acknowledgements}}
-First of all I like to thank Dominik Stöckinger who enthused me with theoretical particle physics and provided me with this interesting topic.
+First of all, I like to thank Dominik Stöckinger who enthused me with theoretical particle physics and provided me with this interesting topic.
 In addition, he was always available for helping discussions whenever I was in need of them.\\
 Special thanks go to Philip Dießner and Wojciech Kotlarski, who contributed significantly to results within this thesis.
-In addition I like to thank them, Markus Bach, Thomas Kwasnitza, Josua Unger and Tom Steudtner for many valuable discussions and support regarding physical questions as well as programming issues and a pleasant atmosphere in the office.
+In addition, I like to thank them, Markus Bach, Thomas Kwasnitza, Josua Unger and Tom Steudtner for many valuable discussions and support regarding physical questions as well as programming issues and a pleasant atmosphere in the office.
 Furthermore, I like to give them thanks for proofreading this thesis.\\
-I am particularly grateful for Rebecca Schmidt's support within the last month which enabled me to focus on my thesis. In addition I like to thank her for proofreading.\\
-Last but not least I would like to thank my family. Without them my physics studies would by no means have been possible in the way they were.
+I am particularly grateful for Rebecca Schmidt's support within the last month which enabled me to focus on my thesis. In addition, I like to thank her for proofreading.\\
+Last but not least, I would like to thank my family. Without them my physics studies would by no means have been possible in the way they were.
 \newpage

### 2016-08-17 NLO.tex
COMMITTED VERSION
changes after submission

@@
 \end{align}
-The single pole is not that succinct and therefore not quoted here.
+The single pole does not take such a succinct form and is therefore not quoted here.
 
@@
 \end{figure}
-For three different choices of $m_{\tilde{q}}$ and $m_{\tilde{g}}$, Philip Dießner checked the results up to permille accuracy by doing the calculation using \texttt{GoSam}\cite{Cullen:2014yla, Cullen:2011ac} and \texttt{MadGraph5\_aMC@NLO}\cite{Alwall:2014hca} on the basis of the same model file.\\
+For three different choices of $m_{\tilde{q}}$ and $m_{\tilde{g}}$, Philip Dießner checked the results up to permille accuracy by doing the calculation using \texttt{GoSam}\cite{Cullen:2014yla, Cullen:2011ac} and \texttt{MadGraph5\_aMC@NLO}\cite{Alwall:2014hca}.\\
 The next-to-leading order cross sections of this chapter bear a relative uncertainty of one percent due to the numerical integration.
-The uncertainty which corresponds to the variation of the scales $\mu_R$ and $\mu_F$, see section \ref{sec:tree-level_cross_sections}, are evaluate to around 15\%.
+The uncertainty which corresponds to the variation of the scales $\mu_R$ and $\mu_F$, see section \ref{sec:tree-level_cross_sections},  evaluate to $\approx$ 15\%.
 
@@
 As the real corrections are identical to those in the MRSSM, it is again these very real corrections which are responsible for an enhancement of the $K$-factor for large values of  $\frac{m_{\mathrm{g}}}{m_{\mathrm{q}}}$.
+This has also been found in \cite{Beenakker:1996ch}.
 Comparing with the results from the MRSSM in table \ref{tab:MRSSMKfactors}, one can state that the $K$-factors of the MRSSM are slightly larger.

### 2016-08-17 TreeLevel.tex
changes after submission

@@
 To rectify this, an additional finite (supersymmetry restoring) counterterm needs to be added to one of the renormalization constants of $g_s$ or $\hat{g}_s$.
-This will be done in \ref{sec:SUSYrestore}.\\
+This will be done in section \ref{sec:SUSYrestore}.\\
 To parametrize results, the usual Mandelstam variables $s,t,u$ and the following modifications of them are used\footnote{The kinematics of the process is denoted in fig. \ref{fig:TreeDiagrams}.}
@@
 \begin{align}
-&\beta_{\tilde{q}} = \sqrt{1-\frac{4 m_{\tilde{q}}^2}{s}} && \beta_{\tilde{g}} = \sqrt{1-\frac{4 m_{\tilde{g}}^2}{s}}\nonumber\\
-&m_-^2 = m_{\tilde{g}}^2 - m_{\tilde{q}}^2 && \kappa = \sqrt{(s-m_{\tilde{g}}^2-m_{\tilde{q}}^2)^2-4m_{\tilde{g}}^2m_{\tilde{q}}^2}\nonumber\\
-& L_1 = \ln \frac{s+2m_-^2 - s\beta_{\tilde{q}}}{s+2m_-^2 + s\beta_{\tilde{q}}} && L_2= \ln \frac{s - 2m_-^2 - s\beta_{\tilde{g}}}{s - 2m_-^2 + s\beta_{\tilde{g}}}\nonumber\\
-& L_3 = \ln \frac{s - m_-^2 - \kappa}{s - m_-^2 + \kappa} && L_4= \ln \frac{s + m_-^2 - \kappa}{s + m_-^2 + \kappa}
+&\beta_{\tilde{q}} = \sqrt{1-\frac{4 m_{\tilde{q}}^2}{s}}, && \beta_{\tilde{g}} = \sqrt{1-\frac{4 m_{\tilde{g}}^2}{s}},\nonumber\\
+&m_-^2 = m_{\tilde{g}}^2 - m_{\tilde{q}}^2, && \kappa = \sqrt{(s-m_{\tilde{g}}^2-m_{\tilde{q}}^2)^2-4m_{\tilde{g}}^2m_{\tilde{q}}^2},
+\nonumber\\
+& L_1 = \ln \frac{s+2m_-^2 - s\beta_{\tilde{q}}}{s+2m_-^2 + s\beta_{\tilde{q}}}, && L_2= \ln \frac{s - 2m_-^2 - s\beta_{\tilde{g}}}{s - 2m_-^2 + s\beta_{\tilde{g}}}, \nonumber\\
+& L_3 = \ln \frac{s - m_-^2 - \kappa}{s - m_-^2 + \kappa}, && L_4= \ln \frac{s + m_-^2 - \kappa}{s + m_-^2 + \kappa}
 \end{align}
@@
 In the MRSSM only the production of ``chirality'' unlike squarks $\tilde{q}_L \tilde{q}_R$ is allowed whilst in the MSSM also ``chirality'' like squarks can be produced.
-This is again a consequence of the conservation of R-charge.
+This is again a consequence of the conservation of $R$-charge.
 The upshot of this is a suppression of squark production in the MRSSM in comparison to the MSSM.
 To be more explicit the suppression of squark production in the MRSSM grows with the gluino mass.
-This can be understood as follows: As in the MRSSM a left handed squark needs to be produced with a right handed squark one can read off, from the Feynman rules given in Appendix \ref{sec:FeynmanRules}, that the gluino propagator $i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2}$ is sandwiched between the projectors $P_L$ and $P_R$ which leads to the cancellation of the gluino mass in the numerator.
+This can be understood as follows: As in the MRSSM a left handed squark needs to be produced with a right handed squark, one can read off, from the Feynman rules given in Appendix \ref{sec:FeynmanRules}, that the gluino propagator $i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2}$ is sandwiched between the projectors $P_L$ and $P_R$ which leads to the cancellation of the gluino mass in the numerator.
 Therefore for small momenta of the gluino compared to the gluino mass one gets $\mathcal{M}$ $\sim m_{\tilde{g}}^{-2}$ in the MRSSM while in the MSSM one finds a suppression proportional to $m_{\tilde{g}}^{-1}$.\\
-When considering squark production, one has to sum $|\mathcal{M}|^2$ over all helicities.
+When considering the total cross section, one has to sum $|\mathcal{M}|^2$ over all helicities.
 The diagrams for those different final state helicities are shown for flavor like squark production in tab.
@@
 \end{tabular}
-\caption{All Feynman diagrams contributing to flavor unlike squark production in the MSSM and the MRSSM for the example of $u$- and $d$-quarks.}\label{tab:squark_unlikeflavor}
+\caption{All Feynman diagrams contributing to flavor unlike squark production in the MSSM and the MRSSM for the example of the initial state with $u$- and $d$-quarks.}\label{tab:squark_unlikeflavor}
 \end{center}

### 2016-08-17 Virt_Real.tex
changes after submission

@@
 It is known that $\alpha_s$ becomes of $\mathcal{O}(1)$ and larger when the energy scale is of $\mathcal{O}(\unit[200]{MeV})$ and smaller\cite{dissertori2003quantum}.
-Fortunately squark production is a process which involves large enough energy to maintain the validity of perturbation theory, as the typical energy scale involved, is the mass of squarks which certainly fulfills $m_{\tilde{q}} > \unit[500]{GeV}$.\\
+Fortunately, squark production is a process which involves large enough energy to maintain the validity of perturbation theory, as the typical energy scale involved, is the mass of squarks which certainly fulfills $m_{\tilde{q}} > \unit[500]{GeV}$.\\
 This section describes the necessary steps in the calculation of the squark production cross section at next-to-leading order, i.e. its $\mathcal{O}(\alpha_s)$-correction.\\

### 2017-10-17 Appendix.tex
updated TreeLevelPlots

@@
 \end{align}
-where $T^a(R)$ is the $a$-th generator of the matrix valued representation $R$, $g^{ab}$ is the metric of the group, $C(R)$ is the quadratic Casimir invariant of the representation $R$ and $\mathbbm{1}$ is the identity in the representation space.\\
+where $T^a(R)$ is the $a$-th generator of the matrix valued representation $R$, $g^{ab}$ is the metric of the group, $C(R)$ is the quadratic Casimir invariant of the representation $R$ and $\mathbbm{1}$ is the identity in representation space.\\
 Apart from $C(R)$ it is common to define the Dynkin-Index $T(R)$:
@@
 \end{align}
-where $\lambda^a_{ij}$ are for $N_c = 3$ the Gell-Mann matrices and $f_{abc}$ are the structure constants of $SU(N_c)$.
+where $\lambda^a_{ij}$ are for $N_c = 3$ the Gell-Mann matrices and $f_{abc}$ are the structure constants of $SU(N_c)$, defined in eq. \eqref{eq:struc_const}.
 %\begin{tabular}{c|c|c}
@@
 	\node at (3,0) {$\hat{=}\ i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2+i\varepsilon}\delta_{ab}$};
+	\path[line width=0.8pt,>-] (0.25,-0.3) edge [out=180, in=0](1.25,-0.3);
 \end{scope}
@@
 \end{scope}
+\begin{scope}[shift={(8,-10.5)}]
+	\node at (-1.5,0.7) {\circled{10a}};
+	\draw[ghost] (0,0)--(45:1);
+	\draw[ghostbar] (0,0)--(-45:1);
+	\draw[gluon] (0,0)--(180:1);
+	\node at (45:1.4) {$\overline{c}^a(-p_1)$};
+	\node at (-45:1.4) {$c^c$};
+	\node at (180:1.3) {$G_\mu^b$};
+	\node at (3,0) {$\hat{=} -g_s f^{abc}p_1^\mu$};
+\end{scope}
 \begin{scope}[shift={(1,-13.5)}]
@@
 \caption{In the Feynman diagrams of the propagators the momentum is flowing from the right to the left hand side. The gluon propagator is given in Feynman gauge.\newline
-In the Feynman diagrams of the vertices all momenta flow towards the vertex, i.e. in diagram 9: $-p_1$ flows towards the vertex.\newline
+In the Feynman diagrams of the vertices all momenta flow towards the vertex, i.e. in diagram 9 and 10a: $-p_1$ flows towards the vertex.\newline
 The indices $A,B \in \left\{ L,R \right\}$ label the left/right ``handedness'' of the squarks.
@@
 	\node(g) at (0.9,-0.6) {};
-	\path[line width=0.8pt,<-] (g) edge [out=135, in=-135] (gbar);
+	\path[line width=0.8pt,->] (g) edge [out=135, in=-135] (gbar);
 	\node at (2,0) {$\hat{=}  - g_s f_{abc} \gamma^\mu$};
@@
 	\node(u) at (0.4,-0.8) {};
-	\path[line width=0.8pt,<-] (g) edge [out=0, in=135] (u);
+	\path[line width=0.8pt,->] (g) edge [out=0, in=135] (u);
 	\node at (3,0) {$\hat{=} -i\sqrt{2}g_s T^a_{ij}P_L$};
@@
 	\node(u) at (0.4,0.8) {};
-	\path[line width=0.8pt,->] (g) edge [out=0, in=225] (u);
+	\path[line width=0.8pt,<-] (g) edge [out=0, in=225] (u);
 	\node at (3,0) {$\hat{=} -i\sqrt{2}g_s T^a_{ij}P_R$};
@@
 	\node(u) at (0.4,-0.8) {};
-	\path[line width=0.8pt,<-] (g) edge [out=0, in=135] (u);
+	\path[line width=0.8pt,->] (g) edge [out=0, in=135] (u);
 	\node at (3,0) {$\hat{=} +i\sqrt{2}g_s T^a_{ij}P_L$};
@@
 	\node(u) at (0.4,0.8) {};
-	\path[line width=0.8pt,->] (g) edge [out=0, in=225] (u);
+	\path[line width=0.8pt,<-] (g) edge [out=0, in=225] (u);
 	\node at (3,0) {$\hat{=} +i\sqrt{2}g_s T^a_{ij}P_R$};
@@
 	\node(u) at (0.4,-0.8) {};
-	\path[line width=0.8pt,<-] (g) edge [out=0, in=135] (u);
+	\path[line width=0.8pt,->] (g) edge [out=0, in=135] (u);
 	\node at (3,0) {$\hat{=} -\sqrt{2}g_s f^{abc}P_L$};
@@
 	\node(u) at (0.4,0.8) {};
-	\path[line width=0.8pt,->] (g) edge [out=0, in=225] (u);
+	\path[line width=0.8pt,<-] (g) edge [out=0, in=225] (u);
 	\node at (3,0) {$\hat{=} +\sqrt{2}g_s f^{abc} P_R$};
@@
 	\node at (-135:1.4) {$\sigma^c$};
-	\node at (3,0) {$\hat{=} \ -g_s^2 (f^{abc}f^{ade} + f^{abc}f^{adc})$};
+	\node at (3,0) {$\hat{=} \ ig_s^2 (f^{abc}f^{ade} + f^{abe}f^{adc})$};
 \end{scope}
@@
 \int \mathrm{d}\Phi_2 = & \frac{1}{s} \frac{\pi^{-\frac{D}{2}+1}}{2^{D-3}\Gamma(\frac{D}{2}-1)} \int \mathrm{d}u\ \mathrm{d}t\ \left( \frac{tu-m_1^2m_2^2}{\mu^{2\epsilon} s} \right)^{\frac{D-4}{2}} \nonumber\\
-&\frac{1}{4}\Theta(tu-4m_1^2m_2^2)\delta \left(s+t+u-m_1^2-m_2^2\right)
+&\frac{1}{4}\Theta(tu-m_1^2m_2^2)\delta \left(s+t+u-m_1^2-m_2^2\right)
 \end{align}

### 2017-10-17 MSSM.tex
updated TreeLevelPlots

@@
 This statement was corrected by the Haag-{\L}opusza\'nski-Sohnius theorem \cite{Haag:1974qh} which weakened the condition of the quantum field theory by allowing also for anticommuting symmetry generators.
-This is, by introducing the generators $Q_\alpha$ and $\overline{Q}^{\dot{\alpha}}$ with $\alpha, \dot{\alpha} \in \left\{ 1,2 \right\}$, the Poincare-algebra eq.
+This is, by introducing the generators $Q_\alpha$ and $\overline{Q}^{\dot{\alpha}}$ with $\alpha, \dot{\alpha} \in \left\{ 1,2 \right\}$, the Poincare algebra eq.
 \eqref{eq:PoincareAlgebra} can be nontrivially extended to the so called superalgebra (see Appendix \eqref{sec:2spinor_notation} for the definition of the $\sigma$-matrices):
@@
 The superalgebra in eq.
-\eqref{eq:SUSYalgebra} is actually the smallest extension of the Poincare-algebra as it is possible to introduce further anticommuting symmetry generators.
+\eqref{eq:SUSYalgebra} is actually the smallest extension of the Poincare algebra as it is possible to introduce further anticommuting symmetry generators.
 Their maximal number is fixed to $N = 8$.

### 2017-10-17 Masterarbeit.tex
updated TreeLevelPlots

@@
   \begin{singlespace}\begin{center}\bfseries\Huge  
-  Squark Production in the R-Symmetric Supersymmetric Standardmodel  
+  Squark Production in the $R$-Symmetric Supersymmetric Standardmodel  
   \end{center}\end{singlespace}
@@
 \thispagestyle{empty}\vspace*{48em}
-Eingereicht am 15.~Juli~2016\vspace{1.5em}
+Eingereicht am 15.~Juli~2016\\
+Abgeänderte Fassung vom 18.~November~2016\vspace{1.5em}
 \par{\large\begin{tabular}{ll}

### 2017-10-17 NLO.tex
updated TreeLevelPlots

@@
 This section discusses the cross section for squark production at next-to-leading order $\sigma^{\mathrm{NLO}}$.
-To do so, the next section gives a justification why on-shell renormalization has been chosen in section \ref{sec:renMRSSM}.
+To comment on the calculation, the next section gives a justification why on-shell renormalization has been chosen in section \ref{sec:renMRSSM} and why loop corrections of external particles (see caption of {fig:1loopdiagrams}) are not taken into account.
 After that, the setup of the calculation of the different contributions to $\sigma^{\mathrm{NLO}}$, which has been performed by a \texttt{C++} program, is explained.
@@
 \end{align}
-means that the physical mass equals the tree level mass.
+means that the physical mass equals the tree level mass.\\
+Finally one can conclude that loop-corrections of the S-matrix-element correspond only to internal loops, i.e.
+self-energies of external particles do not contribute.%as the S-matrix-element is proportional to the amputated Green function
 
@@
 	\node [block4] at (-1,0) (Mathematica) {Mathematica notebook};
-	\node [block1a] at (-1,-2.1) (notebookR) {soft/collinear limit: \newline \texttt{FeynArts} $\to \mathcal{M}^{\mathrm{R}}$ \newline \texttt{FormCalc} $\to$ $\sum |\mathcal{M}^{\mathrm{R}|^2}$};
-	\node [block1a] at (-1,-8) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to$ $\sum |\mathcal{M}^{\mathrm{B}|^2}$};	
+	\node [block1a] at (-1,-2.1) (notebookR) {soft/collinear limit: \newline \texttt{FeynArts} $\to \mathcal{M}^{\mathrm{R}}$ \newline \texttt{FormCalc} $\to$ $\sum |\mathcal{M}^{\mathrm{R}}|^2$};
+	\node [block1a] at (-1,-8) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to$ $\sum |\mathcal{M}^{\mathrm{B}}|^2$};	
 	\node [block1a] at (-1,-5.7) (notebookV) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{1L}}$ \newline \texttt{FormCalc} $\to$ \newline $2\sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$};
@@
 	\path [line, line width = 1] (1.2,-2.0) -- (9.5,-2.0);
-	\node [block6a] at (7.5,-10.7) (Sigma) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}} + \sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$};
+	\node [block6a] at (7.5,-10.7) (Sigma) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}}$};
 	\path [line, line width = 1] (Born) -- (Sigma);

### 2017-10-17 RSymmetry.tex
updated TreeLevelPlots

@@
 As a consequence terms which allow flavor violating processes like $\mu \to e \gamma$ in the MSSM are suppressed in the MRSSM\cite{Kribs:2007ac}.
-Quite interestingly Dirac gauginos can be heavier than Majorana gauginos without being less natural in view of the hierarchy problem\cite{Nelson:2002ca, Kribs:2012gx, Hardy:2013ywa}.
+Quite interestingly Dirac gauginos can be heavier than Majorana gauginos without being less natural in view of the hierarchy problem\cite{Fox:2002bu, Nelson:2002ca, Kribs:2012gx, Hardy:2013ywa}.
+This is because the (one-loop) beta function of the squark mass does not depend on the gluino mass.\footnote{If $m_{\tilde{q}}$ is evolved via renormalization group equation to smaller energies, $m_{\tilde{g}}$ is in the MSSM responsible for an increase of $m_{\tilde{q}}$.
+At a high energy scale, all masses of supersymmetric particles are considered as equal, which forces $m_{\tilde{g}}$ in the MSSM to be ``small'' in order to ensure a not too high squark mass at the EWSB-scale.
+A too high $m_{\tilde{q}}$ would spoil the solution to the hierarchy problem.
+This $m_{\tilde{g}}$ dependence is absent in the MRSSM, which imposes no restriction on $m_{\tilde{g}}$, in this respect.}
 Finally the production cross section of strongly interacting particles is suppressed\cite{Kribs:2012gx, Kribs:2013oda}.
@@
 For gauginos the D-type spurion is given by $\hat{W}_\alpha^\prime = \theta_\alpha D$ and mediates super symmetry breaking at the mediation scale $M$: $\int\mathrm{d}\theta^2\frac{\hat{W}_\alpha^\prime}{M}W_s^\alpha \hat{O}$.
-After integrating out the spurion one obtains\cite{Fox:2002bu, Diessner:2015bna}
+After integrating out the spurion one obtains\cite{Fox:2002bu, Diessner:2014ksa}
 \begin{align}

### 2017-10-17 Renormalization.tex
updated TreeLevelPlots

@@
 \eqref{eq:GammaCtRestore}.
-The only point where particularly care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms:
+The only point where particular care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms:
 \begin{align}
@@
 \end{tikzpicture}
-\caption{Diagrammatic contributions to the self-energy of the squark at 1-loop level}\label{fig:GluinoSE}
+\caption{Diagrammatic contributions to the self-energy of the gluino at 1-loop level}\label{fig:GluinoSE}
 \end{center}
@@
 &+C(A)(1-2(B_0(m_{\tilde{g}}^2,0,m_{\tilde{g}}^2) + B_1(m_{\tilde{g}}^2,0,m_{\tilde{g}}^2)))\nonumber\\
-&+ 4T(F) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left( ((n_f-1))  B_1(p^2,0,m_{\tilde{q}}^2) +  B_1(p^2,m_t^2,m_{\tilde{q}}^2) \right)\nonumber\\
+&+ 4T(F) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left( (n_f-1)  B_1(p^2,0,m_{\tilde{q}}^2) +  B_1(p^2,m_t^2,m_{\tilde{q}}^2) \right)\nonumber\\
 &-2 C(A) m_{\tilde{g}} \frac{\partial}{\partial p^2} \left( B_0(p^2,m_{\tilde{g}}^2,m_{\phi^0}^2)-B_0(p^2,m_{\tilde{g}}^2,m_{\sigma^0}^2) - B_1(p^2,m_{\tilde{g}}^2,m_{\phi^0}^2) - B_1(p^2,m_{\tilde{g}}^2,m_{\sigma^0}^2) \right)\nonumber\\
-&-4 C(A) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left.\left( -B_0(p^2,0,m_{\tilde{g}}^2) + B_0(p^2,0,m_{\tilde{g}}^2) \right)\right]_{p^2=m_{\tilde{g}}^2}
+&-4 C(A) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left.\left( -B_0(p^2,0,m_{\tilde{g}}^2) + B_1(p^2,0,m_{\tilde{g}}^2) \right)\right]_{p^2=m_{\tilde{g}}^2}
 \end{align}
@@
 &+C(A)(1-2(B_0(m_{\tilde{g}}^2,0,m_{\tilde{g}}^2) + B_1(m_{\tilde{g}}^2,0,m_{\tilde{g}}^2)))\nonumber\\
-&+ 4T(F) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left( ((n_f-1))  B_1(p^2,0,m_{\tilde{q}}^2) +  B_1(p^2,m_t^2,m_{\tilde{q}}^2) \right)\nonumber\\
+&+ 4T(F) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left( (n_f-1)  B_1(p^2,0,m_{\tilde{q}}^2) +  B_1(p^2,m_t^2,m_{\tilde{q}}^2) \right)\nonumber\\
 &-2 C(A) m_{\tilde{g}} \frac{\partial}{\partial p^2} \left( B_0(p^2,m_{\tilde{g}}^2,m_{\phi^0}^2)-B_0(p^2,m_{\tilde{g}}^2,m_{\sigma^0}^2) - B_1(p^2,m_{\tilde{g}}^2,m_{\phi^0}^2) - B_1(p^2,m_{\tilde{g}}^2,m_{\sigma^0}^2) \right)\nonumber\\
-&-4 C(A) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left.\left( -B_0(p^2,0,m_{\tilde{g}}^2) + B_0(p^2,0,m_{\tilde{g}}^2) \right)\right]_{p^2=m_{\tilde{g}}^2}.
+&-4 C(A) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left.\left( -B_0(p^2,0,m_{\tilde{g}}^2) + B_1(p^2,0,m_{\tilde{g}}^2) \right)\right]_{p^2=m_{\tilde{g}}^2}.
 \end{align}
@@
 $\epsilon^{-1}$ & $\epsilon^{-1}$ & (\texttt{SetLambda} $\to -1$, \texttt{Dminus4} $\to 0$) \\
-  & $+\mathcal{O}(\epsilon)\cdot\epsilon^{-1}$ & $+$(\texttt{SetLambda} $\to -2$, \texttt{Dminus4} $\to -2$) \\
+  & $+\mathcal{O}(\epsilon)\cdot\epsilon^{-2}$ & $+$(\texttt{SetLambda} $\to -2$, \texttt{Dminus4} $\to -2$) \\
   & & $-$(\texttt{SetLambda} $\to -2$, \texttt{Dminus4} $\to 0$)\\

### 2017-10-17 Standardmodel.tex
updated TreeLevelPlots

@@
 \begin{align}
-[T^a,T^b] = if_{abc}T^c,
+[T^a,T^b] = if_{abc}T^c,\label{eq:struc_const}
 \end{align}
@@
 \end{pmatrix}$\\
-right-handed leptons & $e_{iR}$ & - & 0 & $+1$ & $+1$\\
+right-handed leptons & $e_{iR}$ & - & 0 & $-1$ & $+1$\\
 \hline
@@
 For the other force particles in the Standard Model - the $W^\pm$ bosons, the $Z_0$ boson and the photon the situation is slightly more involved.
-They are obtained as a mixture of the $W^b_\mu$ ($b=1,2,3$) and the $B_\mu$ field which are the gauge fields of $SU_L(2)_L$ and $U_Y(1)_Y$ respectively.
+They are obtained as a mixture of the $W^b_\mu$ ($b=1,2,3$) and the $B_\mu$ field which are the gauge fields of $SU(2)_L$ and $U(1)_Y$ respectively.
 This mixing procedure is explained in section \ref{sec:EWSB}.\\

### 2017-10-17 Summary.tex
updated TreeLevelPlots

@@
 As a result, the comparison of $K$-factors for squark production in the MRSSM and the MSSM showed that they are slightly larger in the MRSSM.
-But since the tree-level cross section of squark production in the MRSSM is, depending on the choice  of squark and gluino mass, about an order of magnitude smaller than in the MSSM, this renders the MRSSM to a perfectly viable extension of the Standard Model.\\
+But since the tree-level cross section of squark production in the MRSSM is, depending on the choice of squark and gluino mass, up to a factor of about eight smaller than in the MSSM, this renders the MRSSM, in this respect, to a perfectly viable extension of the Standard Model.\\
 Among other advantages compared to the MSSM, it explains a suppressed cross section for the production of supersymmetric particles at the LHC.

### 2017-10-17 TreeLevel.tex
updated TreeLevelPlots

@@
 \begin{align}
-\sigma^B(q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij}  \frac{g_s^4}{16\pi s} (n_f-1) \left[ \frac{4}{27} - \frac{16 m_{\tilde{q}}^2}{27s} \right]\nonumber\\
+\sigma^B(q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij}  \frac{g_s^4}{16\pi s} (n_f-1) \left[ \frac{4}{27} - \frac{16 m_{\tilde{q}}^2}{27s} \right]\beta_{\tilde{q}}\nonumber\\
 &+ \delta_{ij} \frac{g_s^2\hat{g}_s^2}{16\pi s}  \left[ \left( \frac{4}{27} + \frac{8 m_-^2}{27 s} \right)\beta_{\tilde{q}}  + \left( \frac{8m_{\tilde{g}}^2}{27s} + \frac{8m_-^4}{27s^2} \right)L_1 \right]\nonumber\\
@@
 The final state particles have to meet the total $R$-charge zero from the initial state.
-Because of this, one only has $\tilde{q}_L \overline{\tilde{q}}_L$ and $\tilde{q}_R \overline{\tilde{q}}_R$ as the final states in the MRSSM whereas in the MSSM one actually has four instead of two t-channel diagrams: The corresponding final states are $\tilde{q}_L \overline{\tilde{q}}_L$, $\tilde{q}_R \overline{\tilde{q}}_R$, $\tilde{q}_L \overline{\tilde{q}}_R$ and $\overline{\tilde{q}}_R \tilde{q}_L$.
+Because of this, one only has $\tilde{q}_L \tilde{q}^\dagger_L$ and $\tilde{q}_R \tilde{q}^\dagger_R$ as the final states in the MRSSM whereas in the MSSM one actually has four instead of two t-channel diagrams: The corresponding final states are $\tilde{q}_L \tilde{q}^\dagger_L$, $\tilde{q}_R \tilde{q}^\dagger_R$, $\tilde{q}_L \tilde{q}^\dagger_R$ and $\tilde{q}_R \tilde{q}^\dagger_L$.
 Consequently contributions from the $t$-channel diagrams are suppressed in the MRSSM in comparison to the MSSM.
@@
 \begin{center}
-\includegraphics[scale=.45]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
-\includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
+\includegraphics[scale=.4]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
+\includegraphics[scale=.4]{figures/rel_weights_mr=2_MSSM+MRSSM}
 \caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC with \mbox{$\sqrt{S} = \unit[13]{GeV}$}.
@@
 
-For the small mass ratio $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ and small squark masses, the dominant contribution comes from gluino (antigluino) production.
-This is even more dominant in the MRSSM which can be explained by the above mentioned factor of two difference in the $GG \to \tilde{g}\tilde{g}(\overline{\tilde{g}})$ channel which comes from the distinguishable gluino and antigluino in the MRSSM.
+For the small mass ratio $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ and small squark masses, the dominant contribution comes from gluino-squark production.
+The subdominant channel is represented by gluino (antigluino) production which is much more pronounced in the MRSSM, which can be explained by the above mentioned factor of two difference in the $GG \to \tilde{g}\tilde{g}(\overline{\tilde{g}})$ channel which comes from the distinguishable gluino and antigluino in the MRSSM.
 Furthermore there is the above mentioned destructive interference term in the $q\overline{q} \to \tilde{g}\tilde{g}(\overline{\tilde{g}})$ channel which makes the cross section for this process in the MRSSM dominant over the one in the MSSM.\\
-For a increasing squark mass, the previously subdominant gluino-squark production takes over and becomes dominant.
 A salient difference between the MSSM and the MRSSM is that squark production is strongly suppressed in the MRSSM.
-While in the MSSM it becomes dominant above  $\approx \unit[1400]{GeV}$ it is subsubdominant for the whole displayed squark mass in the MRSSM.
-This suppression has also already been explained above.\\
+While in the MSSM it becomes dominant above  $\approx \unit[2000]{GeV}$ it is at least subsubdominant for the whole displayed squark mass in the MRSSM.
+This suppression has already been explained above.\\
 Turning from $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ to $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ suppresses quite strongly the production of gluinos in all pertaining channels.
@@
 See also \ref{fig:TreeXsection_fixed_m} for a visualization of this behavior.\\
-Note also, that for sufficiently large squark masses squark production becomes the dominant process, see fig.
+Note also, that for sufficiently large squark masses, squark production becomes the dominant process, see fig.
 \ref{fig:TreeXsection} and \ref{fig:TreeLevelSigma_0,9_2}.
@@
 So looking at large $x$ the proton basically consists of quarks and because the only process involving only quarks in the initial state is squark production, this channel dominates for high masses.\\
-The total cross section in the MRSSM is increasingly smaller than in the MSSM in particular from about $\unit[500]{GeV}$ onwards.
-The is because for masses below that the $GG \to \tilde{q}\tilde{q}^\dagger$ channel, which is the same for both models, is the dominant one.\\
+The total cross section in the MRSSM is increasingly smaller than in the MSSM, which can be seen for $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ when taking the  $GG \to \tilde{q}\tilde{q}^\dagger$ channel, which is the same for both models, as a benchmark.\\
 When raising the gluino squark mass ratio further to $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 5$ the above described tendency continues.
 This is, all processes including a gluino get even more negligible and squark production gets further suppressed.
-While in the MSSM it becomes dominant over $GG \to \tilde{q}\tilde{q}^\dagger$ at $m_{\tilde{q}} \approx \unit[800]{GeV}$, it is subdominant in the MRSSM within the whole displayed mass range, even though it does not fall that steeply as the dominant channel.\\
+While in the MSSM it becomes dominant over $GG \to \tilde{q}\tilde{q}^\dagger$ at $m_{\tilde{q}} \approx \unit[700]{GeV}$, it is subdominant in the MRSSM within the whole displayed mass range, even though it does not fall that steeply as the dominant channel.\\
 
@@
 \includegraphics[scale=.4]{figures/mr=5_MSSM+MRSSM}
-\includegraphics[scale=.45]{figures/rel_weights_mr=5_MSSM+MRSSM}
+\includegraphics[scale=.4]{figures/rel_weights_mr=5_MSSM+MRSSM}
 \caption{Hadronic cross section for squark and gluino production (in the first row) and relative contributions of the indicated final states to the total hadronic cross section (in the second row) in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC with $\sqrt{S} = \unit[13]{GeV}$.

### 2017-10-17 Virt_Real.tex
updated TreeLevelPlots

@@
 In the first line, an example for a self-energy and a vertex-correction diagram is shown.
-The second line lists typical box-diagrams: a three-point box and a four-point box.}\label{fig:1loopdiagrams}
+The second line lists typical box-diagrams: a three-point box and a four-point box.\newline
+There are no loop corrections of external particles, which is expalined in section \ref{sec:LSZ}.}\label{fig:1loopdiagrams}
 \end{center}
@@
 	\node [block1a] (Mvirt) {$\mathcal{M}^{\mathrm{1L}}$ is UV- and  IR-divergent};
-	\node [block2a] at (6,0) (Mreal) {$\mathcal{M}^{\mathrm{real}}$ is IR-divergent};
+	\node [block2a] at (6,0) (Mreal) {$\mathcal{M}^{\mathrm{R}}$ is IR-divergent};
 	\node [block1a] at (0,-2) (Mvirtren) {$\mathcal{M}^{\mathrm{1L}}$ is IR-divergent};

### 2017-10-17 figures/Contour_Plots/MRSSM_TreeLevel_qq_sqsq.py

@@ -38,7 +38,8 @@ def contourdata():
     v = 10**np.linspace(-1, 7, 9, endpoint=True)
     fig = plt.figure(1,figsize=(9, 8)) 
     ax1 = plt.axes()
-    font_size = 18
+    font_size = 22
+    plt.title("MRSSM", size = 2*font_size)
     plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
     plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
     plt.xticks(fontsize = font_size)

### 2017-10-17 figures/Contour_Plots/MSSM_TreeLevel_qq_sqsq.py

@@ -38,7 +38,8 @@ def contourdata():
     v = 10**np.linspace(-1, 7, 9, endpoint=True)
     fig = plt.figure(1,figsize=(9, 8)) 
     ax1 = plt.axes()
-    font_size = 18
+    font_size = 22
+    plt.title("MSSM", size = 2*font_size)
     plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
     plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
     plt.xticks(fontsize = font_size)

### 2017-10-17 figures/NLOContour/MRSSM_uu_susu_Kfactor.py

@@ -51,7 +51,8 @@ def contourdata():
     v2 = np.linspace(0.5, 1.9, 8, endpoint=True)
     fig = plt.figure(1,figsize=(9, 8)) 
     ax1 = plt.axes()
-    font_size = 18
+    font_size = 22
+    plt.title("MRSSM", size = 2*font_size)
     plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
     plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
     plt.xticks(fontsize = font_size)

### 2017-10-17 figures/NLOContour/MSSM_uu_susu_Kfactor.py

@@ -62,7 +62,8 @@ def contourdata():
     v2 = np.linspace(0.5, 1.9, 8, endpoint=True)
     fig = plt.figure(1,figsize=(9, 8)) 
     ax1 = plt.axes()
-    font_size = 18
+    font_size = 22
+    plt.title("MSSM", size = 2*font_size)
     plt.xlabel(r"$m_{\tilde{q}}$ in GeV", size = font_size)
     plt.ylabel(r"$m_{\tilde{g}}$ in GeV", size = font_size)
     plt.xticks(fontsize = font_size)

### 2017-10-17 figures/TreeLevelPlots/output_mr_2TeV/plot.py

@@ -1,0 +1,205 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Dec  9 14:21:19 2015
+
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib import colors
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_squark = np.array([], dtype=float);
+# arrays for 1st parton reaction
+sigma1_MSSM = np.array([], dtype=float);
+# arrays for 2nd parton reaction
+sigma2 = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MSSM = np.array([], dtype=float);
+# arrays for 4th parton reaction
+sigma4_MSSM = np.array([], dtype=float);
+# arrays for 5th parton reaction
+sigma5_MSSM = np.array([], dtype=float);
+# arrays for 6th parton reaction
+sigma6 = np.array([], dtype=float);
+
+
+# arrays for 1st parton reaction
+sigma1_MRSSM = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MRSSM = np.array([], dtype=float);
+# arrays for 4th parton reaction
+sigma4_MRSSM = np.array([], dtype=float);
+# arrays for 5th parton reaction
+sigma5_MRSSM = np.array([], dtype=float);
+
+
+
+f_MSSM1 = open('MSSM_1_qqbar_sqsqdagger.txt', 'r')
+
+for lines in f_MSSM1.readlines():
+    m_squark = np.append(m_squark, float(lines.split()[0]))
+    sigma1_MSSM = np.append(sigma1_MSSM, float(lines.split()[1]))
+
+f_MSSM1.close()
+
+
+f_2 = open('MSSM_MRSSM_2_GG_sqsq.txt', 'r')
+
+for lines in f_2.readlines():
+    discard = f_2.readline()
+    sigma2 = np.append(sigma2, float(lines.split()[1]))
+
+f_2.close()
+
+
+f_MSSM3 = open('MSSM_3_qq_sqsq.txt', 'r')
+
+for lines in f_MSSM3.readlines():
+    discard = f_MSSM3.readline()
[…]

### 2017-10-17 figures/TreeLevelPlots/output_mr_2TeV/rel_plot.py

@@ -1,0 +1,206 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Dec  9 14:21:19 2015
+
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib import colors
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_squark = np.array([], dtype=float);
+# arrays for 1st parton reaction
+sigma1_MSSM = np.array([], dtype=float);
+# arrays for 2nd parton reaction
+sigma2 = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MSSM = np.array([], dtype=float);
+# arrays for 4th parton reaction
+sigma4_MSSM = np.array([], dtype=float);
+# arrays for 5th parton reaction
+sigma5_MSSM = np.array([], dtype=float);
+# arrays for 6th parton reaction
+sigma6 = np.array([], dtype=float);
+
+
+# arrays for 1st parton reaction
+sigma1_MRSSM = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MRSSM = np.array([], dtype=float);
+# arrays for 4th parton reaction
+sigma4_MRSSM = np.array([], dtype=float);
+# arrays for 5th parton reaction
+sigma5_MRSSM = np.array([], dtype=float);
+
+
+
+f_MSSM1 = open('MSSM_1_qqbar_sqsqdagger.txt', 'r')
+
+for lines in f_MSSM1.readlines():
+    m_squark = np.append(m_squark, float(lines.split()[0]))
+    sigma1_MSSM = np.append(sigma1_MSSM, float(lines.split()[1]))
+
+f_MSSM1.close()
+
+
+f_2 = open('MSSM_MRSSM_2_GG_sqsq.txt', 'r')
+
+for lines in f_2.readlines():
+    discard = f_2.readline()
+    sigma2 = np.append(sigma2, float(lines.split()[1]))
+
+f_2.close()
+
+
+f_MSSM3 = open('MSSM_3_qq_sqsq.txt', 'r')
+
+for lines in f_MSSM3.readlines():
+    discard = f_MSSM3.readline()
[…]

### 2017-10-17 figures/TreeLevelPlots/output_mr_5TeV/plot.py

@@ -1,0 +1,205 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Dec  9 14:21:19 2015
+
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib import colors
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_squark = np.array([], dtype=float);
+# arrays for 1st parton reaction
+sigma1_MSSM = np.array([], dtype=float);
+# arrays for 2nd parton reaction
+sigma2 = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MSSM = np.array([], dtype=float);
+# arrays for 4th parton reaction
+sigma4_MSSM = np.array([], dtype=float);
+# arrays for 5th parton reaction
+sigma5_MSSM = np.array([], dtype=float);
+# arrays for 6th parton reaction
+sigma6 = np.array([], dtype=float);
+
+
+# arrays for 1st parton reaction
+sigma1_MRSSM = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MRSSM = np.array([], dtype=float);
+# arrays for 4th parton reaction
+sigma4_MRSSM = np.array([], dtype=float);
+# arrays for 5th parton reaction
+sigma5_MRSSM = np.array([], dtype=float);
+
+
+
+f_MSSM1 = open('MSSM_1_qqbar_sqsqdagger.txt', 'r')
+
+for lines in f_MSSM1.readlines():
+    m_squark = np.append(m_squark, float(lines.split()[0]))
+    sigma1_MSSM = np.append(sigma1_MSSM, float(lines.split()[1]))
+
+f_MSSM1.close()
+
+
+f_2 = open('MSSM_MRSSM_2_GG_sqsq.txt', 'r')
+
+for lines in f_2.readlines():
+    discard = f_2.readline()
+    sigma2 = np.append(sigma2, float(lines.split()[1]))
+
+f_2.close()
+
+
+f_MSSM3 = open('MSSM_3_qq_sqsq.txt', 'r')
+
+for lines in f_MSSM3.readlines():
+    discard = f_MSSM3.readline()
[…]

### 2017-10-17 figures/TreeLevelPlots/output_mr_5TeV/rel_plot.py

@@ -1,0 +1,206 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Dec  9 14:21:19 2015
+
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib import colors
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_squark = np.array([], dtype=float);
+# arrays for 1st parton reaction
+sigma1_MSSM = np.array([], dtype=float);
+# arrays for 2nd parton reaction
+sigma2 = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MSSM = np.array([], dtype=float);
+# arrays for 4th parton reaction
+sigma4_MSSM = np.array([], dtype=float);
+# arrays for 5th parton reaction
+sigma5_MSSM = np.array([], dtype=float);
+# arrays for 6th parton reaction
+sigma6 = np.array([], dtype=float);
+
+
+# arrays for 1st parton reaction
+sigma1_MRSSM = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MRSSM = np.array([], dtype=float);
+# arrays for 4th parton reaction
+sigma4_MRSSM = np.array([], dtype=float);
+# arrays for 5th parton reaction
+sigma5_MRSSM = np.array([], dtype=float);
+
+
+
+f_MSSM1 = open('MSSM_1_qqbar_sqsqdagger.txt', 'r')
+
+for lines in f_MSSM1.readlines():
+    m_squark = np.append(m_squark, float(lines.split()[0]))
+    sigma1_MSSM = np.append(sigma1_MSSM, float(lines.split()[1]))
+
+f_MSSM1.close()
+
+
+f_2 = open('MSSM_MRSSM_2_GG_sqsq.txt', 'r')
+
+for lines in f_2.readlines():
+    discard = f_2.readline()
+    sigma2 = np.append(sigma2, float(lines.split()[1]))
+
+f_2.close()
+
+
+f_MSSM3 = open('MSSM_3_qq_sqsq.txt', 'r')
+
+for lines in f_MSSM3.readlines():
+    discard = f_MSSM3.readline()
[…]

### 2017-10-17 figures/TreeLevelPlots/output_mr_900GeV/plot.py

@@ -1,0 +1,205 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Dec  9 14:21:19 2015
+
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib import colors
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_squark = np.array([], dtype=float);
+# arrays for 1st parton reaction
+sigma1_MSSM = np.array([], dtype=float);
+# arrays for 2nd parton reaction
+sigma2 = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MSSM = np.array([], dtype=float);
+# arrays for 4th parton reaction
+sigma4_MSSM = np.array([], dtype=float);
+# arrays for 5th parton reaction
+sigma5_MSSM = np.array([], dtype=float);
+# arrays for 6th parton reaction
+sigma6 = np.array([], dtype=float);
+
+
+# arrays for 1st parton reaction
+sigma1_MRSSM = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MRSSM = np.array([], dtype=float);
+# arrays for 4th parton reaction
+sigma4_MRSSM = np.array([], dtype=float);
+# arrays for 5th parton reaction
+sigma5_MRSSM = np.array([], dtype=float);
+
+
+
+f_MSSM1 = open('MSSM_1_qqbar_sqsqdagger.txt', 'r')
+
+for lines in f_MSSM1.readlines():
+    m_squark = np.append(m_squark, float(lines.split()[0]))
+    sigma1_MSSM = np.append(sigma1_MSSM, float(lines.split()[1]))
+
+f_MSSM1.close()
+
+
+f_2 = open('MSSM_MRSSM_2_GG_sqsq.txt', 'r')
+
+for lines in f_2.readlines():
+    discard = f_2.readline()
+    sigma2 = np.append(sigma2, float(lines.split()[1]))
+
+f_2.close()
+
+
+f_MSSM3 = open('MSSM_3_qq_sqsq.txt', 'r')
+
+for lines in f_MSSM3.readlines():
+    discard = f_MSSM3.readline()
[…]

### 2017-10-17 figures/TreeLevelPlots/output_mr_900GeV/rel_plot.py

@@ -1,0 +1,206 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Dec  9 14:21:19 2015
+
+@author: sebastian
+"""
+
+import numpy as np
+from matplotlib import pyplot as plt
+from matplotlib import colors
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+m_squark = np.array([], dtype=float);
+# arrays for 1st parton reaction
+sigma1_MSSM = np.array([], dtype=float);
+# arrays for 2nd parton reaction
+sigma2 = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MSSM = np.array([], dtype=float);
+# arrays for 4th parton reaction
+sigma4_MSSM = np.array([], dtype=float);
+# arrays for 5th parton reaction
+sigma5_MSSM = np.array([], dtype=float);
+# arrays for 6th parton reaction
+sigma6 = np.array([], dtype=float);
+
+
+# arrays for 1st parton reaction
+sigma1_MRSSM = np.array([], dtype=float);
+# arrays for 3rd parton reaction
+sigma3_MRSSM = np.array([], dtype=float);
+# arrays for 4th parton reaction
+sigma4_MRSSM = np.array([], dtype=float);
+# arrays for 5th parton reaction
+sigma5_MRSSM = np.array([], dtype=float);
+
+
+
+f_MSSM1 = open('MSSM_1_qqbar_sqsqdagger.txt', 'r')
+
+for lines in f_MSSM1.readlines():
+    m_squark = np.append(m_squark, float(lines.split()[0]))
+    sigma1_MSSM = np.append(sigma1_MSSM, float(lines.split()[1]))
+
+f_MSSM1.close()
+
+
+f_2 = open('MSSM_MRSSM_2_GG_sqsq.txt', 'r')
+
+for lines in f_2.readlines():
+    discard = f_2.readline()
+    sigma2 = np.append(sigma2, float(lines.split()[1]))
+
+f_2.close()
+
+
+f_MSSM3 = open('MSSM_3_qq_sqsq.txt', 'r')
+
+for lines in f_MSSM3.readlines():
+    discard = f_MSSM3.readline()
[…]

### 2017-10-17 figures/WARB_TreeLevel/MSSM+MRSSM_mr=0,9.py
deleted old WARB scripts for tree level plots

@@ -1,429 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Wed Dec  9 14:21:19 2015
-
-@author: sebastian
-"""
-
-import numpy as np
-from matplotlib import pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-
-m_squark = np.array([], dtype=float);
-# arrays for 1st parton reaction
-sigma1_MSSM_dd = np.array([], dtype=float);
-sigma1_MSSM_du = np.array([], dtype=float);
-sigma1_MSSM_ds = np.array([], dtype=float);
-sigma1_MSSM_dc = np.array([], dtype=float);
-sigma1_MSSM_db = np.array([], dtype=float);
-
-sigma1_MSSM_uu = np.array([], dtype=float);
-sigma1_MSSM_us = np.array([], dtype=float);
-sigma1_MSSM_uc = np.array([], dtype=float);
-sigma1_MSSM_ub = np.array([], dtype=float);
-
-sigma1_MSSM_ss = np.array([], dtype=float);
-sigma1_MSSM_sc = np.array([], dtype=float);
-sigma1_MSSM_sb = np.array([], dtype=float);
-
-sigma1_MSSM_cc = np.array([], dtype=float);
-sigma1_MSSM_cb = np.array([], dtype=float);
-
-sigma1_MSSM_bb = np.array([], dtype=float);
-# arrays for 2nd parton reaction
-sigma2_MSSM = np.array([], dtype=float);
-# arrays for 3rd parton reaction
-sigma3_MSSM_dd = np.array([], dtype=float);
-sigma3_MSSM_du = np.array([], dtype=float);
-sigma3_MSSM_ds = np.array([], dtype=float);
-sigma3_MSSM_dc = np.array([], dtype=float);
-sigma3_MSSM_db = np.array([], dtype=float);
-
-sigma3_MSSM_uu = np.array([], dtype=float);
-sigma3_MSSM_us = np.array([], dtype=float);
-sigma3_MSSM_uc = np.array([], dtype=float);
-sigma3_MSSM_ub = np.array([], dtype=float);
-
-sigma3_MSSM_ss = np.array([], dtype=float);
[…]

### 2017-10-17 figures/WARB_TreeLevel/MSSM+MRSSM_mr=2.py

@@ -1,429 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Wed Dec  9 14:21:19 2015
-
-@author: sebastian
-"""
-
-import numpy as np
-from matplotlib import pyplot as plt
-from matplotlib import colors
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-
-m_squark = np.array([], dtype=float);
-# arrays for 1st parton reaction
-sigma1_MSSM_dd = np.array([], dtype=float);
-sigma1_MSSM_du = np.array([], dtype=float);
-sigma1_MSSM_ds = np.array([], dtype=float);
-sigma1_MSSM_dc = np.array([], dtype=float);
-sigma1_MSSM_db = np.array([], dtype=float);
-
-sigma1_MSSM_uu = np.array([], dtype=float);
-sigma1_MSSM_us = np.array([], dtype=float);
-sigma1_MSSM_uc = np.array([], dtype=float);
-sigma1_MSSM_ub = np.array([], dtype=float);
-
-sigma1_MSSM_ss = np.array([], dtype=float);
-sigma1_MSSM_sc = np.array([], dtype=float);
-sigma1_MSSM_sb = np.array([], dtype=float);
-
-sigma1_MSSM_cc = np.array([], dtype=float);
-sigma1_MSSM_cb = np.array([], dtype=float);
-
-sigma1_MSSM_bb = np.array([], dtype=float);
-# arrays for 2nd parton reaction
-sigma2_MSSM = np.array([], dtype=float);
-# arrays for 3rd parton reaction
-sigma3_MSSM_dd = np.array([], dtype=float);
-sigma3_MSSM_du = np.array([], dtype=float);
-sigma3_MSSM_ds = np.array([], dtype=float);
-sigma3_MSSM_dc = np.array([], dtype=float);
-sigma3_MSSM_db = np.array([], dtype=float);
-
-sigma3_MSSM_uu = np.array([], dtype=float);
-sigma3_MSSM_us = np.array([], dtype=float);
-sigma3_MSSM_uc = np.array([], dtype=float);
-sigma3_MSSM_ub = np.array([], dtype=float);
-
[…]

### 2017-10-17 figures/WARB_TreeLevel/MSSM+MRSSM_mr=5.py

@@ -1,429 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Wed Dec  9 14:21:19 2015
-
-@author: sebastian
-"""
-
-import numpy as np
-from matplotlib import pyplot as plt
-from matplotlib import colors
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-
-m_squark = np.array([], dtype=float);
-# arrays for 1st parton reaction
-sigma1_MSSM_dd = np.array([], dtype=float);
-sigma1_MSSM_du = np.array([], dtype=float);
-sigma1_MSSM_ds = np.array([], dtype=float);
-sigma1_MSSM_dc = np.array([], dtype=float);
-sigma1_MSSM_db = np.array([], dtype=float);
-
-sigma1_MSSM_uu = np.array([], dtype=float);
-sigma1_MSSM_us = np.array([], dtype=float);
-sigma1_MSSM_uc = np.array([], dtype=float);
-sigma1_MSSM_ub = np.array([], dtype=float);
-
-sigma1_MSSM_ss = np.array([], dtype=float);
-sigma1_MSSM_sc = np.array([], dtype=float);
-sigma1_MSSM_sb = np.array([], dtype=float);
-
-sigma1_MSSM_cc = np.array([], dtype=float);
-sigma1_MSSM_cb = np.array([], dtype=float);
-
-sigma1_MSSM_bb = np.array([], dtype=float);
-# arrays for 2nd parton reaction
-sigma2_MSSM = np.array([], dtype=float);
-# arrays for 3rd parton reaction
-sigma3_MSSM_dd = np.array([], dtype=float);
-sigma3_MSSM_du = np.array([], dtype=float);
-sigma3_MSSM_ds = np.array([], dtype=float);
-sigma3_MSSM_dc = np.array([], dtype=float);
-sigma3_MSSM_db = np.array([], dtype=float);
-
-sigma3_MSSM_uu = np.array([], dtype=float);
-sigma3_MSSM_us = np.array([], dtype=float);
-sigma3_MSSM_uc = np.array([], dtype=float);
-sigma3_MSSM_ub = np.array([], dtype=float);
-
[…]

### 2017-10-17 figures/WARB_TreeLevel/rel_weights_mr=0.9_MSSM+MRSSM.py

@@ -1,443 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Wed Dec  9 14:21:19 2015
-
-@author: sebastian
-"""
-
-import numpy as np
-from matplotlib import pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-def savitzky_golay(y, window_size, order, deriv=0, rate=1):
-    from math import factorial   
-    try:
-       window_size = np.abs(np.int(window_size))
-       order = np.abs(np.int(order))
-    except ValueError, msg:
-        raise ValueError("window_size and order have to be of type int")
-    if window_size % 2 != 1 or window_size < 1:
-        raise TypeError("window_size size must be a positive odd number")
-    if window_size < order + 2:
-        raise TypeError("window_size is too small for the polynomials order")
-    order_range = range(order+1)
-    half_window = (window_size -1) // 2
-    # precompute coefficients
-    b = np.mat([[k**i for i in order_range] for k in range(-half_window, half_window+1)])
-    m = np.linalg.pinv(b).A[deriv] * rate**deriv * factorial(deriv)
-    # pad the signal at the extremes with
-    # values taken from the signal itself
-    firstvals = y[0] - np.abs( y[1:half_window+1][::-1] - y[0] )
-    lastvals = y[-1] + np.abs(y[-half_window-1:-1][::-1] - y[-1])
-    y = np.concatenate((firstvals, y, lastvals))
-    return np.convolve( m[::-1], y, mode='valid')
-
-
-
-m_squark = np.array([], dtype=float);
-# MRSSM arrays
-# arrays for 1st parton reaction
-sigma1_MRSSM_dd = np.array([], dtype=float);
-sigma1_MRSSM_du = np.array([], dtype=float);
-sigma1_MRSSM_ds = np.array([], dtype=float);
[…]

### 2017-10-17 figures/WARB_TreeLevel/rel_weights_mr=2_MSSM+MRSSM.py

@@ -1,415 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Wed Dec  9 14:21:19 2015
-
-@author: sebastian
-"""
-
-import numpy as np
-from matplotlib import pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-
-m_squark = np.array([], dtype=float);
-# MRSSM arrays
-# arrays for 1st parton reaction
-sigma1_MRSSM_dd = np.array([], dtype=float);
-sigma1_MRSSM_du = np.array([], dtype=float);
-sigma1_MRSSM_ds = np.array([], dtype=float);
-sigma1_MRSSM_dc = np.array([], dtype=float);
-sigma1_MRSSM_db = np.array([], dtype=float);
-
-sigma1_MRSSM_uu = np.array([], dtype=float);
-sigma1_MRSSM_us = np.array([], dtype=float);
-sigma1_MRSSM_uc = np.array([], dtype=float);
-sigma1_MRSSM_ub = np.array([], dtype=float);
-
-sigma1_MRSSM_ss = np.array([], dtype=float);
-sigma1_MRSSM_sc = np.array([], dtype=float);
-sigma1_MRSSM_sb = np.array([], dtype=float);
-
-sigma1_MRSSM_cc = np.array([], dtype=float);
-sigma1_MRSSM_cb = np.array([], dtype=float);
-
-sigma1_MRSSM_bb = np.array([], dtype=float);
-# arrays for 2nd parton reaction
-sigma2_MRSSM = np.array([], dtype=float);
-# arrays for 3rd parton reaction
-sigma3_MRSSM_dd = np.array([], dtype=float);
-sigma3_MRSSM_du = np.array([], dtype=float);
-sigma3_MRSSM_ds = np.array([], dtype=float);
-sigma3_MRSSM_dc = np.array([], dtype=float);
-sigma3_MRSSM_db = np.array([], dtype=float);
-
-sigma3_MRSSM_uu = np.array([], dtype=float);
-sigma3_MRSSM_us = np.array([], dtype=float);
-sigma3_MRSSM_uc = np.array([], dtype=float);
-sigma3_MRSSM_ub = np.array([], dtype=float);
-
[…]

### 2017-10-17 figures/WARB_TreeLevel/rel_weights_mr=5_MSSM+MRSSM.py

@@ -1,415 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Wed Dec  9 14:21:19 2015
-
-@author: sebastian
-"""
-
-import numpy as np
-from matplotlib import pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-
-m_squark = np.array([], dtype=float);
-# MRSSM arrays
-# arrays for 1st parton reaction
-sigma1_MRSSM_dd = np.array([], dtype=float);
-sigma1_MRSSM_du = np.array([], dtype=float);
-sigma1_MRSSM_ds = np.array([], dtype=float);
-sigma1_MRSSM_dc = np.array([], dtype=float);
-sigma1_MRSSM_db = np.array([], dtype=float);
-
-sigma1_MRSSM_uu = np.array([], dtype=float);
-sigma1_MRSSM_us = np.array([], dtype=float);
-sigma1_MRSSM_uc = np.array([], dtype=float);
-sigma1_MRSSM_ub = np.array([], dtype=float);
-
-sigma1_MRSSM_ss = np.array([], dtype=float);
-sigma1_MRSSM_sc = np.array([], dtype=float);
-sigma1_MRSSM_sb = np.array([], dtype=float);
-
-sigma1_MRSSM_cc = np.array([], dtype=float);
-sigma1_MRSSM_cb = np.array([], dtype=float);
-
-sigma1_MRSSM_bb = np.array([], dtype=float);
-# arrays for 2nd parton reaction
-sigma2_MRSSM = np.array([], dtype=float);
-# arrays for 3rd parton reaction
-sigma3_MRSSM_dd = np.array([], dtype=float);
-sigma3_MRSSM_du = np.array([], dtype=float);
-sigma3_MRSSM_ds = np.array([], dtype=float);
-sigma3_MRSSM_dc = np.array([], dtype=float);
-sigma3_MRSSM_db = np.array([], dtype=float);
-
-sigma3_MRSSM_uu = np.array([], dtype=float);
-sigma3_MRSSM_us = np.array([], dtype=float);
-sigma3_MRSSM_uc = np.array([], dtype=float);
-sigma3_MRSSM_ub = np.array([], dtype=float);
-
[…]
